### 2018-10-15 main.tex
added main.tex from overleaf

\documentclass[english]{article}
%\usepackage[utf8]{inputenc}
\usepackage{subfig}
\usepackage{graphicx}
\usepackage{subfig}
\usepackage{babel,blindtext}
\usepackage{amsmath}
\usepackage{hyperref}
\usepackage{setspace}
\usepackage{apacite}
\usepackage{fancyhdr}
\pagestyle{fancy}
\usepackage{natbib}
\usepackage{pxfonts}
\usepackage[utf8]{inputenc}
\usepackage{xfrac}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
\fancyhead[R]{\thepage}
\usepackage{multirow,booktabs,setspace,caption}
\usepackage{tikz}
\captionsetup[figure]{labelsep=period,labelfont=it,justification=justified,
  singlelinecheck=false,font=doublespacing}
  \usepackage[left=1in,right=1in,top=1in,bottom=1in]{geometry}
\lhead{}
\fancyheadoffset[R]{0cm}
\cfoot{}

\fancypagestyle{first page}{
  \lhead{Running head: High-order dynamic correlations}
  \rhead{\thepage}
}

\begin{document}
\title{A scalable approach to inferring the high-order dynamic correlations underlying multi-dimensional timeseries data}
\author{Lucy L. W. Owen$^1$,
Paxton C. Fitzpatrick$^1$,
Kirsten Ziman$^1$,\\
Andrew C. Heusser$^1$,
Stephen F. Satterthwaite$^1$,
Thomas Hao Chang$^{1,2}$,
and\
Jeremy R. Manning\textsuperscript{$1, \dagger$}\\
[0.1in]$^1$Department of Psychological and Brain Sciences, Dartmouth College, Hanover, NH\\
$^2$Amazon.com, Seattle, WA\\
\textsuperscript{$\dagger$}Address correspondence to jeremy.r.manning@dartmouth.edu}

\begin{titlepage}
\thispagestyle{fancy}   
% \center
% \vspace*{\fill}
% \huge{}\\[0.5cm]

% \Large{author 1,
% author 2,
% author 3, and
% Jeremy R. Manning\textsuperscript{$\dagger$}}\\[0.5cm]

% \large{Department of Psychological and Brain Sciences, Dartmouth College, Hanover, NH 03755}\\[0.5cm]

% \textsuperscript{$\dagger$} Address correspondence to jeremy.r.manning@dartmouth.edu

% \vspace*{\fill}
\end{titlepage}

% \addtocounter{page}{1}
% \rhead{\thepage}

\maketitle

\begin{abstract}
Write an abstract...

\end{abstract}

\doublespacing

\section*{Introduction}
The dynamics of the observable universe are meaningful in three respects.  First, the behaviors of the \textit{atomic units} that exhibit those dynamics are highly interrelated.  The actions of one unit typically have implications for one or more other units.  In other words, there is non-trivial \textit{correlational structure} defining how different units interact with and relate to each other.  Second, that correlational structure is \textit{hierarchical} in the sense that it exists on many spatiotemporal scales.  The way one group of units interacts may relate to how another group of units interact, and the interactions between those groups may exhibit some rich structure.  Third, the structure at each level of this correlational hierarchy changes from moment to moment, reflecting the ``behavior'' of the full system.

These three properties (rich correlations, hierarchical organization, and dynamics) are major hallmarks of many complex systems.  For example, within a single cell, the cellular components interact at many spatiotemporal scales, and those interactions change according to what that single cell is doing.  Within a single human brain, the individual neurons interact within each brain structure, and the structures interact to form complex networks.  The interactions at each scale vary according to the functions our brains are carrying out.  And within social groups, interactions at different scales (e.g. between individuals, family units, communities, etc.) vary over time according to changing goals and external constraints.

Although many systems exhibit rich dynamic correlations at many scales, a major challenge to studying such patterns is that typically neither the correlations nor the hierarchical organizations of those correlations can be directly observed.  Rather, these fundamental properties must be inferred indirectly by examining the observable parts of the system-- e.g. the behaviors of the individual atomic units of that system.  Here we propose a series of mathematical operations that may be used to recover dynamic correlations at a range of scales.

There are two basic steps to our approach, which we describe in detail in the \textit{Methods} section.  In the first step, we take a number-of-timepoints ($T$) by number-of-features ($F$) \textit{matrix of observations} ($\mathbf{X}$) and we return a $T$ by $\frac{F^2 - F}{2}$ \textit{matrix of dynamic correlations} ($\mathbf{Y}$).  Here $\mathbf{Y_0}$ describes, at each moment, how all of the features (columns of $\mathbf{X}$) are inferred to be interacting.  (Since the interactions are assumed to be non-recurrent and symmetric, only the upper triangle of the full correlation matrix is computed.)  In the second step, we use a dimensionality reduction technique to project $\mathbf{Y_0}$ onto an $F$ dimensional space, resulting in a new $T$ by $F$ matrix $\mathbf{Y_1}$  Note that $\mathbf{Y_1}$ contains information about the correlation dynamics present in $\mathbf{X}$, but represented in a compressed number of dimensions.  By repeatedly applying these two steps in sequence, we can examine and explore higher order dynamic correlations in $\mathbf{X}$.  In the \textit{Results} section we demonstrate how our approach may be applied to multi-dimensional timeseries data in several domains: human brain data, financial data, social network data, and climate data.

\section*{Methods}

\begin{align}
\mathrm{corr}_t(x,y) &= \frac{\sum_{t=1}^T \left( x_t - \bar{x_t} \right) \left( y_t - \bar{y_t} \right)}{\sqrt{\sum_{t=1}^{T}\sigma ^{2}_{x_{t}}\sigma ^{2}_{y_{t}}}}\mathrm{, where}\\
\bar{a_t} &= \sum_{t=1}^T w(t)_i a_i\\
\sigma^{2}_{a_t} &= \sum_{t=1}^{T} \left(a_t - \bar{a_t} \right)^2\\
w(t) &= \mathcal{N}\left(1...T ~|~ t, \sigma_\mathcal{N}\right) %update to include eye, laplace, and gaussian weights
\end{align}

% \begin{equation}
% c(t) = \sum_{i=1}^{T}w(t)_{i}
% \end{equation}

\section*{Results}
%currently Lucy, Kirsten, and Paxton have agreed to make figures

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Discussion}

\subsection*{Concluding remarks}

\section*{Acknowledgements}
Our work was supported in part by DARPA RAN grant number XXXX and NSF EPSCoR Grant Number XXXX.  We acknowledge useful discussions with Luke Chang, Hany Farid, Qiang Liu, Matthijs van der Meer, and Emily Whitaker.  The content is solely the responsibility of the authors and does not necessarily represent the official views of our supporting organizations.

\bibliographystyle{apacite}
\bibliography{memlab}

\end{document}

### 2018-10-15 boneyard.tex
added boneyard.tex from overleaf

%should we introduce the name levelup in the introduction? ie. "in the second step, levelup, we use..." -ecw
%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Methods}
%%%%%%%%%%%%%%%%%%%%%%%%

The mathematical theories behind the timecorr approach for calculating the moment-by-moment dynamic correlations in systems are described here. The function takes a number-of-timepoint by number-of-features matrix as well as a weight function to determine a moment-by-moment correlations matrix. To calculate the correlations, expectation values are found using equation 1:

\begin{equation}
\mathrm{corr}_{x,y}(t) = \frac{1}{T} \sum_{t} \frac{\left(x(t)-\mathbb{E}[x]\right)\left(y(t)-\mathbb{E}[y]\right)}{\sigma_{x}(t)\sigma_{y}(t)}
\end{equation}

%should the variables in this equation/description change to match the description in the intro?
Here, x is the timepoint component of the matrix and y is the feature component. Timepoint by timepoint, x by x, at each given moment (t) in the matrix is subtracted from the expectation value of the full timepoint matrix. The same process occurs for the features points (y) at each timepoint (t). The product of these are then divided by the standard deviation at that moment for both the timepoint and the feature. Only the upper triangle of the matrix is calculated as the interactions are assumed to be both symmetric and non-recurrent.

Two weight parameters have been used to calculate the connectivity of the data are a Gaussian weight parameter, equation 2, and a LaPlace weights parameter, equation 3.

%label as Gaussian? 
\begin{equation}
\mathcal{N}\left( x | \mu, \sigma \right) = \frac{1}{\sqrt{2\pi\sigma^2}}\exp\left(-\frac{|| x - \mu ||^2}{2\sigma^2}\right)
\end{equation}
where sigma squared is the variance and mu is the expected value.

%label as LaPlace? 
\begin{equation}
\mathcal{L}\left( x | \mu, \lambda \right) = \frac{1}{2 \lambda}\left( x | \mu, \lambda \right) = \exp\left(-\frac{|x - \mu|}{\lambda}\right)
\end{equation}
where mu is the expectation values, lambda is a defined decay constant.

%figure showing the difference b/w two weights in same data set? Using the synthetic data?

When using the Gaussian weights parameter timepoints are more closely correlated to timepoints further away in the matrix than when using then the LaPlace weight function.

%Plot of kernels as Fig 1?

% New section? Mathematical Methods of Levelup? 
In order to understand how the data is interconnected we use the function levelup. Levelup uses the same input as the timecorr function, a timepoint-by-function matrix.

%Diagram of input-->timecorr-->PCaA= levelup?

In the levelup method the the data first goes through the timecorr process and then is reduced using Principal Component Analysis (PCA). By utilizing PCA the output data maintains the same features as the input method. Not only does this allow for a sanity check, but also it allows for repeated use of the function. Using PCA or other reduction techniques is needed as without it the output data would get exponentially large. On the flip side using PCA, or any dimensionality reduction technique, makes the output data less accurate as information is lost.

%PCA equation?
%figure/ chart of how many levels we "go up" before data gets too muddled- depends on the correlation?

Timepoints that share high similarity across all subjects have a high probability of being stimulus driven.

To compute the correlations of multiple subjects the across mode of both timecorr and levelup are used. The across function compares one voxel in a sample to the averages of that voxel in the rest of the dataframe. This occurs throughout every voxel in the dataset. The output of the across mode is a correlation matrix that is a number of timepoints by features matrix.

%F^2-F/2 +F

### 2018-10-15 paper/main.tex
added some notes

--- 2018-10-15 main.tex
@@
 \fancypagestyle{first page}{
-  \lhead{Running head: High-order dynamic correlations}
+  \lhead{Running head: High-order dynamic interactions}
   \rhead{\thepage}
@@
 \begin{document}
-\title{A scalable approach to inferring the high-order dynamic correlations underlying multi-dimensional timeseries data}
+\title{An examination of the high-order dynamic interactions underlying multi-dimensional timeseries data}
 \author{Lucy L. W. Owen$^1$,
@@
 Kirsten Ziman$^1$,\\
-Andrew C. Heusser$^1$,
+Andrew C. Heusser$^{1,2}$,
 Stephen F. Satterthwaite$^1$,
-Thomas Hao Chang$^{1,2}$,
+Thomas Hao Chang$^{1,3}$,\\
+Qiang Liu$^{1,4}$,
 and\
 Jeremy R. Manning\textsuperscript{$1, \dagger$}\\
-[0.1in]$^1$Department of Psychological and Brain Sciences, Dartmouth College, Hanover, NH\\
-$^2$Amazon.com, Seattle, WA\\
+[0.1in]$^1$Department of Psychological and Brain Sciences,\\Dartmouth
+College, Hanover, NH\\
+$^2$Akili Interactive, Inc, Boston, MA\\
+$^3$Amazon.com, Seattle, WA\\
+$^4$Department of Computer Science,\\University of Texas at Austin,
+Austin, TX\\
 \textsuperscript{$\dagger$}Address correspondence to jeremy.r.manning@dartmouth.edu}
@@
 \begin{abstract}
-Write an abstract...
-
+Most complex systems reflect dynamic interations between myriad
+evolving components (e.g., interacting molecules, interacting brain
+systems, interacting individuals within a social network or ecological
+system, coordinated components within a mechanical or digital device, etc.).  
+Despite that these interactions are central to the full system's
+behavior (e.g., removing a component from the full system can
+change the entire system's behavior), dynamic interactions cannot
+typically be directly measured.  Rather, the interactions must be
+inferred through their hypothesized role in guiding the dynamics of
+system components.  Here we use a model-based approach to inferring
+dynamic interactions from timeseries data.  In addition to examining
+first-order interactions (e.g., between pairs of components) we also
+examine higher-order interactions (e.g., that characterize mirrored
+structure in the patterns of interaction dynamics displayed by
+different subsets of components).  We apply our approach to two
+datasets.  First, we use a synthetic dataset, for which the underlying dynamic
+interactions are known, to show that our model recovers those
+ground-truth dynamic interactions.  We also apply our model to a
+neuroimaging dataset and show that the high-order dynamic interactions
+exhibited by brain data vary meaningfully as a function of the
+cognitive ``richness'' of the stimulus people are experiencing.
 \end{abstract}
@@
 \section*{Introduction}
-The dynamics of the observable universe are meaningful in three respects.
-First, the behaviors of the \textit{atomic units} that exhibit those dynamics are highly interrelated.
-The actions of one unit typically have implications for one or more other units.
-In other words, there is non-trivial \textit{correlational structure} defining how different units interact with and relate to each other.
-Second, that correlational structure is \textit{hierarchical} in the sense that it exists on many spatiotemporal scales.
-The way one group of units interacts may relate to how another group of units interact, and the interactions between those groups may exhibit some rich structure.
-Third, the structure at each level of this correlational hierarchy changes from moment to moment, reflecting the ``behavior'' of the full system.
+The dynamics of the observable universe are meaningful in three
+respects.  First, the behaviors of the \textit{atomic units} that
+exhibit those dynamics are highly interrelated.  The actions of one
+unit typically have implications for one or more other units.  In
+other words, there is non-trivial \textit{correlational structure}
+defining how different units interact with and relate to each other.
+Second, that correlational structure is \textit{hierarchical} in the
+sense that it exists on many spatiotemporal scales.  The way one group
+of units interacts may relate to how another group of units interact,
+and the interactions between those groups may exhibit some rich
+structure.  Third, the structure at each level of this correlational
+hierarchy changes from moment to moment, reflecting the ``behavior''
+of the full system.
 
-These three properties (rich correlations, hierarchical organization, and dynamics) are major hallmarks of many complex systems.
-For example, within a single cell, the cellular components interact at many spatiotemporal scales, and those interactions change according to what that single cell is doing.
-Within a single human brain, the individual neurons interact within each brain structure, and the structures interact to form complex networks.
-The interactions at each scale vary according to the functions our brains are carrying out.
-And within social groups, interactions at different scales (e.g.
-between individuals, family units, communities, etc.) vary over time according to changing goals and external constraints.
+These three properties (rich correlations, hierarchical organization,
+and dynamics) are major hallmarks of many complex systems.  For
+example, within a single cell, the cellular components interact at
+many spatiotemporal scales, and those interactions change according to
+what that single cell is doing.  Within a single human brain, the
+individual neurons interact within each brain structure, and the
+structures interact to form complex networks.  The interactions at
+each scale vary according to the functions our brains are carrying
+out.  And within social groups, interactions at different scales
+(e.g., between individuals, family units, communities, etc.) vary over
+time according to changing goals and external constraints.
 
-Although many systems exhibit rich dynamic correlations at many scales, a major challenge to studying such patterns is that typically neither the correlations nor the hierarchical organizations of those correlations can be directly observed.
-Rather, these fundamental properties must be inferred indirectly by examining the observable parts of the system-- e.g.
-the behaviors of the individual atomic units of that system.
-Here we propose a series of mathematical operations that may be used to recover dynamic correlations at a range of scales.
-
-There are two basic steps to our approach, which we describe in detail in the \textit{Methods} section.
-In the first step, we take a number-of-timepoints ($T$) by number-of-features ($F$) \textit{matrix of observations} ($\mathbf{X}$) and we return a $T$ by $\frac{F^2 - F}{2}$ \textit{matrix of dynamic correlations} ($\mathbf{Y}$).
-Here $\mathbf{Y_0}$ describes, at each moment, how all of the features (columns of $\mathbf{X}$) are inferred to be interacting.
-(Since the interactions are assumed to be non-recurrent and symmetric, only the upper triangle of the full correlation matrix is computed.)  In the second step, we use a dimensionality reduction technique to project $\mathbf{Y_0}$ onto an $F$ dimensional space, resulting in a new $T$ by $F$ matrix $\mathbf{Y_1}$  Note that $\mathbf{Y_1}$ contains information about the correlation dynamics present in $\mathbf{X}$, but represented in a compressed number of dimensions.
-By repeatedly applying these two steps in sequence, we can examine and explore higher order dynamic correlations in $\mathbf{X}$.
-In the \textit{Results} section we demonstrate how our approach may be applied to multi-dimensional timeseries data in several domains: human brain data, financial data, social network data, and climate data.
+Although many systems exhibit rich dynamic correlations at many
+scales, a major challenge to studying such patterns is that typically
+neither the correlations nor the hierarchical organizations of those
+correlations may be directly observed.  Rather, these fundamental
+properties must be inferred indirectly by examining the observable
+parts of the system-- e.g., the behaviors of the individual atomic
+units of that system.  In the \textit{Methods} section, we propose a
+series of mathematical operations that may be used to recover dynamic
+correlations at a range of scales (i.e., orders of interaction).  In
+the \textit{Results} section, we demonstrate how our approach may be
+applied to multi-dimensional timeseries data: a synthetic dataset
+where the underlying dynamic correlations are known (we use this
+dataset to validate our approach), and a neuroimaging dataset
+comprising data collected as participants listened to a
+story~\citep{SimoEtal16}.  In different experimental conditions in the
+neuroimaging study, participants listened to altered versions of the
+story that varied in cognitive richness: the intact story (fully
+engaging), a scrambled version of the story where the paragraphs were
+presented in a randomized order (moderately engaging), a second
+scrambled condition where the words were presented in a random order
+(minimally engaging), and a ``rest'' condition where the participants
+did not listen to any version of the story (control condition).  We
+use the neuroimaging dataset to examine how higher-order structure in
+brain data varies as a function of the cognitive richness of the
+stimulus.
 
 \section*{Methods}
+There are two basic steps to our approach.  In the first step, we take
+a number-of-timepoints ($T$) by number-of-features ($F$)
+\textit{matrix of observations} ($\mathbf{X}$) and we return a $T$ by
+$\frac{F^2 - F}{2}$ \textit{matrix of dynamic correlations}
+($\mathbf{Y}$).  Here $\mathbf{Y_0}$ describes, at each moment, how
+all of the features (columns of $\mathbf{X}$) are inferred to be
+interacting.  (Since the interactions are assumed to be non-recurrent
+and symmetric, only the upper triangle of the full correlation matrix
+is computed.)  In the second step, we project $\mathbf{Y_0}$ onto an
+$F$-dimensional space, resulting in a new $T$ by $F$ matrix
+$\mathbf{Y_1}$.  Note that $\mathbf{Y_1}$ contains information about
+the correlation dynamics present in $\mathbf{X}$, but represented in a
+compressed number of dimensions.  By repeatedly applying these two
+steps in sequence, we can examine and explore higher order dynamic
+correlations in $\mathbf{X}$.
 
@@
 \section*{Discussion}
+% multiple timescale representations (a la Hasson group) implies
+% first-order network interactions.  higher-order interactions imply
+% generalizations between interacting representations (e.g. mirrored
+% schema, a la Norman/Baldassano/Hasson).  possibly cite NTB 2013
+% science review, using as evidence that this is where the field is
+% going (voxels --> patterns (L0) --> interactions (L1) --> higher
+% order patterns (L2+).
+
+% related approaches: sliding window, phase-based correlations,
+% within-ROI spatial correlations at each timepoint, granger
+% causality, other explit models (e.g. virtual brain).
+
+%other applications: molecular interactions (protein folding?),
+%diagnosis (e.g. psychiatric disorders as network flow problems--
+%gratton work?), social network dynamics (e.g. financial markets,
+%social media interactions)
 
 \subsection*{Concluding remarks}
+% the universe is complicated and we need scalable approaches to
+% studying how the pieces are interacting to make sense of it.  one
+% small step for mankind, and so on.
 
 \section*{Acknowledgements}
-Our work was supported in part by DARPA RAN grant number XXXX and NSF EPSCoR Grant Number XXXX.
-We acknowledge useful discussions with Luke Chang, Hany Farid, Qiang Liu, Matthijs van der Meer, and Emily Whitaker.
-The content is solely the responsibility of the authors and does not necessarily represent the official views of our supporting organizations.
+We acknowledge useful discussions with Luke Chang, Hany Farid,
+Matthijs van der Meer, and Emily Whitaker. Our work was supported in
+part by NSF EPSCoR Award Number 1632738 to J.R.M. and by a sub-award
+of DARPA RAM Cooperative Agreement N66001-14-2-4-032 to J.R.M.  The
+content is solely the responsibility of the authors and does not
+necessarily represent the official views of our supporting
+organizations.
 
 \bibliographystyle{apacite}
-\bibliography{memlab}
+\bibliography{CDL-bibliography/memlab}
 

### 2018-10-15 paper/main.tex
working on methods section

@@
 \documentclass[english]{article}
-%\usepackage[utf8]{inputenc}
-\usepackage{subfig}
 \usepackage{graphicx}
-\usepackage{subfig}
-\usepackage{babel,blindtext}
 \usepackage{amsmath}
@@
 \usepackage{apacite}
-\usepackage{fancyhdr}
-\pagestyle{fancy}
 \usepackage{natbib}
@@
 \usepackage[utf8]{inputenc}
-\usepackage{xfrac}
-\fancyhf{}
-\renewcommand{\headrulewidth}{0pt}
-\fancyhead[R]{\thepage}
-\usepackage{multirow,booktabs,setspace,caption}
-\usepackage{tikz}
-\captionsetup[figure]{labelsep=period,labelfont=it,justification=justified,
-  singlelinecheck=false,font=doublespacing}
 \usepackage[left=1in,right=1in,top=1in,bottom=1in]{geometry}
-\lhead{}
-\fancyheadoffset[R]{0cm}
-\cfoot{}
+\usepackage[left]{lineno}
+\linenumbers
 
-\fancypagestyle{first page}{
-  \lhead{Running head: High-order dynamic interactions}
-  \rhead{\thepage}
-}
+\title{An examination of the high-order dynamic interactions
+  underlying multi-dimensional timeseries data} \author{Lucy
+  L. W. Owen$^1$, Thomas Hao Chang$^{1,2}$, and\
+  Jeremy R. Manning\textsuperscript{$1, \dagger$}\\
+  [0.1in]$^1$Department of Psychological and Brain
+  Sciences,\\Dartmouth
+  College, Hanover, NH\\
+  $^3$Amazon.com, Seattle, WA\\
+  \textsuperscript{$\dagger$}Address correspondence to
+  jeremy.r.manning@dartmouth.edu}
 
 \begin{document}
-\title{An examination of the high-order dynamic interactions underlying multi-dimensional timeseries data}
-\author{Lucy L. W. Owen$^1$,
-Paxton C. Fitzpatrick$^1$,
-Kirsten Ziman$^1$,\\
-Andrew C. Heusser$^{1,2}$,
-Stephen F. Satterthwaite$^1$,
-Thomas Hao Chang$^{1,3}$,\\
-Qiang Liu$^{1,4}$,
-and\
-Jeremy R. Manning\textsuperscript{$1, \dagger$}\\
-[0.1in]$^1$Department of Psychological and Brain Sciences,\\Dartmouth
-College, Hanover, NH\\
-$^2$Akili Interactive, Inc, Boston, MA\\
-$^3$Amazon.com, Seattle, WA\\
-$^4$Department of Computer Science,\\University of Texas at Austin,
-Austin, TX\\
-\textsuperscript{$\dagger$}Address correspondence to jeremy.r.manning@dartmouth.edu}
-
-\begin{titlepage}
-\thispagestyle{fancy}   
-% \center
-% \vspace*{\fill}
-% \huge{}\\[0.5cm]
-
-% \Large{author 1,
-% author 2,
-% author 3, and
-% Jeremy R. Manning\textsuperscript{$\dagger$}}\\[0.5cm]
-
-% \large{Department of Psychological and Brain Sciences, Dartmouth College, Hanover, NH 03755}\\[0.5cm]
-
-% \textsuperscript{$\dagger$} Address correspondence to jeremy.r.manning@dartmouth.edu
-
-% \vspace*{\fill}
-\end{titlepage}
-
-% \addtocounter{page}{1}
-% \rhead{\thepage}
-
 \maketitle
@@
   evolving components (e.g., interacting molecules, interacting brain
-systems, interacting individuals within a social network or ecological
-system, coordinated components within a mechanical or digital device, etc.).  
-Despite that these interactions are central to the full system's
-behavior (e.g., removing a component from the full system can
-change the entire system's behavior), dynamic interactions cannot
-typically be directly measured.  Rather, the interactions must be
-inferred through their hypothesized role in guiding the dynamics of
-system components.  Here we use a model-based approach to inferring
-dynamic interactions from timeseries data.  In addition to examining
-first-order interactions (e.g., between pairs of components) we also
-examine higher-order interactions (e.g., that characterize mirrored
-structure in the patterns of interaction dynamics displayed by
-different subsets of components).  We apply our approach to two
-datasets.  First, we use a synthetic dataset, for which the underlying dynamic
-interactions are known, to show that our model recovers those
-ground-truth dynamic interactions.  We also apply our model to a
-neuroimaging dataset and show that the high-order dynamic interactions
-exhibited by brain data vary meaningfully as a function of the
-cognitive ``richness'' of the stimulus people are experiencing.
+  systems, interacting individuals within a social network or
+  ecological system, coordinated components within a mechanical or
+  digital device, etc.).  Despite that these interactions are central
+  to the full system's behavior (e.g., removing a component from the
+  full system can change the entire system's behavior), dynamic
+  interactions cannot typically be directly measured.  Rather, the
+  interactions must be inferred through their hypothesized role in
+  guiding the dynamics of system components.  Here we use a
+  model-based approach to inferring dynamic interactions from
+  timeseries data.  In addition to examining first-order interactions
+  (e.g., between pairs of components) we also examine higher-order
+  interactions (e.g., that characterize mirrored structure in the
+  patterns of interaction dynamics displayed by different subsets of
+  components).  We apply our approach to two datasets.  First, we use
+  a synthetic dataset, for which the underlying dynamic interactions
+  are known, to show that our model recovers those ground-truth
+  dynamic interactions.  We also apply our model to a neuroimaging
+  dataset and show that the high-order dynamic interactions exhibited
+  by brain data vary meaningfully as a function of the cognitive
+  ``richness'' of the stimulus people are experiencing.
 \end{abstract}
@@
 
+\subsection*{Dynamic correlations}
+Given a matrix of observations, we can compute the (static)
+correlations between any pair of observations, $\mathbf{X}_i$ and
+$\mathbf{X}_j$ using:
+\begin{align}
+  \mathrm{corr}(\mathbf{X}_i, \mathbf{X}_j) &= \frac{\sum_{t=1}^T \left(\mathbf{X}_i(t)
+                                              -
+                                              \hat{\mathbf{X}_i}\right) \left(\mathbf{X}_j(t)
+                                              -
+                                              \hat{\mathbf{X}_j}\right)}{\sqrt{\sum_{t=1}^T\left(
+                                              \sigma^2_{\mathbf{X}_i}\right) \left(
+                                              \sigma^2_{\mathbf{X}_j}\right)}},~\mathrm{where}\\
+                                    \hat{\mathbf{X}_k} &= \sum_{t=1}^T
+                                                         \mathbf{X}_k(t),~\mathrm{and}\\
+  \sigma^2_{\mathbf{X}_k} &= \sum_{t=1}^T \left( \mathbf{X}_k -
+                            \hat{\mathbf{X}_k} \right)^2 
+\end{align}
+
+We can generalize this formula to compute time-varying correlations by
+incorporating a \textit{weight function} that takes a time $t$ as input,
+and returns how much the observed data every timepoint (including $t$)
+contribute to the correlations at time $t$.
+%include figure showing weights (https://github.com/ContextLab/timecorr-paper/issues/1)
+
+\textbf{JRM STOPPED HERE}
 \begin{align}
@@
 \section*{Acknowledgements}
-We acknowledge useful discussions with Luke Chang, Hany Farid,
-Matthijs van der Meer, and Emily Whitaker. Our work was supported in
+We acknowledge discussions with Luke Chang, Hany Farid, Paxton
+Fitzpatrick, Andrew Heusser, Eshin Jolly, Qiang Liu, Matthijs van der
+Meer, Judith Mildner, Gina Notaro, Stephen Satterthwaite, Emily
+Whitaker, Weizhen Xie, and Kirsten Ziman. Our work was supported in
 part by NSF EPSCoR Award Number 1632738 to J.R.M. and by a sub-award
@@
 
+\section*{Author contributions}
+Concept: J.R.M.  Implementation: T.H.C., L.L.W.O., and
+J.R.M.  Analyses: L.L.W.O and J.R.M.
+
 \bibliographystyle{apacite}

### 2018-10-16 paper/main.tex
made kernels figure

@@
 and returns how much the observed data every timepoint (including $t$)
-contribute to the correlations at time $t$.
+contribute to the correlations at time $t$ (Fig.~\ref{fig:weights}).
+\begin{figure}
+  \centering
+  \includegraphics[width=\textwidth]{figs/kernels}
+  \caption{\textbf{Examples of time-varying weights.  Each panel
+    displays per-timepoint weights computed for 100 timepoints
+    ($0, 1, ..., 99$) with $t = 50$.  a. Uniform weights.} The weights
+  are timepoint-invariant; all timepoints are weighted equally, and do
+  not change as a function of $t$.  This is a special case of weight
+  function that reduces dynamic correlations to static correlations.
+  \textbf{b. Dirac delta function.} Only the timepoint $t$ is given
+  weight (of 1), and all other timepoints' weights are set to 0.
+  \textbf{c. Gaussian weights.} Each timepoint's weights fall off
+  according to a Gaussian probability density function centered on
+  $\mu = t$.  Weights derived using several different example variance
+  parameters ($\sigma^2$ are displayed.  \textbf{d. Laplace weights.}
+  Each timepoint's weights fall off according to a Laplace probability
+  density function centered on $\mu = t$.  Weights derived using
+  several different example scale parameters ($b$) are displayed.}
+  \label{fig:weights}
+\end{figure}
+
 %include figure showing weights (https://github.com/ContextLab/timecorr-paper/issues/1)

### 2018-10-16 paper/main.tex
added mexican hat kernel, working on levelup in methods [WIP]

@@
                                               -
-                                              \hat{\mathbf{X}_j}\right)}{\sqrt{\sum_{t=1}^T\left(
-                                              \sigma^2_{\mathbf{X}_i}\right) \left(
-                                              \sigma^2_{\mathbf{X}_j}\right)}},~\mathrm{where}\\
+                                              \hat{\mathbf{X}_j}\right)}{\sqrt{\sum_{t=1}^T
+                                              \sigma^2_{\mathbf{X}_i} 
+                                              \sigma^2_{\mathbf{X}_j}}},~\mathrm{where}\\\label{eqn:corr}
   \hat{\mathbf{X}_k} &= \sum_{t=1}^T
@@
   \caption{\textbf{Examples of time-varying weights.  Each panel
-    displays per-timepoint weights computed for 100 timepoints
-    ($0, 1, ..., 99$) with $t = 50$.  a. Uniform weights.} The weights
-  are timepoint-invariant; all timepoints are weighted equally, and do
-  not change as a function of $t$.  This is a special case of weight
-  function that reduces dynamic correlations to static correlations.
-  \textbf{b. Dirac delta function.} Only the timepoint $t$ is given
-  weight (of 1), and all other timepoints' weights are set to 0.
-  \textbf{c. Gaussian weights.} Each timepoint's weights fall off
-  according to a Gaussian probability density function centered on
-  $\mu = t$.  Weights derived using several different example variance
-  parameters ($\sigma^2$ are displayed.  \textbf{d. Laplace weights.}
-  Each timepoint's weights fall off according to a Laplace probability
+      displays per-timepoint weights at $t = 50$, evaluated for 100
+      timepoints ($1, ..., 100$).  a. Uniform weights.} The weights
+    are timepoint-invariant; observations at all timepoints are
+    weighted equally, and do not change as a function of $t$.  This is
+    a special case of weight function that reduces dynamic
+    correlations to static correlations.  \textbf{b. Dirac delta
+      function.} Only the observation at timepoint $t$ is given weight
+    (of 1), and weights for observations at all other timepoints are
+    set to 0.  \textbf{c. Gaussian weights.} Each observation's
+    weights fall off in time according to a Gaussian probability
     density function centered on $\mu = t$.  Weights derived using
-  several different example scale parameters ($b$) are displayed.}
+    several different example variance parameters ($\sigma^2$ are
+    displayed.  \textbf{d. Laplace weights.}  Each observation's
+    weights fall off in time according to a Laplace probability
+    density function centered on $\mu = t$.  Weights derived using
+    several different example scale parameters ($b$) are displayed.
+    \textbf{e. Mexican hat (Ricker wavelet) weights.}  Each
+    observation's weights fall off in time according to a Ricker
+    wavelet centered on $t$.  Weights derived using several different
+    example width parameters ($\sigma$) are displayed.}
   \label{fig:weights}
@@
 
-%include figure showing weights (https://github.com/ContextLab/timecorr-paper/issues/1)
+Given a weight function $w(t)$ for timepoint $t$, evaluated at
+timepoints in the interval $\left[ 1, ..., T \right]$, we can extend the static correlation formula
+in Equation~\ref{eqn:corr} to reflect an \textit{instantaneous
+  correlation} at timepoint $t$:
+\begin{align}
+  \mathrm{timecorr}(\mathbf{X}_i, \mathbf{X}_j, t) &= \frac{\sum_{t=1}^T \left(\mathbf{X}_i(t)
+                                              -
+                                              \widetilde{\mathbf{X}}_i(t)\right) \left(\mathbf{X}_j(t)
+                                              -
+                                              \widetilde{\mathbf{X}}_j(t)\right)}{\sqrt{\sum_{t=1}^T
+                                              \widetilde{\sigma}^2_{\mathbf{X}_i}(t) 
+                                              \widetilde{\sigma}^2_{\mathbf{X}_j}}(t)},~\mathrm{where}\\\label{eqn:timecorr}
+  \widetilde{\mathbf{X}}_k(t) &= \sum_{i=1}^T
+                       w(t, i)\mathbf{X}_k(i),\\
+  \widetilde{\sigma}^2_{\mathbf{X}_k}(t) &= \sum_{i=1}^T \left( \mathbf{X}_k(i) -
+                            \widetilde{\mathbf{X}}_k(t) \right)^2,
+\end{align}
+and $w(t, i)$ is shorthand for $w(t)$ evaluated at timepoint $i$.
+Equation~\ref{eqn:timecorr} may be used to estimate the instantaneous
+correlations between every pair of observations, at each timepoint
+(i.e., $\mathbf{Y}$).
+
+\subsection*{Higher-order correlations}
+Given a timeseries of dynamic correlations (e.g., obtained using
+Eqn.~\ref{eqn:timecorr}), higher-order correlations reflect the
+dynamic correlations between columns of $\mathbf{Y}$.  Given unlimited
+computing resources, one could use repeated applications of
+Equation~\ref{eqn:timecorr} to estimate these higher-order
+correlations (i.e., substituting in the previous output, $\mathbf{Y}$,
+for the input, $\mathbf{X}$ in the equation).  However, because each output
+$\mathbf{Y}$ has $O(F^2)$ columns relative to $F$ columns in the input
+$\mathbf{X}$, the output of Equation~\ref{eqn:timecorr} grows with the
+square of the number of repeated applications.  When $F$ is large,
+this approach quickly becomes intractable.
 
 \textbf{JRM STOPPED HERE}
-\begin{align}
-\mathrm{corr}_t(x,y) &= \frac{\sum_{t=1}^T \left( x_t - \bar{x_t} \right) \left( y_t - \bar{y_t} \right)}{\sqrt{\sum_{t=1}^{T}\sigma ^{2}_{x_{t}}\sigma ^{2}_{y_{t}}}}\mathrm{, where}\\
-\bar{a_t} &= \sum_{t=1}^T w(t)_i a_i\\
-\sigma^{2}_{a_t} &= \sum_{t=1}^{T} \left(a_t - \bar{a_t} \right)^2\\
-w(t) &= \mathcal{N}\left(1...T ~|~ t, \sigma_\mathcal{N}\right) %update to include eye, laplace, and gaussian weights
-\end{align}
 
-% \begin{equation}
-% c(t) = \sum_{i=1}^{T}w(t)_{i}
-% \end{equation}
+\subsection*{Timepoint decoding}
+
+\subsection*{Prediction}
 

### 2018-10-16 paper/main.tex
checking in changes-- levelup [WIP]

@@
                                               -
-                                              \hat{\mathbf{X}_i}\right) \left(\mathbf{X}_j(t)
+                                              \bar{\mathbf{X}_i}\right) \left(\mathbf{X}_j(t)
                                               -
-                                              \hat{\mathbf{X}_j}\right)}{\sqrt{\sum_{t=1}^T
+                                              \bar{\mathbf{X}_j}\right)}{\sqrt{\sum_{t=1}^T
                                               \sigma^2_{\mathbf{X}_i} 
                                               \sigma^2_{\mathbf{X}_j}}},~\mathrm{where}\\\label{eqn:corr}
-  \hat{\mathbf{X}_k} &= \sum_{t=1}^T
+  \bar{\mathbf{X}_k} &= \sum_{t=1}^T
                        \mathbf{X}_k(t),~\mathrm{and}\\
   \sigma^2_{\mathbf{X}_k} &= \sum_{t=1}^T \left( \mathbf{X}_k -
-                            \hat{\mathbf{X}_k} \right)^2 
+                            \bar{\mathbf{X}_k} \right)^2 
 \end{align}
@@
 correlations (i.e., substituting in the previous output, $\mathbf{Y}$,
-for the input, $\mathbf{X}$ in the equation).  However, because each output
-$\mathbf{Y}$ has $O(F^2)$ columns relative to $F$ columns in the input
-$\mathbf{X}$, the output of Equation~\ref{eqn:timecorr} grows with the
-square of the number of repeated applications.  When $F$ is large,
+for the input, $\mathbf{X}$ in the equation).  However, because each
+output $\mathbf{Y}$ has $O(F^2)$ columns relative to $F$ columns in
+the input $\mathbf{X}$, the output of Equation~\ref{eqn:timecorr}
+grows with the square of the number of repeated applications (total
+cost of computing $n$\textsuperscript{th} order correlations is
+$O(F^{2(n - 1)})$ for $n \in \mathcal{J}, n > 0$).  When $F$ or $n$ is large,
 this approach quickly becomes intractable.
+
+To make progress in computing $\mathbf{Y_{n+1}}$, we can approximate
+$\mathbf{Y}_n$ by computing an $O(F)$-dimensional embedding of
+$\mathbf{Y}_n$, termed $\hat{\mathbf{Y}}_n$, and then we can apply
+Equation~\ref{eqn:timecorr} to $\hat{\mathbf{Y}}_n$ rather than
+directly to $\mathbf{Y}_n$.  This enables us to maintain $O(n)$
+scaling with respect to $n$, rather than exponential scaling via the
+direct approach.
+
+There are many possible methods for computing $\hat{\mathbf{Y}}_n$
+from $\mathbf{Y}_n$, including traditional dimensionality reduction
+approaches and graph theory based approaches as described next.  In the
+\textit{Discussion} section we elaborate on other potential approaches.
+
+\subsubsection*{Dimensionality reduction-based approaches to computing
+  $\hat{\mathbf{Y}}_n$}
+
+Commonly used dimensionality reduction algorithms include Principal
+Components Analysis~\citep[PCA; ][]{Pear01}, Probabilistic
+PCA~\citep[PPCA; ][]{TippBish99}, Exploratory Factor
+Analysis~\citep[EFA; ][]{Spea04}, Independent Components
+Analysis~\citep[ICA; ][]{JuttHera91, ComoEtal91}, $t$-Stochastic
+Neighbor Embedding~\citep[$t$-SNE; ][]{MaatHint08}, Uniform Manifold
+Approximation and Projection~\citep[UMAP; ][]{McInHeal18},
+non-negative matrix factorization~\citep[NMF; ][]{LeeSeun99},
+Topographic Factor Analysis (TFA)~\cite{MannEtal14b}, Hierarchical
+Topographic Factor analysis (HTFA)~\cite{MannEtal18}, Topographic
+Latent Source Analysis (TLSA)~\cite{GersEtal11}, Dictionary
+learning~\citep{MairEtal09a, MairEtal09b}, deep
+autoencoders~\citep{HintSala06}, among others.  While complete
+characterizations of each of these algorithms is beyond the scope of
+the present manuscript, the general intuition driving these
+approaches is to compute the $\hat{\mathbf{Y}}$ with $i$ columns that
+is closest to the original $\mathbf{Y}$ with $j$ columns, and where
+(typically) $i \ll j$.  The different approaches place different
+constraints on what properties $\hat{\mathbf{Y}}$ must satisfy and
+which aspects of the data are compared (and how) to characterize the
+match between $\hat{\mathbf{Y}}$ and  $\mathbf{Y}$.
+
+\subsubsection*{Graph theory-based approaches to computing
+  $\hat{\mathbf{Y}}_n$}
+
+\textbf{JRM TODO: Need references for each of the below, plus citation
+  of \href{https://github.com/aestrivex/bctpy/wiki}{bctpy toolbox} (source of measures listed below)}
+\begin{itemize}
+\item Betweenness centrality: Wei; Node Betweenness; edge betweenness
+  centrality; edge betweeness wei; 
+\item Shannon-entropy based diversity coefficient
+\item Eigenvector centrality, pagerank centrality
+\item flow coefficient (Honey et al. 2007, PNAS)
+\item k-coreness centrality (directed, undirected)
+\item within-module degree
+\item participation coefficient (signed, unsigned)
+\item subgraph centrality
+\end{itemize}
+
+Idea: for each timepoint, compute relevant measure for node.  Result:
+a $T$ by $F$ matrix characterizing how the given measure for each node
+over time.  We can use this as $\hat{\mathbf{Y}}_n$ and then apply
+Equation~\ref{eqn:timecorr} to compute $\hat{\mathbf{Y}}_{n+1}.$
 
@@
 \subsection*{Timepoint decoding}
+Cite HTFA paper, summarize relevant methods.
 
 \subsection*{Prediction}
+Use Eqn. 12 from SuperEEG paper, extend notation to treat
+$\hat{\mathbf{Y}}_{1...n}(1...(t-1))$ as ``observed'' and use this to
+predict $\mathbf{X}(t)$.  Key question: what is the predictive power
+added by each new level.
 
 \section*{Results}
-%currently Lucy, Kirsten, and Paxton have agreed to make figures
+\subsubsection*{Synthetic data}
+\subsubsection*{Neuroimaging dataset~\citep{SimoEtal16}}
 

### 2018-10-16 paper/main.tex
finished pass through timecorr-specific methods; still need to describe evaluation metrics

@@
 \usepackage[left]{lineno}
+\usepackage{soul}
 \linenumbers
@@
 for the input, $\mathbf{X}$ in the equation).  However, because each
-output $\mathbf{Y}$ has $O(F^2)$ columns relative to $F$ columns in
+output $\mathbf{Y}$ has $\mathcal{O}(F^2)$ columns relative to $F$ columns in
 the input $\mathbf{X}$, the output of Equation~\ref{eqn:timecorr}
@@
 cost of computing $n$\textsuperscript{th} order correlations is
-$O(F^{2(n - 1)})$ for $n \in \mathcal{J}, n > 0$).  When $F$ or $n$ is large,
+$\mathcal{O}(F^{2(n - 1)})$ for $n \in \mathcal{J}, n > 0$).  When $F$ or $n$ is large,
 this approach quickly becomes intractable.
@@
 To make progress in computing $\mathbf{Y_{n+1}}$, we can approximate
-$\mathbf{Y}_n$ by computing an $O(F)$-dimensional embedding of
+$\mathbf{Y}_n$ by computing an $\mathcal{O}(F)$-dimensional embedding of
 $\mathbf{Y}_n$, termed $\hat{\mathbf{Y}}_n$, and then we can apply
 Equation~\ref{eqn:timecorr} to $\hat{\mathbf{Y}}_n$ rather than
-directly to $\mathbf{Y}_n$.  This enables us to maintain $O(n)$
+directly to $\mathbf{Y}_n$.  This enables us to maintain $\mathcal{O}(n)$
 scaling with respect to $n$, rather than exponential scaling via the
@@
 
+Applying dimensionality reduction algorithms to $\mathbf{Y}$ yields a
+$\hat{\mathbf{Y}}$ whose columns reflect weighted combinations (or
+nonlinear transformations) of the original columns of $\mathbf{Y}$.
+This has two main consequences.  First, with each repeated
+dimensionality reduction, the resulting $\hat{\mathbf{Y}}_n$ has lower
+and lower fidelity (with respect to what the ``true'' $\mathbf{Y}_n$
+might have looked like without using dimensionality reduction to
+maintain scalability).  In other words, computing $\hat{\mathbf{Y}}_n$
+is a lossy operation.  Second, whereas the columns of $\mathbf{Y}_n$
+may be mapped directly onto pairs of columns of $\mathbf{Y}_{n-1}$,
+that mapping either becomes less cleanly defined in
+$\hat{\mathbf{Y}}_n$ due to the reweightings and/or nonlinear
+transformations.
+
 \subsubsection*{Graph theory-based approaches to computing
@@
 
-\textbf{JRM TODO: Need references for each of the below, plus citation
-  of \href{https://github.com/aestrivex/bctpy/wiki}{bctpy toolbox} (source of measures listed below)}
-\begin{itemize}
-\item Betweenness centrality: Wei; Node Betweenness; edge betweenness
-  centrality; edge betweeness wei; 
-\item Shannon-entropy based diversity coefficient
-\item Eigenvector centrality, pagerank centrality
-\item flow coefficient (Honey et al. 2007, PNAS)
-\item k-coreness centrality (directed, undirected)
-\item within-module degree
-\item participation coefficient (signed, unsigned)
-\item subgraph centrality
-\end{itemize}
+Graph theoretic measures take as input a matrix of interactions (e.g.,
+using the above notation, an $F \times F$ correlation matrix or
+binarized correlation matrix reconstituded from a single timepoint's
+row of $\mathbf{Y}$) and return as output a set of $F$ measures
+describing how each node (feature) sits within that interactions
+matrix with respect to the rest of the population.  Common measures
+include betweeness centrality~\citep[the proportion of shortest paths
+between each pair of nodes in the population that involves the given
+node in question; e.g., ][]{Newm05, OpsaEtal10, Bart04, GeisEtal08,
+  Free77}; diversity and dissimilarity~\citep[characterizations of how
+differently connected a given node is from others in the population;
+e.g., ][]{Rao82, Lin09, RicoSzei06}; Eigenvector centrality and
+pagerank centrality~\citep[measures of how influential a given node is
+within the broader network; e.g., ][]{Newm08, Bona07, LohmEtal10,
+  HaluEtal13}; transfer entropy and flow coefficients~\citep[a measure
+of how much information is flowing from a given node to other nodes in
+the network; e.g., ][]{HoneEtal07, Schr00}; $k$-coreness
+centrality~\citep[a measure of the connectivity of a node within its
+local sub-graph; e.g., ][]{AlvaEtal05, ChriFowl10}; within-module
+degree~\citep[a measure of how many connections a node has to its
+close neighbors in the network; e.g., ][]{RubiSpor10}; participation
+coefficient~\citep[a measure of the diversity of a node's connections
+to different sub-graphs in the network; e.g., ][]{RubiSpor10}; and
+sub-graph centrality~\citep[a measure of a node's participation in all
+of the network's sub-graphs; e.g., ][]{EstrRodr05}.
 
-Idea: for each timepoint, compute relevant measure for node.  Result:
-a $T$ by $F$ matrix characterizing how the given measure for each node
-over time.  We can use this as $\hat{\mathbf{Y}}_n$ and then apply
-Equation~\ref{eqn:timecorr} to compute $\hat{\mathbf{Y}}_{n+1}.$
-
-\textbf{JRM STOPPED HERE}
+As an alternative to the above dimensionality reduction approach to
+embedding $\mathbf{Y}_n$ in a lower-dimensional space, but still
+allowing for scalable explorations of higher-order structure in the
+data, we also explore using the above graph theoretic measures as a
+means of obtaining $\hat{\mathbf{Y}}_n$.  In particular: for a given
+graph theoretic measure, $\eta: \mathcal{R}^{F \times F} \rightarrow
+\mathcal{R}^F$, we can use $\eta$ to tranform each row of
+$\mathbf{Y}_n$ in a way that characterizes the corresponding
+graph-theoretic properties of each column.  Whereas the dimensionality
+reduction approach to computing $\hat{\mathbf{Y}}_n$ is lossy,
+the graph-theory approach is lossless.  However, whereas the
+dimensionality reduction approach maintains ties (direct or indirect)
+to the original activity patterns reflected in $\mathbf{Y}_{n-1}$, the
+graph-theory approach does not.  Instead, the graph-theory
+characterizes the nature and timecourse of each feature's
+\textit{participation} in the network.
 

### 2018-10-16 paper/main.tex
added timecorr version of ISFC

@@
     observation's weights fall off in time according to a Ricker
-    wavelet centered on $t$.  Weights derived using several different
-    example width parameters ($\sigma$) are displayed.}
+    wavelet centered on $t$.  This function highlights the
+    \textit{contrasts} between local versus surrounding activity
+    patterns in estimating dynamic correlations. Weights derived using
+    several different example width parameters ($\sigma$) are
+    displayed.  }
   \label{fig:weights}
@@
 (i.e., $\mathbf{Y}$).
+
+\subsubsection*{Inter-subject dynamic correlations}
+Equation~\ref{eqn:timecorr} provides a means of taking a single
+observation matrix, $\mathbf{X}$ and estimating the dynamic
+correlations from moment to moment, $\mathbf{Y}$.  Suppose that one
+has access to a set of multiple observation matrices that reflect the
+same phenomenon.  For example, one might collect neuroimaging data
+from several experimental participants, as each participant performs
+the same task (or sequence of tasks).  Let $\{ mathbf{X}_1,
+mathbf{X}_2, ..., mathbf{X}_P\}$ reflect the $T$ by $F$ observation
+matrices for each of $P$ participants in an experiment.  We can use
+\textit{inter-subject functional connectivity}~\citep[ISFC;
+][]{SimoEtal16} to compute the degree of stimulus-driven correlations
+reflected in the multi-participant dataset at a given timepoint $t$
+using:
+\begin{align}
+\bar{\mathbf{C}}(t) = M\left(R\left(\frac{1}{2P} \sum_{i=1}^P
+  Z\left(Y_i(t)\right)^\mathrm{T} + Z\left(Y_i,(t)\right)\right)\right),
+\end{align}
+where $M$ extracts and vectorizes the diagonal and upper triangle of a symmetric
+matrix, $Z$ is the Fisher $z$-transformation~\citep{Zar10}:
+\begin{align}
+Z(r) = \frac{\log(1+r) - \log(1-r)}{2}
+\end{align}
+$R$ is the inverse of $Z$:
+\begin{align}
+R(z) = \frac{\exp(2z - 1)}{\exp(2z + 1)},
+\end{align}
+and $\mathbf{Y}_i(t)$ denotes the correlation matrix
+(Eqn.~\ref{eqn:corr}) between each column of $\mathbf{X}_i$ and each
+column of the average observations from all \textit{other}
+participants, $\bar{\mathbf{X}}_{ \backslash i}$:
+\begin{align}
+  \bar{\mathbf{X}}_{ \backslash i} = R\left(\frac{1}{P-1}\sum_{i \in \backslash i} Z(\mathbf{X}_i\right),
+\end{align}
+where $ \backslash i$ denotes the set of all participants other than
+participant $i$. In this way, the $T$ by $\left( \frac{F^2 - F}{2}
+  + F \right)$
+matrix $\bar{\mathbf{C}}$ is the time-varying extension of the ISFC
+approach developed by \cite{SimoEtal16}.
 
@@
 \subsection*{Timepoint decoding}
+
 Cite HTFA paper, summarize relevant methods.

### 2018-10-16 paper/main.tex
backing up changes; still working through methods [WIP]

@@
 \begin{align}
-  \bar{\mathbf{X}}_{ \backslash i} = R\left(\frac{1}{P-1}\sum_{i \in \backslash i} Z(\mathbf{X}_i\right),
+  \bar{\mathbf{X}}_{ \backslash i} = R\left(\frac{1}{P-1}\sum_{i \in
+  \backslash i} Z\left( \mathbf{X}_i \right) \right),
 \end{align}
@@
 
-\subsection*{Timepoint decoding}
+\subsection*{Evaluation metrics}
+We evaluate our approach to extracting dynamic correlations and
+higher-order correlations using several metrics detailed next.  First,
+we generated synthetic data using known time-varying correlations, and
+then we evaluated the fidelity with which Equation~\ref{eqn:timecorr}
+could recover those correlations (for synthetic datasets with
+different properties, and using different kernels to define the
+weights; Fig.~\ref{fig:weights}).  We then turned to a series of
+analyses on a (real) neuroimaging dataset where the ground truth
+correlations were \textit{not} known.  We evaluated whether the
+recovered correlations could be used to accurately label held-out
+neuroimaging data with the time at which it was collected, and also
+whether the history of correlations (and higher-order correlations)
+from time 0 to $t-1$ could be used to predict future activity patterns
+at time $t$.  We used these latter evaluations (using timepoint
+decoding and predictions of held-out future data) as a proxy for
+gauging how much explanatory power the recovered correlations held
+with respect to the observed data.
 
+\subsubsection*{Generating synthetic data}
+Ramping dataset and block dataset.  Create an example figure for both.
+
+\subsubsection*{Recovery of ground truth parameters from synthetic
+  data}
+Apply timecorr with a given kernel, then correlate each recovered
+correlation matrix with the ground truth.  Explore how recovery varies
+with the kernel, kernel parameters, and specific structure of the data
+(e.g. slow changes as in the ramping dataset, versus rapid changes as
+in the block dataset).
+
+\subsubsection*{Timepoint decoding}
 Cite HTFA paper, summarize relevant methods.
 
-\subsection*{Prediction}
+\subsubsection*{Predicting held-out future data}
 Use Eqn. 12 from SuperEEG paper, extend notation to treat
@@
 predict $\mathbf{X}(t)$.  Key question: what is the predictive power
-added by each new level.
+added by each new level?
 
@@
 \subsubsection*{Synthetic data}
+Figure: overall timecourse of recovery, also recovery near
+event boundaries.
+
 \subsubsection*{Neuroimaging dataset~\citep{SimoEtal16}}
+Figures: decoding by level, predictions by level
 
@@
 \section*{Discussion}
-% multiple timescale representations (a la Hasson group) implies
-% first-order network interactions.  higher-order interactions imply
-% generalizations between interacting representations (e.g. mirrored
-% schema, a la Norman/Baldassano/Hasson).  possibly cite NTB 2013
-% science review, using as evidence that this is where the field is
-% going (voxels --> patterns (L0) --> interactions (L1) --> higher
-% order patterns (L2+).
-
-% related approaches: sliding window, phase-based correlations,
-% within-ROI spatial correlations at each timepoint, granger
-% causality, other explit models (e.g. virtual brain).
-
-%other applications: molecular interactions (protein folding?),
-%diagnosis (e.g. psychiatric disorders as network flow problems--
-%gratton work?), social network dynamics (e.g. financial markets,
-%social media interactions)
+\begin{itemize}
+\item multiple timescale representations (a la Hasson group) implies
+first-order network interactions.  higher-order interactions imply
+generalizations between interacting representations (e.g. mirrored
+schema, a la Norman/Baldassano/Hasson).  possibly cite NTB 2013
+science review, using as evidence that this is where the field is
+going (voxels $\rightarrow$ patterns (L0) $\rightarrow$ interactions (L1) $\rightarrow$ higher
+order patterns (L2$+$).
+\item related approaches: sliding window, phase-based correlations,
+within-ROI spatial correlations at each timepoint, granger
+causality, other explit models (e.g. virtual brain).
+\item other applications: molecular interactions (protein folding?),
+diagnosis (e.g. psychiatric disorders as network flow problems--
+gratton work?), social network dynamics (e.g. financial markets,
+social media interactions)
+\end{itemize}
 
 \subsection*{Concluding remarks}
-% the universe is complicated and we need scalable approaches to
-% studying how the pieces are interacting to make sense of it.  one
-% small step for mankind, and so on.
+the universe is complicated and we need scalable approaches to
+studying how the pieces are interacting to make sense of it.  one
+small step for mankind, and so on.
 

### 2018-10-17 paper/main.tex
working on synthetic data generation

@@
 cost of computing $n$\textsuperscript{th} order correlations is
-$\mathcal{O}(F^{2(n - 1)})$ for $n \in \mathcal{J}, n > 0$).  When $F$ or $n$ is large,
+$\mathcal{O}(F^{2n})$ for $n \in \mathcal{J}, n > 0$).  When $F$ or $n$ is large,
 this approach quickly becomes intractable.

### 2019-01-23 code/scripts/pieman_cluster_submit_level_analysis.py
WIP paper writing and parameter changes to level analysis

@@ -23,9 +23,9 @@ job_script = os.path.join(os.path.dirname(os.path.realpath(__file__)), 'pieman_c
 cond_type = ['intact', 'paragraph', 'word', 'rest']
 
 # options for levels: integer
-levels = str('10')
+levels = str('5')
 # options for reps: integer
-reps =  str('5')
+reps =  str('3')
 
 # options for reps: cfuns
 cfuns =  [str('wisfc')]

### 2019-03-18 code/scripts/pieman_cluster_submit_level_analysis.py
added optimize timepoint decoding analysis to methods section

@@ -40,7 +40,7 @@ rfuns = [str('PCA')]
 widths = [str(5)]
 
 # options for weight functions: laplace, gaussian, mexican hat, delta
-weights = ['mexican_hat']
+weights = ['gaussian']
 
 # options for debug: True or False
 debug = str('False')

### 2019-03-18 paper/main.tex
working on synthetic recovery analyses

@@
 
-\subsubsection*{Predicting held-out future data}
-Use Eqn. 12 from SuperEEG paper, extend notation to treat
-$\hat{\mathbf{Y}}_{1...n}(1...(t-1))$ as ``observed'' and use this to
-predict $\mathbf{X}(t)$.  Key question: what is the predictive power
-added by each new level?
+To explore how higher-order structure varies with stimulus structure
+and complexity, we used a previous neuroimaging dataset
+~\cite{SimoEtal16}  in which participants listened to an audio recording of a story; 36 particpants listen to an intact version of the story, 18 participants listen to time-scrambled recordings of the same story where paragraphs were scrambled, 36 particpants listen to word-scrambled version and 36 participants lay in rest condition.
+
+Prior work has shown participants share similar neural responses to richly structured stimuli when compared to stimuli with less structure.
+To assess whether the moment-by-moment higher order correlations were reliably preserved across participants, we used inter-subject functional connectivity (ISFC) to isolate the time-varying correlational structure (functional connectivity patterns that were specifically driven by the story participants listened to.
+Following the analyses conducted by (HTFA)~\cite{MannEtal18},, We first applied HTFA to the fMRI datasets to obtain a time series of 700 node activities for every participant.
+We then computed the dynamic weighted ISFC using a gaussian kernel with a width of 5.
+We then approximated these dynamic correlation using PCA and computed the dynamic weighted ISFC on the approximations.
+We repeated this process up to 10th order approximated correlations.
+
+To assess decoding accuracy, we randomly divided participants for each stimulus into two groups.
+For the zeroth order, we computed the mean factor activity for each group.
+For all subsequent orders up to the tenth order, we computed the mean approximated dynamic ISFC of factor activity for each group.
+We then took weighted combinations of each order activity, for which we optimized by subdividing one the groups.
+For each group of participants in turn, we compared these activity patterns (using Pearson correlations) to estimate the story times each pattern corresponded to.
 

### 2019-03-19 paper/main.tex
added methods fig to paper

@@
 
+\begin{figure}
+  \centering
+  \includegraphics[width=\textwidth]{figs/methods_fig}
+  \caption{\textbf{Examples of time-varying weights.  Each panel
+      displays per-timepoint weights at $t = 50$, evaluated for 100
+      timepoints ($1, ..., 100$).  a. Uniform weights.} The weights
+    are timepoint-invariant; observations at all timepoints are
+    weighted equally, and do not change as a function of $t$.  This is
+    a special case of weight function that reduces dynamic
+    correlations to static correlations. }
+  \label{fig:methods_fig}
+\end{figure}
+
 There are many possible methods for computing $\hat{\mathbf{Y}}_n$
@@
 To assess whether the moment-by-moment higher order correlations were reliably preserved across participants, we used inter-subject functional connectivity (ISFC) to isolate the time-varying correlational structure (functional connectivity patterns that were specifically driven by the story participants listened to.
-Following the analyses conducted by (HTFA)~\cite{MannEtal18},, We first applied HTFA to the fMRI datasets to obtain a time series of 700 node activities for every participant.
+Following the analyses conducted by (HTFA)~\cite{MannEtal18}, We first applied HTFA to the fMRI datasets to obtain a time series of 700 node activities for every participant.
 We then computed the dynamic weighted ISFC using a gaussian kernel with a width of 5.

### 2019-03-19 code/scripts/pieman_cluster_level_chunked.py
remove duplicate from paragraph data

@@ -47,6 +47,7 @@ pieman_conds = ['intact', 'paragraph', 'word', 'rest']
 
 weights_paramter = eval(wp)
 
+###### REMOVE the duplicate!!
 
 if debug:
     data_thirds = [0] * 3

### 2019-03-20 code/scripts/pieman_pca_analysis_submit.py
added back the PCA analyses now using the non-dupicaled data

@@ -18,13 +18,10 @@ except:
     os.makedirs(config['resultsdir'])
 
 # each job command should be formatted as a string
-job_script = os.path.join(os.path.dirname(os.path.realpath(__file__)), 'pieman_cluster_level_analysis.py')
+job_script = os.path.join(os.path.dirname(os.path.realpath(__file__)), 'pieman_pca_analysis.py')
 
-#cond_type = ['intact', 'paragraph', 'word', 'rest']
-cond_type = ['paragraph']
+cond_type = ['intact', 'paragraph', 'word', 'rest']
 
-# options for levels: integer
-levels = str('10')
 
 # options for reps: integer
 reps =  str('10')
@@ -34,8 +31,7 @@ cfuns =  [str('isfc')]
 
 # options for reps: rfuns
 #rfuns =  [str('eigenvector_centrality'), str('pagerank_centrality'), str('strength')]
-#rfuns =  [str('eigenvector_centrality')]
-rfuns = [str('PCA')]
+rfuns =  [str('PCA')]
 
 # options for widths: integer
 widths = [str(10)]
@@ -43,17 +39,20 @@ widths = [str(10)]
 # options for weight functions: laplace, gaussian, mexican hat, delta
 weights = ['gaussian']
 
+# options for dims: integers
+dims = ['100']
+
 # options for debug: True or False
 debug = str('False')
 
-job_commands = list(np.array([list(map(lambda x: x[0]+" "+str(x[1])+" "+levels+" "+str(r)+
-                                                 " "+cfuns[0]+" "+rfuns[0]+" "+widths[0]+" "+weights[0]+" "+debug,
+job_commands = list(np.array([list(map(lambda x: x[0]+" "+str(x[1])+" "+'unchunked'+" "+str(r)+
+                                                 " "+cfuns[0]+" "+rfuns[0]+" "+widths[0]+" "+weights[0]+" "+ dims[0]+ " "+debug,
                                        zip([job_script]*len(cond_type), cond_type)))
                               for r in range(int(reps))]).flat)
 
 # job_names should specify the file name of each script (as a list, of the same length as job_commands)
-job_names = list(np.array([list(map(lambda x: os.path.basename(os.path.splitext(x)[0])+'_'+levels+'_'+str(r)+'_'
-                                              +cfuns[0]+'_'+rfuns[0]+'_'+widths[0]+'_'+weights[0]+'_'+debug+'.sh', cond_type))
[…]

### 2019-03-20 code/scripts/pieman_pca_chunk_submit.py
added back the PCA analyses now using the non-dupicaled data

@@ -18,13 +18,11 @@ except:
     os.makedirs(config['resultsdir'])
 
 # each job command should be formatted as a string
-job_script = os.path.join(os.path.dirname(os.path.realpath(__file__)), 'pieman_cluster_level_analysis.py')
+job_script = os.path.join(os.path.dirname(os.path.realpath(__file__)), 'pieman_pca_chunk.py')
 
-#cond_type = ['intact', 'paragraph', 'word', 'rest']
-cond_type = ['paragraph']
+cond_type = ['intact', 'paragraph', 'word', 'rest']
 
 # options for levels: integer
-levels = str('10')
 
 # options for reps: integer
 reps =  str('10')
@@ -34,8 +32,7 @@ cfuns =  [str('isfc')]
 
 # options for reps: rfuns
 #rfuns =  [str('eigenvector_centrality'), str('pagerank_centrality'), str('strength')]
-#rfuns =  [str('eigenvector_centrality')]
-rfuns = [str('PCA')]
+rfuns =  [str('PCA')]
 
 # options for widths: integer
 widths = [str(10)]
@@ -43,17 +40,20 @@ widths = [str(10)]
 # options for weight functions: laplace, gaussian, mexican hat, delta
 weights = ['gaussian']
 
+# options for dims: integers
+dims = ['100']
+
 # options for debug: True or False
 debug = str('False')
 
-job_commands = list(np.array([list(map(lambda x: x[0]+" "+str(x[1])+" "+levels+" "+str(r)+
-                                                 " "+cfuns[0]+" "+rfuns[0]+" "+widths[0]+" "+weights[0]+" "+debug,
+job_commands = list(np.array([list(map(lambda x: x[0]+" "+str(x[1])+" "+'chunk'+" "+str(r)+
+                                                 " "+cfuns[0]+" "+rfuns[0]+" "+widths[0]+" "+weights[0]+" "+ dims[0]+ " "+debug,
                                        zip([job_script]*len(cond_type), cond_type)))
                               for r in range(int(reps))]).flat)
 
 # job_names should specify the file name of each script (as a list, of the same length as job_commands)
-job_names = list(np.array([list(map(lambda x: os.path.basename(os.path.splitext(x)[0])+'_'+levels+'_'+str(r)+'_'
-                                              +cfuns[0]+'_'+rfuns[0]+'_'+widths[0]+'_'+weights[0]+'_'+debug+'.sh', cond_type))
[…]

### 2019-03-20 code/scripts/pieman_cluster_level_analysis.py
change code to pull data from number of factors

@@ -51,7 +51,12 @@ gaussian = {'name': 'Gaussian', 'weights': tc.gaussian_weights, 'params': {'var'
 mexican_hat = {'name': 'Mexican hat', 'weights': tc.mexican_hat_weights, 'params': {'sigma': width}}
 
 factors = 700
-pieman_data = loadmat(os.path.join(config['datadir'], 'pieman_data.mat'))
+
+if factors == 100:
+    pieman_name = '../../data/pieman_ica100.mat'
+else:
+    pieman_name = '../../data/pieman_data.mat'
+
 pieman_conds = ['intact', 'paragraph', 'word', 'rest']
 
 

### 2019-03-20 code/scripts/pieman_cluster_level_chunked.py

@@ -41,7 +41,13 @@ delta = {'name': '$\delta$', 'weights': tc.eye_weights, 'params': tc.eye_params}
 gaussian = {'name': 'Gaussian', 'weights': tc.gaussian_weights, 'params': {'var': width}}
 mexican_hat = {'name': 'Mexican hat', 'weights': tc.mexican_hat_weights, 'params': {'sigma': width}}
 
-pieman_data = loadmat(os.path.join(config['datadir'], 'pieman_data.mat'))
+factors = 700
+
+if factors == 100:
+    pieman_name = '../../data/pieman_ica100.mat'
+else:
+    pieman_name = '../../data/pieman_data.mat'
+
 pieman_conds = ['intact', 'paragraph', 'word', 'rest']
 
 
@@ -76,7 +82,15 @@ else:
         data = []
         conds = []
         for c in pieman_conds:
-            next_data = list(map(lambda i: pieman_data[c][:, i][0][divided:divided+100,:], np.arange(pieman_data[c].shape[1])))
+            if c == 'paragraph':
+                if factors == 700:
+                    next_data = list(
+                        map(lambda i: pieman_data[c][:, i][0][divided:divided+100,:], np.where(np.arange(pieman_data[c].shape[1]) != 3)[0]))
+                else:
+                    next_data = list(
+                        map(lambda i: pieman_data[c][:, i][0][divided:divided+100,:], np.where(np.arange(pieman_data[c].shape[1]) != 0)[0]))
+            else:
+                next_data = list(map(lambda i: pieman_data[c][:, i][0], np.arange(pieman_data[c].shape[1])))
             data.extend(next_data)
             conds.extend([c]*len(next_data))
 

### 2019-03-20 code/scripts/pieman_cluster_param_search.py

@@ -43,7 +43,12 @@ gaussian = {'name': 'Gaussian', 'weights': tc.gaussian_weights, 'params': {'var'
 mexican_hat = {'name': 'Mexican hat', 'weights': tc.mexican_hat_weights, 'params': {'sigma': width}}
 
 factors = 700
-pieman_data = loadmat(os.path.join(config['datadir'], 'pieman_data.mat'))
+
+if factors == 100:
+    pieman_name = '../../data/pieman_ica100.mat'
+else:
+    pieman_name = '../../data/pieman_data.mat'
+
 pieman_conds = ['intact', 'paragraph', 'word', 'rest']
 
 

### 2019-03-20 code/scripts/pieman_pca_analysis.py

@@ -44,7 +44,12 @@ gaussian = {'name': 'Gaussian', 'weights': tc.gaussian_weights, 'params': {'var'
 mexican_hat = {'name': 'Mexican hat', 'weights': tc.mexican_hat_weights, 'params': {'sigma': width}}
 
 factors = 100
-pieman_data = loadmat(os.path.join(config['datadir'], 'pieman_ica100.mat'))
+
+if factors == 100:
+    pieman_name = '../../data/pieman_ica100.mat'
+else:
+    pieman_name = '../../data/pieman_data.mat'
+
 pieman_conds = ['intact', 'paragraph', 'word', 'rest']
 
 

### 2019-03-20 code/scripts/pieman_pca_chunk.py

@@ -44,7 +44,12 @@ gaussian = {'name': 'Gaussian', 'weights': tc.gaussian_weights, 'params': {'var'
 mexican_hat = {'name': 'Mexican hat', 'weights': tc.mexican_hat_weights, 'params': {'sigma': width}}
 
 factors=100
-pieman_data = loadmat(os.path.join(config['datadir'], 'pieman_ica100.mat'))
+
+if factors == 100:
+    pieman_name = '../../data/pieman_ica100.mat'
+else:
+    pieman_name = '../../data/pieman_data.mat'
+
 pieman_conds = ['intact', 'paragraph', 'word', 'rest']
 
 

### 2019-03-20 code/scripts/pieman_pca_analysis.py
WIP paper and rerun of analyses and figs

@@ -43,7 +43,7 @@ delta = {'name': '$\delta$', 'weights': tc.eye_weights, 'params': tc.eye_params}
 gaussian = {'name': 'Gaussian', 'weights': tc.gaussian_weights, 'params': {'var': width}}
 mexican_hat = {'name': 'Mexican hat', 'weights': tc.mexican_hat_weights, 'params': {'sigma': width}}
 
-factors = 100
+factors = 700
 
 if factors == 100:
     pieman_name = 'pieman_ica100.mat'

### 2019-03-20 paper/main.tex
remove duplicate from paragraph data
added back the PCA analyses now using the non-dupicaled data
WIP paper and rerun of analyses and figs

@@
 \usepackage{apacite}
+\usepackage{hyperref}
 \usepackage{natbib}
@@
   \includegraphics[width=\textwidth]{figs/methods_fig}
-  \caption{\textbf{Examples of time-varying weights.  Each panel
-      displays per-timepoint weights at $t = 50$, evaluated for 100
-      timepoints ($1, ..., 100$).  a. Uniform weights.} The weights
-    are timepoint-invariant; observations at all timepoints are
-    weighted equally, and do not change as a function of $t$.  This is
-    a special case of weight function that reduces dynamic
-    correlations to static correlations. }
+  \caption{\textbf{Computing higher order correlations. } Correlations
+  are computed then approximated to the same size as original data.
+  This process is repeated to computer }
   \label{fig:methods_fig}
@@
 \subsubsection*{Timepoint decoding}
-Cite HTFA paper, summarize relevant methods.
 
@@
 and complexity, we used a previous neuroimaging dataset
-~\cite{SimoEtal16}  in which participants listened to an audio recording of a story; 36 particpants listen to an intact version of the story, 18 participants listen to time-scrambled recordings of the same story where paragraphs were scrambled, 36 particpants listen to word-scrambled version and 36 participants lay in rest condition.
+~\cite{SimoEtal16}  in which participants listened to an audio recording of a story; 36 particpants listen to an intact version of the story, 17 participants listen to time-scrambled recordings of the same story where paragraphs were scrambled, 36 particpants listen to word-scrambled version and 36 participants lay in rest condition.
 
-Prior work has shown participants share similar neural responses to richly structured stimuli when compared to stimuli with less structure.
-To assess whether the moment-by-moment higher order correlations were reliably preserved across participants, we used inter-subject functional connectivity (ISFC) to isolate the time-varying correlational structure (functional connectivity patterns that were specifically driven by the story participants listened to.
-Following the analyses conducted by (HTFA)~\cite{MannEtal18}, We first applied HTFA to the fMRI datasets to obtain a time series of 700 node activities for every participant.
+Prior work has shown participants share similar neural responses to
+richly structured stimuli when compared to stimuli with less
+structure.  To assess whether the moment-by-moment higher order
+correlations were reliably preserved across participants, we used
+inter-subject functional connectivity (ISFC) to isolate the
+time-varying correlational structure (functional connectivity patterns
+that were specifically driven by the story participants listened to.
+Following the analyses conducted by (HTFA)~\cite{MannEtal18}, we first
+applied \textit{hierarchical topographic factor analysis} (HTFA) to the fMRI datasets to obtain a time series of 700 node activities for every participant.
 We then computed the dynamic weighted ISFC using a gaussian kernel with a width of 5.
@@
 
-To assess decoding accuracy, we randomly divided participants for each stimulus into two groups.
+To assess decoding accuracy, we randomly divided participants for each stimulus into training and testing groups.
 For the zeroth order, we computed the mean factor activity for each group.
 For all subsequent orders up to the tenth order, we computed the mean approximated dynamic ISFC of factor activity for each group.
-We then took weighted combinations of each order activity, for which we optimized by subdividing one the groups.
 For each group of participants in turn, we compared these activity patterns (using Pearson correlations) to estimate the story times each pattern corresponded to.
+
+Specifically, we asked, for each timepoint: what are the correlations
+between the first group's and second group's activity patterns at each
+order.  We then took weighted mixture of the correlation matrices at
+each order using mixing parameter, $\phi$, where $0 <\phi< 1$ reflects a
+weighted mixture of order based decoding.
+We optimized  $\phi$, by subdividing the training group.
+We note that the decoding test we used is a conservative in which we count a timepoint label as incorrect if it is not an exact match.
 
@@
 \subsubsection*{Neuroimaging dataset~\citep{SimoEtal16}}
-Figures: decoding by level, predictions by level
+Figures: decoding by level
+For our decoding analysis, we used HTFA-derived node activities
+~\cite{MannEtal18} from fMRI data collected as participants listened
+to an audio recording of a story (intact condition; 36 participants),
+listened to time scrambled recordings of the same story (17
+participants in the paragraph-scrambled condition listened to the
+paragraphs in a randomized order and 36 in the word-scrambled
+condition listened to the words in a randomized order), or lay resting
+with their eyes open in the scanner (rest condition; 36
+participants). We sought to demonstrate how higher-order correlations
+may be used to examine dynamic interactions of brain patterns in
+(real) multi-subject fMRI datasets. This story listening dataset was
+collected as part of a separate study, where the full imaging
+parameters, image preprocessing methods, and experimental details may
+be found~\citep{SimoEtal16}. The dataset is available at
+\href{url}{http://arks. princeton.edu/ark:/88435/dsp015d86p269k}.
+
+We next evaluated if our model of high-order correlations in brain activity can capture cognitively relevant brain patterns.
+We performed a decoding analysis, using cross validation to estimate (using other participants’ data) which parts of the story each weighted-mixture of higher-order brain activity pattern corresponded to (see \textit{Materials and methods}).
+We note that our primary goal was not to achieve perfect decoding accuracy, but rather to use decoding accuracy as a benchmark for assessing whether different neural features specifically capture cognitively relevant brain patterns.
+
+Separately for each experimental condition, we divided participants
+into two groups. For the zeroth order, we computed the mean factor
+activity for each group.  For all subsequent orders up to the tenth
+order, we computed the mean approximated dynamic ISFC of factor
+activity for each group (see \textit{Materials and methods}).  For
+each order, we correlated the group 1 activity patterns with group 2
+activity patterns.  We then subdivided the group 1 to obtain an
+optimal weighting parameter for each order’s correlation matrix using
+the same cross validation method. We used the optimal weighting
+parameters to obtain a weighted-mixture of each order’s correlation
+matrix. Using these correlations, we labeled the group 1 timepoints
+using the group 2 timepoints with which they were most highly
+correlated; we then computed the proportion of correctly labeled group
+1 timepoints. (We also performed the symmetric analysis whereby we
+labeled the group 2 timepoints using the group 1 timepoints as a
+template.) We repeated this procedure 10 times (randomly re-assigning
+participants to the two groups each time) to obtain a distribution of
+decoding accuracies for each experimental condition. (There were 272
+timepoints for paragraph condition, 300 timepoints for intact and word
+conditions, and 400 timepoints for rest condition,  so chance
+performance on this decoding test is was $\frac{1}{272}$,
+$\frac{1}{300}$, and $\frac{1}{400}$ respectively.
 

### 2019-03-22 paper/main.tex
WIP paper and corrmats notebook

@@
 \section*{Methods}
-There are two basic steps to our approach.  In the first step, we take
+There are two basic steps to our approach (Fig.~\ref{fig:methods_fig}).  In the first step, we take
 a number-of-timepoints ($T$) by number-of-features ($F$)
@@
 \subsubsection*{Generating synthetic data}
-Ramping dataset and block dataset.  Create an example figure for both.
+Ramping dataset and block dataset. Add details (Fig.~\ref{fig:synthetic_data})
+\begin{figure}
+  \centering
+  \includegraphics[width=\textwidth]{figs/synthetic_data.pdf}
+  \caption{\textbf{Dynamic correlation recovery with synthetic data.
+      a.Recovery using a constant dataset.} Using constant dataset,
+    how well can we recover using different
+    kernels. \textbf{b. Recovery using random dataset.}
+    \textbf{c. Ramping recovery.}  \textbf{d. Block recovery} blah}
+  \label{fig:synthetic_data}
+\end{figure}
 

### 2019-03-22 code/scripts/pieman_pca_analysis.py

@@ -86,6 +86,16 @@ data = np.array(data)
 conds = np.array(conds)
 
 append_iter = pd.DataFrame()
+#
+# from timecorr.helpers import isfc, autofc, mean_combine, corrmean_combine, vec2mat
+# weights_fun=weights_paramter['weights']
+# weights_params=weights_paramter['params']
+# combine = corrmean_combine
+#
+#
+# all_data = np.array(data)
+# try_data = np.asarray(tc.timecorr([x for x in all_data[conds == 'intact']], cfun=autofc, rfun=rfun,
+#                                                  weights_function=weights_fun, weights_params=weights_params))
 
 iter_results = tc.helpers.pca_decoder(data[conds == cond], nfolds=2, dims=int(ndims),
                                     combine=mean_combine,

### 2019-03-26 paper/main.tex
Level 1 inter-subject correlation heatmap calculations, redo plots, and WIP paper.

@@
 recovered correlations could be used to accurately label held-out
-neuroimaging data with the time at which it was collected, and also
-whether the history of correlations (and higher-order correlations)
-from time 0 to $t-1$ could be used to predict future activity patterns
-at time $t$.  We used these latter evaluations (using timepoint
-decoding and predictions of held-out future data) as a proxy for
+neuroimaging data with the time at which it was collected.  We used this latter evaluations (using timepoint
+decoding) as a proxy for
 gauging how much explanatory power the recovered correlations held
@@
   data}
-Apply timecorr with a given kernel, then correlate each recovered
+We applied timecorr with a given kernel Fig.~\ref{fig:weights}) to
+synthetic data, then correlate each recovered
 correlation matrix with the ground truth.  Explore how recovery varies
@@
 
-To assess decoding accuracy, we randomly divided participants for each stimulus into training and testing groups.
-For the zeroth order, we computed the mean factor activity for each group.
-For all subsequent orders up to the tenth order, we computed the mean approximated dynamic ISFC of factor activity for each group.
+To assess decoding accuracy, we randomly divided participants for each
+stimulus into training and testing groups. For the zeroth order, we
+computed the mean factor activity for each group.  For all subsequent
+orders up to the tenth order, we computed the mean approximated
+dynamic ISFC of factor activity for each group. To assess how
+additional higher-order correlations contribute to decoding accuracy,
+for each order we included a weighted-mixutre (described below) of the activity patterns of all
+previous orders.
 For each group of participants in turn, we compared these activity patterns (using Pearson correlations) to estimate the story times each pattern corresponded to.
-
 Specifically, we asked, for each timepoint: what are the correlations
 between the first group's and second group's activity patterns at each
-order.  We then took weighted mixture of the correlation matrices at
-each order using mixing parameter, $\phi$, where $0 <\phi< 1$ reflects a
-weighted mixture of order based decoding.
-We optimized  $\phi$, by subdividing the training group.
-We note that the decoding test we used is a conservative in which we count a timepoint label as incorrect if it is not an exact match.
+order. We note that the decoding test we used is a conservative in which we count a timepoint label as incorrect if it is not an exact match.
+
+For each order we obtained the weighted-mixture of the correlation
+matrices for the current order and all previous orders using mixing parameter , $\phi$, where $0 <\phi< 1$ reflects a
+weighted mixture of order based decoding Fig.~\ref{fig:decode_level}
+Panel C. ). We calculated  $\phi$, by
+subdividing the training group and using the quasi-Newton method of
+Broyden, Fletcher, Goldfarb, and Shanno (BFGS) for optimization. We
+repeated this cross-validation process 100 times.
 
@@
 \subsubsection*{Neuroimaging dataset~\citep{SimoEtal16}}
-Figures: decoding by level
 For our decoding analysis, we used HTFA-derived node activities
@@
 
+\begin{figure}
+  \centering
+  \includegraphics[width=\textwidth]{figs/decode_level.pdf}
+  \caption{\textbf{Decoding by order.
+      a. Relative decoding accuracy by order.} Relative to chance,
+    decoding accuracy for each condition (intact, paragraph, word,
+    and rest) as a function of increasingly more orders.  The red dots indicates
+    maximum decoding accuracy for each condition. \textbf{b. Normalized decoding accuracy
+      by order.}  We normalized the decoding accuracy by order to better
+    visualize the order with the maximum decoding accuracy for each
+    condition. \textbf{c. Optimized weights.}
+  For the order with maximum decoding accuracy by condition, we show
+  barplots of the optimized weights $\phi$  for each contributing
+  order.}
+  \label{fig:decoding_level}
+\end{figure}
+
 We next evaluated if our model of high-order correlations in brain activity can capture cognitively relevant brain patterns.
@@
 order, we computed the mean approximated dynamic ISFC of factor
-activity for each group (see \textit{Materials and methods}).  For
+activity for each group (see \textit{Materials and methods}), and
+combined in a weighted mixutre with all previous orders
+(i.e. cross-validation for the second
+order contained a weighted-mixture of zeroth, first, and second order \textbf{c. Optimized weights.}.)  For
 each order, we correlated the group 1 activity patterns with group 2
@@
 the same cross validation method. We used the optimal weighting
-parameters to obtain a weighted-mixture of each order’s correlation
+parameters to obtain a weighted-mixture (see \textit{Materials and methods}) of each order’s correlation
 matrix. Using these correlations, we labeled the group 1 timepoints
@@
 labeled the group 2 timepoints using the group 1 timepoints as a
-template.) We repeated this procedure 10 times (randomly re-assigning
+template.) We repeated this procedure 100 times (randomly re-assigning
 participants to the two groups each time) to obtain a distribution of
@@
 $\frac{1}{300}$, and $\frac{1}{400}$ respectively.
+
+\begin{figure}
+  \centering
+  \includegraphics[width=\textwidth]{figs/corrmats.pdf}
+  \caption{\textbf{Inter-subject correlations by order.
+      a. Inter-subject correlation heatmaps by order.}  Heatmap
+    denoting how correlated each subject is with every other subject
+    for each order, and grouped by condition (intact (I), paragraph
+    (P), word (W),
+    and rest (R)). \textbf{b. Distribution of correlations for each
+      condition by order}
+   Inter-subject correlations by conditon for each order.}
+  \label{fig:corrmats}
+\end{figure}
 

### 2019-03-26 code/scripts/pieman_pca_analysis.py
Level 1 inter-subject correlation heatmap calculations, redo plots, and WIP paper.

@@ -43,7 +43,7 @@ delta = {'name': '$\delta$', 'weights': tc.eye_weights, 'params': tc.eye_params}
 gaussian = {'name': 'Gaussian', 'weights': tc.gaussian_weights, 'params': {'var': width}}
 mexican_hat = {'name': 'Mexican hat', 'weights': tc.mexican_hat_weights, 'params': {'sigma': width}}
 
-factors = 700
+factors = 100
 
 if factors == 100:
     pieman_name = 'pieman_ica100.mat'
@@ -86,13 +86,13 @@ data = np.array(data)
 conds = np.array(conds)
 
 append_iter = pd.DataFrame()
-#
+# #
 # from timecorr.helpers import isfc, autofc, mean_combine, corrmean_combine, vec2mat
 # weights_fun=weights_paramter['weights']
 # weights_params=weights_paramter['params']
 # combine = corrmean_combine
-#
-#
+# #
+# #
 # all_data = np.array(data)
 # try_data = np.asarray(tc.timecorr([x for x in all_data[conds == 'intact']], cfun=autofc, rfun=rfun,
 #                                                  weights_function=weights_fun, weights_params=weights_params))

### 2019-03-27 paper/main.tex

@@
   data}
+
+To explore recovery of a constant correlation, we created a random
+correlation matrix and and added a small amount of Gaussian noise to
+
 We applied timecorr with a given kernel Fig.~\ref{fig:weights}) to
@@
 \href{url}{http://arks. princeton.edu/ark:/88435/dsp015d86p269k}.
-
+Bars of each color display cross-validated decoding performance for decoders trained using different sets of neural features: whole-brain patterns of voxel activities
 \begin{figure}
@@
   \caption{\textbf{Decoding by order.
-      a. Relative decoding accuracy by order.} Relative to chance,
-    decoding accuracy for each condition (intact, paragraph, word,
-    and rest) as a function of increasingly more orders.  The red dots indicates
+      a. Relative decoding accuracy by order.} Ribbons of each
+    color display cross-validated decoding performance for each condition (intact, paragraph, word,
+    and rest. Decoders were trained using increasingly more
+    higher-order information and this ribbons are displayed relative
+    to chance at 0. The red dots indicates
     maximum decoding accuracy for each condition. \textbf{b. Normalized decoding accuracy
@@
     visualize the order with the maximum decoding accuracy for each
-    condition. \textbf{c. Optimized weights.}
+    condition. \textbf{c. Optimized weights.} Bar heights indicate the
+    optimized mixing paramete $\phi$ of each contributing order up to
+    and including the order with the maximum
+    decoding accuracy for each contributing order
   For the order with maximum decoding accuracy by condition, we show
@@
   \caption{\textbf{Inter-subject correlations by order.
-      a. Inter-subject correlation heatmaps by order.}  Heatmap
-    denoting how correlated each subject is with every other subject
-    for each order, and grouped by condition (intact (I), paragraph
+      a. Inter-subject correlation heatmaps by order.}  Heatmaps for
+    each order of how correlated each subject is with every other
+    subject grouped by condition (intact (I), paragraph
     (P), word (W),
-    and rest (R)). \textbf{b. Distribution of correlations for each
-      condition by order}
-   Inter-subject correlations by conditon for each order.}
+    and rest (R)). \textbf{b. Mean correlation for each
+      condition by order.}
+   Bar heights indicate inter-subject correlations by conditon for each order.}
   \label{fig:corrmats}
@@
 \begin{itemize}
+
+\item Decoding accuracy best for level 2 data for all but rest
+  condition.  Could be that the brain is 2nd order or that fMRI can
+  only reliable give 2nd order.  
 \item multiple timescale representations (a la Hasson group) implies
@@
 order patterns (L2$+$).
+
+\begin{figure}
+  \centering
+  \includegraphics[width=\textwidth]{figs/direction_of_field.pdf}
+  \caption{\textbf{Direction of the field.} }
+  \label{fig:direction_of_field}
+\end{figure}
+
 \item related approaches: sliding window, phase-based correlations,

### 2019-03-27 paper/main.tex
corrected some minor formatting things

@@
   \centering
-  \includegraphics[width=\textwidth]{figs/methods_fig}
+  \includegraphics[width=0.5\textwidth]{figs/methods_fig}
   \caption{\textbf{Computing higher order correlations. } Correlations
@@
 matrices for the current order and all previous orders using mixing parameter , $\phi$, where $0 <\phi< 1$ reflects a
-weighted mixture of order based decoding Fig.~\ref{fig:decode_level}
+weighted mixture of order based decoding Fig.~\ref{fig:decoding_level}
 Panel C. ). We calculated  $\phi$, by

### 2019-04-05 code/scripts/corrmats_calc.py
update some plots

@@ -1,86 +1,0 @@
-
-import os
-import numpy as np
-from scipy.io import loadmat
-import timecorr as tc
-import scipy.spatial.distance as sd
-from timecorr.helpers import isfc, autofc, mean_combine, corrmean_combine, vec2mat, reduce
-
-figdir = '../figs'
-if not os.path.exists(figdir):
-    os.mkdir(figdir)
-
-def squareform_timepoints_corr(data, order=0):
-    if not order == 0:
-        for o in range(order):
-            data = np.asarray(tc.timecorr([x for x in data], cfun=autofc, rfun=rfun,
-                                          weights_function=weights_fun, weights_params=weights_params))
-    sq_corr = np.array([])
-    for i in data:
-        corr = np.corrcoef(i)
-        if sq_corr.size == 0:
-            sq_corr = sd.squareform(corr, checks=False)
-        else:
-            sq_corr = np.vstack((sq_corr, sd.squareform(corr, checks=False)))
-    return sq_corr
-
-factors = 700
-
-if factors == 100:
-    pieman_name = '../../data/pieman_ica100.mat'
-else:
-    pieman_name = '../../data/pieman_data.mat'
-
-
-pieman_data = loadmat(pieman_name)
-
-pieman_conds = ['intact', 'paragraph', 'word', 'rest']
-
-debug = False
-
-
-data = []
-conds = []
-for c in pieman_conds:
-    if c == 'paragraph':
-        if factors == 700:
-            next_data = list(map(lambda i: pieman_data[c][:, i][0][:272,:], np.where(np.arange(pieman_data[c].shape[1]) != 3)[0]))
-        else:
-            next_data = list(map(lambda i: pieman_data[c][:, i][0][:272,:], np.where(np.arange(pieman_data[c].shape[1]) != 0)[0]))
-    else:
-        next_data = list(map(lambda i: pieman_data[c][:, i][0][:272,:], np.arange(pieman_data[c].shape[1])))
-    data.extend(next_data)
-    conds.extend([c]*len(next_data))
-
-
-
-all_data = np.array(data)
-conds = np.array(conds)
-
-
-cfun = isfc
-rfun = 'PCA'
-width = 10
-wp = 'gaussian'
-cond = 'intact'
-level = 1
-
-gaussian = {'name': 'Gaussian', 'weights': tc.gaussian_weights, 'params': {'var': width}}
-
-weights_paramter = eval(wp)
-
-
[…]

### 2019-04-05 code/scripts/pieman_cluster_submit_level_analysis.py
change to laplace

@@ -41,7 +41,7 @@ rfuns = [str('PCA')]
 widths = [str(10)]
 
 # options for weight functions: laplace, gaussian, mexican hat, delta
-weights = ['gaussian']
+weights = ['laplace']
 
 # options for debug: True or False
 debug = str('False')

### 2019-04-05 paper/main.tex

--- 2019-03-27 paper/main.tex
@@
   underlying multi-dimensional timeseries data} \author{Lucy
-  L. W. Owen$^1$, Thomas Hao Chang$^{1,2}$, and\
+  L. W. Owen$^1$, Thomas H. Chang$^{1,2}$, and\
   Jeremy R. Manning\textsuperscript{$1, \dagger$}\\
@@
 \begin{abstract}
-  Most complex systems reflect dynamic interations between myriad
+  Most complex systems reflect dynamic interactions between myriad
   evolving components (e.g., interacting molecules, interacting brain
@@
 
-To explore recovery of a constant correlation, we created a random
-correlation matrix and and added a small amount of Gaussian noise to
+To explore recovery of a constant correlation, we generated syntheic
+data sampled from a constant covariance matrix. To do this, we created a random
+correlation matrix $K$ of size $s$, and and added a small amount of Gaussian noise
+to create a timeseries of for $s$ subjects.     \sim\mthcal{N}(\mu,\,\sigma^{2})
 

### 2019-04-06 paper/boneyard.tex
updated abstract

--- 2018-10-15 boneyard.tex
@@
+  Most complex systems reflect dynamic interactions between myriad
+  evolving components (e.g., interacting molecules, interacting brain
+  systems, interacting individuals within a social network or
+  ecological system, coordinated components within a mechanical or
+  digital device, etc.).  Despite that these interactions are central
+  to the full system's behavior (e.g., removing a component from the
+  full system can change the entire system's behavior), dynamic
+  interactions cannot typically be directly measured.  Rather, the
+  interactions must be inferred through their hypothesized role in
+  guiding the dynamics of system components.  Here we use a
+  model-based approach to inferring dynamic interactions from
+  timeseries data.  In addition to examining first-order interactions
+  (e.g., between pairs of components) we also examine higher-order
+  interactions (e.g., that characterize mirrored structure in the
+  patterns of interaction dynamics displayed by different subsets of
+  components).  We apply our approach to two datasets.  First, we use
+  a synthetic dataset, for which the underlying dynamic interactions
+  are known, to show that our model recovers those ground-truth
+  dynamic interactions.  We also apply our model to a neuroimaging
+  dataset and show that the high-order dynamic interactions exhibited
+  by brain data vary meaningfully as a function of the cognitive
+  ``richness'' of the stimulus people are experiencing.
+
 %should we introduce the name levelup in the introduction? ie. "in the second step, levelup, we use..." -ecw

### 2019-04-06 paper/main.tex
updated abstract

@@
 
-\title{An examination of the high-order dynamic interactions
-  underlying multi-dimensional timeseries data} \author{Lucy
+\title{High-order dynamic neural correlations reflect naturalistic processing
+in humans} \author{Lucy
   L. W. Owen$^1$, Thomas H. Chang$^{1,2}$, and\
@@
 \begin{abstract}
-  Most complex systems reflect dynamic interactions between myriad
-  evolving components (e.g., interacting molecules, interacting brain
-  systems, interacting individuals within a social network or
-  ecological system, coordinated components within a mechanical or
-  digital device, etc.).  Despite that these interactions are central
-  to the full system's behavior (e.g., removing a component from the
-  full system can change the entire system's behavior), dynamic
-  interactions cannot typically be directly measured.  Rather, the
-  interactions must be inferred through their hypothesized role in
-  guiding the dynamics of system components.  Here we use a
-  model-based approach to inferring dynamic interactions from
-  timeseries data.  In addition to examining first-order interactions
-  (e.g., between pairs of components) we also examine higher-order
-  interactions (e.g., that characterize mirrored structure in the
-  patterns of interaction dynamics displayed by different subsets of
-  components).  We apply our approach to two datasets.  First, we use
-  a synthetic dataset, for which the underlying dynamic interactions
-  are known, to show that our model recovers those ground-truth
-  dynamic interactions.  We also apply our model to a neuroimaging
-  dataset and show that the high-order dynamic interactions exhibited
-  by brain data vary meaningfully as a function of the cognitive
-  ``richness'' of the stimulus people are experiencing.
+  Our thoughts arise from coordinated activity patterns across our
+  brain.  We examined high-order dynamic correlations in functional
+  neuroimaging data collect as human participants listened to
+  different auditory stimuli varying in cognitive richness, along with
+  an additional resting state condition.  Our approach combines a
+  kernel-based method for estimating the dynamic functional
+  correlations that are similar (within task) across participants,
+  along with a dimensionality reduction approach that enables us to
+  efficiently compute high-order correlations in the data.  We trained
+  classifiers to decode the precise time, relative to the start of the
+  stimulus, when a given neural pattern was recorded.  We trained
+  these classifiers using the neural activity timeseries, first-order
+  dynamic correlations, and higher-order correlations (up to
+  tenth-order correlations), and asked which types of features led to
+  the highest decoding accuracy.  We found that second-order
+  correlations consistently yielded the highest decoding accuracy in
+  all of the listening conditions of the experiment, whereas
+  first-order correlations yielded the highest decoding accuracy at
+  rest.
 \end{abstract}

### 2019-04-17 code/scripts/pieman_cluster_submit_level_chunked.py
WIP paper

@@ -38,10 +38,10 @@ rfuns =  [str('PCA')]
 widths = [str(5)]
 
 # options for weight functions: laplace, gaussian, mexican hat, delta
-weights = ['mexican_hat']
+weights = ['gaussian']
 
 # options for debug: True or False
-debug = str('True')
+debug = str('False')
 
 job_commands = list(np.array([list(map(lambda x: x[0]+" "+str(x[1])+" "+levels+" "+str(r)+
                                                  " "+cfuns[0]+" "+rfuns[0]+" "+widths[0]+" "+weights[0]+" "+debug,

### 2019-04-22 paper/main.tex
WIP paper

@@
 \subsubsection*{Generating synthetic data}
-Ramping dataset and block dataset. Add details (Fig.~\ref{fig:synthetic_data})
+To explore recovery of a constant covariance (Fig.~\ref{fig:synthetic_data},  A.), we generated syntheic
+data sampled from a constant covariance matrix. To do this, we created one random
+covariance matrix, $K$, with 50 features, and for each of the 300 timepoints  we
+sampled from a Gaussian distribution centered on $K$.  Similarly, we generated synthetic data
+sampled from a random covariance matrix (Fig.~\ref{fig:synthetic_data},  B.) by creating a new random
+covariance matrix $K(t)$, for each of the 300 timepoints and sampled from a
+Gaussian distribution centered on $K(t)$.
+
+To generate synthetic data from a dynamically changing covariance
+matrix (ramping covariance matrix Fig.~\ref{fig:synthetic_data},  C.),
+we generated two random covariance
+matrices, $K_{1}$ and $K_{2}$.  We then computed a covariance matrix
+for each of the 300 timepoint, $K(t)$ 
+by taking the linearly spaced weights ($w$) of the two random matrices, 
+\begin{align}
+K(t) = w(t) * K_{1} + 1 - w(t) *  K_{2}
+\end{align}
+
+(Fig.~\ref{fig:synthetic_data})
+
 \begin{figure}
@@
 
-To explore recovery of a constant correlation, we generated syntheic
-data sampled from a constant covariance matrix. To do this, we created a random
-correlation matrix $K$ of size $s$, and and added a small amount of Gaussian noise
-to create a timeseries of for $s$ subjects.     \sim\mthcal{N}(\mu,\,\sigma^{2})
-
-We applied timecorr with a given kernel Fig.~\ref{fig:weights}) to
-synthetic data, then correlate each recovered
+We applied timecorr, using delta and gaussian kernels
+Fig.~\ref{fig:weights}) to each of these 
+synthetic datasets, then correlate each recovered
 correlation matrix with the ground truth.  Explore how recovery varies
-with the kernel, kernel parameters, and specific structure of the data
+with the kernel and the specific structure of the data
 (e.g. slow changes as in the ramping dataset, versus rapid changes as

### 2019-05-06 code/scripts/pieman_cluster_level_chunked.py
WIP paper

@@ -16,6 +16,8 @@ rfun = sys.argv[5]
 width = int(sys.argv[6])
 wp = sys.argv[7]
 
+chunks = 2
+
 if len(sys.argv) < 9:
     debug = False
 else:
@@ -57,58 +59,56 @@ weights_paramter = eval(wp)
 ###### REMOVE the duplicate!!
 
 if debug:
-    data_thirds = [0] * 3
-    conds_thirds = [0] * 3
+    data_chunks = [0] * chunks
+    conds_chunks = [0] * chunks
     divided = 0
-    for third in list(range(3)):
+    for chunk_amt in list(range(chunks)):
         data = []
         conds = []
         for c in pieman_conds:
-            next_data = list(map(lambda i: pieman_data[c][:, i][0][divided:divided+10,:20], np.arange(4)))
+            next_data = list(map(lambda i: pieman_data[c][:, i][0][divided:divided+(30/chunks),:20], np.arange(4)))
             data.extend(next_data)
             conds.extend([c]*len(next_data))
 
-        conds_thirds[third] = conds
-        data_thirds[third] = data
-        divided += 10
+        conds_chunks[chunk_amt] = conds
+        data_chunks[chunk_amt] = data
+        divided += (30/chunks)
 
     del pieman_data
 
 else:
 
-    data_thirds = [0] * 3
-    conds_thirds = [0] * 3
+    data_chunks = [0] * chunks
+    conds_chunks = [0] * chunks
     divided = 0
-    for third in list(range(3)):
+    for chunk_amt in list(range(chunks)):
         data = []
         conds = []
         for c in pieman_conds:
             if c == 'paragraph':
                 if factors == 700:
                     next_data = list(
-                        map(lambda i: pieman_data[c][:, i][0][divided:divided+100,:], np.where(np.arange(pieman_data[c].shape[1]) != 3)[0]))
+                        map(lambda i: pieman_data[c][:, i][0][divided:divided+(300/chunks),:], np.where(np.arange(pieman_data[c].shape[1]) != 3)[0]))
                 else:
                     next_data = list(
-                        map(lambda i: pieman_data[c][:, i][0][divided:divided+100,:], np.where(np.arange(pieman_data[c].shape[1]) != 0)[0]))
+                        map(lambda i: pieman_data[c][:, i][0][divided:divided+(300/chunks),:], np.where(np.arange(pieman_data[c].shape[1]) != 0)[0]))
             else:
[…]

### 2019-05-06 paper/main.tex
WIP paper

@@
   \includegraphics[width=\textwidth]{figs/methods_fig}
-  \caption{\textbf{Computing higher order correlations. } Correlations
-  are computed then approximated to the same size as original data.
-  This process is repeated to computer }
+  \caption{\textbf{Computing higher order correlations. } Dynamic
+    correlations
+  are computed then approximated to the same size as original data
+  using dimensionality reduction.
+  This process is repeated, and can be used to compute up to any
+  arbitrary order with compuations scaling linearly (as opposed to exponentially) with order. }
   \label{fig:methods_fig}
@@
 To generate synthetic data from a dynamically changing covariance
-matrix (ramping covariance matrix Fig.~\ref{fig:synthetic_data},  C.),
+matrix (Ramping, Fig.~\ref{fig:synthetic_data},  C.),
 we generated two random covariance
-matrices, $K_{1}$ and $K_{2}$.  We then computed a covariance matrix
-for each of the 300 timepoint, $K(t)$ 
+matrices, $K_{1}$ and $K_{2}$.  We then computed a weighted average covariance matrix
+for each of the 300 timepoint, $K(t)$, 
 by taking the linearly spaced weights ($w$) of the two random matrices, 
 \begin{align}
-K(t) = w(t) * K_{1} + 1 - w(t) *  K_{2}
+K(t) = w(t) * K_{1} + (1 - w(t)) *  K_{2},
 \end{align}
+and for each of the 300 timepoints sampled from a
+Gaussian distribution centered on $K(t)$. We also explored
+recovery by comparing this ramping synthetic data to only the first random covariance matrix $K_{1}$
+(First, Fig.~\ref{fig:synthetic_data},  C.) and using only the last
+random covariance matrix $K_{2}$ (Last, Fig.~\ref{fig:synthetic_data},
+C.).
+
+For the synthetic data containing block structure, we followed the same
+process of creating synthetic data sampled from a constant covariance
+matrix (see above) but sampled from a new random covariance matrix
+after each 60 consecutive timepoints.  We then pieced the blocks together
+to create a sythetic dataset with 300 total timepoints but drawn from
+5 separate covariance matrices. We then compared recovery using the
+total dataset (All, Fig.~\ref{fig:synthetic_data},  D.) or limiting to
+the block specific covariance matrix (Block 1-5, Fig.~\ref{fig:synthetic_data},  D.).
+
+(Fig.~\ref{fig:synthetic_data},  D.) ,
 
@@
   \includegraphics[width=\textwidth]{figs/synthetic_data.pdf}
-  \caption{\textbf{Dynamic correlation recovery with synthetic data.
-      a.Recovery using a constant dataset.} Using constant dataset,
-    how well can we recover using different
-    kernels. \textbf{b. Recovery using random dataset.}
-    \textbf{c. Ramping recovery.}  \textbf{d. Block recovery} blah}
+  \caption{\textbf{Dynamic correlation recovery with synthetic data. } Using synthetic data containing different
+    underlying correlational structure,
+   we test how well we can recover using two kernels (delta and gaussian,
+    width = 10).  We plot recovery using of datasets containing the
+    following underlying structure:
+    \textbf{a. Constant. b. Random. c. Ramping.  d. Block.}}
   \label{fig:synthetic_data}
@@
 synthetic datasets, then correlate each recovered
-correlation matrix with the ground truth.  Explore how recovery varies
+correlation matrix with the ground truth.  We explore how recovery varies
 with the kernel and the specific structure of the data
@@
 
-\begin{figure}
-  \centering
-  \includegraphics[width=\textwidth]{figs/corrmats.pdf}
-  \caption{\textbf{Inter-subject correlations by order.
-      a. Inter-subject correlation heatmaps by order.}  Heatmaps for
-    each order of how correlated each subject is with every other
-    subject grouped by condition (intact (I), paragraph
-    (P), word (W),
-    and rest (R)). \textbf{b. Mean correlation for each
-      condition by order.}
-   Bar heights indicate inter-subject correlations by conditon for each order.}
-  \label{fig:corrmats}
-\end{figure}
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section*{Discussion}
+
 \begin{itemize}

### 2019-05-07 paper/main.tex
WIP paper; finished methods and results, working on discussion

@@
 from several experimental participants, as each participant performs
-the same task (or sequence of tasks).  Let $\{ mathbf{X}_1,
-mathbf{X}_2, ..., mathbf{X}_P\}$ reflect the $T$ by $F$ observation
+the same task (or sequence of tasks).  Let $\mathbf{X}_1$,
+$\mathbf{X}_2$, ..., $\mathbf{X}_P$ reflect the $T$ by $F$ observation
 matrices for each of $P$ participants in an experiment.  We can use
@@
 where $ \backslash i$ denotes the set of all participants other than
-participant $i$. In this way, the $T$ by $\left( \frac{F^2 - F}{2}
+participant $\i$. In this way, the $T$ by $\left( \frac{F^2 - F}{2}
   + F \right)$
@@
 To generate synthetic data from a dynamically changing covariance
-matrix (Ramping, Fig.~\ref{fig:synthetic_data},  C.),
+matrix (Fig.~\ref{fig:synthetic_data},  C.),
 we generated two random covariance
@@
 \begin{align}
-K(t) = w(t) * K_{1} + (1 - w(t)) *  K_{2},
+K(t) = w(t) * K_{1} + (1 - w(t)) *  K_{2}, \\\label{eqn:ramping}
 \end{align}
 and for each of the 300 timepoints sampled from a
-Gaussian distribution centered on $K(t)$. We also explored
-recovery by comparing this ramping synthetic data to only the first random covariance matrix $K_{1}$
-(First, Fig.~\ref{fig:synthetic_data},  C.) and using only the last
-random covariance matrix $K_{2}$ (Last, Fig.~\ref{fig:synthetic_data},
-C.).
+Gaussian distribution centered on $K(t)$.
 
-For the synthetic data containing block structure, we followed the same
+Lastly, for the synthetic data containing block structure (Fig.~\ref{fig:synthetic_data},  D.), we followed the same
 process of creating synthetic data sampled from a constant covariance
 matrix (see above) but sampled from a new random covariance matrix
-after each 60 consecutive timepoints.  We then pieced the blocks together
+after 60 consecutive timepoints.  We then pieced the blocks together
 to create a sythetic dataset with 300 total timepoints but drawn from
-5 separate covariance matrices. We then compared recovery using the
-total dataset (All, Fig.~\ref{fig:synthetic_data},  D.) or limiting to
-the block specific covariance matrix (Block 1-5, Fig.~\ref{fig:synthetic_data},  D.).
-
-(Fig.~\ref{fig:synthetic_data},  D.) ,
-
-(Fig.~\ref{fig:synthetic_data})
-
-\begin{figure}
-  \centering
-  \includegraphics[width=\textwidth]{figs/synthetic_data.pdf}
-  \caption{\textbf{Dynamic correlation recovery with synthetic data. } Using synthetic data containing different
-    underlying correlational structure,
-   we test how well we can recover using two kernels (delta and gaussian,
-    width = 10).  We plot recovery using of datasets containing the
-    following underlying structure:
-    \textbf{a. Constant. b. Random. c. Ramping.  d. Block.}}
-  \label{fig:synthetic_data}
-\end{figure}
+5 separate covariance matrices.
 
@@
 correlation matrix with the ground truth.  We explore how recovery varies
-with the kernel and the specific structure of the data
-(e.g. slow changes as in the ramping dataset, versus rapid changes as
-in the block dataset).
+with the kernel and the specific structure of the data. For the
+ramping synthetic dataset (Fig.~\ref{fig:synthetic_data},  C.)  and for the
+block synthetic dataset (Fig.~\ref{fig:synthetic_data},  D.)  we made further
+comparisons of the timecorr recovered correlation matrices. We
+compared the ramping recovered correlation matrices to only the first random covariance matrix $K_{1}$
+(First, Fig.~\ref{fig:synthetic_data},  C.) and to only the last
+random covariance matrix $K_{2}$ (Last, Fig.~\ref{fig:synthetic_data},
+C.) from Equation~\ref{eqn:ramping}. We also compared the block recovered correlation matrices in to
+the block specific covariance matrix (Block 1-5,
+Fig.~\ref{fig:synthetic_data},  D.).
 
@@
 \subsubsection*{Synthetic data}
-Figure: overall timecourse of recovery, also recovery near
-event boundaries.
+
+\begin{figure}
+  \centering
+  \includegraphics[width=\textwidth]{figs/synthetic_data.pdf}
+  \caption{\textbf{Dynamic correlation recovery with synthetic data. } Using synthetic data containing different
+    underlying correlational structure,
+   we test how well we can recover dynamic correlation matrices using two kernels (delta and gaussian,
+    width = 10) when compared to groud truth.  We plot recovery using of datasets containing the
+    following underlying structure:
+    \textbf{a. Constant. b. Random. c. Ramping.  d. Block.}}
+  \label{fig:synthetic_data}
+\end{figure}
+
+To assess the performance of dynamic correlation recovery using
+timecorr, we varied width the kernel and the specific structure of the data. We applied timecorr, using delta and gaussian kernels
+Fig.~\ref{fig:weights}) to each of the following  
+synthetic datasets: constant, random, ramping, and block.  We then correlated each recovered
+correlation matrix with the ground truth.
+
+For the constant synthetic dataset, a gaussian kernel (width=10)
+outperformed the delta kernel (Fig.~\ref{fig:synthetic_data},  A.).  This is in contrast with the random
+synthetic dataset, for which the delta kernel best captures the
+rapidly changing structure (Fig.~\ref{fig:synthetic_data},  B.). For
+the ramping synthetic dataset, the slow changing strucutre within the
+data is best
+captured by the gaussian kernel and the best recovery occurs in the
+middle (Ramping, Fig.~\ref{fig:synthetic_data},
+C.). In addition to comparing the timecorr recovered correlation
+matrices to the ground truth, we
+further compared the ramping recovered correlation matrices to only the first random covariance matrix $K_{1}$
+(First, Fig.~\ref{fig:synthetic_data},  C.) and to only the last
+random covariance matrix $K_{2}$ (Last, Fig.~\ref{fig:synthetic_data},
+C.), both of which perform best at the beginning and end respectively.
+
+Similary for the block sythetic dataset, we compared the timecorr
+recovered correlation matrices to the ground truth as well as to each
+block-specific covariance matrix (Block 1-5,
+Fig.~\ref{fig:synthetic_data},  D.).  Although the structure is
+changing by block, the gaussian kernel once again outperforms the
+delta kernel.  Performance does however drop near even boundaries for
+when using the gaussian kernel.
 
@@
 (i.e. cross-validation for the second
-order contained a weighted-mixture of zeroth, first, and second order \textbf{c. Optimized weights.}.)  For
+order contained a weighted-mixture of zeroth, first, and second order (Fig.~\ref{fig:decoding_level},  C.).  For
 each order, we correlated the group 1 activity patterns with group 2
@@
 $\frac{1}{300}$, and $\frac{1}{400}$ respectively.
+
+We found that, during each of the listening conditions in the
+experiment, classifiers that incorporated second-order correlations
+yielded consistently higher accuracy than classifiers trained only on
+lower-order patterns (Fig.~\ref{fig:decoding_level},  A.).  (Incorporating higher-order correlations did
+not further improve decoding accuracy.)  By contrast, these
+higher-order correlations were not necessary to support (minimally
+above chance) decoding during a control rest condition.  This suggests
+that the cognitive processing that supported the listening conditions
+involved second-order (or higher) network dynamics.
 
@@
 
+Dynamic interactions between brain structures underlie our thoughts.
+We developed a model of neural dynamics that takes in a feature
+timeseries and outputs estimated first-order network dynamics (i.e.,
+dynamic functional correlations), second-order network dynamics
+(reflecting homologous networks that dynamically form and disperse),
+and higher-order network dynamics (up to tenth-order dynamic
+correlations).  After validating our model using synthetic data, we
+applied the approach to an fMRI dataset
+~\citep{SimoEtal16} in which participants listened to an audio recording of a story, as well as scrambled versions of the same story (where the scrambling was applied at different temporal scales).
+We trained classifiers to take the output of the model and decode the timepoint in the story (or scrambled story) that the participants were listening to.
+We found that, during each of the listening conditions in the
+experiment, classifiers that incorporated up to second-order correlations
+yielded consistently higher accuracy than classifiers trained only on
+lower-order patterns (Fig.~\ref{fig:decoding_level},  A.).  (Incorporating higher-order correlations did
+not further improve decoding accuracy.)  By contrast, these
+higher-order correlations were not necessary to support (minimally
+above chance) decoding during a control rest condition.  This suggests
+that the cognitive processing that supported the listening conditions
+involved second-order (or higher) network dynamics.
+
+Although we found decoding accuracy was best for second-order network dynamics for all but rest
+  condition, it is unclear if this is a product of the brain or the
+  data collection technique .  It could be that the brain is
+  second-order or it could be that fMRI can
+  only reliably give second-order interactions.  Exploring this method
+  with other data collection technique will be important to
+  disentangle this question.
+
 \subsection*{Concluding remarks}

### 2019-05-08 paper/main.tex
almost done with the draft... small tweaks still needed

@@
 where $ \backslash i$ denotes the set of all participants other than
-participant $\i$. In this way, the $T$ by $\left( \frac{F^2 - F}{2}
+participant $i$. In this way, the $T$ by $\left( \frac{F^2 - F}{2}
   + F \right)$
@@
 Fig.~\ref{fig:weights}) to each of these 
-synthetic datasets, then correlate each recovered
-correlation matrix with the ground truth.  We explore how recovery varies
+synthetic datasets, then correlated each recovered
+correlation matrix with the ground truth.  We repeated this process 10
+times and explored how recovery varies
 with the kernel and the specific structure of the data. For the
@@
 
-\begin{itemize}
-
-\item Decoding accuracy best for level 2 data for all but rest
-  condition.  Could be that the brain is 2nd order or that fMRI can
-  only reliable give 2nd order.  
-\item multiple timescale representations (a la Hasson group) implies
-first-order network interactions.  higher-order interactions imply
-generalizations between interacting representations (e.g. mirrored
-schema, a la Norman/Baldassano/Hasson).  possibly cite NTB 2013
-science review, using as evidence that this is where the field is
-going (voxels $\rightarrow$ patterns (L0) $\rightarrow$ interactions (L1) $\rightarrow$ higher
-order patterns (L2$+$).
-
 \begin{figure}
@@
 
-\item related approaches: sliding window, phase-based correlations,
-within-ROI spatial correlations at each timepoint, granger
-causality, other explit models (e.g. virtual brain).
-\item other applications: molecular interactions (protein folding?),
-diagnosis (e.g. psychiatric disorders as network flow problems--
-gratton work?), social network dynamics (e.g. financial markets,
-social media interactions)
-\end{itemize}
-
-Dynamic interactions between brain structures underlie our thoughts.
-We developed a model of neural dynamics that takes in a feature
-timeseries and outputs estimated first-order network dynamics (i.e.,
-dynamic functional correlations), second-order network dynamics
+Although dynamic interactions between brain structures underlie our
+thoughts, the ways in which we can study these patterns are
+limited. One challenge in studying dynamic interactions is the
+computational resources required to calculate higher-order correlations. 
+We developed a computationally tractable model of network dynamics (Fig.~\ref{fig:methods_fig}) that takes in a feature
+timeseries and outputs approximated first-order dynamics (i.e.,
+dynamic functional correlations), second-order dynamics
 (reflecting homologous networks that dynamically form and disperse),
 and higher-order network dynamics (up to tenth-order dynamic
-correlations).  After validating our model using synthetic data, we
+correlations).
+
+We first validated our model using synthetic data, and explored how
+recovery varied with different underlying data structures  and kernels.   We then 
 applied the approach to an fMRI dataset
@@
 yielded consistently higher accuracy than classifiers trained only on
-lower-order patterns (Fig.~\ref{fig:decoding_level},  A.).  (Incorporating higher-order correlations did
-not further improve decoding accuracy.)  By contrast, these
+lower-order patterns (Fig.~\ref{fig:decoding_level},  A.), and
+incorporating more higher-order correlations did
+not further improve decoding accuracy.  By contrast, these
 higher-order correlations were not necessary to support (minimally
@@
 
-Although we found decoding accuracy was best for second-order network dynamics for all but rest
+Although we found decoding accuracy was best when incorporating
+higher-order network dynamics for all but rest
   condition, it is unclear if this is a product of the brain or the
@@
   \subsection*{Concluding remarks}
-the universe is complicated and we need scalable approaches to
-studying how the pieces are interacting to make sense of it.  one
-small step for mankind, and so on.
+
+How can we better understand how these brain patterns changing over
+time? How to quantify the potential network dynamics that we might be
+driving these changes? One way to judge the techniques of the future is
+to look at the trajectory of the fMRI field so far has taken so far
+(Fig.~\ref{fig:methods_fig}).  The field started with 
+univariate activation, measuring the average activity for each voxel.
+Analyses of multivariate activation followed, looking at spatial patterns of
+activity over voxels. Next, correlations of activity were explored, first
+with measures like resting connectivity that take temporal correlation
+between a seed voxel and all other voxels then with full connectivty
+that measure all pairwise correlations.  Additionally, this path of increasing
+complexity also moved from static to dynamic measurements.  One
+logical next step in this trajectory would be dynamic higher-order
+correlations. We have created a method 
+to support these calculations.
 

### 2019-05-09 paper/main.tex
L draft done

@@
 
-We applied timecorr, using delta and gaussian kernels
+We applied timecorr, using delta and gaussian (width = 10) kernels
 Fig.~\ref{fig:weights}) to each of these 
@@
 yielded consistently higher accuracy than classifiers trained only on
-lower-order patterns (Fig.~\ref{fig:decoding_level},  A.).  (Incorporating higher-order correlations did
-not further improve decoding accuracy.)  By contrast, these
+lower-order patterns (Fig.~\ref{fig:decoding_level},  A.), and incorporating higher-order correlations did
+not further improve decoding accuracy.  By contrast, these
 higher-order correlations were not necessary to support (minimally
@@
 
-How can we better understand how these brain patterns changing over
-time? How to quantify the potential network dynamics that we might be
+How can we better understand how brain patterns change over
+time? How can we quantify the potential network dynamics that might be
 driving these changes? One way to judge the techniques of the future is
@@
 correlations. We have created a method 
-to support these calculations.
+to support these calculations by scalably approximating dynamic higher-order
+correlations.
 

### 2019-07-29 paper/main.tex
updated figure 2 size to be less crazy
updated brain plot code and reworded introduction

@@
   tenth-order correlations), and asked which types of features led to
-  the highest decoding accuracy.  We found that second-order
-  correlations consistently yielded the highest decoding accuracy in
-  all of the listening conditions of the experiment, whereas
-  first-order correlations yielded the highest decoding accuracy at
-  rest.
+  the highest decoding accuracy.  We found that higher-order
+  correlations consistently yielded higher decoding accuracy for
+  the most cogntively rich condition of the experiment, whereas
+  first-order correlations or raw data yielded the highest decoding accuracy at
+   for the less cogntively rich conditions as well as rest.
 \end{abstract}
@@
 \section*{Introduction}
-The dynamics of the observable universe are meaningful in three
-respects.  First, the behaviors of the \textit{atomic units} that
-exhibit those dynamics are highly interrelated.  The actions of one
-unit typically have implications for one or more other units.  In
-other words, there is non-trivial \textit{correlational structure}
-defining how different units interact with and relate to each other.
-Second, that correlational structure is \textit{hierarchical} in the
-sense that it exists on many spatiotemporal scales.  The way one group
-of units interacts may relate to how another group of units interact,
-and the interactions between those groups may exhibit some rich
-structure.  Third, the structure at each level of this correlational
-hierarchy changes from moment to moment, reflecting the ``behavior''
-of the full system.
+To understand the neuronal computations that support cognition, we must understand the cooperative dynamics of populations of neurons.
+These populations of neurons interact within each brain structure, and the structures interact to form complex and dynamic networks.
+These interactions, at each scale, vary according to the functions our brains are carrying out.
 
-These three properties (rich correlations, hierarchical organization,
-and dynamics) are major hallmarks of many complex systems.  For
-example, within a single cell, the cellular components interact at
-many spatiotemporal scales, and those interactions change according to
-what that single cell is doing.  Within a single human brain, the
-individual neurons interact within each brain structure, and the
-structures interact to form complex networks.  The interactions at
-each scale vary according to the functions our brains are carrying
-out.  And within social groups, interactions at different scales
-(e.g., between individuals, family units, communities, etc.) vary over
-time according to changing goals and external constraints.
+In the last several decades, advances in functional magnetic resonance image (fMRI) analyses have evolved to better characterize these interactions of brain structures.
+Resting-state (RS) fMRI has shed light on the spatiotemporal organization of spontaneous brain activity, with rich and complex network organization.
+Functional connectivity (FC) has further characterized the task dependency of these networks.
+However, recent work has shown that FC fluctuates over time (Chang and Glover, 2010), and the assumed stationarity of these analyses may be too simple to capture the dynamic nature of brain activity.
 
-Although many systems exhibit rich dynamic correlations at many
-scales, a major challenge to studying such patterns is that typically
-neither the correlations nor the hierarchical organizations of those
-correlations may be directly observed.  Rather, these fundamental
-properties must be inferred indirectly by examining the observable
-parts of the system-- e.g., the behaviors of the individual atomic
-units of that system.  In the \textit{Methods} section, we propose a
-series of mathematical operations that may be used to recover dynamic
-correlations at a range of scales (i.e., orders of interaction).  In
-the \textit{Results} section, we demonstrate how our approach may be
-applied to multi-dimensional timeseries data: a synthetic dataset
-where the underlying dynamic correlations are known (we use this
-dataset to validate our approach), and a neuroimaging dataset
-comprising data collected as participants listened to a
-story~\citep{SimoEtal16}.  In different experimental conditions in the
-neuroimaging study, participants listened to altered versions of the
-story that varied in cognitive richness: the intact story (fully
-engaging), a scrambled version of the story where the paragraphs were
-presented in a randomized order (moderately engaging), a second
-scrambled condition where the words were presented in a random order
-(minimally engaging), and a ``rest'' condition where the participants
-did not listen to any version of the story (control condition).  We
-use the neuroimaging dataset to examine how higher-order structure in
-brain data varies as a function of the cognitive richness of the
-stimulus.
+Similarly, multivariate activity patterns have given an advance over univariate activity patterns because they allow relative contributions of voxels to be combined.
+Furthermore, recent work show that dynamic correlations between multivariate voxel patterns can add an additional boost (Manning, 2018).
+
+Following this trajectory of analyses, one possible next step would be to better characterize the dynamic patterns of connectivity.
+To this end, we wished to understand if higher order cognitive processing is mediated by dynamic higher-order correlations.
+
+However, a major challenge to studying such patterns is that typically neither the correlations nor the hierarchical organizations of those correlations may be directly observed.
+Rather, these fundamental properties must be inferred indirectly by examining the observable parts of the system-- e.g., the behaviors of the individual units of that system.
+In the \textit{Methods} section, we propose a series of mathematical operations that may be used to recover dynamic correlations at a range of scales (i.e., orders of interaction).
+In the \textit{Results} section, we demonstrate how our approach may be applied to multi-dimensional timeseries data: a synthetic dataset where the underlying dynamic correlations are known (we use this dataset to validate our approach), and a neuroimaging dataset comprising data collected as participants listened to a story~\citep{SimoEtal16}.
+In different experimental conditions in the neuroimaging study, participants listened to altered versions of the story that varied in cognitive richness: the intact story (fully engaging), a scrambled version of the story where the paragraphs were presented in a randomized order (moderately engaging), a second scrambled condition where the words were presented in a random order (minimally engaging), and a ``rest'' condition where the participants did not listen to any version of the story (control condition).
+We use the neuroimaging dataset to examine how higher-order structure in brain data varies as a function of the cognitive richness of the stimulus.
 
@@
   \centering
-  \includegraphics[width=\textwidth]{figs/methods_fig}
+  \includegraphics[width=0.5\textwidth]{figs/methods_fig}
   \caption{\textbf{Computing higher order correlations. } Dynamic

### 2019-07-29 paper/main.tex
WIP paper edits

@@
 
-In the last several decades, advances in functional magnetic resonance image (fMRI) analyses have evolved to better characterize these interactions of brain structures.
-Resting-state (RS) fMRI has shed light on the spatiotemporal organization of spontaneous brain activity, with rich and complex network organization.
-Functional connectivity (FC) has further characterized the task dependency of these networks.
-However, recent work has shown that FC fluctuates over time (Chang and Glover, 2010), and the assumed stationarity of these analyses may be too simple to capture the dynamic nature of brain activity.
+In the last several decades, advances in functional magnetic resonance
+image (fMRI) analyses have evolved to better characterize these
+interactions of brain structures.  As Turk-Brown (2013) outlines,
+analyses using multivariate patterns of activity have given an advance
+over univariate activity patterns because they allow relative
+contributions of voxels to be combined and better assess distrubted
+representations. Resting-state connectivity (RS) fMRI, which is the
+temporal correlation of regions during rest, has shed light on the
+rich and complex spatiotemporal organization of spontaneous brain
+activity.  Functional connectivity (FC) has further characterized the
+cognitive state dependency of this network organization.
 
-Similarly, multivariate activity patterns have given an advance over univariate activity patterns because they allow relative contributions of voxels to be combined.
-Furthermore, recent work show that dynamic correlations between multivariate voxel patterns can add an additional boost (Manning, 2018).
-
-Following this trajectory of analyses, one possible next step would be to better characterize the dynamic patterns of connectivity.
-To this end, we wished to understand if higher order cognitive processing is mediated by dynamic higher-order correlations.
-
-However, a major challenge to studying such patterns is that typically neither the correlations nor the hierarchical organizations of those correlations may be directly observed.
-Rather, these fundamental properties must be inferred indirectly by examining the observable parts of the system-- e.g., the behaviors of the individual units of that system.
-In the \textit{Methods} section, we propose a series of mathematical operations that may be used to recover dynamic correlations at a range of scales (i.e., orders of interaction).
-In the \textit{Results} section, we demonstrate how our approach may be applied to multi-dimensional timeseries data: a synthetic dataset where the underlying dynamic correlations are known (we use this dataset to validate our approach), and a neuroimaging dataset comprising data collected as participants listened to a story~\citep{SimoEtal16}.
-In different experimental conditions in the neuroimaging study, participants listened to altered versions of the story that varied in cognitive richness: the intact story (fully engaging), a scrambled version of the story where the paragraphs were presented in a randomized order (moderately engaging), a second scrambled condition where the words were presented in a random order (minimally engaging), and a ``rest'' condition where the participants did not listen to any version of the story (control condition).
-We use the neuroimaging dataset to examine how higher-order structure in brain data varies as a function of the cognitive richness of the stimulus.
+Recent work has shown that FC fluctuates over time (Chang and Glover, 2010), and the assumed stationarity of these analyses may be too simple to capture the dynamic nature of brain activity.
+Additionally, recent work show that dynamic correlations between multivariate voxel patterns can add an additional boost (Manning, 2018).
+Following this line of reasoning, we expect higher-order network
+dynamics might provide even richer insights into the neural basis of
+cognition. We sought to test this hypothesis by developing an approach
+to inferring high-order network dynamics from timeseries data,
+validating the approach using synthetic data, and then applying the approach to
+a neuroimaging dataset comprising data collected as participants listened to a story~\citep{SimoEtal16}.
+We tested the hypothesis that as people listen to stimuli varying in cognitive richness, the neural patterns that
+support processing of those stimuli vary with respect to the order of the dynamic interactions recruited.
 
 \section*{Methods}
+A major challenge to studying such patterns is that typically neither
+the correlations nor the hierarchical organizations of those
+correlations may be directly observed.  Rather, these fundamental
+properties must be inferred indirectly by examining the observable
+parts of the system-- e.g., the behaviors of the individual units of
+that system.  Here we propose a series of mathematical operations that may be used to approximate dynamic correlations at a range of scales (i.e., orders of interaction).
+
 There are two basic steps to our approach (Fig.~\ref{fig:methods_fig}).  In the first step, we take
@@
 Following the analyses conducted by (HTFA)~\cite{MannEtal18}, we first
-applied \textit{hierarchical topographic factor analysis} (HTFA) to the fMRI datasets to obtain a time series of 700 node activities for every participant.
-We then computed the dynamic weighted ISFC using a gaussian kernel with a width of 5.
-We then approximated these dynamic correlation using PCA and computed the dynamic weighted ISFC on the approximations.
+applied \textit{hierarchical topographic factor analysis} (HTFA) to
+the fMRI datasets to obtain a time series of 700 node activities for
+every participant.  We then computed the dynamic weighted ISFC using a
+range of kernels and widths.  Specifically, we used Gaussian, Laplace,
+and mexican hat kernels, as well as widths of 5, 10, 20, and 50.  We
+then approximated these dynamic correlation using two reduction measures, PCA and eigenvector centrality, and computed the dynamic weighted ISFC on the approximations.
 We repeated this process up to 10th order approximated correlations.
@@
 To assess the performance of dynamic correlation recovery using
-timecorr, we varied width the kernel and the specific structure of the data. We applied timecorr, using delta and gaussian kernels
+timecorr, we varied width the kernel and the specific structure of the
+data. We applied timecorr, using delta and gaussian kernels
 Fig.~\ref{fig:weights}) to each of the following  
@@
   \caption{\textbf{Decoding by order.
-      a. Relative decoding accuracy by order.} Ribbons of each
-    color display cross-validated decoding performance for each condition (intact, paragraph, word,
-    and rest. Decoders were trained using increasingly more
+      a. d. Relative decoding accuracy by order.} Ribbons of each
+    color display cross-validated decoding performance averaged over
+    all parameters for each condition (intact, paragraph, word,
+    and rest) using PCA (a.) or eigenvector centrality (d.) to
+    approximate correlations. Decoders were trained using increasingly more
     higher-order information and this ribbons are displayed relative
     to chance at 0. The red dots indicates
-    maximum decoding accuracy for each condition. \textbf{b. Normalized decoding accuracy
-      by order.}  We normalized the decoding accuracy by order to better
+    maximum decoding accuracy for each condition. \textbf{b. e. Z-transformed decoding accuracy
+      by order.}  We Z-transformed the decoding accuracy by order to better
     visualize the order with the maximum decoding accuracy for each
-    condition. \textbf{c. Optimized weights.} Bar heights indicate the
+    condition using PCA (b.) or eigenvector centrality (e.) to
+    approximate correlations. \textbf{c. f. Optimized weights.} Bar heights indicate the
     optimized mixing paramete $\phi$ of each contributing order up to
     and including the order with the maximum
-    decoding accuracy for each contributing order
+    decoding accuracy for each contributing order using PCA (c.) or eigenvector centrality (f.) to
+    approximate correlations.
   For the order with maximum decoding accuracy by condition, we show
@@
 (i.e. cross-validation for the second
-order contained a weighted-mixture of zeroth, first, and second order (Fig.~\ref{fig:decoding_level},  C.).  For
+order contained a weighted-mixture of zeroth, first, and second order
+(Fig.~\ref{fig:decoding_level}, c. and f.).  For
 each order, we correlated the group 1 activity patterns with group 2
@@
 participants to the two groups each time) to obtain a distribution of
-decoding accuracies for each experimental condition. (There were 272
+decoding accuracies for each experimental condition. There were 272
 timepoints for paragraph condition, 300 timepoints for intact and word
@@
 
-We found that, during each of the listening conditions in the
-experiment, classifiers that incorporated second-order correlations
+We repeated this process for each set of parameters, varying kernel
+type and width, and averaged over the reduction technique used to
+approximate the higher-order correlations (PCA Fig.~\ref{fig:decoding_level},  a.-c. and eigenvector
+centrality Fig.~\ref{fig:decoding_level},  d.-f.).  Since there is no ground truth in these analyses, and we did not know
+which parameters best capture the data, we instead report a robustness
+search by averaging over the parameters and reporting which results
+consistently showed up across all parameters.
+\begin{figure}
+  \centering
+  \includegraphics[width=\textwidth]{figs/brain_plots.pdf}
+  \caption{\textbf{Average correlations by order for the intact listening condition.} Using eigenvector
+    centrality to approximate higher-order correlations for the intact
+    listening condition, we plot the
+    strongest 25\% absolute value
+    mean correlation for \textbf{a. order 1. b. order 2. c. order 3.,
+      and d. order 4}.}
+  \label{fig:brain_plots}
+\end{figure}
+
+The two methods used to approximate the higher-order correlations (PCA Fig.~\ref{fig:decoding_level},  a.-c. and eigenvector
+centrality Fig.~\ref{fig:decoding_level},  d.-f.) capture different
+facets of the activity patterns.  Using PCA, the higher-order
+correlations are all linked to the original activity patterns, whereas
+eigenvectory centrality breaks the immediate link with specific brain
+areas and instead characterizes the position of the nodes in the
+network that are similar over time.
+
+We found for both PCA and eigenvector centrality, during the intact condition in the
+experiment, classifiers that incorporated higher-order correlations
 yielded consistently higher accuracy than classifiers trained only on
-lower-order patterns (Fig.~\ref{fig:decoding_level},  A.), and incorporating higher-order correlations did
-not further improve decoding accuracy.  By contrast, these
-higher-order correlations were not necessary to support (minimally
-above chance) decoding during a control rest condition.  This suggests
-that the cognitive processing that supported the listening conditions
-involved second-order (or higher) network dynamics.
+lower-order patterns (Fig.~\ref{fig:decoding_level},  a. d.).  We plot
+the average correlations for up to the fourth order for the intact
+condition Fig.~\ref{fig:brain_plots}.  By
+contrast, we found that incorporating higher-order (greater than first
+order) correlations did
+not further improve decoding accuracy for the other listening
+conditions or rest condition.  This suggests
+that the cognitive processing that supported the most cognitively rich
+condition
+involved higher-order network dynamics.
 
@@
   \includegraphics[width=\textwidth]{figs/direction_of_field.pdf}
-  \caption{\textbf{Direction of the field.} }
+  \caption{\textbf{Direction of the field adapted from
+      ~\citep{Turk13}.} The evolution of fMRI analyses started with
+    univariate activation, which refers to
+    the average amplitude of BOLD activity evoked by events of an
+    experimental condition. Next, multivariate classifiers are trained
+    on patterns of activation across voxels to decode distributed
+    representations for specific events. The next, resting
+    connectivity, is the temporal correlation of one or more seed
+    regions with the remainder of the brain during rest. Additionally,
+    task-based connectivity examines how these correlations differ by
+    cognitive state. Following this increasing trajectory of
+    increasing complexity, full connectivity considers all pairwise
+    correlations in the brain, most commonly at rest.  Next, dynamic
+    full connectivity considers how full connectivity changes over
+    time. Continuing this line of reasoning, we expect higher-order network dynamics might provide even richer insights into the neural basis of cognition.}
   \label{fig:direction_of_field}
@@
 
-Although dynamic interactions between brain structures underlie our
-thoughts, the ways in which we can study these patterns are
-limited. One challenge in studying dynamic interactions is the
+Based on prior work (CITE) and following the direction of the field ~\citep{Turk13} we think our thoughts might be encoded in
+dynamic network patterns, and possibly higher order network
+patterns (Fig.~\ref{fig:direction_of_field}). We sought to test this hypothesis by developing an approach
+to inferring high-order network dynamics from timeseries data.
+
+One challenge in studying dynamic interactions is the
 computational resources required to calculate higher-order correlations. 
@@
 applied the approach to an fMRI dataset
-~\citep{SimoEtal16} in which participants listened to an audio recording of a story, as well as scrambled versions of the same story (where the scrambling was applied at different temporal scales).
-We trained classifiers to take the output of the model and decode the timepoint in the story (or scrambled story) that the participants were listening to.
-We found that, during each of the listening conditions in the
-experiment, classifiers that incorporated up to second-order correlations
+~\citep{SimoEtal16} in which participants listened to an audio
+recording of a story, as well as scrambled versions of the same story
+(where the scrambling was applied at different temporal scales).  We
+trained classifiers to take the output of the model and decode the
+timepoint in the story (or scrambled story) that the participants were
+listening to. We found that, during the intact listening condition in the
+experiment, classifiers that incorporated higher-order correlations
 yielded consistently higher accuracy than classifiers trained only on
-lower-order patterns (Fig.~\ref{fig:decoding_level},  A.), and
-incorporating more higher-order correlations did
-not further improve decoding accuracy.  By contrast, these
-higher-order correlations were not necessary to support (minimally
-above chance) decoding during a control rest condition.  This suggests
-that the cognitive processing that supported the listening conditions
+lower-order patterns (Fig.~\ref{fig:decoding_level},  a. d.).  By contrast, these
+higher-order correlations were not necessary to support decoding the other
+listening conditions and (minimally
+above chance) during a control rest condition.  This suggests
+that the cognitive processing that supported the most cogntively rich listening conditions
 involved second-order (or higher) network dynamics.

### 2019-07-30 paper/main.tex
added citations, doing last read through for draft

@@
 \section*{Introduction}
-To understand the neuronal computations that support cognition, we must understand the cooperative dynamics of populations of neurons.
-These populations of neurons interact within each brain structure, and the structures interact to form complex and dynamic networks.
-These interactions, at each scale, vary according to the functions our brains are carrying out.
+To understand the neuronal computations that support cognition, we
+must understand the cooperative dynamics of populations of neurons.
+These populations of neurons interact within each brain structure, and
+the structures interact to form complex and dynamic networks. These
+interactions, at each scale, vary according to the functions our
+brains are carrying out and recent work has shown these dynamic
+complex patterns support consciousness~\citep{DemeEtal19}.
 
@@
 image (fMRI) analyses have evolved to better characterize these
-interactions of brain structures.  As Turk-Brown (2013) outlines,
+interactions of brain structures.  As~\cite{Turk13} outlines,
 analyses using multivariate patterns of activity have given an advance
@@
 
-Recent work has shown that FC fluctuates over time (Chang and Glover, 2010), and the assumed stationarity of these analyses may be too simple to capture the dynamic nature of brain activity.
-Additionally, recent work show that dynamic correlations between multivariate voxel patterns can add an additional boost (Manning, 2018).
+Recent work has shown that FC fluctuates over time~\citep{ChanGlov10}~\citep[for review]{LuriEtal19}, and the assumed stationarity of these analyses may be too
+simple to capture the dynamic nature of brain activity.  Additionally,
+recent work has shown that temporal
+variability in functional connectivity predicts attention task
+performance~\citep{FongEtal18} and that
+dynamic correlations between multivariate voxel patterns can add an
+additional boost compared to static multivariate voxel patterns alone~\citep{MannEtal18}.
+
 Following this line of reasoning, we expect higher-order network
@@
 validating the approach using synthetic data, and then applying the approach to
-a neuroimaging dataset comprising data collected as participants listened to a story~\citep{SimoEtal16}.
-We tested the hypothesis that as people listen to stimuli varying in cognitive richness, the neural patterns that
-support processing of those stimuli vary with respect to the order of the dynamic interactions recruited.
+a neuroimaging dataset comprising data collected as participants
+listened to a story varying in cognitive richness~\citep{SimoEtal16}.
 
@@
 For each order we obtained the weighted-mixture of the correlation
-matrices for the current order and all previous orders using mixing parameter , $\phi$, where $0 <\phi< 1$ reflects a
+matrices for the current order and all previous orders using mixing parameter, $\phi$, where $0 <\phi< 1$ reflects a
 weighted mixture of order based decoding Fig.~\ref{fig:decoding_level}
@@
 subdividing the training group and using the quasi-Newton method of
-Broyden, Fletcher, Goldfarb, and Shanno (BFGS) for optimization. We
-repeated this cross-validation process 100 times.
+Broyden, Fletcher, Goldfarb, and Shanno (BFGS ~\citep{NoceWrig06}) for optimization. We
+repeated this cross-validation process 10 times for each parameter set.
 
@@
 \href{url}{http://arks. princeton.edu/ark:/88435/dsp015d86p269k}.
-Bars of each color display cross-validated decoding performance for decoders trained using different sets of neural features: whole-brain patterns of voxel activities
+
 \begin{figure}
@@
   \caption{\textbf{Decoding by order.
-      a. d. Relative decoding accuracy by order.} Ribbons of each
+      a.\&d. Relative decoding accuracy by order.} Ribbons of each
     color display cross-validated decoding performance averaged over
@@
     to chance at 0. The red dots indicates
-    maximum decoding accuracy for each condition. \textbf{b. e. Z-transformed decoding accuracy
+    maximum decoding accuracy for each condition. \textbf{b.\&e. Z-transformed decoding accuracy
       by order.}  We Z-transformed the decoding accuracy by order to better
@@
     condition using PCA (b.) or eigenvector centrality (e.) to
-    approximate correlations. \textbf{c. f. Optimized weights.} Bar heights indicate the
+    approximate correlations. \textbf{c.\&f. Optimized weights.} Bar heights indicate the
     optimized mixing paramete $\phi$ of each contributing order up to
@@
     mean correlation for \textbf{a. order 1. b. order 2. c. order 3.,
-      and d. order 4}.}
+      and d. order 4}, representing the degree of agreement by
+    location pair over time.}
   \label{fig:brain_plots}
@@
 yielded consistently higher accuracy than classifiers trained only on
-lower-order patterns (Fig.~\ref{fig:decoding_level},  a. d.).  We plot
+lower-order patterns (Fig.~\ref{fig:decoding_level},  a.\&d.).  We plot
 the average correlations for up to the fourth order for the intact
-condition Fig.~\ref{fig:brain_plots}.  By
+condition (Fig.~\ref{fig:brain_plots}) representing the degree of
+agreement by location pair over time.  By
 contrast, we found that incorporating higher-order (greater than first
@@
   \includegraphics[width=\textwidth]{figs/direction_of_field.pdf}
-  \caption{\textbf{Direction of the field adapted from
-      ~\citep{Turk13}.} The evolution of fMRI analyses started with
+  \caption{\textbf{Direction of the field (adapted from
+      ~\citep{Turk13}).} The evolution of fMRI analyses started with
     univariate activation, which refers to
@@
 
-Based on prior work (CITE) and following the direction of the field ~\citep{Turk13} we think our thoughts might be encoded in
+Based on prior work ~\citep{Deme19} and following the direction of the field ~\citep{Turk13} we think our thoughts might be encoded in
 dynamic network patterns, and possibly higher order network

### 2019-07-30 paper/main.tex
minor formatting updates

@@
 \subsubsection*{Generating synthetic data}
-To explore recovery of a constant covariance (Fig.~\ref{fig:synthetic_data},  A.), we generated syntheic
+To explore recovery of a constant covariance (Fig.~\ref{fig:synthetic_data},  a.), we generated syntheic
 data sampled from a constant covariance matrix. To do this, we created one random
@@
 sampled from a Gaussian distribution centered on $K$.  Similarly, we generated synthetic data
-sampled from a random covariance matrix (Fig.~\ref{fig:synthetic_data},  B.) by creating a new random
+sampled from a random covariance matrix (Fig.~\ref{fig:synthetic_data}, b.) by creating a new random
 covariance matrix $K(t)$, for each of the 300 timepoints and sampled from a
@@
 To generate synthetic data from a dynamically changing covariance
-matrix (Fig.~\ref{fig:synthetic_data},  C.),
+matrix (Fig.~\ref{fig:synthetic_data},  c.),
 we generated two random covariance
@@
 
-Lastly, for the synthetic data containing block structure (Fig.~\ref{fig:synthetic_data},  D.), we followed the same
+Lastly, for the synthetic data containing block structure (Fig.~\ref{fig:synthetic_data},  d.), we followed the same
 process of creating synthetic data sampled from a constant covariance
@@
 with the kernel and the specific structure of the data. For the
-ramping synthetic dataset (Fig.~\ref{fig:synthetic_data},  C.)  and for the
-block synthetic dataset (Fig.~\ref{fig:synthetic_data},  D.)  we made further
+ramping synthetic dataset (Fig.~\ref{fig:synthetic_data},  c.)  and for the
+block synthetic dataset (Fig.~\ref{fig:synthetic_data},  d.)  we made further
 comparisons of the timecorr recovered correlation matrices. We
 compared the ramping recovered correlation matrices to only the first random covariance matrix $K_{1}$
-(First, Fig.~\ref{fig:synthetic_data},  C.) and to only the last
+(First, Fig.~\ref{fig:synthetic_data},  c.) and to only the last
 random covariance matrix $K_{2}$ (Last, Fig.~\ref{fig:synthetic_data},
-C.) from Equation~\ref{eqn:ramping}. We also compared the block recovered correlation matrices in to
+c.) from Equation~\ref{eqn:ramping}. We also compared the block recovered correlation matrices in to
 the block specific covariance matrix (Block 1-5,
-Fig.~\ref{fig:synthetic_data},  D.).
+Fig.~\ref{fig:synthetic_data},  d.).
 
@@
 weighted mixture of order based decoding Fig.~\ref{fig:decoding_level}
-Panel C. ). We calculated  $\phi$, by
+Panel c. ). We calculated  $\phi$, by
 subdividing the training group and using the quasi-Newton method of
@@
 For the constant synthetic dataset, a gaussian kernel (width=10)
-outperformed the delta kernel (Fig.~\ref{fig:synthetic_data},  A.).  This is in contrast with the random
+outperformed the delta kernel (Fig.~\ref{fig:synthetic_data},  a.).  This is in contrast with the random
 synthetic dataset, for which the delta kernel best captures the
-rapidly changing structure (Fig.~\ref{fig:synthetic_data},  B.). For
+rapidly changing structure (Fig.~\ref{fig:synthetic_data},  b.). For
 the ramping synthetic dataset, the slow changing strucutre within the
@@
 middle (Ramping, Fig.~\ref{fig:synthetic_data},
-C.). In addition to comparing the timecorr recovered correlation
+c.). In addition to comparing the timecorr recovered correlation
 matrices to the ground truth, we
 further compared the ramping recovered correlation matrices to only the first random covariance matrix $K_{1}$
-(First, Fig.~\ref{fig:synthetic_data},  C.) and to only the last
+(First, Fig.~\ref{fig:synthetic_data},  c.) and to only the last
 random covariance matrix $K_{2}$ (Last, Fig.~\ref{fig:synthetic_data},
-C.), both of which perform best at the beginning and end respectively.
+c.), both of which perform best at the beginning and end respectively.
 
@@
 block-specific covariance matrix (Block 1-5,
-Fig.~\ref{fig:synthetic_data},  D.).  Although the structure is
+Fig.~\ref{fig:synthetic_data},  d.).  Although the structure is
 changing by block, the gaussian kernel once again outperforms the
@@
 order contained a weighted-mixture of zeroth, first, and second order
-(Fig.~\ref{fig:decoding_level}, c. and f.).  For
+(Fig.~\ref{fig:decoding_level}, c.\&f.).  For
 each order, we correlated the group 1 activity patterns with group 2
@@
     strongest 25\% absolute value
-    mean correlation for \textbf{a. order 1. b. order 2. c. order 3.,
-      and d. order 4}, representing the degree of agreement by
+    mean correlation for order: \textbf{a. 1. b. 2. c. 3.,
+      and d. 4}, representing the degree of agreement by
     location pair over time.}
@@
   \includegraphics[width=\textwidth]{figs/direction_of_field.pdf}
-  \caption{\textbf{Direction of the field (adapted from
-      ~\citep{Turk13}).} The evolution of fMRI analyses started with
+  \caption{\textbf{Direction of the field (adapted from~\citep{Turk13}).} The evolution of fMRI analyses started with
     univariate activation, which refers to
@@
 yielded consistently higher accuracy than classifiers trained only on
-lower-order patterns (Fig.~\ref{fig:decoding_level},  a. d.).  By contrast, these
+lower-order patterns (Fig.~\ref{fig:decoding_level},  a.\&d.).  By contrast, these
 higher-order correlations were not necessary to support decoding the other
@@
   condition, it is unclear if this is a product of the brain or the
-  data collection technique .  It could be that the brain is
+  data collection technique.  It could be that the brain is
   second-order or it could be that fMRI can

### 2019-08-02 paper/main.tex

@@
 
-Recent work has shown that FC fluctuates over time~\citep{ChanGlov10}~\citep[for review]{LuriEtal19}, and the assumed stationarity of these analyses may be too
+Recent work has shown that FC fluctuates over time~\citep{ChanGlov10}~\citep[for review]{LuriEtal18}, and the assumed stationarity of these analyses may be too
 simple to capture the dynamic nature of brain activity.  Additionally,
@@
 variability in functional connectivity predicts attention task
-performance~\citep{FongEtal18} and that
+performance~\citep{FongEtal19} and that
 dynamic correlations between multivariate voxel patterns can add an
@@
     underlying correlational structure,
-   we test how well we can recover dynamic correlation matrices using two kernels (delta and gaussian,
-    width = 10) when compared to groud truth.  We plot recovery using of datasets containing the
+   we test how well we can recover dynamic correlation matrices using
+   different kernels when compared to groud truth.  We compare the results using a delta kernel
+   with averaged results from several kernels (Gaussian, Laplace, and
+   mexican hat) and several widths (5, 10, 20, and 50).  We plot recovery using of datasets containing the
     following underlying structure:
@@
   \caption{\textbf{Average correlations by order for the intact listening condition.} Using eigenvector
-    centrality to approximate higher-order correlations for the intact
-    listening condition, we plot the
+    centrality to approximate higher-order correlations for \textbf{a.-d. intact, e.-h. paragraph scrambled,
+      i.-l. word scrambled, and m.-p. rest } conditions, we plot the
     strongest 25\% absolute value
-    mean correlation for order: \textbf{a. 1. b. 2. c. 3.,
-      and d. 4}, representing the degree of agreement by
+    mean correlation for first through fourth orders, representing the degree of agreement by
     location pair over time.}
@@
 
-Based on prior work ~\citep{Deme19} and following the direction of the field ~\citep{Turk13} we think our thoughts might be encoded in
+Based on prior work ~\citep{DemeEtal19} and following the direction of the field ~\citep{Turk13} we think our thoughts might be encoded in
 dynamic network patterns, and possibly higher order network

### 2019-08-07 paper/boneyard.tex
re-worked abstract and intro, updated bibliography

@@
+To understand the neuronal computations that support cognition, we
+must understand the cooperative dynamics of populations of neurons.
+These populations of neurons interact within each brain structure, and
+the structures interact to form complex and dynamic networks. These
+interactions, at each scale, vary according to the functions our
+brains are carrying out and recent work has shown these dynamic
+complex patterns support consciousness~\citep{DemeEtal19}.
+
+In the last several decades, advances in functional magnetic resonance
+image (fMRI) analyses have evolved to better characterize these
+interactions of brain structures.  As~\cite{Turk13} outlines,
+analyses using multivariate patterns of activity have given an advance
+over univariate activity patterns because they allow relative
+contributions of voxels to be combined and better assess distrubted
+representations. Resting-state connectivity (RS) fMRI, which is the
+temporal correlation of regions during rest, has shed light on the
+rich and complex spatiotemporal organization of spontaneous brain
+activity.  Functional connectivity (FC) has further characterized the
+cognitive state dependency of this network organization.
+
+Recent work has shown that FC fluctuates over time~\citep{ChanGlov10}~\citep[for review]{LuriEtal18}, and the assumed stationarity of these analyses may be too
+simple to capture the dynamic nature of brain activity.  Additionally,
+recent work has shown that temporal
+variability in functional connectivity predicts attention task
+performance~\citep{FongEtal19} and that
+dynamic correlations between multivariate voxel patterns can add an
+additional boost compared to static multivariate voxel patterns alone~\citep{MannEtal18}.
+
   Most complex systems reflect dynamic interactions between myriad

### 2019-08-07 paper/main.tex
re-worked abstract and intro, updated bibliography

@@
 \usepackage{hyperref}
-\usepackage{natbib}
+\usepackage[sort]{natbib}
 \usepackage{pxfonts}
@@
 
-\title{High-order dynamic neural correlations reflect naturalistic processing
-in humans} \author{Lucy
-  L. W. Owen$^1$, Thomas H. Chang$^{1,2}$, and\
+\title{High-level cognition is supported by at least second order
+  dynamic correlations in neural activity patterns}
+
+\author{Lucy L. W. Owen$^1$, Thomas H. Chang$^{1,2}$, and\
   Jeremy R. Manning\textsuperscript{$1, \dagger$}\\
@@
 \begin{abstract}
-  Our thoughts arise from coordinated activity patterns across our
-  brain. We examined high-order dynamic correlations in functional
-  neuroimaging data collect as human participants listened to
-  different auditory stimuli varying in cognitive richness, along with
-  an additional resting state condition. Our approach combines a
-  kernel-based method for estimating the dynamic functional
-  correlations that are similar (within task) across participants,
-  along with a dimensionality reduction approach that enables us to
-  efficiently compute high-order correlations in the data. We trained
-  classifiers to decode the precise time, relative to the start of the
-  stimulus, when a given neural pattern was recorded. We trained
-  these classifiers using the neural activity timeseries, first-order
-  dynamic correlations, and higher-order correlations (up to
-  tenth-order correlations), and asked which types of features led to
-  the highest decoding accuracy. We found that higher-order
-  correlations consistently yielded higher decoding accuracy for
-  the most cogntively rich condition of the experiment, whereas
-  first-order correlations or raw data yielded the highest decoding accuracy at
-   for the less cogntively rich conditions as well as rest.
+  Our thoughts arise from coordinated patterns of interactions between
+  brain structures that change with our ongoing experiences.
+  High-order dynamic correlations in brain activity patterns reflect
+  different subgraphs of the brain's connectome that display
+  homologous lower-level dynamic correlations.  We tested the
+  hypothesis that high-level cognition is supported by high-order
+  dynamic correlations in brain activity patterns.  We developed an
+  approach to estimating high-order dynamic correlations in timeseries
+  data, and we applied the approach to neuroimaging data collected as
+  human participants either listened to a ten-minute story or a
+  temporally scrambled version of the story, or underwent a resting
+  state scan.  We trained across-participants pattern classifiers to
+  decode (in held-out data) when in the session each activity snapshot
+  was collected.  We found that classifiers trained to decode from
+  high-order dynamic correlations yielded better performance on data
+  collected as participants listened to the (unscrambled) story.  By
+  contrast, classifiers trained to decode data from scrambled versions
+  of the story or during the resting state scan yielded the best
+  performance when they were trained using first-order dynamic
+  correlations or raw activity patterns.  We suggest that as our
+  thoughts become more complex, they are supported by higher-order
+  patterns of dynamic network interactions throughout the brain.
 \end{abstract}
@@
 \section*{Introduction}
-To understand the neuronal computations that support cognition, we
-must understand the cooperative dynamics of populations of neurons.
-These populations of neurons interact within each brain structure, and
-the structures interact to form complex and dynamic networks. These
-interactions, at each scale, vary according to the functions our
-brains are carrying out and recent work has shown these dynamic
-complex patterns support consciousness~\citep{DemeEtal19}.
+A central goal in cognitive neuroscience is to elucidate the
+\textit{neural code}: the mapping between (a) mental states or
+cognitive representations and (b) neural activity patterns. One means
+of testing models of the neural code is to ask how accurately that
+model is able to ``translate'' neural activity patterns into known (or
+hypothesized) mental states or cognitive
+representations~\citep[e.g.,][]{HaxbEtal01, NormEtal06, TongPrat12,
+  MitcEtal08a, KamiTong05, NishEtal11, PereEtal18, HuthEtal12,
+  HuthEtal16}.  Training decoding models on different types of neural
+features can also help to elucidate which specific aspects of neural
+activity patterns are informative about cognition-- and, by extension,
+which types of neural activity patterns might comprise the neural
+code.  For example, prior work has used region of interest analyses to
+estimate the anatomical locations of specific neural
+representations~\citep[e.g.,][]{EtzeEtal09}, or to compare the
+relative contributions to the neural code of multivariate activity
+patterns versus patterns of dynamic correlations between neural
+activity patterns~\citep[e.g.,][]{MannEtal18, FongEtal19}.  An
+emerging theme in this literature is that cognition is mediated by
+complex dynamic interactions between brain
+structures~\citep{SporHone06, BassEtal06, Turk13, DemeEtal19}.
 
-In the last several decades, advances in functional magnetic resonance
-image (fMRI) analyses have evolved to better characterize these
-interactions of brain structures.  As~\cite{Turk13} outlines,
-analyses using multivariate patterns of activity have given an advance
-over univariate activity patterns because they allow relative
-contributions of voxels to be combined and better assess distrubted
-representations. Resting-state connectivity (RS) fMRI, which is the
-temporal correlation of regions during rest, has shed light on the
-rich and complex spatiotemporal organization of spontaneous brain
-activity.  Functional connectivity (FC) has further characterized the
-cognitive state dependency of this network organization.
+Studies of the neural code to date have primarily focused on
+univariate or multivariate neural patterns~\cite[for review
+see][NormEtal06], or (more recently) on patterns of dynamic
+first-order correlations~\citep[i.e., interactions between pairs of
+brain structures;][]{MannEtal18, FongEtal19}.  We wondered what the
+future of this line of work might hold.  For example, is the neural
+code mediated by higher-order interactions between brain structures?
+Second-order correlations reflect \textit{homologous} patterns of
+correlation.  In other words, if the changing patterns of correlations
+between two regions, $A$ and $B$, are similar to those between two
+other regions, $C$ and $D$, this would be reflected in the
+second-order correlations between ($A$--$B$) and ($C$--$D$).  In this
+way, second-order correlations identify similarities and differences
+between subgraphs of the brain's connectome.  Analogously, third-order
+correlations reflect homologies between second-order correlations--
+i.e., homologous patterns of homologous interactions between brain
+regions.  More generally, higher-order correlations reflect homologies
+between patterns of lower-order correlations.  We can then ask: which
+``orders'' of interaction are most reflective of high-level cognitive
+processes?
 
-Recent work has shown that FC fluctuates over time~\citep{ChanGlov10}~\citep[for review]{LuriEtal18}, and the assumed stationarity of these analyses may be too
-simple to capture the dynamic nature of brain activity.  Additionally,
-recent work has shown that temporal
-variability in functional connectivity predicts attention task
-performance~\citep{FongEtal19} and that
-dynamic correlations between multivariate voxel patterns can add an
-additional boost compared to static multivariate voxel patterns alone~\citep{MannEtal18}.
+Another central question pertains to the extent to which the neural
+code is carried by activity patterns that directly reflect ongoing
+cognition~\citep[e.g., following][]{HaxbEtal01, NormEtal06}, versus
+the dynamic properties of the network structure itself, independent of
+specific activity patterns in any given set of regions~\citep[e.g.,
+following][]{BassEtal06}.  For example, graph theoretic measures such
+as centrality and degree~\citep{BullSpor09} may be used to estimate
+how a given brain structure is ``communicating'' with other
+structures, independently of the specific neural representations
+carried by those structures.  If one considers a brain region's graph
+theoretic position in the network (e.g., its eigenvector centrality)
+as a dynamic property, one can compare how the positions of different
+regions are correlated, and/or how those patterns of correlations change
+over time.  We can also compute higher-order patterns in these
+correlations to characterize homologous subgraphs in the connectome
+that display similar changes in their constituent brain structures'
+interactions with the rest of the brain.
 
-Following this line of reasoning, we expect higher-order network
-dynamics might provide even richer insights into the neural basis of
-cognition. We sought to test this hypothesis by developing an approach
-to inferring high-order network dynamics from timeseries data,
-validating the approach using synthetic data, and then applying the approach to
-a neuroimaging dataset comprising data collected as participants
-listened to a story varying in cognitive richness~\citep{SimoEtal16}.
+To gain insights into the above aspects of the neural code, we
+developed a computational framework for estimating dynamic high-order
+correlations in timeseries data. This framework provides an important
+advance, in that it enables us to examine patterns in higher-order
+correlations that are computationally intractable to estimate via
+conventional methods.  Given a multivariate timeseries, our framework
+provides timepoint-by-timepoint estimates of the first-order
+correlations, second-order correlations, and so on (up to tenth-order
+correlations in this manuscript).  Our approach combines a
+kernel-based method for computing dynamic correlations in timeseries
+data with a dimensionality reduction step that projects the resulting
+dynamic correlations into a low-dimensional space.  We explored two
+dimensionality reduction approaches: principle components
+analysis~\citep[PCA;][]{Pear01}, which preserves an approximately invertable
+transformation back to the original data; and a second non-invertible
+algorithm that explored patterns in eigenvector
+centrality~\citep{Land95}.  This latter approach characterizes
+correlations between each feature dimension's relative
+\textit{position} in the network in favor of the specific activity
+histories of different features.
+
+We validated our approach using synthetic data where the underlying
+correlations were known.  We then applied our framework to a
+neuroimaging dataset collected as 125 participants listened to either
+an audio recording of a ten-minute story or a temporally scrambled
+version of the story, or underwent a resting state
+scan~\citep{SimoEtal16}.  We used a subset of the data to train
+across-participant classifiers to decode listening times using a blend
+of neural features (comprising neural activity patterns, as well as
+different orders of correlations between those patterns that were
+inferred using our computational framework).  We found that both the
+PCA-based and eigenvector centrality-based approaches yielded neural
+patterns that could be used to decode accurately.  Both approaches
+also yielded the best decoding accuracy for data collected during
+(intact) story listening when high-order (PCA:
+second-order; eigenvector centrality: fourth-order) dynamic
+correlation patterns were included as features.  When we trained
+classifiers on the scambled stories or resting state data, only
+lower-order dynamic patterns were informative to the decoders.  Taken
+together, our results indicate that high-level cognition is supported
+by high-order dynamic patterns of communication between brain
+structures.  \textbf{JRM STOPPED HERE}
 

### 2019-08-19 paper/main.tex
update figure with new ordered up to correlations (up to 15)

@@
   \caption{\textbf{Average correlations by order for the intact listening condition.} Using eigenvector
-    centrality to approximate higher-order correlations for \textbf{a.-d. intact, e.-h. paragraph scrambled,
-      i.-l. word scrambled, and m.-p. rest } conditions, we plot the
-    strongest 25\% absolute value
-    mean correlation for first through fourth orders, representing the degree of agreement by
-    location pair over time.}
+    centrality to approximate higher-order correlations for the
+    intact, paragraph scrambled, word scrambled, and rest condition.
+    We plot the
+    strongest 50\% absolute value
+    mean correlation for \textbf{a.-d. first order, e.-h. second order,
+      i.-l. third order, and m.-p. fourth order }, representing the degree of agreement by
+    location pair over time.  To demonstrate how this method is
+    computationally scalable, we also approximated
+    \textbf{a.-d. fifteenth order} dynamic correlation, which would be
+    possible to compute using conventional methods since it would require more bits to represent the solution than there are molecules in the universe.}
   \label{fig:brain_plots}

### 2019-08-21 paper/main.tex

@@
 by high-order dynamic patterns of communication between brain
-structures.  \textbf{JRM STOPPED HERE}
+structures.
 
 \section*{Methods}
+Our general approach to comprises four general steps.  First, we
+derive a kernel-based approach to computing dynamic pairwise
+correlations in a multivariate timeseries.  Next, we apply a
+dimensionality reduction step to \textbf{JRM STOPPED HERE}
+
 A major challenge to studying such patterns is that typically neither

### 2019-08-23 paper/main.tex
working on methods

@@
 derive a kernel-based approach to computing dynamic pairwise
-correlations in a multivariate timeseries.  Next, we apply a
-dimensionality reduction step to \textbf{JRM STOPPED HERE}
+correlations in a $T$ (timepoints) by $K$ (features) multivariate
+timeseries, $x_0$.  This yields a $T$ by $\mathcal{O}(K^2)$ matrix of
+dynamic correlations, $y_1$, where each row comprises the upper
+triangle of the correlation matrix at a single timepoint, reshaped
+into a row vector.  Second, we apply a dimensionality reduction step
+to project the matrix of dynamic correlations back onto a
+$K$-dimensional space.  This yields a $T$ by $K$ matrix, $x_1$, that
+reflects an approximation of the dynamic correlations reflected in the
+original data.  Third, we use repeated applications of the
+kernel-based dynamic correlation step to $x_n$ and the dimensionality
+reduction step to the resulting $y_{n+1}$ to estimate high-order
+dynamnic correlations.  Each application of these steps to a $T$ by
+$K$ time series $x_n$ yields a $T$ by $K$ matrix, $x_{n+1}$, that
+reflects the dynamic correlations between the columns of $x_n$.  In
+this way, we refer to $n$ as the \textit{order} of the timeseries,
+where $x_0$ (order 0) denotes the original data and $x_n$ denotes
+$n^\mathrm{th}$-order dynamic correlations between the columns of
+$x_0$.  Finally, we use a cross-validation--based decoding approach to
+evaluate how well information contained in a given order (or weighted
+mixture of orders) may be used to decode relevant cognitive states.
+If including a given $x_n$ in the feature set yields higher
+classification accuracy on held-out data, we interpret this as
+evidence that the given cognitive states are reflected in patterns of
+$n^\mathrm{th}$-order correlations.
+
+\textbf{JRM STOPPED HERE}
 

### 2019-08-23 paper/boneyard.tex
working on methods-- dynamic correlations

@@
+A major challenge to studying such patterns is that typically neither
+the correlations nor the hierarchical organizations of those
+correlations may be directly observed.  Rather, these fundamental
+properties must be inferred indirectly by examining the observable
+parts of the system-- e.g., the behaviors of the individual units of
+that system.  Here we propose a series of mathematical operations that may be used to approximate dynamic correlations at a range of scales (i.e., orders of interaction).
+
+There are two basic steps to our approach (Fig.~\ref{fig:methods_fig}).  In the first step, we take
+a number-of-timepoints ($T$) by number-of-features ($F$)
+\textit{matrix of observations} ($\mathbf{X}$) and we return a $T$ by
+$\frac{F^2 - F}{2}$ \textit{matrix of dynamic correlations}
+($\mathbf{Y}$).  Here $\mathbf{Y_0}$ describes, at each moment, how
+all of the features (columns of $\mathbf{X}$) are inferred to be
+interacting.  (Since the interactions are assumed to be non-recurrent
+and symmetric, only the upper triangle of the full correlation matrix
+is computed.)  In the second step, we project $\mathbf{Y_0}$ onto an
+$F$-dimensional space, resulting in a new $T$ by $F$ matrix
+$\mathbf{Y_1}$.  Note that $\mathbf{Y_1}$ contains information about
+the correlation dynamics present in $\mathbf{X}$, but represented in a
+compressed number of dimensions.  By repeatedly applying these two
+steps in sequence, we can examine and explore higher order dynamic
+correlations in $\mathbf{X}$.
+
 To understand the neuronal computations that support cognition, we

### 2019-08-23 paper/main.tex
working on methods-- dynamic correlations

--- 2019-08-19 paper/main.tex
@@
 by high-order dynamic patterns of communication between brain
-structures.  \textbf{JRM STOPPED HERE}
+structures.
 
 \section*{Methods}
-A major challenge to studying such patterns is that typically neither
-the correlations nor the hierarchical organizations of those
-correlations may be directly observed.  Rather, these fundamental
-properties must be inferred indirectly by examining the observable
-parts of the system-- e.g., the behaviors of the individual units of
-that system.  Here we propose a series of mathematical operations that may be used to approximate dynamic correlations at a range of scales (i.e., orders of interaction).
+Our general approach to comprises four general steps.  First, we
+derive a kernel-based approach to computing dynamic pairwise
+correlations in a $T$ (timepoints) by $K$ (features) multivariate
+timeseries, $\mathbf{X}_0$.  This yields a $T$ by $\mathcal{O}(K^2)$ matrix of
+dynamic correlations, $\mathbf{Y}_1$, where each row comprises the upper
+triangle of the correlation matrix at a single timepoint, reshaped
+into a row vector.  Second, we apply a dimensionality reduction step
+to project the matrix of dynamic correlations back onto a
+$K$-dimensional space.  This yields a $T$ by $K$ matrix, $\mathbf{X}_1$, that
+reflects an approximation of the dynamic correlations reflected in the
+original data.  Third, we use repeated applications of the
+kernel-based dynamic correlation step to $\mathbf{X}_n$ and the dimensionality
+reduction step to the resulting $\mathbf{Y}_{n+1}$ to estimate high-order
+dynamnic correlations.  Each application of these steps to a $T$ by
+$K$ time series $\mathbf{X}_n$ yields a $T$ by $K$ matrix, $\mathbf{X}_{n+1}$, that
+reflects the dynamic correlations between the columns of $\mathbf{X}_n$.  In
+this way, we refer to $n$ as the \textit{order} of the timeseries,
+where $\mathbf{X}_0$ (order 0) denotes the original data and $\mathbf{X}_n$ denotes
+$n^\mathrm{th}$-order dynamic correlations between the columns of
+$\mathbf{X}_0$.  Finally, we use a cross-validation--based decoding approach to
+evaluate how well information contained in a given order (or weighted
+mixture of orders) may be used to decode relevant cognitive states.
+If including a given $\mathbf{X}_n$ in the feature set yields higher
+classification accuracy on held-out data, we interpret this as
+evidence that the given cognitive states are reflected in patterns of
+$n^\mathrm{th}$-order correlations.
 
-There are two basic steps to our approach (Fig.~\ref{fig:methods_fig}).  In the first step, we take
-a number-of-timepoints ($T$) by number-of-features ($F$)
-\textit{matrix of observations} ($\mathbf{X}$) and we return a $T$ by
-$\frac{F^2 - F}{2}$ \textit{matrix of dynamic correlations}
-($\mathbf{Y}$).  Here $\mathbf{Y_0}$ describes, at each moment, how
-all of the features (columns of $\mathbf{X}$) are inferred to be
-interacting.  (Since the interactions are assumed to be non-recurrent
-and symmetric, only the upper triangle of the full correlation matrix
-is computed.)  In the second step, we project $\mathbf{Y_0}$ onto an
-$F$-dimensional space, resulting in a new $T$ by $F$ matrix
-$\mathbf{Y_1}$.  Note that $\mathbf{Y_1}$ contains information about
-the correlation dynamics present in $\mathbf{X}$, but represented in a
-compressed number of dimensions.  By repeatedly applying these two
-steps in sequence, we can examine and explore higher order dynamic
-correlations in $\mathbf{X}$.
-
-\subsection*{Dynamic correlations}
+\subsection*{Kernel-based approach for computing dynamic correlations}
 Given a matrix of observations, we can compute the (static)
-correlations between any pair of observations, $\mathbf{X}_i$ and
-$\mathbf{X}_j$ using:
+correlations between any pair of columns, $\mathbf{X}(\cdot, i)$ and
+$\mathbf{X}(\cdot, j)$ using:
 \begin{align}
-  \mathrm{corr}(\mathbf{X}_i, \mathbf{X}_j) &= \frac{\sum_{t=1}^T \left(\mathbf{X}_i(t)
+  \mathrm{corr}(\mathbf{X}(\cdot, i), \mathbf{X}(\cdot, j)) &=
+                                                              \frac{\sum_{t=1}^T
+                                                              \left(\mathbf{X}(t,
+                                                              i)
                                                               -
-                                              \bar{\mathbf{X}_i}\right) \left(\mathbf{X}_j(t)
+                                                              \bar{\mathbf{X}(\cdot,
+                                                              i)}\right)
+                                                              \left(\mathbf{X}(t,
+                                                              j)
                                                               -
-                                              \bar{\mathbf{X}_j}\right)}{\sqrt{\sum_{t=1}^T
-                                              \sigma^2_{\mathbf{X}_i} 
-                                              \sigma^2_{\mathbf{X}_j}}},~\mathrm{where}\\\label{eqn:corr}
-  \bar{\mathbf{X}_k} &= \sum_{t=1}^T
-                       \mathbf{X}_k(t),~\mathrm{and}\\
-  \sigma^2_{\mathbf{X}_k} &= \sum_{t=1}^T \left( \mathbf{X}_k -
-                            \bar{\mathbf{X}_k} \right)^2 
+                                                              \bar{\mathbf{X}(\cdot, j)}\right)}{\sqrt{\sum_{t=1}^T
+                                                              \sigma^2_{\mathbf{X}(\cdot, i)} 
+                                                              \sigma^2_{\mathbf{X}(\cdot, j)}}},~\mathrm{where}\\\label{eqn:corr}
+  \bar{\mathbf{X}(\cdot, k)} &= \sum_{t=1}^T
+                       \mathbf{X}(t, k),~\mathrm{and}\\
+  \sigma^2_{\mathbf{X}(\cdot, k)} &= \sum_{t=1}^T \left( \mathbf{X}(t, k) -
+                            \bar{\mathbf{X}(\cdot, k)} \right)^2 
 \end{align}
 
+\textbf{JRM STOPPED HERE}
 We can generalize this formula to compute time-varying correlations by

### 2019-08-23 paper/main.tex
working on methods section-- low-dimensional representations of dynanmic correlations

@@
 Given a matrix of observations, we can compute the (static)
-correlations between any pair of columns, $\mathbf{X}(\cdot, i)$ and
-$\mathbf{X}(\cdot, j)$ using:
+Pearson's correlation between any pair of columns, $\mathbf{X}(\cdot, i)$ and
+$\mathbf{X}(\cdot, j)$ using~\citep{Pear01}:
 \begin{align}
@@
 \end{align}
-
-\textbf{JRM STOPPED HERE}
 We can generalize this formula to compute time-varying correlations by
-incorporating a \textit{weight function} that takes a time $t$ as input,
-and returns how much the observed data every timepoint (including $t$)
-contribute to the correlations at time $t$ (Fig.~\ref{fig:weights}).
+incorporating a \textit{kernel function} that takes a time $t$ as
+input, and returns how much the observed data at each timepoint
+$\tau \in \left[ -\infty, \infty \right]$ contributes to the estimated instantaneous
+correlation at time $t$ (Fig.~\ref{fig:kernels}).
 \begin{figure}
@@
   \includegraphics[width=\textwidth]{figs/kernels}
-  \caption{\textbf{Examples of time-varying weights.  Each panel
+  \caption{\textbf{Examples of kernel functions.} Each panel
     displays per-timepoint weights at $t = 50$, evaluated for 100
-      timepoints ($1, ..., 100$).  a. Uniform weights.} The weights
-    are timepoint-invariant; observations at all timepoints are
-    weighted equally, and do not change as a function of $t$.  This is
-    a special case of weight function that reduces dynamic
-    correlations to static correlations.  \textbf{b. Dirac delta
-      function.} Only the observation at timepoint $t$ is given weight
-    (of 1), and weights for observations at all other timepoints are
-    set to 0.  \textbf{c. Gaussian weights.} Each observation's
-    weights fall off in time according to a Gaussian probability
-    density function centered on $\mu = t$.  Weights derived using
-    several different example variance parameters ($\sigma^2$ are
-    displayed.  \textbf{d. Laplace weights.}  Each observation's
-    weights fall off in time according to a Laplace probability
-    density function centered on $\mu = t$.  Weights derived using
-    several different example scale parameters ($b$) are displayed.
-    \textbf{e. Mexican hat (Ricker wavelet) weights.}  Each
-    observation's weights fall off in time according to a Ricker
-    wavelet centered on $t$.  This function highlights the
-    \textit{contrasts} between local versus surrounding activity
-    patterns in estimating dynamic correlations. Weights derived using
-    several different example width parameters ($\sigma$) are
-    displayed.  }
-  \label{fig:weights}
+    timepoints ($\tau \in \left[1, ..., 100\right]$).  \textbf{a. Uniform
+      kernel.} The weights are timepoint-invariant; observations at
+    all timepoints are weighted equally, and do not change as a
+    function of $\tau$.  This is a special case of weight function that
+    reduces dynamic correlations to static correlations.
+    \textbf{b. Dirac $\delta$ kernel.} Only the observation at
+    timepoint $t$ is given a non-zero weight (of 1).
+    \textbf{c. Gaussian kernels.} Each kernel's weights fall off
+    in time according to a Gaussian probability density function
+    centered on time $t$.  Weights derived using several different
+    example variance parameters ($\sigma^2$ are displayed.
+    \textbf{d. Laplace kernels.}  Each kernel's weights fall off
+    in time according to a Laplace probability density function
+    centered on time $t$.  Weights derived using several different
+    example scale parameters ($b$) are displayed.  \textbf{e. Mexican
+      hat (Ricker wavelet) kernels.}  Each kernel's weights fall
+    off in time according to a Ricker wavelet centered on time $t$.  This
+    function highlights the \textit{contrasts} between local versus
+    surrounding activity patterns in estimating dynamic
+    correlations. Weights derived using several different example
+    width parameters ($\sigma$) are displayed.}
+  \label{fig:kernels}
 \end{figure}
 
-Given a weight function $w(t)$ for timepoint $t$, evaluated at
-timepoints in the interval $\left[ 1, ..., T \right]$, we can extend the static correlation formula
-in Equation~\ref{eqn:corr} to reflect an \textit{instantaneous
-  correlation} at timepoint $t$:
+Given a kernel function $\kappa_t(\cdot)$ for timepoint $t$,
+evaluated at timepoints $\tau \in \left[ 1, ..., T \right]$, we
+can update the static correlation formula in Equation~\ref{eqn:corr}
+to estimate the \textit{instantaneous correlation} at timepoint $t$:
 \begin{align}
-  \mathrm{timecorr}(\mathbf{X}_i, \mathbf{X}_j, t) &= \frac{\sum_{t=1}^T \left(\mathbf{X}_i(t)
-                                              -
-                                              \widetilde{\mathbf{X}}_i(t)\right) \left(\mathbf{X}_j(t)
-                                              -
-                                              \widetilde{\mathbf{X}}_j(t)\right)}{\sqrt{\sum_{t=1}^T
-                                              \widetilde{\sigma}^2_{\mathbf{X}_i}(t) 
-                                              \widetilde{\sigma}^2_{\mathbf{X}_j}}(t)},~\mathrm{where}\\\label{eqn:timecorr}
-  \widetilde{\mathbf{X}}_k(t) &= \sum_{i=1}^T
-                       w(t, i)\mathbf{X}_k(i),\\
-  \widetilde{\sigma}^2_{\mathbf{X}_k}(t) &= \sum_{i=1}^T \left( \mathbf{X}_k(i) -
-                            \widetilde{\mathbf{X}}_k(t) \right)^2,
+  \mathrm{timecorr}_{\kappa_t}\left(\mathbf{X}(\cdot, i), \mathbf{X}(\cdot, j)\right) &= \frac{\sum_{\tau=1}^T \left( \mathbf{X}(\tau, i) -
+                                       \widetilde{\mathbf{X}}_{\kappa_t}(i) \right)
+                                 \left( \mathbf{X}(\tau, j) -
+                                        \widetilde{\mathbf{X}}_{\kappa_t}(j)\right)}
+              {\sqrt{\sum_{\tau=1}^T
+                                              \widetilde{\sigma}_{\kappa_t}^2(\mathbf{X}(\cdot,
+                                                                                        i))
+                                              \widetilde{\sigma}_{\kappa_t}^2(\mathbf{X}(\cdot, j))}},~\mathrm{where}\\\label{eqn:timecorr}
+  \widetilde{\mathbf{X}}_{\kappa_t}(t, k) &= \sum_{\tau=1}^T
+                       \kappa_t(\tau, k)\mathbf{X}(\tau, k),\\
+  \widetilde{\sigma}_{\kappa_t}^2(\mathbf{X}(\cdot, k)) &= \sum_{\tau=1}^T
+                                                  \left(
+                                                  \mathbf{X}(\tau, k) -
+                            \widetilde{\mathbf{X}}_{\kappa_t}(t, k) \right)^2.
 \end{align}
-and $w(t, i)$ is shorthand for $w(t)$ evaluated at timepoint $i$.
-Equation~\ref{eqn:timecorr} may be used to estimate the instantaneous
-correlations between every pair of observations, at each timepoint
-(i.e., $\mathbf{Y}$).
+Here $\mathrm{timecorr}(\mathbf{X}(\cdot, i), \mathbf{X}(\cdot, j),
+  \kappa_t)$ reflects the correlation at time $t$ between columns $i$
+  and $j$ of $\mathbf{X}$, estimated using the kernel $\kappa_t$.
 
@@
 Equation~\ref{eqn:timecorr} provides a means of taking a single
-observation matrix, $\mathbf{X}$ and estimating the dynamic
-correlations from moment to moment, $\mathbf{Y}$.  Suppose that one
-has access to a set of multiple observation matrices that reflect the
-same phenomenon.  For example, one might collect neuroimaging data
+observation matrix, $\mathbf{X}_n$ and estimating the dynamic
+correlations from moment to moment, $\mathbf{Y}_{n+1}$.  Suppose that
+one has access to a set of multiple observation matrices that reflect
+the same phenomenon.  For example, one might collect neuroimaging data
 from several experimental participants, as each participant performs
-the same task (or sequence of tasks).  Let $\mathbf{X}_1$,
-$\mathbf{X}_2$, ..., $\mathbf{X}_P$ reflect the $T$ by $F$ observation
-matrices for each of $P$ participants in an experiment.  We can use
+the same task (or sequence of tasks).  Let $\mathbf{X}_n^1$,
+$\mathbf{X}_n^2$, ..., $\mathbf{X}_n^P$ reflect the $T$ by $K$
+observation matrices ($n = 0$) or reduced correlation matrices
+($n > 0$) for each of $P$ participants in an experiment.  We can use
 \textit{inter-subject functional connectivity}~\citep[ISFC;
@@
 \begin{align}
-\bar{\mathbf{C}}(t) = M\left(R\left(\frac{1}{2P} \sum_{i=1}^P
-  Z\left(Y_i(t)\right)^\mathrm{T} + Z\left(Y_i,(t)\right)\right)\right),
+\bar{\mathbf{C}}(t) = M\left(R\left(\frac{1}{2P} \sum_{p=1}^P
+  Z\left(Y_n^p(t)\right)^\mathrm{T} + Z\left(Y_n^p(t)\right)\right)\right),
 \end{align}
@@
 \end{align}
-and $\mathbf{Y}_i(t)$ denotes the correlation matrix
-(Eqn.~\ref{eqn:corr}) between each column of $\mathbf{X}_i$ and each
-column of the average observations from all \textit{other}
-participants, $\bar{\mathbf{X}}_{ \backslash i}$:
+and $\mathbf{Y}_n^p(t)$ denotes the correlation matrix
+(Eqn.~\ref{eqn:corr}) between each column of $\mathbf{X}_n^p$ and each
+column of the average $\mathbf{X}_n$ from all \textit{other}
+participants, $\bar{\mathbf{X}}_n^{ \backslash p}$:
 \begin{align}
-  \bar{\mathbf{X}}_{ \backslash i} = R\left(\frac{1}{P-1}\sum_{i \in
-  \backslash i} Z\left( \mathbf{X}_i \right) \right),
+  \bar{\mathbf{X}}_n^{ \backslash p} = R\left(\frac{1}{P-1}\sum_{q \in
+  \backslash p} Z\left( \mathbf{X}_n^q \right) \right),
 \end{align}
-where $ \backslash i$ denotes the set of all participants other than
-participant $i$. In this way, the $T$ by $\left( \frac{F^2 - F}{2}
-  + F \right)$
-matrix $\bar{\mathbf{C}}$ is the time-varying extension of the ISFC
+where $\backslash p$ denotes the set of all participants other than
+participant $p$. In this way, the $T$ by $\mathcal{O}(K^2)$
+matrix $\bar{\mathbf{C}}$ provides a time-varying extension of the ISFC
 approach developed by \cite{SimoEtal16}.
 
-\subsection*{Higher-order correlations}
-Given a timeseries of dynamic correlations (e.g., obtained using
-Eqn.~\ref{eqn:timecorr}), higher-order correlations reflect the
-dynamic correlations between columns of $\mathbf{Y}$.  Given unlimited
-computing resources, one could use repeated applications of
-Equation~\ref{eqn:timecorr} to estimate these higher-order
-correlations (i.e., substituting in the previous output, $\mathbf{Y}$,
-for the input, $\mathbf{X}$ in the equation).  However, because each
-output $\mathbf{Y}$ has $\mathcal{O}(F^2)$ columns relative to $F$ columns in
-the input $\mathbf{X}$, the output of Equation~\ref{eqn:timecorr}
-grows with the square of the number of repeated applications (total
-cost of computing $n$\textsuperscript{th} order correlations is
-$\mathcal{O}(F^{2n})$ for $n \in \mathcal{J}, n > 0$).  When $F$ or $n$ is large,
-this approach quickly becomes intractable.
+\subsection*{Low-dimensional representations of dynamic
+  correlations}
 
-To make progress in computing $\mathbf{Y_{n+1}}$, we can approximate
-$\mathbf{Y}_n$ by computing an $\mathcal{O}(F)$-dimensional embedding of
-$\mathbf{Y}_n$, termed $\hat{\mathbf{Y}}_n$, and then we can apply
-Equation~\ref{eqn:timecorr} to $\hat{\mathbf{Y}}_n$ rather than
-directly to $\mathbf{Y}_n$.  This enables us to maintain $\mathcal{O}(n)$
-scaling with respect to $n$, rather than exponential scaling via the
-direct approach.
-
-\begin{figure}
-  \centering
-  \includegraphics[width=0.5\textwidth]{figs/methods_fig}
-  \caption{\textbf{Computing higher order correlations. } Dynamic
-    correlations
-  are computed then approximated to the same size as original data
-  using dimensionality reduction.
-  This process is repeated, and can be used to compute up to any
-  arbitrary order with compuations scaling linearly (as opposed to exponentially) with order. }
-  \label{fig:methods_fig}
-\end{figure}
-
-There are many possible methods for computing $\hat{\mathbf{Y}}_n$
-from $\mathbf{Y}_n$, including traditional dimensionality reduction
-approaches and graph theory based approaches as described next.  In the
-\textit{Discussion} section we elaborate on other potential approaches.
+Given a $T$ by $\mathcal{O}(K^2)$ matrix of dynamic correlations,
+$\mathbf{Y}_n$, we propose two general approaches to computing a $T$ by $K$
+low-dimensional representation of these correlations, $\mathbf{X}_n$.
+The first approach uses dimensionality reduction algorithms to project
+$\mathbf{Y}_n$ onto a $K$-dimensional space.  The second approach uses
+graph-theoretic measures to characterize the relative positions of
+each feature ($k \in \left[1, ..., K \right]$) in the network defined
+by the correlation matrix at each timepoint. \textbf{JRM STOPPED HERE}
 
 \subsubsection*{Dimensionality reduction-based approaches to computing
-  $\hat{\mathbf{Y}}_n$}
+  $\mathbf{X}_n$}
 
@@
 
-\subsubsection*{Graph theory-based approaches to computing
-  $\hat{\mathbf{Y}}_n$}
+\subsubsection*{Graph theoretic approaches to computing
+  $\mathbf{X}_n$}
 
@@
 
+\subsection*{Higher-order correlations}
+Given a timeseries of dynamic correlations (e.g., obtained using
+Eqn.~\ref{eqn:timecorr}), higher-order correlations reflect the
+dynamic correlations between columns of $\mathbf{Y}$.  Given unlimited
+computing resources, one could use repeated applications of
+Equation~\ref{eqn:timecorr} to estimate these higher-order
+correlations (i.e., substituting in the previous output, $\mathbf{Y}$,
+for the input, $\mathbf{X}$ in the equation).  However, because each
+output $\mathbf{Y}$ has $\mathcal{O}(F^2)$ columns relative to $F$ columns in
+the input $\mathbf{X}$, the output of Equation~\ref{eqn:timecorr}
+grows with the square of the number of repeated applications (total
+cost of computing $n$\textsuperscript{th} order correlations is
+$\mathcal{O}(F^{2n})$ for $n \in \mathcal{J}, n > 0$).  When $F$ or $n$ is large,
+this approach quickly becomes intractable.
+
+To make progress in computing $\mathbf{Y_{n+1}}$, we can approximate
+$\mathbf{Y}_n$ by computing an $\mathcal{O}(F)$-dimensional embedding of
+$\mathbf{Y}_n$, termed $\hat{\mathbf{Y}}_n$, and then we can apply
+Equation~\ref{eqn:timecorr} to $\hat{\mathbf{Y}}_n$ rather than
+directly to $\mathbf{Y}_n$.  This enables us to maintain $\mathcal{O}(n)$
+scaling with respect to $n$, rather than exponential scaling via the
+direct approach.
+
+\begin{figure}
+  \centering
+  \includegraphics[width=0.5\textwidth]{figs/methods_fig}
+  \caption{\textbf{Computing higher order correlations. } Dynamic
+    correlations
+  are computed then approximated to the same size as original data
+  using dimensionality reduction.
+  This process is repeated, and can be used to compute up to any
+  arbitrary order with compuations scaling linearly (as opposed to exponentially) with order. }
+  \label{fig:methods_fig}
+\end{figure}
+
+There are many possible methods for computing $\hat{\mathbf{Y}}_n$
+from $\mathbf{Y}_n$, including traditional dimensionality reduction
+approaches and graph theory based approaches as described next.  In the
+\textit{Discussion} section we elaborate on other potential approaches.
+
 \subsection*{Evaluation metrics}
@@
 different properties, and using different kernels to define the
-weights; Fig.~\ref{fig:weights}).  We then turned to a series of
+weights; Fig.~\ref{fig:kernels}).  We then turned to a series of
 analyses on a (real) neuroimaging dataset where the ground truth
@@
 We applied timecorr, using delta and gaussian (width = 10) kernels
-Fig.~\ref{fig:weights}) to each of these 
+Fig.~\ref{fig:kernels}) to each of these 
 synthetic datasets, then correlated each recovered
@@
 data. We applied timecorr, using delta and gaussian kernels
-Fig.~\ref{fig:weights}) to each of the following  
+Fig.~\ref{fig:kernels}) to each of the following  
 synthetic datasets: constant, random, ramping, and block.  We then correlated each recovered

### 2019-08-24 paper/main.tex
working on dimensionality reduction section of methods

@@
 triangle of the correlation matrix at a single timepoint, reshaped
-into a row vector.  Second, we apply a dimensionality reduction step
+into a row vector (this reshaped vector is $(\frac{K^2 - K}{2})$-dimensional).  Second, we apply a dimensionality reduction step
 to project the matrix of dynamic correlations back onto a
@@
 
-\subsubsection*{Inter-subject dynamic correlations}
+\subsubsection*{Dynamic inter-subject functional connectivity (DISFC)}
 Equation~\ref{eqn:timecorr} provides a means of taking a single
@@
 where $\backslash p$ denotes the set of all participants other than
-participant $p$. In this way, the $T$ by $\mathcal{O}(K^2)$
+participant $p$. In this way, the $T$ by $\frac{K^2 - K}{2}$ DISFC
 matrix $\bar{\mathbf{C}}$ provides a time-varying extension of the ISFC
@@
 
-Given a $T$ by $\mathcal{O}(K^2)$ matrix of dynamic correlations,
-$\mathbf{Y}_n$, we propose two general approaches to computing a $T$ by $K$
-low-dimensional representation of these correlations, $\mathbf{X}_n$.
-The first approach uses dimensionality reduction algorithms to project
-$\mathbf{Y}_n$ onto a $K$-dimensional space.  The second approach uses
-graph-theoretic measures to characterize the relative positions of
-each feature ($k \in \left[1, ..., K \right]$) in the network defined
-by the correlation matrix at each timepoint. \textbf{JRM STOPPED HERE}
+Given a $T$ by $\frac{K^2 - K}{2}$ matrix of dynamic correlations,
+$\mathbf{Y}_n$, we propose two general approaches to computing a $T$
+by $K$ low-dimensional representation of these correlations,
+$\mathbf{X}_n$.  The first approach uses dimensionality reduction
+algorithms to project $\mathbf{Y}_n$ onto a $K$-dimensional space.
+The second approach uses graph-theoretic measures to characterize the
+relative positions of each feature ($k \in \left[1, ..., K \right]$)
+in the network defined by the correlation matrix at each timepoint.
+
+Because $\mathbf{X}_n$ will have the same shape as the original data
+$\mathbf{X}_0$, approximating $\mathbf{Y}_n$ with a lower-dimensional
+$\mathbf{X}_n$ enables us to estimate high-order dynamic correlations
+in a scalable way.  Given a $T$ by $K$ input matrix, the output of
+Equation~\ref{eqn:timecorr} requires $\mathcal{O}(TK^2)$ space to
+store.  Repeated applications of Equation~\ref{eqn:timecorr} (i.e.,
+computing dynamic correlations between the columns of the outputted
+dynamic correlation matrix) each require exponentially more space; in
+general the $n^\mathrm{th}$-order dynamic correlations of a $T$ by $K$
+timeseries occupies $\mathcal{O}(TK^{2n})$ space.  However, when we
+approximate the output of Equation~\ref{eqn:timecorr} with a $T$ by
+$K$ matrix (as described next), it becomes feasible to compute even
+very high-order correlations in high-dimensional data.  Specifically,
+approximating the $n^\mathrm{th}$-order dynamic correlations of a $T$
+by $K$ timeseries requires only $\mathcal{O}(TK^2)$ space-- the same
+as would be required to compute first-order dynamic
+correlations. \textbf{JRM STOPPED HERE}
 

### 2019-08-28 code/scripts/animate_largest.py
plot most positive and negative correlation locations with visbrain

@@ -1,0 +1,80 @@
+import supereeg as se
+import numpy as np
+import os
+from visbrain.objects import BrainObj, SceneObj, SourceObj
+
+cmap = 'autumn_r'
+
+neurosynth_dir ='../figs/neurosynth_data'
+
+bo_dir = os.path.join(neurosynth_dir, 'bos')
+
+n_f_dir = os.path.join(neurosynth_dir, 'figs')
+if not os.path.exists(n_f_dir):
+    os.mkdir(n_f_dir)
+
+b1 = se.load(os.path.join(bo_dir, 'intact_1_largest.bo'))
+b2 = se.load(os.path.join(bo_dir, 'intact_2_largest.bo'))
+b3 = se.load(os.path.join(bo_dir, 'intact_3_largest.bo'))
+b4 = se.load(os.path.join(bo_dir, 'intact_4_largest.bo'))
+
+data1 = b1.get_data().values.ravel()
+xyz1 = b1.locs.values
+xyz1 = xyz1[data1>.9999]
+data1 = data1[data1>.9999]
+data1 = np.ones(data1.shape)
+
+
+data2 = b2.get_data().values.ravel()
+xyz2 = b2.locs.values
+xyz2 = xyz2[data2>.9999]
+data2 = data2[data2>.9999]
+data2 = np.ones(data2.shape)+1
+
+data3 = b3.get_data().values.ravel()
+xyz3 = b3.locs.values
+xyz3 = xyz3[data3>.9999]
+data3 = data3[data3>.9999]
+data3 = np.ones(data3.shape)+2
+
+data4 = b4.get_data().values.ravel()
+xyz4 = b4.locs.values
+xyz4 = xyz4[data4>.9999]
+data4 = data4[data4>.9999]
+data4 = np.ones(data4.shape)+3
+
+template_brain = 'B3'
+
+sc = SceneObj(bgcolor='white', size=(500, 500))
+
+CBAR_STATE = dict(cbtxtsz=12, clim=[0, 6], txtsz=10., width=.1, cbtxtsh=3.,
+                  rect=(-.3, -2., 1., 4.))
+KW = dict(title_size=14., zoom=1)
+
+s_obj_1 = SourceObj('iEEG', xyz1, data=data1, cmap=cmap)
+s_obj_1.color_sources(data=data1)
+s_obj_2 = SourceObj('iEEG', xyz2, data=data2, cmap=cmap)
+s_obj_2.color_sources(data=data2)
[…]

### 2019-08-28 code/scripts/plot_largest.py

@@ -1,0 +1,75 @@
+
+import supereeg as se
+import os
+from visbrain.objects import BrainObj, SceneObj, SourceObj
+
+cmap = 'autumn_r'
+
+neurosynth_dir ='../figs/neurosynth_data'
+
+bo_dir = os.path.join(neurosynth_dir, 'bos')
+
+n_f_dir = os.path.join(neurosynth_dir, 'figs')
+if not os.path.exists(n_f_dir):
+    os.mkdir(n_f_dir)
+
+conditions = ['intact', 'paragraph', 'rest', 'word']
+
+for c in conditions:
+
+
+    b1 = se.load(os.path.join(bo_dir,f'{c}_1_largest.bo'))
+    b2 = se.load(os.path.join(bo_dir,f'{c}_2_largest.bo'))
+    b3 = se.load(os.path.join(bo_dir,f'{c}_3_largest.bo'))
+    b4 = se.load(os.path.join(bo_dir,f'{c}_4_largest.bo'))
+
+    data1 = b1.get_data().values.ravel()
+    xyz1 = b1.locs.values
+
+    data2 = b2.get_data().values.ravel()
+    xyz2 = b2.locs.values
+
+    data3 = b3.get_data().values.ravel()
+    xyz3 = b3.locs.values
+
+    data4 = b4.get_data().values.ravel()
+    xyz4 = b4.locs.values
+
+
+    template_brain = 'B3'
+
+    sc = SceneObj(bgcolor='white', size=(1000, 1000))
+
+    CBAR_STATE = dict(cbtxtsz=12, clim=[0, 6], txtsz=10., width=.1, cbtxtsh=3.,
+                      rect=(-.3, -2., 1., 4.))
+    KW = dict(title_size=14., zoom=1)
+
+    s_obj_1 = SourceObj('iEEG', xyz1, data=data1, cmap=cmap)
+    s_obj_1.color_sources(data=data1)
+    s_obj_2 = SourceObj('iEEG', xyz2, data=data2, cmap=cmap)
+    s_obj_2.color_sources(data=data2)
+    s_obj_3 = SourceObj('iEEG', xyz3, data=data3, cmap=cmap)
+    s_obj_3.color_sources(data=data3)
+    s_obj_4 = SourceObj('iEEG', xyz4, data=data4, cmap=cmap)
+    s_obj_4.color_sources(data=data4)
+
+    s_obj_all = s_obj_1 + s_obj_2 + s_obj_3 + s_obj_4
+
[…]

### 2019-08-28 code/scripts/plot_smallest.py

@@ -1,0 +1,75 @@
+
+import supereeg as se
+import os
+from visbrain.objects import BrainObj, SceneObj, SourceObj
+
+cmap = 'winter_r'
+
+neurosynth_dir ='../figs/neurosynth_data'
+
+bo_dir = os.path.join(neurosynth_dir, 'bos')
+
+n_f_dir = os.path.join(neurosynth_dir, 'figs')
+if not os.path.exists(n_f_dir):
+    os.mkdir(n_f_dir)
+
+conditions = ['intact', 'paragraph', 'rest', 'word']
+
+for c in conditions:
+
+
+    b1 = se.load(os.path.join(bo_dir,f'{c}_1_smallest.bo'))
+    b2 = se.load(os.path.join(bo_dir,f'{c}_2_smallest.bo'))
+    b3 = se.load(os.path.join(bo_dir,f'{c}_3_smallest.bo'))
+    b4 = se.load(os.path.join(bo_dir,f'{c}_4_smallest.bo'))
+
+    data1 = b1.get_data().values.ravel()
+    xyz1 = b1.locs.values
+
+    data2 = b2.get_data().values.ravel()
+    xyz2 = b2.locs.values
+
+    data3 = b3.get_data().values.ravel()
+    xyz3 = b3.locs.values
+
+    data4 = b4.get_data().values.ravel()
+    xyz4 = b4.locs.values
+
+
+    template_brain = 'B3'
+
+    sc = SceneObj(bgcolor='white', size=(1000, 1000))
+
+    CBAR_STATE = dict(cbtxtsz=12, clim=[0, 6], txtsz=10., width=.1, cbtxtsh=3.,
+                      rect=(-.3, -2., 1., 4.))
+    KW = dict(title_size=14., zoom=1)
+
+    s_obj_1 = SourceObj('iEEG', xyz1, data=data1, cmap=cmap)
+    s_obj_1.color_sources(data=data1)
+    s_obj_2 = SourceObj('iEEG', xyz2, data=data2, cmap=cmap)
+    s_obj_2.color_sources(data=data2)
+    s_obj_3 = SourceObj('iEEG', xyz3, data=data3, cmap=cmap)
+    s_obj_3.color_sources(data=data3)
+    s_obj_4 = SourceObj('iEEG', xyz4, data=data4, cmap=cmap)
+    s_obj_4.color_sources(data=data4)
+
+    s_obj_all = s_obj_1 + s_obj_2 + s_obj_3 + s_obj_4
+
[…]

### 2019-08-29 paper/main.tex
wrote some notes in the methods and discussion sections

@@
 \section*{Methods}
-Our general approach to comprises four general steps.  First, we
-derive a kernel-based approach to computing dynamic pairwise
-correlations in a $T$ (timepoints) by $K$ (features) multivariate
-timeseries, $\mathbf{X}_0$.  This yields a $T$ by $\mathcal{O}(K^2)$ matrix of
-dynamic correlations, $\mathbf{Y}_1$, where each row comprises the upper
-triangle of the correlation matrix at a single timepoint, reshaped
-into a row vector (this reshaped vector is $(\frac{K^2 - K}{2})$-dimensional).  Second, we apply a dimensionality reduction step
-to project the matrix of dynamic correlations back onto a
-$K$-dimensional space.  This yields a $T$ by $K$ matrix, $\mathbf{X}_1$, that
-reflects an approximation of the dynamic correlations reflected in the
-original data.  Third, we use repeated applications of the
-kernel-based dynamic correlation step to $\mathbf{X}_n$ and the dimensionality
-reduction step to the resulting $\mathbf{Y}_{n+1}$ to estimate high-order
-dynamnic correlations.  Each application of these steps to a $T$ by
-$K$ time series $\mathbf{X}_n$ yields a $T$ by $K$ matrix, $\mathbf{X}_{n+1}$, that
-reflects the dynamic correlations between the columns of $\mathbf{X}_n$.  In
-this way, we refer to $n$ as the \textit{order} of the timeseries,
-where $\mathbf{X}_0$ (order 0) denotes the original data and $\mathbf{X}_n$ denotes
-$n^\mathrm{th}$-order dynamic correlations between the columns of
-$\mathbf{X}_0$.  Finally, we use a cross-validation--based decoding approach to
-evaluate how well information contained in a given order (or weighted
-mixture of orders) may be used to decode relevant cognitive states.
-If including a given $\mathbf{X}_n$ in the feature set yields higher
-classification accuracy on held-out data, we interpret this as
-evidence that the given cognitive states are reflected in patterns of
-$n^\mathrm{th}$-order correlations.
+Our general approach to comprises four general steps
+(Fig.~\ref{fig:methods}).  First, we derive a kernel-based approach to
+computing dynamic pairwise correlations in a $T$ (timepoints) by $K$
+(features) multivariate timeseries, $\mathbf{X}_0$.  This yields a $T$
+by $\mathcal{O}(K^2)$ matrix of dynamic correlations, $\mathbf{Y}_1$,
+where each row comprises the upper triangle of the correlation matrix
+at a single timepoint, reshaped into a row vector (this reshaped
+vector is $(\frac{K^2 - K}{2})$-dimensional).  Second, we apply a
+dimensionality reduction step to project the matrix of dynamic
+correlations back onto a $K$-dimensional space.  This yields a $T$ by
+$K$ matrix, $\mathbf{X}_1$, that reflects an approximation of the
+dynamic correlations reflected in the original data.  Third, we use
+repeated applications of the kernel-based dynamic correlation step to
+$\mathbf{X}_n$ and the dimensionality reduction step to the resulting
+$\mathbf{Y}_{n+1}$ to estimate high-order dynamnic correlations.  Each
+application of these steps to a $T$ by $K$ time series $\mathbf{X}_n$
+yields a $T$ by $K$ matrix, $\mathbf{X}_{n+1}$, that reflects the
+dynamic correlations between the columns of $\mathbf{X}_n$.  In this
+way, we refer to $n$ as the \textit{order} of the timeseries, where
+$\mathbf{X}_0$ (order 0) denotes the original data and $\mathbf{X}_n$
+denotes $n^\mathrm{th}$-order dynamic correlations between the columns
+of $\mathbf{X}_0$.  Finally, we use a cross-validation--based decoding
+approach to evaluate how well information contained in a given order
+(or weighted mixture of orders) may be used to decode relevant
+cognitive states.  If including a given $\mathbf{X}_n$ in the feature
+set yields higher classification accuracy on held-out data, we
+interpret this as evidence that the given cognitive states are
+reflected in patterns of $n^\mathrm{th}$-order correlations.
+
+\begin{figure}
+  \centering
+  \includegraphics[width=0.4\textwidth]{figs/methods_fig}
+  \caption{\textbf{Estimating dynamnic high-order correlations.}  Given
+    a $T$ by $K$ matrix of multivariate timeseries data,
+    $\mathbf{Y}_n$ (where $n \in \mathbb{N}, n \geq 0$), we use
+    Equation~\ref{eqn:timecorr} to compute a timeseries of
+    $K$ by $K$ correlation matrices, $\mathbf{Y}_{n+1}$.  We then
+    approximate $\mathbf{Y}_{n+1}$ with the $T$ by $K$ matrix
+    $\mathbf{X}_{n+1}$.  This process may be repeated to scalably estimate
+    iteratively higher-order correlations in the data.}
+  \label{fig:methods}
+\end{figure}
 
@@
 
-Because $\mathbf{X}_n$ will have the same shape as the original data
-$\mathbf{X}_0$, approximating $\mathbf{Y}_n$ with a lower-dimensional
-$\mathbf{X}_n$ enables us to estimate high-order dynamic correlations
-in a scalable way.  Given a $T$ by $K$ input matrix, the output of
-Equation~\ref{eqn:timecorr} requires $\mathcal{O}(TK^2)$ space to
-store.  Repeated applications of Equation~\ref{eqn:timecorr} (i.e.,
-computing dynamic correlations between the columns of the outputted
-dynamic correlation matrix) each require exponentially more space; in
-general the $n^\mathrm{th}$-order dynamic correlations of a $T$ by $K$
-timeseries occupies $\mathcal{O}(TK^{2n})$ space.  However, when we
-approximate the output of Equation~\ref{eqn:timecorr} with a $T$ by
-$K$ matrix (as described next), it becomes feasible to compute even
-very high-order correlations in high-dimensional data.  Specifically,
-approximating the $n^\mathrm{th}$-order dynamic correlations of a $T$
-by $K$ timeseries requires only $\mathcal{O}(TK^2)$ space-- the same
-as would be required to compute first-order dynamic
-correlations. \textbf{JRM STOPPED HERE}
-
 \subsubsection*{Dimensionality reduction-based approaches to computing
@@
 
-Commonly used dimensionality reduction algorithms include Principal
-Components Analysis~\citep[PCA; ][]{Pear01}, Probabilistic
+The modern library of dimensionality reduction algorithms include
+Principal Components Analysis~\citep[PCA; ][]{Pear01}, Probabilistic
 PCA~\citep[PPCA; ][]{TippBish99}, Exploratory Factor
@@
 characterizations of each of these algorithms is beyond the scope of
-the present manuscript, the general intuition driving these
-approaches is to compute the $\hat{\mathbf{Y}}$ with $i$ columns that
-is closest to the original $\mathbf{Y}$ with $j$ columns, and where
-(typically) $i \ll j$.  The different approaches place different
-constraints on what properties $\hat{\mathbf{Y}}$ must satisfy and
-which aspects of the data are compared (and how) to characterize the
-match between $\hat{\mathbf{Y}}$ and  $\mathbf{Y}$.
+the present manuscript, the general intuition driving these approaches
+is to compute the $T$ by $I$ matrix, $\mathbf{X}$, that is closest
+to the original $T$ by $J$ matrix, $\mathbf{Y}$, where (typically)
+$I \ll J$.  The different approaches place different constraints on
+what properties $\mathbf{X}$ must satisfy and which aspects of
+the data are compared (and how) to characterize the match between
+$\mathbf{X}$ and $\mathbf{Y}$.
 
 Applying dimensionality reduction algorithms to $\mathbf{Y}$ yields a
-$\hat{\mathbf{Y}}$ whose columns reflect weighted combinations (or
-nonlinear transformations) of the original columns of $\mathbf{Y}$.
-This has two main consequences.  First, with each repeated
-dimensionality reduction, the resulting $\hat{\mathbf{Y}}_n$ has lower
-and lower fidelity (with respect to what the ``true'' $\mathbf{Y}_n$
-might have looked like without using dimensionality reduction to
-maintain scalability).  In other words, computing $\hat{\mathbf{Y}}_n$
-is a lossy operation.  Second, whereas the columns of $\mathbf{Y}_n$
-may be mapped directly onto pairs of columns of $\mathbf{Y}_{n-1}$,
-that mapping either becomes less cleanly defined in
-$\hat{\mathbf{Y}}_n$ due to the reweightings and/or nonlinear
-transformations.
+$\mathbf{X}$ whose columns reflect weighted combinations (or nonlinear
+transformations) of the original columns of $\mathbf{Y}$.  This has
+two main consequences.  First, with each repeated dimensionality
+reduction, the resulting $\mathbf{X}_n$ has lower and lower fidelity
+(with respect to what the ``true'' $\mathbf{Y}_n$ might have looked
+like without using dimensionality reduction to maintain scalability).
+In other words, computing $\mathbf{X}_n$ is a lossy operation.
+Second, whereas each columns of $\mathbf{Y}_n$ may always be mapped
+directly onto specific pairs of columns of $\mathbf{Y}_{n-1}$, the
+columns of $\mathbf{X}_n$ reflect weighted combinations and/or
+nonlinear transformations of the columns of $\mathbf{Y}_n$.  Many
+dimensionality reduction algorithms are invertable (or approximately
+invertable).  However, attempting to map a given $\mathbf{X}_n$ back
+onto the original feature space of $\mathbf{Y}_0$ will usually require
+$\mathcal{O}(TK^{2n})$ space and therefore quickly becomes intractable
+as $n$ or $K$ grow large.
 
@@
   $\mathbf{X}_n$}
+The above dimensionality reduction approaches to approximating a given
+$\mathbf{Y}_n$ with a lower-dimensional $\mathbf{X}_n$ preserve a
+(potentially recombined and transformed) mapping back to the original
+data in $\mathbf{Y}_0$.  We also explore graph theoretic approaches
+that forgo a preserved mapping back to the original data in favor of
+preserving each feature's relative \textit{position} in the broader
+network of interactions and connections.  To illustrate the
+distinction between the two general approaches we explore, suppose a
+network comprises nodes $A$, $B$, and $C$.  If $A$ and $B$ exhibit
+uncorrelated activity patterns, the functional connection between
+them will be (by definition) close to 0.  However, if $A$ and $B$ each
+interact with $C$ in similar ways, we might attempt to capture those
+similarities using a measure that reflects the how $A$ and $B$
+interact in the network.
 
-Graph theoretic measures take as input a matrix of interactions (e.g.,
-using the above notation, an $F \times F$ correlation matrix or
-binarized correlation matrix reconstituded from a single timepoint's
-row of $\mathbf{Y}$) and return as output a set of $F$ measures
-describing how each node (feature) sits within that interactions
-matrix with respect to the rest of the population.  Common measures
-include betweeness centrality~\citep[the proportion of shortest paths
-between each pair of nodes in the population that involves the given
-node in question; e.g., ][]{Newm05, OpsaEtal10, Bart04, GeisEtal08,
-  Free77}; diversity and dissimilarity~\citep[characterizations of how
-differently connected a given node is from others in the population;
-e.g., ][]{Rao82, Lin09, RicoSzei06}; Eigenvector centrality and
-pagerank centrality~\citep[measures of how influential a given node is
-within the broader network; e.g., ][]{Newm08, Bona07, LohmEtal10,
+In general, graph theoretic measures take as input a matrix of
+interactions (e.g., using the above notation, an $K$ by $K$
+correlation matrix or binarized correlation matrix reconstituded from
+a single timepoint's row of $\mathbf{Y}$) and return as output a set
+of $K$ measures describing how each node (feature) sits within that
+correlation matrix with respect to the rest of the population.  Widely
+used measures include betweeness centrality~\citep[the proportion of
+shortest paths between each pair of nodes in the population that
+involves the given node in question; e.g., ][]{Newm05, OpsaEtal10,
+  Bart04, GeisEtal08, Free77}; diversity and
+dissimilarity~\citep[characterizations of how differently connected a
+given node is from others in the population; e.g., ][]{Rao82, Lin09,
+  RicoSzei06}; Eigenvector centrality and pagerank
+centrality~\citep[measures of how influential a given node is within
+the broader network; e.g., ][]{Newm08, Bona07, LohmEtal10,
   HaluEtal13}; transfer entropy and flow coefficients~\citep[a measure
@@
 sub-graph centrality~\citep[a measure of a node's participation in all
-of the network's sub-graphs; e.g., ][]{EstrRodr05}.
+of the network's sub-graphs; e.g., ][]{EstrRodr05}; among others.
 
-As an alternative to the above dimensionality reduction approach to
-embedding $\mathbf{Y}_n$ in a lower-dimensional space, but still
-allowing for scalable explorations of higher-order structure in the
-data, we also explore using the above graph theoretic measures as a
-means of obtaining $\hat{\mathbf{Y}}_n$.  In particular: for a given
-graph theoretic measure, $\eta: \mathcal{R}^{F \times F} \rightarrow
-\mathcal{R}^F$, we can use $\eta$ to tranform each row of
-$\mathbf{Y}_n$ in a way that characterizes the corresponding
-graph-theoretic properties of each column.  Whereas the dimensionality
-reduction approach to computing $\hat{\mathbf{Y}}_n$ is lossy,
-the graph-theory approach is lossless.  However, whereas the
-dimensionality reduction approach maintains ties (direct or indirect)
-to the original activity patterns reflected in $\mathbf{Y}_{n-1}$, the
-graph-theory approach does not.  Instead, the graph-theory
-characterizes the nature and timecourse of each feature's
-\textit{participation} in the network.
+For a given graph theoretic measure,
+$\eta: \mathcal{R}^{K \times K} \rightarrow \mathbb{R}^K$, we can use
+$\eta$ to tranform each row of $\mathbf{Y}_n$ in a way that
+characterizes the corresponding graph-theoretic properties of each
+column.  This results in a new $T$ by $K$ matrix, $\mathbf{X}_n$, that
+reflects how the features reflected in the columns of $\mathbf{Y}_n$
+participate in the network during each timepoint (row).
 
 \subsection*{Higher-order correlations}
-Given a timeseries of dynamic correlations (e.g., obtained using
-Eqn.~\ref{eqn:timecorr}), higher-order correlations reflect the
-dynamic correlations between columns of $\mathbf{Y}$.  Given unlimited
-computing resources, one could use repeated applications of
-Equation~\ref{eqn:timecorr} to estimate these higher-order
-correlations (i.e., substituting in the previous output, $\mathbf{Y}$,
-for the input, $\mathbf{X}$ in the equation).  However, because each
-output $\mathbf{Y}$ has $\mathcal{O}(F^2)$ columns relative to $F$ columns in
-the input $\mathbf{X}$, the output of Equation~\ref{eqn:timecorr}
-grows with the square of the number of repeated applications (total
-cost of computing $n$\textsuperscript{th} order correlations is
-$\mathcal{O}(F^{2n})$ for $n \in \mathcal{J}, n > 0$).  When $F$ or $n$ is large,
-this approach quickly becomes intractable.
 
-To make progress in computing $\mathbf{Y_{n+1}}$, we can approximate
-$\mathbf{Y}_n$ by computing an $\mathcal{O}(F)$-dimensional embedding of
-$\mathbf{Y}_n$, termed $\hat{\mathbf{Y}}_n$, and then we can apply
-Equation~\ref{eqn:timecorr} to $\hat{\mathbf{Y}}_n$ rather than
-directly to $\mathbf{Y}_n$.  This enables us to maintain $\mathcal{O}(n)$
-scaling with respect to $n$, rather than exponential scaling via the
-direct approach.
+Because $\mathbf{X}_n$ has the same shape as the original data
+$\mathbf{X}_0$, approximating $\mathbf{Y}_n$ with a lower-dimensional
+$\mathbf{X}_n$ enables us to estimate high-order dynamic correlations
+in a scalable way.  Given a $T$ by $K$ input matrix, the output of
+Equation~\ref{eqn:timecorr} requires $\mathcal{O}(TK^2)$ space to
+store.  Repeated applications of Equation~\ref{eqn:timecorr} (i.e.,
+computing dynamic correlations between the columns of the outputted
+dynamic correlation matrix) each require exponentially more space; in
+general the $n^\mathrm{th}$-order dynamic correlations of a $T$ by $K$
+timeseries occupies $\mathcal{O}(TK^{2n})$ space.  However, when we
+approximate or summarize the output of Equation~\ref{eqn:timecorr} with a $T$ by
+$K$ matrix (as described above), it becomes feasible to compute even
+very high-order correlations in high-dimensional data.  Specifically,
+approximating the $n^\mathrm{th}$-order dynamic correlations of a $T$
+by $K$ timeseries requires only $\mathcal{O}(TK^2)$ additional space--
+the same as would be required to compute first-order dynamic
+correlations. In other words, the space required to store $n+1$
+multivariate timeseries reflecting up to $n^\mathrm{th}$ order
+correlations in the original data scales linearly with $n$ using our
+approach (Fig.~\ref{fig:methods}). \textbf{JRM STOPPED HERE}
 
-\begin{figure}
-  \centering
-  \includegraphics[width=0.5\textwidth]{figs/methods_fig}
-  \caption{\textbf{Computing higher order correlations. } Dynamic
-    correlations
-  are computed then approximated to the same size as original data
-  using dimensionality reduction.
-  This process is repeated, and can be used to compute up to any
-  arbitrary order with compuations scaling linearly (as opposed to exponentially) with order. }
-  \label{fig:methods_fig}
-\end{figure}
+\subsection*{Data}
+We examined two types of data: synthetic data and human functional
+neuroimaging data.  We constructed and leveraged the synthetic data to
+evaluate our general approach.  Specifically, we tested how well
+Equation~\ref{eqn:timecorr} could be used to recover known dynamic
+correlations using different choices of kernel ($\kappa$;
+Fig.~\ref{fig:kernels}), for each of several synthetic datasets that
+exhibited different temporal properties.  We applied our approach to a
+functional neuroimaging dataset to test the hypothesis that ongoing
+cognitive processing is reflected in high-order dynamic correlations.
+We used an across-participant classification test to estimate whether
+dynamic correlations of different orders contain information about
+which timepoint in a story participants were listening to.
 
-There are many possible methods for computing $\hat{\mathbf{Y}}_n$
-from $\mathbf{Y}_n$, including traditional dimensionality reduction
-approaches and graph theory based approaches as described next.  In the
-\textit{Discussion} section we elaborate on other potential approaches.
+\subsubsection*{Synthetic data}
+\paragraph*{Constant.}
+\paragraph*{Random.}
+\paragraph*{Ramping.}
+\paragraph*{Event.}
+
+\subsubsection*{Functional neuroimaging data collected during story
+  listening}
+
+\subsection*{Estimating high-order correlations in neuroimaging data}
+
+\subsection*{Temporal decoding}
+\subsubsection*{Forward inference, cross validation, and feature selection}
+\subsubsection*{Identifying robust decoding results}
+\subsubsection*{Reverse inference}
+
+\textbf{JRM OUTLINE STOPPED HERE}
 
@@
 
-We found for both PCA and eigenvector centrality, during the intact condition in the
-experiment, classifiers that incorporated higher-order correlations
-yielded consistently higher accuracy than classifiers trained only on
-lower-order patterns (Fig.~\ref{fig:decoding_level},  a.\&d.).  We plot
-the average correlations for up to the fourth order for the intact
-condition (Fig.~\ref{fig:brain_plots}) representing the degree of
-agreement by location pair over time.  By
-contrast, we found that incorporating higher-order (greater than first
-order) correlations did
-not further improve decoding accuracy for the other listening
-conditions or rest condition.  This suggests
-that the cognitive processing that supported the most cognitively rich
-condition
-involved higher-order network dynamics.
+We found for both PCA and eigenvector centrality, during the intact
+condition in the experiment, classifiers that incorporated
+higher-order correlations yielded consistently higher accuracy than
+classifiers trained only on lower-order patterns
+(Fig.~\ref{fig:decoding_level}, a.\&d.).  We plot the average
+correlations for up to the fourth order for the intact condition
+(Fig.~\ref{fig:brain_plots}) representing the degree of agreement by
+location pair over time.  By contrast, we found that incorporating
+higher-order (greater than first order) correlations did not further
+improve decoding accuracy for the other listening conditions or rest
+condition.  This suggests that the cognitive processing that supported
+the most cognitively rich condition involved higher-order network
+dynamics.
 
@@
 \section*{Discussion}
+
+\begin{itemize}
+  \item Methods advances: kernel-based dynamic correlations, extension to
+    dynamic ISFC, efficient method for estimating high-order dynamic
+    correlations, identifying robust results by averaging
+  \item Discoveries:
+    \begin{itemize}
+      \item Dimensionality reduction and graph theoretic approaches
+        give different insights into the data and identify different
+        patterns as being relevant to cognition (different peak
+        orders).
+        \item An insight common to both approaches is that high-order
+          (greater than first order) dynamic correlations are
+          informative about ongoing high-level cognitive processing.
+          As the level of cognitive processing decreases, cognition is
+          reflected by lower-order correlations.
+        \item Correlations at different orders are also associated
+          with different networks of brain regions.  However, which
+          networks reflect which types of interactions depends on the
+          current task.  In general, lower order correlations during
+          auditory listening reflect processing of low-level
+          (auditory) features; mid-order correlations reflect speech
+          and linguistic processing; higher-order correlations reflect
+          across-sensory integration (e.g. ties to visual areas) and
+          cognitive control areas.  This hierarchy dissolves during
+          lower-order cognitive processing.
+      \end{itemize}
+  \end{itemize}
 
@@
 computational resources required to calculate higher-order correlations. 
-We developed a computationally tractable model of network dynamics (Fig.~\ref{fig:methods_fig}) that takes in a feature
+We developed a computationally tractable model of network dynamics (Fig.~\ref{fig:methods}) that takes in a feature
 timeseries and outputs approximated first-order dynamics (i.e.,
@@
 to look at the trajectory of the fMRI field so far has taken so far
-(Fig.~\ref{fig:methods_fig}).  The field started with 
+(Fig.~\ref{fig:methods}).  The field started with 
 univariate activation, measuring the average activity for each voxel.

### 2019-08-29 code/scripts/plot_largest_abs.py
updated methods fig

@@ -1,0 +1,75 @@
+
+import supereeg as se
+import os
+from visbrain.objects import BrainObj, SceneObj, SourceObj
+
+cmap = 'autumn_r'
+
+neurosynth_dir ='../figs/neurosynth_data'
+
+bo_dir = os.path.join(neurosynth_dir, 'bos')
+
+n_f_dir = os.path.join(neurosynth_dir, 'figs')
+if not os.path.exists(n_f_dir):
+    os.mkdir(n_f_dir)
+
+conditions = ['intact', 'paragraph', 'rest', 'word']
+
+for c in conditions:
+
+
+    b1 = se.load(os.path.join(bo_dir,f'{c}_1_largest_abs.bo'))
+    b2 = se.load(os.path.join(bo_dir,f'{c}_2_largest_abs.bo'))
+    b3 = se.load(os.path.join(bo_dir,f'{c}_3_largest_abs.bo'))
+    b4 = se.load(os.path.join(bo_dir,f'{c}_4_largest_abs.bo'))
+
+    data1 = b1.get_data().values.ravel()
+    xyz1 = b1.locs.values
+
+    data2 = b2.get_data().values.ravel()
+    xyz2 = b2.locs.values
+
+    data3 = b3.get_data().values.ravel()
+    xyz3 = b3.locs.values
+
+    data4 = b4.get_data().values.ravel()
+    xyz4 = b4.locs.values
+
+
+    template_brain = 'B3'
+
+    sc = SceneObj(bgcolor='white', size=(1000, 1000))
+
+    CBAR_STATE = dict(cbtxtsz=12, clim=[0, 6], txtsz=10., width=.1, cbtxtsh=3.,
+                      rect=(-.3, -2., 1., 4.))
+    KW = dict(title_size=14., zoom=1)
+
+    s_obj_1 = SourceObj('iEEG', xyz1, data=data1, cmap=cmap)
+    s_obj_1.color_sources(data=data1)
+    s_obj_2 = SourceObj('iEEG', xyz2, data=data2, cmap=cmap)
+    s_obj_2.color_sources(data=data2)
+    s_obj_3 = SourceObj('iEEG', xyz3, data=data3, cmap=cmap)
+    s_obj_3.color_sources(data=data3)
+    s_obj_4 = SourceObj('iEEG', xyz4, data=data4, cmap=cmap)
+    s_obj_4.color_sources(data=data4)
+
+    s_obj_all = s_obj_1 + s_obj_2 + s_obj_3 + s_obj_4
+
[…]

### 2019-08-29 code/scripts/plot_largest_abs.py
added abs figs and updated links

@@ -7,6 +7,8 @@ cmap = 'autumn_r'
 
 neurosynth_dir ='../figs/neurosynth_data'
 
+fig_dir = '../figs'
+
 bo_dir = os.path.join(neurosynth_dir, 'bos')
 
 n_f_dir = os.path.join(neurosynth_dir, 'figs')
@@ -72,4 +74,4 @@ for c in conditions:
     b_obj_proj_right.project_sources(s_obj_all, clim=(0, 4), cmap=cmap)
     sc.add_to_subplot(b_obj_proj_right, row=0, col=3, rotate='right', use_this_cam=True)
 
-    sc.screenshot(os.path.join(n_f_dir, f'{c}_largest_abs.png'), transparent=True)
+    sc.screenshot(os.path.join(fig_dir, f'{c}_largest_abs.png'), transparent=True)

### 2019-08-29 paper/main.tex
working on methods section, up to fmri section

@@
 correlations were known.  We then applied our framework to a
-neuroimaging dataset collected as 125 participants listened to either
-an audio recording of a ten-minute story or a temporally scrambled
-version of the story, or underwent a resting state
-scan~\citep{SimoEtal16}.  We used a subset of the data to train
+neuroimaging dataset collected as participants
+listened to either an audio recording of a ten-minute story or a
+temporally scrambled version of the story, or underwent a resting
+state scan~\citep{SimoEtal16}.  We used a subset of the data to train
 across-participant classifiers to decode listening times using a blend
@@
 also yielded the best decoding accuracy for data collected during
-(intact) story listening when high-order (PCA:
-second-order; eigenvector centrality: fourth-order) dynamic
-correlation patterns were included as features.  When we trained
-classifiers on the scambled stories or resting state data, only
-lower-order dynamic patterns were informative to the decoders.  Taken
-together, our results indicate that high-level cognition is supported
-by high-order dynamic patterns of communication between brain
-structures.
+(intact) story listening when high-order (PCA: second-order;
+eigenvector centrality: fourth-order) dynamic correlation patterns
+were included as features.  When we trained classifiers on the
+scambled stories or resting state data, only lower-order dynamic
+patterns were informative to the decoders.  Taken together, our
+results indicate that high-level cognition is supported by high-order
+dynamic patterns of communication between brain structures.
 
@@
     $\mathbf{X}_{n+1}$.  This process may be repeated to scalably estimate
-    iteratively higher-order correlations in the data.}
-  \label{fig:methods}
+    iteratively higher-order correlations in the data.  Note that the
+    transposes of $\mathbf{Y}_n$ and $\mathbf{X}_{n+1}$ are displayed
+    in the figure for compactness.
+  \label{fig:methods}}
 \end{figure}
@@
 For a given graph theoretic measure,
-$\eta: \mathcal{R}^{K \times K} \rightarrow \mathbb{R}^K$, we can use
+$\eta: \mathbb{R}^{K \times K} \rightarrow \mathbb{R}^K$, we can use
 $\eta$ to tranform each row of $\mathbf{Y}_n$ in a way that
@@
 correlations in the original data scales linearly with $n$ using our
-approach (Fig.~\ref{fig:methods}). \textbf{JRM STOPPED HERE}
+approach (Fig.~\ref{fig:methods}).
 
@@
 \subsubsection*{Synthetic data}
-\paragraph*{Constant.}
-\paragraph*{Random.}
-\paragraph*{Ramping.}
-\paragraph*{Event.}
+We constructed a total of 40 multivariate timeseries, collectively
+reflecting a total of 4 different patterns of dynamic correlations
+(i.e., 10 datasets reflecting each type of dynamic pattern).  Each
+timeseries comprised 50 features (dimensions) that varied over 300
+timepoints.  The observations at each timepoint were drawn from a
+zero-mean multivariate Gaussian distribution with a covariance matrix
+defined for each timepoint as described below.  We drew the observations at
+each timepoint independently from the draws at all other timepoints;
+in other words, for each observation $s_t \sim
+\mathcal{N}\left(\mathbf{0}, \mathbf{\Sigma}_t\right)$ at timepoint $t$, $p(s_t) = p(s_t | p_{\backslash t})$.
+
+\paragraph*{Constant.}  We generated data with stable underlying
+correlations to evaluate how Equation~\ref{eqn:timecorr} characterized
+correlation ``dynamics'' when the ground truth correlations were
+static.  We constructed 10 multivariate timeseries, whose observations
+were each drawn from a single (stable) Gaussian distribution.  For
+each dataset, we constructed a random covariance matrix,
+$\mathbf{\Sigma}_m$:
+\begin{align}
+  \mathbf{C}(i, j) &\sim \mathcal{N}(0, 1)\\
+  \mathbf{\Sigma}_m &= \mathbf{C}
+                                          \mathbf{C}^\top~\mathrm{, where}\label{eqn:randcorr}
+  \end{align}
+  $i, j \in \left[1, 2, ..., 50 \right]$.  In other words, all of the
+  observations (for each of the 300 timepoints) within each dataset
+  were drawn from a multivariate Gaussian distribution with the same
+  covariance matrix, and the 10 datasets each used a different
+  covariance matrix.
+
+  \paragraph*{Random.}  We generated a second set of 10 synthetic
+  datasets whose observations at each timepoint were drawn from a
+  Gaussian distribution with a new randomly constructed (using
+  Eqn.~\ref{eqn:randcorr}) covariance matrix.  Because each
+  timepoint's covariance matrix was drawn independently of the
+  covariance matrices for all other timepoints, these datasets
+  provided a test of reconstruction accuracy in the absence of any
+  meaningful underlying temporal structure in the dynamic correlations
+  underlying the data.
+
+  \paragraph*{Ramping.}  We generated a third set of 10 synthetic
+  datasets whose underlying correlations changed gradually over time.
+  For each dataset, we constructed two \textit{anchor} correlation
+  matrices using Equation~\ref{eqn:randcorr},
+  $\mathbf{\Sigma}_{\mathrm{start}}$ and
+  $\mathbf{\Sigma}_{\mathrm{end}}$.  For each of the 300 timepoints in
+  each dataset, we drew the observations from a multivariate Gaussian
+  distribution whose covariance matrix at each timepoint $t \in
+  \left[0, ..., 299\right]$ was given by
+  \begin{align}
+    \mathbf{\Sigma}_t = \left( 1 - \frac{1 - t}{299} \right)
+    \mathbf{\Sigma}_{\mathrm{start}} + \frac{t}{299}\mathbf{\Sigma}_{\mathrm{end}}.
+  \end{align}
+The gradually changing correlations underlying these datasets allow us
+to evaluate the recovery of dynamic correlations when each timepoint's
+correlation matrix is unique (as in the random datasets), but where
+the correlation dynamics are structured.
+
+\paragraph*{Event.} We generated a fourth set of 10 synthetic datasets
+whose underlying correlation matrices exhibited prolonged intervals of
+stability, intersperced with abrupt changes.  For each dataset, we
+used Equation~\ref{fig:randcorr} to generate 5 random covariance
+matrices.  We constructed a timeseries where each set of 60 consecutive samples
+was drawn from a Gaussian with the same covariance matrix.  These
+datasets were intended to simulate a system that undergoes occasional
+abrupt state changes.
+
+\textbf{JRM STOPPED HERE}
 

### 2019-08-30 code/scripts/animate_largest.py
updates for synthetic, methods, and future directions figures

@@ -7,6 +7,8 @@ cmap = 'autumn_r'
 
 neurosynth_dir ='../figs/neurosynth_data'
 
+fig_dir = '../figs'
+
 bo_dir = os.path.join(neurosynth_dir, 'bos')
 
 n_f_dir = os.path.join(neurosynth_dir, 'figs')
@@ -50,6 +52,12 @@ sc = SceneObj(bgcolor='white', size=(500, 500))
 CBAR_STATE = dict(cbtxtsz=12, clim=[0, 6], txtsz=10., width=.1, cbtxtsh=3.,
                   rect=(-.3, -2., 1., 4.))
 KW = dict(title_size=14., zoom=1)
+
+sc_blank = SceneObj(bgcolor='white', size=(500, 500))
+b_obj_proj_blank = BrainObj(template_brain, hemisphere='left', translucent=False)
+sc_blank.add_to_subplot(b_obj_proj_blank, row=0, col=0, rotate='left', use_this_cam=True)
+sc_blank.screenshot(os.path.join(fig_dir, 'blank.png'), transparent=True)
+
 
 s_obj_1 = SourceObj('iEEG', xyz1, data=data1, cmap=cmap)
 s_obj_1.color_sources(data=data1)

### 2019-08-30 paper/main.tex

--- 2019-08-29 paper/main.tex
@@
 
-\subsection*{Data}
-We examined two types of data: synthetic data and human functional
-neuroimaging data.  We constructed and leveraged the synthetic data to
-evaluate our general approach.  Specifically, we tested how well
-Equation~\ref{eqn:timecorr} could be used to recover known dynamic
-correlations using different choices of kernel ($\kappa$;
-Fig.~\ref{fig:kernels}), for each of several synthetic datasets that
-exhibited different temporal properties.  We applied our approach to a
-functional neuroimaging dataset to test the hypothesis that ongoing
-cognitive processing is reflected in high-order dynamic correlations.
-We used an across-participant classification test to estimate whether
-dynamic correlations of different orders contain information about
-which timepoint in a story participants were listening to.
-
-\subsubsection*{Synthetic data}
-\paragraph*{Constant.}
-\paragraph*{Random.}
-\paragraph*{Ramping.}
-\paragraph*{Event.}
-
-\subsubsection*{Functional neuroimaging data collected during story
-  listening}
-
-\subsection*{Estimating high-order correlations in neuroimaging data}
-
-\subsection*{Temporal decoding}
-\subsubsection*{Forward inference, cross validation, and feature selection}
-\subsubsection*{Identifying robust decoding results}
-\subsubsection*{Reverse inference}
-
-\textbf{JRM OUTLINE STOPPED HERE}
-
 \subsection*{Evaluation metrics}
@@
 
-We found for both PCA and eigenvector centrality, during the intact
-condition in the experiment, classifiers that incorporated
-higher-order correlations yielded consistently higher accuracy than
-classifiers trained only on lower-order patterns
-(Fig.~\ref{fig:decoding_level}, a.\&d.).  We plot the average
-correlations for up to the fourth order for the intact condition
-(Fig.~\ref{fig:brain_plots}) representing the degree of agreement by
-location pair over time.  By contrast, we found that incorporating
-higher-order (greater than first order) correlations did not further
-improve decoding accuracy for the other listening conditions or rest
-condition.  This suggests that the cognitive processing that supported
-the most cognitively rich condition involved higher-order network
-dynamics.
+We found for both PCA and eigenvector centrality, during the intact condition in the
+experiment, classifiers that incorporated higher-order correlations
+yielded consistently higher accuracy than classifiers trained only on
+lower-order patterns (Fig.~\ref{fig:decoding_level},  a.\&d.).  We plot
+the average correlations for up to the fourth order for the intact
+condition (Fig.~\ref{fig:brain_plots}) representing the degree of
+agreement by location pair over time.  By
+contrast, we found that incorporating higher-order (greater than first
+order) correlations did
+not further improve decoding accuracy for the other listening
+conditions or rest condition.  This suggests
+that the cognitive processing that supported the most cognitively rich
+condition
+involved higher-order network dynamics.
 
@@
 \section*{Discussion}
-
-\begin{itemize}
-  \item Methods advances: kernel-based dynamic correlations, extension to
-    dynamic ISFC, efficient method for estimating high-order dynamic
-    correlations, identifying robust results by averaging
-  \item Discoveries:
-    \begin{itemize}
-      \item Dimensionality reduction and graph theoretic approaches
-        give different insights into the data and identify different
-        patterns as being relevant to cognition (different peak
-        orders).
-        \item An insight common to both approaches is that high-order
-          (greater than first order) dynamic correlations are
-          informative about ongoing high-level cognitive processing.
-          As the level of cognitive processing decreases, cognition is
-          reflected by lower-order correlations.
-        \item Correlations at different orders are also associated
-          with different networks of brain regions.  However, which
-          networks reflect which types of interactions depends on the
-          current task.  In general, lower order correlations during
-          auditory listening reflect processing of low-level
-          (auditory) features; mid-order correlations reflect speech
-          and linguistic processing; higher-order correlations reflect
-          across-sensory integration (e.g. ties to visual areas) and
-          cognitive control areas.  This hierarchy dissolves during
-          lower-order cognitive processing.
-      \end{itemize}
-  \end{itemize}
 

### 2019-08-30 paper/boneyard.tex
finished neuroimaging methods

@@
+\subsection*{Evaluation metrics}
+We evaluate our approach to extracting dynamic correlations and
+higher-order correlations using several metrics detailed next.  First,
+we generated synthetic data using known time-varying correlations, and
+then we evaluated the fidelity with which Equation~\ref{eqn:timecorr}
+could recover those correlations (for synthetic datasets with
+different properties, and using different kernels to define the
+weights; Fig.~\ref{fig:kernels}).  We then turned to a series of
+analyses on a (real) neuroimaging dataset where the ground truth
+correlations were \textit{not} known.  We evaluated whether the
+recovered correlations could be used to accurately label held-out
+neuroimaging data with the time at which it was collected.  We used this latter evaluations (using timepoint
+decoding) as a proxy for
+gauging how much explanatory power the recovered correlations held
+with respect to the observed data.
+
+\subsubsection*{Generating synthetic data}
+To explore recovery of a constant covariance (Fig.~\ref{fig:synthetic_data},  a.), we generated syntheic
+data sampled from a constant covariance matrix. To do this, we created one random
+covariance matrix, $K$, with 50 features, and for each of the 300 timepoints  we
+sampled from a Gaussian distribution centered on $K$.  Similarly, we generated synthetic data
+sampled from a random covariance matrix (Fig.~\ref{fig:synthetic_data}, b.) by creating a new random
+covariance matrix $K(t)$, for each of the 300 timepoints and sampled from a
+Gaussian distribution centered on $K(t)$.
+
+To generate synthetic data from a dynamically changing covariance
+matrix (Fig.~\ref{fig:synthetic_data},  c.),
+we generated two random covariance
+matrices, $K_{1}$ and $K_{2}$.  We then computed a weighted average covariance matrix
+for each of the 300 timepoint, $K(t)$, 
+by taking the linearly spaced weights ($w$) of the two random matrices, 
+\begin{align}
+K(t) = w(t) * K_{1} + (1 - w(t)) *  K_{2}, \\\label{eqn:ramping}
+\end{align}
+and for each of the 300 timepoints sampled from a
+Gaussian distribution centered on $K(t)$.
+
+Lastly, for the synthetic data containing block structure (Fig.~\ref{fig:synthetic_data},  d.), we followed the same
+process of creating synthetic data sampled from a constant covariance
+matrix (see above) but sampled from a new random covariance matrix
+after 60 consecutive timepoints.  We then pieced the blocks together
+to create a sythetic dataset with 300 total timepoints but drawn from
+5 separate covariance matrices.
+
+\subsubsection*{Recovery of ground truth parameters from synthetic
+  data}
+
+We applied timecorr, using delta and gaussian (width = 10) kernels
+Fig.~\ref{fig:kernels}) to each of these 
+synthetic datasets, then correlated each recovered
+correlation matrix with the ground truth.  We repeated this process 10
+times and explored how recovery varies
+with the kernel and the specific structure of the data. For the
+ramping synthetic dataset (Fig.~\ref{fig:synthetic_data},  c.)  and for the
+block synthetic dataset (Fig.~\ref{fig:synthetic_data},  d.)  we made further
+comparisons of the timecorr recovered correlation matrices. We
+compared the ramping recovered correlation matrices to only the first random covariance matrix $K_{1}$
+(First, Fig.~\ref{fig:synthetic_data},  c.) and to only the last
+random covariance matrix $K_{2}$ (Last, Fig.~\ref{fig:synthetic_data},
+c.) from Equation~\ref{eqn:ramping}. We also compared the block recovered correlation matrices in to
+the block specific covariance matrix (Block 1-5,
+Fig.~\ref{fig:synthetic_data},  d.).
+
 A major challenge to studying such patterns is that typically neither

### 2019-08-30 paper/main.tex
finished neuroimaging methods

--- 2019-08-29 paper/main.tex
@@
 
-\textbf{JRM STOPPED HERE}
-
 \subsubsection*{Functional neuroimaging data collected during story
   listening}
+We examined an fMRI dataset collected by \cite{SimoEtal16} that the
+authors have made publically available at
+http://arks.princeton.edu/ark:/88435/dsp015d86p269k.  The dataset
+comprises neuroimaging data collected as participants listened
+to an audio recording of a story (intact condition; 36 participants),
+listened to time scrambled recordings of the same story (17
+participants in the paragraph-scrambled condition listened to the
+paragraphs in a randomized order and 36 in the word-scrambled
+condition listened to the words in a randomized order), or lay resting
+with their eyes open in the scanner (rest condition; 36
+participants).  Full neuroimaging details may be found in the original
+paper~\citep{SimoEtal16}.
 
-\subsection*{Estimating high-order correlations in neuroimaging data}
+Following our prior related work, we used hierarchical topographic
+factor analysis~\citep{MannEtal18} to derive a compact representation
+of the data.  In brief, this approach approximates the timeseries of voxel
+activations (44,415 voxels) using a much smaller number of radial
+basis function nodes (in this case 700 nodes).  This provides a convenient
+representation for examining full-brain network dynamics.  All of the
+analyses we carried out on the neuroimaging dataset were performed in
+this lower-dimensional space. \textbf{JRM STOPPED HERE}
 
@@
 \textbf{JRM OUTLINE STOPPED HERE}
-
-\subsection*{Evaluation metrics}
-We evaluate our approach to extracting dynamic correlations and
-higher-order correlations using several metrics detailed next.  First,
-we generated synthetic data using known time-varying correlations, and
-then we evaluated the fidelity with which Equation~\ref{eqn:timecorr}
-could recover those correlations (for synthetic datasets with
-different properties, and using different kernels to define the
-weights; Fig.~\ref{fig:kernels}).  We then turned to a series of
-analyses on a (real) neuroimaging dataset where the ground truth
-correlations were \textit{not} known.  We evaluated whether the
-recovered correlations could be used to accurately label held-out
-neuroimaging data with the time at which it was collected.  We used this latter evaluations (using timepoint
-decoding) as a proxy for
-gauging how much explanatory power the recovered correlations held
-with respect to the observed data.
-
-\subsubsection*{Generating synthetic data}
-To explore recovery of a constant covariance (Fig.~\ref{fig:synthetic_data},  a.), we generated syntheic
-data sampled from a constant covariance matrix. To do this, we created one random
-covariance matrix, $K$, with 50 features, and for each of the 300 timepoints  we
-sampled from a Gaussian distribution centered on $K$.  Similarly, we generated synthetic data
-sampled from a random covariance matrix (Fig.~\ref{fig:synthetic_data}, b.) by creating a new random
-covariance matrix $K(t)$, for each of the 300 timepoints and sampled from a
-Gaussian distribution centered on $K(t)$.
-
-To generate synthetic data from a dynamically changing covariance
-matrix (Fig.~\ref{fig:synthetic_data},  c.),
-we generated two random covariance
-matrices, $K_{1}$ and $K_{2}$.  We then computed a weighted average covariance matrix
-for each of the 300 timepoint, $K(t)$, 
-by taking the linearly spaced weights ($w$) of the two random matrices, 
-\begin{align}
-K(t) = w(t) * K_{1} + (1 - w(t)) *  K_{2}, \\\label{eqn:ramping}
-\end{align}
-and for each of the 300 timepoints sampled from a
-Gaussian distribution centered on $K(t)$.
-
-Lastly, for the synthetic data containing block structure (Fig.~\ref{fig:synthetic_data},  d.), we followed the same
-process of creating synthetic data sampled from a constant covariance
-matrix (see above) but sampled from a new random covariance matrix
-after 60 consecutive timepoints.  We then pieced the blocks together
-to create a sythetic dataset with 300 total timepoints but drawn from
-5 separate covariance matrices.
-
-\subsubsection*{Recovery of ground truth parameters from synthetic
-  data}
-
-We applied timecorr, using delta and gaussian (width = 10) kernels
-Fig.~\ref{fig:kernels}) to each of these 
-synthetic datasets, then correlated each recovered
-correlation matrix with the ground truth.  We repeated this process 10
-times and explored how recovery varies
-with the kernel and the specific structure of the data. For the
-ramping synthetic dataset (Fig.~\ref{fig:synthetic_data},  c.)  and for the
-block synthetic dataset (Fig.~\ref{fig:synthetic_data},  d.)  we made further
-comparisons of the timecorr recovered correlation matrices. We
-compared the ramping recovered correlation matrices to only the first random covariance matrix $K_{1}$
-(First, Fig.~\ref{fig:synthetic_data},  c.) and to only the last
-random covariance matrix $K_{2}$ (Last, Fig.~\ref{fig:synthetic_data},
-c.) from Equation~\ref{eqn:ramping}. We also compared the block recovered correlation matrices in to
-the block specific covariance matrix (Block 1-5,
-Fig.~\ref{fig:synthetic_data},  d.).
 
@@
 when using the gaussian kernel.
-
-\subsubsection*{Neuroimaging dataset~\citep{SimoEtal16}}
-For our decoding analysis, we used HTFA-derived node activities
-~\cite{MannEtal18} from fMRI data collected as participants listened
-to an audio recording of a story (intact condition; 36 participants),
-listened to time scrambled recordings of the same story (17
-participants in the paragraph-scrambled condition listened to the
-paragraphs in a randomized order and 36 in the word-scrambled
-condition listened to the words in a randomized order), or lay resting
-with their eyes open in the scanner (rest condition; 36
-participants). We sought to demonstrate how higher-order correlations
-may be used to examine dynamic interactions of brain patterns in
-(real) multi-subject fMRI datasets. This story listening dataset was
-collected as part of a separate study, where the full imaging
-parameters, image preprocessing methods, and experimental details may
-be found~\citep{SimoEtal16}. The dataset is available at
-\href{url}{http://arks. princeton.edu/ark:/88435/dsp015d86p269k}.
 

### 2019-08-30 paper/main.tex
working on temporal decoding section

@@
 interpret this as evidence that the given cognitive states are
-reflected in patterns of $n^\mathrm{th}$-order correlations.
+reflected in patterns of $n^\mathrm{th}$-order correlations.  All of
+the code used to produce the figures and results in this manuscript,
+along with links to the corresponding datasets, may be found at
+\href{https://github.com/ContextLab/timecorr-paper}{github.com/ContextLab/timecorr-paper}.  In addition, we have
+released a Python toolbox for computing dynamic high-order
+correlations in timeseries data; our toolbox may be found at
+\href{https://timecorr.readthedocs.io/}{timecorr.readthedocs.io}. \textbf{JRM NOTE: CHECK LINK}
 
@@
 authors have made publically available at
-http://arks.princeton.edu/ark:/88435/dsp015d86p269k.  The dataset
+\href{http://arks.princeton.edu/ark:/88435/dsp015d86p269k}{arks.princeton.edu/ark:/88435/dsp015d86p269k}.  The dataset
 comprises neuroimaging data collected as participants listened
@@
 factor analysis~\citep{MannEtal18} to derive a compact representation
-of the data.  In brief, this approach approximates the timeseries of voxel
-activations (44,415 voxels) using a much smaller number of radial
-basis function nodes (in this case 700 nodes).  This provides a convenient
-representation for examining full-brain network dynamics.  All of the
-analyses we carried out on the neuroimaging dataset were performed in
-this lower-dimensional space. \textbf{JRM STOPPED HERE}
+of the data.  In brief, this approach approximates the timeseries of
+voxel activations (44,415 voxels) using a much smaller number of
+radial basis function nodes (in this case 700 nodes).  This provides a
+convenient representation for examining full-brain network dynamics.
+All of the analyses we carried out on the neuroimaging dataset were
+performed in this lower-dimensional space.  Code for carrying out
+hierarchical topographic factor analyses on fMRI data may be found as
+part of the BrainIAK toolbox~\citep{brainiak}, which may be downloaded
+at \href{https://brainiak.org/}{brainiak.org}.
 
 \subsection*{Temporal decoding}
-\subsubsection*{Forward inference, cross validation, and feature selection}
+We sought to identify neural patterns that reflected participants'
+ongoing cognitive processing of incoming stimulus information.  As
+reviewed by \cite{SimoEtal16}, one way of homing in on these
+stimulus-driven neural patterns is to compare activity patterns across
+individuals (e.g., using ISFC analyses).  In particular, neural
+patterns will be similar across individuals, to the extent that the
+neural patterns under consideration are stimulus driven, and to the
+extent that the corresponding cognitive representations are reflected
+in similar spatial patterns across people.  Following this logic, we
+used an across-participants temporal decoding test developed by
+\cite{MannEtal18} to assess the degree to which different neural
+patterns reflected ongoing stimulus-driven cognitive processing across
+people.  The approach entails using a subset of the data to train a
+classifier to decode which stimulus timepoint (i.e., moment in the
+story participants listened to).  We use decoding accuracy on held-out
+data (from held-out participants) as a proxy for the extent to which
+the inputted neural patterns reflected stimulus-driven cognitive
+processing in a similar way across individuals.  \textbf{JRM STOPPED HERE}
+
+\subsubsection*{Forward inference}
+
+\subsubsection*{Cross validation}
+\subsubsection*{Feature selection}
 \subsubsection*{Identifying robust decoding results}
@@
 \subsubsection*{Timepoint decoding}
-
-To explore how higher-order structure varies with stimulus structure
-and complexity, we used a previous neuroimaging dataset
-~\cite{SimoEtal16}  in which participants listened to an audio recording of a story; 36 particpants listen to an intact version of the story, 17 participants listen to time-scrambled recordings of the same story where paragraphs were scrambled, 36 particpants listen to word-scrambled version and 36 participants lay in rest condition.
 

### 2019-08-30 paper/boneyard.tex
working on cross validation and forward inference section

@@
+\subsubsection*{Timepoint decoding}
+
+Prior work has shown participants share similar neural responses to
+richly structured stimuli when compared to stimuli with less
+structure.  To assess whether the moment-by-moment higher order
+correlations were reliably preserved across participants, we used
+inter-subject functional connectivity (ISFC) to isolate the
+time-varying correlational structure (functional connectivity patterns
+that were specifically driven by the story participants listened to.
+Following the analyses conducted by (HTFA)~\cite{MannEtal18}, we first
+applied \textit{hierarchical topographic factor analysis} (HTFA) to
+the fMRI datasets to obtain a time series of 700 node activities for
+every participant.  We then computed the dynamic weighted ISFC using a
+range of kernels and widths.  Specifically, we used Gaussian, Laplace,
+and mexican hat kernels, as well as widths of 5, 10, 20, and 50.  We
+then approximated these dynamic correlation using two reduction measures, PCA and eigenvector centrality, and computed the dynamic weighted ISFC on the approximations.
+We repeated this process up to 10th order approximated correlations.
+
+To assess decoding accuracy, we randomly divided participants for each
+stimulus into training and testing groups. For the zeroth order, we
+computed the mean factor activity for each group.  For all subsequent
+orders up to the tenth order, we computed the mean approximated
+dynamic ISFC of factor activity for each group. To assess how
+additional higher-order correlations contribute to decoding accuracy,
+for each order we included a weighted-mixutre (described below) of the activity patterns of all
+previous orders.
+For each group of participants in turn, we compared these activity patterns (using Pearson correlations) to estimate the story times each pattern corresponded to.
+Specifically, we asked, for each timepoint: what are the correlations
+between the first group's and second group's activity patterns at each
+order. We note that the decoding test we used is a conservative in which we count a timepoint label as incorrect if it is not an exact match.
+
+For each order we obtained the weighted-mixture of the correlation
+matrices for the current order and all previous orders using mixing parameter, $\phi$, where $0 <\phi< 1$ reflects a
+weighted mixture of order based decoding Fig.~\ref{fig:decoding_level}
+Panel c. ). We calculated  $\phi$, by
+subdividing the training group and using the quasi-Newton method of
+Broyden, Fletcher, Goldfarb, and Shanno (BFGS ~\citep{NoceWrig06}) for optimization. We
+repeated this cross-validation process 10 times for each parameter set.
+
 \subsection*{Evaluation metrics}

### 2019-08-30 paper/main.tex
working on cross validation and forward inference section

@@
 \bar{\mathbf{C}}(t) = M\left(R\left(\frac{1}{2P} \sum_{p=1}^P
-  Z\left(Y_n^p(t)\right)^\mathrm{T} + Z\left(Y_n^p(t)\right)\right)\right),
+  Z\left(Y_n^p(t)\right)^\mathrm{T} + Z\left(Y_n^p(t)\right)\right)\right),\label{eqn:disfc}
 \end{align}
@@
 participants).  Full neuroimaging details may be found in the original
-paper~\citep{SimoEtal16}.
+paper for which the data were collected~\citep{SimoEtal16}.
 
-Following our prior related work, we used hierarchical topographic
-factor analysis~\citep{MannEtal18} to derive a compact representation
-of the data.  In brief, this approach approximates the timeseries of
-voxel activations (44,415 voxels) using a much smaller number of
-radial basis function nodes (in this case 700 nodes).  This provides a
-convenient representation for examining full-brain network dynamics.
-All of the analyses we carried out on the neuroimaging dataset were
-performed in this lower-dimensional space.  Code for carrying out
-hierarchical topographic factor analyses on fMRI data may be found as
-part of the BrainIAK toolbox~\citep{brainiak}, which may be downloaded
-at \href{https://brainiak.org/}{brainiak.org}.
+\paragraph{Hierarchical topographic factor analysis (HTFA).}
+Following our prior related work, we used HTFA~\citep{MannEtal18} to
+derive a compact representation of the data.  In brief, this approach
+approximates the timeseries of voxel activations (44,415 voxels) using
+a much smaller number of radial basis function nodes (in this case 700
+nodes).  This provides a convenient representation for examining
+full-brain network dynamics.  All of the analyses we carried out on
+the neuroimaging dataset were performed in this lower-dimensional
+space.  In other words, each participant's data matrix,
+$\mathbf{Y}_0$, was a number-of-timepoints by 700 matrix of
+HTFA-derived factor weights (where the row and column labels were
+matched across participants).  Code for carrying out HTFA on fMRI data
+may be found as part of the BrainIAK toolbox~\citep{brainiak}, which
+may be downloaded at \href{https://brainiak.org/}{brainiak.org}.
 
@@
 classifier to decode which stimulus timepoint (i.e., moment in the
-story participants listened to).  We use decoding accuracy on held-out
-data (from held-out participants) as a proxy for the extent to which
-the inputted neural patterns reflected stimulus-driven cognitive
-processing in a similar way across individuals.  \textbf{JRM STOPPED HERE}
+story participants listened to).  We use decoding (forward inference)
+accuracy on held-out data, from held-out participants, as a proxy for
+the extent to which the inputted neural patterns reflected
+stimulus-driven cognitive processing in a similar way across
+individuals.
 
-\subsubsection*{Forward inference}
+\subsubsection*{Forward inference and decoding accuracy}
+We used an across-participants correlation-based classifier to decode
+which stimulus timepoint matched a given neural pattern.  We first
+divided the participants into two groups: a template group,
+$\mathcal{G}_{\mathrm{template}}$, and a to-be-decoded group,
+$\mathcal{G}_{\mathrm{decode}}$.  We used Equation~\ref{eqn:disfc} to
+compute a DISFC matrix for each group
+($\bar{\textbf{C}}_{\mathrm{template}}$ and
+$\bar{\textbf{C}}_{\mathrm{decode}}$, respectively).  We then
+correlated the rows of $\bar{\textbf{C}}_{\mathrm{template}}$ and
+$\bar{\textbf{C}}_{\mathrm{decode}}$ to form a number-of-timepoints by
+number-of-timepoints decoding matrix, $\mathbf{\Lambda}$.  In this
+way, the rows of $\mathbf{\Lambda}$ reflected timepoints from the
+template group, while the columns reflected timepoints from the
+to-be-decoded group.  We assigned temporal labels to each row
+$\bar{\textbf{C}}_{\mathrm{decode}}$ using the row of
+$\bar{\textbf{C}}_{\mathrm{template}}$ to which it was most highly
+correlated.  We then repeated this decoding procedure, but using
+$\mathcal{G}_{\mathrm{decode}}$ as the template group and
+$\mathcal{G}_{\mathrm{template}}$ as the to-be-decoded group.  Given
+the true timepoint labels (for each group), we defined the
+\textit{decoding accuracy} as the proportion of correctly decoded
+timepoints, across both groups.
 
-\subsubsection*{Cross validation}
 \subsubsection*{Feature selection}
+We sought to examine which types of neural features (i.e.,
+activations, first-order dynamic correlations, and higher-order
+dynamic correlations) were informative to the temporal decoders.
+Using the notation above, these features correspond to $\mathbf{Y}_0$,
+$\mathbf{X}_1$, $\mathbf{X}_2$, $\mathbf{X}_3$, and so on (we examined
+up to tenth order correlations, or $\mathbf{X}_{10}$).  Separately for
+each of these types of features, we \textbf{JRM STOPPED HERE}--
+compute lambda, then compute optimal weighted mix using half of the
+template data, then decode the to-be-decoded data using those weights.
+
+From below: quasi-Newton method of Broyden, Fletcher, Goldfarb, and Shanno (BFGS
+~\citep{NoceWrig06}) for optimization. We repeated this
+cross-validation process 10 times for each parameter set.
+
 \subsubsection*{Identifying robust decoding results}
+Params: Gaussian, Laplace, mexican hat kernels.  Widths of 5, 10, 20,
+and 50.
+
 \subsubsection*{Reverse inference}
-
-\textbf{JRM OUTLINE STOPPED HERE}
-
-\subsubsection*{Timepoint decoding}
-
-Prior work has shown participants share similar neural responses to
-richly structured stimuli when compared to stimuli with less
-structure.  To assess whether the moment-by-moment higher order
-correlations were reliably preserved across participants, we used
-inter-subject functional connectivity (ISFC) to isolate the
-time-varying correlational structure (functional connectivity patterns
-that were specifically driven by the story participants listened to.
-Following the analyses conducted by (HTFA)~\cite{MannEtal18}, we first
-applied \textit{hierarchical topographic factor analysis} (HTFA) to
-the fMRI datasets to obtain a time series of 700 node activities for
-every participant.  We then computed the dynamic weighted ISFC using a
-range of kernels and widths.  Specifically, we used Gaussian, Laplace,
-and mexican hat kernels, as well as widths of 5, 10, 20, and 50.  We
-then approximated these dynamic correlation using two reduction measures, PCA and eigenvector centrality, and computed the dynamic weighted ISFC on the approximations.
-We repeated this process up to 10th order approximated correlations.
-
-To assess decoding accuracy, we randomly divided participants for each
-stimulus into training and testing groups. For the zeroth order, we
-computed the mean factor activity for each group.  For all subsequent
-orders up to the tenth order, we computed the mean approximated
-dynamic ISFC of factor activity for each group. To assess how
-additional higher-order correlations contribute to decoding accuracy,
-for each order we included a weighted-mixutre (described below) of the activity patterns of all
-previous orders.
-For each group of participants in turn, we compared these activity patterns (using Pearson correlations) to estimate the story times each pattern corresponded to.
-Specifically, we asked, for each timepoint: what are the correlations
-between the first group's and second group's activity patterns at each
-order. We note that the decoding test we used is a conservative in which we count a timepoint label as incorrect if it is not an exact match.
-
-For each order we obtained the weighted-mixture of the correlation
-matrices for the current order and all previous orders using mixing parameter, $\phi$, where $0 <\phi< 1$ reflects a
-weighted mixture of order based decoding Fig.~\ref{fig:decoding_level}
-Panel c. ). We calculated  $\phi$, by
-subdividing the training group and using the quasi-Newton method of
-Broyden, Fletcher, Goldfarb, and Shanno (BFGS ~\citep{NoceWrig06}) for optimization. We
-repeated this cross-validation process 10 times for each parameter set.
+top 10 strongest correlations for each level; identify endpoint nodes
+(RBFs); make map (threshold at $\theta$-- \textbf{JRM NOTE: what
+  threshold did you use, Lucy?}); decode using neurosynth (cite).
 

### 2019-08-30 code/scripts/plot_largest.py
updates for figs

@@ -18,10 +18,22 @@ conditions = ['intact', 'paragraph', 'rest', 'word']
 for c in conditions:
 
 
-    b1 = se.load(os.path.join(bo_dir,f'{c}_1_largest.bo'))
-    b2 = se.load(os.path.join(bo_dir,f'{c}_2_largest.bo'))
-    b3 = se.load(os.path.join(bo_dir,f'{c}_3_largest.bo'))
-    b4 = se.load(os.path.join(bo_dir,f'{c}_4_largest.bo'))
+    b1 = se.load(os.path.join(bo_dir,f'{c}_1_largest_abs.bo'))
+    b2 = se.load(os.path.join(bo_dir,f'{c}_2_largest_abs.bo'))
+    b3 = se.load(os.path.join(bo_dir,f'{c}_3_largest_abs.bo'))
+    b4 = se.load(os.path.join(bo_dir,f'{c}_4_largest_abs.bo'))
+    b5 = se.load(os.path.join(bo_dir, f'{c}_5_largest_abs.bo'))
+    b6 = se.load(os.path.join(bo_dir, f'{c}_6_largest_abs.bo'))
+    b7 = se.load(os.path.join(bo_dir, f'{c}_7_largest_abs.bo'))
+    b8 = se.load(os.path.join(bo_dir, f'{c}_8_largest_abs.bo'))
+    b9 = se.load(os.path.join(bo_dir, f'{c}_9_largest_abs.bo'))
+    b10 = se.load(os.path.join(bo_dir, f'{c}_10_largest_abs.bo'))
+    b11 = se.load(os.path.join(bo_dir, f'{c}_11_largest_abs.bo'))
+    b12 = se.load(os.path.join(bo_dir, f'{c}_12_largest_abs.bo'))
+    b13 = se.load(os.path.join(bo_dir, f'{c}_13_largest_abs.bo'))
+    b14 = se.load(os.path.join(bo_dir, f'{c}_14_largest_abs.bo'))
+    b15 = se.load(os.path.join(bo_dir, f'{c}_15_largest_abs.bo'))
+
 
     data1 = b1.get_data().values.ravel()
     xyz1 = b1.locs.values
@@ -35,6 +47,38 @@ for c in conditions:
     data4 = b4.get_data().values.ravel()
     xyz4 = b4.locs.values
 
+    data5 = b5.get_data().values.ravel()
+    xyz5 = b5.locs.values
+
[…]

### 2019-08-30 paper/main.tex
backing up progress, working on feature selection

@@
 
-\subsubsection*{Feature selection}
+\subsubsection*{Feature selection and testing}
 We sought to examine which types of neural features (i.e.,
@@
 $\mathbf{X}_1$, $\mathbf{X}_2$, $\mathbf{X}_3$, and so on (we examined
-up to tenth order correlations, or $\mathbf{X}_{10}$).  Separately for
-each of these types of features, we \textbf{JRM STOPPED HERE}--
+up to tenth order correlations, or $\mathbf{X}_{10}$).
+
+One challenge to fairly evaluating high-order correlations is that if
+the kernel used in Equation~\ref{eqn:timecorr} is wider than a single
+timepoint, each repeated application of the equation will result in
+further temporal blur.  Because our primary assessment metric is
+temporal decoding accuracy, this unfairly biases against detecting
+meaningful signal in higher-order correlations (relative to
+lower-order correlations).  We attempted to mitigate temporal blur in
+estimating each $\mathbf{X}_n$ by using a Dirac $\delta$ function
+kernel (which places all of its mass over a single timepoint;
+Fig.~\ref{fig:kernels}b) to compute each lower-order correlation
+($\mathbf{X}_1, \mathbf{X}_2, ..., \mathbf{X}_{n-1}$).  We then used a
+(potentially wider, as described below) kernel to compute $\mathbf{X}_{n}$ from
+$\mathbf{X}_{n-1}$.  In this way, temporal blurring was applied only in the
+last step of computing $\mathbf{X}_n$.  We note that, because each
+$\mathbf{X}_n$ is a low-dimensional representation of the
+corresponding $\mathbf{Y}_n$, the higher-order correlations we
+estimated reflect true correlations in the data with lower-fidelity
+than estimates of lower-order correlations.
+
+After computing each
+$\mathbf{X}_1, \mathbf{X}_2, ..., \mathbf{X}_{n-1}$ for each
+participant, we divided participants into two equally sized groups
+($\pm 1$ for odd numbers of participants):
+$\mathcal{G}_{\mathrm{train}}$ and $\mathcal{G}_{\mathrm{test}}$.  We
+then further subdivided $\mathcal{G}_{\mathrm{train}}$ into
+$\mathcal{G}_{\mathrm{train}_1}$ and $\mathcal{G}_{\mathrm{train}_2}$.
+We then computed $\mathbf{\Lambda}$ temporal correlation matrices for
+each type of neural feature, using $\mathcal{G}_{\mathrm{train}_1}$
+and $\mathcal{G}_{\mathrm{train}_2}$.  This resulted in $n+1$
+$\mathbf{\Lambda}$ matrices (one for the original timeseries of neural
+activations, and one for each of $n$ orders of dynamic correlations).
+Our objective was to find a set of weights of each of these
+$\mathbf{\Lambda}$ matrices such that the weighted average of the
+$n+1$ matrices yielded the highest decoding accuracy.  We used
+quasi-Newton gradient ascent~\citep{NoceWrig06}, using decoding
+accuracy as the objective function to be maximized, to find an optimal
+set of training data-derived weights, $\phi_{0, 1, ..., n}$, where
+$\sum_{i=0}^n \phi_i = 1$ and where
+$\phi_i \geq 0 \forall i \in \left[0, 1, ..., n\right]$.
+
+After estimating an optimal set of weights, we computed a new set of
+$n + 1$ $\mathbf{\Lambda}$ matrices correlating timepoints from  $\mathcal{G}_{\mathrm{train}}$
+and $\mathcal{G}_{\mathrm{test}}$.
+
+\textbf{JRM STOPPED HERE}--
+say something about delta function kernel to avoid something at higher
+orders, then in the last order use a gaussian, laplace, or mexican hat kernel.
+
 compute lambda, then compute optimal weighted mix using half of the

### 2019-08-30 paper/main.tex
working on parameter robustness testing section

@@
 
-\subsubsection*{Feature selection and testing}
+\subsubsection*{Feature weighting and testing}
 We sought to examine which types of neural features (i.e.,
@@
 After estimating an optimal set of weights, we computed a new set of
-$n + 1$ $\mathbf{\Lambda}$ matrices correlating timepoints from  $\mathcal{G}_{\mathrm{train}}$
-and $\mathcal{G}_{\mathrm{test}}$.
+$n + 1$ $\mathbf{\Lambda}$ matrices correlating the DISFC patterns
+from $\mathcal{G}_{\mathrm{train}}$ and $\mathcal{G}_{\mathrm{test}}$
+at each timepoint.  We use the resulting decoding accuracy of
+$\mathcal{G}_{\mathrm{test}}$ timepoints to estimate how informative
+the set up neural features containing up to $n^\mathrm{th}$ order
+correlations were.
 
-\textbf{JRM STOPPED HERE}--
-say something about delta function kernel to avoid something at higher
-orders, then in the last order use a gaussian, laplace, or mexican hat kernel.
-
-compute lambda, then compute optimal weighted mix using half of the
-template data, then decode the to-be-decoded data using those weights.
-
-From below: quasi-Newton method of Broyden, Fletcher, Goldfarb, and Shanno (BFGS
-~\citep{NoceWrig06}) for optimization. We repeated this
-cross-validation process 10 times for each parameter set.
+We used a permutation-based procedure to form a stable estimate of
+decoding accuracy for each set of neural features.  In particular, we
+computed the decoding accuracy for each of 10 random group assignments of
+$\mathcal{G}_{\mathrm{train}}$ and $\mathcal{G}_{\mathrm{test}}$.  We
+report the mean accuracy (and 95\% confidence intervals) for each set
+of neural features.
 
 \subsubsection*{Identifying robust decoding results}
+For synthetic data where the true underyling dynamic correlations are
+known, we are able to directly evaluate how well the recovered
+correlations match the ground truth, for different choices of kernel
+shape and width.  For real-world data (where the ground truth is not
+known), we use decoding accuracy to estimate whether a given set of
+neural features reliably reflects ongoing stimulus-driven cognitive
+processing.  We cannot know which choice of kernel most accurately
+reflects the ``true'' information content of the data.  For example, a
+given kernel might highlight particular temporal aspects of the data
+in a way that enhances or diminishes decoding performance.
+\textbf{JRM STOPPED HERE}
+
 Params: Gaussian, Laplace, mexican hat kernels.  Widths of 5, 10, 20,

### 2019-09-01 paper/boneyard.tex
finished robustness testing section, backing up progress

@@
+For synthetic data where the true underyling dynamic correlations are
+known, we are able to directly evaluate how well the recovered
+correlations match the ground truth, for different choices of kernel
+shape and width.  In contrast, or real-world data (where the ground
+truth is not known), we use decoding accuracy to estimate whether a
+given set of neural features reliably reflects ongoing stimulus-driven
+cognitive processing.  However, under different circumstances,
+different classifier properties (e.g., kernel shapes, kernel widths,
+classification algorithm, etc.) will give rise to different decoding
+accuracies.  We can average over different cross validation group
+assignments to improve the stability of the decoding accuracy
+assessments (to factor out effects due to particular group
+assignments), but
+
+cannot know whether a given
+
+Because decoding accuracy is an indirect
+reflection of how much a given set of neural features
+
+We cannot know which choice of kernel most accurately
+reflects the ``true'' information content of the data.
+
+For example, a
+given kernel might highlight particular temporal aspects of the data
+in a way that enhances or diminishes decoding performance.
+\textbf{JRM STOPPED HERE}
+
 \subsubsection*{Timepoint decoding}

### 2019-09-01 paper/main.tex
finished robustness testing section, backing up progress

@@
 \subsubsection*{Identifying robust decoding results}
-For synthetic data where the true underyling dynamic correlations are
-known, we are able to directly evaluate how well the recovered
-correlations match the ground truth, for different choices of kernel
-shape and width.  For real-world data (where the ground truth is not
-known), we use decoding accuracy to estimate whether a given set of
-neural features reliably reflects ongoing stimulus-driven cognitive
-processing.  We cannot know which choice of kernel most accurately
-reflects the ``true'' information content of the data.  For example, a
-given kernel might highlight particular temporal aspects of the data
-in a way that enhances or diminishes decoding performance.
+The temporal decoding procedure we use to estimate which neural
+features support ongoing cognitive processing is goverened by many
+parameters.  For example, Equation~\ref{eqn:timecorr} requires
+defining a kernel function, which can take on different shapes and
+widths.  For a fixed set of neural features, each of these parameters
+can yield different decoding accuracies.  Further, the best decoding
+accuracy for a given timepoint may be reliably achieved by one set of
+parameters, whereas the best decoding accuracy for another timepoint
+might be reliably achieved by a different set of parameters, and the
+best decoding accuracy across \textit{all} timepoints might be
+reliably achieved by still another different set of parameters.
+Rather than attempting to maximize decoding accuracy, we sought to
+discover the trends in the data that were robust to specific
+classifier parameters choices.  Specifically, we sought to
+characterize how decoding accuracy varied (under different
+experimental conditions) as a function of which neural features were
+considered.
+
+To identify decoding results that were robust to specific classifier
+parameter choices, we repeated our decoding analyses that substituted
+in a variety of kernel shapes and widths for
+Equation~\ref{eqn:timecorr}.  We examined Gaussian
+(Fig.~\ref{fig:kernels}c), Laplace (Fig.~\ref{fig:kernels}d), and
+Mexican Hat (Fig.~\ref{fig:kernels}e) kernels, each with widths of 5,
+10, 20, and 50 samples.  We then report the average decoding
+accuracies across all of these parameter choices.  This enabled us to
+(roughly) factor out performance characteristics that were parameter
+dependent (within the space of parameters we examined).
+
 \textbf{JRM STOPPED HERE}
-
-Params: Gaussian, Laplace, mexican hat kernels.  Widths of 5, 10, 20,
-and 50.
 

### 2019-09-01 paper/main.tex
changed figure 2 caption to match methods section text

@@
     centered on time $t$.  Weights derived using several different
-    example variance parameters ($\sigma^2$ are displayed.
+    example width parameters ($\sigma^2$) are displayed.
     \textbf{d. Laplace kernels.}  Each kernel's weights fall off
@@
     centered on time $t$.  Weights derived using several different
-    example scale parameters ($b$) are displayed.  \textbf{e. Mexican
+    example width parameters ($b$) are displayed.  \textbf{e. Mexican
       hat (Ricker wavelet) kernels.}  Each kernel's weights fall

### 2019-09-01 paper/main.tex
backing up notes on reverse inference section

@@
 \subsubsection*{Reverse inference}
-top 10 strongest correlations for each level; identify endpoint nodes
-(RBFs); make map (threshold at $\theta$-- \textbf{JRM NOTE: what
-  threshold did you use, Lucy?}); decode using neurosynth (cite).
+copying from lucy's message on slack:
+- for each order, compute the average (pairwise) correlations
+- pick the 10 strongest (absolute value) correlations
+- find the RBFs on the endpoints of those correlations (i.e. the features being correlated)
+- make a map by summing together those (thresholded at 0.999) RBFs
+- decode with neurosynth
+- print out top 10 terms
 

### 2019-09-01 paper/main.tex
finished going through methods section, outlined results section rewrite in comments

--- 2019-09-01 paper/main.tex
@@
 approximates the timeseries of voxel activations (44,415 voxels) using
-a much smaller number of radial basis function nodes (in this case 700
+a much smaller number of radial basis function (RBF) nodes (in this case 700
 nodes).  This provides a convenient representation for examining
@@
 
+\subsubsection*{Reverse inference}
+The dynamic patterns we examine comprise high-dimensional correlation
+patterns at each timepoint.  To help interpret the resulting patterns
+in the context of other studies, we created summary maps by computing
+the across-timepoint average pairwise correlations at each order of
+analysis (first order, second order, etc., up to fifteenth order
+correlations).  We selected the 10 strongest (absolute value)
+correlations at each order.  Each correlation is between the dynamic
+activity patterns (or patterns of dynamic high-order correlations)
+measured at two RBF nodes (see \textit{Hierarchical Topographic Factor
+  Analysis}).  Therefore, the 10 strongest correlations involved up to
+20 RBF nodes.  Each RBF defines a spatial function whose activations
+range from 0 to 1.  We thresholded each RBF at 0.999 to construct a
+map of spherical components that denoted the endpoints of the 10
+strongest correlations.  We then carried out a meta analysis using
+Neurosynth~\citep{RubiEtal17} to identify the 10 terms most commonly
+associated with the given map.  This resulted in a set of 10 terms
+associated with the average dynamic correlation patterns at each order.
+
+\section*{Results}
 \textbf{JRM STOPPED HERE}
 
-\subsubsection*{Reverse inference}
-top 10 strongest correlations for each level; identify endpoint nodes
-(RBFs); make map (threshold at $\theta$-- \textbf{JRM NOTE: what
-  threshold did you use, Lucy?}); decode using neurosynth (cite).
-
-\section*{Results}
+%overview: first validate our approach with synthetic data, then apply
+%to fMRI data
+
+%synthetic data: we can recover dynamic correlations using different
+%kernels
+% wider kernels (Laplace, Gaussian) performed best when the
+% correlations varied in a temporally structured way
+% delta function kernels were best when the correlations varied
+% randomly over time
+% overall we recovered the structure we embedded in the data under all
+% synthetic datasets we tested.  our approach performed best when the
+% underlying correlational structure was either constant or gradually
+% changing.  our approach performed worst when the underlying
+% correlations varied randomly for one timepoint to the next.
+
+% we used temporal decoders to identify cognitivly relevant neural
+% patterns in fMRI data (see forward inference section of methods).
+% we explored two approaches to effiently computing high-order
+% correlations: PCA (dimensionality reduction) and eigenvector
+% centrality (graph measure).  both approaches yielded qualitatively
+% similar results for the story listening conditions: intact story was
+% best decoded using high-order correlations, whereas scrambled
+% stories were best decoded using lower-order correlations.  both
+% approaches also yielded slightly above-chance decoding of resting state times
+% (perhaps picking up on decreasing attention and/or increasing
+% mind-wandering as the resting state scan progressed).  The PCA-based
+% approach achieved the highest decoding accuracy using
+% non-correlational (activation-based) data, whereas the eigenvector
+% centrality approach identified second-order correlations as being
+% most informative about resting state times.
+
+% finally, we sought to identify which specific brain areas were
+% involved in supporting cognition through high-order interactions.
+% we used the eigenvector centrality results, which preserves the
+% original feature space when characterizing high-order dynamic
+% correlations.  we found that first and second-order correlations
+% reflected auditory and speech processing in all of the story
+% listening conditions.  during intact story listening, third order
+% correlations reflected integration with visual areas, and fourth
+% order correlations recruited high-level cognition regions.  however,
+% during listening to temporally scrambled stories, these higher-order
+% correlations did not involve visual areas or high-order cognitive
+% control regions.  during rest we found a much different set of
+% patterns.  first order correlations involved counting networks; second-order
+% correlations recruited visual networks; third-order correlations
+% recruited working memory networks; fourth-order correlations
+% recruited episodic memory areas.
+
 \subsubsection*{Synthetic data}

### 2019-09-02 paper/main.tex
working on results for synthetic data

@@
 \end{align}
-Here $\mathrm{timecorr}(\mathbf{X}(\cdot, i), \mathbf{X}(\cdot, j),
+Here
+$\mathrm{timecorr}(\mathbf{X}(\cdot, i), \mathbf{X}(\cdot, j),
 \kappa_t)$ reflects the correlation at time $t$ between columns $i$
-  and $j$ of $\mathbf{X}$, estimated using the kernel $\kappa_t$.
+and $j$ of $\mathbf{X}$, estimated using the kernel $\kappa_t$.  We
+evaluate Equation~\ref{eqn:timecorr} in turn each pair of columns in
+$\mathbf{X}$ and for kernels centered on each timepoint in the
+timeseries, respectively, to obtain a $T$ by $K$ by $K$ timeseries of
+dynamic correlations, $\mathbf{Y}$.  For convenience, we then reshape
+the upper triangles of each timepoint's correlation matrix into a row
+vector to obtain an equivalent $T$ by $\frac{K^2 - K}{2}$ matrix.
 
@@
 
-\subsection*{Higher-order correlations}
+\subsection*{Dynamic higher-order correlations}
 
@@
 \section*{Results}
-\textbf{JRM STOPPED HERE}
-
-%overview: first validate our approach with synthetic data, then apply
-%to fMRI data
+We sought to understand whether high-level cognition is supported by
+dynamic patterns of high-order correlations.  To that end, we
+developed a computational framework for estimating the dynamics of
+high-order correlations in multivariate timeseries data (see
+\textit{Dynamic inter-subject functional connectivity (DISFC)} and
+\textit{Dynamic higher-order correlations}).  We evaluated the
+efficacy of this framework at recovering known patterns in several
+synthetic datasets (see \textit{Synthetic data}).  We then applied the
+framework to a public fMRI dataset collected as participants listened
+to an auditorally presented story, a temporally scrambled version of
+the story, or underwent a resting state scan (see \textit{Functional
+  neuroimaing data collected during story listening}).  We used the
+relative decoding accuracies of classifiers trained on
+different sets of neural features to estimate which types of features
+reflected ongoing cognitive processing.
+
+\subsection*{Recovering known dynamic correlations from synthetic data}
 
@@
 % correlations varied randomly for one timepoint to the next.
+
+\begin{figure}[tp]
+  \centering
+  \includegraphics[width=\textwidth]{figs/synthetic_data.pdf}
+  \caption{\textbf{Recovering known dynamic correlations from
+      synthetic data.}  Each panel displays the average correlations between
+    the vectorized upper triangles of the recovered correlation matrix
+    at each timepoint and either the true underlying correlation at each timepoint or a
+    reference correlation matrix.  (The averages are taken across 10
+    different randomly generated synthetic datasets.) Error ribbons
+    denote 95\% confidence intervals (taken across datasets). Different colors denote different
+    kernel shapes, whereas the shading within each color type denotes
+    kernel widths.  For a complete description of each synthetic
+    dataset, see \textit{Synthetic data}.  \textbf{a. Constant
+      correlations.} These datasets have a stable (unchanging)
+    underlying correlation matrix.  \textbf{b. Random
+      correlations.}  These datasets are generated using a new
+    independently drawn correlation matrix at each new timepoint.  \textbf{c. Ramping
+      correlations.}  These datasets are generated by smoothly varying
+    the underlying correlations between the randomly drawn
+    correlation matrices at first and last timepoints.  The left
+    panel displays the correlations between the recovered dynamic
+    correlations and the underlying ground truth correlations.  The
+    middle panel compares the recovered correlations with the
+    \textit{first} timepoint's correlation matrix.  The right panel
+    compares the recovered correlations with the
+    \textit{last} timepoint's correlation matrix.
+    \textbf{d. Event-based correlations.}  These datasets are each
+    generated using five randomly drawn correlation matrices that each
+    remain stable for a fifth of the total timecourse.  The left panel
+    displays the correlations between the recovered dynamic
+    correlations and the underlying ground truth correlations.  The
+    right panels compare the recovered correlations with the
+    correlation matrices unique to each event.}
+  \label{fig:synthetic_data}
+\end{figure}
+
+\textbf{JRM STOPPED HERE}
 
@@
 \subsubsection*{Synthetic data}
-
-\begin{figure}
-  \centering
-  \includegraphics[width=\textwidth]{figs/synthetic_data.pdf}
-  \caption{\textbf{Dynamic correlation recovery with synthetic data. } Using synthetic data containing different
-    underlying correlational structure,
-   we test how well we can recover dynamic correlation matrices using
-   different kernels when compared to groud truth.  We compare the results using a delta kernel
-   with averaged results from several kernels (Gaussian, Laplace, and
-   mexican hat) and several widths (5, 10, 20, and 50).  We plot recovery using of datasets containing the
-    following underlying structure:
-    \textbf{a. Constant. b. Random. c. Ramping.  d. Block.}}
-  \label{fig:synthetic_data}
-\end{figure}
 

### 2019-09-02 paper/boneyard.tex
working on fmri temporal decoding results

@@
+We next evaluated if our model of high-order correlations in brain activity can capture cognitively relevant brain patterns.
+We performed a decoding analysis, using cross validation to estimate (using other participants’ data) which parts of the story each weighted-mixture of higher-order brain activity pattern corresponded to (see \textit{Materials and methods}).
+We note that our primary goal was not to achieve perfect decoding accuracy, but rather to use decoding accuracy as a benchmark for assessing whether different neural features specifically capture cognitively relevant brain patterns.
+
+Separately for each experimental condition, we divided participants
+into two groups. For the zeroth order, we computed the mean factor
+activity for each group.  For all subsequent orders up to the tenth
+order, we computed the mean approximated dynamic ISFC of factor
+activity for each group (see \textit{Materials and methods}), and
+combined in a weighted mixutre with all previous orders
+(i.e. cross-validation for the second
+order contained a weighted-mixture of zeroth, first, and second order
+(Fig.~\ref{fig:decoding_level}, c.\&f.).  For
+each order, we correlated the group 1 activity patterns with group 2
+activity patterns.  We then subdivided the group 1 to obtain an
+optimal weighting parameter for each order’s correlation matrix using
+the same cross validation method. We used the optimal weighting
+parameters to obtain a weighted-mixture (see \textit{Materials and methods}) of each order’s correlation
+matrix. Using these correlations, we labeled the group 1 timepoints
+using the group 2 timepoints with which they were most highly
+correlated; we then computed the proportion of correctly labeled group
+1 timepoints. (We also performed the symmetric analysis whereby we
+labeled the group 2 timepoints using the group 1 timepoints as a
+template.) We repeated this procedure 100 times (randomly re-assigning
+participants to the two groups each time) to obtain a distribution of
+decoding accuracies for each experimental condition. There were 272
+timepoints for paragraph condition, 300 timepoints for intact and word
+conditions, and 400 timepoints for rest condition,  so chance
+performance on this decoding test is was $\frac{1}{272}$,
+$\frac{1}{300}$, and $\frac{1}{400}$ respectively.
+
+We repeated this process for each set of parameters, varying kernel
+type and width, and averaged over the reduction technique used to
+approximate the higher-order correlations (PCA Fig.~\ref{fig:decoding_level},  a.-c. and eigenvector
+centrality Fig.~\ref{fig:decoding_level},  d.-f.).  Since there is no ground truth in these analyses, and we did not know
+which parameters best capture the data, we instead report a robustness
+search by averaging over the parameters and reporting which results
+consistently showed up across all parameters.
+\begin{figure}
+  \centering
+  \includegraphics[width=\textwidth]{figs/brain_plots.pdf}
+  \caption{\textbf{Average correlations by order for the intact listening condition.} Using eigenvector
+    centrality to approximate higher-order correlations for the
+    intact, paragraph scrambled, word scrambled, and rest condition.
+    We plot the
+    strongest 50\% absolute value
+    mean correlation for \textbf{a.-d. first order, e.-h. second order,
+      i.-l. third order, and m.-p. fourth order }, representing the degree of agreement by
+    location pair over time.  To demonstrate how this method is
+    computationally scalable, we also approximated
+    \textbf{a.-d. fifteenth order} dynamic correlation, which would be
+    possible to compute using conventional methods since it would require more bits to represent the solution than there are molecules in the universe.}
+  \label{fig:brain_plots}
+\end{figure}
+
+The two methods used to approximate the higher-order correlations (PCA Fig.~\ref{fig:decoding_level},  a.-c. and eigenvector
+centrality Fig.~\ref{fig:decoding_level},  d.-f.) capture different
+facets of the activity patterns.  Using PCA, the higher-order
+correlations are all linked to the original activity patterns, whereas
+eigenvectory centrality breaks the immediate link with specific brain
+areas and instead characterizes the position of the nodes in the
+network that are similar over time.
+
+We found for both PCA and eigenvector centrality, during the intact
+condition in the experiment, classifiers that incorporated
+higher-order correlations yielded consistently higher accuracy than
+classifiers trained only on lower-order patterns
+(Fig.~\ref{fig:decoding_level}, a.\&d.).  We plot the average
+correlations for up to the fourth order for the intact condition
+(Fig.~\ref{fig:brain_plots}) representing the degree of agreement by
+location pair over time.  By contrast, we found that incorporating
+higher-order (greater than first order) correlations did not further
+improve decoding accuracy for the other listening conditions or rest
+condition.  This suggests that the cognitive processing that supported
+the most cognitively rich condition involved higher-order network
+dynamics.
+
+%synthetic data: we can recover dynamic correlations using different
+%kernels
+% wider kernels (Laplace, Gaussian) performed best when the
+% correlations varied in a temporally structured way
+% delta function kernels were best when the correlations varied
+% randomly over time
+% overall we recovered the structure we embedded in the data under all
+% synthetic datasets we tested.  our approach performed best when the
+% underlying correlational structure was either constant or gradually
+% changing.  our approach performed worst when the underlying
+% correlations varied randomly for one timepoint to the next.
+
+\subsubsection*{Synthetic data}
+
+To assess the performance of dynamic correlation recovery using
+timecorr, we varied width the kernel and the specific structure of the
+data. We applied timecorr, using delta and gaussian kernels
+Fig.~\ref{fig:kernels}) to each of the following  
+synthetic datasets: constant, random, ramping, and block.  We then correlated each recovered
+correlation matrix with the ground truth.
+
+For the constant synthetic dataset, a gaussian kernel (width=10)
+outperformed the delta kernel (Fig.~\ref{fig:synthetic_data},  a.).  This is in contrast with the random
+synthetic dataset, for which the delta kernel best captures the
+rapidly changing structure (Fig.~\ref{fig:synthetic_data},  b.). For
+the ramping synthetic dataset, the slow changing strucutre within the
+data is best
+captured by the gaussian kernel and the best recovery occurs in the
+middle (Ramping, Fig.~\ref{fig:synthetic_data},
+c.). In addition to comparing the timecorr recovered correlation
+matrices to the ground truth, we
+further compared the ramping recovered correlation matrices to only the first random covariance matrix $K_{1}$
+(First, Fig.~\ref{fig:synthetic_data},  c.) and to only the last
+random covariance matrix $K_{2}$ (Last, Fig.~\ref{fig:synthetic_data},
+c.), both of which perform best at the beginning and end respectively.
+
+Similary for the block sythetic dataset, we compared the timecorr
+recovered correlation matrices to the ground truth as well as to each
+block-specific covariance matrix (Block 1-5,
+Fig.~\ref{fig:synthetic_data},  d.).  Although the structure is
+changing by block, the gaussian kernel once again outperforms the
+delta kernel.  Performance does however drop near even boundaries for
+when using the gaussian kernel.
+
 For synthetic data where the true underyling dynamic correlations are

### 2019-09-02 paper/main.tex
working on fmri temporal decoding results

@@
 specific activity patterns in any given set of regions~\citep[e.g.,
-following][]{BassEtal06}.  For example, graph theoretic measures such
-as centrality and degree~\citep{BullSpor09} may be used to estimate
-how a given brain structure is ``communicating'' with other
-structures, independently of the specific neural representations
-carried by those structures.  If one considers a brain region's graph
-theoretic position in the network (e.g., its eigenvector centrality)
-as a dynamic property, one can compare how the positions of different
-regions are correlated, and/or how those patterns of correlations change
-over time.  We can also compute higher-order patterns in these
-correlations to characterize homologous subgraphs in the connectome
-that display similar changes in their constituent brain structures'
-interactions with the rest of the brain.
+following][]{BassEtal06}.  For example, graph measures such as
+centrality and degree~\citep{BullSpor09} may be used to estimate how a
+given brain structure is ``communicating'' with other structures,
+independently of the specific neural representations carried by those
+structures.  If one considers a brain region's position in the network
+(e.g., its eigenvector centrality) as a dynamic property, one can
+compare how the positions of different regions are correlated, and/or
+how those patterns of correlations change over time.  We can also
+compute higher-order patterns in these correlations to characterize
+homologous subgraphs in the connectome that display similar changes in
+their constituent brain structures' interactions with the rest of the
+brain.
 
@@
 algorithms to project $\mathbf{Y}_n$ onto a $K$-dimensional space.
-The second approach uses graph-theoretic measures to characterize the
+The second approach uses graph measures to characterize the
 relative positions of each feature ($k \in \left[1, ..., K \right]$)
@@
 
-\subsubsection*{Graph theoretic approaches to computing
+\subsubsection*{Graph measure approaches to computing
   $\mathbf{X}_n$}
@@
 (potentially recombined and transformed) mapping back to the original
-data in $\mathbf{Y}_0$.  We also explore graph theoretic approaches
+data in $\mathbf{Y}_0$.  We also explore graph measure approaches
 that forgo a preserved mapping back to the original data in favor of
@@
 
-In general, graph theoretic measures take as input a matrix of
+In general, graph measures take as input a matrix of
 interactions (e.g., using the above notation, an $K$ by $K$
@@
 
-For a given graph theoretic measure,
+For a given graph measure,
 $\eta: \mathbb{R}^{K \times K} \rightarrow \mathbb{R}^K$, we can use
 $\eta$ to tranform each row of $\mathbf{Y}_n$ in a way that
-characterizes the corresponding graph-theoretic properties of each
+characterizes the corresponding graph properties of each
 column.  This results in a new $T$ by $K$ matrix, $\mathbf{X}_n$, that
@@
 \subsection*{Recovering known dynamic correlations from synthetic data}
-
-%synthetic data: we can recover dynamic correlations using different
-%kernels
-% wider kernels (Laplace, Gaussian) performed best when the
-% correlations varied in a temporally structured way
-% delta function kernels were best when the correlations varied
-% randomly over time
-% overall we recovered the structure we embedded in the data under all
-% synthetic datasets we tested.  our approach performed best when the
-% underlying correlational structure was either constant or gradually
-% changing.  our approach performed worst when the underlying
-% correlations varied randomly for one timepoint to the next.
+We generated synthetic datasets that differed in how the underlying
+correlations changed over time.  For each dataset, we applied
+Equation~\ref{eqn:timecorr} with a variety of kernel shapes and
+widths.  We assessed how well the true underlying correlations at each
+timepoint matched the recovered correlations
+(Fig.~\ref{fig:synthetic}).  For every kernel and dataset we tested,
+our approach recovered the correlation dynamics we embedded into the
+data.  However, the quality of these recoveries varied across
+different synthetic datasets in a kernel-dependent way.
 
@@
   \caption{\textbf{Recovering known dynamic correlations from
-      synthetic data.}  Each panel displays the average correlations between
-    the vectorized upper triangles of the recovered correlation matrix
-    at each timepoint and either the true underlying correlation at each timepoint or a
-    reference correlation matrix.  (The averages are taken across 10
-    different randomly generated synthetic datasets.) Error ribbons
-    denote 95\% confidence intervals (taken across datasets). Different colors denote different
-    kernel shapes, whereas the shading within each color type denotes
-    kernel widths.  For a complete description of each synthetic
-    dataset, see \textit{Synthetic data}.  \textbf{a. Constant
-      correlations.} These datasets have a stable (unchanging)
-    underlying correlation matrix.  \textbf{b. Random
-      correlations.}  These datasets are generated using a new
-    independently drawn correlation matrix at each new timepoint.  \textbf{c. Ramping
-      correlations.}  These datasets are generated by smoothly varying
-    the underlying correlations between the randomly drawn
-    correlation matrices at first and last timepoints.  The left
-    panel displays the correlations between the recovered dynamic
-    correlations and the underlying ground truth correlations.  The
-    middle panel compares the recovered correlations with the
-    \textit{first} timepoint's correlation matrix.  The right panel
-    compares the recovered correlations with the
-    \textit{last} timepoint's correlation matrix.
+      synthetic data.}  Each panel displays the average correlations
+    between the vectorized upper triangles of the recovered
+    correlation matrix at each timepoint and either the true
+    underlying correlation at each timepoint or a reference
+    correlation matrix.  (The averages are taken across 10 different
+    randomly generated synthetic datasets of the given category.)
+    Error ribbons denote 95\% confidence intervals (taken across
+    datasets). Different colors denote different kernel shapes,
+    whereas the shading within each color type denotes kernel widths.
+    For a complete description of each synthetic dataset, see
+    \textit{Synthetic data}.  \textbf{a. Constant correlations.} These
+    datasets have a stable (unchanging) underlying correlation matrix.
+    \textbf{b. Random correlations.}  These datasets are generated
+    using a new independently drawn correlation matrix at each new
+    timepoint.  \textbf{c. Ramping correlations.}  These datasets are
+    generated by smoothly varying the underlying correlations between
+    the randomly drawn correlation matrices at first and last
+    timepoints.  The left panel displays the correlations between the
+    recovered dynamic correlations and the underlying ground truth
+    correlations.  The middle panel compares the recovered
+    correlations with the \textit{first} timepoint's correlation
+    matrix.  The right panel compares the recovered correlations with
+    the \textit{last} timepoint's correlation matrix.
     \textbf{d. Event-based correlations.}  These datasets are each
@@
     correlation matrices unique to each event.}
-  \label{fig:synthetic_data}
+  \label{fig:synthetic}
+\end{figure}
+
+In general, wide monotonic kernels (Laplace, Gaussian) performed best
+when the correlations varied gradually from moment-to-moment
+(Figs.~\ref{fig:synthetic}a, c, and d).  \textbf{TODO: Say something
+  about kernel widths within a shape.}  In the extreme, as the rate of
+change in correlations approaches 0 (Fig.~\ref{fig:synthetic}a), an
+infinitely wide kernel would exactly recover the Pearson's correlation
+(e.g., compare Eqns.~\ref{eqn:corr} and \ref{eqn:timecorr}).
+
+When the correlation dynamics were unstructured in time
+(Fig.~\ref{fig:synthetic}b), a Dirac $\delta$ kernel (infinitely
+narrow) performed best.  This is because, when every timepoint's
+correlations are independent of the correlations in every other
+timepoint, averaging data over time dilutes the available signal.
+\textbf{TODO: Say something about kernel widths within a shape.}
+
+\subsection*{Cognitively relevant dynamic high-order correlations in
+  fMRI data}
+We used across-participant temporal decoders to identify cognitively
+relevant neural patterns in fMRI data (see \textit{Forward inference
+  and decoding accuracy}).  The dataset we examined~\citep[collected
+by][]{SimoEtal16} comprised four experimental conditions that exposed
+participants to stimuli that varied systematically in how cognitively
+engaging they were.  The \textit{intact} experimental condition had
+participants listen to an audio recording of a 10-minute story.  The
+\textit{paragraph}-scrambled experimental condition had participants
+listen to a temporally scrambled version of the story, where the
+paragraphs occurred out of order (but where the same total set of
+paragraphs were presented over the full listening interval).  All
+participants in this condition experienced the scrambled paragraphs in
+the same order.  The \textit{word}-scrambled experimental condition
+had participants listen to a temporally scrambled version of the story
+where the words in the story occurred in a random order.  All
+participants in the word conditions experienced the scrambled words in
+the same order.  Finally, in a \textit{rest} experimental condition
+participants lay in the scanner with no overt stimulus, with their
+eyes open (blinking as needed).  This dataset provided a convenient
+means of testing our hypothesis that different levels of cognitive
+engagement might be supported by different orders of complex brain
+activity dynamics.
+
+In brief, we computed timeseries of dynamic high-order correlations
+that were similar across participants in each of two randomly assigned
+groups: a training group and a test group.  We then trained
+classifiers on the training group's data to match each sample from the
+test group with a stimulus timepoint.  Each classifier comprised a
+weighted blend of neural patterns that reflected up to
+$n^\mathrm{th}$-order dynamic correlations (see \textit{Feature
+  weighting and testing}).  We repeated this process for
+$n \in \left\{ 0, 1, 2, ..., 10 \right\}$.  Our examinations of synthetic
+data suggested that none of the kernels we examined were ``universal''
+in the sense of optimally recovering underlying correlations
+regardless of the structure of those correlations.  In our analyses of
+neural data, we therefore averaged our decoding results over a variety
+of kernel shapes and widths in order to identify results that were
+robust to specific kernel parameters (also see \textit{Identifying
+  robust decoding results}).
+
+Our approach to estimating dynamic high-order correlations requires
+mapping the high-dimensional feature space of correlations (a $T$ by
+$\mathcal{O}(K^2)$ matrix) onto a lower-dimensional $T$ by $K$ matrix.
+We carried out two sets of analyses that differed in how this mapping
+was computed.  The first set of analyses used PCA to find a
+low-dimensional embedding of the original dynamic correlation matrices
+(Fig.~\ref{fig:decoding}a,b).  The second set of analyses
+characterized correlations in dynamics of each feature's eigenvector
+centrality, but did not preserve the underlying activity dynamics
+(Fig.~\ref{fig:decoding}c,d).
+
+\begin{figure}[hp]
+  \centering
+  \includegraphics[width=\textwidth]{figs/decode_level.pdf}
+  \caption{\textbf{Across-participant decoding accuracy varies with
+      correlation order and cognitive engagement.}
+    \textbf{a. Decoding accuracy as a function of order: PCA.} \textit{Order}
+    ($x$-axis) refers to the maximum order of dynamic correlations that were
+    available to the classifiers (see \textit{Feature weighting and
+      testing}).  The reported across-participant decoding accuracies
+    are averaged over all kernel shapes and widths (see
+    \textit{Identifying robust decoding results}).  The $y$-values are
+    displayed relative to chance accuracy.    The error bars
+    denote 95\% confidence intervals across cross-validation folds
+    (i.e., random assignments of participants to the training and test
+    sets).  The colors denote the experimental condition.  Arrows
+    denote sets of features that yielded reliably higher (upwards
+    facing) or lower (downward facing) decoding accuracy than the mean
+    of all other features (via a two-tailed test, thresholded at $p <
+    0.05$).  The circled values represent the maximum decoding
+    accuracy within each experimental condition.
+    \textbf{b. Normalized decoding accuracy as a function of order: PCA.}
+    This panel displays the same results as Panel a, but here each
+    curve has been normalized to have a maximum value of 1 and and a
+    minimum value of 0 (including the upper and lower bounds of the
+    respective 95\% confidence intervals).  Panels a and b used PCA to
+    project each high-dimensional pattern of dynamic correlations onto
+    a lower-dimensional space.  \textbf{c.  Decoding accuracy as a
+      function of order: eigenvector centrality.} This panel is in the
+    same format as Panel a, but here eigenvector centrality has been
+    used to project the high-dimensional patterns of dynamic
+    correlations onto a lower-dimensional space.
+    \textbf{d. Noramlized decoding accuracy as a function of order:
+      eigenvector centrality.} This panel is in the same format as
+    Panel b, but here eigenvector centrality has been
+    used to project the high-dimensional patterns of dynamic
+    correlations onto a lower-dimensional space.}
+  \label{fig:decoding}
 \end{figure}
@@
 % recruited episodic memory areas.
-
-\subsubsection*{Synthetic data}
-
-To assess the performance of dynamic correlation recovery using
-timecorr, we varied width the kernel and the specific structure of the
-data. We applied timecorr, using delta and gaussian kernels
-Fig.~\ref{fig:kernels}) to each of the following  
-synthetic datasets: constant, random, ramping, and block.  We then correlated each recovered
-correlation matrix with the ground truth.
-
-For the constant synthetic dataset, a gaussian kernel (width=10)
-outperformed the delta kernel (Fig.~\ref{fig:synthetic_data},  a.).  This is in contrast with the random
-synthetic dataset, for which the delta kernel best captures the
-rapidly changing structure (Fig.~\ref{fig:synthetic_data},  b.). For
-the ramping synthetic dataset, the slow changing strucutre within the
-data is best
-captured by the gaussian kernel and the best recovery occurs in the
-middle (Ramping, Fig.~\ref{fig:synthetic_data},
-c.). In addition to comparing the timecorr recovered correlation
-matrices to the ground truth, we
-further compared the ramping recovered correlation matrices to only the first random covariance matrix $K_{1}$
-(First, Fig.~\ref{fig:synthetic_data},  c.) and to only the last
-random covariance matrix $K_{2}$ (Last, Fig.~\ref{fig:synthetic_data},
-c.), both of which perform best at the beginning and end respectively.
-
-Similary for the block sythetic dataset, we compared the timecorr
-recovered correlation matrices to the ground truth as well as to each
-block-specific covariance matrix (Block 1-5,
-Fig.~\ref{fig:synthetic_data},  d.).  Although the structure is
-changing by block, the gaussian kernel once again outperforms the
-delta kernel.  Performance does however drop near even boundaries for
-when using the gaussian kernel.
-
-\begin{figure}
-  \centering
-  \includegraphics[width=\textwidth]{figs/decode_level.pdf}
-  \caption{\textbf{Decoding by order.
-      a.\&d. Relative decoding accuracy by order.} Ribbons of each
-    color display cross-validated decoding performance averaged over
-    all parameters for each condition (intact, paragraph, word,
-    and rest) using PCA (a.) or eigenvector centrality (d.) to
-    approximate correlations. Decoders were trained using increasingly more
-    higher-order information and this ribbons are displayed relative
-    to chance at 0. The red dots indicates
-    maximum decoding accuracy for each condition. \textbf{b.\&e. Z-transformed decoding accuracy
-      by order.}  We Z-transformed the decoding accuracy by order to better
-    visualize the order with the maximum decoding accuracy for each
-    condition using PCA (b.) or eigenvector centrality (e.) to
-    approximate correlations. \textbf{c.\&f. Optimized weights.} Bar heights indicate the
-    optimized mixing paramete $\phi$ of each contributing order up to
-    and including the order with the maximum
-    decoding accuracy for each contributing order using PCA (c.) or eigenvector centrality (f.) to
-    approximate correlations.
-  For the order with maximum decoding accuracy by condition, we show
-  barplots of the optimized weights $\phi$  for each contributing
-  order.}
-  \label{fig:decoding_level}
-\end{figure}
-
-We next evaluated if our model of high-order correlations in brain activity can capture cognitively relevant brain patterns.
-We performed a decoding analysis, using cross validation to estimate (using other participants’ data) which parts of the story each weighted-mixture of higher-order brain activity pattern corresponded to (see \textit{Materials and methods}).
-We note that our primary goal was not to achieve perfect decoding accuracy, but rather to use decoding accuracy as a benchmark for assessing whether different neural features specifically capture cognitively relevant brain patterns.
-
-Separately for each experimental condition, we divided participants
-into two groups. For the zeroth order, we computed the mean factor
-activity for each group.  For all subsequent orders up to the tenth
-order, we computed the mean approximated dynamic ISFC of factor
-activity for each group (see \textit{Materials and methods}), and
-combined in a weighted mixutre with all previous orders
-(i.e. cross-validation for the second
-order contained a weighted-mixture of zeroth, first, and second order
-(Fig.~\ref{fig:decoding_level}, c.\&f.).  For
-each order, we correlated the group 1 activity patterns with group 2
-activity patterns.  We then subdivided the group 1 to obtain an
-optimal weighting parameter for each order’s correlation matrix using
-the same cross validation method. We used the optimal weighting
-parameters to obtain a weighted-mixture (see \textit{Materials and methods}) of each order’s correlation
-matrix. Using these correlations, we labeled the group 1 timepoints
-using the group 2 timepoints with which they were most highly
-correlated; we then computed the proportion of correctly labeled group
-1 timepoints. (We also performed the symmetric analysis whereby we
-labeled the group 2 timepoints using the group 1 timepoints as a
-template.) We repeated this procedure 100 times (randomly re-assigning
-participants to the two groups each time) to obtain a distribution of
-decoding accuracies for each experimental condition. There were 272
-timepoints for paragraph condition, 300 timepoints for intact and word
-conditions, and 400 timepoints for rest condition,  so chance
-performance on this decoding test is was $\frac{1}{272}$,
-$\frac{1}{300}$, and $\frac{1}{400}$ respectively.
-
-We repeated this process for each set of parameters, varying kernel
-type and width, and averaged over the reduction technique used to
-approximate the higher-order correlations (PCA Fig.~\ref{fig:decoding_level},  a.-c. and eigenvector
-centrality Fig.~\ref{fig:decoding_level},  d.-f.).  Since there is no ground truth in these analyses, and we did not know
-which parameters best capture the data, we instead report a robustness
-search by averaging over the parameters and reporting which results
-consistently showed up across all parameters.
-\begin{figure}
-  \centering
-  \includegraphics[width=\textwidth]{figs/brain_plots.pdf}
-  \caption{\textbf{Average correlations by order for the intact listening condition.} Using eigenvector
-    centrality to approximate higher-order correlations for the
-    intact, paragraph scrambled, word scrambled, and rest condition.
-    We plot the
-    strongest 50\% absolute value
-    mean correlation for \textbf{a.-d. first order, e.-h. second order,
-      i.-l. third order, and m.-p. fourth order }, representing the degree of agreement by
-    location pair over time.  To demonstrate how this method is
-    computationally scalable, we also approximated
-    \textbf{a.-d. fifteenth order} dynamic correlation, which would be
-    possible to compute using conventional methods since it would require more bits to represent the solution than there are molecules in the universe.}
-  \label{fig:brain_plots}
-\end{figure}
-
-The two methods used to approximate the higher-order correlations (PCA Fig.~\ref{fig:decoding_level},  a.-c. and eigenvector
-centrality Fig.~\ref{fig:decoding_level},  d.-f.) capture different
-facets of the activity patterns.  Using PCA, the higher-order
-correlations are all linked to the original activity patterns, whereas
-eigenvectory centrality breaks the immediate link with specific brain
-areas and instead characterizes the position of the nodes in the
-network that are similar over time.
-
-We found for both PCA and eigenvector centrality, during the intact
-condition in the experiment, classifiers that incorporated
-higher-order correlations yielded consistently higher accuracy than
-classifiers trained only on lower-order patterns
-(Fig.~\ref{fig:decoding_level}, a.\&d.).  We plot the average
-correlations for up to the fourth order for the intact condition
-(Fig.~\ref{fig:brain_plots}) representing the degree of agreement by
-location pair over time.  By contrast, we found that incorporating
-higher-order (greater than first order) correlations did not further
-improve decoding accuracy for the other listening conditions or rest
-condition.  This suggests that the cognitive processing that supported
-the most cognitively rich condition involved higher-order network
-dynamics.
 

### 2019-09-03 paper/main.tex
backing up progress on results section

@@
 
+Both sets of temporal decoding analyses yielded qualitatively similar
+results for the auditory (non-rest) conditions of the experiment.  The
+highest decoding accuracy for participants who listened to the intact
+(unscrambled) story was achieved using high-order dynamic correlations (PCA:
+second-order; eigenvector-centrality: fourth-order).  Scambled
+versions of the story were best decoded by lower-order correlations
+(PCA/paragraph: first-order; PCA/word: order zero; eigenvector
+centrality/paragraph: order zero; eigenvector centrality/word: order
+zero).  The two sets of analyses yielded different results on resting
+state data (which we note could be decoded only very slightly above
+chance).  The PCA-based approach achieved the highest resting state
+decoding accuracy using order zero features (non-correlational
+activation-based), whereas the eigenvector centrality-based approach
+achieved the highest resting state decoding accuracy using
+second-order correlations.
+
 \textbf{JRM STOPPED HERE}

### 2019-09-03 paper/main.tex
backing up progress on results section: decoding results

@@
       correlation order and cognitive engagement.}
-    \textbf{a. Decoding accuracy as a function of order: PCA.} \textit{Order}
-    ($x$-axis) refers to the maximum order of dynamic correlations that were
-    available to the classifiers (see \textit{Feature weighting and
-      testing}).  The reported across-participant decoding accuracies
-    are averaged over all kernel shapes and widths (see
-    \textit{Identifying robust decoding results}).  The $y$-values are
-    displayed relative to chance accuracy.    The error bars
+    \textbf{a. Decoding accuracy as a function of order: PCA.}
+    \textit{Order} ($x$-axis) refers to the maximum order of dynamic
+    correlations that were available to the classifiers (see
+    \textit{Feature weighting and testing}).  The reported
+    across-participant decoding accuracies are averaged over all
+    kernel shapes and widths (see \textit{Identifying robust decoding
+      results}).  The $y$-values are displayed relative to chance
+    accuracy (intact: $\frac{1}{300}$; paragraph: $\frac{1}{272}$;
+    word: $\frac{1}{300}$; rest: $\frac{1}{400}$).  The error bars
     denote 95\% confidence intervals across cross-validation folds
@@
     facing) or lower (downward facing) decoding accuracy than the mean
-    of all other features (via a two-tailed test, thresholded at $p <
-    0.05$).  The circled values represent the maximum decoding
+    of all other features (via a two-tailed test, thresholded at
+    $p < 0.05$).  The circled values represent the maximum decoding
     accuracy within each experimental condition.
-    \textbf{b. Normalized decoding accuracy as a function of order: PCA.}
-    This panel displays the same results as Panel a, but here each
-    curve has been normalized to have a maximum value of 1 and and a
-    minimum value of 0 (including the upper and lower bounds of the
-    respective 95\% confidence intervals).  Panels a and b used PCA to
-    project each high-dimensional pattern of dynamic correlations onto
-    a lower-dimensional space.  \textbf{c.  Decoding accuracy as a
-      function of order: eigenvector centrality.} This panel is in the
-    same format as Panel a, but here eigenvector centrality has been
-    used to project the high-dimensional patterns of dynamic
-    correlations onto a lower-dimensional space.
+    \textbf{b. Normalized decoding accuracy as a function of order:
+      PCA.}  This panel displays the same results as Panel a, but here
+    each curve has been normalized to have a maximum value of 1 and
+    and a minimum value of 0 (including the upper and lower bounds of
+    the respective 95\% confidence intervals).  Panels a and b used
+    PCA to project each high-dimensional pattern of dynamic
+    correlations onto a lower-dimensional space.  \textbf{c.  Decoding
+      accuracy as a function of order: eigenvector centrality.} This
+    panel is in the same format as Panel a, but here eigenvector
+    centrality has been used to project the high-dimensional patterns
+    of dynamic correlations onto a lower-dimensional space.
     \textbf{d. Noramlized decoding accuracy as a function of order:
       eigenvector centrality.} This panel is in the same format as
-    Panel b, but here eigenvector centrality has been
-    used to project the high-dimensional patterns of dynamic
-    correlations onto a lower-dimensional space.}
+    Panel b, but here eigenvector centrality has been used to project
+    the high-dimensional patterns of dynamic correlations onto a
+    lower-dimensional space.}
   \label{fig:decoding}
@@
 Both sets of temporal decoding analyses yielded qualitatively similar
-results for the auditory (non-rest) conditions of the experiment.  The
-highest decoding accuracy for participants who listened to the intact
-(unscrambled) story was achieved using high-order dynamic correlations (PCA:
-second-order; eigenvector-centrality: fourth-order).  Scambled
+results for the auditory (non-rest) conditions of the experiment
+(Fig.~\ref{fig:decoding}: pink, yellow, and teal lines).  The highest
+decoding accuracy for participants who listened to the intact
+(unscrambled) story was achieved using high-order dynamic correlations
+(PCA: second-order; eigenvector-centrality: fourth-order).  Scambled
 versions of the story were best decoded by lower-order correlations
@@
 centrality/paragraph: order zero; eigenvector centrality/word: order
-zero).  The two sets of analyses yielded different results on resting
-state data (which we note could be decoded only very slightly above
-chance).  The PCA-based approach achieved the highest resting state
-decoding accuracy using order zero features (non-correlational
+zero).  The two sets of analyses yielded different decoding results on
+resting state data (Fig.~\ref{fig:decoding}: purple lines).  We note
+could be decoded only very slightly above chance; we speculate that
+the decoders might have picked up on attentional drift, boredom, or
+tiredness; we hypothesize these all increase throughought the resting
+state scan.  Our decoders might be picking up on aspects of these
+loosely defined cognitive states that are common across individuals.
+The PCA-based approach achieved the highest resting state decoding
+accuracy using order zero features (non-correlational
 activation-based), whereas the eigenvector centrality-based approach
 achieved the highest resting state decoding accuracy using
-second-order correlations.
+second-order correlations.  Taken together, these analyses indicate
+that high-level cognitive processing (while listening to the intact
+story) is reflected in the dynamics of high-order correlations in
+brain activity, whereas lower-level cognitive processing (while
+listening to scrambled versions of the story that lack rich meaning)
+is reflected in the dynamics of lower-order correlations and
+non-correlational activity dynamics.  Further, these patterns are
+associated both with the underlying activity patterns (characterized
+using PCA) and also with the changing relative positions that
+different brain areas occupy in their associated networks
+(characterized using eigenvector centrality).
 
 \textbf{JRM STOPPED HERE}
-
-% we used temporal decoders to identify cognitivly relevant neural
-% patterns in fMRI data (see forward inference section of methods).
-% we explored two approaches to effiently computing high-order
-% correlations: PCA (dimensionality reduction) and eigenvector
-% centrality (graph measure).  both approaches yielded qualitatively
-% similar results for the story listening conditions: intact story was
-% best decoded using high-order correlations, whereas scrambled
-% stories were best decoded using lower-order correlations.  both
-% approaches also yielded slightly above-chance decoding of resting state times
-% (perhaps picking up on decreasing attention and/or increasing
-% mind-wandering as the resting state scan progressed).  The PCA-based
-% approach achieved the highest decoding accuracy using
-% non-correlational (activation-based) data, whereas the eigenvector
-% centrality approach identified second-order correlations as being
-% most informative about resting state times.
 

### 2019-09-03 paper/boneyard.tex
backing up progress on results section: decoding results
finished pass through results section

@@
+% finally, we sought to identify which specific brain areas were
+% involved in supporting cognition through high-order interactions.
+% we used the eigenvector centrality results, which preserves the
+% original feature space when characterizing high-order dynamic
+% correlations.  we found that first and second-order correlations
+% reflected auditory and speech processing in all of the story
+% listening conditions.  during intact story listening, third order
+% correlations reflected integration with visual areas, and fourth
+% order correlations recruited high-level cognition regions.  however,
+% during listening to temporally scrambled stories, these higher-order
+% correlations did not involve visual areas or high-order cognitive
+% control regions.  during rest we found a much different set of
+% patterns.  first order correlations involved counting networks; second-order
+% correlations recruited visual networks; third-order correlations
+% recruited working memory networks; fourth-order correlations
+% recruited episodic memory areas.
+
+\subsubsection*{Reverse inference}
+The dynamic patterns we examine comprise high-dimensional correlation
+patterns at each timepoint.  To help interpret the resulting patterns
+in the context of other studies, we created summary maps by computing
+the across-timepoint average pairwise correlations at each order of
+analysis (first order, second order, etc., up to fifteenth order
+correlations).  We selected the 10 strongest (absolute value)
+correlations at each order.  Each correlation is between the dynamic
+activity patterns (or patterns of dynamic high-order correlations)
+measured at two RBF nodes (see \textit{Hierarchical Topographic Factor
+  Analysis}).  Therefore, the 10 strongest correlations involved up to
+20 RBF nodes.  Each RBF defines a spatial function whose activations
+range from 0 to 1.  We thresholded each RBF at 0.999 to construct a
+map of spherical components that denoted the endpoints of the 10
+strongest correlations.  We then carried out a meta analysis using
+Neurosynth~\citep{RubiEtal17} to identify the 10 terms most commonly
+associated with the given map.  This resulted in a set of 10 terms
+associated with the average dynamic correlation patterns at each
+order.
+
+%%%%
+For each order $n \in \{1, 2, 3, 4}$
+we used the selected kernel to compute the $(n-1)^\mathrm{th}$-order
+DISFC timeseries across all participants (for $n = 1$ we simply
+averaged the ``order 0'' activity timeseries across participants).  We
+then computed the average $n^\mathrm{th}$-order correlations (over
+time) by correlating the columns of the $(n-1)^\mathrm{th}$-order
+DISFC timeseries.  This yielded a single $K$ by $K$
+$n^\mathrm{th}$-order correlation matrix.  Separately for each
+experimental condition and order of correlations, we identified the
+endpoints of the 10 strongest (absolute value) correlations
+(Fig.~\ref{fig:neurosynth}).
+
+We used this kernel to compute 
+%%%%
+
+% we used temporal decoders to identify cognitivly relevant neural
+% patterns in fMRI data (see forward inference section of methods).
+% we explored two approaches to effiently computing high-order
+% correlations: PCA (dimensionality reduction) and eigenvector
+% centrality (graph measure).  both approaches yielded qualitatively
+% similar results for the story listening conditions: intact story was
+% best decoded using high-order correlations, whereas scrambled
+% stories were best decoded using lower-order correlations.  both
+% approaches also yielded slightly above-chance decoding of resting state times
+% (perhaps picking up on decreasing attention and/or increasing
+% mind-wandering as the resting state scan progressed).  The PCA-based
+% approach achieved the highest decoding accuracy using
+% non-correlational (activation-based) data, whereas the eigenvector
+% centrality approach identified second-order correlations as being
+% most informative about resting state times.
+
 We next evaluated if our model of high-order correlations in brain activity can capture cognitively relevant brain patterns.

### 2019-09-03 paper/main.tex
finished pass through results section

@@
   \centering
-  \includegraphics[width=\textwidth]{figs/synthetic_data.pdf}
+  \includegraphics[width=\textwidth]{figs/synthetic_data}
   \caption{\textbf{Recovering known dynamic correlations from
@@
   \centering
-  \includegraphics[width=\textwidth]{figs/decode_level.pdf}
+  \includegraphics[width=\textwidth]{figs/decode_level}
   \caption{\textbf{Across-participant decoding accuracy varies with
@@
 
+\begin{figure}[ht]
+  \centering
+  \includegraphics[width=\textwidth]{figs/most_abs}
+  \caption{\textbf{Top terms associated with the endpoints of the
+      strongest correlations.}  Each color corresponds to one order of
+    correlations, averaged across participants and time. The inflated
+    brain plots display the locations of the endpoints of the 10
+    strongest (absolute value) correlations at each order, projected
+    onto the cortical surface~\citep{CombEtal19}.  The lists of terms
+    on the right display the top five Neurosynth
+    terms~\citep{RubiEtal17} decoded from the corresponding brain maps
+    for each order.  Each row displays data from a different
+    experimental condition.  Additional maps and their corresponding
+    Neurosynth terms may be found in the \textit{Supplementary
+      materials} (intact: Figure S1; paragraph: Figure S2; word:
+    Figure S3; rest: Figure S4).}
+  \label{fig:neurosynth}
+\end{figure}
+
+Having established that patterns of high-order correlations are
+informative to decoders, we next wondered which specific networks of
+brain regions contributed most to these patterns.  As a representative
+example, we selected the kernel parameters that yielded decoding
+accuracies that best matched the average accuracies across all of the
+kernel parameters we examined.  Using Figure~\ref{decoding}c as a
+template, the best-matching kernel was a Laplace kernel with a width
+of 50 (Fig.~\ref{fig:kernels}d).  We used this kernel to compute a
+single $K$ by $K$ $n^\mathrm{th}$-order correlation matrix for each
+experimental condition, along with the Neurosynth~\citep{RubiEtal17}
+terms most highly associated with each of these matrices
+(Fig.~\ref{fig:neurosynth}; see \textit{Reverse inference}).
+
+For all of the story listening conditions (intact, paragraph, and
+word), we found that first- and second-order correlations were most
+strongly associated with auditory and speech processing.  During
+intact story listening, third-order correlations reflected integration
+with visual areas, and fourth-order correlations reflected integration
+with areas associated with high-level cognition and cognitive control,
+such as the ventrolateral prefrontal cortex.  However, during
+listening to temporally scrambled stories, these higher-order
+correlations instead involved interactions with additional regions
+associated with speech and semantic processing.  By contrast, we found
+a much different set of patterns in the resting state data.
+First-order resting state correlations were most strongly associated
+with regions involved in counting and numerical understanding.
+Second-order resting state correlations were strongest in visual
+areas; third-order correlations were strongest in task-positive areas;
+and fourth-order correlations were strongest in regions associated
+with autobiographical and episodic memory.  We carried out analogous
+analyses to create maps (and decode the top associated Neurosynth
+terms) for up to fifteenth-order correlations (Figs. S1, S2, S3, and
+S4).  Of note, examining fifteenth-order correlations between 700
+nodes using conventional methods would have required storing roughly
+$\frac{700^{2 \times 15}}{2} \approx 1.13 \times 10^{85}$ floating point
+numbers-- assuming single-precision (32 bits each), this would require
+roughly 32 times as many bits as there are molecules in the known
+universe!  Although these fifteenth-order correlations do appear
+(visually) to have some well-formed structure, we provide this latter
+example primarily as a demonstration of the efficiency and scalability
+of our approach.
+
 \textbf{JRM STOPPED HERE}
-
-% finally, we sought to identify which specific brain areas were
-% involved in supporting cognition through high-order interactions.
-% we used the eigenvector centrality results, which preserves the
-% original feature space when characterizing high-order dynamic
-% correlations.  we found that first and second-order correlations
-% reflected auditory and speech processing in all of the story
-% listening conditions.  during intact story listening, third order
-% correlations reflected integration with visual areas, and fourth
-% order correlations recruited high-level cognition regions.  however,
-% during listening to temporally scrambled stories, these higher-order
-% correlations did not involve visual areas or high-order cognitive
-% control regions.  during rest we found a much different set of
-% patterns.  first order correlations involved counting networks; second-order
-% correlations recruited visual networks; third-order correlations
-% recruited working memory networks; fourth-order correlations
-% recruited episodic memory areas.
 
@@
   \centering
-  \includegraphics[width=\textwidth]{figs/direction_of_field.pdf}
+  \includegraphics[width=\textwidth]{figs/direction_of_field}
   \caption{\textbf{Direction of the field (adapted from~\citep{Turk13}).} The evolution of fMRI analyses started with

### 2019-09-03 paper/main.tex
minor typo fixes

@@
 Studies of the neural code to date have primarily focused on
-univariate or multivariate neural patterns~\cite[for review
-see][NormEtal06], or (more recently) on patterns of dynamic
+univariate or multivariate neural patterns~\citep[for review
+see][]{NormEtal06}, or (more recently) on patterns of dynamic
 first-order correlations~\citep[i.e., interactions between pairs of

### 2019-09-04 paper/main.tex
updated cartoon brains figure

@@
 structures~\citep{SporHone06, BassEtal06, Turk13, DemeEtal19}.
+
+\begin{figure}[tp]
+  \centering
+  \includegraphics[width=0.65\textwidth]{figs/direction_of_field}
+  \caption{\textbf{Neural patterns.} The evolution of fMRI analyses started with
+    univariate activation, which refers to
+    the average amplitude of BOLD activity evoked by events of an
+    experimental condition. Next, multivariate classifiers are trained
+    on patterns of activation across voxels to decode distributed
+    representations for specific events. The next, resting
+    connectivity, is the temporal correlation of one or more seed
+    regions with the remainder of the brain during rest. Additionally,
+    task-based connectivity examines how these correlations differ by
+    cognitive state. Following this increasing trajectory of
+    increasing complexity, full connectivity considers all pairwise
+    correlations in the brain, most commonly at rest.  Next, dynamic
+    full connectivity considers how full connectivity changes over
+    time. Continuing this line of reasoning, we expect higher-order network dynamics might provide even richer insights into the neural basis of cognition.}
+  \label{fig:direction_of_field}
+\end{figure}
 
@@
 
-\begin{figure}[hp]
+\begin{figure}[tp]
   \centering
@@
 
-\begin{figure}[ht]
+\begin{figure}[tp]
   \centering
@@
 
-\begin{figure}
-  \centering
-  \includegraphics[width=\textwidth]{figs/direction_of_field}
-  \caption{\textbf{Direction of the field (adapted from~\citep{Turk13}).} The evolution of fMRI analyses started with
-    univariate activation, which refers to
-    the average amplitude of BOLD activity evoked by events of an
-    experimental condition. Next, multivariate classifiers are trained
-    on patterns of activation across voxels to decode distributed
-    representations for specific events. The next, resting
-    connectivity, is the temporal correlation of one or more seed
-    regions with the remainder of the brain during rest. Additionally,
-    task-based connectivity examines how these correlations differ by
-    cognitive state. Following this increasing trajectory of
-    increasing complexity, full connectivity considers all pairwise
-    correlations in the brain, most commonly at rest.  Next, dynamic
-    full connectivity considers how full connectivity changes over
-    time. Continuing this line of reasoning, we expect higher-order network dynamics might provide even richer insights into the neural basis of cognition.}
-  \label{fig:direction_of_field}
-\end{figure}
-
 Based on prior work ~\citep{DemeEtal19} and following the direction of the field ~\citep{Turk13} we think our thoughts might be encoded in

### 2019-09-04 paper/main.tex
moved patterns figure to intro

@@
   HuthEtal16}.  Training decoding models on different types of neural
-features can also help to elucidate which specific aspects of neural
-activity patterns are informative about cognition-- and, by extension,
-which types of neural activity patterns might comprise the neural
-code.  For example, prior work has used region of interest analyses to
-estimate the anatomical locations of specific neural
-representations~\citep[e.g.,][]{EtzeEtal09}, or to compare the
-relative contributions to the neural code of multivariate activity
-patterns versus patterns of dynamic correlations between neural
-activity patterns~\citep[e.g.,][]{MannEtal18, FongEtal19}.  An
+features (Fig.~\ref{fig:patterns}a) can also help to elucidate which
+specific aspects of neural activity patterns are informative about
+cognition-- and, by extension, which types of neural activity patterns
+might comprise the neural code.  For example, prior work has used
+region of interest analyses to estimate the anatomical locations of
+specific neural representations~\citep[e.g.,][]{EtzeEtal09}, or to
+compare the relative contributions to the neural code of multivariate
+activity patterns versus patterns of dynamic correlations between
+neural activity patterns~\citep[e.g.,][]{MannEtal18, FongEtal19}.  An
 emerging theme in this literature is that cognition is mediated by
@@
   \centering
-  \includegraphics[width=0.65\textwidth]{figs/direction_of_field}
-  \caption{\textbf{Neural patterns.} The evolution of fMRI analyses started with
-    univariate activation, which refers to
-    the average amplitude of BOLD activity evoked by events of an
-    experimental condition. Next, multivariate classifiers are trained
-    on patterns of activation across voxels to decode distributed
-    representations for specific events. The next, resting
-    connectivity, is the temporal correlation of one or more seed
-    regions with the remainder of the brain during rest. Additionally,
-    task-based connectivity examines how these correlations differ by
-    cognitive state. Following this increasing trajectory of
-    increasing complexity, full connectivity considers all pairwise
-    correlations in the brain, most commonly at rest.  Next, dynamic
-    full connectivity considers how full connectivity changes over
-    time. Continuing this line of reasoning, we expect higher-order network dynamics might provide even richer insights into the neural basis of cognition.}
-  \label{fig:direction_of_field}
+  \includegraphics[width=\textwidth]{figs/patterns}
+  \caption{\textbf{Neural patterns.  a. A space of neural analyses}
+    Within-brain analyses are carried out within a single brain,
+    whereas across-brain analyses compare neural patterns across two
+    or more individuals' brains.  Univariate analyses characterize the
+    activities of individual units (e.g., nodes, small networks,
+    hierarchies of networks, etc.), whereas multivariate analyses
+    characterize the patterns of activities across units.  Order 0
+    patterns involve individual nodes; order 1 patterns involve
+    node-node interactions; order 2 (and higher) patterns relate to
+    interactions between homologous networks.  Each of these patterns
+    may be static (e.g., averaging over time) or dynamic.
+    \textbf{b. Summarizing neural patterns.}  To efficiently compute
+    with complex neural patterns, it can be useful to characterize the
+    patterns using summary measures.  Dimensionality reduction
+    algorithms project the patterns onto lower-dimensional spaces
+    whose dimensions reflect weighted combinations of the dimensions
+    in the original space.  Graph measures characterize each unit's
+    participation in its associated network.}
+  \label{fig:patterns}
 \end{figure}
@@
 kernel-based method for computing dynamic correlations in timeseries
-data with a dimensionality reduction step that projects the resulting
-dynamic correlations into a low-dimensional space.  We explored two
-dimensionality reduction approaches: principle components
-analysis~\citep[PCA;][]{Pear01}, which preserves an approximately invertable
-transformation back to the original data; and a second non-invertible
-algorithm that explored patterns in eigenvector
-centrality~\citep{Land95}.  This latter approach characterizes
-correlations between each feature dimension's relative
-\textit{position} in the network in favor of the specific activity
-histories of different features.
+data with a dimensionality reduction step (Fig.~\ref{fig:patterns}b)
+that projects the resulting dynamic correlations into a
+low-dimensional space.  We explored two dimensionality reduction
+approaches: principle components analysis~\citep[PCA;][]{Pear01},
+which preserves an approximately invertable transformation back to the
+original data; and a second non-invertible algorithm that explored
+patterns in eigenvector centrality~\citep{Land95}.  This latter
+approach characterizes correlations between each feature dimension's
+relative \textit{position} in the network in favor of the specific
+activity histories of different features.
 

### 2019-09-04 paper/boneyard.tex
working on discussion, added summaries of a bunch of papers

@@
+\item Discoveries:
+    \begin{itemize}
+      \item Dimensionality reduction and graph theoretic approaches
+        give different insights into the data and identify different
+        patterns as being relevant to cognition (different peak
+        orders).
+        \item An insight common to both approaches is that high-order
+          (greater than first order) dynamic correlations are
+          informative about ongoing high-level cognitive processing.
+          As the level of cognitive processing decreases, cognition is
+          reflected by lower-order correlations.
+        \item Correlations at different orders are also associated
+          with different networks of brain regions.  However, which
+          networks reflect which types of interactions depends on the
+          current task.  In general, lower order correlations during
+          auditory listening reflect processing of low-level
+          (auditory) features; mid-order correlations reflect speech
+          and linguistic processing; higher-order correlations reflect
+          across-sensory integration (e.g. ties to visual areas) and
+          cognitive control areas.  This hierarchy dissolves during
+          lower-order cognitive processing.
+      \end{itemize}
+
+      %%%%%%%
+
+Based on prior work ~\citep{DemeEtal19} and following the direction of the field ~\citep{Turk13} we think our thoughts might be encoded in
+dynamic network patterns, and possibly higher order network
+patterns (Fig.~\ref{fig:direction_of_field}). We sought to test this hypothesis by developing an approach
+to inferring high-order network dynamics from timeseries data.
+
+One challenge in studying dynamic interactions is the
+computational resources required to calculate higher-order correlations. 
+We developed a computationally tractable model of network dynamics (Fig.~\ref{fig:methods}) that takes in a feature
+timeseries and outputs approximated first-order dynamics (i.e.,
+dynamic functional correlations), second-order dynamics
+(reflecting homologous networks that dynamically form and disperse),
+and higher-order network dynamics (up to tenth-order dynamic
+correlations).
+
+We first validated our model using synthetic data, and explored how
+recovery varied with different underlying data structures and kernels.   We then 
+applied the approach to an fMRI dataset
+~\citep{SimoEtal16} in which participants listened to an audio
+recording of a story, as well as scrambled versions of the same story
+(where the scrambling was applied at different temporal scales).  We
+trained classifiers to take the output of the model and decode the
+timepoint in the story (or scrambled story) that the participants were
+listening to. We found that, during the intact listening condition in the
+experiment, classifiers that incorporated higher-order correlations
+yielded consistently higher accuracy than classifiers trained only on
+lower-order patterns (Fig.~\ref{fig:decoding_level},  a.\&d.).  By contrast, these
+higher-order correlations were not necessary to support decoding the other
+listening conditions and (minimally
+above chance) during a control rest condition.  This suggests
+that the cognitive processing that supported the most cogntively rich listening conditions
+involved second-order (or higher) network dynamics.
+
+Although we found decoding accuracy was best when incorporating
+higher-order network dynamics for all but rest
+  condition, it is unclear if this is a product of the brain or the
+  data collection technique.  It could be that the brain is
+  second-order or it could be that fMRI can
+  only reliably give second-order interactions. Exploring this method
+  with other data collection technique will be important to
+  disentangle this question.
+
+  \subsection*{Concluding remarks}
+
+How can we better understand how brain patterns change over
+time? How can we quantify the potential network dynamics that might be
+driving these changes? One way to judge the techniques of the future is
+to look at the trajectory of the fMRI field so far has taken so far
+(Fig.~\ref{fig:methods}).  The field started with 
+univariate activation, measuring the average activity for each voxel.
+Analyses of multivariate activation followed, looking at spatial patterns of
+activity over voxels. Next, correlations of activity were explored, first
+with measures like resting connectivity that take temporal correlation
+between a seed voxel and all other voxels then with full connectivty
+that measure all pairwise correlations.  Additionally, this path of increasing
+complexity also moved from static to dynamic measurements.  One
+logical next step in this trajectory would be dynamic higher-order
+correlations. We have created a method 
+to support these calculations by scalably approximating dynamic higher-order
+correlations.
+
 % finally, we sought to identify which specific brain areas were

### 2019-09-04 paper/main.tex
added discussion figure
working on discussion, added summaries of a bunch of papers

@@
 
-\textbf{JRM STOPPED HERE}
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section*{Discussion}
-
+We tested the hypothesis that high-level cognition is supported by
+high-order brain network dynamics.  We examined high-order network
+dynamics in functional neuroimaging data collected during a story
+listening experiment.  When participants listened to an auditory
+recording of the story, participants exhibited similar high-order
+brain network dynamics.  By contrast, when participants instead
+listened to temporally scrambled recordings of the story, only
+lower-order brain network dynamics were similar across participants.
+Our results indicate that higher orders of network interactions
+support higher-level aspects of cognitive processing
+(Fig.\ref{fig:discussion}).
+
+\begin{figure}[tp]
+  \centering
+  \includegraphics[width=0.6\textwidth]{figs/discussion}
+  \caption{\textbf{Proposed high-order network dynamics underlying
+      high-level cognition.}
+    Higher orders of network interactions support higher-level aspects
+    of cognitive processing.  When tasks evoke richer, deeper, and/or
+    higher-level processing, this is reflected in higher-order network
+    interactions.}
+  \label{fig:discussion}
+\end{figure}
+
+Identifying higher-order network dynamics associated with high-level
+cognition required several important methods advances.  First, we used
+kernel-based dynamic correlations to extended the notion of (static)
+inter-subject functional connectivity~\citep{SimoEtal16} to a dynamic
+measure of inter-subject functional connectivity (DISFC) that does not
+rely on sliding windows, and that may be computed at individual
+timepoints.  This allowed us to precisely characterize stimulus-evoked
+network dynamics that were similar across individuals.  Second, we
+developed a computational framework for efficiently and scalably estimating
+high-order dynamic correlations.  Our approach uses dimensionality
+reduction algorithms and graph measures to obtain low-dimensional
+embeddings of patterns of network dynamics.  Third, we developed an
+analysis framework for identifying robust decoding results by carrying
+out our analyses using a range of parameter values and then
+identifying which results were robust to specific parameter choices.
+
+Relevant literature:
 \begin{itemize}
-  \item Methods advances: kernel-based dynamic correlations, extension to
-    dynamic ISFC, efficient method for estimating high-order dynamic
-    correlations, identifying robust results by averaging
-  \item Discoveries:
-    \begin{itemize}
-      \item Dimensionality reduction and graph theoretic approaches
-        give different insights into the data and identify different
-        patterns as being relevant to cognition (different peak
-        orders).
-        \item An insight common to both approaches is that high-order
-          (greater than first order) dynamic correlations are
-          informative about ongoing high-level cognitive processing.
-          As the level of cognitive processing decreases, cognition is
-          reflected by lower-order correlations.
-        \item Correlations at different orders are also associated
-          with different networks of brain regions.  However, which
-          networks reflect which types of interactions depends on the
-          current task.  In general, lower order correlations during
-          auditory listening reflect processing of low-level
-          (auditory) features; mid-order correlations reflect speech
-          and linguistic processing; higher-order correlations reflect
-          across-sensory integration (e.g. ties to visual areas) and
-          cognitive control areas.  This hierarchy dissolves during
-          lower-order cognitive processing.
+\item \cite{SoloEtal19}: more complex concepts involve more complex network
+dynamics
+
+\item \cite{DemeEtal19}: human consciousness is supported by dynamic
+complex patterns of brain signal coordination.  studied the brains of
+healthy vs minimally conscious patients; conscious patients displayed
+richer and more structured patterns of network interactions
+
+\item \cite{MackEtal17}: richer task structure is supported by more complex (higher
+rank) brain patterns in the prefrontal cortex
+
+\item \cite{LuriEtal19}: review of time-varying connectivity
+
+\item \cite{FongEtal18}: higher variability in dynamic functional connectivity
+predicts worse attention.  also, dymamic functional connectivity
+improves attention predictions over static functional connectivity.
+
+\item \cite{ParkEtal17}: dynamic causal modelling: compute causal interaction
+dynamics in multivariate timeseries data.  important to consider
+causation in interpreting the direction of information flow reflected
+in the patterns we identified through our analyses.
+
+\item \cite{PretEtal17}: another review of time varying connectivity
+
+\item \cite{RoyEtal19}: memories are distributed across functionally connected
+brain areas
+
+\item \cite{FallEtal19}: the timescale of spontaneous resting state
+  fMRI increases with structural connectivity strength (in mouse and
+  human brains)
+
+\item \cite{LiegEtal19}: dynamic resting state functional connectivity best captures
+task-based phenotypes (processing speed, fluid intelligence), whereas
+static and dynamic functional connectivity equally capture
+self-reported measures like loneliness and life satisfaction.  suggest
+that different timescales of connectivity dynamics reflect different
+aspects of behavior.
+
+\item \cite{ZhenEtal19}: characterize brain connectectomes at different geometric
+scales
+
+\item \cite{McInJirs19}: neural processes reflect system interactions that occur on
+relatively low-dimensional manifolds, thereby constraining possible
+functional configurations.  (motivation for dimensionality reduction
+approach?)
+
+\item \cite{TokeSomm19}: another approach to reducing dimensionality of network
+interactions, using spectral clustering
+
+\item \cite{ZouEtal19}: another review of complex network dynamics in timeseries
+data
+
+\item \cite{ShapEtal19}: state-based analyses of network dynamics using hidden
+semi-Markov models.  could be a useful direction for extended our
+work; for example, we could define kernel functions to only integrate
+within an ``event.''  This could potentially improve resolution of
+event-specific network dynamics.
+
+\item \cite{ColeEtal19}: potential artifacts or spurious insights that affect
+standard functional connectivity analyses (not sure this applies)
+
+\item \cite{RichEtal18}: simulations for benchmarking time-varying connectivity
+methods (should we use this? seems useful! could potentially replace
+synthetic data section)
+
+\item \cite{ChanGlob09}
+
+\item \cite{SizeEtal18}
+
+\item \cite{ReimEtal17}
+
+\item \cite{GonzEtal19}
+
+\item \cite{BetzEtal19}
+
 \end{itemize}
-  \end{itemize}
-
-Based on prior work ~\citep{DemeEtal19} and following the direction of the field ~\citep{Turk13} we think our thoughts might be encoded in
-dynamic network patterns, and possibly higher order network
-patterns (Fig.~\ref{fig:direction_of_field}). We sought to test this hypothesis by developing an approach
-to inferring high-order network dynamics from timeseries data.
-
-One challenge in studying dynamic interactions is the
-computational resources required to calculate higher-order correlations. 
-We developed a computationally tractable model of network dynamics (Fig.~\ref{fig:methods}) that takes in a feature
-timeseries and outputs approximated first-order dynamics (i.e.,
-dynamic functional correlations), second-order dynamics
-(reflecting homologous networks that dynamically form and disperse),
-and higher-order network dynamics (up to tenth-order dynamic
-correlations).
-
-We first validated our model using synthetic data, and explored how
-recovery varied with different underlying data structures and kernels.   We then 
-applied the approach to an fMRI dataset
-~\citep{SimoEtal16} in which participants listened to an audio
-recording of a story, as well as scrambled versions of the same story
-(where the scrambling was applied at different temporal scales).  We
-trained classifiers to take the output of the model and decode the
-timepoint in the story (or scrambled story) that the participants were
-listening to. We found that, during the intact listening condition in the
-experiment, classifiers that incorporated higher-order correlations
-yielded consistently higher accuracy than classifiers trained only on
-lower-order patterns (Fig.~\ref{fig:decoding_level},  a.\&d.).  By contrast, these
-higher-order correlations were not necessary to support decoding the other
-listening conditions and (minimally
-above chance) during a control rest condition.  This suggests
-that the cognitive processing that supported the most cogntively rich listening conditions
-involved second-order (or higher) network dynamics.
-
-Although we found decoding accuracy was best when incorporating
-higher-order network dynamics for all but rest
-  condition, it is unclear if this is a product of the brain or the
-  data collection technique.  It could be that the brain is
-  second-order or it could be that fMRI can
-  only reliably give second-order interactions. Exploring this method
-  with other data collection technique will be important to
-  disentangle this question.
-
-  \subsection*{Concluding remarks}
-
-How can we better understand how brain patterns change over
-time? How can we quantify the potential network dynamics that might be
-driving these changes? One way to judge the techniques of the future is
-to look at the trajectory of the fMRI field so far has taken so far
-(Fig.~\ref{fig:methods}).  The field started with 
-univariate activation, measuring the average activity for each voxel.
-Analyses of multivariate activation followed, looking at spatial patterns of
-activity over voxels. Next, correlations of activity were explored, first
-with measures like resting connectivity that take temporal correlation
-between a seed voxel and all other voxels then with full connectivty
-that measure all pairwise correlations.  Additionally, this path of increasing
-complexity also moved from static to dynamic measurements.  One
-logical next step in this trajectory would be dynamic higher-order
-correlations. We have created a method 
-to support these calculations by scalably approximating dynamic higher-order
-correlations.
 

### 2019-09-04 paper/main.tex
working on discussion-- added more summaries
corrected some typos and refs

@@
 stability, intersperced with abrupt changes.  For each dataset, we
-used Equation~\ref{fig:randcorr} to generate 5 random covariance
+used Equation~\ref{eqn:randcorr} to generate 5 random covariance
 matrices.  We constructed a timeseries where each set of 60 consecutive samples
@@
 accuracies that best matched the average accuracies across all of the
-kernel parameters we examined.  Using Figure~\ref{decoding}c as a
+kernel parameters we examined.  Using Figure~\ref{fig:decoding}c as a
 template, the best-matching kernel was a Laplace kernel with a width
@@
 
-\item \cite{LuriEtal19}: review of time-varying connectivity
-
-\item \cite{FongEtal18}: higher variability in dynamic functional connectivity
+\item \cite{LuriEtal18}: review of time-varying connectivity
+
+\item \cite{FongEtal19}: higher variability in dynamic functional connectivity
 predicts worse attention.  also, dymamic functional connectivity
@@
 
-\item \cite{ParkEtal17}: dynamic causal modelling: compute causal interaction
+\item \cite{ParkEtal18b}: dynamic causal modelling: compute causal interaction
 dynamics in multivariate timeseries data.  important to consider
@@
 
-\item \cite{RichEtal18}: simulations for benchmarking time-varying connectivity
+\item \cite{ThomEtal18}: simulations for benchmarking time-varying connectivity
 methods (should we use this? seems useful! could potentially replace
@@
 
-\item \cite{ChanGlob09}
-
-\item \cite{SizeEtal18}
+\item \cite{ChanGlov10}: early citation arguing that dynamic
+  functional connectivity might contain valuable signal that is
+  different from static functional connectivity.
+
+\item \cite{SizeEtal18}:
 

### 2019-09-05 paper/main.tex
finished summarizing key papers for discussion

@@
 
-\item \cite{SizeEtal18}:
-
-\item \cite{ReimEtal17}
-
-\item \cite{GonzEtal19}
-
-\item \cite{BetzEtal19}
+\item \cite{SizeEtal18}: there are common patterns of connectivity
+  (graph measures) across people; potential citation to motivate
+  eigenvector centrality approach
+
+\item \cite{ReimEtal17}: they propose that the brain processes stimuli
+  by forming increasingly complex functional cliques and cavities;
+  good motivation for our general approach
+
+\item \cite{GonzEtal19}: dynamic functional connectivity during rest
+  is influenced by spontaneous cognitive-task-like processes.  they
+  also use low-dimensional embeddings to visualize how dynamic functional
+  connectivity during rest can reveal periods of externally imposed tasks
+
+\item \cite{BetzEtal19}: during movie watching, the brain's
+  connectivity profile dynamically reconfigures.  when ISFC is high,
+  this corresponds to times when network modularity is low and
+  connectivity between cognitive systems is high.
 

### 2019-09-05 paper/main.tex
finished draft of discussion

--- 2019-09-04 paper/main.tex
@@
 complex dynamic interactions between brain
-structures~\citep{SporHone06, BassEtal06, Turk13, DemeEtal19}.
+structures~\citep{SporHone06, BassEtal06, Turk13, DemeEtal19,
+  SoloEtal19, LuriEtal18, PretEtal17, ZouEtal19, MackEtal17}.
 
@@
 first-order correlations~\citep[i.e., interactions between pairs of
-brain structures;][]{MannEtal18, FongEtal19}.  We wondered what the
+brain structures;][]{MannEtal18, FongEtal19, LuriEtal18, PretEtal17,
+  ZouEtal19, DemeEtal19}.  We wondered what the
 future of this line of work might hold.  For example, is the neural
-code mediated by higher-order interactions between brain structures?
+code mediated by higher-order interactions between brain
+structures~\citep[e.g., see][]{ReimEtal17}?
 Second-order correlations reflect \textit{homologous} patterns of
@@
 which preserves an approximately invertable transformation back to the
-original data; and a second non-invertible algorithm that explored
-patterns in eigenvector centrality~\citep{Land95}.  This latter
-approach characterizes correlations between each feature dimension's
-relative \textit{position} in the network in favor of the specific
-activity histories of different features.
+original data~\citep[e.g., this follows related approaches taken
+by][]{McInJirs19, TokeSomm19, GonzEtal19}; and a second non-invertible
+algorithm that explored patterns in eigenvector
+centrality~\citep{Land95}.  This latter approach characterizes
+correlations between each feature dimension's relative
+\textit{position} in the network in favor of the specific activity
+histories of different features~\citep[also see][]{BetzEtal19,
+  SizeEtal18, ReimEtal17}.
 
@@
 $\tau \in \left[ -\infty, \infty \right]$ contributes to the estimated instantaneous
-correlation at time $t$ (Fig.~\ref{fig:kernels}).
+correlation at time $t$~\citep[Fig.~\ref{fig:kernels}; also see][for a
+similar approach]{AlleEtal12b}.
 \begin{figure}
@@
 neuroimaging data.  We constructed and leveraged the synthetic data to
-evaluate our general approach.  Specifically, we tested how well
+evaluate our general approach~\citep[for a related approach,
+see][]{ThomEtal18}.  Specifically, we tested how well
 Equation~\ref{eqn:timecorr} could be used to recover known dynamic
@@
 We tested the hypothesis that high-level cognition is supported by
-high-order brain network dynamics.  We examined high-order network
-dynamics in functional neuroimaging data collected during a story
-listening experiment.  When participants listened to an auditory
-recording of the story, participants exhibited similar high-order
-brain network dynamics.  By contrast, when participants instead
-listened to temporally scrambled recordings of the story, only
-lower-order brain network dynamics were similar across participants.
-Our results indicate that higher orders of network interactions
-support higher-level aspects of cognitive processing
-(Fig.\ref{fig:discussion}).
+high-order brain network dynamics~\citep[e.g., see][]{SoloEtal19,
+  ReimEtal17}.  We examined high-order network dynamics in functional
+neuroimaging data collected during a story listening experiment.  When
+participants listened to an auditory recording of the story,
+participants exhibited similar high-order brain network dynamics.  By
+contrast, when participants instead listened to temporally scrambled
+recordings of the story, only lower-order brain network dynamics were
+similar across participants.  Our results indicate that higher orders
+of network interactions support higher-level aspects of cognitive
+processing (Fig.\ref{fig:discussion}).
 
@@
 \end{figure}
+
+The notion that cognition is reflected in (and possibly mediated by)
+patterns of network dynamics has been suggested by or proposed in
+myriad empirical studies and reviews~\citep[e.g., ][]{DemeEtal19,
+  Turk13, LuriEtal18, FongEtal19, ParkEtal18b, PretEtal17,
+  RoyEtal19, LiegEtal19, ZouEtal19, ChanGlov10, GonzEtal19}.  Our
+study extends this line of work by finding cognitively relevant
+higher-order network dynamics that reflect ongoing cognition.  Our
+findings complement other work that uses graph theory and topology to
+characterize how brain networks reconifigure during
+cognition~\citep[e.g., ][]{BassEtal06, ZhenEtal19, McInJirs19,
+  TokeSomm19, SizeEtal18, ReimEtal17, BetzEtal19}.
+
+An open question not addressed by our study pertains to how different
+structures integrate incoming information with different time
+constants.  For example, one line of work suggests that the cortical
+surface comprises a structured map such that nearby brain structures
+process incoming information at similar timescales.  Low-level sensory
+areas integrate information relatively quickly, whereas higher-level
+regions integrate information relatively slowly~\citep{BaldEtal17,
+  HassEtal08, HassEtal15, HoneEtal12a, LernEtal11, LernEtal14}.  Other
+related work in human and mouse brains indicates that the temporal
+response profile of a given brain structure may relate to how strongly
+connected that structure is with other brain
+areas~\citep{FallEtal19}.  Further study is needed to understand the
+role of temporal integration at different scales of network
+interaction, and across different anatomical structures.
+
+Another potential limitation of our approach relates to recent work
+suggesting that the brain undergoes rapid state changes, for example
+across event boundaries~\citep[e.g., ][]{BaldEtal17}.
+\cite{ShapEtal19} used hidden semi-Markov models to estimate
+state-specific network dynamics.  Our general approach might be
+extended by considering putative state transitions. For example,
+rather than weighting all timepoints using a similar kernel
+(Eqn.~\ref{eqn:timecorr}), the kernel function could adapt on a
+timepoint-by-timepoint basis such that only timepoints determined to
+be in the same ``state'' were given non-zero weight.
 
@@
 
-Relevant literature:
-\begin{itemize}
-\item \cite{SoloEtal19}: more complex concepts involve more complex network
-dynamics
-
-\item \cite{DemeEtal19}: human consciousness is supported by dynamic
-complex patterns of brain signal coordination.  studied the brains of
-healthy vs minimally conscious patients; conscious patients displayed
-richer and more structured patterns of network interactions
-
-\item \cite{MackEtal17}: richer task structure is supported by more complex (higher
-rank) brain patterns in the prefrontal cortex
-
-\item \cite{LuriEtal18}: review of time-varying connectivity
-
-\item \cite{FongEtal19}: higher variability in dynamic functional connectivity
-predicts worse attention.  also, dymamic functional connectivity
-improves attention predictions over static functional connectivity.
-
-\item \cite{ParkEtal18b}: dynamic causal modelling: compute causal interaction
-dynamics in multivariate timeseries data.  important to consider
-causation in interpreting the direction of information flow reflected
-in the patterns we identified through our analyses.
-
-\item \cite{PretEtal17}: another review of time varying connectivity
-
-\item \cite{RoyEtal19}: memories are distributed across functionally connected
-brain areas
-
-\item \cite{FallEtal19}: the timescale of spontaneous resting state
-  fMRI increases with structural connectivity strength (in mouse and
-  human brains)
-
-\item \cite{LiegEtal19}: dynamic resting state functional connectivity best captures
-task-based phenotypes (processing speed, fluid intelligence), whereas
-static and dynamic functional connectivity equally capture
-self-reported measures like loneliness and life satisfaction.  suggest
-that different timescales of connectivity dynamics reflect different
-aspects of behavior.
-
-\item \cite{ZhenEtal19}: characterize brain connectectomes at different geometric
-scales
-
-\item \cite{McInJirs19}: neural processes reflect system interactions that occur on
-relatively low-dimensional manifolds, thereby constraining possible
-functional configurations.  (motivation for dimensionality reduction
-approach?)
-
-\item \cite{TokeSomm19}: another approach to reducing dimensionality of network
-interactions, using spectral clustering
-
-\item \cite{ZouEtal19}: another review of complex network dynamics in timeseries
-data
-
-\item \cite{ShapEtal19}: state-based analyses of network dynamics using hidden
-semi-Markov models.  could be a useful direction for extended our
-work; for example, we could define kernel functions to only integrate
-within an ``event.''  This could potentially improve resolution of
-event-specific network dynamics.
-
-\item \cite{ColeEtal19}: potential artifacts or spurious insights that affect
-standard functional connectivity analyses (not sure this applies)
-
-\item \cite{ThomEtal18}: simulations for benchmarking time-varying connectivity
-methods (should we use this? seems useful! could potentially replace
-synthetic data section)
-
-\item \cite{ChanGlov10}: early citation arguing that dynamic
-  functional connectivity might contain valuable signal that is
-  different from static functional connectivity.
-
-\item \cite{SizeEtal18}:
-
-\item \cite{ReimEtal17}
-
-\item \cite{GonzEtal19}
-
-\item \cite{BetzEtal19}
-
-\end{itemize}
+\subsection*{Concluding remarks}
+The complex hierarchy of dynamic interactions that underlie our
+thoughts is perhaps the greatest mystery in modern science.  Methods
+for characterizing the dynamics of high-order correlations in neural
+data provides a window into the neural basis of cognition.
+\textbf{Need a good closing sentence.}
 

### 2019-09-05 paper/main.tex
spell checked document

@@
 approaches: principle components analysis~\citep[PCA;][]{Pear01},
-which preserves an approximately invertable transformation back to the
+which preserves an approximately invertible transformation back to the
 original data~\citep[e.g., this follows related approaches taken
@@
 were included as features.  When we trained classifiers on the
-scambled stories or resting state data, only lower-order dynamic
+scrambled stories or resting state data, only lower-order dynamic
 patterns were informative to the decoders.  Taken together, our
@@
 $\mathbf{X}_n$ and the dimensionality reduction step to the resulting
-$\mathbf{Y}_{n+1}$ to estimate high-order dynamnic correlations.  Each
+$\mathbf{Y}_{n+1}$ to estimate high-order dynamic correlations.  Each
 application of these steps to a $T$ by $K$ time series $\mathbf{X}_n$
@@
   \includegraphics[width=0.4\textwidth]{figs/methods_fig}
-  \caption{\textbf{Estimating dynamnic high-order correlations.}  Given
+  \caption{\textbf{Estimating dynamic high-order correlations.}  Given
     a $T$ by $K$ matrix of multivariate timeseries data,
@@
 learning~\citep{MairEtal09a, MairEtal09b}, deep
-autoencoders~\citep{HintSala06}, among others.  While complete
+auto-encoders~\citep{HintSala06}, among others.  While complete
 characterizations of each of these algorithms is beyond the scope of
@@
 nonlinear transformations of the columns of $\mathbf{Y}_n$.  Many
-dimensionality reduction algorithms are invertable (or approximately
-invertable).  However, attempting to map a given $\mathbf{X}_n$ back
+dimensionality reduction algorithms are invertible (or approximately
+invertible).  However, attempting to map a given $\mathbf{X}_n$ back
 onto the original feature space of $\mathbf{Y}_0$ will usually require
@@
 interactions (e.g., using the above notation, an $K$ by $K$
-correlation matrix or binarized correlation matrix reconstituded from
+correlation matrix or binarized correlation matrix reconstituted from
 a single timepoint's row of $\mathbf{Y}$) and return as output a set
@@
 correlation matrix with respect to the rest of the population.  Widely
-used measures include betweeness centrality~\citep[the proportion of
+used measures include betweenness centrality~\citep[the proportion of
 shortest paths between each pair of nodes in the population that
@@
 whose underlying correlation matrices exhibited prolonged intervals of
-stability, intersperced with abrupt changes.  For each dataset, we
+stability, interspersed with abrupt changes.  For each dataset, we
 used Equation~\ref{eqn:randcorr} to generate 5 random covariance
@@
 We examined an fMRI dataset collected by \cite{SimoEtal16} that the
-authors have made publically available at
+authors have made publicly available at
 \href{http://arks.princeton.edu/ark:/88435/dsp015d86p269k}{arks.princeton.edu/ark:/88435/dsp015d86p269k}.  The dataset
@@
 The temporal decoding procedure we use to estimate which neural
-features support ongoing cognitive processing is goverened by many
+features support ongoing cognitive processing is governed by many
 parameters.  For example, Equation~\ref{eqn:timecorr} requires
@@
 the story, or underwent a resting state scan (see \textit{Functional
-  neuroimaing data collected during story listening}).  We used the
+  neuroimaging data collected during story listening}).  We used the
 relative decoding accuracies of classifiers trained on
@@
     of dynamic correlations onto a lower-dimensional space.
-    \textbf{d. Noramlized decoding accuracy as a function of order:
+    \textbf{d. Normalized decoding accuracy as a function of order:
       eigenvector centrality.} This panel is in the same format as
@@
 (unscrambled) story was achieved using high-order dynamic correlations
-(PCA: second-order; eigenvector-centrality: fourth-order).  Scambled
+(PCA: second-order; eigenvector-centrality: fourth-order).  Scrambled
 versions of the story were best decoded by lower-order correlations
@@
 the decoders might have picked up on attentional drift, boredom, or
-tiredness; we hypothesize these all increase throughought the resting
+tiredness; we hypothesize these all increase throughout the resting
 state scan.  Our decoders might be picking up on aspects of these
@@
 findings complement other work that uses graph theory and topology to
-characterize how brain networks reconifigure during
+characterize how brain networks reconfigure during
 cognition~\citep[e.g., ][]{BassEtal06, ZhenEtal19, McInJirs19,

### 2019-09-05 code/scripts/plot_15.py
WIP updates to figs

@@ -1,11 +1,13 @@
 
 import supereeg as se
 import os
-from visbrain.objects import BrainObj, SceneObj, SourceObj
+from visbrain.objects import BrainObj, SceneObj, SourceObj, ColorbarObj
 
 cmap = 'autumn_r'
 
 neurosynth_dir ='../figs/neurosynth_data'
+
+fig_dir = '../figs'
 
 bo_dir = os.path.join(neurosynth_dir, 'bos')
 
@@ -84,7 +86,7 @@ for c in conditions:
 
     sc = SceneObj(bgcolor='white', size=(1000, 1000))
 
-    CBAR_STATE = dict(cbtxtsz=12, clim=[0, 6], txtsz=10., width=.1, cbtxtsh=3.,
+    CBAR_STATE = dict(cbtxtsz=12, clim=[0, 15], txtsz=10., width=.1, cbtxtsh=3.,
                       rect=(-.3, -2., 1., 4.))
     KW = dict(title_size=14., zoom=1)
 
@@ -139,4 +141,7 @@ for c in conditions:
     b_obj_proj_right.project_sources(s_obj_all, clim=(0, 16), cmap=cmap)
     sc.add_to_subplot(b_obj_proj_right, row=0, col=3, rotate='right', use_this_cam=True)
 
-    sc.screenshot(os.path.join(n_f_dir, f'{c}_15.png'), transparent=True)
+    # cb_proj = ColorbarObj(b_obj_proj_right, cblabel='Order', **CBAR_STATE)
+    # sc.add_to_subplot(cb_proj, row=0, col=4, width_max=200)
+
+    sc.screenshot(os.path.join(fig_dir, f'{c}_15.png'), transparent=True)

### 2019-09-05 code/scripts/plot_smallest.py

@@ -1,75 +1,0 @@
-
-import supereeg as se
-import os
-from visbrain.objects import BrainObj, SceneObj, SourceObj
-
-cmap = 'winter_r'
-
-neurosynth_dir ='../figs/neurosynth_data'
-
-bo_dir = os.path.join(neurosynth_dir, 'bos')
-
-n_f_dir = os.path.join(neurosynth_dir, 'figs')
-if not os.path.exists(n_f_dir):
-    os.mkdir(n_f_dir)
-
-conditions = ['intact', 'paragraph', 'rest', 'word']
-
-for c in conditions:
-
-
-    b1 = se.load(os.path.join(bo_dir,f'{c}_1_smallest.bo'))
-    b2 = se.load(os.path.join(bo_dir,f'{c}_2_smallest.bo'))
-    b3 = se.load(os.path.join(bo_dir,f'{c}_3_smallest.bo'))
-    b4 = se.load(os.path.join(bo_dir,f'{c}_4_smallest.bo'))
-
-    data1 = b1.get_data().values.ravel()
-    xyz1 = b1.locs.values
-
-    data2 = b2.get_data().values.ravel()
-    xyz2 = b2.locs.values
-
-    data3 = b3.get_data().values.ravel()
-    xyz3 = b3.locs.values
-
-    data4 = b4.get_data().values.ravel()
-    xyz4 = b4.locs.values
-
-
-    template_brain = 'B3'
-
-    sc = SceneObj(bgcolor='white', size=(1000, 1000))
-
-    CBAR_STATE = dict(cbtxtsz=12, clim=[0, 6], txtsz=10., width=.1, cbtxtsh=3.,
-                      rect=(-.3, -2., 1., 4.))
-    KW = dict(title_size=14., zoom=1)
-
-    s_obj_1 = SourceObj('iEEG', xyz1, data=data1, cmap=cmap)
-    s_obj_1.color_sources(data=data1)
-    s_obj_2 = SourceObj('iEEG', xyz2, data=data2, cmap=cmap)
-    s_obj_2.color_sources(data=data2)
-    s_obj_3 = SourceObj('iEEG', xyz3, data=data3, cmap=cmap)
-    s_obj_3.color_sources(data=data3)
-    s_obj_4 = SourceObj('iEEG', xyz4, data=data4, cmap=cmap)
-    s_obj_4.color_sources(data=data4)
-
-    s_obj_all = s_obj_1 + s_obj_2 + s_obj_3 + s_obj_4
-
[…]

### 2019-09-05 paper/boneyard.tex

@@
 
-\subsubsection*{Timepoint decoding}
-
-Prior work has shown participants share similar neural responses to
-richly structured stimuli when compared to stimuli with less
-structure.  To assess whether the moment-by-moment higher order
-correlations were reliably preserved across participants, we used
-inter-subject functional connectivity (ISFC) to isolate the
-time-varying correlational structure (functional connectivity patterns
-that were specifically driven by the story participants listened to.
-Following the analyses conducted by (HTFA)~\cite{MannEtal18}, we first
-applied \textit{hierarchical topographic factor analysis} (HTFA) to
-the fMRI datasets to obtain a time series of 700 node activities for
-every participant.  We then computed the dynamic weighted ISFC using a
-range of kernels and widths.  Specifically, we used Gaussian, Laplace,
-and mexican hat kernels, as well as widths of 5, 10, 20, and 50.  We
-then approximated these dynamic correlation using two reduction measures, PCA and eigenvector centrality, and computed the dynamic weighted ISFC on the approximations.
-We repeated this process up to 10th order approximated correlations.
-
-To assess decoding accuracy, we randomly divided participants for each
-stimulus into training and testing groups. For the zeroth order, we
-computed the mean factor activity for each group.  For all subsequent
-orders up to the tenth order, we computed the mean approximated
-dynamic ISFC of factor activity for each group. To assess how
-additional higher-order correlations contribute to decoding accuracy,
-for each order we included a weighted-mixutre (described below) of the activity patterns of all
-previous orders.
-For each group of participants in turn, we compared these activity patterns (using Pearson correlations) to estimate the story times each pattern corresponded to.
-Specifically, we asked, for each timepoint: what are the correlations
-between the first group's and second group's activity patterns at each
-order. We note that the decoding test we used is a conservative in which we count a timepoint label as incorrect if it is not an exact match.
-
-For each order we obtained the weighted-mixture of the correlation
-matrices for the current order and all previous orders using mixing parameter, $\phi$, where $0 <\phi< 1$ reflects a
-weighted mixture of order based decoding Fig.~\ref{fig:decoding_level}
-Panel c. ). We calculated  $\phi$, by
-subdividing the training group and using the quasi-Newton method of
-Broyden, Fletcher, Goldfarb, and Shanno (BFGS ~\citep{NoceWrig06}) for optimization. We
-repeated this cross-validation process 10 times for each parameter set.
-
-\subsection*{Evaluation metrics}
-We evaluate our approach to extracting dynamic correlations and
-higher-order correlations using several metrics detailed next.  First,
-we generated synthetic data using known time-varying correlations, and
-then we evaluated the fidelity with which Equation~\ref{eqn:timecorr}
-could recover those correlations (for synthetic datasets with
-different properties, and using different kernels to define the
-weights; Fig.~\ref{fig:kernels}).  We then turned to a series of
-analyses on a (real) neuroimaging dataset where the ground truth
-correlations were \textit{not} known.  We evaluated whether the
-recovered correlations could be used to accurately label held-out
-neuroimaging data with the time at which it was collected.  We used this latter evaluations (using timepoint
-decoding) as a proxy for
-gauging how much explanatory power the recovered correlations held
-with respect to the observed data.
-
-\subsubsection*{Generating synthetic data}
-To explore recovery of a constant covariance (Fig.~\ref{fig:synthetic_data},  a.), we generated syntheic
-data sampled from a constant covariance matrix. To do this, we created one random
-covariance matrix, $K$, with 50 features, and for each of the 300 timepoints  we
-sampled from a Gaussian distribution centered on $K$.  Similarly, we generated synthetic data
-sampled from a random covariance matrix (Fig.~\ref{fig:synthetic_data}, b.) by creating a new random
-covariance matrix $K(t)$, for each of the 300 timepoints and sampled from a
-Gaussian distribution centered on $K(t)$.
-
-To generate synthetic data from a dynamically changing covariance
-matrix (Fig.~\ref{fig:synthetic_data},  c.),
-we generated two random covariance
-matrices, $K_{1}$ and $K_{2}$.  We then computed a weighted average covariance matrix
-for each of the 300 timepoint, $K(t)$, 
-by taking the linearly spaced weights ($w$) of the two random matrices, 
-\begin{align}
-K(t) = w(t) * K_{1} + (1 - w(t)) *  K_{2}, \\\label{eqn:ramping}
-\end{align}
-and for each of the 300 timepoints sampled from a
-Gaussian distribution centered on $K(t)$.
-
-Lastly, for the synthetic data containing block structure (Fig.~\ref{fig:synthetic_data},  d.), we followed the same
-process of creating synthetic data sampled from a constant covariance
-matrix (see above) but sampled from a new random covariance matrix
-after 60 consecutive timepoints.  We then pieced the blocks together
-to create a sythetic dataset with 300 total timepoints but drawn from
-5 separate covariance matrices.
-
-\subsubsection*{Recovery of ground truth parameters from synthetic
-  data}
-
-We applied timecorr, using delta and gaussian (width = 10) kernels
-Fig.~\ref{fig:kernels}) to each of these 
-synthetic datasets, then correlated each recovered
-correlation matrix with the ground truth.  We repeated this process 10
-times and explored how recovery varies
-with the kernel and the specific structure of the data. For the
-ramping synthetic dataset (Fig.~\ref{fig:synthetic_data},  c.)  and for the
-block synthetic dataset (Fig.~\ref{fig:synthetic_data},  d.)  we made further
-comparisons of the timecorr recovered correlation matrices. We
-compared the ramping recovered correlation matrices to only the first random covariance matrix $K_{1}$
-(First, Fig.~\ref{fig:synthetic_data},  c.) and to only the last
-random covariance matrix $K_{2}$ (Last, Fig.~\ref{fig:synthetic_data},
-c.) from Equation~\ref{eqn:ramping}. We also compared the block recovered correlation matrices in to
-the block specific covariance matrix (Block 1-5,
-Fig.~\ref{fig:synthetic_data},  d.).
-
 A major challenge to studying such patterns is that typically neither

### 2019-09-05 paper/main.tex
updated patterns figure, inputing notes to textt

@@
 
-\title{High-level cognition is supported by at least second order
-  dynamic correlations in neural activity patterns}
+\title{High-level cognition during story listening is reflected in
+  high-order dynamic correlations in neural activity patterns}
 
@@
   data, and we applied the approach to neuroimaging data collected as
-  human participants either listened to a ten-minute story or a
-  temporally scrambled version of the story, or underwent a resting
-  state scan.  We trained across-participants pattern classifiers to
-  decode (in held-out data) when in the session each activity snapshot
-  was collected.  We found that classifiers trained to decode from
-  high-order dynamic correlations yielded better performance on data
-  collected as participants listened to the (unscrambled) story.  By
-  contrast, classifiers trained to decode data from scrambled versions
-  of the story or during the resting state scan yielded the best
-  performance when they were trained using first-order dynamic
-  correlations or raw activity patterns.  We suggest that as our
-  thoughts become more complex, they are supported by higher-order
-  patterns of dynamic network interactions throughout the brain.
+  human participants either listened to a ten-minute story, listened
+  to a temporally scrambled version of the story, or underwent a
+  resting state scan.  We trained across-participants pattern
+  classifiers to decode (in held-out data) when in the session each
+  neural activity snapshot was collected.  We found that classifiers
+  trained to decode from high-order dynamic correlations yielded the
+  best performance on data collected as participants listened to the
+  (unscrambled) story.  By contrast, classifiers trained to decode
+  data from scrambled versions of the story or during the resting
+  state scan yielded the best performance when they were trained using
+  first-order dynamic correlations or non-correlational activity patterns.  We
+  suggest that as our thoughts become more complex, they are supported
+  by higher-order patterns of dynamic network interactions throughout
+  the brain.
 \end{abstract}
@@
 provides timepoint-by-timepoint estimates of the first-order
-correlations, second-order correlations, and so on (up to tenth-order
-correlations in this manuscript).  Our approach combines a
-kernel-based method for computing dynamic correlations in timeseries
-data with a dimensionality reduction step (Fig.~\ref{fig:patterns}b)
-that projects the resulting dynamic correlations into a
-low-dimensional space.  We explored two dimensionality reduction
-approaches: principle components analysis~\citep[PCA;][]{Pear01},
-which preserves an approximately invertible transformation back to the
-original data~\citep[e.g., this follows related approaches taken
-by][]{McInJirs19, TokeSomm19, GonzEtal19}; and a second non-invertible
-algorithm that explored patterns in eigenvector
-centrality~\citep{Land95}.  This latter approach characterizes
-correlations between each feature dimension's relative
-\textit{position} in the network in favor of the specific activity
-histories of different features~\citep[also see][]{BetzEtal19,
-  SizeEtal18, ReimEtal17}.
+correlations, second-order correlations, and so on.  Our approach
+combines a kernel-based method for computing dynamic correlations in
+timeseries data with a dimensionality reduction step
+(Fig.~\ref{fig:patterns}b) that projects the resulting dynamic
+correlations into a low-dimensional space.  We explored two
+dimensionality reduction approaches: principle components
+analysis~\citep[PCA;][]{Pear01}, which preserves an approximately
+invertible transformation back to the original data~\citep[e.g., this
+follows related approaches taken by][]{McInJirs19, TokeSomm19,
+  GonzEtal19}; and a second non-invertible algorithm that explored
+patterns in eigenvector centrality~\citep{Land95}.  This latter
+approach characterizes correlations between each feature dimension's
+relative \textit{position} in the network in favor of the specific
+activity histories of different features~\citep[also
+see][]{BetzEtal19, SizeEtal18, ReimEtal17}.
 
@@
 correlations were known.  We then applied our framework to a
-neuroimaging dataset collected as participants
-listened to either an audio recording of a ten-minute story or a
-temporally scrambled version of the story, or underwent a resting
-state scan~\citep{SimoEtal16}.  We used a subset of the data to train
+neuroimaging dataset collected as participants listened to either an
+audio recording of a ten-minute story or a temporally scrambled
+version of the story, or underwent a resting state
+scan~\citep{SimoEtal16}.  We used a subset of the data to train
 across-participant classifiers to decode listening times using a blend
 of neural features (comprising neural activity patterns, as well as
-different orders of correlations between those patterns that were
-inferred using our computational framework).  We found that both the
-PCA-based and eigenvector centrality-based approaches yielded neural
-patterns that could be used to decode accurately.  Both approaches
-also yielded the best decoding accuracy for data collected during
-(intact) story listening when high-order (PCA: second-order;
-eigenvector centrality: fourth-order) dynamic correlation patterns
-were included as features.  When we trained classifiers on the
-scrambled stories or resting state data, only lower-order dynamic
-patterns were informative to the decoders.  Taken together, our
-results indicate that high-level cognition is supported by high-order
-dynamic patterns of communication between brain structures.
+different orders of dynamic correlations between those patterns that
+were inferred using our computational framework).  We found that both
+the PCA-based and eigenvector centrality-based approaches yielded
+neural patterns that could be used to decode accurately (well above
+chance).  Both approaches also yielded the best decoding accuracy for
+data collected during (intact) story listening when high-order (PCA:
+second-order; eigenvector centrality: fourth-order) dynamic
+correlation patterns were included as features.  When we trained
+classifiers on the scrambled stories or resting state data, only
+lower-order dynamic patterns were informative to the decoders.  Taken
+together, our results indicate that high-level cognition is supported
+by high-order dynamic patterns of communication between brain
+structures.
 
@@
 $\mathbf{X}_0$ (order 0) denotes the original data and $\mathbf{X}_n$
-denotes $n^\mathrm{th}$-order dynamic correlations between the columns
-of $\mathbf{X}_0$.  Finally, we use a cross-validation--based decoding
-approach to evaluate how well information contained in a given order
-(or weighted mixture of orders) may be used to decode relevant
-cognitive states.  If including a given $\mathbf{X}_n$ in the feature
-set yields higher classification accuracy on held-out data, we
-interpret this as evidence that the given cognitive states are
-reflected in patterns of $n^\mathrm{th}$-order correlations.  All of
-the code used to produce the figures and results in this manuscript,
-along with links to the corresponding datasets, may be found at
-\href{https://github.com/ContextLab/timecorr-paper}{github.com/ContextLab/timecorr-paper}.  In addition, we have
-released a Python toolbox for computing dynamic high-order
-correlations in timeseries data; our toolbox may be found at
-\href{https://timecorr.readthedocs.io/}{timecorr.readthedocs.io}. \textbf{JRM NOTE: CHECK LINK}
+denotes (approximated) $n^\mathrm{th}$-order dynamic correlations
+between the columns of $\mathbf{X}_0$.  Finally, we use a
+cross-validation--based decoding approach to evaluate how well
+information contained in a given order (or weighted mixture of orders)
+may be used to decode relevant cognitive states.  If including a given
+$\mathbf{X}_n$ in the feature set yields higher classification
+accuracy on held-out data, we interpret this as evidence that the
+given cognitive states are reflected in patterns of
+$n^\mathrm{th}$-order correlations.  All of the code used to produce
+the figures and results in this manuscript, along with links to the
+corresponding datasets, may be found at
+\href{https://github.com/ContextLab/timecorr-paper}{github.com/ContextLab/timecorr-paper}.
+In addition, we have released a Python toolbox for computing dynamic
+high-order correlations in timeseries data; our toolbox may be found
+at
+\href{https://timecorr.readthedocs.io/}{timecorr.readthedocs.io}. \textbf{JRM
+  NOTE: CHECK LINK}
 
@@
     a $T$ by $K$ matrix of multivariate timeseries data,
-    $\mathbf{Y}_n$ (where $n \in \mathbb{N}, n \geq 0$), we use
+    $\mathbf{X}_n$ (where $n \in \mathbb{N}, n \geq 0$), we use
     Equation~\ref{eqn:timecorr} to compute a timeseries of
@@
     iteratively higher-order correlations in the data.  Note that the
-    transposes of $\mathbf{Y}_n$ and $\mathbf{X}_{n+1}$ are displayed
+    transposes of $\mathbf{X}_n$ and $\mathbf{X}_{n+1}$ are displayed
     in the figure for compactness.
@@
 \subsection*{Kernel-based approach for computing dynamic correlations}
-Given a matrix of observations, we can compute the (static)
+Given a $T$ by $K$ matrix of observations, $\mathbf{X}$, we can compute the (static)
 Pearson's correlation between any pair of columns, $\mathbf{X}(\cdot, i)$ and
@@
                                                               \frac{\sum_{t=1}^T
-                                                              \left(\mathbf{X}(t,
+                                                              \left(\bar{\mathbf{X}}(t,
                                                               i)
                                                               -
-                                                              \bar{\mathbf{X}(\cdot,
-                                                              i)}\right)
+                                                              \mathbf{X}(\cdot,
+                                                              i)\right)
                                                               \left(\mathbf{X}(t,
@@
                                                               -
-                                                              \bar{\mathbf{X}(\cdot, j)}\right)}{\sqrt{\sum_{t=1}^T
+                                                              \bar{\mathbf{X}}(\cdot, j)\right)}{\sqrt{\sum_{t=1}^T
                                                               \sigma^2_{\mathbf{X}(\cdot, i)} 
                                                               \sigma^2_{\mathbf{X}(\cdot, j)}}},~\mathrm{where}\\\label{eqn:corr}
-  \bar{\mathbf{X}(\cdot, k)} &= \sum_{t=1}^T
+  \bar{\mathbf{X}}(\cdot, k) &= \frac{1}{T}\sum_{t=1}^T
                        \mathbf{X}(t, k),~\mathrm{and}\\
-  \sigma^2_{\mathbf{X}(\cdot, k)} &= \sum_{t=1}^T \left( \mathbf{X}(t, k) -
-                            \bar{\mathbf{X}(\cdot, k)} \right)^2 
+  \sigma^2_{\mathbf{X}(\cdot, k)} &= \frac{1}{T}\sum_{t=1}^T \left( \mathbf{X}(t, k) -
+                            \bar{\mathbf{X}}(\cdot, k) \right)^2 
 \end{align}
@@
   \mathrm{timecorr}_{\kappa_t}\left(\mathbf{X}(\cdot, i), \mathbf{X}(\cdot, j)\right) &= \frac{\sum_{\tau=1}^T \left( \mathbf{X}(\tau, i) -
-                                       \widetilde{\mathbf{X}}_{\kappa_t}(i) \right)
+                                       \widetilde{\mathbf{X}}_{\kappa_t}(\cdot,
+                                                                                        i) \right)
                                  \left( \mathbf{X}(\tau, j) -
-                                        \widetilde{\mathbf{X}}_{\kappa_t}(j)\right)}
+                                        \widetilde{\mathbf{X}}_{\kappa_t}(\cdot,
+                                                                                        j)\right)}
               {\sqrt{\sum_{\tau=1}^T
@@
                                                                                         i))
-                                              \widetilde{\sigma}_{\kappa_t}^2(\mathbf{X}(\cdot, j))}},~\mathrm{where}\\\label{eqn:timecorr}
-  \widetilde{\mathbf{X}}_{\kappa_t}(t, k) &= \sum_{\tau=1}^T
+                                              \widetilde{\sigma}_{\kappa_t}^2(\mathbf{X}(\cdot, j))}},~\mathrm{where}\label{eqn:timecorr}\\
+  \widetilde{\mathbf{X}}_{\kappa_t}(t) &= \sum_{\tau=1}^T
                        \kappa_t(\tau, k)\mathbf{X}(\tau, k),\\
@@
 Here
-$\mathrm{timecorr}(\mathbf{X}(\cdot, i), \mathbf{X}(\cdot, j),
-\kappa_t)$ reflects the correlation at time $t$ between columns $i$
-and $j$ of $\mathbf{X}$, estimated using the kernel $\kappa_t$.  We
-evaluate Equation~\ref{eqn:timecorr} in turn each pair of columns in
+$\mathrm{timecorr}_{\kappa_t}(\mathbf{X}(\cdot, i), \mathbf{X}(\cdot,
+j))$ reflects the correlation at time $t$ between columns $i$ and $j$
+of $\mathbf{X}$, estimated using the kernel $\kappa_t$.  We evaluate
+Equation~\ref{eqn:timecorr} in turn each pair of columns in
 $\mathbf{X}$ and for kernels centered on each timepoint in the
@@
 dynamic correlations, $\mathbf{Y}$.  For convenience, we then reshape
-the upper triangles of each timepoint's correlation matrix into a row
-vector to obtain an equivalent $T$ by $\frac{K^2 - K}{2}$ matrix.
+the upper triangles and diagonals of each timepoint's correlation matrix into a row
+vector to obtain an equivalent $T$ by $\frac{K^2 - K}{2} + K$ matrix.
 
@@
 where $\backslash p$ denotes the set of all participants other than
-participant $p$. In this way, the $T$ by $\frac{K^2 - K}{2}$ DISFC
+participant $p$. In this way, the $T$ by $\frac{K^2 - K}{2} + K$ DISFC
 matrix $\bar{\mathbf{C}}$ provides a time-varying extension of the ISFC
@@
 
-Given a $T$ by $\frac{K^2 - K}{2}$ matrix of dynamic correlations,
+Given a $T$ by $\frac{K^2 - K}{2} + K$ matrix of dynamic correlations,
 $\mathbf{Y}_n$, we propose two general approaches to computing a $T$
@@
 
-The modern library of dimensionality reduction algorithms include
+The modern toolkit of dimensionality reduction algorithms include
 Principal Components Analysis~\citep[PCA; ][]{Pear01}, Probabilistic
@@
 Topographic Factor analysis (HTFA)~\cite{MannEtal18}, Topographic
-Latent Source Analysis (TLSA)~\cite{GersEtal11}, Dictionary
+Latent Source Analysis~\cite[TLSA; ]{GersEtal11}, Dictionary
 learning~\citep{MairEtal09a, MairEtal09b}, deep
@@
 the present manuscript, the general intuition driving these approaches
-is to compute the $T$ by $I$ matrix, $\mathbf{X}$, that is closest
-to the original $T$ by $J$ matrix, $\mathbf{Y}$, where (typically)
-$I \ll J$.  The different approaches place different constraints on
+is to compute the $T$ by $M$ matrix, $\mathbf{X}$, that is closest
+to the original $T$ by $N$ matrix, $\mathbf{Y}$, where (typically)
+$M \ll N$.  The different approaches place different constraints on
 what properties $\mathbf{X}$ must satisfy and which aspects of
@@
 
-Applying dimensionality reduction algorithms to $\mathbf{Y}$ yields a
+Applying dimensionality reduction algorithms to $\mathbf{Y}$ yields an
 $\mathbf{X}$ whose columns reflect weighted combinations (or nonlinear
@@
 (potentially recombined and transformed) mapping back to the original
-data in $\mathbf{Y}_0$.  We also explore graph measure approaches
-that forgo a preserved mapping back to the original data in favor of
-preserving each feature's relative \textit{position} in the broader
+data in $\mathbf{Y}_0$.  We also explore graph measures that instead
+characterize each feature's relative \textit{position} in the broader
 network of interactions and connections.  To illustrate the
@@
 network comprises nodes $A$, $B$, and $C$.  If $A$ and $B$ exhibit
-uncorrelated activity patterns, the functional connection between
-them will be (by definition) close to 0.  However, if $A$ and $B$ each
-interact with $C$ in similar ways, we might attempt to capture those
-similarities using a measure that reflects the how $A$ and $B$
-interact in the network.
+uncorrelated activity patterns, the functional connection
+(correlation) between them will be (by definition) close to 0.
+However, if $A$ and $B$ each interact with $C$ in similar ways, we
+might attempt to capture those similarities using a measure that
+reflects the how $A$ and $B$ interact in the network.
 
 In general, graph measures take as input a matrix of
-interactions (e.g., using the above notation, an $K$ by $K$
+interactions (e.g., using the above notation, a $K$ by $K$
 correlation matrix or binarized correlation matrix reconstituted from
@@
 shortest paths between each pair of nodes in the population that
-involves the given node in question; e.g., ][]{Newm05, OpsaEtal10,
+involves the given node in question; e.g.,][]{Newm05, OpsaEtal10,
   Bart04, GeisEtal08, Free77}; diversity and
 dissimilarity~\citep[characterizations of how differently connected a
-given node is from others in the population; e.g., ][]{Rao82, Lin09,
+given node is from others in the population; e.g.,][]{Rao82, Lin09,
   RicoSzei06}; Eigenvector centrality and pagerank
 centrality~\citep[measures of how influential a given node is within
-the broader network; e.g., ][]{Newm08, Bona07, LohmEtal10,
+the broader network; e.g.,][]{Newm08, Bona07, LohmEtal10,
   HaluEtal13}; transfer entropy and flow coefficients~\citep[a measure
 of how much information is flowing from a given node to other nodes in
-the network; e.g., ][]{HoneEtal07, Schr00}; $k$-coreness
+the network; e.g.,][]{HoneEtal07, Schr00}; $k$-coreness
 centrality~\citep[a measure of the connectivity of a node within its
-local sub-graph; e.g., ][]{AlvaEtal05, ChriFowl10}; within-module
+local sub-graph; e.g.,][]{AlvaEtal05, ChriFowl10}; within-module
 degree~\citep[a measure of how many connections a node has to its
-close neighbors in the network; e.g., ][]{RubiSpor10}; participation
+close neighbors in the network; e.g.,][]{RubiSpor10}; participation
 coefficient~\citep[a measure of the diversity of a node's connections
-to different sub-graphs in the network; e.g., ][]{RubiSpor10}; and
+to different sub-graphs in the network; e.g.,][]{RubiSpor10}; and
 sub-graph centrality~\citep[a measure of a node's participation in all
-of the network's sub-graphs; e.g., ][]{EstrRodr05}; among others.
+of the network's sub-graphs; e.g.,][]{EstrRodr05}; among others.
 
@@
 neuroimaging data.  We constructed and leveraged the synthetic data to
-evaluate our general approach~\citep[for a related approach,
-see][]{ThomEtal18}.  Specifically, we tested how well
+evaluate our general approach~\citep[for a related validation
+approach, see][]{ThomEtal18}.  Specifically, we tested how well
 Equation~\ref{eqn:timecorr} could be used to recover known dynamic
@@
 \subsubsection*{Synthetic data}
-We constructed a total of 40 multivariate timeseries, collectively
-reflecting a total of 4 different patterns of dynamic correlations
-(i.e., 10 datasets reflecting each type of dynamic pattern).  Each
-timeseries comprised 50 features (dimensions) that varied over 300
-timepoints.  The observations at each timepoint were drawn from a
-zero-mean multivariate Gaussian distribution with a covariance matrix
-defined for each timepoint as described below.  We drew the observations at
-each timepoint independently from the draws at all other timepoints;
-in other words, for each observation $s_t \sim
-\mathcal{N}\left(\mathbf{0}, \mathbf{\Sigma}_t\right)$ at timepoint $t$, $p(s_t) = p(s_t | p_{\backslash t})$.
+We constructed a total of 40 different multivariate timeseries,
+collectively reflecting a total of 4 qualitatively different patterns
+of dynamic correlations (i.e., 10 datasets reflecting each type of
+dynamic pattern).  Each timeseries comprised 50 features (dimensions)
+that varied over 300 timepoints.  The observations at each timepoint
+were drawn from a zero-mean multivariate Gaussian distribution with a
+covariance matrix defined for each timepoint as described below.  We
+drew the observations at each timepoint independently from the draws
+at all other timepoints; in other words, for each observation
+$s_t \sim \mathcal{N}\left(\mathbf{0}, \mathbf{\Sigma}_t\right)$ at
+timepoint $t$, $p(s_t) = p(s_t | s_{\backslash t})$.
 
@@
 were each drawn from a single (stable) Gaussian distribution.  For
-each dataset, we constructed a random covariance matrix,
+each dataset (indexed by $m$), we constructed a random covariance matrix,
 $\mathbf{\Sigma}_m$:
@@
 Following our prior related work, we used HTFA~\citep{MannEtal18} to
-derive a compact representation of the data.  In brief, this approach
-approximates the timeseries of voxel activations (44,415 voxels) using
-a much smaller number of radial basis function (RBF) nodes (in this case 700
-nodes).  This provides a convenient representation for examining
-full-brain network dynamics.  All of the analyses we carried out on
-the neuroimaging dataset were performed in this lower-dimensional
-space.  In other words, each participant's data matrix,
-$\mathbf{Y}_0$, was a number-of-timepoints by 700 matrix of
+derive a compact representation of the neuroimaging data.  In brief,
+this approach approximates the timeseries of voxel activations (44,415
+voxels) using a much smaller number of radial basis function (RBF)
+nodes~\citep[in this case, 700 nodes, as determined by an optimization
+procedure described by][]{MannEtal18}.  This provides a convenient
+representation for examining full-brain network dynamics.  All of the
+analyses we carried out on the neuroimaging dataset were performed in
+this lower-dimensional space.  In other words, each participant's data
+matrix, $\mathbf{X}_0$, was a number-of-timepoints by 700 matrix of
 HTFA-derived factor weights (where the row and column labels were
@@
 people.  The approach entails using a subset of the data to train a
-classifier to decode which stimulus timepoint (i.e., moment in the
-story participants listened to).  We use decoding (forward inference)
-accuracy on held-out data, from held-out participants, as a proxy for
-the extent to which the inputted neural patterns reflected
-stimulus-driven cognitive processing in a similar way across
-individuals.
+classifier to decode stimulus timepoints (i.e., moment in the story
+participants listened to) from neural patterns.  We use decoding
+(forward inference) accuracy on held-out data, from held-out
+participants, as a proxy for the extent to which the inputted neural
+patterns reflected stimulus-driven cognitive processing in a similar
+way across individuals.
 
@@
 template group, while the columns reflected timepoints from the
-to-be-decoded group.  We assigned temporal labels to each row
-$\bar{\textbf{C}}_{\mathrm{decode}}$ using the row of
-$\bar{\textbf{C}}_{\mathrm{template}}$ to which it was most highly
+to-be-decoded group.  We used $\mathbf{\Lambda}$ to assign temporal
+labels to each row $\bar{\textbf{C}}_{\mathrm{decode}}$ using the row
+of $\bar{\textbf{C}}_{\mathrm{template}}$ to which it was most highly
 correlated.  We then repeated this decoding procedure, but using
@@
 \textit{decoding accuracy} as the proportion of correctly decoded
-timepoints, across both groups.
+timepoints, across both groups.  We defined the \textit{relative
+  decoding accuracy} as the difference between the decoding accuracy
+and chance accuracy (i.e., $\frac{1}{T}$).
 
@@
 dynamic correlations) were informative to the temporal decoders.
-Using the notation above, these features correspond to $\mathbf{Y}_0$,
+Using the notation above, these features correspond to $\mathbf{X}_0$,
 $\mathbf{X}_1$, $\mathbf{X}_2$, $\mathbf{X}_3$, and so on (we examined
@@
 ($\mathbf{X}_1, \mathbf{X}_2, ..., \mathbf{X}_{n-1}$).  We then used a
-(potentially wider, as described below) kernel to compute $\mathbf{X}_{n}$ from
-$\mathbf{X}_{n-1}$.  In this way, temporal blurring was applied only in the
-last step of computing $\mathbf{X}_n$.  We note that, because each
-$\mathbf{X}_n$ is a low-dimensional representation of the
-corresponding $\mathbf{Y}_n$, the higher-order correlations we
-estimated reflect true correlations in the data with lower-fidelity
-than estimates of lower-order correlations.
+new (potentially wider, as described below) kernel to compute
+$\mathbf{X}_{n}$ from $\mathbf{X}_{n-1}$.  In this way, temporal
+blurring was applied only in the last step of computing
+$\mathbf{X}_n$.  We note that, because each $\mathbf{X}_n$ is a
+low-dimensional representation of the corresponding $\mathbf{Y}_n$,
+the higher-order correlations we estimated reflect true correlations
+in the data with lower-fidelity than estimates of lower-order
+correlations.  Thefore, even after correcting for temporal blurring,
+our approach is still biased against finding meaningful signal in
+higher-order correlations.
 
@@
 $\mathcal{G}_{\mathrm{train}_1}$ and $\mathcal{G}_{\mathrm{train}_2}$.
-We then computed $\mathbf{\Lambda}$ temporal correlation matrices for
+We then computed $\mathbf{\Lambda}$ (temporal correlation) matrices for
 each type of neural feature, using $\mathcal{G}_{\mathrm{train}_1}$
@@
 $\mathcal{G}_{\mathrm{test}}$ timepoints to estimate how informative
-the set up neural features containing up to $n^\mathrm{th}$ order
+the set of neural features containing up to $n^\mathrm{th}$ order
 correlations were.
 
-We used a permutation-based procedure to form a stable estimate of
+We used a permutation-based procedure to form stable estimates of
 decoding accuracy for each set of neural features.  In particular, we
@@
 $\mathcal{G}_{\mathrm{train}}$ and $\mathcal{G}_{\mathrm{test}}$.  We
-report the mean accuracy (and 95\% confidence intervals) for each set
+report the mean accuracy (along with 95\% confidence intervals) for each set
 of neural features.
@@
 The temporal decoding procedure we use to estimate which neural
-features support ongoing cognitive processing is governed by many
-parameters.  For example, Equation~\ref{eqn:timecorr} requires
+features support ongoing cognitive processing is governed by several
+parameters. In particular, Equation~\ref{eqn:timecorr} requires
 defining a kernel function, which can take on different shapes and
@@
 accuracies across all of these parameter choices.  This enabled us to
-(roughly) factor out performance characteristics that were parameter
-dependent (within the space of parameters we examined).
+(partially) factor out performance characteristics that were
+parameter-dependent, within the set of parameters we examined.
 
 \subsubsection*{Reverse inference}
-The dynamic patterns we examine comprise high-dimensional correlation
+The dynamic patterns we examined comprise high-dimensional correlation
 patterns at each timepoint.  To help interpret the resulting patterns
@@
 the across-timepoint average pairwise correlations at each order of
-analysis (first order, second order, etc., up to fifteenth order
-correlations).  We selected the 10 strongest (absolute value)
-correlations at each order.  Each correlation is between the dynamic
-activity patterns (or patterns of dynamic high-order correlations)
-measured at two RBF nodes (see \textit{Hierarchical Topographic Factor
-  Analysis}).  Therefore, the 10 strongest correlations involved up to
-20 RBF nodes.  Each RBF defines a spatial function whose activations
-range from 0 to 1.  We thresholded each RBF at 0.999 to construct a
-map of spherical components that denoted the endpoints of the 10
-strongest correlations.  We then carried out a meta analysis using
+analysis (first order, second order, etc.).  We selected the 10
+strongest (absolute value) correlations at each order.  Each
+correlation is between the dynamic activity patterns (or patterns of
+dynamic high-order correlations) measured at two RBF nodes (see
+\textit{Hierarchical Topographic Factor Analysis}).  Therefore, the 10
+strongest correlations involved up to 20 RBF nodes.  Each RBF defines
+a spatial function whose activations range from 0 to 1.  We
+thresholded each RBF at 0.999 to construct a map of spherical
+components that denoted the endpoints of the 10 strongest
+correlations.  We then carried out a meta analysis using
 Neurosynth~\citep{RubiEtal17} to identify the 10 terms most commonly
 associated with the given map.  This resulted in a set of 10 terms
-associated with the average dynamic correlation patterns at each order.
+associated with the average dynamic correlation patterns at each
+order.
 
@@
 participants in the word conditions experienced the scrambled words in
-the same order.  Finally, in a \textit{rest} experimental condition
+the same order.  Finally, in a \textit{rest} experimental condition,
 participants lay in the scanner with no overt stimulus, with their
@@
 means of testing our hypothesis that different levels of cognitive
-engagement might be supported by different orders of complex brain
+processing and engagement are supported by different orders of brain
 activity dynamics.
@@
   weighting and testing}).  We repeated this process for
-$n \in \left\{ 0, 1, 2, ..., 10 \right\}$.  Our examinations of synthetic
-data suggested that none of the kernels we examined were ``universal''
-in the sense of optimally recovering underlying correlations
-regardless of the structure of those correlations.  In our analyses of
-neural data, we therefore averaged our decoding results over a variety
-of kernel shapes and widths in order to identify results that were
-robust to specific kernel parameters (also see \textit{Identifying
-  robust decoding results}).
-
-Our approach to estimating dynamic high-order correlations requires
+$n \in \left\{ 0, 1, 2, ..., 10 \right\}$.  Our examinations of
+synthetic data suggested that none of the kernels we examined were
+``universal'' in the sense of optimally recovering underlying
+correlations regardless of the structure of those correlations.  We
+found a similar pattern in the (real) fMRI data, whereby different
+kernels yielded different decoding accuracies, but no single kernel
+emerged as the clear ``best.''  In our analyses of neural data, we
+therefore averaged our decoding results over a variety of kernel
+shapes and widths in order to identify results that were robust to
+specific kernel parameters (see \textit{Identifying robust
+  decoding results}).
+
+Our approach to estimating dynamic high-order correlations entails
 mapping the high-dimensional feature space of correlations (a $T$ by
@@
 resting state data (Fig.~\ref{fig:decoding}: purple lines).  We note
-could be decoded only very slightly above chance; we speculate that
-the decoders might have picked up on attentional drift, boredom, or
-tiredness; we hypothesize these all increase throughout the resting
-state scan.  Our decoders might be picking up on aspects of these
-loosely defined cognitive states that are common across individuals.
-The PCA-based approach achieved the highest resting state decoding
-accuracy using order zero features (non-correlational
-activation-based), whereas the eigenvector centrality-based approach
-achieved the highest resting state decoding accuracy using
-second-order correlations.  Taken together, these analyses indicate
-that high-level cognitive processing (while listening to the intact
-story) is reflected in the dynamics of high-order correlations in
-brain activity, whereas lower-level cognitive processing (while
-listening to scrambled versions of the story that lack rich meaning)
-is reflected in the dynamics of lower-order correlations and
-non-correlational activity dynamics.  Further, these patterns are
-associated both with the underlying activity patterns (characterized
-using PCA) and also with the changing relative positions that
-different brain areas occupy in their associated networks
-(characterized using eigenvector centrality).
+that the resting state times could be decoded reliably, but only very
+slightly above chance; we speculate that the decoders might have
+picked up on attentional drift, boredom, or tiredness; we hypothesize
+these all increase throughout the resting state scan.  Our decoders
+might be picking up on aspects of these loosely defined cognitive
+states that are common across individuals.  The PCA-based approach
+achieved the highest resting state decoding accuracy using order zero
+features (non-correlational activation-based), whereas the eigenvector
+centrality-based approach achieved the highest resting state decoding
+accuracy using second-order correlations.  Taken together, these
+analyses indicate that high-level cognitive processing (while
+listening to the intact story) is reflected in the dynamics of
+high-order correlations in brain activity, whereas lower-level
+cognitive processing (while listening to scrambled versions of the
+story that lack rich meaning) is reflected in the dynamics of
+lower-order correlations and non-correlational activity dynamics.
+Further, these patterns are associated both with the underlying
+activity patterns (characterized using PCA) and also with the changing
+relative positions that different brain areas occupy in their
+associated networks (characterized using eigenvector centrality).
 
@@
 patterns of network dynamics has been suggested by or proposed in
-myriad empirical studies and reviews~\citep[e.g., ][]{DemeEtal19,
+myriad empirical studies and reviews~\citep[e.g.,][]{DemeEtal19,
   Turk13, LuriEtal18, FongEtal19, ParkEtal18b, PretEtal17,
@@
 characterize how brain networks reconfigure during
-cognition~\citep[e.g., ][]{BassEtal06, ZhenEtal19, McInJirs19,
+cognition~\citep[e.g.,][]{BassEtal06, ZhenEtal19, McInJirs19,
   TokeSomm19, SizeEtal18, ReimEtal17, BetzEtal19}.
@@
 suggesting that the brain undergoes rapid state changes, for example
-across event boundaries~\citep[e.g., ][]{BaldEtal17}.
+across event boundaries~\citep[e.g.,][]{BaldEtal17}.
 \cite{ShapEtal19} used hidden semi-Markov models to estimate

### 2019-09-05 paper/main.tex
copied newest content
finished first pass of edits

@@
 in the data with lower-fidelity than estimates of lower-order
-correlations.  Thefore, even after correcting for temporal blurring,
+correlations.  Therefore, even after correcting for temporal blurring,
 our approach is still biased against finding meaningful signal in
@@
 resting state data (Fig.~\ref{fig:decoding}: purple lines).  We note
-that the resting state times could be decoded reliably, but only very
-slightly above chance; we speculate that the decoders might have
-picked up on attentional drift, boredom, or tiredness; we hypothesize
-these all increase throughout the resting state scan.  Our decoders
-might be picking up on aspects of these loosely defined cognitive
-states that are common across individuals.  The PCA-based approach
-achieved the highest resting state decoding accuracy using order zero
-features (non-correlational activation-based), whereas the eigenvector
-centrality-based approach achieved the highest resting state decoding
-accuracy using second-order correlations.  Taken together, these
-analyses indicate that high-level cognitive processing (while
-listening to the intact story) is reflected in the dynamics of
-high-order correlations in brain activity, whereas lower-level
-cognitive processing (while listening to scrambled versions of the
-story that lack rich meaning) is reflected in the dynamics of
-lower-order correlations and non-correlational activity dynamics.
-Further, these patterns are associated both with the underlying
-activity patterns (characterized using PCA) and also with the changing
-relative positions that different brain areas occupy in their
-associated networks (characterized using eigenvector centrality).
+that while the resting state times could be decoded reliably, the
+accuracies were only very slightly above chance.  We speculate that
+the decoders might have picked up on attentional drift, boredom, or
+tiredness; we hypothesize these all increase throughout the resting
+state scan.  The decoders might be picking up on aspects of these
+loosely defined cognitive states that are common across individuals.
+The PCA-based approach achieved the highest resting state decoding
+accuracy using order zero features (non-correlational,
+activation-based), whereas the eigenvector centrality-based approach
+achieved the highest resting state decoding accuracy using
+second-order correlations.  Taken together, these analyses indicate
+that high-level cognitive processing (while listening to the intact
+story) is reflected in the dynamics of high-order correlations in
+brain activity, whereas lower-level cognitive processing (while
+listening to scrambled versions of the story that lack rich meaning)
+is reflected in the dynamics of lower-order correlations and
+non-correlational activity dynamics.  Further, these patterns are
+associated both with the underlying activity patterns (characterized
+using PCA) and also with the changing relative positions that
+different brain areas occupy in their associated networks
+(characterized using eigenvector centrality).
 
@@
 word), we found that first- and second-order correlations were most
-strongly associated with auditory and speech processing.  During
+strongly associated with auditory and speech processing areas.  During
 intact story listening, third-order correlations reflected integration
@@
 nodes using conventional methods would have required storing roughly
-$\frac{700^{2 \times 15}}{2} \approx 1.13 \times 10^{85}$ floating point
-numbers-- assuming single-precision (32 bits each), this would require
-roughly 32 times as many bits as there are molecules in the known
-universe!  Although these fifteenth-order correlations do appear
+$\frac{700^{2 \times 15}}{2} \approx 1.13 \times 10^{85}$ floating
+point numbers-- assuming single-precision (32 bits each), this would
+require roughly 32 times as many bits as there are molecules in the
+known universe!  Although these fifteenth-order correlations do appear
 (visually) to have some well-formed structure, we provide this latter
@@
   \caption{\textbf{Proposed high-order network dynamics underlying
-      high-level cognition.}
-    Higher orders of network interactions support higher-level aspects
-    of cognitive processing.  When tasks evoke richer, deeper, and/or
-    higher-level processing, this is reflected in higher-order network
+      high-level cognition during story listening.}  Higher orders of
+    network interactions support higher-level aspects of cognitive
+    processing.  When tasks evoke richer, deeper, and/or higher-level
+    processing, this is reflected in higher-order network
     interactions.}
@@
 study extends this line of work by finding cognitively relevant
-higher-order network dynamics that reflect ongoing cognition.  Our
+\textit{higher-order} network dynamics that reflect ongoing cognition.  Our
 findings complement other work that uses graph theory and topology to
@@
 \cite{ShapEtal19} used hidden semi-Markov models to estimate
-state-specific network dynamics.  Our general approach might be
-extended by considering putative state transitions. For example,
-rather than weighting all timepoints using a similar kernel
-(Eqn.~\ref{eqn:timecorr}), the kernel function could adapt on a
-timepoint-by-timepoint basis such that only timepoints determined to
-be in the same ``state'' were given non-zero weight.
+state-specific network dynamics~\citep[also see][]{VidaEtal18}.  Our
+general approach might be extended by considering putative state
+transitions. For example, rather than weighting all timepoints using a
+similar kernel (Eqn.~\ref{eqn:timecorr}), the kernel function could
+adapt on a timepoint-by-timepoint basis such that only timepoints
+determined to be in the same ``state'' were given non-zero weight.
 
@@
 for characterizing the dynamics of high-order correlations in neural
-data provides a window into the neural basis of cognition.
-\textbf{Need a good closing sentence.}
+data provides a window into the neural basis of cognition.  By showing
+that high-level cognition is reflected in high-order network dynamics
+we have elucidated the next step on the path towards understanding the
+neural basis of cognition.
 

### 2019-09-05 paper/main.tex
update main.txt to current version
added aaron to acknowledgements

@@
 We acknowledge discussions with Luke Chang, Hany Farid, Paxton
-Fitzpatrick, Andrew Heusser, Eshin Jolly, Qiang Liu, Matthijs van der
-Meer, Judith Mildner, Gina Notaro, Stephen Satterthwaite, Emily
-Whitaker, Weizhen Xie, and Kirsten Ziman. Our work was supported in
-part by NSF EPSCoR Award Number 1632738 to J.R.M. and by a sub-award
-of DARPA RAM Cooperative Agreement N66001-14-2-4-032 to J.R.M.  The
-content is solely the responsibility of the authors and does not
-necessarily represent the official views of our supporting
-organizations.
+Fitzpatrick, Andrew Heusser, Eshin Jolly, Aaron Lee, Qiang Liu,
+Matthijs van der Meer, Judith Mildner, Gina Notaro, Stephen
+Satterthwaite, Emily Whitaker, Weizhen Xie, and Kirsten Ziman. Our
+work was supported in part by NSF EPSCoR Award Number 1632738 to
+J.R.M. and by a sub-award of DARPA RAM Cooperative Agreement
+N66001-14-2-4-032 to J.R.M.  The content is solely the responsibility
+of the authors and does not necessarily represent the official views
+of our supporting organizations.
 

### 2019-09-05 paper/main.tex
updated text with tentative (predicted) synthetic data results in bold

@@
     Error ribbons denote 95\% confidence intervals (taken across
-    datasets). Different colors denote different kernel shapes,
-    whereas the shading within each color type denotes kernel widths.
-    For a complete description of each synthetic dataset, see
-    \textit{Synthetic data}.  \textbf{a. Constant correlations.} These
-    datasets have a stable (unchanging) underlying correlation matrix.
-    \textbf{b. Random correlations.}  These datasets are generated
-    using a new independently drawn correlation matrix at each new
-    timepoint.  \textbf{c. Ramping correlations.}  These datasets are
-    generated by smoothly varying the underlying correlations between
-    the randomly drawn correlation matrices at first and last
-    timepoints.  The left panel displays the correlations between the
-    recovered dynamic correlations and the underlying ground truth
-    correlations.  The middle panel compares the recovered
-    correlations with the \textit{first} timepoint's correlation
-    matrix.  The right panel compares the recovered correlations with
-    the \textit{last} timepoint's correlation matrix.
-    \textbf{d. Event-based correlations.}  These datasets are each
-    generated using five randomly drawn correlation matrices that each
-    remain stable for a fifth of the total timecourse.  The left panel
-    displays the correlations between the recovered dynamic
+    datasets). Different colors denote different kernel shapes, and
+    the shading within each color family denotes the kernel width
+    parameter.  For a complete description of each synthetic dataset,
+    see \textit{Synthetic data}.  \textbf{a. Constant correlations.}
+    These datasets have a stable (unchanging) underlying correlation
+    matrix.  \textbf{b. Random correlations.}  These datasets are
+    generated using a new independently drawn correlation matrix at
+    each new timepoint.  \textbf{c. Ramping correlations.}  These
+    datasets are generated by smoothly varying the underlying
+    correlations between the randomly drawn correlation matrices at
+    first and last timepoints.  The left panel displays the
+    correlations between the recovered dynamic correlations and the
+    underlying ground truth correlations.  The middle panel compares
+    the recovered correlations with the \textit{first} timepoint's
+    correlation matrix.  The right panel compares the recovered
+    correlations with the \textit{last} timepoint's correlation
+    matrix.  \textbf{d. Event-based correlations.}  These datasets are
+    each generated using five randomly drawn correlation matrices that
+    each remain stable for a fifth of the total timecourse.  The left
+    panel displays the correlations between the recovered dynamic
     correlations and the underlying ground truth correlations.  The
@@
 
-In general, wide monotonic kernels (Laplace, Gaussian) performed best
-when the correlations varied gradually from moment-to-moment
-(Figs.~\ref{fig:synthetic}a, c, and d).  \textbf{TODO: Say something
-  about kernel widths within a shape.}  In the extreme, as the rate of
-change in correlations approaches 0 (Fig.~\ref{fig:synthetic}a), an
-infinitely wide kernel would exactly recover the Pearson's correlation
-(e.g., compare Eqns.~\ref{eqn:corr} and \ref{eqn:timecorr}).
+In general, wide monotonic kernel shapes (Laplace, Gaussian)\textbf{, and
+wider kernels (within a shape), }performed best when the correlations
+varied gradually from moment-to-moment (Figs.~\ref{fig:synthetic}a, c,
+and d).  In the extreme, as the rate of change in correlations
+approaches 0 (Fig.~\ref{fig:synthetic}a), an infinitely wide kernel
+would exactly recover the Pearson's correlation (e.g., compare
+Eqns.~\ref{eqn:corr} and \ref{eqn:timecorr}).
 
@@
 timepoint, averaging data over time dilutes the available signal.
-\textbf{TODO: Say something about kernel widths within a shape.}
+\textbf{Following a similar patterns, holding kernel shape fixed,
+  narrower kernel parameters better recovered randomly varying
+  correlations.}
 

### 2019-09-05 paper/nature neuroscience submission/cover_letter.tex
added draft of cover letter

\title{Nature Neuroscience Submission Letter}
%
% See http://texblog.org/2013/11/11/latexs-alternative-letter-class-newlfm/
% and http://www.ctan.org/tex-archive/macros/latex/contrib/newlfm
% for more information.
%
\documentclass[11pt,stdletter,orderfromtodate,sigleft]{newlfm}
\usepackage{blindtext, xfrac, animate, hyperref, pxfonts}

  \setlength{\voffset}{0in}

\newlfmP{dateskipbefore=0pt}
\newlfmP{sigsize=20pt}
\newlfmP{sigskipbefore=10pt}

\newlfmP{Headlinewd=0pt,Footlinewd=0pt}

\namefrom{Jeremy R. Manning, Ph.D.}
\addrfrom{
	Dartmouth College\\
    Department of Psychological \& Brain Sciences\\
    HB 6207 Moore Hall\\
	Hanover, NH  03755}

\addrto{}
\dateset{\today}

\greetto{To the editors of \textit{Nature Neuroscience}:}

\closeline{Sincerely,}

\begin{document}
\begin{newlfm}
  We have enclosed our manuscript entitled \textit{High-level
    cognition during story listening is reflected in high-order
    dynamic correlations in neural activity patterns}, which we wish
  to submit for publication as a Brief Communication in \textit{Nature
    Neuroscience}.

  Our manuscript reports on a series of analyses carried out on
  neuroimaging data collected by Uri Hasson's group (Simony et al,
  2016) as participants listened to either an auditory story or a
  temporally scrambled version of the story.  We applied to this
  dataset a new computational framework for estimating high-order
  dynamic correlations that reflect ongoing cognitive processing.

  Prior work has indicated that dynamic functional (first-order)
  correlations---i.e., pairwise correlations between brain structures
  that change from moment to moment---change according to ongoing
  cognitive processes.  Our computational framework also enabled us to
  examine higher-order dynamic correlations.  For example,
  second-order correlations reflect \textit{homologous} patterns of
  correlation.  In other words, if the changing patterns of
  correlations between two regions, $A$ and $B$, are similar to those
  between two other regions, $C$ and $D$, this would be reflected in
  the second-order correlations between ($A$--$B$) and ($C$--$D$).  In
  this way, second-order correlations identify similarities and
  differences between subgraphs of the brain's connectome.
  Analogously, third-order correlations reflect homologies between
  second-order correlations-- i.e., homologous patterns of homologous
  interactions between brain regions.  More generally, higher-order
  correlations reflect homologies between patterns of lower-order
  correlations.  We can then ask: which ``orders'' of interaction are
  most reflective of high-level cognitive processes?

  When participants listened to an intact recording of the story, they
  exhibited similar (across-participants) high-order brain network
  dynamics.  These across-participant similarities are a reflection of
  the extent to which neural patterns are stimulus-driven, since the
  shared experimental stimulus was the only constant shared across
  participants.  By contrast, when participants instead listened to
  temporally scrambled recordings of the story, only lower-order brain
  network dynamics were similar across participants.  Further, the
  brain areas that mediate high-order correlations are associated with
  higher-level cognitive processes (cross-modality sensory
  integration, cognitive control, etc.), whereas low-order
  correlations and non-correlational activity dynamics most involve
  brain areas associated with lower-level cognitive processing
  (auditory processing, speech processing areas).  Our results
  indicate that higher orders of network interactions support
  higher-level aspects of cognitive processing

  In addition to the theoretical advances we report, identifying
  higher-order network dynamics associated with high-level cognition
  also required several important methods advances.  First, we used
  kernel-based dynamic correlations to extended the notion of (static)
  inter-subject functional connectivity (Simony et al., 2016) to a
  dynamic measure of inter-subject functional connectivity that does
  not rely on temporal sliding windows, and that may be computed at
  individual timepoints.  This allowed us to precisely characterize
  stimulus-evoked network dynamics that were similar across
  individuals.  Second, we developed a computational framework for
  efficiently and scalably estimating high-order dynamic correlations.
  Our approach uses dimensionality reduction algorithms and graph
  measures to obtain low-dimensional embeddings of patterns of network
  dynamics.  Third, we developed an analysis framework for identifying
  robust decoding results by carrying out our analyses using a range
  of parameter values and then identifying which results were robust
  to specific parameter choices.

  We have published and documented all of the data and analysis code
  used to generate the figures in our manuscript (link:
  \href{https://github.com/ContextLab/timecorr-paper}{github.com/ContextLab/timecorr-paper}),
  along with a concurrent release of a Python toolbox for carrying out
  analogous analyses on new datasets (link:
  \href{http://timecorr.readthedocs.io}{timecorr.readthedocs.io}).

  We have suggested the following scientists as expert reviewers:
  Richard Betzel (EMAIL), Danielle Bassett (EMAIL), Emily Finn
  (EMAIL), Olaf Sporns (EMAIL), and Christopher Honey (EMAIL).

  We note that we have included the complete methods section in the
  main text to facilitate peer review.  If deemed potentially suitable
  for publication, we will update our manuscript by moving the current
  methods section into our supporting document, and by adding a
  methods summary conforming to the Brief Communications format.
  Thank you for considering our manuscript for publication in Nature
  Neuroscience.

\end{newlfm}
\end{document}

### 2019-09-05 paper/main.tex
another pass through the text, updated patterns figure

@@
 
+\newcommand{\ttests}{S1}
+\newcommand{\intact}{S2}
+\newcommand{\para}{S3}
+\newcommand{\word}{S4}
+\newcommand{\rest}{S5}
+
 \title{High-level cognition during story listening is reflected in
@@
   College, Hanover, NH\\
-  $^3$Amazon.com, Seattle, WA\\
+  $^2$Amazon.com, Seattle, WA\\
   \textsuperscript{$\dagger$}Address correspondence to
@@
   brain structures that change with our ongoing experiences.
-  High-order dynamic correlations in brain activity patterns reflect
+  High-order dynamic correlations in neural activity patterns reflect
   different subgraphs of the brain's connectome that display
@@
 emerging theme in this literature is that cognition is mediated by
-complex dynamic interactions between brain
-structures~\citep{SporHone06, BassEtal06, Turk13, DemeEtal19,
-  SoloEtal19, LuriEtal18, PretEtal17, ZouEtal19, MackEtal17}.
+dynamic interactions between brain structures~\citep{SporHone06,
+  BassEtal06, Turk13, DemeEtal19, SoloEtal19, LuriEtal18, PretEtal17,
+  ZouEtal19, MackEtal17}.
 
@@
 brain structures;][]{MannEtal18, FongEtal19, LuriEtal18, PretEtal17,
-  ZouEtal19, DemeEtal19}.  We wondered what the
-future of this line of work might hold.  For example, is the neural
-code mediated by higher-order interactions between brain
-structures~\citep[e.g., see][]{ReimEtal17}?
-Second-order correlations reflect \textit{homologous} patterns of
-correlation.  In other words, if the changing patterns of correlations
-between two regions, $A$ and $B$, are similar to those between two
-other regions, $C$ and $D$, this would be reflected in the
-second-order correlations between ($A$--$B$) and ($C$--$D$).  In this
-way, second-order correlations identify similarities and differences
-between subgraphs of the brain's connectome.  Analogously, third-order
-correlations reflect homologies between second-order correlations--
-i.e., homologous patterns of homologous interactions between brain
-regions.  More generally, higher-order correlations reflect homologies
-between patterns of lower-order correlations.  We can then ask: which
-``orders'' of interaction are most reflective of high-level cognitive
-processes?
+  ZouEtal19, DemeEtal19}.  We wondered what the future of this line of
+work might hold.  For example, is the neural code mediated by
+higher-order interactions between brain structures~\citep[e.g.,
+see][]{ReimEtal17}?  Second-order correlations reflect
+\textit{homologous} patterns of correlation.  In other words, if the
+dynamic patterns of correlations between two regions, $A$ and $B$, are
+similar to those between two other regions, $C$ and $D$, this would be
+reflected in the second-order correlations between ($A$--$B$) and
+($C$--$D$).  In this way, second-order correlations identify
+similarities and differences between subgraphs of the brain's
+connectome.  Analogously, third-order correlations reflect homologies
+between second-order correlations-- i.e., homologous patterns of
+homologous interactions between brain regions.  More generally,
+higher-order correlations reflect homologies between patterns of
+lower-order correlations.  We can then ask: which ``orders'' of
+interaction are most reflective of high-level cognitive processes?
 
@@
 the PCA-based and eigenvector centrality-based approaches yielded
-neural patterns that could be used to decode accurately (well above
+neural patterns that could be used to decode accurately (i.e., well above
 chance).  Both approaches also yielded the best decoding accuracy for
@@
 \section*{Methods}
-Our general approach to comprises four general steps
-(Fig.~\ref{fig:methods}).  First, we derive a kernel-based approach to
-computing dynamic pairwise correlations in a $T$ (timepoints) by $K$
-(features) multivariate timeseries, $\mathbf{X}_0$.  This yields a $T$
-by $\mathcal{O}(K^2)$ matrix of dynamic correlations, $\mathbf{Y}_1$,
-where each row comprises the upper triangle of the correlation matrix
-at a single timepoint, reshaped into a row vector (this reshaped
-vector is $(\frac{K^2 - K}{2})$-dimensional).  Second, we apply a
-dimensionality reduction step to project the matrix of dynamic
-correlations back onto a $K$-dimensional space.  This yields a $T$ by
-$K$ matrix, $\mathbf{X}_1$, that reflects an approximation of the
-dynamic correlations reflected in the original data.  Third, we use
-repeated applications of the kernel-based dynamic correlation step to
+Our general approach to efficiently estimating high-order dynamic
+correlations comprises four general steps (Fig.~\ref{fig:methods}).
+First, we derive a kernel-based approach to computing dynamic pairwise
+correlations in a $T$ (timepoints) by $K$ (features) multivariate
+timeseries, $\mathbf{X}_0$.  This yields a $T$ by $\mathcal{O}(K^2)$
+matrix of dynamic correlations, $\mathbf{Y}_1$, where each row
+comprises the upper triangle and diagonal of the correlation matrix at a single
+timepoint, reshaped into a row vector (this reshaped vector is
+$\left( \frac{K^2 - K}{2} + K \right)$-dimensional).  Second, we apply a dimensionality
+reduction step to project the matrix of dynamic correlations back onto
+a $K$-dimensional space.  This yields a $T$ by $K$ matrix,
+$\mathbf{X}_1$, that reflects an approximation of the dynamic
+correlations reflected in the original data.  Third, we use repeated
+applications of the kernel-based dynamic correlation step to
 $\mathbf{X}_n$ and the dimensionality reduction step to the resulting
@@
                                                               \frac{\sum_{t=1}^T
-                                                              \left(\bar{\mathbf{X}}(t,
+                                                              \left(\mathbf{X}(t,
                                                               i)
                                                               -
-                                                              \mathbf{X}(\cdot,
+                                                              \bar{\mathbf{X}}(\cdot,
                                                               i)\right)
@@
   \includegraphics[width=\textwidth]{figs/kernels}
-  \caption{\textbf{Examples of kernel functions.} Each panel
-    displays per-timepoint weights at $t = 50$, evaluated for 100
-    timepoints ($\tau \in \left[1, ..., 100\right]$).  \textbf{a. Uniform
-      kernel.} The weights are timepoint-invariant; observations at
-    all timepoints are weighted equally, and do not change as a
-    function of $\tau$.  This is a special case of weight function that
-    reduces dynamic correlations to static correlations.
+  \caption{\textbf{Examples of kernel functions.} Each panel displays
+    per-timepoint weights for a kernel centered at $t = 50$, evaluated
+    at 100 timepoints ($\tau \in \left[1, ..., 100\right]$).
+    \textbf{a. Uniform kernel.} The weights are timepoint-invariant;
+    observations at all timepoints are weighted equally, and do not
+    change as a function of $\tau$.  This is a special case kernel
+    function that reduces dynamic correlations to static correlations.
     \textbf{b. Dirac $\delta$ kernel.} Only the observation at
     timepoint $t$ is given a non-zero weight (of 1).
-    \textbf{c. Gaussian kernels.} Each kernel's weights fall off
-    in time according to a Gaussian probability density function
-    centered on time $t$.  Weights derived using several different
-    example width parameters ($\sigma^2$) are displayed.
-    \textbf{d. Laplace kernels.}  Each kernel's weights fall off
-    in time according to a Laplace probability density function
-    centered on time $t$.  Weights derived using several different
-    example width parameters ($b$) are displayed.  \textbf{e. Mexican
-      hat (Ricker wavelet) kernels.}  Each kernel's weights fall
-    off in time according to a Ricker wavelet centered on time $t$.  This
-    function highlights the \textit{contrasts} between local versus
-    surrounding activity patterns in estimating dynamic
-    correlations. Weights derived using several different example
-    width parameters ($\sigma$) are displayed.}
+    \textbf{c. Gaussian kernels.} Each kernel's weights fall off in
+    time according to a Gaussian probability density function centered
+    on time $t$.  Weights derived using several different example
+    width parameters ($\sigma^2$) are displayed.  \textbf{d. Laplace
+      kernels.}  Each kernel's weights fall off in time according to a
+    Laplace probability density function centered on time $t$.
+    Weights derived using several different example width parameters
+    ($b$) are displayed.  \textbf{e. Mexican hat (Ricker wavelet)
+      kernels.}  Each kernel's weights fall off in time according to a
+    Ricker wavelet centered on time $t$.  This function highlights the
+    \textit{contrasts} between local versus surrounding activity
+    patterns in estimating dynamic correlations. Weights derived using
+    several different example width parameters ($\sigma$) are
+    displayed.}
   \label{fig:kernels}
@@
   \widetilde{\mathbf{X}}_{\kappa_t}(t) &= \sum_{\tau=1}^T
-                       \kappa_t(\tau, k)\mathbf{X}(\tau, k),\\
+                       \kappa_t(\tau)\mathbf{X}(\tau, k),\\
   \widetilde{\sigma}_{\kappa_t}^2(\mathbf{X}(\cdot, k)) &= \sum_{\tau=1}^T
@@
 the upper triangles and diagonals of each timepoint's correlation matrix into a row
-vector to obtain an equivalent $T$ by $\frac{K^2 - K}{2} + K$ matrix.
+vector to obtain an equivalent $T$ by $\left( \frac{K^2 - K}{2} + K \right)$ matrix.
 
@@
 \textit{inter-subject functional connectivity}~\citep[ISFC;
-][]{SimoEtal16} to compute the degree of stimulus-driven correlations
-reflected in the multi-participant dataset at a given timepoint $t$
-using:
+][]{SimoEtal16} to compute the stimulus-driven correlations reflected
+in the multi-participant dataset at a given timepoint $t$ using:
 \begin{align}
@@
 \end{align}
-and $\mathbf{Y}_n^p(t)$ denotes the correlation matrix
-(Eqn.~\ref{eqn:corr}) between each column of $\mathbf{X}_n^p$ and each
+and $\mathbf{Y}_n^p(t)$ denotes the correlation matrix at timepoint $t$
+(Eqn.~\ref{eqn:timecorr}) between each column of $\mathbf{X}_n^p$ and each
 column of the average $\mathbf{X}_n$ from all \textit{other}
@@
 where $\backslash p$ denotes the set of all participants other than
-participant $p$. In this way, the $T$ by $\frac{K^2 - K}{2} + K$ DISFC
+participant $p$. In this way, the $T$ by $\left( \frac{K^2 - K}{2} + K \right)$ DISFC
 matrix $\bar{\mathbf{C}}$ provides a time-varying extension of the ISFC
@@
 
-Given a $T$ by $\frac{K^2 - K}{2} + K$ matrix of dynamic correlations,
-$\mathbf{Y}_n$, we propose two general approaches to computing a $T$
-by $K$ low-dimensional representation of these correlations,
-$\mathbf{X}_n$.  The first approach uses dimensionality reduction
-algorithms to project $\mathbf{Y}_n$ onto a $K$-dimensional space.
-The second approach uses graph measures to characterize the
-relative positions of each feature ($k \in \left[1, ..., K \right]$)
-in the network defined by the correlation matrix at each timepoint.
+Given a $T$ by $\left( \frac{K^2 - K}{2} + K \right)$ matrix of
+dynamic correlations, $\mathbf{Y}_n$, we propose two general
+approaches to computing a $T$ by $K$ low-dimensional representation of
+those correlations, $\mathbf{X}_n$.  The first approach uses
+dimensionality reduction algorithms to project $\mathbf{Y}_n$ onto a
+$K$-dimensional space.  The second approach uses graph measures to
+characterize the relative positions of each feature
+($k \in \left[1, ..., K \right]$) in the network defined by the
+correlation matrix at each timepoint.
 
@@
 The modern toolkit of dimensionality reduction algorithms include
-Principal Components Analysis~\citep[PCA; ][]{Pear01}, Probabilistic
-PCA~\citep[PPCA; ][]{TippBish99}, Exploratory Factor
-Analysis~\citep[EFA; ][]{Spea04}, Independent Components
-Analysis~\citep[ICA; ][]{JuttHera91, ComoEtal91}, $t$-Stochastic
-Neighbor Embedding~\citep[$t$-SNE; ][]{MaatHint08}, Uniform Manifold
-Approximation and Projection~\citep[UMAP; ][]{McInHeal18},
-non-negative matrix factorization~\citep[NMF; ][]{LeeSeun99},
-Topographic Factor Analysis (TFA)~\cite{MannEtal14b}, Hierarchical
-Topographic Factor analysis (HTFA)~\cite{MannEtal18}, Topographic
-Latent Source Analysis~\cite[TLSA; ]{GersEtal11}, Dictionary
+Principal Components Analysis~\citep[PCA;][]{Pear01}, Probabilistic
+PCA~\citep[PPCA;][]{TippBish99}, Exploratory Factor
+Analysis~\citep[EFA;][]{Spea04}, Independent Components
+Analysis~\citep[ICA;][]{JuttHera91, ComoEtal91}, $t$-Stochastic
+Neighbor Embedding~\citep[$t$-SNE;][]{MaatHint08}, Uniform Manifold
+Approximation and Projection~\citep[UMAP;][]{McInHeal18}, non-negative
+matrix factorization~\citep[NMF;][]{LeeSeun99}, Topographic Factor
+Analysis~\cite[TFA;][]{MannEtal14b}, Hierarchical Topographic Factor
+analysis~\cite[HTFA;][]{MannEtal18}, Topographic Latent Source
+Analysis~\cite[TLSA;][]{GersEtal11}, Dictionary
 learning~\citep{MairEtal09a, MairEtal09b}, deep
@@
 the present manuscript, the general intuition driving these approaches
-is to compute the $T$ by $M$ matrix, $\mathbf{X}$, that is closest
-to the original $T$ by $N$ matrix, $\mathbf{Y}$, where (typically)
+is to compute the $T$ by $M$ matrix, $\mathbf{X}$, that is closest to
+the original $T$ by $N$ matrix, $\mathbf{Y}$, where (typically)
 $M \ll N$.  The different approaches place different constraints on
-what properties $\mathbf{X}$ must satisfy and which aspects of
-the data are compared (and how) to characterize the match between
-$\mathbf{X}$ and $\mathbf{Y}$.
+what properties $\mathbf{X}$ must satisfy and which aspects of the
+data are compared (and how) in order to characterize how well
+$\mathbf{X}$ approximates $\mathbf{Y}$.
 
@@
 (potentially recombined and transformed) mapping back to the original
-data in $\mathbf{Y}_0$.  We also explore graph measures that instead
+data in $\mathbf{X}_0$.  We also explore graph measures that instead
 characterize each feature's relative \textit{position} in the broader
@@
 might attempt to capture those similarities using a measure that
-reflects the how $A$ and $B$ interact in the network.
+reflects how $A$ and $B$ interact with \textit{other} members of the
+network.
 
@@
 correlation ``dynamics'' when the ground truth correlations were
-static.  We constructed 10 multivariate timeseries, whose observations
+static.  We constructed 10 multivariate timeseries whose observations
 were each drawn from a single (stable) Gaussian distribution.  For
@@
   Eqn.~\ref{eqn:randcorr}) covariance matrix.  Because each
-  timepoint's covariance matrix was drawn independently of the
+  timepoint's covariance matrix was drawn independently from the
   covariance matrices for all other timepoints, these datasets
@@
   \begin{align}
-    \mathbf{\Sigma}_t = \left( 1 - \frac{1 - t}{299} \right)
+    \mathbf{\Sigma}_t = \left( 1 - \frac{t}{299} \right)
     \mathbf{\Sigma}_{\mathrm{start}} + \frac{t}{299}\mathbf{\Sigma}_{\mathrm{end}}.
@@
 individuals (e.g., using ISFC analyses).  In particular, neural
-patterns will be similar across individuals, to the extent that the
-neural patterns under consideration are stimulus driven, and to the
+patterns will be similar across individuals to the extent that the
+neural patterns under consideration are stimulus-driven, and to the
 extent that the corresponding cognitive representations are reflected
@@
 We used an across-participants correlation-based classifier to decode
-which stimulus timepoint matched a given neural pattern.  We first
-divided the participants into two groups: a template group,
+which stimulus timepoint matched each timepoint's neural pattern.  We
+first divided the participants into two groups: a template group,
 $\mathcal{G}_{\mathrm{template}}$, and a to-be-decoded group,
@@
 labels to each row $\bar{\textbf{C}}_{\mathrm{decode}}$ using the row
-of $\bar{\textbf{C}}_{\mathrm{template}}$ to which it was most highly
-correlated.  We then repeated this decoding procedure, but using
-$\mathcal{G}_{\mathrm{decode}}$ as the template group and
+of $\bar{\textbf{C}}_{\mathrm{template}}$ with which it was most
+highly correlated.  We then repeated this decoding procedure, but
+using $\mathcal{G}_{\mathrm{decode}}$ as the template group and
 $\mathcal{G}_{\mathrm{template}}$ as the to-be-decoded group.  Given
 the true timepoint labels (for each group), we defined the
-\textit{decoding accuracy} as the proportion of correctly decoded
-timepoints, across both groups.  We defined the \textit{relative
-  decoding accuracy} as the difference between the decoding accuracy
-and chance accuracy (i.e., $\frac{1}{T}$).
+\textit{decoding accuracy} as the average proportion of correctly
+decoded timepoints, across both groups.  We defined the
+\textit{relative decoding accuracy} as the difference between the
+decoding accuracy and chance accuracy (i.e., $\frac{1}{T}$).
 
@@
 Using the notation above, these features correspond to $\mathbf{X}_0$,
-$\mathbf{X}_1$, $\mathbf{X}_2$, $\mathbf{X}_3$, and so on (we examined
-up to tenth order correlations, or $\mathbf{X}_{10}$).
+$\mathbf{X}_1$, $\mathbf{X}_2$, $\mathbf{X}_3$, and so on.
 
@@
 $\mathcal{G}_{\mathrm{train}_1}$ and $\mathcal{G}_{\mathrm{train}_2}$.
-We then computed $\mathbf{\Lambda}$ (temporal correlation) matrices for
-each type of neural feature, using $\mathcal{G}_{\mathrm{train}_1}$
-and $\mathcal{G}_{\mathrm{train}_2}$.  This resulted in $n+1$
-$\mathbf{\Lambda}$ matrices (one for the original timeseries of neural
-activations, and one for each of $n$ orders of dynamic correlations).
-Our objective was to find a set of weights of each of these
-$\mathbf{\Lambda}$ matrices such that the weighted average of the
-$n+1$ matrices yielded the highest decoding accuracy.  We used
-quasi-Newton gradient ascent~\citep{NoceWrig06}, using decoding
-accuracy as the objective function to be maximized, to find an optimal
-set of training data-derived weights, $\phi_{0, 1, ..., n}$, where
-$\sum_{i=0}^n \phi_i = 1$ and where
+We then computed $\mathbf{\Lambda}$ (temporal correlation) matrices
+for each type of neural feature, using
+$\mathcal{G}_{\mathrm{train}_1}$ and $\mathcal{G}_{\mathrm{train}_2}$.
+This resulted in $n+1$ $\mathbf{\Lambda}$ matrices (one for the
+original timeseries of neural activations, and one for each of $n$
+orders of dynamic correlations).  Our objective was to find a set of
+weights of each of these $\mathbf{\Lambda}$ matrices such that the
+weighted average of the $n+1$ matrices yielded the highest decoding
+accuracy.  We used quasi-Newton gradient ascent~\citep{NoceWrig06},
+using decoding accuracy (for $\mathcal{G}_{\mathrm{train}_1}$ and
+$\mathcal{G}_{\mathrm{train}_2}$) as the objective function to be
+maximized, to find an optimal set of training data-derived weights,
+$\phi_{0, 1, ..., n}$, where $\sum_{i=0}^n \phi_i = 1$ and where
 $\phi_i \geq 0 \forall i \in \left[0, 1, ..., n\right]$.
@@
 Rather than attempting to maximize decoding accuracy, we sought to
-discover the trends in the data that were robust to specific
-classifier parameters choices.  Specifically, we sought to
-characterize how decoding accuracy varied (under different
-experimental conditions) as a function of which neural features were
-considered.
+discover the trends in the data that were robust to classifier
+parameters choices.  Specifically, we sought to characterize how
+decoding accuracy varied (under different experimental conditions) as
+a function of which neural features were considered.
 
 To identify decoding results that were robust to specific classifier
-parameter choices, we repeated our decoding analyses that substituted
-in a variety of kernel shapes and widths for
+parameter choices, we repeated our decoding analyses after
+substituting in each of a variety of kernel shapes and widths for
 Equation~\ref{eqn:timecorr}.  We examined Gaussian
@@
 framework to a public fMRI dataset collected as participants listened
-to an auditorally presented story, a temporally scrambled version of
-the story, or underwent a resting state scan (see \textit{Functional
-  neuroimaging data collected during story listening}).  We used the
-relative decoding accuracies of classifiers trained on
-different sets of neural features to estimate which types of features
-reflected ongoing cognitive processing.
+to an auditorally presented story, listened to a temporally scrambled
+version of the story, or underwent a resting state scan (see
+\textit{Functional neuroimaging data collected during story
+  listening}).  We used the relative decoding accuracies of
+classifiers trained on different sets of neural features to estimate
+which types of features reflected ongoing cognitive processing.
 
@@
 
-In general, wide monotonic kernel shapes (Laplace, Gaussian)\textbf{, and
-wider kernels (within a shape), }performed best when the correlations
+In general, wide monotonic kernel shapes (Laplace, Gaussian), and
+wider kernels (within a shape), performed best when the correlations
 varied gradually from moment-to-moment (Figs.~\ref{fig:synthetic}a, c,
@@
 narrow) performed best.  This is because, when every timepoint's
-correlations are independent of the correlations in every other
+correlations are independent of the correlations at every other
 timepoint, averaging data over time dilutes the available signal.
-\textbf{Following a similar patterns, holding kernel shape fixed,
-  narrower kernel parameters better recovered randomly varying
-  correlations.}
+Following a similar pattern, holding kernel shape fixed, narrower
+kernel parameters better recovered randomly varying correlations.
 
@@
       correlation order and cognitive engagement.}
-    \textbf{a. Decoding accuracy as a function of order: PCA.}
+    \textbf{a.~Decoding accuracy as a function of order: PCA.}
     \textit{Order} ($x$-axis) refers to the maximum order of dynamic
@@
     of all other features (via a two-tailed test, thresholded at
-    $p < 0.05$).  The circled values represent the maximum decoding
+    $p < 0.05$).  Figure~\ttests displays additional comparisons between
+    the decoding accuracies achieved using different sets of neural
+    features.  The circled values represent the maximum decoding
     accuracy within each experimental condition.
-    \textbf{b. Normalized decoding accuracy as a function of order:
+    \textbf{b.~Normalized decoding accuracy as a function of order:
       PCA.}  This panel displays the same results as Panel a, but here
@@
     PCA to project each high-dimensional pattern of dynamic
-    correlations onto a lower-dimensional space.  \textbf{c.  Decoding
+    correlations onto a lower-dimensional space.  \textbf{c.~Decoding
       accuracy as a function of order: eigenvector centrality.} This
@@
     of dynamic correlations onto a lower-dimensional space.
-    \textbf{d. Normalized decoding accuracy as a function of order:
+    \textbf{d.~Normalized decoding accuracy as a function of order:
       eigenvector centrality.} This panel is in the same format as
@@
 the decoders might have picked up on attentional drift, boredom, or
-tiredness; we hypothesize these all increase throughout the resting
+tiredness; we hypothesize that these all increased throughout the resting
 state scan.  The decoders might be picking up on aspects of these
@@
       strongest correlations.}  Each color corresponds to one order of
-    correlations, averaged across participants and time. The inflated
-    brain plots display the locations of the endpoints of the 10
-    strongest (absolute value) correlations at each order, projected
-    onto the cortical surface~\citep{CombEtal19}.  The lists of terms
-    on the right display the top five Neurosynth
-    terms~\citep{RubiEtal17} decoded from the corresponding brain maps
-    for each order.  Each row displays data from a different
-    experimental condition.  Additional maps and their corresponding
-    Neurosynth terms may be found in the \textit{Supplementary
-      materials} (intact: Figure S1; paragraph: Figure S2; word:
-    Figure S3; rest: Figure S4).}
+    inter-subject functional correlations. The inflated brain plots
+    display the locations of the endpoints of the 10 strongest
+    (absolute value) correlations at each order, projected onto the
+    cortical surface~\citep{CombEtal19}.  The lists of terms on the
+    right display the top five Neurosynth terms~\citep{RubiEtal17}
+    decoded from the corresponding brain maps for each order.  Each
+    row displays data from a different experimental condition.
+    Additional maps and their corresponding Neurosynth terms may be
+    found in the \textit{Supplementary materials} (intact: Figure~\intact;
+    paragraph: Figure~\para; word: Figure~\word; rest: Figure~\rest).}
   \label{fig:neurosynth}
@@
 of 50 (Fig.~\ref{fig:kernels}d).  We used this kernel to compute a
-single $K$ by $K$ $n^\mathrm{th}$-order correlation matrix for each
-experimental condition, along with the Neurosynth~\citep{RubiEtal17}
-terms most highly associated with each of these matrices
+single $K$ by $K$ $n^\mathrm{th}$-order DISFC matrix for each
+experimental condition.  We then used Neurosynth~\citep{RubiEtal17} to
+compute the terms most highly associated with the most strongly
+correlated pairs of regions in each of these matrices
 (Fig.~\ref{fig:neurosynth}; see \textit{Reverse inference}).
@@
 analyses to create maps (and decode the top associated Neurosynth
-terms) for up to fifteenth-order correlations (Figs. S1, S2, S3, and
-S4).  Of note, examining fifteenth-order correlations between 700
+terms) for up to fifteenth-order correlations (Figs.~\intact, \para, \word, and
+\rest).  Of note, examining fifteenth-order correlations between 700
 nodes using conventional methods would have required storing roughly
@@
 of network interactions support higher-level aspects of cognitive
-processing (Fig.\ref{fig:discussion}).
+processing (Fig.~\ref{fig:discussion}).
 
@@
 The notion that cognition is reflected in (and possibly mediated by)
-patterns of network dynamics has been suggested by or proposed in
-myriad empirical studies and reviews~\citep[e.g.,][]{DemeEtal19,
-  Turk13, LuriEtal18, FongEtal19, ParkEtal18b, PretEtal17,
-  RoyEtal19, LiegEtal19, ZouEtal19, ChanGlov10, GonzEtal19}.  Our
-study extends this line of work by finding cognitively relevant
-\textit{higher-order} network dynamics that reflect ongoing cognition.  Our
-findings complement other work that uses graph theory and topology to
-characterize how brain networks reconfigure during
-cognition~\citep[e.g.,][]{BassEtal06, ZhenEtal19, McInJirs19,
-  TokeSomm19, SizeEtal18, ReimEtal17, BetzEtal19}.
+patterns of first-order network dynamics has been suggested by or
+proposed in myriad empirical studies and
+reviews~\citep[e.g.,][]{DemeEtal19, Turk13, LuriEtal18, FongEtal19,
+  ParkEtal18b, PretEtal17, RoyEtal19, LiegEtal19, ZouEtal19,
+  ChanGlov10, GonzEtal19}.  Our study extends this line of work by
+finding cognitively relevant \textit{higher-order} network dynamics
+that reflect ongoing cognition.  Our findings complement other work
+that uses graph theory and topology to characterize how brain networks
+reconfigure during cognition~\citep[e.g.,][]{BassEtal06, ZhenEtal19,
+  McInJirs19, TokeSomm19, SizeEtal18, ReimEtal17, BetzEtal19}.
 
@@
 for characterizing the dynamics of high-order correlations in neural
-data provides a window into the neural basis of cognition.  By showing
-that high-level cognition is reflected in high-order network dynamics
+data provide a window into the neural basis of cognition.  By showing
+that high-level cognition is reflected in high-order network dynamics,
 we have elucidated the next step on the path towards understanding the
@@
 \section*{Acknowledgements}
-We acknowledge discussions with Luke Chang, Hany Farid, Paxton
-Fitzpatrick, Andrew Heusser, Eshin Jolly, Aaron Lee, Qiang Liu,
-Matthijs van der Meer, Judith Mildner, Gina Notaro, Stephen
+We acknowledge discussions with Luke Chang, Vassiki Chauhan, Hany
+Farid, Paxton Fitzpatrick, Andrew Heusser, Eshin Jolly, Aaron Lee,
+Qiang Liu, Matthijs van der Meer, Judith Mildner, Gina Notaro, Stephen
 Satterthwaite, Emily Whitaker, Weizhen Xie, and Kirsten Ziman. Our
@@
 \section*{Author contributions}
-Concept: J.R.M.  Implementation: T.H.C., L.L.W.O., and
-J.R.M.  Analyses: L.L.W.O and J.R.M.
+Concept: J.R.M.  Implementation: T.H.C., L.L.W.O., and J.R.M.
+Analyses: L.L.W.O. and J.R.M.  Writing: L.L.W.O. and J.R.M.
 

### 2019-09-06 paper/supporting_information.tex
added supplementary text

\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage[font=small,labelfont=bf]{caption}
\usepackage{geometry}
\usepackage{natbib}
\usepackage{pxfonts}
\usepackage{graphicx}
\usepackage{newfloat}
\usepackage{setspace}
%\doublespacing

\newcommand{\argmax}{\mathop{\mathrm{argmax}}\limits}

\title{\textit{Supporting Information for: } High-level cognition during story listening is reflected in high-order dynamic correlations in neural activity patterns}
\author{Lucy L. W. Owen$^1$, Thomas H. Chang$^{1,2}$, and\
  Jeremy R. Manning\textsuperscript{$1, \dagger$}\\
  [0.1in]$^1$Department of Psychological and Brain
  Sciences,\\Dartmouth
  College, Hanover, NH\\
  $^2$Amazon.com, Seattle, WA\\
  \textsuperscript{$\dagger$}Address correspondence to
  jeremy.r.manning@dartmouth.edu}

\bibliographystyle{apa}

\begin{document}
\maketitle

\setcounter{equation}{0}
\setcounter{figure}{0}
\setcounter{table}{0}
\setcounter{page}{1}
\setcounter{section}{0}
\makeatletter
\renewcommand{\theequation}{S\arabic{equation}}
\renewcommand{\thefigure}{S\arabic{figure}}
\renewcommand{\bibnumfmt}[1]{[S#1]}
\renewcommand{\citenumfont}[1]{S#1}

\section*{Overview}
This document provides additional details and figures about the methods we used in the main text.

\begin{figure}[p!]
\centering
\includegraphics[width=1\textwidth]{figs/stats_heatmaps}
\caption{\small \textbf{Heatmaps conveying statistical results comparing decoding accuracy for each order.}  For each condition (intact, paragraph scrambled, word scrambled, and rest) and for each reduction technique (PCA and eigenvector centrality), we compared the distribution of decoding accuracy for each order. The upper triangle of each heatmap conveys the results of t-tests, and the lower triangle conveys corresponding p-values.  The diagonal is the results of the optimization of the phi parameter. }
\label{fig:stats_heatmaps}
\end{figure}

\begin{figure}[p!]
\centering
\includegraphics[width=\textwidth]{figs/supp_15_intact}
\caption{\small \textbf{Top 10 terms associated with the endpoints of the
      strongest correlations for the intact experimental condition.}  Each color corresponds to orders 1-15 of
    inter-subject functional correlations. The inflated brain plots
    display the locations of the endpoints of the 10 strongest
    (absolute value) correlations at each order, projected onto the
    cortical surface~\citep{CombEtal19}.  The lists of terms on the
    right display the top 10 Neurosynth terms~\citep{RubiEtal17}
    decoded from the corresponding brain maps for each order for the intact condition.}
\label{fig:intact}
\end{figure}

\begin{figure}[p!]
\centering
\includegraphics[width=\textwidth]{figs/supp_15_paragraph}
\caption{\small \textbf{Top 10 terms associated with the endpoints of the
      strongest correlations for the paragraph scrambled condition.}  Each color corresponds to orders 1-15 of
    inter-subject functional correlations for the paragraph scrambled condition. The inflated brain plots
    display the locations of the endpoints of the 10 strongest
    (absolute value) correlations at each order, projected onto the
    cortical surface~\citep{CombEtal19}.  The lists of terms on the
    right display the top 10 Neurosynth terms~\citep{RubiEtal17}
    decoded from the corresponding brain maps for each order.}
\label{fig:paragraph}
\end{figure}

\begin{figure}[p!]
\centering
\includegraphics[width=\textwidth]{figs/supp_15_word}
\caption{\small \textbf{Top 10 terms associated with the endpoints of the
      strongest correlations for the word scrambled condition.}  Each color corresponds to orders 1-15 of
    inter-subject functional correlations for the word scrambled condition. The inflated brain plots
    display the locations of the endpoints of the 10 strongest
    (absolute value) correlations at each order, projected onto the
    cortical surface~\citep{CombEtal19}.  The lists of terms on the
    right display the top 10 Neurosynth terms~\citep{RubiEtal17}
    decoded from the corresponding brain maps for each order.}
\label{fig:word}
\end{figure}

\begin{figure}[p!]
\centering
\includegraphics[width=\textwidth]{figs/supp_15_rest}
\caption{\small \textbf{Top 10 terms associated with the endpoints of the
      strongest correlations for the rest condition.}  Each color corresponds to orders 1-15 of
    inter-subject functional correlations for the rest condition. The inflated brain plots
    display the locations of the endpoints of the 10 strongest
    (absolute value) correlations at each order, projected onto the
    cortical surface~\citep{CombEtal19}.  The lists of terms on the
    right display the top 10 Neurosynth terms~\citep{RubiEtal17}
    decoded from the corresponding brain maps for each order.}
\label{fig:rest}
\end{figure}

%\section*{Participant-level figures referenced in the main text}

% Supporting information

\newpage
\renewcommand{\refname}{Supplemental references}
\bibliography{memlab}

\end{document}

### 2019-09-06 paper/nature neuroscience submission/cover_letter.tex
added emails to cover letter

@@
   We have suggested the following scientists as expert reviewers:
-  Richard Betzel (EMAIL), Danielle Bassett (EMAIL), Emily Finn
-  (EMAIL), Olaf Sporns (EMAIL), and Christopher Honey (EMAIL).
+  Richard Betzel (rbetzel@indiana.edu), Danielle Bassett (dsb@seas.upenn.edu), Emily Finn
+  (emily.finn@nih.gov), Olaf Sporns (osporns@indiana.edu), and Christopher Honey (chris.honey@jhu.edu).
 

### 2019-09-06 paper/supporting_information.tex
tweaks to stats heatmap figure

@@
 
-\title{\textit{Supporting Information for: } High-level cognition during story listening is reflected in high-order dynamic correlations in neural activity patterns}
-\author{Lucy L. W. Owen$^1$, Thomas H. Chang$^{1,2}$, and\
+\title{\textit{Supplementary materials for: } High-level cognition
+  during story listening is reflected in high-order dynamic
+  correlations in neural activity patterns} \author{Lucy
+  L. W. Owen$^1$, Thomas H. Chang$^{1,2}$, and\
   Jeremy R. Manning\textsuperscript{$1, \dagger$}\\
@@
 
-\section*{Overview}
-This document provides additional details and figures about the methods we used in the main text.
-
-\begin{figure}[p!]
+\begin{figure}[tp]
 \centering
 \includegraphics[width=1\textwidth]{figs/stats_heatmaps}
-\caption{\small \textbf{Heatmaps conveying statistical results comparing decoding accuracy for each order.}  For each condition (intact, paragraph scrambled, word scrambled, and rest) and for each reduction technique (PCA and eigenvector centrality), we compared the distribution of decoding accuracy for each order.
-The upper triangle of each heatmap conveys the results of t-tests, and the lower triangle conveys corresponding p-values.
-The diagonal is the results of the optimization of the phi parameter.
-}
+\caption{\textbf{Statistical summary of decoding accuracies for
+    different neural features.}  Each heatmap displays decoding
+  results for one experimental condition (intact, paragraph, word, and
+  rest).  We considered dynamic activity patterns (order 0) and
+  dynamic correlations at different orders (order $> 0$).  We used two-tailed $t$-tests to compare the
+  distributions of decoding accuracies obtained using each pair of
+  features.  The distributions for each feature reflect the set of
+  decoding accuracies obtained
+
+  In the upper triangles of each map, warmer colors (positive $t$-values) indicate that the
+  neural feature indicated in the given row yielded higher accuracy than the
+  feature indicated in the given column.  Cooler colors (negative
+  $t$-values) indicate that
+  the feature in the given row yielded lower decoding accuracy than
+  the feature in the given column.
+
+  The upper triangles of each heatmap report the $t$-values
+  from a
+
+  \textbf{Heatmaps conveying statistical results comparing decoding
+    accuracy for each order.}  For each condition (intact, paragraph
+  scrambled, word scrambled, and rest) and for each reduction
+  technique (PCA and eigenvector centrality), we compared the
+  distribution of decoding accuracy for each order. The upper triangle
+  of each heatmap conveys the results of t-tests, and the lower
+  triangle conveys corresponding p-values.  The diagonal is the
+  results of the optimization of the phi parameter. }
 \label{fig:stats_heatmaps}
@@
 \centering
-\includegraphics[width=\textwidth]{figs/supp_15_intact}
-\caption{\small \textbf{Top 10 terms associated with the endpoints of the
+\includegraphics[width=0.75\textwidth]{figs/supp_15_intact}
+\caption{\textbf{Top 10 terms associated with the endpoints of the
       strongest correlations for the intact experimental condition.}  Each color corresponds to orders 1-15 of
@@
 \centering
-\includegraphics[width=\textwidth]{figs/supp_15_paragraph}
-\caption{\small \textbf{Top 10 terms associated with the endpoints of the
+\includegraphics[width=0.75\textwidth]{figs/supp_15_paragraph}
+\caption{\textbf{Top 10 terms associated with the endpoints of the
       strongest correlations for the paragraph scrambled condition.}  Each color corresponds to orders 1-15 of
@@
 \centering
-\includegraphics[width=\textwidth]{figs/supp_15_word}
-\caption{\small \textbf{Top 10 terms associated with the endpoints of the
+\includegraphics[width=0.75\textwidth]{figs/supp_15_word}
+\caption{\textbf{Top 10 terms associated with the endpoints of the
       strongest correlations for the word scrambled condition.}  Each color corresponds to orders 1-15 of
@@
 \centering
-\includegraphics[width=\textwidth]{figs/supp_15_rest}
-\caption{\small \textbf{Top 10 terms associated with the endpoints of the
+\includegraphics[width=0.75\textwidth]{figs/supp_15_rest}
+\caption{\textbf{Top 10 terms associated with the endpoints of the
       strongest correlations for the rest condition.}  Each color corresponds to orders 1-15 of

### 2019-09-06 paper/main.tex
moved heatmaps to main text

@@
 
-\newcommand{\ttests}{S1}
-\newcommand{\intact}{S2}
-\newcommand{\para}{S3}
-\newcommand{\word}{S4}
-\newcommand{\rest}{S5}
+%\newcommand{\ttests}{S1}
+\newcommand{\intact}{S1}
+\newcommand{\para}{S2}
+\newcommand{\word}{S3}
+\newcommand{\rest}{S4}
 
@@
 
-In brief, we computed timeseries of dynamic high-order correlations
-that were similar across participants in each of two randomly assigned
-groups: a training group and a test group.  We then trained
-classifiers on the training group's data to match each sample from the
-test group with a stimulus timepoint.  Each classifier comprised a
-weighted blend of neural patterns that reflected up to
-$n^\mathrm{th}$-order dynamic correlations (see \textit{Feature
-  weighting and testing}).  We repeated this process for
-$n \in \left\{ 0, 1, 2, ..., 10 \right\}$.  Our examinations of
-synthetic data suggested that none of the kernels we examined were
-``universal'' in the sense of optimally recovering underlying
-correlations regardless of the structure of those correlations.  We
-found a similar pattern in the (real) fMRI data, whereby different
-kernels yielded different decoding accuracies, but no single kernel
-emerged as the clear ``best.''  In our analyses of neural data, we
-therefore averaged our decoding results over a variety of kernel
-shapes and widths in order to identify results that were robust to
-specific kernel parameters (see \textit{Identifying robust
-  decoding results}).
-
-Our approach to estimating dynamic high-order correlations entails
-mapping the high-dimensional feature space of correlations (a $T$ by
-$\mathcal{O}(K^2)$ matrix) onto a lower-dimensional $T$ by $K$ matrix.
-We carried out two sets of analyses that differed in how this mapping
-was computed.  The first set of analyses used PCA to find a
-low-dimensional embedding of the original dynamic correlation matrices
-(Fig.~\ref{fig:decoding}a,b).  The second set of analyses
-characterized correlations in dynamics of each feature's eigenvector
-centrality, but did not preserve the underlying activity dynamics
-(Fig.~\ref{fig:decoding}c,d).
-
 \begin{figure}[tp]
@@
     of all other features (via a two-tailed test, thresholded at
-    $p < 0.05$).  Figure~\ttests displays additional comparisons between
+    $p < 0.05$).  Figure~\ref{fig:ttests} displays additional comparisons between
     the decoding accuracies achieved using different sets of neural
@@
 
+In brief, we computed timeseries of dynamic high-order correlations
+that were similar across participants in each of two randomly assigned
+groups: a training group and a test group.  We then trained
+classifiers on the training group's data to match each sample from the
+test group with a stimulus timepoint.  Each classifier comprised a
+weighted blend of neural patterns that reflected up to
+$n^\mathrm{th}$-order dynamic correlations (see \textit{Feature
+  weighting and testing}).  We repeated this process for
+$n \in \left\{ 0, 1, 2, ..., 10 \right\}$.  Our examinations of
+synthetic data suggested that none of the kernels we examined were
+``universal'' in the sense of optimally recovering underlying
+correlations regardless of the structure of those correlations.  We
+found a similar pattern in the (real) fMRI data, whereby different
+kernels yielded different decoding accuracies, but no single kernel
+emerged as the clear ``best.''  In our analyses of neural data, we
+therefore averaged our decoding results over a variety of kernel
+shapes and widths in order to identify results that were robust to
+specific kernel parameters (see \textit{Identifying robust
+  decoding results}).
+
+Our approach to estimating dynamic high-order correlations entails
+mapping the high-dimensional feature space of correlations (a $T$ by
+$\mathcal{O}(K^2)$ matrix) onto a lower-dimensional $T$ by $K$ matrix.
+We carried out two sets of analyses that differed in how this mapping
+was computed.  The first set of analyses used PCA to find a
+low-dimensional embedding of the original dynamic correlation matrices
+(Fig.~\ref{fig:decoding}a,b).  The second set of analyses
+characterized correlations in dynamics of each feature's eigenvector
+centrality, but did not preserve the underlying activity dynamics
+(Fig.~\ref{fig:decoding}c,d).
+
+\begin{figure}[tp]
+\centering
+\includegraphics[width=1\textwidth]{figs/stats_heatmaps}
+\caption{\textbf{Statistical summary of decoding accuracies for
+    different neural features.}  Each column displays decoding
+  results for one experimental condition (intact, paragraph, word, and
+  rest).  We considered dynamic activity patterns (order 0) and
+  dynamic correlations at different orders (order $> 0$).  We used
+  two-tailed $t$-tests to compare the
+  distributions of decoding accuracies obtained using each pair of
+  features.  The distributions for each feature reflect the set of
+  average decoding accuracies (across all kernel parameters), obtained
+  for each random assignment of training and test groups.
+  In the upper triangles of each map, warmer colors (positive $t$-values) indicate that the
+  neural feature indicated in the given row yielded higher accuracy than the
+  feature indicated in the given column.  Cooler colors (negative
+  $t$-values) indicate that
+  the feature in the given row yielded lower decoding accuracy than
+  the feature in the given column.  The lower triangles of each map
+  denote the corresponding $p$-values for the $t$-tests.  The diagonal
+  entries display the relative average optimized weight given to each type of feature, in
+  a decoder that included all feature types (see \textit{Feature
+    weighting and testing}).}
+\label{fig:ttests}
+\end{figure}
+
 Both sets of temporal decoding analyses yielded qualitatively similar
 results for the auditory (non-rest) conditions of the experiment
-(Fig.~\ref{fig:decoding}: pink, yellow, and teal lines).  The highest
+(Fig.~\ref{fig:decoding}: pink, yellow, and teal lines;
+Fig.~\ref{fig:ttests}: three leftmost columns).  The highest
 decoding accuracy for participants who listened to the intact
@@
 zero).  The two sets of analyses yielded different decoding results on
-resting state data (Fig.~\ref{fig:decoding}: purple lines).  We note
+resting state data (Fig.~\ref{fig:decoding}: purple lines;
+Fig.~\ref{fig:ttests}: rightmost column).  We note
 that while the resting state times could be decoded reliably, the

### 2019-09-06 paper/supporting_information.tex
moved heatmaps to main text

@@
   rest).  We considered dynamic activity patterns (order 0) and
-  dynamic correlations at different orders (order $> 0$).  We used two-tailed $t$-tests to compare the
+  dynamic correlations at different orders (order $> 0$).  We used
+  two-tailed $t$-tests to compare the
   distributions of decoding accuracies obtained using each pair of
   features.  The distributions for each feature reflect the set of
-  decoding accuracies obtained
-
+  average decoding accuracies (across all kernel parameters), obtained
+  for each random assignment of training and test groups.
   In the upper triangles of each map, warmer colors (positive $t$-values) indicate that the
@@
   the feature in the given row yielded lower decoding accuracy than
-  the feature in the given column.
-
-  The upper triangles of each heatmap report the $t$-values
-  from a
-
-  \textbf{Heatmaps conveying statistical results comparing decoding
-    accuracy for each order.}  For each condition (intact, paragraph
-  scrambled, word scrambled, and rest) and for each reduction
-  technique (PCA and eigenvector centrality), we compared the
-  distribution of decoding accuracy for each order. The upper triangle
-  of each heatmap conveys the results of t-tests, and the lower
-  triangle conveys corresponding p-values.  The diagonal is the
-  results of the optimization of the phi parameter. }
+  the feature in the given column.  The lower triangles of each map
+  denote the corresponding $p$-values for the $t$-tests.  The diagonal
+  entries display the relative average optimized weight given to each type of feature, in
+  a decoder that included all feature types (see \textbf{Feature
+    weighting and testing}).}
 \label{fig:stats_heatmaps}

### 2019-09-06 paper/supporting_information.tex
updated supplemental materials caption

@@
 
+\newcommand{\neurosynth}{7}
+
 \begin{document}
@@
 
-\begin{figure}[tp]
-\centering
-\includegraphics[width=1\textwidth]{figs/stats_heatmaps}
-\caption{\textbf{Statistical summary of decoding accuracies for
-    different neural features.}  Each heatmap displays decoding
-  results for one experimental condition (intact, paragraph, word, and
-  rest).  We considered dynamic activity patterns (order 0) and
-  dynamic correlations at different orders (order $> 0$).  We used
-  two-tailed $t$-tests to compare the
-  distributions of decoding accuracies obtained using each pair of
-  features.  The distributions for each feature reflect the set of
-  average decoding accuracies (across all kernel parameters), obtained
-  for each random assignment of training and test groups.
-  In the upper triangles of each map, warmer colors (positive $t$-values) indicate that the
-  neural feature indicated in the given row yielded higher accuracy than the
-  feature indicated in the given column.  Cooler colors (negative
-  $t$-values) indicate that
-  the feature in the given row yielded lower decoding accuracy than
-  the feature in the given column.  The lower triangles of each map
-  denote the corresponding $p$-values for the $t$-tests.  The diagonal
-  entries display the relative average optimized weight given to each type of feature, in
-  a decoder that included all feature types (see \textbf{Feature
-    weighting and testing}).}
-\label{fig:stats_heatmaps}
-\end{figure}
-
 \begin{figure}[p!]
@@
 \includegraphics[width=0.75\textwidth]{figs/supp_15_intact}
-\caption{\textbf{Top 10 terms associated with the endpoints of the
-      strongest correlations for the intact experimental condition.}  Each color corresponds to orders 1-15 of
-    inter-subject functional correlations. The inflated brain plots
-    display the locations of the endpoints of the 10 strongest
-    (absolute value) correlations at each order, projected onto the
-    cortical surface~\citep{CombEtal19}.  The lists of terms on the
-    right display the top 10 Neurosynth terms~\citep{RubiEtal17}
-    decoded from the corresponding brain maps for each order for the intact condition.}
+\caption{\textbf{Top terms associated with the endpoints of the
+    strongest correlations for the \textit{intact} experimental
+    condition.}  Each color corresponds to one order of inter-subject
+functional correlations. The inflated brain plots display the
+locations of the endpoints of the 10 strongest (absolute value)
+correlations at each order, projected onto the cortical
+surface~\citep{CombEtal19}.  The lists of terms display
+the top 10 Neurosynth terms~\citep{RubiEtal17} decoded from the
+corresponding brain maps for each order.  (Also see Fig.~\neurosynth,
+top row, in the main text.)}
 \label{fig:intact}
@@
 \includegraphics[width=0.75\textwidth]{figs/supp_15_paragraph}
-\caption{\textbf{Top 10 terms associated with the endpoints of the
-      strongest correlations for the paragraph scrambled condition.}  Each color corresponds to orders 1-15 of
-    inter-subject functional correlations for the paragraph scrambled condition. The inflated brain plots
-    display the locations of the endpoints of the 10 strongest
-    (absolute value) correlations at each order, projected onto the
-    cortical surface~\citep{CombEtal19}.  The lists of terms on the
-    right display the top 10 Neurosynth terms~\citep{RubiEtal17}
-    decoded from the corresponding brain maps for each order.}
+\caption{\textbf{Top terms associated with the endpoints of the
+    strongest correlations for the \textit{paragraph} experimental
+    condition.}  This figure is in the same format as
+  Figure~\ref{fig:intact}, but displays results for the
+  paragraph-scrambled story listening condition.  (Also see Fig.~\neurosynth,
+second row, in the main text.)}
 \label{fig:paragraph}
@@
 \includegraphics[width=0.75\textwidth]{figs/supp_15_word}
-\caption{\textbf{Top 10 terms associated with the endpoints of the
-      strongest correlations for the word scrambled condition.}  Each color corresponds to orders 1-15 of
-    inter-subject functional correlations for the word scrambled condition. The inflated brain plots
-    display the locations of the endpoints of the 10 strongest
-    (absolute value) correlations at each order, projected onto the
-    cortical surface~\citep{CombEtal19}.  The lists of terms on the
-    right display the top 10 Neurosynth terms~\citep{RubiEtal17}
-    decoded from the corresponding brain maps for each order.}
+\caption{\textbf{Top terms associated with the endpoints of the
+    strongest correlations for the \textit{word} experimental
+    condition.}  This figure is in the same format as
+  Figure~\ref{fig:intact}, but displays results for the
+  word-scrambled story listening condition.  (Also see Fig.~\neurosynth,
+third row, in the main text.)}
 \label{fig:word}
@@
 \includegraphics[width=0.75\textwidth]{figs/supp_15_rest}
-\caption{\textbf{Top 10 terms associated with the endpoints of the
-      strongest correlations for the rest condition.}  Each color corresponds to orders 1-15 of
-    inter-subject functional correlations for the rest condition. The inflated brain plots
-    display the locations of the endpoints of the 10 strongest
-    (absolute value) correlations at each order, projected onto the
-    cortical surface~\citep{CombEtal19}.  The lists of terms on the
-    right display the top 10 Neurosynth terms~\citep{RubiEtal17}
-    decoded from the corresponding brain maps for each order.}
+\caption{\textbf{Top terms associated with the endpoints of the
+    strongest correlations for the \textit{rest} experimental
+    condition.}  This figure is in the same format as
+  Figure~\ref{fig:intact}, but displays results for the
+  resting state condition.  (Also see Fig.~\neurosynth,
+bottom row, in the main text.)}
 \label{fig:rest}

### 2019-09-06 paper/nature neuroscience submission/cover_letter.tex
updated cover letter

--- 2019-09-05 paper/nature neuroscience submission/cover_letter.tex
@@
     dynamic correlations in neural activity patterns}, which we wish
-  to submit for publication as a Brief Communication in \textit{Nature
+  to submit for publication as an Article in \textit{Nature
     Neuroscience}.
@@
   We have suggested the following scientists as expert reviewers:
-  Richard Betzel (EMAIL), Danielle Bassett (EMAIL), Emily Finn
-  (EMAIL), Olaf Sporns (EMAIL), and Christopher Honey (EMAIL).
+  Richard Betzel (r\-bet\-zel@in\-di\-ana.edu), Danielle Bassett (dsb@seas.upenn.edu), Emily Finn
+  (emily.finn@nih.gov), Olaf Sporns (o\-sporns@in\-di\-ana.edu), and Christopher Honey (chris.honey@jhu.edu).
 
@@
   for publication, we will update our manuscript by moving the current
-  methods section into our supporting document, and by adding a
-  methods summary conforming to the Brief Communications format.
-  Thank you for considering our manuscript for publication in Nature
-  Neuroscience.
+  methods section into an \textit{Online methods} section in our
+  supporting document.  Thank you for considering our manuscript for
+  publication in Nature Neuroscience.
 

### 2019-09-06 code/scripts/pieman_cluster_level_chunked.py
code cleanup

@@ -1,140 +1,0 @@
-
-import timecorr as tc
-from timecorr.helpers import isfc, wisfc, mean_combine, corrmean_combine
-from scipy.io import loadmat
-import numpy as np
-import sys
-import os
-from config import config
-import pandas as pd
-
-cond = sys.argv[1]
-level = sys.argv[2]
-reps = sys.argv[3]
-cfun = sys.argv[4]
-rfun = sys.argv[5]
-width = int(sys.argv[6])
-wp = sys.argv[7]
-
-chunks = 3
-
-if len(sys.argv) < 9:
-    debug = False
-else:
-    debug = eval(sys.argv[8])
-
-result_name = 'level_analysis_chunked'
-
-if debug:
-    results_dir = os.path.join(config['resultsdir'], result_name, cfun + '_' + rfun + '_' + wp + '_' + str(width) + '_debug')
-
-else:
-    results_dir = os.path.join(config['resultsdir'], result_name, cfun + '_' + rfun + '_' + wp + '_' + str(width))
-
-try:
-    if not os.path.exists(results_dir):
-        os.makedirs(results_dir)
-except OSError as err:
-   print(err)
-
-
-laplace = {'name': 'Laplace', 'weights': tc.laplace_weights, 'params': {'scale': width}}
-delta = {'name': '$\delta$', 'weights': tc.eye_weights, 'params': tc.eye_params}
-gaussian = {'name': 'Gaussian', 'weights': tc.gaussian_weights, 'params': {'var': width}}
-mexican_hat = {'name': 'Mexican hat', 'weights': tc.mexican_hat_weights, 'params': {'sigma': width}}
-
-factors = 700
-
-if factors == 100:
-    pieman_name = 'pieman_ica100.mat'
-else:
-    pieman_name = 'pieman_data.mat'
-
-pieman_data = loadmat(os.path.join(config['datadir'], pieman_name))
-pieman_conds = ['intact', 'paragraph', 'word', 'rest']
-
-
-weights_paramter = eval(wp)
-
-###### REMOVE the duplicate!!
-
-if debug:
-    data_chunks = [0] * chunks
-    conds_chunks = [0] * chunks
-    divided = 0
-    for chunk_amt in list(range(chunks)):
-        data = []
-        conds = []
-        for c in pieman_conds:
-            next_data = list(map(lambda i: pieman_data[c][:, i][0][divided:divided+(30/chunks),:20], np.arange(4)))
-            data.extend(next_data)
[…]

### 2019-09-06 code/scripts/pieman_cluster_submit_level_chunked.py

@@ -1,166 +1,0 @@
-#!/usr/bin/python
-
-# create a bunch of job scripts
-from config import config
-from subprocess import call
-import numpy as np
-import os
-import socket
-import getpass
-import datetime as dt
-
-
-# ====== MODIFY ONLY THE CODE BETWEEN THESE LINES ======
-
-try:
-    os.stat(config['resultsdir'])
-except:
-    os.makedirs(config['resultsdir'])
-
-# each job command should be formatted as a string
-job_script = os.path.join(os.path.dirname(os.path.realpath(__file__)), 'pieman_cluster_level_chunked.py')
-
-cond_type = ['intact', 'paragraph', 'word', 'rest']
-
-# options for levels: integer
-levels = str('10')
-# options for reps: integer
-reps =  str('10')
-
-# options for reps: cfuns
-cfuns =  [str('isfc')]
-
-# options for reps: rfuns
-#rfuns =  [str('eigenvector_centrality'), str('pagerank_centrality'), str('strength')]
-rfuns =  [str('PCA')]
-
-# options for widths: integer
-widths = [str(10)]
-
-# options for weight functions: laplace, gaussian, mexican hat, delta
-weights = ['gaussian']
-
-# options for debug: True or False
-debug = str('False')
-
-job_commands = list(np.array([list(map(lambda x: x[0]+" "+str(x[1])+" "+levels+" "+str(r)+
-                                                 " "+cfuns[0]+" "+rfuns[0]+" "+widths[0]+" "+weights[0]+" "+debug,
-                                       zip([job_script]*len(cond_type), cond_type)))
-                              for r in range(int(reps))]).flat)
-
-# job_names should specify the file name of each script (as a list, of the same length as job_commands)
-job_names = list(np.array([list(map(lambda x: os.path.basename(os.path.splitext(x)[0])+'_'+levels+'_'+str(r)+'_'
-                                              +cfuns[0]+'_'+rfuns[0]+'_'+widths[0]+'_'+weights[0]+'_'+debug+'.sh', cond_type))
-                           for r in range(int(reps))]).flat)
-
-
-
-# ====== MODIFY ONLY THE CODE BETWEEN THESE LINES ======
-
-assert(len(job_commands) == len(job_names))
-
-
-# job_command is referenced in the run_job.sh script
-# noinspection PyBroadException,PyUnusedLocal
-def create_job(name, job_command):
-    # noinspection PyUnusedLocal,PyShadowingNames
-    def create_helper(s, job_command):
[…]

### 2019-09-06 paper/main.tex
more typo corrections, minor figure tweaks

@@
   to a temporally scrambled version of the story, or underwent a
-  resting state scan.  We trained across-participants pattern
+  resting state scan.  We trained across-participant pattern
   classifiers to decode (in held-out data) when in the session each
@@
 correlations in timeseries data. This framework provides an important
-advance, in that it enables us to examine patterns in higher-order
+advance, in that it enables us to examine patterns of higher-order
 correlations that are computationally intractable to estimate via
@@
 neuroimaging dataset collected as participants listened to either an
-audio recording of a ten-minute story or a temporally scrambled
+audio recording of a ten-minute story, listened to a temporally scrambled
 version of the story, or underwent a resting state
@@
                                               \widetilde{\sigma}_{\kappa_t}^2(\mathbf{X}(\cdot, j))}},~\mathrm{where}\label{eqn:timecorr}\\
-  \widetilde{\mathbf{X}}_{\kappa_t}(t) &= \sum_{\tau=1}^T
+  \widetilde{\mathbf{X}}_{\kappa_t}(\cdot, k) &= \sum_{\tau=1}^T
                        \kappa_t(\tau)\mathbf{X}(\tau, k),\\
@@
                                                   \mathbf{X}(\tau, k) -
-                            \widetilde{\mathbf{X}}_{\kappa_t}(t, k) \right)^2.
+                            \widetilde{\mathbf{X}}_{\kappa_t}(\cdot, k) \right)^2.
 \end{align}
@@
 \bar{\mathbf{C}}(t) = M\left(R\left(\frac{1}{2P} \sum_{p=1}^P
-  Z\left(Y_n^p(t)\right)^\mathrm{T} + Z\left(Y_n^p(t)\right)\right)\right),\label{eqn:disfc}
+  Z\left(\mathbf{Y}_{n+1}^p(t)\right)^\mathrm{T} + Z\left(\mathbf{Y}_{n+1}^p(t)\right)\right)\right),\label{eqn:disfc}
 \end{align}
-where $M$ extracts and vectorizes the diagonal and upper triangle of a symmetric
+where $M$ extracts and vectorizes the upper triangle and diagonal of a symmetric
 matrix, $Z$ is the Fisher $z$-transformation~\citep{Zar10}:
@@
 \end{align}
-and $\mathbf{Y}_n^p(t)$ denotes the correlation matrix at timepoint $t$
+and $\mathbf{Y}_{n+1}^p(t)$ denotes the correlation matrix at timepoint $t$
 (Eqn.~\ref{eqn:timecorr}) between each column of $\mathbf{X}_n^p$ and each
@@
 analysis~\cite[HTFA;][]{MannEtal18}, Topographic Latent Source
-Analysis~\cite[TLSA;][]{GersEtal11}, Dictionary
-learning~\citep{MairEtal09a, MairEtal09b}, deep
+Analysis~\cite[TLSA;][]{GersEtal11}, dictionary
+learning~\citep{MairEtal09a, MairEtal09b}, and deep
 auto-encoders~\citep{HintSala06}, among others.  While complete
@@
 the present manuscript, the general intuition driving these approaches
-is to compute the $T$ by $M$ matrix, $\mathbf{X}$, that is closest to
-the original $T$ by $N$ matrix, $\mathbf{Y}$, where (typically)
-$M \ll N$.  The different approaches place different constraints on
+is to compute the $T$ by $K$ matrix, $\mathbf{X}$, that is closest to
+the original $T$ by $J$ matrix, $\mathbf{Y}$, where (typically)
+$K \ll J$.  The different approaches place different constraints on
 what properties $\mathbf{X}$ must satisfy and which aspects of the
-data are compared (and how) in order to characterize how well
+data are compared (and how) in order to optimize how well
 $\mathbf{X}$ approximates $\mathbf{Y}$.
@@
 In other words, computing $\mathbf{X}_n$ is a lossy operation.
-Second, whereas each columns of $\mathbf{Y}_n$ may always be mapped
-directly onto specific pairs of columns of $\mathbf{Y}_{n-1}$, the
+Second, whereas each columns of $\mathbf{Y}_n$ may be mapped
+directly onto specific pairs of columns of $\mathbf{X}_{n-1}$, the
 columns of $\mathbf{X}_n$ reflect weighted combinations and/or
@@
 invertible).  However, attempting to map a given $\mathbf{X}_n$ back
-onto the original feature space of $\mathbf{Y}_0$ will usually require
+onto the original feature space of $\mathbf{X}_0$ will usually require
 $\mathcal{O}(TK^{2n})$ space and therefore quickly becomes intractable
@@
 column.  This results in a new $T$ by $K$ matrix, $\mathbf{X}_n$, that
-reflects how the features reflected in the columns of $\mathbf{Y}_n$
+reflects how the features reflected in the columns of $\mathbf{X}_{n-1}$
 participate in the network during each timepoint (row).
@@
 evaluate our general approach~\citep[for a related validation
-approach, see][]{ThomEtal18}.  Specifically, we tested how well
+approach see][]{ThomEtal18}.  Specifically, we tested how well
 Equation~\ref{eqn:timecorr} could be used to recover known dynamic
@@
 in similar spatial patterns across people.  Following this logic, we
-used an across-participants temporal decoding test developed by
+used an across-participant temporal decoding test developed by
 \cite{MannEtal18} to assess the degree to which different neural
@@
 \subsubsection*{Forward inference and decoding accuracy}
-We used an across-participants correlation-based classifier to decode
+We used an across-participant correlation-based classifier to decode
 which stimulus timepoint matched each timepoint's neural pattern.  We
@@
 orders of dynamic correlations).  Our objective was to find a set of
-weights of each of these $\mathbf{\Lambda}$ matrices such that the
+weights for each of these $\mathbf{\Lambda}$ matrices such that the
 weighted average of the $n+1$ matrices yielded the highest decoding
@@
 developed a computational framework for estimating the dynamics of
-high-order correlations in multivariate timeseries data (see
-\textit{Dynamic inter-subject functional connectivity (DISFC)} and
-\textit{Dynamic higher-order correlations}).  We evaluated the
-efficacy of this framework at recovering known patterns in several
-synthetic datasets (see \textit{Synthetic data}).  We then applied the
-framework to a public fMRI dataset collected as participants listened
-to an auditorally presented story, listened to a temporally scrambled
-version of the story, or underwent a resting state scan (see
-\textit{Functional neuroimaging data collected during story
-  listening}).  We used the relative decoding accuracies of
+stimulus-driven high-order correlations in multivariate timeseries
+data (see \textit{Dynamic inter-subject functional connectivity
+  (DISFC)} and \textit{Dynamic higher-order correlations}).  We
+evaluated the efficacy of this framework at recovering known patterns
+in several synthetic datasets (see \textit{Synthetic data}).  We then
+applied the framework to a public fMRI dataset collected as
+participants listened to an auditorally presented story, listened to a
+temporally scrambled version of the story, or underwent a resting
+state scan (see \textit{Functional neuroimaging data collected during
+  story listening}).  We used the relative decoding accuracies of
 classifiers trained on different sets of neural features to estimate
@@
     accuracy (intact: $\frac{1}{300}$; paragraph: $\frac{1}{272}$;
-    word: $\frac{1}{300}$; rest: $\frac{1}{400}$).  The error bars
+    word: $\frac{1}{300}$; rest: $\frac{1}{400}$).  The error ribbons
     denote 95\% confidence intervals across cross-validation folds

### 2019-09-09 paper/main.tex
inputted JRM edits

@@
 compare the relative contributions to the neural code of multivariate
-activity patterns versus patterns of dynamic correlations between
-neural activity patterns~\citep[e.g.,][]{MannEtal18, FongEtal19}.  An
-emerging theme in this literature is that cognition is mediated by
-dynamic interactions between brain structures~\citep{SporHone06,
-  BassEtal06, Turk13, DemeEtal19, SoloEtal19, LuriEtal18, PretEtal17,
-  ZouEtal19, MackEtal17}.
+activity patterns versus dynamic correlations between neural activity
+patterns~\citep[e.g.,][]{MannEtal18, FongEtal19}.  An emerging theme
+in this literature is that cognition is mediated by dynamic
+interactions between brain structures~\citep{SporHone06, BassEtal06,
+  Turk13, DemeEtal19, SoloEtal19, LuriEtal18, PretEtal17, ZouEtal19,
+  MackEtal17}.
 
@@
     algorithms project the patterns onto lower-dimensional spaces
-    whose dimensions reflect weighted combinations of the dimensions
-    in the original space.  Graph measures characterize each unit's
-    participation in its associated network.}
+    whose dimensions reflect weighted combinations or non-linear
+    transformations of the dimensions in the original space.  Graph
+    measures characterize each unit's participation in its associated
+    network.}
   \label{fig:patterns}
@@
 at
-\href{https://timecorr.readthedocs.io/}{timecorr.readthedocs.io}. \textbf{JRM
-  NOTE: CHECK LINK}
+\href{https://timecorr.readthedocs.io/}{timecorr.readthedocs.io}.
 
@@
                                                               \sigma^2_{\mathbf{X}(\cdot, i)} 
-                                                              \sigma^2_{\mathbf{X}(\cdot, j)}}},~\mathrm{where}\\\label{eqn:corr}
+                                                              \sigma^2_{\mathbf{X}(\cdot, j)}}},~\mathrm{where}\label{eqn:corr}\\
   \bar{\mathbf{X}}(\cdot, k) &= \frac{1}{T}\sum_{t=1}^T
@@
 of $\mathbf{X}$, estimated using the kernel $\kappa_t$.  We evaluate
-Equation~\ref{eqn:timecorr} in turn each pair of columns in
+Equation~\ref{eqn:timecorr} in turn for each pair of columns in
 $\mathbf{X}$ and for kernels centered on each timepoint in the
@@
 \bar{\mathbf{C}}(t) = M\left(R\left(\frac{1}{2P} \sum_{p=1}^P
-  Z\left(\mathbf{Y}_{n+1}^p(t)\right)^\mathrm{T} + Z\left(\mathbf{Y}_{n+1}^p(t)\right)\right)\right),\label{eqn:disfc}
+  Z\left(\mathbf{Y}_{n+1}^p(t)\right)^\top + Z\left(\mathbf{Y}_{n+1}^p(t)\right)\right)\right),\label{eqn:disfc}
 \end{align}
@@
 \begin{align}
-Z(r) = \frac{\log(1+r) - \log(1-r)}{2}
+Z(r) = \frac{\log(1+r) - \log(1-r)}{2},
 \end{align}
@@
 \begin{align}
-  \bar{\mathbf{X}}_n^{ \backslash p} = R\left(\frac{1}{P-1}\sum_{q \in
-  \backslash p} Z\left( \mathbf{X}_n^q \right) \right),
+  \bar{\mathbf{X}}_n^{ \backslash p} = \frac{1}{P-1}\sum_{q \in
+  \backslash p} \mathbf{X}_n^q,
 \end{align}
@@
 Given a $T$ by $\left( \frac{K^2 - K}{2} + K \right)$ matrix of
-dynamic correlations, $\mathbf{Y}_n$, we propose two general
-approaches to computing a $T$ by $K$ low-dimensional representation of
-those correlations, $\mathbf{X}_n$.  The first approach uses
-dimensionality reduction algorithms to project $\mathbf{Y}_n$ onto a
-$K$-dimensional space.  The second approach uses graph measures to
-characterize the relative positions of each feature
+$n^\mathrm{th}$-order dynamic correlations, $\mathbf{Y}_n$, we propose
+two general approaches to computing a $T$ by $K$ low-dimensional
+representation of those correlations, $\mathbf{X}_n$.  The first
+approach uses dimensionality reduction algorithms to project
+$\mathbf{Y}_n$ onto a $K$-dimensional space.  The second approach uses
+graph measures to characterize the relative positions of each feature
 ($k \in \left[1, ..., K \right]$) in the network defined by the
@@
 In other words, computing $\mathbf{X}_n$ is a lossy operation.
-Second, whereas each columns of $\mathbf{Y}_n$ may be mapped
+Second, whereas each column of $\mathbf{Y}_n$ may be mapped
 directly onto specific pairs of columns of $\mathbf{X}_{n-1}$, the
@@
 onto the original feature space of $\mathbf{X}_0$ will usually require
-$\mathcal{O}(TK^{2n})$ space and therefore quickly becomes intractable
+$\mathcal{O}(TK^{2n})$ space and therefore becomes intractable
 as $n$ or $K$ grow large.
@@
 correlation matrix or binarized correlation matrix reconstituted from
-a single timepoint's row of $\mathbf{Y}$) and return as output a set
+a single timepoint's row of $\mathbf{Y}$), and return as output a set
 of $K$ measures describing how each node (feature) sits within that
@@
 given node is from others in the population; e.g.,][]{Rao82, Lin09,
-  RicoSzei06}; Eigenvector centrality and pagerank
+  RicoSzei06}; eigenvector centrality and pagerank
 centrality~\citep[measures of how influential a given node is within
@@
 centrality~\citep[a measure of the connectivity of a node within its
-local sub-graph; e.g.,][]{AlvaEtal05, ChriFowl10}; within-module
+local subgraph; e.g.,][]{AlvaEtal05, ChriFowl10}; within-module
 degree~\citep[a measure of how many connections a node has to its
@@
 coefficient~\citep[a measure of the diversity of a node's connections
-to different sub-graphs in the network; e.g.,][]{RubiSpor10}; and
-sub-graph centrality~\citep[a measure of a node's participation in all
-of the network's sub-graphs; e.g.,][]{EstrRodr05}; among others.
+to different subgraphs in the network; e.g.,][]{RubiSpor10}; and
+subgraph centrality~\citep[a measure of a node's participation in all
+of the network's subgraphs; e.g.,][]{EstrRodr05}; among others.
 
@@
   datasets whose underlying correlations changed gradually over time.
-  For each dataset, we constructed two \textit{anchor} correlation
+  For each dataset, we constructed two \textit{anchor} covariance
   matrices using Equation~\ref{eqn:randcorr},
@@
 to an audio recording of a story (intact condition; 36 participants),
-listened to time scrambled recordings of the same story (17
+listened to temporally scrambled recordings of the same story (17
 participants in the paragraph-scrambled condition listened to the
@@
 people.  The approach entails using a subset of the data to train a
-classifier to decode stimulus timepoints (i.e., moment in the story
+classifier to decode stimulus timepoints (i.e., moments in the story
 participants listened to) from neural patterns.  We use decoding
@@
 at each timepoint.  We use the resulting decoding accuracy of
-$\mathcal{G}_{\mathrm{test}}$ timepoints to estimate how informative
+$\mathcal{G}_{\mathrm{test}}$ timepoints (using the weights in
+$\phi_{0, 1, ..., n}$ to average the $\Lambda$ matrices) to estimate how informative
 the set of neural features containing up to $n^\mathrm{th}$ order
@@
 parameter choices, we repeated our decoding analyses after
-substituting in each of a variety of kernel shapes and widths for
-Equation~\ref{eqn:timecorr}.  We examined Gaussian
+substituting into Equation~\ref{eqn:timecorr} each of a variety of
+kernel shapes and widths.  We examined Gaussian
 (Fig.~\ref{fig:kernels}c), Laplace (Fig.~\ref{fig:kernels}d), and
@@
     correlations between the randomly drawn correlation matrices at
-    first and last timepoints.  The left panel displays the
+    the first and last timepoints.  The left panel displays the
     correlations between the recovered dynamic correlations and the
@@
 where the words in the story occurred in a random order.  All
-participants in the word conditions experienced the scrambled words in
+participants in the word condition experienced the scrambled words in
 the same order.  Finally, in a \textit{rest} experimental condition,
@@
     of all other features (via a two-tailed test, thresholded at
-    $p < 0.05$).  Figure~\ref{fig:ttests} displays additional comparisons between
-    the decoding accuracies achieved using different sets of neural
-    features.  The circled values represent the maximum decoding
-    accuracy within each experimental condition.
+    $p < 0.05$).  Figure~\ref{fig:ttests} displays additional
+    comparisons between the decoding accuracies achieved using
+    different sets of neural features.  The circled values represent
+    the maximum decoding accuracy within each experimental condition.
     \textbf{b.~Normalized decoding accuracy as a function of order:
       PCA.}  This panel displays the same results as Panel a, but here
-    each curve has been normalized to have a maximum value of 1 and
-    and a minimum value of 0 (including the upper and lower bounds of
-    the respective 95\% confidence intervals).  Panels a and b used
-    PCA to project each high-dimensional pattern of dynamic
-    correlations onto a lower-dimensional space.  \textbf{c.~Decoding
-      accuracy as a function of order: eigenvector centrality.} This
-    panel is in the same format as Panel a, but here eigenvector
-    centrality has been used to project the high-dimensional patterns
-    of dynamic correlations onto a lower-dimensional space.
+    each curve has been normalized to have a maximum value of 1 and a
+    minimum value of 0 (including the upper and lower bounds of the
+    respective 95\% confidence intervals).  Panels a and b used PCA to
+    project each high-dimensional pattern of dynamic correlations onto
+    a lower-dimensional space.  \textbf{c.~Decoding accuracy as a
+      function of order: eigenvector centrality.} This panel is in the
+    same format as Panel a, but here eigenvector centrality has been
+    used to project the high-dimensional patterns of dynamic
+    correlations onto a lower-dimensional space.
     \textbf{d.~Normalized decoding accuracy as a function of order:
@@
 ``universal'' in the sense of optimally recovering underlying
-correlations regardless of the structure of those correlations.  We
-found a similar pattern in the (real) fMRI data, whereby different
-kernels yielded different decoding accuracies, but no single kernel
-emerged as the clear ``best.''  In our analyses of neural data, we
-therefore averaged our decoding results over a variety of kernel
-shapes and widths in order to identify results that were robust to
-specific kernel parameters (see \textit{Identifying robust
+correlations regardless of the temporal structure of those
+correlations.  We found a similar pattern in the (real) fMRI data,
+whereby different kernels yielded different decoding accuracies, but
+no single kernel emerged as the clear ``best.''  In our analyses of
+neural data, we therefore averaged our decoding results over a variety
+of kernel shapes and widths in order to identify results that were
+robust to specific kernel parameters (see \textit{Identifying robust
   decoding results}).
@@
 results for the auditory (non-rest) conditions of the experiment
-(Fig.~\ref{fig:decoding}: pink, yellow, and teal lines;
+(Fig.~\ref{fig:decoding}: pink, green, and teal lines;
 Fig.~\ref{fig:ttests}: three leftmost columns).  The highest
@@
     Additional maps and their corresponding Neurosynth terms may be
-    found in the \textit{Supplementary materials} (intact: Figure~\intact;
-    paragraph: Figure~\para; word: Figure~\word; rest: Figure~\rest).}
+    found in the \textit{Supplementary materials} (intact: Fig.~\intact;
+    paragraph: Fig.~\para; word: Fig.~\word; rest: Fig.~\rest).}
   \label{fig:neurosynth}
@@
 
-Identifying higher-order network dynamics associated with high-level
+Identifying high-order network dynamics associated with high-level
 cognition required several important methods advances.  First, we used

### 2019-09-09 code/scripts/pieman_cluster_submit_level_analysis.py
WIP code cleanup

@@ -33,7 +33,6 @@ reps =  str('10')
 cfuns =  [str('isfc')]
 
 # options for reps: rfuns
-#rfuns =  [str('eigenvector_centrality'), str('pagerank_centrality'), str('strength')]
 #rfuns =  [str('eigenvector_centrality')]
 rfuns = [str('PCA')]
 

### 2019-09-09 paper/main.tex

@@
   \includegraphics[width=\textwidth]{figs/patterns}
-  \caption{\textbf{Neural patterns.  a. A space of neural analyses}
+  \caption{\textbf{Neural patterns.  a. A space of neural features.}
     Within-brain analyses are carried out within a single brain,
@@
   \centering
-  \includegraphics[width=0.4\textwidth]{figs/methods_fig}
+  \includegraphics[width=0.5\textwidth]{figs/methods_fig}
   \caption{\textbf{Estimating dynamic high-order correlations.}  Given
@@
 a spatial function whose activations range from 0 to 1.  We
-thresholded each RBF at 0.999 to construct a map of spherical
-components that denoted the endpoints of the 10 strongest
-correlations.  We then carried out a meta analysis using
+constructed a map of RBF components that denoted the endpoints of the
+10 strongest correlations (we set each RBF to have a maximum value of
+1).  We then carried out a meta analysis using
 Neurosynth~\citep{RubiEtal17} to identify the 10 terms most commonly
@@
     display the locations of the endpoints of the 10 strongest
-    (absolute value) correlations at each order, projected onto the
-    cortical surface~\citep{CombEtal19}.  The lists of terms on the
-    right display the top five Neurosynth terms~\citep{RubiEtal17}
-    decoded from the corresponding brain maps for each order.  Each
-    row displays data from a different experimental condition.
-    Additional maps and their corresponding Neurosynth terms may be
-    found in the \textit{Supplementary materials} (intact: Fig.~\intact;
-    paragraph: Fig.~\para; word: Fig.~\word; rest: Fig.~\rest).}
+    (absolute value) correlations at each order, thresholded at 0.999,
+    and projected onto the cortical surface~\citep{CombEtal19}.  The
+    lists of terms on the right display the top five Neurosynth
+    terms~\citep{RubiEtal17} decoded from the corresponding brain maps
+    for each order.  Each row displays data from a different
+    experimental condition.  Additional maps and their corresponding
+    Neurosynth terms may be found in the \textit{Supplementary
+      materials} (intact: Fig.~\intact; paragraph: Fig.~\para; word:
+    Fig.~\word; rest: Fig.~\rest).}
   \label{fig:neurosynth}

### 2020-06-02 paper/main.tex
WIP nat comm revision

@@
 
+\begin{figure}[tp]
+  \centering
+  \includegraphics[width=\textwidth]{figs/higher_order_sims}
+  \caption{\textbf{Recovery of simulated first and second order dynamic correlations.}  Each panel displays the average correlations
+    between the vectorized upper triangles of the recovered
+    correlation matrix and the simulated correlation matrix at each
+    timepoint and for each synthetic dataset.  (The averages are taken across 10 different
+    randomly generated synthetic datasets of the given category.)
+    Error ribbons denote 95\% confidence intervals (taken across
+    datasets).  For a complete description of each synthetic dataset,
+    see \textit{Synthetic data}.  \textbf{a. Constant correlations.}
+    These first and second order dynamic correlation were
+    simulated from datasets have a stable (unchanging) underlying correlation
+    matrix.  \textbf{b. Random correlations.}  These first and second order dynamic correlation were
+    simulated from datasets are
+    generated using a new independently drawn correlation matrix at
+    each new timepoint.  \textbf{c. Ramping correlations.}  These first and second order dynamic correlation were
+    simulated from
+    datasets are generated by smoothly varying the underlying
+    correlations between the randomly drawn correlation matrices at
+    the first and last timepoints and displays the
+    correlations between the recovered dynamic correlations and the
+  simualted correlation first and second order correlation matrices.   \textbf{d. Event-based correlations.}  These first and second order dynamic correlation were
+    simulated from datasets are
+    each generated using five randomly drawn correlation matrices that
+    each remain stable for a fifth of the total timecourse.  }
+  \label{fig:higherr_order_sims}
+\end{figure}
+
 \subsection*{Cognitively relevant dynamic high-order correlations in
@@
 regions integrate information relatively slowly~\citep{BaldEtal17,
-  HassEtal08, HassEtal15, HoneEtal12a, LernEtal11, LernEtal14}.  Other
+  HassEtal08, HassEtal15, HoneEtal12a, LernEtal11, LernEtal14, ChieHone19}.  Other
 related work in human and mouse brains indicates that the temporal

### 2020-06-02 paper/supporting_information.tex
WIP nat comm revision

@@
 \renewcommand{\citenumfont}[1]{S#1}
+
+\begin{figure}[p!]
+\centering
+\includegraphics[width=0.75\textwidth]{figs/decode_levels_kernels}
+\caption{\textbf{Across-participant decoding accuracy varies with
+      correlation order and cognitive engagement across kernels}  \textbf{a-d..~Decoding accuracy as a function of order: PCA.}\textit{Order} ($x$-axis) refers to the maximum order of dynamic
+    correlations that were available to the classifiers (see
+    \textit{Feature weighting and testing}).  The reported
+    across-participant decoding accuracies are averaged over all
+    kernel shapes and widths (see \textit{Identifying robust decoding
+      results}).  The $y$-values are displayed relative to chance
+    accuracy (intact: $\frac{1}{300}$; paragraph: $\frac{1}{272}$;
+    word: $\frac{1}{300}$; rest: $\frac{1}{400}$).  The error ribbons
+    denote 95\% confidence intervals across cross-validation folds
+    (i.e., random assignments of participants to the training and test
+    sets).  The colors denote the experimental condition.  Arrows
+    denote sets of features that yielded reliably higher (upwards
+    facing) or lower (downward facing) decoding accuracy than the mean
+    of all other features (via a two-tailed test, thresholded at
+    $p < 0.05$).  Figure~\ref{fig:ttests} displays additional
+    comparisons between the decoding accuracies achieved using
+    different sets of neural features.  The circled values represent
+    the maximum decoding accuracy within each experimental condition.)}
+\label{fig:supp_kernels}
+\end{figure}
+
+\begin{figure}[p!]
+\centering
+\includegraphics[width=0.75\textwidth]{figs/decode_levels_widths}
+\caption{\textbf{Top terms associated with the endpoints of the
+    strongest correlations for the \textit{intact} experimental
+    condition.}  Each color corresponds to one order of inter-subject
+functional correlations. The inflated brain plots display the
+locations of the endpoints of the 10 strongest (absolute value)
+correlations at each order, projected onto the cortical
+surface~\citep{CombEtal19}.  The lists of terms display
+the top 10 Neurosynth terms~\citep{RubiEtal17} decoded from the
+corresponding brain maps for each order.  (Also see Fig.~\neurosynth,
+top row, in the main text.)}
+\label{fig:supp_widths}
+\end{figure}
 

### 2020-06-04 paper/main.tex
WIP paper higher order corrs write up

@@
 Fig.~\ref{fig:kernels}), for each of several synthetic datasets that
-exhibited different temporal properties.  We applied our approach to a
+exhibited different temporal properties. We also used this synthetic
+data to simulate higher-order correlations and tested how well Equation~\ref{eqn:timecorr}
+could recover these correlations using the best kernel from the
+previous synthetic data analysis.  We applied our approach to a
 functional neuroimaging dataset to test the hypothesis that ongoing
@@
 abrupt state changes.
+
+\subsubsection*{Simulated higher-order correlations}
+We simulated first and second order correlations reflecting the 4 qualitatively different patterns
+of synthetic dynamic correlations.
+ We repeated the processes 10 times for each order and for each of the 4 dynamic pattern (Constant, Random, Ramping, and
+Event) explored in \textit{Synthetic data}.  First,
+ we generated a timeseries of correlations which comprised 50 features (dimensions)
+that varied over 300 timepoints using 1 of the 4 \textit{Synthetic data} dynamic
+patterns. To calculate the next increasing order of corrrelations, ${ Y_{n+1,t}}$, we
+multiplied the vectorized correlation matrix by its transpose, for
+each timepoint:
+
+\begin{align}
+Y_{n+1,t} = vec(\mathbf{\Sigma}_{n,t})\cdot vec(\mathbf{\Sigma}_{n,t})^\top\label{eqn:veccorr}
+  \end{align}
+
+ Observations were then drawn at each timepoint from a  ${ Y_{n,t}}$-mean multivariate Gaussian distribution with a
+covariance matrix defined as ${ Y_{n+1,t}}$.
 
@@
 kernel parameters better recovered randomly varying correlations.
+
+\subsection*{Recovering known higher-order dynamic correlations from synthetic data}
+We generated synthetic datasets that differed in how the underlying
+correlations changed over time.  For each dataset, we applied
+Equation~\ref{eqn:timecorr} with a variety of kernel shapes and
+widths.  We assessed how well the true underlying correlations at each
+timepoint matched the recovered correlations
+(Fig.~\ref{fig:synthetic}).  For every kernel and dataset we tested,
+our approach recovered the correlation dynamics we embedded into the
+data.  However, the quality of these recoveries varied across
+different synthetic datasets in a kernel-dependent way.
 

### 2020-06-04 code/scripts/higher_order_sims.py

@@ -10,7 +10,7 @@ from matplotlib import pyplot as plt
 cond= sys.argv[1]
 r= sys.argv[2]
 
-F = 5 #number of features
+F = 4 #number of features
 T = 30 #number of timepoints
 K = 2 #order
 

### 2020-06-04 code/scripts/pieman_cluster_order_up.py

@@ -1,6 +1,6 @@
 
 import timecorr as tc
-from timecorr.helpers import isfc, corrmean_combine, reduce, vec2mat
+from timecorr.helpers import isfc, reduce, vec2mat
 from scipy.io import loadmat
 import numpy as np
 import sys
@@ -30,7 +30,7 @@ raw_fun = raw_parameter['weights']
 raw_params = raw_parameter['params']
 
 
-result_name = 'corrs_ordered_up'
+result_name = 'corrs_ordered_up_for_PCA'
 
 corrsdir = os.path.join(config['resultsdir'], result_name, cfun + '_' + rfun + '_' + smooth + '_' + str(width))
 
@@ -68,9 +68,8 @@ conds.extend([cond] * len(next_data))
 all_data = np.array(data)
 conds = np.array(conds)
 
-combine = corrmean_combine
 
-levels = range(3)
+levels = range(int(level))
 
 print(levels)
 
@@ -95,11 +94,11 @@ for lev in levels:
         print('data: ' + str(data[0][0]))
         print(str(lev) + '_smooth data calculated')
 
-        corr = tc.helpers.z2r(np.mean(tc.helpers.r2z(np.stack(data, axis=2)), axis=2))
+        #corr = tc.helpers.z2r(np.mean(tc.helpers.r2z(np.stack(data, axis=2)), axis=2))
 
         print(str(lev) + '_corrs calculated')
 
-        np.save(os.path.join(corrsdir, 'lev_' + str(lev) + '_' + cond + '.npy'), corr)
+        np.save(os.path.join(corrsdir, 'lev_' + str(lev) + '_' + cond + '.npy'), data)
 
         data = np.asarray(tc.timecorr([x for x in lev_data], cfun=isfc, rfun=None,
                                       weights_function=raw_fun, weights_params=raw_params))
@@ -119,24 +118,25 @@ for lev in levels:
         print('data_r: ' + str(data_r[0][0]))
     del data
 
+### to combine across patients:
 
-data_dir = '/dartfs/rc/lab/D/DBIC/CDL/f002s72/timecorr_paper/pieman/results'
-corrs_dir = os.path.join(data_dir, 'laplace_50_orderedup_corrs')
-
-levels = np.arange(0,16,1)
-conditions = ['intact', 'paragraph', 'rest', 'word']
-
-for l in levels:
-    for c in conditions:
-        con = os.path.join(corrs_dir, f'lev_{l}'+ f'_{c}'+ '.npy')
-        try:
[…]

### 2020-06-04 code/scripts/pieman_cluster_pca_leveled.py

@@ -1,0 +1,84 @@
+
+import timecorr as tc
+from timecorr.helpers import isfc, reduce, vec2mat
+from scipy.io import loadmat
+from sklearn.decomposition import PCA, IncrementalPCA
+import numpy as np
+import sys
+import os
+from config import config
+
+cond = sys.argv[1]
+level = sys.argv[2]
+cfun = sys.argv[3]
+rfun = sys.argv[4]
+width = int(sys.argv[5])
+
+laplace = {'name': 'Laplace', 'weights': tc.laplace_weights, 'params': {'scale': width}}
+delta = {'name': '$\delta$', 'weights': tc.eye_weights, 'params': tc.eye_params}
+gaussian = {'name': 'Gaussian', 'weights': tc.gaussian_weights, 'params': {'var': width}}
+mexican_hat = {'name': 'Mexican hat', 'weights': tc.mexican_hat_weights, 'params': {'sigma': width}}
+
+smooth = sys.argv[6]
+raw = 'delta'
+
+smooth_parameter = eval(smooth)
+raw_parameter = eval(raw)
+
+smooth_fun = smooth_parameter['weights']
+smooth_params = smooth_parameter['params']
+raw_fun = raw_parameter['weights']
+raw_params = raw_parameter['params']
+
+
+result_name = 'corrs_ordered_up_for_PCA'
+
+corrsdir = os.path.join(config['resultsdir'], result_name, cfun + '_' + rfun + '_' + smooth + '_' + str(width))
+
+levels = np.arange(0,4,1)
+conditions = ['intact', 'paragraph', 'rest', 'word']
+
+for l in levels:
+    for c in conditions:
+        con = os.path.join(corrsdir, f'lev_{l}'+ f'_{c}'+ '.npy')
+        try:
+            corrs = np.load(con)
+            for s in np.arange(corrs.shape[0]):
+                mat_corrs = tc.helpers.vec2mat(corrs[s])
+                x = mat_corrs
+                split = np.cumsum([len(xi) for xi in x])[:-1]
+                pca = IncrementalPCA(n_components=np.shape(x)[2])
+                x_r = np.vsplit(pca.fit_transform(np.vstack(x)), split)
+
+            #next_corrdir = os.path.join(data_dir, 'mean_corrs', f'level_{l}')
+            # if not os.path.exists(next_corrdir):
+            #     os.makedirs(next_corrdir)
+            # mean_corrs = mat_corrs.mean(axis=2)
[…]

### 2020-06-04 code/scripts/pieman_cluster_submit_order_up.py

@@ -24,7 +24,7 @@ cond_type = ['intact', 'paragraph', 'word', 'rest']
 #cond_type = ['paragraph']
 
 # options for levels: integer
-levels = str('16')
+levels = str('4')
 
 # options for reps: integer
 reps =  str('1')
@@ -34,7 +34,7 @@ cfuns =  [str('isfc')]
 
 # options for reps: rfuns
 #rfuns =  [str('eigenvector_centrality'), str('pagerank_centrality'), str('strength')]
-rfuns =  [str('eigenvector_centrality')]
+rfuns =  [str('eigenvector_centrality'), str('PCA')]
 
 # options for widths: integer
 widths = [str(50)]
@@ -43,13 +43,19 @@ widths = [str(50)]
 weights = ['laplace']
 
 
+param_grid = [(c, r, wi, we) for c in cfuns for r in rfuns for wi in widths for we in weights]
+
+
+
 job_commands = list(np.array([list(map(lambda x: x[0]+" "+str(x[1])+" "+levels+
-                                                 " "+cfuns[0]+" "+rfuns[0]+" "+widths[0]+" "+weights[0],
-                                       zip([job_script]*len(cond_type), cond_type)))]).flat)
+                                                 " "+e[0]+" "+e[1]+" "+e[2]+" "+e[3],
+                                       zip([job_script]*len(cond_type), cond_type)))
+                              for i, e in enumerate(param_grid)]).flat)
 
 # job_names should specify the file name of each script (as a list, of the same length as job_commands)
-job_names = list(np.array([list(map(lambda x: os.path.basename(os.path.splitext(x)[0])+'_'+levels+'_'+cfuns[0]
-                                              +'_'+rfuns[0]+'_'+widths[0]+'_'+weights[0]+'.sh', cond_type))]).flat)
+job_names = list(np.array([list(map(lambda x: os.path.basename(os.path.splitext(x)[0])+'_'+levels+'_'
+                                              +e[0]+'_'+e[1]+'_'+e[2]+'_'+e[3]+'.sh', cond_type))
+                           for i, e in enumerate(param_grid)]).flat)
 
 
 

### 2020-06-06 paper/main.tex
updates to paper and to pca level analysis

@@
 \begin{align}
-Y_{n+1,t} = vec(\mathbf{\Sigma}_{n,t})\cdot vec(\mathbf{\Sigma}_{n,t})^\top\label{eqn:veccorr}
+Y_{n=1,t} = vec(\mathbf{\Sigma}_{t})\cdot
+  vec(\mathbf{\Sigma}_{t})^\top \\
+  Y_{n+1,t} = vec(Y_{n,t}) \cdot vec(Y_{n,t})^\top\label{eqn:veccorr}
   \end{align}
 
- Observations were then drawn at each timepoint from a  ${ Y_{n,t}}$-mean multivariate Gaussian distribution with a
-covariance matrix defined as ${ Y_{n+1,t}}$.
+  We repeated this processes for the number of desired orders (N) to
+  generate a timeseries of $\mathbf{N^{th}}$ correlation matrices.  Then, observations were drawn at each timepoint from a  ${ Y_{N-1,t}}$-mean multivariate Gaussian distribution with a
+ covariance matrix defined as ${ Y_{N+1,t}}$ and the resultant vector
+ was reshaped to the matrix the size of ${ Y_{N-1,t}}$:
+ \begin{align}
+   { \hat{Y}_{N-1,t}} \sim vec(\mathcal{N}({ Y_{n,t}}, { Y_{N,t}}))^{-1}
+   \end{align}
+ This process was then repeated for all decreasing orders, in which
+ observations werre drawn at each timepoint from a  ${ Y_{n,t}}$-mean
+ multivariate Gaussian distribution, but the covariance matrix is
+ defined at the previously estimated reshaped matrix $\hat{Y}_{n,t}$:
+ \begin{align}
+   { \hat{Y}_{n,t}} \sim vec(\mathcal{N}({ Y_{n,t}}, {\hat{ Y}_{n+1,t}}))^{-1}
+ \end{align}
+We repeat this process until $n = 1$, then we drew observations at each timepoint
+from a zero-mean multivariate Gaussian distribution with a
+covariance matrix defined for each timepoint as described below:
+
+\begin{align}
+ s_t \sim \mathcal{N}(\mathbf{0},  \hat{Y}_{n=1,t})
+\end{align}
+
+For our specific analyses the resulting synthetic timeseries comprised
+50 features and 300 timepoints. We then used this synthetic data to test how well Equation~\ref{eqn:timecorr}
+could recover the simulated first and second order correlations.  To mitigate temporal blur in
+estimating each timeseries of dynamic correlations, we used a Dirac $\delta$ function
+kernel (which places all of its mass over a single timepoint)
+Fig.~\ref{fig:kernels}b) to compute each lower-order correlation and then used a
+Laplace kernel with a width of 20 to compute  $\mathbf{ X_{n,t}}$, applying
+temporal blur at just the last step.  Then, for each timepoint, we
+correlated the simulated correlation matix, ${ Y_{n,t}}$ with the
+Equation~\ref{eqn:timecorr} estimated correrlation matric, $\mathbf{ X_{n,t}}$.
 
@@
 \subsection*{Recovering known higher-order dynamic correlations from synthetic data}
-We generated synthetic datasets that differed in how the underlying
+We generated a synthetic timeseries from simulated first and second order dynamic correlation
+matrices that differed in how the underlying
 correlations changed over time.  For each dataset, we applied
-Equation~\ref{eqn:timecorr} with a variety of kernel shapes and
-widths.  We assessed how well the true underlying correlations at each
-timepoint matched the recovered correlations
-(Fig.~\ref{fig:synthetic}).  For every kernel and dataset we tested,
+Equation~\ref{eqn:timecorr} with a Laplace kernel with a width of 20.
+We assessed how well the recovered correlations matched simulated
+first and second order correlations. 
+(Fig.~\ref{fig:higher_order_sims}).  For every dataset we tested,
 our approach recovered the correlation dynamics we embedded into the
 data.  However, the quality of these recoveries varied across
-different synthetic datasets in a kernel-dependent way.
+different synthetic datasets.
 
@@
     each remain stable for a fifth of the total timecourse.  }
-  \label{fig:higherr_order_sims}
+  \label{fig:higher_order_sims}
 \end{figure}

### 2020-06-06 code/scripts/pieman_cluster_order_up.py

@@ -48,6 +48,8 @@ else:
     pieman_name = 'pieman_data.mat'
 
 pieman_data = loadmat(os.path.join(config['datadir'], pieman_name))
+pieman_conds = ['intact', 'paragraph', 'word', 'rest']
+
 
 data = []
 conds = []

### 2020-06-06 code/scripts/pieman_cluster_pca_leveled.py

@@ -4,6 +4,9 @@ from timecorr.helpers import isfc, reduce, vec2mat
 from scipy.io import loadmat
 from sklearn.decomposition import PCA, IncrementalPCA
 import numpy as np
+import scipy.stats
+import pandas as pd
+import seaborn as sns
 import sys
 import os
 from config import config
@@ -35,50 +38,40 @@ result_name = 'corrs_ordered_up_for_PCA'
 
 corrsdir = os.path.join(config['resultsdir'], result_name, cfun + '_' + rfun + '_' + smooth + '_' + str(width))
 
+pcadir = os.path.join(config['resultsdir'], result_name, 'corrs_results')
+
+try:
+    if not os.path.exists(pcadir):
+        os.makedirs(pcadir)
+except OSError as err:
+   print(err)
+
 levels = np.arange(0,4,1)
 conditions = ['intact', 'paragraph', 'rest', 'word']
 
 for l in levels:
-    for c in conditions:
-        con = os.path.join(corrsdir, f'lev_{l}'+ f'_{c}'+ '.npy')
-        try:
-            corrs = np.load(con)
-            for s in np.arange(corrs.shape[0]):
-                mat_corrs = tc.helpers.vec2mat(corrs[s])
-                x = mat_corrs
-                split = np.cumsum([len(xi) for xi in x])[:-1]
-                pca = IncrementalPCA(n_components=np.shape(x)[2])
-                x_r = np.vsplit(pca.fit_transform(np.vstack(x)), split)
+    con = os.path.join(corrsdir, f'lev_{l}'+ f'_{cond}'+ '.npy')
+    save_file = os.path.join(pcadir, f'rfun_{rfun}' + f'lev_{l}'+ f'_{cond}')
+    print(save_file)
+    corrs = np.load(con)
+    stacked = np.vstack(corrs)
+    split = np.cumsum([len(xi) for xi in corrs])[:-1]
+    pca = IncrementalPCA(n_components=np.shape(stacked)[1])
+    x_r = np.vsplit(pca.fit_transform(np.vstack(stacked)), split)
+    r = []
+    k_samps = np.unique(np.geomspace(3, corrs.shape[2], num=1000, dtype=int))
+    corrs_all = pd.DataFrame(index=k_samps, columns=np.arange(corrs.shape[0]))
+    for s in np.arange(corrs.shape[0]):
+        rs = []
+        S = x_r[s]
+        s_true = np.corrcoef(S)
[…]

### 2020-06-16 paper/supporting_information.tex
WIP pca fig

--- 2019-09-06 paper/supporting_information.tex
@@
 \renewcommand{\citenumfont}[1]{S#1}
+
+\begin{figure}[p!]
+\centering
+\includegraphics[width=0.95\textwidth]{figs/decode_levels_kernels}
+\caption{\textbf{Across-participant decoding accuracy varies with
+      correlation order and cognitive engagement across kernels.}
+    \textbf{a.-c.~Decoding accuracy as a function of order: PCA.} \textit{Order} ($x$-axis) refers to the maximum order of dynamic
+    correlations that were available to the classifiers (see
+    \textit{Feature weighting and testing}).  The reported
+    across-participant decoding accuracies for \textbf{a. Gaussian},
+    \textbf{b. Laplace}, and \textbf{c. Mexican hat} kernels are averaged over all
+   widths (see \textit{Identifying robust decoding
+      results}).  The $y$-values are displayed relative to chance
+    accuracy (intact: $\frac{1}{300}$; paragraph: $\frac{1}{272}$;
+    word: $\frac{1}{300}$; rest: $\frac{1}{400}$).  The error ribbons
+    denote 95\% confidence intervals across cross-validation folds
+    (i.e., random assignments of participants to the training and test
+    sets).  The colors denote the experimental condition.  Arrows
+    denote sets of features that yielded reliably higher (upwards
+    facing) or lower (downward facing) decoding accuracy than the mean
+    of all other features (via a two-tailed test, thresholded at
+    $p < 0.05$).  The circled values represent
+    the maximum decoding accuracy within each experimental
+    condition. Panels a.-c. used PCA to
+    project each high-dimensional pattern of dynamic correlations onto
+    a lower-dimensional space. \textbf{d.-f.~Decoding accuracy as a
+      function of order: eigenvector centrality.} This panel is in the
+    same format as Panel a.-c., but here eigenvector centrality has been
+    used to project the high-dimensional patterns of dynamic
+    correlations onto a lower-dimensional space.}
+\label{fig:supp_kernels}
+\end{figure}
+
+\begin{figure}[p!]
+\centering
+\includegraphics[width=0.95\textwidth]{figs/decode_levels_widths}
+\caption{\textbf{Across-participant decoding accuracy varies with
+      correlation order and cognitive engagement across widths.}
+    \textbf{a.-d.~Decoding accuracy as a function of order: PCA.} \textit{Order} ($x$-axis) refers to the maximum order of dynamic
+    correlations that were available to the classifiers (see
+    \textit{Feature weighting and testing}).  The reported
+    across-participant decoding accuracies for \textbf{a. 5},
+    \textbf{b. 10}, \textbf{c. 20}, and \textbf{d. 50}  are averaged over all
+    kernel shapes (see \textit{Identifying robust decoding
+      results}).  The $y$-values are displayed relative to chance
+    accuracy (intact: $\frac{1}{300}$; paragraph: $\frac{1}{272}$;
+    word: $\frac{1}{300}$; rest: $\frac{1}{400}$).  The error ribbons
+    denote 95\% confidence intervals across cross-validation folds
+    (i.e., random assignments of participants to the training and test
+    sets).  The colors denote the experimental condition.  Arrows
+    denote sets of features that yielded reliably higher (upwards
+    facing) or lower (downward facing) decoding accuracy than the mean
+    of all other features (via a two-tailed test, thresholded at
+    $p < 0.05$).  The circled values represent
+    the maximum decoding accuracy within each experimental condition.  Panels a.-d. used PCA to
+    project each high-dimensional pattern of dynamic correlations onto
+    a lower-dimensional space.\textbf{e.-h.~Decoding accuracy as a
+      function of order: eigenvector centrality.} This panel is in the
+    same format as Panel a.-d., but here eigenvector centrality has been
+    used to project the high-dimensional patterns of dynamic
+    correlations onto a lower-dimensional space.}
+\label{fig:supp_widths}
+\end{figure}
 
@@
 
+\begin{figure}[p!]
+\centering
+\includegraphics[width=0.75\textwidth]{figs/pca}
+\caption{\textbf{Cumulative percent variance explained as a function
+    of the number of principle components for correlation orders and reduction types.}  \textit{Order} refers to the order of the dynamic
+    correlations calculated. Principle components analysis was
+    performed, and reduced independently for each subject.  Maximum number of components varies with
+    the total time for each condition (intact: 300; paragraph:272;
+    word: 300; rest: 400). \textbf{a.~Cumlative percent
+    variance as a function of number of components for Order 0.} PCA
+  was performed on the raw acitivity patterns (Order 0). \textbf{b.-e.~Cumlative percent
+    variance as a function of number of components for Orders 1.-4.:
+    PCA} Dynamic correlation were calculated for orders 1-4 using PCA to
+    project each high-dimensional pattern of dynamic correlations onto
+    a lower-dimensional space.   \textbf{f.-i.~Cumlative percent
+    variance as a function of number of components for Orders 1.-4.: eigenvector centrality.} These panels arer in the
+    same format as Panel b.-e., but here eigenvector centrality has been
+    used to project the high-dimensional patterns of dynamic
+    correlations onto a lower-dimensional space. }
+\label{fig:pca}
+\end{figure}
+
 %\section*{Participant-level figures referenced in the main text}

### 2020-06-16 paper/main.tex
WIP paper

@@
 correlation matrix is unique (as in the random datasets), but where
-the correlation dynamics are structured.
+the correlation dynamics are structured and exhibit first-order
+autocorrelations (as in the constant datasets).
 
@@
   \caption{\textbf{Proposed high-order network dynamics underlying
-      high-level cognition during story listening.}  Higher orders of
+      high-level cognition during story listening.}  Schematic depicts
+    higher orders of
     network interactions support higher-level aspects of cognitive
@@
 role of temporal integration at different scales of network
-interaction, and across different anatomical structures.
+interaction, and across different anatomical structures. Importantly,
+our analyses do no speak to the physiological basis of higher-order
+dynamics, and could reflect nonlinearities, chaotic patterns,
+non-stationarities, or multistability, etc. However, our decoding analyses do indicate
+that higher-order dynamics are
+consistent across individuals, and therefore unlikely to be driven by
+non-stimulus-driven dynamics which are unlikely to be similar across
+individuals.
 

### 2020-06-16 paper/main.tex
updated text to reflect reviews up to PCA review

@@
   homologous lower-level dynamic correlations.  We tested the
-  hypothesis that high-level cognition is supported by high-order
+  hypothesis that high-level cognition is reflected in high-order
   dynamic correlations in brain activity patterns.  We developed an
@@
   first-order dynamic correlations or non-correlational activity patterns.  We
-  suggest that as our thoughts become more complex, they are supported
-  by higher-order patterns of dynamic network interactions throughout
+  suggest that as our thoughts become more complex, they are reflected
+  in higher-order patterns of dynamic network interactions throughout
   the brain.
@@
 \section*{Results}
-We sought to understand whether high-level cognition is supported by
+We sought to understand whether high-level cognition is reflected in
 dynamic patterns of high-order correlations.  To that end, we
@@
 means of testing our hypothesis that different levels of cognitive
-processing and engagement are supported by different orders of brain
+processing and engagement are reflected in different orders of brain
 activity dynamics.
@@
   \includegraphics[width=\textwidth]{figs/decode_level}
-  \caption{\textbf{Across-participant decoding accuracy varies with
+  \caption{\textbf{Across-participant timepoint decoding accuracy varies with
       correlation order and cognitive engagement.}
@@
     the maximum decoding accuracy within each experimental condition.
-    \textbf{b.~Normalized decoding accuracy as a function of order:
+    \textbf{b.~Normalized timepoint decoding accuracy as a function of order:
       PCA.}  This panel displays the same results as Panel a, but here
@@
     project each high-dimensional pattern of dynamic correlations onto
-    a lower-dimensional space.  \textbf{c.~Decoding accuracy as a
+    a lower-dimensional space.  \textbf{c.~Timepoint decoding accuracy as a
       function of order: eigenvector centrality.} This panel is in the
@@
     correlations onto a lower-dimensional space.
-    \textbf{d.~Normalized decoding accuracy as a function of order:
+    \textbf{d.~Normalized timepoint decoding accuracy as a function of order:
       eigenvector centrality.} This panel is in the same format as
@@
       strongest correlations.}  Each color corresponds to one order of
-    inter-subject functional correlations. The inflated brain plots
+    inter-subject functional correlations.  To calculate the dynamic
+    correlations, eigenvector centrality has been used to project
+    the high-dimensional patterns of dynamic correlations onto a
+    lower-dimensional space at each previous order, which allows us
+    the map the brain regions at each order by retaining the
+    features of the original space. The inflated brain plots
     display the locations of the endpoints of the 10 strongest
@@
 \section*{Discussion}
-We tested the hypothesis that high-level cognition is supported by
+We tested the hypothesis that high-level cognition is reflected in
 high-order brain network dynamics~\citep[e.g., see][]{SoloEtal19,
@@
     higher orders of
-    network interactions support higher-level aspects of cognitive
+    network interactions supporting higher-level aspects of cognitive
     processing.  When tasks evoke richer, deeper, and/or higher-level

### 2020-06-16 paper/supporting_information.tex
updated text to reflect reviews up to PCA review

@@
 \includegraphics[width=0.95\textwidth]{figs/decode_levels_kernels}
-\caption{\textbf{Across-participant decoding accuracy varies with
+\caption{\textbf{Across-participant timepoint decoding accuracy varies with
       correlation order and cognitive engagement across kernels.}
-    \textbf{a.-c.~Decoding accuracy as a function of order: PCA.} \textit{Order} ($x$-axis) refers to the maximum order of dynamic
+    \textbf{a.-c.~Timepoint decoding accuracy as a function of order: PCA.} \textit{Order} ($x$-axis) refers to the maximum order of dynamic
     correlations that were available to the classifiers (see
@@
     project each high-dimensional pattern of dynamic correlations onto
-    a lower-dimensional space. \textbf{d.-f.~Decoding accuracy as a
+    a lower-dimensional space. \textbf{d.-f.~Timepoint decoding accuracy as a
       function of order: eigenvector centrality.} This panel is in the
@@
 \includegraphics[width=0.95\textwidth]{figs/decode_levels_widths}
-\caption{\textbf{Across-participant decoding accuracy varies with
+\caption{\textbf{Across-participant timepoint decoding accuracy varies with
       correlation order and cognitive engagement across widths.}
-    \textbf{a.-d.~Decoding accuracy as a function of order: PCA.} \textit{Order} ($x$-axis) refers to the maximum order of dynamic
+    \textbf{a.-d.~Timepoint decoding accuracy as a function of order: PCA.} \textit{Order} ($x$-axis) refers to the maximum order of dynamic
     correlations that were available to the classifiers (see
@@
     project each high-dimensional pattern of dynamic correlations onto
-    a lower-dimensional space.\textbf{e.-h.~Decoding accuracy as a
+    a lower-dimensional space.\textbf{e.-h.~Timepoint decoding accuracy as a
       function of order: eigenvector centrality.} This panel is in the

### 2020-06-18 paper/supporting_information.tex
updates to PCA figure

@@
     performed, and reduced independently for each subject.  Maximum number of components varies with
-    the total time for each condition (intact: 300; paragraph:272;
+    the total time for each condition (intact: 300; paragraph: 272;
     word: 300; rest: 400). \textbf{a.~Cumlative percent
     variance as a function of number of components for Order 0.} PCA
-  was performed on the raw acitivity patterns (Order 0). \textbf{b.-e.~Cumlative percent
-    variance as a function of number of components for Orders 1.-4.:
-    PCA} Dynamic correlation were calculated for orders 1-4 using PCA to
+  was performed on the raw acitivity patterns (Order
+  0). \textbf{b.~Proportion of components to explain 85\% variance for
+    each condition and order.} PCA was performed for dynamic
+  correlations for each order.  Proportion was calculated by finding
+  the number of components to explain 85\% variance and dividing by
+  the total time for each condition (intact: 300; paragraph: 272;
+    word: 300; rest: 400).  Dynamic correlation were calculated for
+    orders 1-4 using PCA (solid lines) and eignenvector centrality
+    (dashed lines) to
     project each high-dimensional pattern of dynamic correlations onto
-    a lower-dimensional space.   \textbf{f.-i.~Cumlative percent
-    variance as a function of number of components for Orders 1.-4.: eigenvector centrality.} These panels arer in the
+    a lower-dimensional space.  \textbf{c.-f.~Cumlative percent
+    variance as a function of proportion of components for Orders 1.-4.:
+    PCA.} Dynamic correlation were calculated for orders 1-4 using PCA to
+    project each high-dimensional pattern of dynamic correlations onto
+    a lower-dimensional space.   \textbf{g.-j.~Cumlative percent
+    variance as a function of proportion of components for Orders 1.-4.: eigenvector centrality.} These panels arer in the
     same format as Panel b.-e., but here eigenvector centrality has been

### 2020-06-26 code/scripts/pieman_cluster_level_analysis.py
WIP removed reduce wrapper

@@ -50,7 +50,7 @@ delta = {'name': '$\delta$', 'weights': tc.eye_weights, 'params': tc.eye_params}
 gaussian = {'name': 'Gaussian', 'weights': tc.gaussian_weights, 'params': {'var': width}}
 mexican_hat = {'name': 'Mexican hat', 'weights': tc.mexican_hat_weights, 'params': {'sigma': width}}
 
-factors = 700
+factors = 100
 
 if factors == 100:
     pieman_name = 'pieman_ica100.mat'

### 2020-06-26 code/scripts/pieman_cluster_level_analysis.py
updates to decoding analysis

@@ -1,6 +1,6 @@
 
 import timecorr as tc
-from timecorr.helpers import isfc, wisfc, mean_combine, corrmean_combine
+from timecorr.helpers import isfc, wisfc, autofc, mean_combine, corrmean_combine
 from scipy.io import loadmat
 import numpy as np
 import sys

### 2020-10-07 paper/main.tex
WIP removed reduce wrapper
recompiled pdf, updated formatting

@@
 Neighbor Embedding~\citep[$t$-SNE;][]{MaatHint08}, Uniform Manifold
-Approximation and Projection~\citep[UMAP;][]{McInHeal18}, non-negative
+Approximation and Projection~\citep[UMAP;][]{McInEtal18}, non-negative
 matrix factorization~\citep[NMF;][]{LeeSeun99}, Topographic Factor
@@
 $\mathbf{X}_1$, $\mathbf{X}_2$, $\mathbf{X}_3$, and so on.
+
+\begin{figure}[tp]
+  \centering
+  \includegraphics[width=0.7\textwidth]{figs/timecorr_pipeline}
+  \caption{\textbf{Across-participant timepoint decoding accuracy varies with
+      correlation order and cognitive engagement.}
+    \textbf{a.~Decoding accuracy as a function of order: PCA.}
+    \textit{Order} ($x$-axis) refers to the maximum order of dynamic
+    correlations that were available to the classifiers (see
+    \textit{Feature weighting and testing}).  The reported
+    across-participant decoding accuracies are averaged over all
+    kernel shapes and widths (see \textit{Identifying robust decoding
+      results}).  The $y$-values are displayed relative to chance
+    accuracy (intact: $\frac{1}{300}$; paragraph: $\frac{1}{272}$;
+    word: $\frac{1}{300}$; rest: $\frac{1}{400}$).  The error ribbons
+    denote 95\% confidence intervals across cross-validation folds
+    (i.e., random assignments of participants to the training and test
+    sets).  The colors denote the experimental condition.  Arrows
+    denote sets of features that yielded reliably higher (upwards
+    facing) or lower (downward facing) decoding accuracy than the mean
+    of all other features (via a two-tailed test, thresholded at
+    $p < 0.05$).  Figure~\ref{fig:ttests} displays additional
+    comparisons between the decoding accuracies achieved using
+    different sets of neural features.  The circled values represent
+    the maximum decoding accuracy within each experimental condition.
+    \textbf{b.~Normalized timepoint decoding accuracy as a function of order:
+      PCA.}  This panel displays the same results as Panel a, but here
+    each curve has been normalized to have a maximum value of 1 and a
+    minimum value of 0 (including the upper and lower bounds of the
+    respective 95\% confidence intervals).  Panels a and b used PCA to
+    project each high-dimensional pattern of dynamic correlations onto
+    a lower-dimensional space.  \textbf{c.~Timepoint decoding accuracy as a
+      function of order: eigenvector centrality.} This panel is in the
+    same format as Panel a, but here eigenvector centrality has been
+    used to project the high-dimensional patterns of dynamic
+    correlations onto a lower-dimensional space.
+    \textbf{d.~Normalized timepoint decoding accuracy as a function of order:
+      eigenvector centrality.} This panel is in the same format as
+    Panel b, but here eigenvector centrality has been used to project
+    the high-dimensional patterns of dynamic correlations onto a
+    lower-dimensional space.}
+  \label{fig:pipeline}
+\end{figure}
 

### 2020-10-20 paper/main.tex
updated description of synthetic data with given high-order dynamics

@@
 
-\subsubsection*{Simulated higher-order correlations}
-We simulated first and second order correlations reflecting the 4 qualitatively different patterns
-of synthetic dynamic correlations.
- We repeated the processes 10 times for each order and for each of the 4 dynamic pattern (Constant, Random, Ramping, and
-Event) explored in \textit{Synthetic data}.  First,
- we generated a timeseries of correlations which comprised 50 features (dimensions)
-that varied over 300 timepoints using 1 of the 4 \textit{Synthetic data} dynamic
-patterns. To calculate the next increasing order of corrrelations, ${ Y_{n+1,t}}$, we
-multiplied the vectorized correlation matrix by its transpose, for
-each timepoint:
-
+\subsubsection*{Synthetic data: simulating dynamic high-order
+  correlations}
+
+We developed an iterative procedure for constructing timeseries data
+that exhibits known dynamic high-order correlations.  The procedure
+builds on our approach to generating dynamic first-order correlations.
+Essentially, once we generate a timeseries with known first-order
+correlations, we can use the known first-order correlations as a
+template to generate a new timeseries of second-order correlations.
+In turn, we can generate a timeseries of third-order correlations from
+the second-order correlations, and so on.  In general, we can generate
+order $n$ correlations given a timeseries of order $n - 1$ correlations,
+for any $n > 1$.  Finally, given the order $n$ timeseries, we can
+reverse the preceding process to generate an order $n - 1$ timeseries, an
+order $n - 2$ order timeseries, and so on, until we obtain an order 0
+timeseries of simulated data that reflects the chosen high-order dynamics.
+
+The central mathematical operations in our procedure are two
+functions, $\mathrm{vec}(\cdot)$ and $\mathrm{mat}(\cdot)$.  The
+$\mathrm{vec}(\cdot)$ function takes as input a $K \times K$ symmetric
+matrix and returns as output a
+$\left(\frac{K^2 - K}{2} + K\right)$-dimensional column vector
+containing the entries in the upper triangle and diagonal.  The
+$\mathrm{mat}(\cdot)$ function inverts $\mathrm{vec}(\cdot)$ by taking
+as input a $\left(\frac{K^2 - K}{2} + K\right)$-dimensional column
+vector and returning a $K \times K$ symmetric matrix as output.  We
+can then generate an order $n$ correlation matrix (for one timepoint, $t$) from an order
+$n - 1$ template (from the same timepoint) as follows:
 \begin{align}
-Y_{n=1,t} = vec(\mathbf{\Sigma}_{t})\cdot
-  vec(\mathbf{\Sigma}_{t})^\top \\
-  Y_{n+1,t} = vec(Y_{n,t}) \cdot vec(Y_{n,t})^\top\label{eqn:veccorr}
+  \mathbf{\Sigma_{n}}(t) &= \mathrm{mat}(\mathrm{vec}(\mathbf{\Sigma_{n-1}}(t)) \otimes \mathrm{vec}(\mathbf{\Sigma_{n-1}}(t))^\top).\label{eqn:veccorr}
 \end{align}
 
-  We repeated this processes for the number of desired orders (N) to
-  generate a timeseries of $\mathbf{N^{th}}$ correlation matrices.  Then, observations were drawn at each timepoint from a  ${ Y_{N-1,t}}$-mean multivariate Gaussian distribution with a
- covariance matrix defined as ${ Y_{N+1,t}}$ and the resultant vector
- was reshaped to the matrix the size of ${ Y_{N-1,t}}$:
+Given a timeseries of order $n$ correlation matrices, we can draw an
+order $n-1$ correlation matrix for each timpoint $t$ using
 \begin{align}
-   { \hat{Y}_{N-1,t}} \sim vec(\mathcal{N}({ Y_{n,t}}, { Y_{N,t}}))^{-1}
+ \mathbf{\sigma_{n-1}}(t) &\sim \mathcal{N}\left(\mathbf{0}, \mathbf{\Sigma_n}(t)
+                   \right)\label{eqn:highorder-gen1}\\
+  \mathbf{\Sigma_{n-1}}(t) &= \mathrm{mat}(\mathbf{\sigma_{n-1}}(t)).\label{eqn:highorder-gen2}
   \end{align}
- This process was then repeated for all decreasing orders, in which
- observations werre drawn at each timepoint from a  ${ Y_{n,t}}$-mean
- multivariate Gaussian distribution, but the covariance matrix is
- defined at the previously estimated reshaped matrix $\hat{Y}_{n,t}$:
- \begin{align}
-   { \hat{Y}_{n,t}} \sim vec(\mathcal{N}({ Y_{n,t}}, {\hat{ Y}_{n+1,t}}))^{-1}
- \end{align}
-We repeat this process until $n = 1$, then we drew observations at each timepoint
-from a zero-mean multivariate Gaussian distribution with a
-covariance matrix defined for each timepoint as described below:
-
-\begin{align}
- s_t \sim \mathcal{N}(\mathbf{0},  \hat{Y}_{n=1,t})
-\end{align}
-
-For our specific analyses the resulting synthetic timeseries comprised
-50 features and 300 timepoints. We then used this synthetic data to test how well Equation~\ref{eqn:timecorr}
-could recover the simulated first and second order correlations.  To mitigate temporal blur in
-estimating each timeseries of dynamic correlations, we used a Dirac $\delta$ function
-kernel (which places all of its mass over a single timepoint)
-Fig.~\ref{fig:kernels}b) to compute each lower-order correlation and then used a
-Laplace kernel with a width of 20 to compute  $\mathbf{ X_{n,t}}$, applying
-temporal blur at just the last step.  Then, for each timepoint, we
-correlated the simulated correlation matix, ${ Y_{n,t}}$ with the
-Equation~\ref{eqn:timecorr} estimated correrlation matric, $\mathbf{ X_{n,t}}$.
+  We can then use repeated applications of
+  Equations~\ref{eqn:highorder-gen1} and~\ref{eqn:highorder-gen2} in
+  order to obtain a synthetic dataset.
+
+ When the template first-order correlations are constructed to exhibit different
+ temporal profiles (e.g., using the constant, random, ramping, and
+ event procedures described above), the resulting high-order
+ correlations and synthetic data will exhibit the same category of
+ temporal profile.
+
+ Following our approach to generating synthetic data exhibiting known
+ first-order correlations, we constructed a total of 40 additional multivariate timeseries,
+collectively reflecting a total of 4 qualitatively different patterns
+of dynamic correlations (i.e., 10 datasets reflecting each type of
+dynamic pattern: constant, random, ramping, and event).
 

### 2020-10-23 paper/main.tex
took a complete pass through paper, updated bibliography, reorganized sections

@@
 brain structures;][]{MannEtal18, FongEtal19, LuriEtal18, PretEtal17,
-  ZouEtal19, DemeEtal19}.  We wondered what the future of this line of
-work might hold.  For example, is the neural code mediated by
+  ZouEtal19, DemeEtal19}.  What might the future of this line of work
+hold?  For example, is the neural code implemented through
 higher-order interactions between brain structures~\citep[e.g.,
@@
 structures.
+
+\section*{Results}
+We sought to understand whether high-level cognition is reflected in
+dynamic patterns of high-order correlations.  To that end, we
+developed a computational framework for estimating the dynamics of
+stimulus-driven high-order correlations in multivariate timeseries
+data (see \textit{Dynamic inter-subject functional connectivity
+  (DISFC)} and \textit{Dynamic higher-order correlations}).  We
+evaluated the efficacy of this framework at recovering known patterns
+in several synthetic datasets (see \textit{Synthetic data: simulating
+  dynamic first-order correlations} and \textit{Synthetic data:
+  simulating dynamic higher-order correlations}).  We then
+applied the framework to a public fMRI dataset collected as
+participants listened to an auditorally presented story, listened to a
+temporally scrambled version of the story, or underwent a resting
+state scan (see \textit{Functional neuroimaging data collected during
+  story listening}).  We used the relative decoding accuracies of
+classifiers trained on different sets of neural features to estimate
+which types of features reflected ongoing cognitive processing.
+
+\subsection*{Recovering known dynamic correlations from synthetic
+  data}
+\subsubsection*{Recovering dynamic first-order correlations}
+We generated synthetic datasets that differed in how the underlying first-order
+correlations changed over time.  For each dataset, we applied
+Equation~\ref{eqn:timecorr} with a variety of kernel shapes and
+widths.  We assessed how well the true underlying correlations at each
+timepoint matched the recovered correlations
+(Fig.~\ref{fig:synthetic}).  For every kernel and dataset we tested,
+our approach recovered the correlation dynamics we embedded into the
+data.  However, the quality of these recoveries varied across
+different synthetic datasets in a kernel-dependent way.
+
+\begin{figure}[tp]
+  \centering
+  \includegraphics[width=\textwidth]{figs/synthetic_data}
+  \caption{\textbf{Recovering known dynamic first-order correlations
+      from synthetic data.}  Each panel displays the average
+    correlations between the vectorized upper triangles of the
+    recovered correlation matrix at each timepoint and either the true
+    underlying correlation at each timepoint or a reference
+    correlation matrix.  (The averages are taken across 10 different
+    randomly generated synthetic datasets of the given category.)
+    Error ribbons denote 95\% confidence intervals (taken across
+    datasets). Different colors denote different kernel shapes, and
+    the shading within each color family denotes the kernel width
+    parameter.  For a complete description of each synthetic dataset,
+    see \textit{Synthetic data: simulating dynamic first-order
+      correlations}.  \textbf{a. Constant correlations.}  These
+    datasets have a stable (unchanging) underlying correlation matrix.
+    \textbf{b. Random correlations.}  These datasets are generated
+    using a new independently drawn correlation matrix at each new
+    timepoint.  \textbf{c. Ramping correlations.}  These datasets are
+    generated by smoothly varying the underlying correlations between
+    the randomly drawn correlation matrices at the first and last
+    timepoints.  The left panel displays the correlations between the
+    recovered dynamic correlations and the underlying ground truth
+    correlations.  The middle panel compares the recovered
+    correlations with the \textit{first} timepoint's correlation
+    matrix.  The right panel compares the recovered correlations with
+    the \textit{last} timepoint's correlation matrix.
+    \textbf{d. Event-based correlations.}  These datasets are each
+    generated using five randomly drawn correlation matrices that each
+    remain stable for a fifth of the total timecourse.  The left panel
+    displays the correlations between the recovered dynamic
+    correlations and the underlying ground truth correlations.  The
+    right panels compare the recovered correlations with the
+    correlation matrices unique to each event.}
+  \label{fig:synthetic}
+\end{figure}
+
+In general, wide monotonic kernel shapes (Laplace, Gaussian), and
+wider kernels (within a shape), performed best when the correlations
+varied gradually from moment-to-moment (Figs.~\ref{fig:synthetic}a, c,
+and d).  In the extreme, as the rate of change in correlations
+approaches 0 (Fig.~\ref{fig:synthetic}a), an infinitely wide kernel
+would exactly recover the Pearson's correlation (e.g., compare
+Eqns.~\ref{eqn:corr} and \ref{eqn:timecorr}).
+
+When the correlation dynamics were unstructured in time
+(Fig.~\ref{fig:synthetic}b), a Dirac $\delta$ kernel (infinitely
+narrow) performed best.  This is because, when every timepoint's
+correlations are independent of the correlations at every other
+timepoint, averaging data over time dilutes the available signal.
+Following a similar pattern, holding kernel shape fixed, narrower
+kernel parameters better recovered randomly varying correlations.
+
+\subsubsection*{Recovering dynamic higher-order correlations}
+Following our approach to evaluating our ability to recover known
+dynamic first-order correlations from synthetic data, we generated an
+analogous second set of synthetic datasets that we designed to exhibit
+known dynamic first-order \textit{and} second-order correlations (see
+\textit{Synthetic data: simulating dynamic higher-order
+  correlations}).  We generated a total of 40 datasets that varied in
+how the first-order and second-order correlations changed over time.
+We then repeatedly applied Equation~\ref{eqn:timecorr} using the
+overall best-performing kernel from our first-order tests (a Laplace
+kernel with a width of 20; Fig.~\ref{fig:synthetic}) to assess how
+closely the recovered dynamic correlations matched the dynamic
+correlations we had embedded into the datasets.
+
+Overall, we found that we could reliably recover both first-order and
+second-order correlations from the synthetic data
+(Fig.~\ref{fig:higher_order_sims}).  When the correlations were stable
+for longer intervals, or changed gradually (constant, ramping, and
+event datasets), recovery performance was relatively high, and we were
+better able to recover dynamic first-order correlations than
+second-order correlations.  We expected that this would happen, given
+that errors in our estimation procedure at lower orders necessarily
+propagate to higher orders (since lower-order correlations are used to
+estimate higher-order correlations).  Interestingly, we also found
+that when the correlations were particularly \textit{un}stable (random
+datasets), we better recovered second-order correlations.
+
+\begin{figure}[tp]
+  \centering
+  \includegraphics[width=\textwidth]{figs/higher_order_sims}
+  \caption{\textbf{Recovery of simulated first-order and second-order dynamic correlations.}  Each panel displays the average correlations
+    between the vectorized upper triangles of the recovered
+    correlation matrix and the simulated correlation matrix at each
+    timepoint and for each synthetic dataset.  (The averages are taken across 10 different
+    randomly generated synthetic datasets of the given category.)
+    Error ribbons denote 95\% confidence intervals (taken across
+    datasets).  For a complete description of each synthetic dataset,
+    see \textit{Synthetic data: simulating dynamic higher-order
+      correlations}.  All results in this figure used a Laplace kernel
+    (width~$=20$).  \textbf{a. Constant correlations.}
+    These first and second order dynamic correlation were
+    simulated from datasets have a stable (unchanging) underlying correlation
+    matrix.  \textbf{b. Random correlations.}  These first and second order dynamic correlation were
+    simulated from datasets are
+    generated using a new independently drawn correlation matrix at
+    each new timepoint.  \textbf{c. Ramping correlations.}  These first and second order dynamic correlation were
+    simulated from
+    datasets are generated by smoothly varying the underlying
+    correlations between the randomly drawn correlation matrices at
+    the first and last timepoints and displays the
+    correlations between the recovered dynamic correlations and the
+  simualted correlation first and second order correlation matrices.   \textbf{d. Event-based correlations.}  These first and second order dynamic correlation were
+    simulated from datasets are
+    each generated using five randomly drawn correlation matrices that
+    each remain stable for a fifth of the total timecourse.  }
+  \label{fig:higher_order_sims}
+\end{figure}
+
+Taken together, our explorations using synthetic data indicated that
+we are able to partially, but not perfectly, recover ground truth
+dynamic first-order and second-order correlations.  This suggests that
+our modeling approach provides a meaningful (if noisy) estimate of
+high-order correlations.  We next turned to analyses of human fMRI data
+to examine whether the recovered dynamics might reflect the dynamics
+of human cognition during a naturalistic story-listening task.
+
+\subsection*{Cognitively relevant dynamic high-order correlations in
+  fMRI data}
+We used across-participant temporal decoders to identify cognitively
+relevant neural patterns in fMRI data (see \textit{Forward inference
+  and decoding accuracy}).  The dataset we examined~\citep[collected
+by][]{SimoEtal16} comprised four experimental conditions that exposed
+participants to stimuli that varied systematically in how cognitively
+engaging they were.  The \textit{intact} experimental condition had
+participants listen to an audio recording of a 10-minute story.  The
+\textit{paragraph}-scrambled experimental condition had participants
+listen to a temporally scrambled version of the story, where the
+paragraphs occurred out of order (but where the same total set of
+paragraphs were presented over the full listening interval).  All
+participants in this condition experienced the scrambled paragraphs in
+the same order.  The \textit{word}-scrambled experimental condition
+had participants listen to a temporally scrambled version of the story
+where the words in the story occurred in a random order.  All
+participants in the word condition experienced the scrambled words in
+the same order.  Finally, in a \textit{rest} experimental condition,
+participants lay in the scanner with no overt stimulus, with their
+eyes open (blinking as needed).  This dataset provided a convenient
+means of testing our hypothesis that different levels of cognitive
+processing and engagement are reflected in different orders of brain
+activity dynamics.
+
+\begin{figure}[tp]
+  \centering
+  \includegraphics[width=\textwidth]{figs/decode_level}
+  \caption{\textbf{Across-participant timepoint decoding accuracy varies with
+      correlation order and cognitive engagement.}
+    \textbf{a.~Decoding accuracy as a function of order: PCA.}
+    \textit{Order} ($x$-axis) refers to the maximum order of dynamic
+    correlations that were available to the classifiers (see
+    \textit{Feature weighting and testing}).  The reported
+    across-participant decoding accuracies are averaged over all
+    kernel shapes and widths (see \textit{Identifying robust decoding
+      results}).  The $y$-values are displayed relative to chance
+    accuracy (intact: $\frac{1}{300}$; paragraph: $\frac{1}{272}$;
+    word: $\frac{1}{300}$; rest: $\frac{1}{400}$).  The error ribbons
+    denote 95\% confidence intervals across cross-validation folds
+    (i.e., random assignments of participants to the training and test
+    sets).  The colors denote the experimental condition.  Arrows
+    denote sets of features that yielded reliably higher (upwards
+    facing) or lower (downward facing) decoding accuracy than the mean
+    of all other features (via a two-tailed test, thresholded at
+    $p < 0.05$).  Figure~\ref{fig:ttests} displays additional
+    comparisons between the decoding accuracies achieved using
+    different sets of neural features.  The circled values represent
+    the maximum decoding accuracy within each experimental condition.
+    \textbf{b.~Normalized timepoint decoding accuracy as a function of order:
+      PCA.}  This panel displays the same results as Panel a, but here
+    each curve has been normalized to have a maximum value of 1 and a
+    minimum value of 0 (including the upper and lower bounds of the
+    respective 95\% confidence intervals).  Panels a and b used PCA to
+    project each high-dimensional pattern of dynamic correlations onto
+    a lower-dimensional space.  \textbf{c.~Timepoint decoding accuracy as a
+      function of order: eigenvector centrality.} This panel is in the
+    same format as Panel a, but here eigenvector centrality has been
+    used to project the high-dimensional patterns of dynamic
+    correlations onto a lower-dimensional space.
+    \textbf{d.~Normalized timepoint decoding accuracy as a function of order:
+      eigenvector centrality.} This panel is in the same format as
+    Panel b, but here eigenvector centrality has been used to project
+    the high-dimensional patterns of dynamic correlations onto a
+    lower-dimensional space.}
+  \label{fig:decoding}
+\end{figure}
+
+In brief, we computed timeseries of dynamic high-order correlations
+that were similar across participants in each of two randomly assigned
+groups: a training group and a test group.  We then trained
+classifiers on the training group's data to match each sample from the
+test group with a stimulus timepoint.  Each classifier comprised a
+weighted blend of neural patterns that reflected up to
+$n^\mathrm{th}$-order dynamic correlations (see \textit{Feature
+  weighting and testing}, Fig.~\ref{fig:pipeline}).  We repeated this process for
+$n \in \left\{ 0, 1, 2, ..., 10 \right\}$.  Our examinations of
+synthetic data suggested that none of the kernels we examined were
+``universal'' in the sense of optimally recovering underlying
+correlations regardless of the temporal structure of those
+correlations.  We found a similar pattern in the (real) fMRI data,
+whereby different kernels yielded different decoding accuracies, but
+no single kernel emerged as the clear ``best.''  In our analyses of
+neural data, we therefore averaged our decoding results over a variety
+of kernel shapes and widths in order to identify results that were
+robust to specific kernel parameters (see \textit{Identifying robust
+  decoding results}).
+
+Our approach to estimating dynamic high-order correlations entails
+mapping the high-dimensional feature space of correlations
+(represented by a $T$ by
+$\mathcal{O}(K^2)$ matrix) onto a lower-dimensional feature space
+(represented by a $T$ by $K$ matrix).
+We carried out two sets of analyses that differed in how this mapping
+was computed.  The first set of analyses used PCA to find a
+low-dimensional embedding of the original dynamic correlation matrices
+(Fig.~\ref{fig:decoding}a,b).  The second set of analyses
+characterized correlations in dynamics of each feature's eigenvector
+centrality, but did not preserve the underlying activity dynamics
+(Fig.~\ref{fig:decoding}c,d).
+
+\begin{figure}[tp]
+\centering
+\includegraphics[width=1\textwidth]{figs/stats_heatmaps}
+\caption{\textbf{Statistical summary of decoding accuracies for
+    different neural features.}  Each column displays decoding
+  results for one experimental condition (intact, paragraph, word, and
+  rest).  We considered dynamic activity patterns (order 0) and
+  dynamic correlations at different orders (order $> 0$).  We used
+  two-tailed $t$-tests to compare the
+  distributions of decoding accuracies obtained using each pair of
+  features.  The distributions for each feature reflect the set of
+  average decoding accuracies (across all kernel parameters), obtained
+  for each random assignment of training and test groups.
+  In the upper triangles of each map, warmer colors (positive $t$-values) indicate that the
+  neural feature indicated in the given row yielded higher accuracy than the
+  feature indicated in the given column.  Cooler colors (negative
+  $t$-values) indicate that
+  the feature in the given row yielded lower decoding accuracy than
+  the feature in the given column.  The lower triangles of each map
+  denote the corresponding $p$-values for the $t$-tests.  The diagonal
+  entries display the relative average optimized weight given to each type of feature, in
+  a decoder that included all feature types (see \textit{Feature
+    weighting and testing}).}
+\label{fig:ttests}
+\end{figure}
+
+Both sets of temporal decoding analyses yielded qualitatively similar
+results for the auditory (non-rest) conditions of the experiment
+(Fig.~\ref{fig:decoding}: pink, green, and teal lines;
+Fig.~\ref{fig:ttests}: three leftmost columns).  The highest
+decoding accuracy for participants who listened to the intact
+(unscrambled) story was achieved using high-order dynamic correlations
+(PCA: second-order; eigenvector-centrality: fourth-order).  Scrambled
+versions of the story were best decoded by lower-order correlations
+(PCA/paragraph: first-order; PCA/word: order zero; eigenvector
+centrality/paragraph: order zero; eigenvector centrality/word: order
+zero).  The two sets of analyses yielded different decoding results on
+resting state data (Fig.~\ref{fig:decoding}: purple lines;
+Fig.~\ref{fig:ttests}: rightmost column).  We note
+that while the resting state times could be decoded reliably, the
+accuracies were only very slightly above chance.  We speculate that
+the decoders might have picked up on attentional drift, boredom, or
+tiredness; we hypothesize that these all increased throughout the resting
+state scan.  The decoders might be picking up on aspects of these
+loosely defined cognitive states that are common across individuals.
+The PCA-based approach achieved the highest resting state decoding
+accuracy using order zero features (non-correlational,
+activation-based), whereas the eigenvector centrality-based approach
+achieved the highest resting state decoding accuracy using
+second-order correlations.  Taken together, these analyses indicate
+that high-level cognitive processing (while listening to the intact
+story) is reflected in the dynamics of high-order correlations in
+brain activity, whereas lower-level cognitive processing (while
+listening to scrambled versions of the story that lack rich meaning)
+is reflected in the dynamics of lower-order correlations and
+non-correlational activity dynamics.  Further, these patterns are
+associated both with the underlying activity patterns (characterized
+using PCA) and also with the changing relative positions that
+different brain areas occupy in their associated networks
+(characterized using eigenvector centrality).
+
+\begin{figure}[tp]
+  \centering
+  \includegraphics[width=\textwidth]{figs/most_abs}
+  \caption{\textbf{Top terms associated with the endpoints of the
+      strongest correlations.}  Each color corresponds to one order of
+    inter-subject functional correlations.  To calculate the dynamic
+    correlations, eigenvector centrality has been used to project
+    the high-dimensional patterns of dynamic correlations onto a
+    lower-dimensional space at each previous order, which allows us
+    the map the brain regions at each order by retaining the
+    features of the original space. The inflated brain plots
+    display the locations of the endpoints of the 10 strongest
+    (absolute value) correlations at each order, thresholded at 0.999,
+    and projected onto the cortical surface~\citep{CombEtal19}.  The
+    lists of terms on the right display the top five Neurosynth
+    terms~\citep{RubiEtal17} decoded from the corresponding brain maps
+    for each order.  Each row displays data from a different
+    experimental condition.  Additional maps and their corresponding
+    Neurosynth terms may be found in the \textit{Supplementary
+      materials} (intact: Fig.~\intact; paragraph: Fig.~\para; word:
+    Fig.~\word; rest: Fig.~\rest).}
+  \label{fig:neurosynth}
+\end{figure}
+
+Having established that patterns of high-order correlations are
+informative to decoders, we next wondered which specific networks of
+brain regions contributed most to these patterns.  As a representative
+example, we selected the kernel parameters that yielded decoding
+accuracies that best matched the average accuracies across all of the
+kernel parameters we examined.  Using Figure~\ref{fig:decoding}c as a
+template, the best-matching kernel was a Laplace kernel with a width
+of 50 (Fig.~\ref{fig:kernels}d).  We used this kernel to compute a
+single $K$ by $K$ $n^\mathrm{th}$-order DISFC matrix for each
+experimental condition.  We then used Neurosynth~\citep{RubiEtal17} to
+compute the terms most highly associated with the most strongly
+correlated pairs of regions in each of these matrices
+(Fig.~\ref{fig:neurosynth}; see \textit{Reverse inference}).
+
+For all of the story listening conditions (intact, paragraph, and
+word), we found that first- and second-order correlations were most
+strongly associated with auditory and speech processing areas.  During
+intact story listening, third-order correlations reflected integration
+with visual areas, and fourth-order correlations reflected integration
+with areas associated with high-level cognition and cognitive control,
+such as the ventrolateral prefrontal cortex.  However, during
+listening to temporally scrambled stories, these higher-order
+correlations instead involved interactions with additional regions
+associated with speech and semantic processing.  By contrast, we found
+a much different set of patterns in the resting state data.
+First-order resting state correlations were most strongly associated
+with regions involved in counting and numerical understanding.
+Second-order resting state correlations were strongest in visual
+areas; third-order correlations were strongest in task-positive areas;
+and fourth-order correlations were strongest in regions associated
+with autobiographical and episodic memory.  We carried out analogous
+analyses to create maps (and decode the top associated Neurosynth
+terms) for up to fifteenth-order correlations (Figs.~\intact, \para, \word, and
+\rest).  Of note, examining fifteenth-order correlations between 700
+nodes using conventional methods would have required storing roughly
+$\frac{700^{2 \times 15}}{2} \approx 1.13 \times 10^{85}$ floating
+point numbers-- assuming single-precision (32 bits each), this would
+require roughly 32 times as many bits as there are molecules in the
+known universe!  Although these fifteenth-order correlations do appear
+(visually) to have some well-formed structure, we provide this latter
+example primarily as a demonstration of the efficiency and scalability
+of our approach.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section*{Discussion}
+We tested the hypothesis that high-level cognition is reflected in
+high-order brain network dynamics~\citep[e.g., see][]{SoloEtal19,
+  ReimEtal17}.  We examined high-order network dynamics in functional
+neuroimaging data collected during a story listening experiment.  When
+participants listened to an auditory recording of the story,
+participants exhibited similar high-order brain network dynamics.  By
+contrast, when participants instead listened to temporally scrambled
+recordings of the story, only lower-order brain network dynamics were
+similar across participants.  Our results indicate that higher orders
+of network interactions support higher-level aspects of cognitive
+processing (Fig.~\ref{fig:discussion}).
+
+\begin{figure}[tp]
+  \centering
+  \includegraphics[width=0.6\textwidth]{figs/discussion}
+  \caption{\textbf{Proposed high-order network dynamics underlying
+      high-level cognition during story listening.}  Schematic depicts
+    higher orders of
+    network interactions supporting higher-level aspects of cognitive
+    processing.  When tasks evoke richer, deeper, and/or higher-level
+    processing, this is reflected in higher-order network
+    interactions.}
+  \label{fig:discussion}
+\end{figure}
+
+The notion that cognition is reflected in (and possibly mediated by)
+patterns of first-order network dynamics has been suggested by or
+proposed in myriad empirical studies and
+reviews~\citep[e.g.,][]{DemeEtal19, Turk13, LuriEtal18, FongEtal19,
+  ParkEtal18b, PretEtal17, RoyEtal19, LiegEtal19, ZouEtal19,
+  ChanGlov10, GonzEtal19}.  Our study extends this line of work by
+finding cognitively relevant \textit{higher-order} network dynamics
+that reflect ongoing cognition.  Our findings complement other work
+that uses graph theory and topology to characterize how brain networks
+reconfigure during cognition~\citep[e.g.,][]{BassEtal06, ZhenEtal19,
+  McInJirs19, TokeSomm19, SizeEtal18, ReimEtal17, BetzEtal19}.
+
+An open question not addressed by our study pertains to how different
+structures integrate incoming information with different time
+constants.  For example, one line of work suggests that the cortical
+surface comprises a structured map such that nearby brain structures
+process incoming information at similar timescales.  Low-level sensory
+areas integrate information relatively quickly, whereas higher-level
+regions integrate information relatively slowly~\citep{BaldEtal17,
+  HassEtal08, HassEtal15, HoneEtal12a, LernEtal11, LernEtal14,
+  ChieHone19}.  A similar hierarchy appears to play a role in
+predicting future events~\citep{LeeEtal20}.  Other
+related work in human and mouse brains indicates that the temporal
+response profile of a given brain structure may relate to how strongly
+connected that structure is with other brain
+areas~\citep{FallEtal19}.  Further study is needed to understand the
+role of temporal integration at different scales of network
+interaction, and across different anatomical structures. Importantly,
+our analyses do not speak to the physiological basis of higher-order
+dynamics, and could reflect nonlinearities, chaotic patterns,
+non-stationarities, or multistability, etc. However, our decoding analyses do indicate
+that higher-order dynamics are
+consistent across individuals, and therefore unlikely to be driven by
+non-stimulus-driven dynamics which are unlikely to be similar across
+individuals.
+
+Another potential limitation of our approach relates to recent work
+suggesting that the brain undergoes rapid state changes, for example
+across event boundaries~\citep[e.g.,][]{BaldEtal17}.
+\cite{ShapEtal19} used hidden semi-Markov models to estimate
+state-specific network dynamics~\citep[also see][]{VidaEtal18}.  Our
+general approach might be extended by considering putative state
+transitions. For example, rather than weighting all timepoints using a
+similar kernel (Eqn.~\ref{eqn:timecorr}), the kernel function could
+adapt on a timepoint-by-timepoint basis such that only timepoints
+determined to be in the same ``state'' were given non-zero weight.
+
+Identifying high-order network dynamics associated with high-level
+cognition required several important methods advances.  First, we used
+kernel-based dynamic correlations to extended the notion of (static)
+inter-subject functional connectivity~\citep{SimoEtal16} to a dynamic
+measure of inter-subject functional connectivity (DISFC) that does not
+rely on sliding windows, and that may be computed at individual
+timepoints.  This allowed us to precisely characterize stimulus-evoked
+network dynamics that were similar across individuals.  Second, we
+developed a computational framework for efficiently and scalably estimating
+high-order dynamic correlations.  Our approach uses dimensionality
+reduction algorithms and graph measures to obtain low-dimensional
+embeddings of patterns of network dynamics.  Third, we developed an
+analysis framework for identifying robust decoding results by carrying
+out our analyses using a range of parameter values and then
+identifying which results were robust to specific parameter choices.
+
+\subsection*{Concluding remarks}
+The complex hierarchy of dynamic interactions that underlie our
+thoughts is perhaps the greatest mystery in modern science.  Methods
+for characterizing the dynamics of high-order correlations in neural
+data provide a window into the neural basis of cognition.  By showing
+that high-level cognition is reflected in high-order network dynamics,
+we have elucidated the next step on the path towards understanding the
+neural basis of cognition.
 
@@
 given cognitive states are reflected in patterns of
-$n^\mathrm{th}$-order correlations.  All of the code used to produce
+$n^\mathrm{th}$-order correlations.
+
+All of the code used to produce
 the figures and results in this manuscript, along with links to the
@@
 dynamic correlations, $\mathbf{Y}$.  For convenience, we then reshape
-the upper triangles and diagonals of each timepoint's correlation matrix into a row
+the upper triangles and diagonals of each timepoint's symmetric correlation matrix into a row
 vector to obtain an equivalent $T$ by $\left( \frac{K^2 - K}{2} + K \right)$ matrix.
@@
 \textit{inter-subject functional connectivity}~\citep[ISFC;
-][]{SimoEtal16} to compute the stimulus-driven correlations reflected
+][]{SimoEtal16, SimoChan20} to compute the stimulus-driven correlations reflected
 in the multi-participant dataset at a given timepoint $t$ using:
@@
 (with respect to what the ``true'' $\mathbf{Y}_n$ might have looked
-like without using dimensionality reduction to maintain scalability).
+like without using dimensionality reduction to maintain tractability).
 In other words, computing $\mathbf{X}_n$ is a lossy operation.
@@
 distinction between the two general approaches we explore, suppose a
-network comprises nodes $A$, $B$, and $C$.  If $A$ and $B$ exhibit
-uncorrelated activity patterns, the functional connection
-(correlation) between them will be (by definition) close to 0.
-However, if $A$ and $B$ each interact with $C$ in similar ways, we
-might attempt to capture those similarities using a measure that
-reflects how $A$ and $B$ interact with \textit{other} members of the
-network.
+network comprises nodes $A$ and $B$, along with several other nodes.  If $A$ and $B$ exhibit
+uncorrelated activity patterns, then by definition the functional connection
+(correlation) between them will be close to 0.
+However, if $A$ and $B$ each interact with \textit{other} nodes in similar ways, we
+might attempt to capture those similarities between $A$'s and $B$'s
+interactions with those other members of the network.
 
@@
 general the $n^\mathrm{th}$-order dynamic correlations of a $T$ by $K$
-timeseries occupies $\mathcal{O}(TK^{2n})$ space.  However, when we
+timeseries occupies $\mathcal{O}(TK^{2^n})$ space.  However, when we
 approximate or summarize the output of Equation~\ref{eqn:timecorr} with a $T$ by
@@
 neuroimaging data.  We constructed and leveraged the synthetic data to
-evaluate our general approach~\citep[for a related validation
-approach see][]{ThomEtal18}.  Specifically, we tested how well
+evaluate our general approach~\citep[for a related validation approach
+see][]{ThomEtal18}.  Specifically, we tested how well
 Equation~\ref{eqn:timecorr} could be used to recover known dynamic
@@
 Fig.~\ref{fig:kernels}), for each of several synthetic datasets that
-exhibited different temporal properties. We also used this synthetic
-data to simulate higher-order correlations and tested how well Equation~\ref{eqn:timecorr}
-could recover these correlations using the best kernel from the
-previous synthetic data analysis.  We applied our approach to a
-functional neuroimaging dataset to test the hypothesis that ongoing
-cognitive processing is reflected in high-order dynamic correlations.
-We used an across-participant classification test to estimate whether
-dynamic correlations of different orders contain information about
-which timepoint in a story participants were listening to.
-
-\subsubsection*{Synthetic data}
+exhibited different temporal properties. We also simulated
+higher-order correlations and tested how well
+Equation~\ref{eqn:timecorr} could recover these correlations using the
+best kernel from the previous synthetic data analyses.  We then applied our
+approach to a functional neuroimaging dataset to test the hypothesis
+that ongoing cognitive processing is reflected in high-order dynamic
+correlations.  We used an across-participant classification test to
+estimate whether dynamic correlations of different orders contain
+information about which timepoint in a story participants were
+listening to.
+
+\subsubsection*{Synthetic data: simulating dynamic first-order correlations}
 We constructed a total of 40 different multivariate timeseries,
 collectively reflecting a total of 4 qualitatively different patterns
-of dynamic correlations (i.e., 10 datasets reflecting each type of
+of dynamic first-order correlations (i.e., 10 datasets reflecting each type of
 dynamic pattern).  Each timeseries comprised 50 features (dimensions)
@@
 \begin{align}
-  \mathbf{C}(i, j) &\sim \mathcal{N}(0, 1)\\
    \mathbf{\Sigma}_m &= \mathbf{C}
-                                          \mathbf{C}^\top~\mathrm{, where}\label{eqn:randcorr}
+                                          \mathbf{C}^\top\mathrm{,~where}\label{eqn:randcorr}\\
+  \mathbf{C}(i, j) &\sim \mathcal{N}(0, 1)\mathrm{,~and~where}
   \end{align}
@@
 was drawn from a Gaussian with the same covariance matrix.  These
-datasets were intended to simulate a system that undergoes occasional
-abrupt state changes.
+datasets were intended to simulate a system that exhibits periods of
+stability punctuated by occasional abrupt state changes.
 
@@
 extent that the corresponding cognitive representations are reflected
-in similar spatial patterns across people.  Following this logic, we
+in similar spatial patterns across people~\citep[also see][]{SimoChan20}.  Following this logic, we
 used an across-participant temporal decoding test developed by
@@
 patterns reflected ongoing stimulus-driven cognitive processing across
-people.  The approach entails using a subset of the data to train a
+people (Fig.~\ref{fig:pipeline}).  The approach entails using a subset of the data to train a
 classifier to decode stimulus timepoints (i.e., moments in the story
@@
 We used an across-participant correlation-based classifier to decode
-which stimulus timepoint matched each timepoint's neural pattern.  We
+which stimulus timepoint matched each timepoint's neural pattern(Fig.~\ref{fig:pipeline}.  We
 first divided the participants into two groups: a template group,
-$\mathcal{G}_{\mathrm{template}}$, and a to-be-decoded group,
-$\mathcal{G}_{\mathrm{decode}}$.  We used Equation~\ref{eqn:disfc} to
+$\mathcal{G}_{\mathrm{template}}$ (i.e., training data), and a to-be-decoded group,
+$\mathcal{G}_{\mathrm{decode}}$ (i.e., test data).  We used Equation~\ref{eqn:disfc} to
 compute a DISFC matrix for each group
@@
   \centering
-  \includegraphics[width=0.7\textwidth]{figs/timecorr_pipeline}
-  \caption{\textbf{Across-participant timepoint decoding accuracy varies with
-      correlation order and cognitive engagement.}
-    \textbf{a.~Decoding accuracy as a function of order: PCA.}
-    \textit{Order} ($x$-axis) refers to the maximum order of dynamic
-    correlations that were available to the classifiers (see
-    \textit{Feature weighting and testing}).  The reported
-    across-participant decoding accuracies are averaged over all
-    kernel shapes and widths (see \textit{Identifying robust decoding
-      results}).  The $y$-values are displayed relative to chance
-    accuracy (intact: $\frac{1}{300}$; paragraph: $\frac{1}{272}$;
-    word: $\frac{1}{300}$; rest: $\frac{1}{400}$).  The error ribbons
-    denote 95\% confidence intervals across cross-validation folds
-    (i.e., random assignments of participants to the training and test
-    sets).  The colors denote the experimental condition.  Arrows
-    denote sets of features that yielded reliably higher (upwards
-    facing) or lower (downward facing) decoding accuracy than the mean
-    of all other features (via a two-tailed test, thresholded at
-    $p < 0.05$).  Figure~\ref{fig:ttests} displays additional
-    comparisons between the decoding accuracies achieved using
-    different sets of neural features.  The circled values represent
-    the maximum decoding accuracy within each experimental condition.
-    \textbf{b.~Normalized timepoint decoding accuracy as a function of order:
-      PCA.}  This panel displays the same results as Panel a, but here
-    each curve has been normalized to have a maximum value of 1 and a
-    minimum value of 0 (including the upper and lower bounds of the
-    respective 95\% confidence intervals).  Panels a and b used PCA to
-    project each high-dimensional pattern of dynamic correlations onto
-    a lower-dimensional space.  \textbf{c.~Timepoint decoding accuracy as a
-      function of order: eigenvector centrality.} This panel is in the
-    same format as Panel a, but here eigenvector centrality has been
-    used to project the high-dimensional patterns of dynamic
-    correlations onto a lower-dimensional space.
-    \textbf{d.~Normalized timepoint decoding accuracy as a function of order:
-      eigenvector centrality.} This panel is in the same format as
-    Panel b, but here eigenvector centrality has been used to project
-    the high-dimensional patterns of dynamic correlations onto a
-    lower-dimensional space.}
-  \label{fig:pipeline}
+  \includegraphics[width=0.85\textwidth]{figs/timecorr_pipeline}
+  \caption{\textbf{Decoding analysis pipeline.  a. Computing dynamic
+      correlations from timeseries data.}  Given a timeseries of
+    observations as a $T \times K$ matrix (or a set of $S$ such
+    matrics), we use Equation~\ref{eqn:timecorr} to compute each
+    participant's DISFC (relative to other participants in the
+    training or test sub-group, as appropriate). We repeat this
+    process twice-- once using the analysis kernel (shown here as a
+    Gaussian in the upper row of the panel), and once using a $\delta$
+    function kernel (lower row of the panel).    \textbf{b. Projecting
+      dynamic correlations into a lower-dimensional space.}  We
+    project the training and test data into $K$-dimensional spaces to
+    create compact representations of dynamic correlations at the
+    given order (estimated using the analysis kernel).
+    \textbf{c. Kernel trick.} We project the dynamic correlations
+    computed using a $\delta$ function kernel into a common
+    $K$-dimensional space.  These low-dimensional embeddings are fed
+    back through the analysis pipeline in order to compute features at
+    the next-highest order.  \textbf{d. Decoding analysis.} We split
+    the training data into two equal groups, and optimize the feature
+    weights (i.e., dynamic correlations at each order) to maximize
+    decoding accuracy.  We then apply the trained classifer to the
+    (held-out) test data.
+  \label{fig:pipeline}}
 \end{figure}
@@
 kernel (which places all of its mass over a single timepoint;
-Fig.~\ref{fig:kernels}b) to compute each lower-order correlation
+Fig.~\ref{fig:kernels}b, \ref{fig:pipeline}a) to compute each lower-order correlation
 ($\mathbf{X}_1, \mathbf{X}_2, ..., \mathbf{X}_{n-1}$).  We then used a
@@
 
-\section*{Results}
-We sought to understand whether high-level cognition is reflected in
-dynamic patterns of high-order correlations.  To that end, we
-developed a computational framework for estimating the dynamics of
-stimulus-driven high-order correlations in multivariate timeseries
-data (see \textit{Dynamic inter-subject functional connectivity
-  (DISFC)} and \textit{Dynamic higher-order correlations}).  We
-evaluated the efficacy of this framework at recovering known patterns
-in several synthetic datasets (see \textit{Synthetic data}).  We then
-applied the framework to a public fMRI dataset collected as
-participants listened to an auditorally presented story, listened to a
-temporally scrambled version of the story, or underwent a resting
-state scan (see \textit{Functional neuroimaging data collected during
-  story listening}).  We used the relative decoding accuracies of
-classifiers trained on different sets of neural features to estimate
-which types of features reflected ongoing cognitive processing.
-
-\subsection*{Recovering known dynamic correlations from synthetic data}
-We generated synthetic datasets that differed in how the underlying
-correlations changed over time.  For each dataset, we applied
-Equation~\ref{eqn:timecorr} with a variety of kernel shapes and
-widths.  We assessed how well the true underlying correlations at each
-timepoint matched the recovered correlations
-(Fig.~\ref{fig:synthetic}).  For every kernel and dataset we tested,
-our approach recovered the correlation dynamics we embedded into the
-data.  However, the quality of these recoveries varied across
-different synthetic datasets in a kernel-dependent way.
-
-\begin{figure}[tp]
-  \centering
-  \includegraphics[width=\textwidth]{figs/synthetic_data}
-  \caption{\textbf{Recovering known dynamic correlations from
-      synthetic data.}  Each panel displays the average correlations
-    between the vectorized upper triangles of the recovered
-    correlation matrix at each timepoint and either the true
-    underlying correlation at each timepoint or a reference
-    correlation matrix.  (The averages are taken across 10 different
-    randomly generated synthetic datasets of the given category.)
-    Error ribbons denote 95\% confidence intervals (taken across
-    datasets). Different colors denote different kernel shapes, and
-    the shading within each color family denotes the kernel width
-    parameter.  For a complete description of each synthetic dataset,
-    see \textit{Synthetic data}.  \textbf{a. Constant correlations.}
-    These datasets have a stable (unchanging) underlying correlation
-    matrix.  \textbf{b. Random correlations.}  These datasets are
-    generated using a new independently drawn correlation matrix at
-    each new timepoint.  \textbf{c. Ramping correlations.}  These
-    datasets are generated by smoothly varying the underlying
-    correlations between the randomly drawn correlation matrices at
-    the first and last timepoints.  The left panel displays the
-    correlations between the recovered dynamic correlations and the
-    underlying ground truth correlations.  The middle panel compares
-    the recovered correlations with the \textit{first} timepoint's
-    correlation matrix.  The right panel compares the recovered
-    correlations with the \textit{last} timepoint's correlation
-    matrix.  \textbf{d. Event-based correlations.}  These datasets are
-    each generated using five randomly drawn correlation matrices that
-    each remain stable for a fifth of the total timecourse.  The left
-    panel displays the correlations between the recovered dynamic
-    correlations and the underlying ground truth correlations.  The
-    right panels compare the recovered correlations with the
-    correlation matrices unique to each event.}
-  \label{fig:synthetic}
-\end{figure}
-
-In general, wide monotonic kernel shapes (Laplace, Gaussian), and
-wider kernels (within a shape), performed best when the correlations
-varied gradually from moment-to-moment (Figs.~\ref{fig:synthetic}a, c,
-and d).  In the extreme, as the rate of change in correlations
-approaches 0 (Fig.~\ref{fig:synthetic}a), an infinitely wide kernel
-would exactly recover the Pearson's correlation (e.g., compare
-Eqns.~\ref{eqn:corr} and \ref{eqn:timecorr}).
-
-When the correlation dynamics were unstructured in time
-(Fig.~\ref{fig:synthetic}b), a Dirac $\delta$ kernel (infinitely
-narrow) performed best.  This is because, when every timepoint's
-correlations are independent of the correlations at every other
-timepoint, averaging data over time dilutes the available signal.
-Following a similar pattern, holding kernel shape fixed, narrower
-kernel parameters better recovered randomly varying correlations.
-
-\subsection*{Recovering known higher-order dynamic correlations from synthetic data}
-We generated a synthetic timeseries from simulated first and second order dynamic correlation
-matrices that differed in how the underlying
-correlations changed over time.  For each dataset, we applied
-Equation~\ref{eqn:timecorr} with a Laplace kernel with a width of 20.
-We assessed how well the recovered correlations matched simulated
-first and second order correlations. 
-(Fig.~\ref{fig:higher_order_sims}).  For every dataset we tested,
-our approach recovered the correlation dynamics we embedded into the
-data.  However, the quality of these recoveries varied across
-different synthetic datasets.
-
-\begin{figure}[tp]
-  \centering
-  \includegraphics[width=\textwidth]{figs/higher_order_sims}
-  \caption{\textbf{Recovery of simulated first and second order dynamic correlations.}  Each panel displays the average correlations
-    between the vectorized upper triangles of the recovered
-    correlation matrix and the simulated correlation matrix at each
-    timepoint and for each synthetic dataset.  (The averages are taken across 10 different
-    randomly generated synthetic datasets of the given category.)
-    Error ribbons denote 95\% confidence intervals (taken across
-    datasets).  For a complete description of each synthetic dataset,
-    see \textit{Synthetic data}.  \textbf{a. Constant correlations.}
-    These first and second order dynamic correlation were
-    simulated from datasets have a stable (unchanging) underlying correlation
-    matrix.  \textbf{b. Random correlations.}  These first and second order dynamic correlation were
-    simulated from datasets are
-    generated using a new independently drawn correlation matrix at
-    each new timepoint.  \textbf{c. Ramping correlations.}  These first and second order dynamic correlation were
-    simulated from
-    datasets are generated by smoothly varying the underlying
-    correlations between the randomly drawn correlation matrices at
-    the first and last timepoints and displays the
-    correlations between the recovered dynamic correlations and the
-  simualted correlation first and second order correlation matrices.   \textbf{d. Event-based correlations.}  These first and second order dynamic correlation were
-    simulated from datasets are
-    each generated using five randomly drawn correlation matrices that
-    each remain stable for a fifth of the total timecourse.  }
-  \label{fig:higher_order_sims}
-\end{figure}
-
-\subsection*{Cognitively relevant dynamic high-order correlations in
-  fMRI data}
-We used across-participant temporal decoders to identify cognitively
-relevant neural patterns in fMRI data (see \textit{Forward inference
-  and decoding accuracy}).  The dataset we examined~\citep[collected
-by][]{SimoEtal16} comprised four experimental conditions that exposed
-participants to stimuli that varied systematically in how cognitively
-engaging they were.  The \textit{intact} experimental condition had
-participants listen to an audio recording of a 10-minute story.  The
-\textit{paragraph}-scrambled experimental condition had participants
-listen to a temporally scrambled version of the story, where the
-paragraphs occurred out of order (but where the same total set of
-paragraphs were presented over the full listening interval).  All
-participants in this condition experienced the scrambled paragraphs in
-the same order.  The \textit{word}-scrambled experimental condition
-had participants listen to a temporally scrambled version of the story
-where the words in the story occurred in a random order.  All
-participants in the word condition experienced the scrambled words in
-the same order.  Finally, in a \textit{rest} experimental condition,
-participants lay in the scanner with no overt stimulus, with their
-eyes open (blinking as needed).  This dataset provided a convenient
-means of testing our hypothesis that different levels of cognitive
-processing and engagement are reflected in different orders of brain
-activity dynamics.
-
-\begin{figure}[tp]
-  \centering
-  \includegraphics[width=\textwidth]{figs/decode_level}
-  \caption{\textbf{Across-participant timepoint decoding accuracy varies with
-      correlation order and cognitive engagement.}
-    \textbf{a.~Decoding accuracy as a function of order: PCA.}
-    \textit{Order} ($x$-axis) refers to the maximum order of dynamic
-    correlations that were available to the classifiers (see
-    \textit{Feature weighting and testing}).  The reported
-    across-participant decoding accuracies are averaged over all
-    kernel shapes and widths (see \textit{Identifying robust decoding
-      results}).  The $y$-values are displayed relative to chance
-    accuracy (intact: $\frac{1}{300}$; paragraph: $\frac{1}{272}$;
-    word: $\frac{1}{300}$; rest: $\frac{1}{400}$).  The error ribbons
-    denote 95\% confidence intervals across cross-validation folds
-    (i.e., random assignments of participants to the training and test
-    sets).  The colors denote the experimental condition.  Arrows
-    denote sets of features that yielded reliably higher (upwards
-    facing) or lower (downward facing) decoding accuracy than the mean
-    of all other features (via a two-tailed test, thresholded at
-    $p < 0.05$).  Figure~\ref{fig:ttests} displays additional
-    comparisons between the decoding accuracies achieved using
-    different sets of neural features.  The circled values represent
-    the maximum decoding accuracy within each experimental condition.
-    \textbf{b.~Normalized timepoint decoding accuracy as a function of order:
-      PCA.}  This panel displays the same results as Panel a, but here
-    each curve has been normalized to have a maximum value of 1 and a
-    minimum value of 0 (including the upper and lower bounds of the
-    respective 95\% confidence intervals).  Panels a and b used PCA to
-    project each high-dimensional pattern of dynamic correlations onto
-    a lower-dimensional space.  \textbf{c.~Timepoint decoding accuracy as a
-      function of order: eigenvector centrality.} This panel is in the
-    same format as Panel a, but here eigenvector centrality has been
-    used to project the high-dimensional patterns of dynamic
-    correlations onto a lower-dimensional space.
-    \textbf{d.~Normalized timepoint decoding accuracy as a function of order:
-      eigenvector centrality.} This panel is in the same format as
-    Panel b, but here eigenvector centrality has been used to project
-    the high-dimensional patterns of dynamic correlations onto a
-    lower-dimensional space.}
-  \label{fig:decoding}
-\end{figure}
-
-In brief, we computed timeseries of dynamic high-order correlations
-that were similar across participants in each of two randomly assigned
-groups: a training group and a test group.  We then trained
-classifiers on the training group's data to match each sample from the
-test group with a stimulus timepoint.  Each classifier comprised a
-weighted blend of neural patterns that reflected up to
-$n^\mathrm{th}$-order dynamic correlations (see \textit{Feature
-  weighting and testing}).  We repeated this process for
-$n \in \left\{ 0, 1, 2, ..., 10 \right\}$.  Our examinations of
-synthetic data suggested that none of the kernels we examined were
-``universal'' in the sense of optimally recovering underlying
-correlations regardless of the temporal structure of those
-correlations.  We found a similar pattern in the (real) fMRI data,
-whereby different kernels yielded different decoding accuracies, but
-no single kernel emerged as the clear ``best.''  In our analyses of
-neural data, we therefore averaged our decoding results over a variety
-of kernel shapes and widths in order to identify results that were
-robust to specific kernel parameters (see \textit{Identifying robust
-  decoding results}).
-
-Our approach to estimating dynamic high-order correlations entails
-mapping the high-dimensional feature space of correlations (a $T$ by
-$\mathcal{O}(K^2)$ matrix) onto a lower-dimensional $T$ by $K$ matrix.
-We carried out two sets of analyses that differed in how this mapping
-was computed.  The first set of analyses used PCA to find a
-low-dimensional embedding of the original dynamic correlation matrices
-(Fig.~\ref{fig:decoding}a,b).  The second set of analyses
-characterized correlations in dynamics of each feature's eigenvector
-centrality, but did not preserve the underlying activity dynamics
-(Fig.~\ref{fig:decoding}c,d).
-
-\begin{figure}[tp]
-\centering
-\includegraphics[width=1\textwidth]{figs/stats_heatmaps}
-\caption{\textbf{Statistical summary of decoding accuracies for
-    different neural features.}  Each column displays decoding
-  results for one experimental condition (intact, paragraph, word, and
-  rest).  We considered dynamic activity patterns (order 0) and
-  dynamic correlations at different orders (order $> 0$).  We used
-  two-tailed $t$-tests to compare the
-  distributions of decoding accuracies obtained using each pair of
-  features.  The distributions for each feature reflect the set of
-  average decoding accuracies (across all kernel parameters), obtained
-  for each random assignment of training and test groups.
-  In the upper triangles of each map, warmer colors (positive $t$-values) indicate that the
-  neural feature indicated in the given row yielded higher accuracy than the
-  feature indicated in the given column.  Cooler colors (negative
-  $t$-values) indicate that
-  the feature in the given row yielded lower decoding accuracy than
-  the feature in the given column.  The lower triangles of each map
-  denote the corresponding $p$-values for the $t$-tests.  The diagonal
-  entries display the relative average optimized weight given to each type of feature, in
-  a decoder that included all feature types (see \textit{Feature
-    weighting and testing}).}
-\label{fig:ttests}
-\end{figure}
-
-Both sets of temporal decoding analyses yielded qualitatively similar
-results for the auditory (non-rest) conditions of the experiment
-(Fig.~\ref{fig:decoding}: pink, green, and teal lines;
-Fig.~\ref{fig:ttests}: three leftmost columns).  The highest
-decoding accuracy for participants who listened to the intact
-(unscrambled) story was achieved using high-order dynamic correlations
-(PCA: second-order; eigenvector-centrality: fourth-order).  Scrambled
-versions of the story were best decoded by lower-order correlations
-(PCA/paragraph: first-order; PCA/word: order zero; eigenvector
-centrality/paragraph: order zero; eigenvector centrality/word: order
-zero).  The two sets of analyses yielded different decoding results on
-resting state data (Fig.~\ref{fig:decoding}: purple lines;
-Fig.~\ref{fig:ttests}: rightmost column).  We note
-that while the resting state times could be decoded reliably, the
-accuracies were only very slightly above chance.  We speculate that
-the decoders might have picked up on attentional drift, boredom, or
-tiredness; we hypothesize that these all increased throughout the resting
-state scan.  The decoders might be picking up on aspects of these
-loosely defined cognitive states that are common across individuals.
-The PCA-based approach achieved the highest resting state decoding
-accuracy using order zero features (non-correlational,
-activation-based), whereas the eigenvector centrality-based approach
-achieved the highest resting state decoding accuracy using
-second-order correlations.  Taken together, these analyses indicate
-that high-level cognitive processing (while listening to the intact
-story) is reflected in the dynamics of high-order correlations in
-brain activity, whereas lower-level cognitive processing (while
-listening to scrambled versions of the story that lack rich meaning)
-is reflected in the dynamics of lower-order correlations and
-non-correlational activity dynamics.  Further, these patterns are
-associated both with the underlying activity patterns (characterized
-using PCA) and also with the changing relative positions that
-different brain areas occupy in their associated networks
-(characterized using eigenvector centrality).
-
-\begin{figure}[tp]
-  \centering
-  \includegraphics[width=\textwidth]{figs/most_abs}
-  \caption{\textbf{Top terms associated with the endpoints of the
-      strongest correlations.}  Each color corresponds to one order of
-    inter-subject functional correlations.  To calculate the dynamic
-    correlations, eigenvector centrality has been used to project
-    the high-dimensional patterns of dynamic correlations onto a
-    lower-dimensional space at each previous order, which allows us
-    the map the brain regions at each order by retaining the
-    features of the original space. The inflated brain plots
-    display the locations of the endpoints of the 10 strongest
-    (absolute value) correlations at each order, thresholded at 0.999,
-    and projected onto the cortical surface~\citep{CombEtal19}.  The
-    lists of terms on the right display the top five Neurosynth
-    terms~\citep{RubiEtal17} decoded from the corresponding brain maps
-    for each order.  Each row displays data from a different
-    experimental condition.  Additional maps and their corresponding
-    Neurosynth terms may be found in the \textit{Supplementary
-      materials} (intact: Fig.~\intact; paragraph: Fig.~\para; word:
-    Fig.~\word; rest: Fig.~\rest).}
-  \label{fig:neurosynth}
-\end{figure}
-
-Having established that patterns of high-order correlations are
-informative to decoders, we next wondered which specific networks of
-brain regions contributed most to these patterns.  As a representative
-example, we selected the kernel parameters that yielded decoding
-accuracies that best matched the average accuracies across all of the
-kernel parameters we examined.  Using Figure~\ref{fig:decoding}c as a
-template, the best-matching kernel was a Laplace kernel with a width
-of 50 (Fig.~\ref{fig:kernels}d).  We used this kernel to compute a
-single $K$ by $K$ $n^\mathrm{th}$-order DISFC matrix for each
-experimental condition.  We then used Neurosynth~\citep{RubiEtal17} to
-compute the terms most highly associated with the most strongly
-correlated pairs of regions in each of these matrices
-(Fig.~\ref{fig:neurosynth}; see \textit{Reverse inference}).
-
-For all of the story listening conditions (intact, paragraph, and
-word), we found that first- and second-order correlations were most
-strongly associated with auditory and speech processing areas.  During
-intact story listening, third-order correlations reflected integration
-with visual areas, and fourth-order correlations reflected integration
-with areas associated with high-level cognition and cognitive control,
-such as the ventrolateral prefrontal cortex.  However, during
-listening to temporally scrambled stories, these higher-order
-correlations instead involved interactions with additional regions
-associated with speech and semantic processing.  By contrast, we found
-a much different set of patterns in the resting state data.
-First-order resting state correlations were most strongly associated
-with regions involved in counting and numerical understanding.
-Second-order resting state correlations were strongest in visual
-areas; third-order correlations were strongest in task-positive areas;
-and fourth-order correlations were strongest in regions associated
-with autobiographical and episodic memory.  We carried out analogous
-analyses to create maps (and decode the top associated Neurosynth
-terms) for up to fifteenth-order correlations (Figs.~\intact, \para, \word, and
-\rest).  Of note, examining fifteenth-order correlations between 700
-nodes using conventional methods would have required storing roughly
-$\frac{700^{2 \times 15}}{2} \approx 1.13 \times 10^{85}$ floating
-point numbers-- assuming single-precision (32 bits each), this would
-require roughly 32 times as many bits as there are molecules in the
-known universe!  Although these fifteenth-order correlations do appear
-(visually) to have some well-formed structure, we provide this latter
-example primarily as a demonstration of the efficiency and scalability
-of our approach.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section*{Discussion}
-We tested the hypothesis that high-level cognition is reflected in
-high-order brain network dynamics~\citep[e.g., see][]{SoloEtal19,
-  ReimEtal17}.  We examined high-order network dynamics in functional
-neuroimaging data collected during a story listening experiment.  When
-participants listened to an auditory recording of the story,
-participants exhibited similar high-order brain network dynamics.  By
-contrast, when participants instead listened to temporally scrambled
-recordings of the story, only lower-order brain network dynamics were
-similar across participants.  Our results indicate that higher orders
-of network interactions support higher-level aspects of cognitive
-processing (Fig.~\ref{fig:discussion}).
-
-\begin{figure}[tp]
-  \centering
-  \includegraphics[width=0.6\textwidth]{figs/discussion}
-  \caption{\textbf{Proposed high-order network dynamics underlying
-      high-level cognition during story listening.}  Schematic depicts
-    higher orders of
-    network interactions supporting higher-level aspects of cognitive
-    processing.  When tasks evoke richer, deeper, and/or higher-level
-    processing, this is reflected in higher-order network
-    interactions.}
-  \label{fig:discussion}
-\end{figure}
-
-The notion that cognition is reflected in (and possibly mediated by)
-patterns of first-order network dynamics has been suggested by or
-proposed in myriad empirical studies and
-reviews~\citep[e.g.,][]{DemeEtal19, Turk13, LuriEtal18, FongEtal19,
-  ParkEtal18b, PretEtal17, RoyEtal19, LiegEtal19, ZouEtal19,
-  ChanGlov10, GonzEtal19}.  Our study extends this line of work by
-finding cognitively relevant \textit{higher-order} network dynamics
-that reflect ongoing cognition.  Our findings complement other work
-that uses graph theory and topology to characterize how brain networks
-reconfigure during cognition~\citep[e.g.,][]{BassEtal06, ZhenEtal19,
-  McInJirs19, TokeSomm19, SizeEtal18, ReimEtal17, BetzEtal19}.
-
-An open question not addressed by our study pertains to how different
-structures integrate incoming information with different time
-constants.  For example, one line of work suggests that the cortical
-surface comprises a structured map such that nearby brain structures
-process incoming information at similar timescales.  Low-level sensory
-areas integrate information relatively quickly, whereas higher-level
-regions integrate information relatively slowly~\citep{BaldEtal17,
-  HassEtal08, HassEtal15, HoneEtal12a, LernEtal11, LernEtal14, ChieHone19}.  Other
-related work in human and mouse brains indicates that the temporal
-response profile of a given brain structure may relate to how strongly
-connected that structure is with other brain
-areas~\citep{FallEtal19}.  Further study is needed to understand the
-role of temporal integration at different scales of network
-interaction, and across different anatomical structures. Importantly,
-our analyses do no speak to the physiological basis of higher-order
-dynamics, and could reflect nonlinearities, chaotic patterns,
-non-stationarities, or multistability, etc. However, our decoding analyses do indicate
-that higher-order dynamics are
-consistent across individuals, and therefore unlikely to be driven by
-non-stimulus-driven dynamics which are unlikely to be similar across
-individuals.
-
-Another potential limitation of our approach relates to recent work
-suggesting that the brain undergoes rapid state changes, for example
-across event boundaries~\citep[e.g.,][]{BaldEtal17}.
-\cite{ShapEtal19} used hidden semi-Markov models to estimate
-state-specific network dynamics~\citep[also see][]{VidaEtal18}.  Our
-general approach might be extended by considering putative state
-transitions. For example, rather than weighting all timepoints using a
-similar kernel (Eqn.~\ref{eqn:timecorr}), the kernel function could
-adapt on a timepoint-by-timepoint basis such that only timepoints
-determined to be in the same ``state'' were given non-zero weight.
-
-Identifying high-order network dynamics associated with high-level
-cognition required several important methods advances.  First, we used
-kernel-based dynamic correlations to extended the notion of (static)
-inter-subject functional connectivity~\citep{SimoEtal16} to a dynamic
-measure of inter-subject functional connectivity (DISFC) that does not
-rely on sliding windows, and that may be computed at individual
-timepoints.  This allowed us to precisely characterize stimulus-evoked
-network dynamics that were similar across individuals.  Second, we
-developed a computational framework for efficiently and scalably estimating
-high-order dynamic correlations.  Our approach uses dimensionality
-reduction algorithms and graph measures to obtain low-dimensional
-embeddings of patterns of network dynamics.  Third, we developed an
-analysis framework for identifying robust decoding results by carrying
-out our analyses using a range of parameter values and then
-identifying which results were robust to specific parameter choices.
-
-\subsection*{Concluding remarks}
-The complex hierarchy of dynamic interactions that underlie our
-thoughts is perhaps the greatest mystery in modern science.  Methods
-for characterizing the dynamics of high-order correlations in neural
-data provide a window into the neural basis of cognition.  By showing
-that high-level cognition is reflected in high-order network dynamics,
-we have elucidated the next step on the path towards understanding the
-neural basis of cognition.
-
 \section*{Acknowledgements}

### 2020-10-30 paper/main.tex
working through reviewer 3 concerns [WIP]

@@
 
+One reason one might expect to see homologous networks in a dataset is
+related to the notion that network dynamics reflect ongoing neural
+computations or cognitive processing~\citep[e.g.,][]{BeatEtal16}.  If
+the nodes in two brain networks are interacting (within each network)
+in similar ways then, according to our characterization of network
+dynamics, we refer to the similarities between those patterns of
+interaction as higher-order correlations.  When higher-order
+correlations are themselves changing over time, we can also attempt to
+capture and characterize those high-order dynamics.
+
 Another central question pertains to the extent to which the neural
@@
 neuroimaging dataset collected as participants listened to either an
-audio recording of a ten-minute story, listened to a temporally scrambled
-version of the story, or underwent a resting state
-scan~\citep{SimoEtal16}.  We used a subset of the data to train
+audio recording of a ten-minute story, listened to a temporally
+scrambled version of the story, or underwent a resting state
+scan~\citep{SimoEtal16}.  Temporal scrambling has been used in a
+growing number of studies, largely by Uri Hasson's group, to identify
+brain regions that are sensitive to higher-order and longer-timescale
+information (e.g., cross-sensory integration, rich narrative meaning,
+complex situations, etc.) versus regions that are primarily sensitive
+to low-order (e.g., sensory) information.  For example,
+\cite{HassEtal08} argues that when brain areas are sensitive to fine
+versus coarse temporal scrambling, this indicates that they are
+``higher order'' in the sense that they process contextual information
+pertaining to further-away timescales.  By contrast, low-level
+regions, such as primary sensory cortices, do not meaningfully change
+their responses (after correcting for presentation order) even when
+the stimulus is scrambled at fine timescales.
+
+We used a subset of the story listening and rest data to train
 across-participant classifiers to decode listening times using a blend
@@
 the PCA-based and eigenvector centrality-based approaches yielded
-neural patterns that could be used to decode accurately (i.e., well above
-chance).  Both approaches also yielded the best decoding accuracy for
-data collected during (intact) story listening when high-order (PCA:
-second-order; eigenvector centrality: fourth-order) dynamic
-correlation patterns were included as features.  When we trained
-classifiers on the scrambled stories or resting state data, only
-lower-order dynamic patterns were informative to the decoders.  Taken
-together, our results indicate that high-level cognition is supported
-by high-order dynamic patterns of communication between brain
-structures.
+neural patterns that could be used to decode accurately (i.e., well
+above chance).  Both approaches also yielded the best decoding
+accuracy for data collected during (intact) story listening when
+high-order (PCA: second-order; eigenvector centrality: fourth-order)
+dynamic correlation patterns were included as features.  When we
+trained classifiers on the scrambled stories or resting state data,
+only lower-order dynamic patterns were informative to the decoders.
+Taken together, our results indicate that high-level cognition is
+supported by high-order dynamic patterns of communication between
+brain structures.
 

### 2020-11-03 paper/main.tex
edits made while text banking-- review carefully

@@
   data, and we applied the approach to neuroimaging data collected as
-  human participants either listened to a ten-minute story, listened
-  to a temporally scrambled version of the story, or underwent a
-  resting state scan.  We trained across-participant pattern
-  classifiers to decode (in held-out data) when in the session each
-  neural activity snapshot was collected.  We found that classifiers
-  trained to decode from high-order dynamic correlations yielded the
-  best performance on data collected as participants listened to the
-  (unscrambled) story.  By contrast, classifiers trained to decode
-  data from scrambled versions of the story or during the resting
-  state scan yielded the best performance when they were trained using
-  first-order dynamic correlations or non-correlational activity patterns.  We
-  suggest that as our thoughts become more complex, they are reflected
-  in higher-order patterns of dynamic network interactions throughout
-  the brain.
+  human participants either listened to a ten-minute story or listened
+  to a temporally scrambled version of the story.  We trained
+  across-participant pattern classifiers to decode (in held-out data)
+  when in the session each neural activity snapshot was collected.  We
+  found that classifiers trained to decode from high-order dynamic
+  correlations yielded the best performance on data collected as
+  participants listened to the (unscrambled) story.  By contrast,
+  classifiers trained to decode data from scrambled versions of the
+  story yielded the best performance when they were trained using
+  first-order dynamic correlations or non-correlational activity
+  patterns.  We suggest that as our thoughts become more complex, they
+  are reflected in higher-order patterns of dynamic network
+  interactions throughout the brain.
 \end{abstract}
@@
 trained classifiers on the scrambled stories or resting state data,
-only lower-order dynamic patterns were informative to the decoders.
+only (relatively) lower-order dynamic patterns were informative to the decoders.
 Taken together, our results indicate that high-level cognition is

### 2020-11-04 paper/main.tex
working on addressing R3 comments

@@
 \caption{\textbf{Statistical summary of decoding accuracies for
-    different neural features.}  Each column displays decoding
+    different neural features.}  Each column of matrices displays decoding
   results for one experimental condition (intact, paragraph, word, and
@@
   for each random assignment of training and test groups.
-  In the upper triangles of each map, warmer colors (positive $t$-values) indicate that the
+  In the upper triangles of each matrix, warmer colors (positive $t$-values) indicate that the
   neural feature indicated in the given row yielded higher accuracy than the

### 2020-11-11 paper/main.tex
finished addressing reviewer comments

@@
 We used a subset of the story listening and rest data to train
-across-participant classifiers to decode listening times using a blend
-of neural features (comprising neural activity patterns, as well as
-different orders of dynamic correlations between those patterns that
-were inferred using our computational framework).  We found that both
-the PCA-based and eigenvector centrality-based approaches yielded
-neural patterns that could be used to decode accurately (i.e., well
-above chance).  Both approaches also yielded the best decoding
-accuracy for data collected during (intact) story listening when
-high-order (PCA: second-order; eigenvector centrality: fourth-order)
-dynamic correlation patterns were included as features.  When we
-trained classifiers on the scrambled stories or resting state data,
-only (relatively) lower-order dynamic patterns were informative to the decoders.
-Taken together, our results indicate that high-level cognition is
-supported by high-order dynamic patterns of communication between
-brain structures.
+across-participant classifiers to decode listening times (of groups of
+participants) using a blend of neural features (comprising neural
+activity patterns, as well as different orders of dynamic correlations
+between those patterns that were inferred using our computational
+framework).  We found that both the PCA-based and eigenvector
+centrality-based approaches yielded neural patterns that could be used
+to decode accurately (i.e., well above chance).  Both approaches also
+yielded the best decoding accuracy for data collected during (intact)
+story listening when high-order (PCA: second-order; eigenvector
+centrality: fourth-order) dynamic correlation patterns were included
+as features.  When we trained classifiers on the scrambled stories or
+resting state data, only (relatively) lower-order dynamic patterns
+were informative to the decoders.  Taken together, our results
+indicate that high-level cognition is supported by high-order dynamic
+patterns of communication between brain structures.
 
@@
 reviews~\citep[e.g.,][]{DemeEtal19, Turk13, LuriEtal18, FongEtal19,
-  ParkEtal18b, PretEtal17, RoyEtal19, LiegEtal19, ZouEtal19,
+  ParkEtal18b, PretEtal17, MannEtal18, RoyEtal19, LiegEtal19, ZouEtal19,
   ChanGlov10, GonzEtal19}.  Our study extends this line of work by
@@
 measure of inter-subject functional connectivity (DISFC) that does not
-rely on sliding windows, and that may be computed at individual
-timepoints.  This allowed us to precisely characterize stimulus-evoked
-network dynamics that were similar across individuals.  Second, we
-developed a computational framework for efficiently and scalably estimating
-high-order dynamic correlations.  Our approach uses dimensionality
-reduction algorithms and graph measures to obtain low-dimensional
-embeddings of patterns of network dynamics.  Third, we developed an
-analysis framework for identifying robust decoding results by carrying
-out our analyses using a range of parameter values and then
-identifying which results were robust to specific parameter choices.
+rely on sliding windows~\citep[e.g., as in][]{MannEtal18}, and that
+may be computed at individual timepoints.  This allowed us to
+precisely characterize stimulus-evoked network dynamics that were
+similar across individuals.  Second, we developed a computational
+framework for efficiently and scalably estimating high-order dynamic
+correlations.  Our approach uses dimensionality reduction algorithms
+and graph measures to obtain low-dimensional embeddings of patterns of
+network dynamics.  Third, we developed an analysis framework for
+identifying robust decoding results by carrying out our analyses using
+a range of parameter values and then identifying which results were
+robust to specific parameter choices.
 
 \subsection*{Concluding remarks}
-The complex hierarchy of dynamic interactions that underlie our
-thoughts is perhaps the greatest mystery in modern science.  Methods
-for characterizing the dynamics of high-order correlations in neural
-data provide a window into the neural basis of cognition.  By showing
-that high-level cognition is reflected in high-order network dynamics,
-we have elucidated the next step on the path towards understanding the
-neural basis of cognition.
+Methods for characterizing the dynamics of high-order correlations in
+neural data provide a window into the neural basis of cognition.  By
+showing that high-level cognition is reflected in high-order network
+dynamics, we have elucidated the next step on the path towards
+understanding the neural basis of cognition.
 

### 2020-11-13 paper/main.tex
minor tweaks made after going over response letter again, also added track changes doc

@@
   High-order dynamic correlations in neural activity patterns reflect
-  different subgraphs of the brain's connectome that display
+  different subgraphs of the brain's functional connectome that display
   homologous lower-level dynamic correlations.  We tested the
@@
 cognition-- and, by extension, which types of neural activity patterns
-might comprise the neural code.  For example, prior work has used
+might compose the neural code.  For example, prior work has used
 region of interest analyses to estimate the anatomical locations of
@@
 in this literature is that cognition is mediated by dynamic
-interactions between brain structures~\citep{SporHone06, BassEtal06,
+interactions between brain structures~\citep{Gros88, Fris00, SporHone06, BassEtal06,
   Turk13, DemeEtal19, SoloEtal19, LuriEtal18, PretEtal17, ZouEtal19,
@@
 applied the framework to a public fMRI dataset collected as
-participants listened to an auditorally presented story, listened to a
+participants listened to an auditorily presented story, listened to a
 temporally scrambled version of the story, or underwent a resting
@@
     right panels compare the recovered correlations with the
-    correlation matrices unique to each event.}
+    correlation matrices unique to each event.  The vertical lines
+    denote event boundaries.}
   \label{fig:synthetic}
@@
     correlations between the recovered dynamic correlations and the
-  simualted correlation first and second order correlation matrices.   \textbf{d. Event-based correlations.}  These first and second order dynamic correlation were
+  simulated correlation first and second order correlation matrices.   \textbf{d. Event-based correlations.}  These first and second order dynamic correlation were
     simulated from datasets are
     each generated using five randomly drawn correlation matrices that
-    each remain stable for a fifth of the total timecourse.  }
+    each remain stable for a fifth of the total timecourse.  The
+    vertical lines denote event boundaries.}
   \label{fig:higher_order_sims}
@@
 Given a timeseries of order $n$ correlation matrices, we can draw an
-order $n-1$ correlation matrix for each timpoint $t$ using
+order $n-1$ correlation matrix for each timepoint $t$ using
 \begin{align}
@@
     observations as a $T \times K$ matrix (or a set of $S$ such
-    matrics), we use Equation~\ref{eqn:timecorr} to compute each
+    matrices), we use Equation~\ref{eqn:timecorr} to compute each
     participant's DISFC (relative to other participants in the
@@
     weights (i.e., dynamic correlations at each order) to maximize
-    decoding accuracy.  We then apply the trained classifer to the
+    decoding accuracy.  We then apply the trained classifier to the
     (held-out) test data.

### 2020-11-13 paper/old.tex
minor tweaks made after going over response letter again, also added track changes doc

--- 2020-11-04 paper/main.tex
@@
   homologous lower-level dynamic correlations.  We tested the
-  hypothesis that high-level cognition is reflected in high-order
+  hypothesis that high-level cognition is supported by high-order
   dynamic correlations in brain activity patterns.  We developed an
@@
   data, and we applied the approach to neuroimaging data collected as
-  human participants either listened to a ten-minute story or listened
-  to a temporally scrambled version of the story.  We trained
-  across-participant pattern classifiers to decode (in held-out data)
-  when in the session each neural activity snapshot was collected.  We
-  found that classifiers trained to decode from high-order dynamic
-  correlations yielded the best performance on data collected as
-  participants listened to the (unscrambled) story.  By contrast,
-  classifiers trained to decode data from scrambled versions of the
-  story yielded the best performance when they were trained using
-  first-order dynamic correlations or non-correlational activity
-  patterns.  We suggest that as our thoughts become more complex, they
-  are reflected in higher-order patterns of dynamic network
-  interactions throughout the brain.
+  human participants either listened to a ten-minute story, listened
+  to a temporally scrambled version of the story, or underwent a
+  resting state scan.  We trained across-participant pattern
+  classifiers to decode (in held-out data) when in the session each
+  neural activity snapshot was collected.  We found that classifiers
+  trained to decode from high-order dynamic correlations yielded the
+  best performance on data collected as participants listened to the
+  (unscrambled) story.  By contrast, classifiers trained to decode
+  data from scrambled versions of the story or during the resting
+  state scan yielded the best performance when they were trained using
+  first-order dynamic correlations or non-correlational activity patterns.  We
+  suggest that as our thoughts become more complex, they are supported
+  by higher-order patterns of dynamic network interactions throughout
+  the brain.
 \end{abstract}
@@
 brain structures;][]{MannEtal18, FongEtal19, LuriEtal18, PretEtal17,
-  ZouEtal19, DemeEtal19}.  What might the future of this line of work
-hold?  For example, is the neural code implemented through
+  ZouEtal19, DemeEtal19}.  We wondered what the future of this line of
+work might hold.  For example, is the neural code mediated by
 higher-order interactions between brain structures~\citep[e.g.,
@@
 interaction are most reflective of high-level cognitive processes?
-
-One reason one might expect to see homologous networks in a dataset is
-related to the notion that network dynamics reflect ongoing neural
-computations or cognitive processing~\citep[e.g.,][]{BeatEtal16}.  If
-the nodes in two brain networks are interacting (within each network)
-in similar ways then, according to our characterization of network
-dynamics, we refer to the similarities between those patterns of
-interaction as higher-order correlations.  When higher-order
-correlations are themselves changing over time, we can also attempt to
-capture and characterize those high-order dynamics.
 
@@
 neuroimaging dataset collected as participants listened to either an
-audio recording of a ten-minute story, listened to a temporally
-scrambled version of the story, or underwent a resting state
-scan~\citep{SimoEtal16}.  Temporal scrambling has been used in a
-growing number of studies, largely by Uri Hasson's group, to identify
-brain regions that are sensitive to higher-order and longer-timescale
-information (e.g., cross-sensory integration, rich narrative meaning,
-complex situations, etc.) versus regions that are primarily sensitive
-to low-order (e.g., sensory) information.  For example,
-\cite{HassEtal08} argues that when brain areas are sensitive to fine
-versus coarse temporal scrambling, this indicates that they are
-``higher order'' in the sense that they process contextual information
-pertaining to further-away timescales.  By contrast, low-level
-regions, such as primary sensory cortices, do not meaningfully change
-their responses (after correcting for presentation order) even when
-the stimulus is scrambled at fine timescales.
-
-We used a subset of the story listening and rest data to train
+audio recording of a ten-minute story, listened to a temporally scrambled
+version of the story, or underwent a resting state
+scan~\citep{SimoEtal16}.  We used a subset of the data to train
 across-participant classifiers to decode listening times using a blend
@@
 the PCA-based and eigenvector centrality-based approaches yielded
-neural patterns that could be used to decode accurately (i.e., well
-above chance).  Both approaches also yielded the best decoding
-accuracy for data collected during (intact) story listening when
-high-order (PCA: second-order; eigenvector centrality: fourth-order)
-dynamic correlation patterns were included as features.  When we
-trained classifiers on the scrambled stories or resting state data,
-only (relatively) lower-order dynamic patterns were informative to the decoders.
-Taken together, our results indicate that high-level cognition is
-supported by high-order dynamic patterns of communication between
-brain structures.
-
-\section*{Results}
-We sought to understand whether high-level cognition is reflected in
-dynamic patterns of high-order correlations.  To that end, we
-developed a computational framework for estimating the dynamics of
-stimulus-driven high-order correlations in multivariate timeseries
-data (see \textit{Dynamic inter-subject functional connectivity
-  (DISFC)} and \textit{Dynamic higher-order correlations}).  We
-evaluated the efficacy of this framework at recovering known patterns
-in several synthetic datasets (see \textit{Synthetic data: simulating
-  dynamic first-order correlations} and \textit{Synthetic data:
-  simulating dynamic higher-order correlations}).  We then
-applied the framework to a public fMRI dataset collected as
-participants listened to an auditorally presented story, listened to a
-temporally scrambled version of the story, or underwent a resting
-state scan (see \textit{Functional neuroimaging data collected during
-  story listening}).  We used the relative decoding accuracies of
-classifiers trained on different sets of neural features to estimate
-which types of features reflected ongoing cognitive processing.
-
-\subsection*{Recovering known dynamic correlations from synthetic
-  data}
-\subsubsection*{Recovering dynamic first-order correlations}
-We generated synthetic datasets that differed in how the underlying first-order
-correlations changed over time.  For each dataset, we applied
-Equation~\ref{eqn:timecorr} with a variety of kernel shapes and
-widths.  We assessed how well the true underlying correlations at each
-timepoint matched the recovered correlations
-(Fig.~\ref{fig:synthetic}).  For every kernel and dataset we tested,
-our approach recovered the correlation dynamics we embedded into the
-data.  However, the quality of these recoveries varied across
-different synthetic datasets in a kernel-dependent way.
-
-\begin{figure}[tp]
-  \centering
-  \includegraphics[width=\textwidth]{figs/synthetic_data}
-  \caption{\textbf{Recovering known dynamic first-order correlations
-      from synthetic data.}  Each panel displays the average
-    correlations between the vectorized upper triangles of the
-    recovered correlation matrix at each timepoint and either the true
-    underlying correlation at each timepoint or a reference
-    correlation matrix.  (The averages are taken across 10 different
-    randomly generated synthetic datasets of the given category.)
-    Error ribbons denote 95\% confidence intervals (taken across
-    datasets). Different colors denote different kernel shapes, and
-    the shading within each color family denotes the kernel width
-    parameter.  For a complete description of each synthetic dataset,
-    see \textit{Synthetic data: simulating dynamic first-order
-      correlations}.  \textbf{a. Constant correlations.}  These
-    datasets have a stable (unchanging) underlying correlation matrix.
-    \textbf{b. Random correlations.}  These datasets are generated
-    using a new independently drawn correlation matrix at each new
-    timepoint.  \textbf{c. Ramping correlations.}  These datasets are
-    generated by smoothly varying the underlying correlations between
-    the randomly drawn correlation matrices at the first and last
-    timepoints.  The left panel displays the correlations between the
-    recovered dynamic correlations and the underlying ground truth
-    correlations.  The middle panel compares the recovered
-    correlations with the \textit{first} timepoint's correlation
-    matrix.  The right panel compares the recovered correlations with
-    the \textit{last} timepoint's correlation matrix.
-    \textbf{d. Event-based correlations.}  These datasets are each
-    generated using five randomly drawn correlation matrices that each
-    remain stable for a fifth of the total timecourse.  The left panel
-    displays the correlations between the recovered dynamic
-    correlations and the underlying ground truth correlations.  The
-    right panels compare the recovered correlations with the
-    correlation matrices unique to each event.}
-  \label{fig:synthetic}
-\end{figure}
-
-In general, wide monotonic kernel shapes (Laplace, Gaussian), and
-wider kernels (within a shape), performed best when the correlations
-varied gradually from moment-to-moment (Figs.~\ref{fig:synthetic}a, c,
-and d).  In the extreme, as the rate of change in correlations
-approaches 0 (Fig.~\ref{fig:synthetic}a), an infinitely wide kernel
-would exactly recover the Pearson's correlation (e.g., compare
-Eqns.~\ref{eqn:corr} and \ref{eqn:timecorr}).
-
-When the correlation dynamics were unstructured in time
-(Fig.~\ref{fig:synthetic}b), a Dirac $\delta$ kernel (infinitely
-narrow) performed best.  This is because, when every timepoint's
-correlations are independent of the correlations at every other
-timepoint, averaging data over time dilutes the available signal.
-Following a similar pattern, holding kernel shape fixed, narrower
-kernel parameters better recovered randomly varying correlations.
-
-\subsubsection*{Recovering dynamic higher-order correlations}
-Following our approach to evaluating our ability to recover known
-dynamic first-order correlations from synthetic data, we generated an
-analogous second set of synthetic datasets that we designed to exhibit
-known dynamic first-order \textit{and} second-order correlations (see
-\textit{Synthetic data: simulating dynamic higher-order
-  correlations}).  We generated a total of 40 datasets that varied in
-how the first-order and second-order correlations changed over time.
-We then repeatedly applied Equation~\ref{eqn:timecorr} using the
-overall best-performing kernel from our first-order tests (a Laplace
-kernel with a width of 20; Fig.~\ref{fig:synthetic}) to assess how
-closely the recovered dynamic correlations matched the dynamic
-correlations we had embedded into the datasets.
-
-Overall, we found that we could reliably recover both first-order and
-second-order correlations from the synthetic data
-(Fig.~\ref{fig:higher_order_sims}).  When the correlations were stable
-for longer intervals, or changed gradually (constant, ramping, and
-event datasets), recovery performance was relatively high, and we were
-better able to recover dynamic first-order correlations than
-second-order correlations.  We expected that this would happen, given
-that errors in our estimation procedure at lower orders necessarily
-propagate to higher orders (since lower-order correlations are used to
-estimate higher-order correlations).  Interestingly, we also found
-that when the correlations were particularly \textit{un}stable (random
-datasets), we better recovered second-order correlations.
-
-\begin{figure}[tp]
-  \centering
-  \includegraphics[width=\textwidth]{figs/higher_order_sims}
-  \caption{\textbf{Recovery of simulated first-order and second-order dynamic correlations.}  Each panel displays the average correlations
-    between the vectorized upper triangles of the recovered
-    correlation matrix and the simulated correlation matrix at each
-    timepoint and for each synthetic dataset.  (The averages are taken across 10 different
-    randomly generated synthetic datasets of the given category.)
-    Error ribbons denote 95\% confidence intervals (taken across
-    datasets).  For a complete description of each synthetic dataset,
-    see \textit{Synthetic data: simulating dynamic higher-order
-      correlations}.  All results in this figure used a Laplace kernel
-    (width~$=20$).  \textbf{a. Constant correlations.}
-    These first and second order dynamic correlation were
-    simulated from datasets have a stable (unchanging) underlying correlation
-    matrix.  \textbf{b. Random correlations.}  These first and second order dynamic correlation were
-    simulated from datasets are
-    generated using a new independently drawn correlation matrix at
-    each new timepoint.  \textbf{c. Ramping correlations.}  These first and second order dynamic correlation were
-    simulated from
-    datasets are generated by smoothly varying the underlying
-    correlations between the randomly drawn correlation matrices at
-    the first and last timepoints and displays the
-    correlations between the recovered dynamic correlations and the
-  simualted correlation first and second order correlation matrices.   \textbf{d. Event-based correlations.}  These first and second order dynamic correlation were
-    simulated from datasets are
-    each generated using five randomly drawn correlation matrices that
-    each remain stable for a fifth of the total timecourse.  }
-  \label{fig:higher_order_sims}
-\end{figure}
-
-Taken together, our explorations using synthetic data indicated that
-we are able to partially, but not perfectly, recover ground truth
-dynamic first-order and second-order correlations.  This suggests that
-our modeling approach provides a meaningful (if noisy) estimate of
-high-order correlations.  We next turned to analyses of human fMRI data
-to examine whether the recovered dynamics might reflect the dynamics
-of human cognition during a naturalistic story-listening task.
-
-\subsection*{Cognitively relevant dynamic high-order correlations in
-  fMRI data}
-We used across-participant temporal decoders to identify cognitively
-relevant neural patterns in fMRI data (see \textit{Forward inference
-  and decoding accuracy}).  The dataset we examined~\citep[collected
-by][]{SimoEtal16} comprised four experimental conditions that exposed
-participants to stimuli that varied systematically in how cognitively
-engaging they were.  The \textit{intact} experimental condition had
-participants listen to an audio recording of a 10-minute story.  The
-\textit{paragraph}-scrambled experimental condition had participants
-listen to a temporally scrambled version of the story, where the
-paragraphs occurred out of order (but where the same total set of
-paragraphs were presented over the full listening interval).  All
-participants in this condition experienced the scrambled paragraphs in
-the same order.  The \textit{word}-scrambled experimental condition
-had participants listen to a temporally scrambled version of the story
-where the words in the story occurred in a random order.  All
-participants in the word condition experienced the scrambled words in
-the same order.  Finally, in a \textit{rest} experimental condition,
-participants lay in the scanner with no overt stimulus, with their
-eyes open (blinking as needed).  This dataset provided a convenient
-means of testing our hypothesis that different levels of cognitive
-processing and engagement are reflected in different orders of brain
-activity dynamics.
-
-\begin{figure}[tp]
-  \centering
-  \includegraphics[width=\textwidth]{figs/decode_level}
-  \caption{\textbf{Across-participant timepoint decoding accuracy varies with
-      correlation order and cognitive engagement.}
-    \textbf{a.~Decoding accuracy as a function of order: PCA.}
-    \textit{Order} ($x$-axis) refers to the maximum order of dynamic
-    correlations that were available to the classifiers (see
-    \textit{Feature weighting and testing}).  The reported
-    across-participant decoding accuracies are averaged over all
-    kernel shapes and widths (see \textit{Identifying robust decoding
-      results}).  The $y$-values are displayed relative to chance
-    accuracy (intact: $\frac{1}{300}$; paragraph: $\frac{1}{272}$;
-    word: $\frac{1}{300}$; rest: $\frac{1}{400}$).  The error ribbons
-    denote 95\% confidence intervals across cross-validation folds
-    (i.e., random assignments of participants to the training and test
-    sets).  The colors denote the experimental condition.  Arrows
-    denote sets of features that yielded reliably higher (upwards
-    facing) or lower (downward facing) decoding accuracy than the mean
-    of all other features (via a two-tailed test, thresholded at
-    $p < 0.05$).  Figure~\ref{fig:ttests} displays additional
-    comparisons between the decoding accuracies achieved using
-    different sets of neural features.  The circled values represent
-    the maximum decoding accuracy within each experimental condition.
-    \textbf{b.~Normalized timepoint decoding accuracy as a function of order:
-      PCA.}  This panel displays the same results as Panel a, but here
-    each curve has been normalized to have a maximum value of 1 and a
-    minimum value of 0 (including the upper and lower bounds of the
-    respective 95\% confidence intervals).  Panels a and b used PCA to
-    project each high-dimensional pattern of dynamic correlations onto
-    a lower-dimensional space.  \textbf{c.~Timepoint decoding accuracy as a
-      function of order: eigenvector centrality.} This panel is in the
-    same format as Panel a, but here eigenvector centrality has been
-    used to project the high-dimensional patterns of dynamic
-    correlations onto a lower-dimensional space.
-    \textbf{d.~Normalized timepoint decoding accuracy as a function of order:
-      eigenvector centrality.} This panel is in the same format as
-    Panel b, but here eigenvector centrality has been used to project
-    the high-dimensional patterns of dynamic correlations onto a
-    lower-dimensional space.}
-  \label{fig:decoding}
-\end{figure}
-
-In brief, we computed timeseries of dynamic high-order correlations
-that were similar across participants in each of two randomly assigned
-groups: a training group and a test group.  We then trained
-classifiers on the training group's data to match each sample from the
-test group with a stimulus timepoint.  Each classifier comprised a
-weighted blend of neural patterns that reflected up to
-$n^\mathrm{th}$-order dynamic correlations (see \textit{Feature
-  weighting and testing}, Fig.~\ref{fig:pipeline}).  We repeated this process for
-$n \in \left\{ 0, 1, 2, ..., 10 \right\}$.  Our examinations of
-synthetic data suggested that none of the kernels we examined were
-``universal'' in the sense of optimally recovering underlying
-correlations regardless of the temporal structure of those
-correlations.  We found a similar pattern in the (real) fMRI data,
-whereby different kernels yielded different decoding accuracies, but
-no single kernel emerged as the clear ``best.''  In our analyses of
-neural data, we therefore averaged our decoding results over a variety
-of kernel shapes and widths in order to identify results that were
-robust to specific kernel parameters (see \textit{Identifying robust
-  decoding results}).
-
-Our approach to estimating dynamic high-order correlations entails
-mapping the high-dimensional feature space of correlations
-(represented by a $T$ by
-$\mathcal{O}(K^2)$ matrix) onto a lower-dimensional feature space
-(represented by a $T$ by $K$ matrix).
-We carried out two sets of analyses that differed in how this mapping
-was computed.  The first set of analyses used PCA to find a
-low-dimensional embedding of the original dynamic correlation matrices
-(Fig.~\ref{fig:decoding}a,b).  The second set of analyses
-characterized correlations in dynamics of each feature's eigenvector
-centrality, but did not preserve the underlying activity dynamics
-(Fig.~\ref{fig:decoding}c,d).
-
-\begin{figure}[tp]
-\centering
-\includegraphics[width=1\textwidth]{figs/stats_heatmaps}
-\caption{\textbf{Statistical summary of decoding accuracies for
-    different neural features.}  Each column of matrices displays decoding
-  results for one experimental condition (intact, paragraph, word, and
-  rest).  We considered dynamic activity patterns (order 0) and
-  dynamic correlations at different orders (order $> 0$).  We used
-  two-tailed $t$-tests to compare the
-  distributions of decoding accuracies obtained using each pair of
-  features.  The distributions for each feature reflect the set of
-  average decoding accuracies (across all kernel parameters), obtained
-  for each random assignment of training and test groups.
-  In the upper triangles of each matrix, warmer colors (positive $t$-values) indicate that the
-  neural feature indicated in the given row yielded higher accuracy than the
-  feature indicated in the given column.  Cooler colors (negative
-  $t$-values) indicate that
-  the feature in the given row yielded lower decoding accuracy than
-  the feature in the given column.  The lower triangles of each map
-  denote the corresponding $p$-values for the $t$-tests.  The diagonal
-  entries display the relative average optimized weight given to each type of feature, in
-  a decoder that included all feature types (see \textit{Feature
-    weighting and testing}).}
-\label{fig:ttests}
-\end{figure}
-
-Both sets of temporal decoding analyses yielded qualitatively similar
-results for the auditory (non-rest) conditions of the experiment
-(Fig.~\ref{fig:decoding}: pink, green, and teal lines;
-Fig.~\ref{fig:ttests}: three leftmost columns).  The highest
-decoding accuracy for participants who listened to the intact
-(unscrambled) story was achieved using high-order dynamic correlations
-(PCA: second-order; eigenvector-centrality: fourth-order).  Scrambled
-versions of the story were best decoded by lower-order correlations
-(PCA/paragraph: first-order; PCA/word: order zero; eigenvector
-centrality/paragraph: order zero; eigenvector centrality/word: order
-zero).  The two sets of analyses yielded different decoding results on
-resting state data (Fig.~\ref{fig:decoding}: purple lines;
-Fig.~\ref{fig:ttests}: rightmost column).  We note
-that while the resting state times could be decoded reliably, the
-accuracies were only very slightly above chance.  We speculate that
-the decoders might have picked up on attentional drift, boredom, or
-tiredness; we hypothesize that these all increased throughout the resting
-state scan.  The decoders might be picking up on aspects of these
-loosely defined cognitive states that are common across individuals.
-The PCA-based approach achieved the highest resting state decoding
-accuracy using order zero features (non-correlational,
-activation-based), whereas the eigenvector centrality-based approach
-achieved the highest resting state decoding accuracy using
-second-order correlations.  Taken together, these analyses indicate
-that high-level cognitive processing (while listening to the intact
-story) is reflected in the dynamics of high-order correlations in
-brain activity, whereas lower-level cognitive processing (while
-listening to scrambled versions of the story that lack rich meaning)
-is reflected in the dynamics of lower-order correlations and
-non-correlational activity dynamics.  Further, these patterns are
-associated both with the underlying activity patterns (characterized
-using PCA) and also with the changing relative positions that
-different brain areas occupy in their associated networks
-(characterized using eigenvector centrality).
-
-\begin{figure}[tp]
-  \centering
-  \includegraphics[width=\textwidth]{figs/most_abs}
-  \caption{\textbf{Top terms associated with the endpoints of the
-      strongest correlations.}  Each color corresponds to one order of
-    inter-subject functional correlations.  To calculate the dynamic
-    correlations, eigenvector centrality has been used to project
-    the high-dimensional patterns of dynamic correlations onto a
-    lower-dimensional space at each previous order, which allows us
-    the map the brain regions at each order by retaining the
-    features of the original space. The inflated brain plots
-    display the locations of the endpoints of the 10 strongest
-    (absolute value) correlations at each order, thresholded at 0.999,
-    and projected onto the cortical surface~\citep{CombEtal19}.  The
-    lists of terms on the right display the top five Neurosynth
-    terms~\citep{RubiEtal17} decoded from the corresponding brain maps
-    for each order.  Each row displays data from a different
-    experimental condition.  Additional maps and their corresponding
-    Neurosynth terms may be found in the \textit{Supplementary
-      materials} (intact: Fig.~\intact; paragraph: Fig.~\para; word:
-    Fig.~\word; rest: Fig.~\rest).}
-  \label{fig:neurosynth}
-\end{figure}
-
-Having established that patterns of high-order correlations are
-informative to decoders, we next wondered which specific networks of
-brain regions contributed most to these patterns.  As a representative
-example, we selected the kernel parameters that yielded decoding
-accuracies that best matched the average accuracies across all of the
-kernel parameters we examined.  Using Figure~\ref{fig:decoding}c as a
-template, the best-matching kernel was a Laplace kernel with a width
-of 50 (Fig.~\ref{fig:kernels}d).  We used this kernel to compute a
-single $K$ by $K$ $n^\mathrm{th}$-order DISFC matrix for each
-experimental condition.  We then used Neurosynth~\citep{RubiEtal17} to
-compute the terms most highly associated with the most strongly
-correlated pairs of regions in each of these matrices
-(Fig.~\ref{fig:neurosynth}; see \textit{Reverse inference}).
-
-For all of the story listening conditions (intact, paragraph, and
-word), we found that first- and second-order correlations were most
-strongly associated with auditory and speech processing areas.  During
-intact story listening, third-order correlations reflected integration
-with visual areas, and fourth-order correlations reflected integration
-with areas associated with high-level cognition and cognitive control,
-such as the ventrolateral prefrontal cortex.  However, during
-listening to temporally scrambled stories, these higher-order
-correlations instead involved interactions with additional regions
-associated with speech and semantic processing.  By contrast, we found
-a much different set of patterns in the resting state data.
-First-order resting state correlations were most strongly associated
-with regions involved in counting and numerical understanding.
-Second-order resting state correlations were strongest in visual
-areas; third-order correlations were strongest in task-positive areas;
-and fourth-order correlations were strongest in regions associated
-with autobiographical and episodic memory.  We carried out analogous
-analyses to create maps (and decode the top associated Neurosynth
-terms) for up to fifteenth-order correlations (Figs.~\intact, \para, \word, and
-\rest).  Of note, examining fifteenth-order correlations between 700
-nodes using conventional methods would have required storing roughly
-$\frac{700^{2 \times 15}}{2} \approx 1.13 \times 10^{85}$ floating
-point numbers-- assuming single-precision (32 bits each), this would
-require roughly 32 times as many bits as there are molecules in the
-known universe!  Although these fifteenth-order correlations do appear
-(visually) to have some well-formed structure, we provide this latter
-example primarily as a demonstration of the efficiency and scalability
-of our approach.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section*{Discussion}
-We tested the hypothesis that high-level cognition is reflected in
-high-order brain network dynamics~\citep[e.g., see][]{SoloEtal19,
-  ReimEtal17}.  We examined high-order network dynamics in functional
-neuroimaging data collected during a story listening experiment.  When
-participants listened to an auditory recording of the story,
-participants exhibited similar high-order brain network dynamics.  By
-contrast, when participants instead listened to temporally scrambled
-recordings of the story, only lower-order brain network dynamics were
-similar across participants.  Our results indicate that higher orders
-of network interactions support higher-level aspects of cognitive
-processing (Fig.~\ref{fig:discussion}).
-
-\begin{figure}[tp]
-  \centering
-  \includegraphics[width=0.6\textwidth]{figs/discussion}
-  \caption{\textbf{Proposed high-order network dynamics underlying
-      high-level cognition during story listening.}  Schematic depicts
-    higher orders of
-    network interactions supporting higher-level aspects of cognitive
-    processing.  When tasks evoke richer, deeper, and/or higher-level
-    processing, this is reflected in higher-order network
-    interactions.}
-  \label{fig:discussion}
-\end{figure}
-
-The notion that cognition is reflected in (and possibly mediated by)
-patterns of first-order network dynamics has been suggested by or
-proposed in myriad empirical studies and
-reviews~\citep[e.g.,][]{DemeEtal19, Turk13, LuriEtal18, FongEtal19,
-  ParkEtal18b, PretEtal17, RoyEtal19, LiegEtal19, ZouEtal19,
-  ChanGlov10, GonzEtal19}.  Our study extends this line of work by
-finding cognitively relevant \textit{higher-order} network dynamics
-that reflect ongoing cognition.  Our findings complement other work
-that uses graph theory and topology to characterize how brain networks
-reconfigure during cognition~\citep[e.g.,][]{BassEtal06, ZhenEtal19,
-  McInJirs19, TokeSomm19, SizeEtal18, ReimEtal17, BetzEtal19}.
-
-An open question not addressed by our study pertains to how different
-structures integrate incoming information with different time
-constants.  For example, one line of work suggests that the cortical
-surface comprises a structured map such that nearby brain structures
-process incoming information at similar timescales.  Low-level sensory
-areas integrate information relatively quickly, whereas higher-level
-regions integrate information relatively slowly~\citep{BaldEtal17,
-  HassEtal08, HassEtal15, HoneEtal12a, LernEtal11, LernEtal14,
-  ChieHone19}.  A similar hierarchy appears to play a role in
-predicting future events~\citep{LeeEtal20}.  Other
-related work in human and mouse brains indicates that the temporal
-response profile of a given brain structure may relate to how strongly
-connected that structure is with other brain
-areas~\citep{FallEtal19}.  Further study is needed to understand the
-role of temporal integration at different scales of network
-interaction, and across different anatomical structures. Importantly,
-our analyses do not speak to the physiological basis of higher-order
-dynamics, and could reflect nonlinearities, chaotic patterns,
-non-stationarities, or multistability, etc. However, our decoding analyses do indicate
-that higher-order dynamics are
-consistent across individuals, and therefore unlikely to be driven by
-non-stimulus-driven dynamics which are unlikely to be similar across
-individuals.
-
-Another potential limitation of our approach relates to recent work
-suggesting that the brain undergoes rapid state changes, for example
-across event boundaries~\citep[e.g.,][]{BaldEtal17}.
-\cite{ShapEtal19} used hidden semi-Markov models to estimate
-state-specific network dynamics~\citep[also see][]{VidaEtal18}.  Our
-general approach might be extended by considering putative state
-transitions. For example, rather than weighting all timepoints using a
-similar kernel (Eqn.~\ref{eqn:timecorr}), the kernel function could
-adapt on a timepoint-by-timepoint basis such that only timepoints
-determined to be in the same ``state'' were given non-zero weight.
-
-Identifying high-order network dynamics associated with high-level
-cognition required several important methods advances.  First, we used
-kernel-based dynamic correlations to extended the notion of (static)
-inter-subject functional connectivity~\citep{SimoEtal16} to a dynamic
-measure of inter-subject functional connectivity (DISFC) that does not
-rely on sliding windows, and that may be computed at individual
-timepoints.  This allowed us to precisely characterize stimulus-evoked
-network dynamics that were similar across individuals.  Second, we
-developed a computational framework for efficiently and scalably estimating
-high-order dynamic correlations.  Our approach uses dimensionality
-reduction algorithms and graph measures to obtain low-dimensional
-embeddings of patterns of network dynamics.  Third, we developed an
-analysis framework for identifying robust decoding results by carrying
-out our analyses using a range of parameter values and then
-identifying which results were robust to specific parameter choices.
-
-\subsection*{Concluding remarks}
-The complex hierarchy of dynamic interactions that underlie our
-thoughts is perhaps the greatest mystery in modern science.  Methods
-for characterizing the dynamics of high-order correlations in neural
-data provide a window into the neural basis of cognition.  By showing
-that high-level cognition is reflected in high-order network dynamics,
-we have elucidated the next step on the path towards understanding the
-neural basis of cognition.
+neural patterns that could be used to decode accurately (i.e., well above
+chance).  Both approaches also yielded the best decoding accuracy for
+data collected during (intact) story listening when high-order (PCA:
+second-order; eigenvector centrality: fourth-order) dynamic
+correlation patterns were included as features.  When we trained
+classifiers on the scrambled stories or resting state data, only
+lower-order dynamic patterns were informative to the decoders.  Taken
+together, our results indicate that high-level cognition is supported
+by high-order dynamic patterns of communication between brain
+structures.
 
@@
 given cognitive states are reflected in patterns of
-$n^\mathrm{th}$-order correlations.
-
-All of the code used to produce
+$n^\mathrm{th}$-order correlations.  All of the code used to produce
 the figures and results in this manuscript, along with links to the
@@
 dynamic correlations, $\mathbf{Y}$.  For convenience, we then reshape
-the upper triangles and diagonals of each timepoint's symmetric correlation matrix into a row
+the upper triangles and diagonals of each timepoint's correlation matrix into a row
 vector to obtain an equivalent $T$ by $\left( \frac{K^2 - K}{2} + K \right)$ matrix.
@@
 \textit{inter-subject functional connectivity}~\citep[ISFC;
-][]{SimoEtal16, SimoChan20} to compute the stimulus-driven correlations reflected
+][]{SimoEtal16} to compute the stimulus-driven correlations reflected
 in the multi-participant dataset at a given timepoint $t$ using:
@@
 Neighbor Embedding~\citep[$t$-SNE;][]{MaatHint08}, Uniform Manifold
-Approximation and Projection~\citep[UMAP;][]{McInEtal18}, non-negative
+Approximation and Projection~\citep[UMAP;][]{McInHeal18}, non-negative
 matrix factorization~\citep[NMF;][]{LeeSeun99}, Topographic Factor
@@
 (with respect to what the ``true'' $\mathbf{Y}_n$ might have looked
-like without using dimensionality reduction to maintain tractability).
+like without using dimensionality reduction to maintain scalability).
 In other words, computing $\mathbf{X}_n$ is a lossy operation.
@@
 distinction between the two general approaches we explore, suppose a
-network comprises nodes $A$ and $B$, along with several other nodes.  If $A$ and $B$ exhibit
-uncorrelated activity patterns, then by definition the functional connection
-(correlation) between them will be close to 0.
-However, if $A$ and $B$ each interact with \textit{other} nodes in similar ways, we
-might attempt to capture those similarities between $A$'s and $B$'s
-interactions with those other members of the network.
+network comprises nodes $A$, $B$, and $C$.  If $A$ and $B$ exhibit
+uncorrelated activity patterns, the functional connection
+(correlation) between them will be (by definition) close to 0.
+However, if $A$ and $B$ each interact with $C$ in similar ways, we
+might attempt to capture those similarities using a measure that
+reflects how $A$ and $B$ interact with \textit{other} members of the
+network.
 
@@
 general the $n^\mathrm{th}$-order dynamic correlations of a $T$ by $K$
-timeseries occupies $\mathcal{O}(TK^{2^n})$ space.  However, when we
+timeseries occupies $\mathcal{O}(TK^{2n})$ space.  However, when we
 approximate or summarize the output of Equation~\ref{eqn:timecorr} with a $T$ by
@@
 neuroimaging data.  We constructed and leveraged the synthetic data to
-evaluate our general approach~\citep[for a related validation approach
-see][]{ThomEtal18}.  Specifically, we tested how well
+evaluate our general approach~\citep[for a related validation
+approach see][]{ThomEtal18}.  Specifically, we tested how well
 Equation~\ref{eqn:timecorr} could be used to recover known dynamic
@@
 Fig.~\ref{fig:kernels}), for each of several synthetic datasets that
-exhibited different temporal properties. We also simulated
-higher-order correlations and tested how well
-Equation~\ref{eqn:timecorr} could recover these correlations using the
-best kernel from the previous synthetic data analyses.  We then applied our
-approach to a functional neuroimaging dataset to test the hypothesis
-that ongoing cognitive processing is reflected in high-order dynamic
-correlations.  We used an across-participant classification test to
-estimate whether dynamic correlations of different orders contain
-information about which timepoint in a story participants were
-listening to.
-
-\subsubsection*{Synthetic data: simulating dynamic first-order correlations}
+exhibited different temporal properties.  We applied our approach to a
+functional neuroimaging dataset to test the hypothesis that ongoing
+cognitive processing is reflected in high-order dynamic correlations.
+We used an across-participant classification test to estimate whether
+dynamic correlations of different orders contain information about
+which timepoint in a story participants were listening to.
+
+\subsubsection*{Synthetic data}
 We constructed a total of 40 different multivariate timeseries,
 collectively reflecting a total of 4 qualitatively different patterns
-of dynamic first-order correlations (i.e., 10 datasets reflecting each type of
+of dynamic correlations (i.e., 10 datasets reflecting each type of
 dynamic pattern).  Each timeseries comprised 50 features (dimensions)
@@
 \begin{align}
+  \mathbf{C}(i, j) &\sim \mathcal{N}(0, 1)\\
   \mathbf{\Sigma}_m &= \mathbf{C}
-                                          \mathbf{C}^\top\mathrm{,~where}\label{eqn:randcorr}\\
-  \mathbf{C}(i, j) &\sim \mathcal{N}(0, 1)\mathrm{,~and~where}
+                                          \mathbf{C}^\top~\mathrm{, where}\label{eqn:randcorr}
   \end{align}
@@
 correlation matrix is unique (as in the random datasets), but where
-the correlation dynamics are structured and exhibit first-order
-autocorrelations (as in the constant datasets).
+the correlation dynamics are structured.
 
@@
 was drawn from a Gaussian with the same covariance matrix.  These
-datasets were intended to simulate a system that exhibits periods of
-stability punctuated by occasional abrupt state changes.
-
-\subsubsection*{Synthetic data: simulating dynamic high-order
-  correlations}
-
-We developed an iterative procedure for constructing timeseries data
-that exhibits known dynamic high-order correlations.  The procedure
-builds on our approach to generating dynamic first-order correlations.
-Essentially, once we generate a timeseries with known first-order
-correlations, we can use the known first-order correlations as a
-template to generate a new timeseries of second-order correlations.
-In turn, we can generate a timeseries of third-order correlations from
-the second-order correlations, and so on.  In general, we can generate
-order $n$ correlations given a timeseries of order $n - 1$ correlations,
-for any $n > 1$.  Finally, given the order $n$ timeseries, we can
-reverse the preceding process to generate an order $n - 1$ timeseries, an
-order $n - 2$ order timeseries, and so on, until we obtain an order 0
-timeseries of simulated data that reflects the chosen high-order dynamics.
-
-The central mathematical operations in our procedure are two
-functions, $\mathrm{vec}(\cdot)$ and $\mathrm{mat}(\cdot)$.  The
-$\mathrm{vec}(\cdot)$ function takes as input a $K \times K$ symmetric
-matrix and returns as output a
-$\left(\frac{K^2 - K}{2} + K\right)$-dimensional column vector
-containing the entries in the upper triangle and diagonal.  The
-$\mathrm{mat}(\cdot)$ function inverts $\mathrm{vec}(\cdot)$ by taking
-as input a $\left(\frac{K^2 - K}{2} + K\right)$-dimensional column
-vector and returning a $K \times K$ symmetric matrix as output.  We
-can then generate an order $n$ correlation matrix (for one timepoint, $t$) from an order
-$n - 1$ template (from the same timepoint) as follows:
-\begin{align}
-  \mathbf{\Sigma_{n}}(t) &= \mathrm{mat}(\mathrm{vec}(\mathbf{\Sigma_{n-1}}(t)) \otimes \mathrm{vec}(\mathbf{\Sigma_{n-1}}(t))^\top).\label{eqn:veccorr}
-\end{align}
-
-Given a timeseries of order $n$ correlation matrices, we can draw an
-order $n-1$ correlation matrix for each timpoint $t$ using
-\begin{align}
- \mathbf{\sigma_{n-1}}(t) &\sim \mathcal{N}\left(\mathbf{0}, \mathbf{\Sigma_n}(t)
-                   \right)\label{eqn:highorder-gen1}\\
-  \mathbf{\Sigma_{n-1}}(t) &= \mathrm{mat}(\mathbf{\sigma_{n-1}}(t)).\label{eqn:highorder-gen2}
-  \end{align}
-  We can then use repeated applications of
-  Equations~\ref{eqn:highorder-gen1} and~\ref{eqn:highorder-gen2} in
-  order to obtain a synthetic dataset.
-
- When the template first-order correlations are constructed to exhibit different
- temporal profiles (e.g., using the constant, random, ramping, and
- event procedures described above), the resulting high-order
- correlations and synthetic data will exhibit the same category of
- temporal profile.
-
- Following our approach to generating synthetic data exhibiting known
- first-order correlations, we constructed a total of 40 additional multivariate timeseries,
-collectively reflecting a total of 4 qualitatively different patterns
-of dynamic correlations (i.e., 10 datasets reflecting each type of
-dynamic pattern: constant, random, ramping, and event).
+datasets were intended to simulate a system that undergoes occasional
+abrupt state changes.
 
@@
 extent that the corresponding cognitive representations are reflected
-in similar spatial patterns across people~\citep[also see][]{SimoChan20}.  Following this logic, we
+in similar spatial patterns across people.  Following this logic, we
 used an across-participant temporal decoding test developed by
@@
 patterns reflected ongoing stimulus-driven cognitive processing across
-people (Fig.~\ref{fig:pipeline}).  The approach entails using a subset of the data to train a
+people.  The approach entails using a subset of the data to train a
 classifier to decode stimulus timepoints (i.e., moments in the story
@@
 We used an across-participant correlation-based classifier to decode
-which stimulus timepoint matched each timepoint's neural pattern(Fig.~\ref{fig:pipeline}.  We
+which stimulus timepoint matched each timepoint's neural pattern.  We
 first divided the participants into two groups: a template group,
-$\mathcal{G}_{\mathrm{template}}$ (i.e., training data), and a to-be-decoded group,
-$\mathcal{G}_{\mathrm{decode}}$ (i.e., test data).  We used Equation~\ref{eqn:disfc} to
+$\mathcal{G}_{\mathrm{template}}$, and a to-be-decoded group,
+$\mathcal{G}_{\mathrm{decode}}$.  We used Equation~\ref{eqn:disfc} to
 compute a DISFC matrix for each group
@@
 
-\begin{figure}[tp]
-  \centering
-  \includegraphics[width=0.85\textwidth]{figs/timecorr_pipeline}
-  \caption{\textbf{Decoding analysis pipeline.  a. Computing dynamic
-      correlations from timeseries data.}  Given a timeseries of
-    observations as a $T \times K$ matrix (or a set of $S$ such
-    matrics), we use Equation~\ref{eqn:timecorr} to compute each
-    participant's DISFC (relative to other participants in the
-    training or test sub-group, as appropriate). We repeat this
-    process twice-- once using the analysis kernel (shown here as a
-    Gaussian in the upper row of the panel), and once using a $\delta$
-    function kernel (lower row of the panel).    \textbf{b. Projecting
-      dynamic correlations into a lower-dimensional space.}  We
-    project the training and test data into $K$-dimensional spaces to
-    create compact representations of dynamic correlations at the
-    given order (estimated using the analysis kernel).
-    \textbf{c. Kernel trick.} We project the dynamic correlations
-    computed using a $\delta$ function kernel into a common
-    $K$-dimensional space.  These low-dimensional embeddings are fed
-    back through the analysis pipeline in order to compute features at
-    the next-highest order.  \textbf{d. Decoding analysis.} We split
-    the training data into two equal groups, and optimize the feature
-    weights (i.e., dynamic correlations at each order) to maximize
-    decoding accuracy.  We then apply the trained classifer to the
-    (held-out) test data.
-  \label{fig:pipeline}}
-\end{figure}
-
 One challenge to fairly evaluating high-order correlations is that if
@@
 kernel (which places all of its mass over a single timepoint;
-Fig.~\ref{fig:kernels}b, \ref{fig:pipeline}a) to compute each lower-order correlation
+Fig.~\ref{fig:kernels}b) to compute each lower-order correlation
 ($\mathbf{X}_1, \mathbf{X}_2, ..., \mathbf{X}_{n-1}$).  We then used a
@@
 
+\section*{Results}
+We sought to understand whether high-level cognition is supported by
+dynamic patterns of high-order correlations.  To that end, we
+developed a computational framework for estimating the dynamics of
+stimulus-driven high-order correlations in multivariate timeseries
+data (see \textit{Dynamic inter-subject functional connectivity
+  (DISFC)} and \textit{Dynamic higher-order correlations}).  We
+evaluated the efficacy of this framework at recovering known patterns
+in several synthetic datasets (see \textit{Synthetic data}).  We then
+applied the framework to a public fMRI dataset collected as
+participants listened to an auditorally presented story, listened to a
+temporally scrambled version of the story, or underwent a resting
+state scan (see \textit{Functional neuroimaging data collected during
+  story listening}).  We used the relative decoding accuracies of
+classifiers trained on different sets of neural features to estimate
+which types of features reflected ongoing cognitive processing.
+
+\subsection*{Recovering known dynamic correlations from synthetic data}
+We generated synthetic datasets that differed in how the underlying
+correlations changed over time.  For each dataset, we applied
+Equation~\ref{eqn:timecorr} with a variety of kernel shapes and
+widths.  We assessed how well the true underlying correlations at each
+timepoint matched the recovered correlations
+(Fig.~\ref{fig:synthetic}).  For every kernel and dataset we tested,
+our approach recovered the correlation dynamics we embedded into the
+data.  However, the quality of these recoveries varied across
+different synthetic datasets in a kernel-dependent way.
+
+\begin{figure}[tp]
+  \centering
+  \includegraphics[width=\textwidth]{figs/synthetic_data}
+  \caption{\textbf{Recovering known dynamic correlations from
+      synthetic data.}  Each panel displays the average correlations
+    between the vectorized upper triangles of the recovered
+    correlation matrix at each timepoint and either the true
+    underlying correlation at each timepoint or a reference
+    correlation matrix.  (The averages are taken across 10 different
+    randomly generated synthetic datasets of the given category.)
+    Error ribbons denote 95\% confidence intervals (taken across
+    datasets). Different colors denote different kernel shapes, and
+    the shading within each color family denotes the kernel width
+    parameter.  For a complete description of each synthetic dataset,
+    see \textit{Synthetic data}.  \textbf{a. Constant correlations.}
+    These datasets have a stable (unchanging) underlying correlation
+    matrix.  \textbf{b. Random correlations.}  These datasets are
+    generated using a new independently drawn correlation matrix at
+    each new timepoint.  \textbf{c. Ramping correlations.}  These
+    datasets are generated by smoothly varying the underlying
+    correlations between the randomly drawn correlation matrices at
+    the first and last timepoints.  The left panel displays the
+    correlations between the recovered dynamic correlations and the
+    underlying ground truth correlations.  The middle panel compares
+    the recovered correlations with the \textit{first} timepoint's
+    correlation matrix.  The right panel compares the recovered
+    correlations with the \textit{last} timepoint's correlation
+    matrix.  \textbf{d. Event-based correlations.}  These datasets are
+    each generated using five randomly drawn correlation matrices that
+    each remain stable for a fifth of the total timecourse.  The left
+    panel displays the correlations between the recovered dynamic
+    correlations and the underlying ground truth correlations.  The
+    right panels compare the recovered correlations with the
+    correlation matrices unique to each event.}
+  \label{fig:synthetic}
+\end{figure}
+
+In general, wide monotonic kernel shapes (Laplace, Gaussian), and
+wider kernels (within a shape), performed best when the correlations
+varied gradually from moment-to-moment (Figs.~\ref{fig:synthetic}a, c,
+and d).  In the extreme, as the rate of change in correlations
+approaches 0 (Fig.~\ref{fig:synthetic}a), an infinitely wide kernel
+would exactly recover the Pearson's correlation (e.g., compare
+Eqns.~\ref{eqn:corr} and \ref{eqn:timecorr}).
+
+When the correlation dynamics were unstructured in time
+(Fig.~\ref{fig:synthetic}b), a Dirac $\delta$ kernel (infinitely
+narrow) performed best.  This is because, when every timepoint's
+correlations are independent of the correlations at every other
+timepoint, averaging data over time dilutes the available signal.
+Following a similar pattern, holding kernel shape fixed, narrower
+kernel parameters better recovered randomly varying correlations.
+
+\subsection*{Cognitively relevant dynamic high-order correlations in
+  fMRI data}
+We used across-participant temporal decoders to identify cognitively
+relevant neural patterns in fMRI data (see \textit{Forward inference
+  and decoding accuracy}).  The dataset we examined~\citep[collected
+by][]{SimoEtal16} comprised four experimental conditions that exposed
+participants to stimuli that varied systematically in how cognitively
+engaging they were.  The \textit{intact} experimental condition had
+participants listen to an audio recording of a 10-minute story.  The
+\textit{paragraph}-scrambled experimental condition had participants
+listen to a temporally scrambled version of the story, where the
+paragraphs occurred out of order (but where the same total set of
+paragraphs were presented over the full listening interval).  All
+participants in this condition experienced the scrambled paragraphs in
+the same order.  The \textit{word}-scrambled experimental condition
+had participants listen to a temporally scrambled version of the story
+where the words in the story occurred in a random order.  All
+participants in the word condition experienced the scrambled words in
+the same order.  Finally, in a \textit{rest} experimental condition,
+participants lay in the scanner with no overt stimulus, with their
+eyes open (blinking as needed).  This dataset provided a convenient
+means of testing our hypothesis that different levels of cognitive
+processing and engagement are supported by different orders of brain
+activity dynamics.
+
+\begin{figure}[tp]
+  \centering
+  \includegraphics[width=\textwidth]{figs/decode_level}
+  \caption{\textbf{Across-participant decoding accuracy varies with
+      correlation order and cognitive engagement.}
+    \textbf{a.~Decoding accuracy as a function of order: PCA.}
+    \textit{Order} ($x$-axis) refers to the maximum order of dynamic
+    correlations that were available to the classifiers (see
+    \textit{Feature weighting and testing}).  The reported
+    across-participant decoding accuracies are averaged over all
+    kernel shapes and widths (see \textit{Identifying robust decoding
+      results}).  The $y$-values are displayed relative to chance
+    accuracy (intact: $\frac{1}{300}$; paragraph: $\frac{1}{272}$;
+    word: $\frac{1}{300}$; rest: $\frac{1}{400}$).  The error ribbons
+    denote 95\% confidence intervals across cross-validation folds
+    (i.e., random assignments of participants to the training and test
+    sets).  The colors denote the experimental condition.  Arrows
+    denote sets of features that yielded reliably higher (upwards
+    facing) or lower (downward facing) decoding accuracy than the mean
+    of all other features (via a two-tailed test, thresholded at
+    $p < 0.05$).  Figure~\ref{fig:ttests} displays additional
+    comparisons between the decoding accuracies achieved using
+    different sets of neural features.  The circled values represent
+    the maximum decoding accuracy within each experimental condition.
+    \textbf{b.~Normalized decoding accuracy as a function of order:
+      PCA.}  This panel displays the same results as Panel a, but here
+    each curve has been normalized to have a maximum value of 1 and a
+    minimum value of 0 (including the upper and lower bounds of the
+    respective 95\% confidence intervals).  Panels a and b used PCA to
+    project each high-dimensional pattern of dynamic correlations onto
+    a lower-dimensional space.  \textbf{c.~Decoding accuracy as a
+      function of order: eigenvector centrality.} This panel is in the
+    same format as Panel a, but here eigenvector centrality has been
+    used to project the high-dimensional patterns of dynamic
+    correlations onto a lower-dimensional space.
+    \textbf{d.~Normalized decoding accuracy as a function of order:
+      eigenvector centrality.} This panel is in the same format as
+    Panel b, but here eigenvector centrality has been used to project
+    the high-dimensional patterns of dynamic correlations onto a
+    lower-dimensional space.}
+  \label{fig:decoding}
+\end{figure}
+
+In brief, we computed timeseries of dynamic high-order correlations
+that were similar across participants in each of two randomly assigned
+groups: a training group and a test group.  We then trained
+classifiers on the training group's data to match each sample from the
+test group with a stimulus timepoint.  Each classifier comprised a
+weighted blend of neural patterns that reflected up to
+$n^\mathrm{th}$-order dynamic correlations (see \textit{Feature
+  weighting and testing}).  We repeated this process for
+$n \in \left\{ 0, 1, 2, ..., 10 \right\}$.  Our examinations of
+synthetic data suggested that none of the kernels we examined were
+``universal'' in the sense of optimally recovering underlying
+correlations regardless of the temporal structure of those
+correlations.  We found a similar pattern in the (real) fMRI data,
+whereby different kernels yielded different decoding accuracies, but
+no single kernel emerged as the clear ``best.''  In our analyses of
+neural data, we therefore averaged our decoding results over a variety
+of kernel shapes and widths in order to identify results that were
+robust to specific kernel parameters (see \textit{Identifying robust
+  decoding results}).
+
+Our approach to estimating dynamic high-order correlations entails
+mapping the high-dimensional feature space of correlations (a $T$ by
+$\mathcal{O}(K^2)$ matrix) onto a lower-dimensional $T$ by $K$ matrix.
+We carried out two sets of analyses that differed in how this mapping
+was computed.  The first set of analyses used PCA to find a
+low-dimensional embedding of the original dynamic correlation matrices
+(Fig.~\ref{fig:decoding}a,b).  The second set of analyses
+characterized correlations in dynamics of each feature's eigenvector
+centrality, but did not preserve the underlying activity dynamics
+(Fig.~\ref{fig:decoding}c,d).
+
+\begin{figure}[tp]
+\centering
+\includegraphics[width=1\textwidth]{figs/stats_heatmaps}
+\caption{\textbf{Statistical summary of decoding accuracies for
+    different neural features.}  Each column displays decoding
+  results for one experimental condition (intact, paragraph, word, and
+  rest).  We considered dynamic activity patterns (order 0) and
+  dynamic correlations at different orders (order $> 0$).  We used
+  two-tailed $t$-tests to compare the
+  distributions of decoding accuracies obtained using each pair of
+  features.  The distributions for each feature reflect the set of
+  average decoding accuracies (across all kernel parameters), obtained
+  for each random assignment of training and test groups.
+  In the upper triangles of each map, warmer colors (positive $t$-values) indicate that the
+  neural feature indicated in the given row yielded higher accuracy than the
+  feature indicated in the given column.  Cooler colors (negative
+  $t$-values) indicate that
+  the feature in the given row yielded lower decoding accuracy than
+  the feature in the given column.  The lower triangles of each map
+  denote the corresponding $p$-values for the $t$-tests.  The diagonal
+  entries display the relative average optimized weight given to each type of feature, in
+  a decoder that included all feature types (see \textit{Feature
+    weighting and testing}).}
+\label{fig:ttests}
+\end{figure}
+
+Both sets of temporal decoding analyses yielded qualitatively similar
+results for the auditory (non-rest) conditions of the experiment
+(Fig.~\ref{fig:decoding}: pink, green, and teal lines;
+Fig.~\ref{fig:ttests}: three leftmost columns).  The highest
+decoding accuracy for participants who listened to the intact
+(unscrambled) story was achieved using high-order dynamic correlations
+(PCA: second-order; eigenvector-centrality: fourth-order).  Scrambled
+versions of the story were best decoded by lower-order correlations
+(PCA/paragraph: first-order; PCA/word: order zero; eigenvector
+centrality/paragraph: order zero; eigenvector centrality/word: order
+zero).  The two sets of analyses yielded different decoding results on
+resting state data (Fig.~\ref{fig:decoding}: purple lines;
+Fig.~\ref{fig:ttests}: rightmost column).  We note
+that while the resting state times could be decoded reliably, the
+accuracies were only very slightly above chance.  We speculate that
+the decoders might have picked up on attentional drift, boredom, or
+tiredness; we hypothesize that these all increased throughout the resting
+state scan.  The decoders might be picking up on aspects of these
+loosely defined cognitive states that are common across individuals.
+The PCA-based approach achieved the highest resting state decoding
+accuracy using order zero features (non-correlational,
+activation-based), whereas the eigenvector centrality-based approach
+achieved the highest resting state decoding accuracy using
+second-order correlations.  Taken together, these analyses indicate
+that high-level cognitive processing (while listening to the intact
+story) is reflected in the dynamics of high-order correlations in
+brain activity, whereas lower-level cognitive processing (while
+listening to scrambled versions of the story that lack rich meaning)
+is reflected in the dynamics of lower-order correlations and
+non-correlational activity dynamics.  Further, these patterns are
+associated both with the underlying activity patterns (characterized
+using PCA) and also with the changing relative positions that
+different brain areas occupy in their associated networks
+(characterized using eigenvector centrality).
+
+\begin{figure}[tp]
+  \centering
+  \includegraphics[width=\textwidth]{figs/most_abs}
+  \caption{\textbf{Top terms associated with the endpoints of the
+      strongest correlations.}  Each color corresponds to one order of
+    inter-subject functional correlations. The inflated brain plots
+    display the locations of the endpoints of the 10 strongest
+    (absolute value) correlations at each order, thresholded at 0.999,
+    and projected onto the cortical surface~\citep{CombEtal19}.  The
+    lists of terms on the right display the top five Neurosynth
+    terms~\citep{RubiEtal17} decoded from the corresponding brain maps
+    for each order.  Each row displays data from a different
+    experimental condition.  Additional maps and their corresponding
+    Neurosynth terms may be found in the \textit{Supplementary
+      materials} (intact: Fig.~\intact; paragraph: Fig.~\para; word:
+    Fig.~\word; rest: Fig.~\rest).}
+  \label{fig:neurosynth}
+\end{figure}
+
+Having established that patterns of high-order correlations are
+informative to decoders, we next wondered which specific networks of
+brain regions contributed most to these patterns.  As a representative
+example, we selected the kernel parameters that yielded decoding
+accuracies that best matched the average accuracies across all of the
+kernel parameters we examined.  Using Figure~\ref{fig:decoding}c as a
+template, the best-matching kernel was a Laplace kernel with a width
+of 50 (Fig.~\ref{fig:kernels}d).  We used this kernel to compute a
+single $K$ by $K$ $n^\mathrm{th}$-order DISFC matrix for each
+experimental condition.  We then used Neurosynth~\citep{RubiEtal17} to
+compute the terms most highly associated with the most strongly
+correlated pairs of regions in each of these matrices
+(Fig.~\ref{fig:neurosynth}; see \textit{Reverse inference}).
+
+For all of the story listening conditions (intact, paragraph, and
+word), we found that first- and second-order correlations were most
+strongly associated with auditory and speech processing areas.  During
+intact story listening, third-order correlations reflected integration
+with visual areas, and fourth-order correlations reflected integration
+with areas associated with high-level cognition and cognitive control,
+such as the ventrolateral prefrontal cortex.  However, during
+listening to temporally scrambled stories, these higher-order
+correlations instead involved interactions with additional regions
+associated with speech and semantic processing.  By contrast, we found
+a much different set of patterns in the resting state data.
+First-order resting state correlations were most strongly associated
+with regions involved in counting and numerical understanding.
+Second-order resting state correlations were strongest in visual
+areas; third-order correlations were strongest in task-positive areas;
+and fourth-order correlations were strongest in regions associated
+with autobiographical and episodic memory.  We carried out analogous
+analyses to create maps (and decode the top associated Neurosynth
+terms) for up to fifteenth-order correlations (Figs.~\intact, \para, \word, and
+\rest).  Of note, examining fifteenth-order correlations between 700
+nodes using conventional methods would have required storing roughly
+$\frac{700^{2 \times 15}}{2} \approx 1.13 \times 10^{85}$ floating
+point numbers-- assuming single-precision (32 bits each), this would
+require roughly 32 times as many bits as there are molecules in the
+known universe!  Although these fifteenth-order correlations do appear
+(visually) to have some well-formed structure, we provide this latter
+example primarily as a demonstration of the efficiency and scalability
+of our approach.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section*{Discussion}
+We tested the hypothesis that high-level cognition is supported by
+high-order brain network dynamics~\citep[e.g., see][]{SoloEtal19,
+  ReimEtal17}.  We examined high-order network dynamics in functional
+neuroimaging data collected during a story listening experiment.  When
+participants listened to an auditory recording of the story,
+participants exhibited similar high-order brain network dynamics.  By
+contrast, when participants instead listened to temporally scrambled
+recordings of the story, only lower-order brain network dynamics were
+similar across participants.  Our results indicate that higher orders
+of network interactions support higher-level aspects of cognitive
+processing (Fig.~\ref{fig:discussion}).
+
+\begin{figure}[tp]
+  \centering
+  \includegraphics[width=0.6\textwidth]{figs/discussion}
+  \caption{\textbf{Proposed high-order network dynamics underlying
+      high-level cognition during story listening.}  Higher orders of
+    network interactions support higher-level aspects of cognitive
+    processing.  When tasks evoke richer, deeper, and/or higher-level
+    processing, this is reflected in higher-order network
+    interactions.}
+  \label{fig:discussion}
+\end{figure}
+
+The notion that cognition is reflected in (and possibly mediated by)
+patterns of first-order network dynamics has been suggested by or
+proposed in myriad empirical studies and
+reviews~\citep[e.g.,][]{DemeEtal19, Turk13, LuriEtal18, FongEtal19,
+  ParkEtal18b, PretEtal17, RoyEtal19, LiegEtal19, ZouEtal19,
+  ChanGlov10, GonzEtal19}.  Our study extends this line of work by
+finding cognitively relevant \textit{higher-order} network dynamics
+that reflect ongoing cognition.  Our findings complement other work
+that uses graph theory and topology to characterize how brain networks
+reconfigure during cognition~\citep[e.g.,][]{BassEtal06, ZhenEtal19,
+  McInJirs19, TokeSomm19, SizeEtal18, ReimEtal17, BetzEtal19}.
+
+An open question not addressed by our study pertains to how different
+structures integrate incoming information with different time
+constants.  For example, one line of work suggests that the cortical
+surface comprises a structured map such that nearby brain structures
+process incoming information at similar timescales.  Low-level sensory
+areas integrate information relatively quickly, whereas higher-level
+regions integrate information relatively slowly~\citep{BaldEtal17,
+  HassEtal08, HassEtal15, HoneEtal12a, LernEtal11, LernEtal14, ChieHone19}.  Other
+related work in human and mouse brains indicates that the temporal
+response profile of a given brain structure may relate to how strongly
+connected that structure is with other brain
+areas~\citep{FallEtal19}.  Further study is needed to understand the
+role of temporal integration at different scales of network
+interaction, and across different anatomical structures.
+
+Another potential limitation of our approach relates to recent work
+suggesting that the brain undergoes rapid state changes, for example
+across event boundaries~\citep[e.g.,][]{BaldEtal17}.
+\cite{ShapEtal19} used hidden semi-Markov models to estimate
+state-specific network dynamics~\citep[also see][]{VidaEtal18}.  Our
+general approach might be extended by considering putative state
+transitions. For example, rather than weighting all timepoints using a
+similar kernel (Eqn.~\ref{eqn:timecorr}), the kernel function could
+adapt on a timepoint-by-timepoint basis such that only timepoints
+determined to be in the same ``state'' were given non-zero weight.
+
+Identifying high-order network dynamics associated with high-level
+cognition required several important methods advances.  First, we used
+kernel-based dynamic correlations to extended the notion of (static)
+inter-subject functional connectivity~\citep{SimoEtal16} to a dynamic
+measure of inter-subject functional connectivity (DISFC) that does not
+rely on sliding windows, and that may be computed at individual
+timepoints.  This allowed us to precisely characterize stimulus-evoked
+network dynamics that were similar across individuals.  Second, we
+developed a computational framework for efficiently and scalably estimating
+high-order dynamic correlations.  Our approach uses dimensionality
+reduction algorithms and graph measures to obtain low-dimensional
+embeddings of patterns of network dynamics.  Third, we developed an
+analysis framework for identifying robust decoding results by carrying
+out our analyses using a range of parameter values and then
+identifying which results were robust to specific parameter choices.
+
+\subsection*{Concluding remarks}
+The complex hierarchy of dynamic interactions that underlie our
+thoughts is perhaps the greatest mystery in modern science.  Methods
+for characterizing the dynamics of high-order correlations in neural
+data provide a window into the neural basis of cognition.  By showing
+that high-level cognition is reflected in high-order network dynamics,
+we have elucidated the next step on the path towards understanding the
+neural basis of cognition.
+
 \section*{Acknowledgements}

### 2020-11-16 paper/main.tex
working on final pass through main text [WIP]

@@
     between the vectorized upper triangles of the recovered
-    correlation matrix and the simulated correlation matrix at each
+    first-order and second-order correlation matrices and the true
+    (simulated) first-order and second order correlation matrices at each
     timepoint and for each synthetic dataset.  (The averages are taken across 10 different
@@
     see \textit{Synthetic data: simulating dynamic higher-order
-      correlations}.  All results in this figure used a Laplace kernel
-    (width~$=20$).  \textbf{a. Constant correlations.}
-    These first and second order dynamic correlation were
-    simulated from datasets have a stable (unchanging) underlying correlation
-    matrix.  \textbf{b. Random correlations.}  These first and second order dynamic correlation were
-    simulated from datasets are
-    generated using a new independently drawn correlation matrix at
-    each new timepoint.  \textbf{c. Ramping correlations.}  These first and second order dynamic correlation were
-    simulated from
-    datasets are generated by smoothly varying the underlying
-    correlations between the randomly drawn correlation matrices at
-    the first and last timepoints and displays the
-    correlations between the recovered dynamic correlations and the
-  simulated correlation first and second order correlation matrices.   \textbf{d. Event-based correlations.}  These first and second order dynamic correlation were
-    simulated from datasets are
-    each generated using five randomly drawn correlation matrices that
-    each remain stable for a fifth of the total timecourse.  The
+      correlations}.  All estimates represented in this figure were
+    computed using a Laplace kernel
+    (width~$=20$).  \textbf{a. Constant correlations.}  These datasets
+    have stable (unchanging) underlying second-order correlation
+    matrices.  \textbf{b. Random correlations.} These datasets are
+    generated using a new independently drawn second-order correlation
+    matrix at each timepoint.  \textbf{c. Ramping correlations.}
+    These datasets are generated by smoothly varying the underlying
+    second-order correlations between the randomly drawn correlation
+    matrices at the first and last timepoints.  \textbf{d. Event-based
+      correlations.}  These datasets are each generated using five
+    randomly drawn second-order correlation matrices that each remain
+    stable for a fifth of the total timecourse.  The
     vertical lines denote event boundaries.}
@@
 onto the original feature space of $\mathbf{X}_0$ will usually require
-$\mathcal{O}(TK^{2n})$ space and therefore becomes intractable
+$\mathcal{O}(TK^{2^n})$ space and therefore becomes intractable
 as $n$ or $K$ grow large.

### 2020-11-20 paper/main.tex
removed unused figure, corrected figure ordering in main text
edits and tweaks to main text, recompiled diff.tex

@@
 
-%\newcommand{\ttests}{S1}
-\newcommand{\intact}{S1}
-\newcommand{\para}{S2}
-\newcommand{\word}{S3}
-\newcommand{\rest}{S4}
+\newcommand{\kernelshape}{S1}
+\newcommand{\kernelwidth}{S2}
+\newcommand{\intact}{S3}
+\newcommand{\para}{S4}
+\newcommand{\word}{S5}
+\newcommand{\rest}{S6}
+\newcommand{\pca}{S7}
 
@@
 specific aspects of neural activity patterns are informative about
-cognition-- and, by extension, which types of neural activity patterns
+cognition and, by extension, which types of neural activity patterns
 might compose the neural code.  For example, prior work has used
@@
     hierarchies of networks, etc.), whereas multivariate analyses
-    characterize the patterns of activities across units.  Order 0
+    characterize the patterns of activity across units.  Order 0
     patterns involve individual nodes; order 1 patterns involve
@@
 follows related approaches taken by][]{McInJirs19, TokeSomm19,
-  GonzEtal19}; and a second non-invertible algorithm that explored
-patterns in eigenvector centrality~\citep{Land95}.  This latter
-approach characterizes correlations between each feature dimension's
-relative \textit{position} in the network in favor of the specific
-activity histories of different features~\citep[also
-see][]{BetzEtal19, SizeEtal18, ReimEtal17}.
+  GonzEtal19}; and a second non-invertible algorithm for computing
+dynamic patterns in eigenvector centrality~\citep{Land95}.  This
+latter approach characterizes correlations between each feature
+dimension's relative \textit{position} in the network (at each moment
+in time) in favor of the specific activity histories of different
+features~\citep[also see][]{BetzEtal19, SizeEtal18, ReimEtal17}.
 
@@
 ``higher order'' in the sense that they process contextual information
-pertaining to further-away timescales.  By contrast, low-level
+pertaining to further-away timepoints.  By contrast, low-level
 regions, such as primary sensory cortices, do not meaningfully change
@@
 participants lay in the scanner with no overt stimulus, with their
-eyes open (blinking as needed).  This dataset provided a convenient
+eyes open (blinking as needed).  This public dataset provided a convenient
 means of testing our hypothesis that different levels of cognitive
@@
     accuracy (intact: $\frac{1}{300}$; paragraph: $\frac{1}{272}$;
-    word: $\frac{1}{300}$; rest: $\frac{1}{400}$).  The error ribbons
+    word: $\frac{1}{300}$; rest: $\frac{1}{400}$; these chance accuracies
+    were subtracted from the observed accuracies to obtain the
+    relative accuracies reported on the $y$-axis).  The error ribbons
     denote 95\% confidence intervals across cross-validation folds
@@
     facing) or lower (downward facing) decoding accuracy than the mean
-    of all other features (via a two-tailed test, thresholded at
+    of all other features (via a two-tailed $t$-test, thresholded at
     $p < 0.05$).  Figure~\ref{fig:ttests} displays additional
@@
     the high-dimensional patterns of dynamic correlations onto a
-    lower-dimensional space.}
+    lower-dimensional space. See Figures~\kernelshape~and~\kernelwidth~for decoding results broken down by kernel shape and width, respectively.}
   \label{fig:decoding}
@@
   denote the corresponding $p$-values for the $t$-tests.  The diagonal
-  entries display the relative average optimized weight given to each type of feature, in
+  entries display the relative average optimized weight given to each type of feature in
   a decoder that included all feature types (see \textit{Feature
@@
 Fig.~\ref{fig:ttests}: rightmost column).  We note
-that while the resting state times could be decoded reliably, the
+that, while the resting state times could be decoded reliably, the
 accuracies were only very slightly above chance.  We speculate that
@@
   \includegraphics[width=\textwidth]{figs/most_abs}
-  \caption{\textbf{Top terms associated with the endpoints of the
-      strongest correlations.}  Each color corresponds to one order of
+  \caption{\textbf{Top terms associated with the most strongly
+      correlated nodes at each order.}  Each color corresponds to one order of
     inter-subject functional correlations.  To calculate the dynamic
@@
 example, we selected the kernel parameters that yielded decoding
-accuracies that best matched the average accuracies across all of the
+accuracies that were the most strongly correlated (across conditions
+and orders) with the average accuracies across all of the
 kernel parameters we examined.  Using Figure~\ref{fig:decoding}c as a
 template, the best-matching kernel was a Laplace kernel with a width
-of 50 (Fig.~\ref{fig:kernels}d).  We used this kernel to compute a
+of 50 (Fig.~\ref{fig:kernels}d; also see Fig.~\pca).  We used this kernel to compute a
 single $K$ by $K$ $n^\mathrm{th}$-order DISFC matrix for each
@@
 For all of the story listening conditions (intact, paragraph, and
-word), we found that first- and second-order correlations were most
-strongly associated with auditory and speech processing areas.  During
-intact story listening, third-order correlations reflected integration
-with visual areas, and fourth-order correlations reflected integration
-with areas associated with high-level cognition and cognitive control,
-such as the ventrolateral prefrontal cortex.  However, during
-listening to temporally scrambled stories, these higher-order
+word; top three rows of Fig.~\ref{fig:neurosynth}), we found that
+first- and second-order correlations were most strongly associated
+with auditory and speech processing areas.  During intact story
+listening, third-order correlations reflected integration with visual
+areas, and fourth-order correlations reflected integration with areas
+associated with high-level cognition and cognitive control, such as
+the ventrolateral prefrontal cortex.  However, when participants
+listened to temporally scrambled stories, these higher-order
 correlations instead involved interactions with additional regions
-associated with speech and semantic processing.  By contrast, we found
-a much different set of patterns in the resting state data.
+associated with speech and semantic processing (second and third rows
+of Fig.~\ref{fig:neurosynth}).  By contrast, we found
+a much different set of patterns in the resting state data
+(Fig.~\ref{fig:neurosynth}, bottom row).
 First-order resting state correlations were most strongly associated
@@
 analyses to create maps (and decode the top associated Neurosynth
-terms) for up to fifteenth-order correlations (Figs.~\intact, \para, \word, and
-\rest).  Of note, examining fifteenth-order correlations between 700
-nodes using conventional methods would have required storing roughly
+terms) for up to fifteenth-order correlations (Figs.~\intact, \para,
+\word, and \rest).  Of note, examining fifteenth-order correlations
+between 700 nodes using conventional methods would have required
+storing roughly
 $\frac{700^{2 \times 15}}{2} \approx 1.13 \times 10^{85}$ floating
@@
 finding cognitively relevant \textit{higher-order} network dynamics
-that reflect ongoing cognition.  Our findings complement other work
+that reflect ongoing cognition.  Our findings also complement other work
 that uses graph theory and topology to characterize how brain networks
@@
   ChieHone19}.  A similar hierarchy appears to play a role in
-predicting future events~\citep{LeeEtal20}.  Other
-related work in human and mouse brains indicates that the temporal
-response profile of a given brain structure may relate to how strongly
-connected that structure is with other brain
-areas~\citep{FallEtal19}.  Further study is needed to understand the
-role of temporal integration at different scales of network
-interaction, and across different anatomical structures. Importantly,
-our analyses do not speak to the physiological basis of higher-order
-dynamics, and could reflect nonlinearities, chaotic patterns,
-non-stationarities, or multistability, etc. However, our decoding analyses do indicate
-that higher-order dynamics are
-consistent across individuals, and therefore unlikely to be driven by
-non-stimulus-driven dynamics which are unlikely to be similar across
-individuals.
+predicting future events~\citep{LeeEtal20}.  Other related work in
+human and mouse brains indicates that the temporal response profile of
+a given brain structure may relate to how strongly connected that
+structure is with other brain areas~\citep{FallEtal19}.  Further study
+is needed to understand the role of temporal integration at different
+scales of network interaction, and across different anatomical
+structures. Importantly, our analyses do not speak to the
+physiological basis of higher-order dynamics, and could reflect
+nonlinearities, chaotic patterns, non-stationarities, and/or
+multistability, etc. However, our decoding analyses do indicate that
+higher-order dynamics are consistent across individuals, and therefore
+unlikely to reflect non-stimulus-driven dynamics that are unlikely to
+be similar across individuals.
 
@@
 identifying robust decoding results by carrying out our analyses using
-a range of parameter values and then identifying which results were
-robust to specific parameter choices.
-
-\subsection*{Concluding remarks}
-Methods for characterizing the dynamics of high-order correlations in
-neural data provide a window into the neural basis of cognition.  By
-showing that high-level cognition is reflected in high-order network
-dynamics, we have elucidated the next step on the path towards
-understanding the neural basis of cognition.
+a range of parameter values and identifying which results were robust
+to specific parameter choices. By showing that high-level cognition is
+reflected in high-order network dynamics, we have elucidated the next
+step on the path towards understanding the neural basis of cognition.
 
@@
 
-The central mathematical operations in our procedure are two
+The central mathematical operations in our procedure are two bookkeeping
 functions, $\mathrm{vec}(\cdot)$ and $\mathrm{mat}(\cdot)$.  The
@@
  correlations and synthetic data will exhibit the same category of
- temporal profile.
-
- Following our approach to generating synthetic data exhibiting known
+ temporal profile. Following our approach to generating synthetic data exhibiting known
  first-order correlations, we constructed a total of 40 additional multivariate timeseries,

### 2020-11-20 paper/main.tex
minor edits to main text and supplementary materials, recompiled diff.tex

@@
     sets).  The colors denote the experimental condition.  Arrows
-    denote sets of features that yielded reliably higher (upwards
+    denote sets of features that yielded reliably higher (upward
     facing) or lower (downward facing) decoding accuracy than the mean

### 2020-11-20 paper/supplementary_materials.tex
removed unused figure, corrected figure ordering in main text
minor edits to main text and supplementary materials, recompiled diff.tex

--- 2020-06-16 paper/supporting_information.tex
@@
 
-\newcommand{\neurosynth}{7}
+\newcommand{\neurosynth}{6}
 
@@
     across-participant decoding accuracies for \textbf{a. Gaussian},
-    \textbf{b. Laplace}, and \textbf{c. Mexican hat} kernels are averaged over all
+    \textbf{b. Laplace}, and \textbf{c. Mexican hat} kernel shapes are averaged over all
    widths (see \textit{Identifying robust decoding
@@
     sets).  The colors denote the experimental condition.  Arrows
-    denote sets of features that yielded reliably higher (upwards
+    denote sets of features that yielded reliably higher (upward
     facing) or lower (downward facing) decoding accuracy than the mean
-    of all other features (via a two-tailed test, thresholded at
+    of all other features (via a two-tailed $t$-test, thresholded at
     $p < 0.05$).  The circled values represent
@@
     a lower-dimensional space. \textbf{d.-f.~Timepoint decoding accuracy as a
-      function of order: eigenvector centrality.} This panel is in the
+      function of order: eigenvector centrality.} These panels are in the
     same format as Panel a.-c., but here eigenvector centrality has been
     used to project the high-dimensional patterns of dynamic
-    correlations onto a lower-dimensional space.}
+    correlations into lower-dimensional spaces.}
 \label{fig:supp_kernels}
@@
     \textit{Feature weighting and testing}).  The reported
-    across-participant decoding accuracies for \textbf{a. 5},
+    across-participant decoding accuracies for kernel widths of \textbf{a. 5},
     \textbf{b. 10}, \textbf{c. 20}, and \textbf{d. 50} are averaged over all
@@
     a lower-dimensional space.\textbf{e.-h.~Timepoint decoding accuracy as a
-      function of order: eigenvector centrality.} This panel is in the
+      function of order: eigenvector centrality.} These panels are in the
     same format as Panel a.-d., but here eigenvector centrality has been
     used to project the high-dimensional patterns of dynamic
-    correlations onto a lower-dimensional space.}
+    correlations into lower-dimensional spaces.}
 \label{fig:supp_widths}
@@
 \includegraphics[width=0.75\textwidth]{figs/supp_15_intact}
-\caption{\textbf{Top terms associated with the endpoints of the
-    strongest correlations for the \textit{intact} experimental
+\caption{\textbf{Top terms associated with the most strongly
+      correlated nodes at each order, for the \textit{intact} experimental
     condition.}  Each color corresponds to one order of inter-subject
@@
 \includegraphics[width=0.75\textwidth]{figs/supp_15_paragraph}
-\caption{\textbf{Top terms associated with the endpoints of the
-    strongest correlations for the \textit{paragraph} experimental
+\caption{\textbf{Top terms associated with the most strongly
+      correlated nodes at each order, for the \textit{paragraph} experimental
     condition.}  This figure is in the same format as
@@
 \includegraphics[width=0.75\textwidth]{figs/supp_15_word}
-\caption{\textbf{Top terms associated with the endpoints of the
-    strongest correlations for the \textit{word} experimental
+\caption{\textbf{Top terms associated with the most strongly
+      correlated nodes at each order, for the \textit{word} experimental
     condition.}  This figure is in the same format as
@@
 \includegraphics[width=0.75\textwidth]{figs/supp_15_rest}
-\caption{\textbf{Top terms associated with the endpoints of the
-    strongest correlations for the \textit{rest} experimental
+\caption{\textbf{Top terms associated with the most strongly
+      correlated nodes at each order, for the \textit{rest} experimental
     condition.}  This figure is in the same format as
@@
 \caption{\textbf{Cumulative percent variance explained as a function
-    of the number of principle components for correlation orders and reduction types.}  \textit{Order} refers to the order of the dynamic
+    of the number of principle components.}  \textit{Order} refers to the order of the dynamic
     correlations calculated. Principle components analysis was
     performed, and reduced independently for each subject.  Maximum number of components varies with
-    the total time for each condition (intact: 300; paragraph:272;
-    word: 300; rest: 400). \textbf{a.~Cumlative percent
+    the total time for each condition (intact: 300; paragraph: 272;
+    word: 300; rest: 400). \textbf{a.~Cumulative percent
     variance as a function of number of components for Order 0.} PCA
-  was performed on the raw acitivity patterns (Order 0). \textbf{b.-e.~Cumlative percent
+  was performed on the raw activity patterns (Order 0). \textbf{b.-e.~Cumlative percent
     variance as a function of number of components for Orders 1.-4.:
@@
     a lower-dimensional space.   \textbf{f.-i.~Cumlative percent
-    variance as a function of number of components for Orders 1.-4.: eigenvector centrality.} These panels arer in the
+    variance as a function of number of components for Orders 1.-4.: eigenvector centrality.} These panels are in the
     same format as Panel b.-e., but here eigenvector centrality has been
@@
 \newpage
-\renewcommand{\refname}{Supplemental references}
-\bibliography{memlab}
+\renewcommand{\refname}{Supplementary references}
+\bibliography{CDL-bibliography/memlab}
 

### 2021-01-13 code/scripts/higher_order_sims.py
WIP search over time and number of features for higher order sims

@@ -8,7 +8,7 @@ import timecorr as tc
 from matplotlib import pyplot as plt
 
 cond= sys.argv[1]
-r= sys.argv[2]
+r = sys.argv[2] #reps
 
 F = 4 #number of features
 T = 30 #number of timepoints
@@ -18,7 +18,7 @@ fname = cond + '_' + str(F) + '_' + str(T) + '_' + str(K)
 
 width = 20
 
-results_dir = os.path.join(config['resultsdir'], 'higher_order_sims', cond)
+results_dir = os.path.join(config['resultsdir'], 'higher_order_sims', cond + '_' + str(T))
 
 try:
     if not os.path.exists(results_dir):

### 2021-01-13 code/scripts/higher_order_sims_submit.py

@@ -24,26 +24,42 @@ job_script = os.path.join(os.path.dirname(os.path.realpath(__file__)), 'higher_o
 # options for reps: integer
 reps =  str('10')
 
+cond_type = ['ramping']
+#cond_type = ['paragraph']
+
+
+# options for widths: integer
+times = [str(10), str(50), str(100), str(500)]
+
+# options for widths: integer
+widths = [str(5), str(10), str(20), str(50)]
+
+
+param_grid = [(wi, ts, re) for wi in widths for ts in times for re in range(int(reps))]
+
+
+
+job_commands = list(np.array([list(map(lambda x: x[0]+" "+str(x[1]) +" "+str(e[2]) +" "+e[0]+" "+e[1],
+                                       zip([job_script]*len(cond_type), cond_type)))
+                              for i, e in enumerate(param_grid)]).flat)
+
+# job_names should specify the file name of each script (as a list, of the same length as job_commands)
+job_names = list(np.array([list(map(lambda x: os.path.basename(os.path.splitext(x)[0])+'_'+str(e[2])+'_'
+                                              +e[0]+'_'+e[1]+'_higher_order_sim.sh', cond_type))
+                           for i, e in enumerate(param_grid)]).flat)
+
+
+
+# cond_type = ['random']
 #
-# job_commands = list(np.array([list(map(lambda x: x[0]+" "+str(x[1]),
-#                                        zip([job_script]*1, [r])))
+# job_commands = list(np.array([list(map(lambda x: x[0]+" "+str(x[1])+" "+str(r),
+#                                        zip([job_script]*len(cond_type), cond_type)))
 #                               for r in range(int(reps))]).flat)
 #
 # # job_names should specify the file name of each script (as a list, of the same length as job_commands)
-# job_names = list(np.array([list(map(lambda x: os.path.basename(os.path.splitext(x)[0])+'_higher_order_sim.sh', [str(r)]))
+# job_names = list(np.array([list(map(lambda x: os.path.basename(os.path.splitext(x)[0])+'_'+str(r)+
+#                                               '_higher_order_sim.sh', cond_type))
 #                            for r in range(int(reps))]).flat)
-#
-
-cond_type = ['random']
-
-job_commands = list(np.array([list(map(lambda x: x[0]+" "+str(x[1])+" "+str(r),
-                                       zip([job_script]*len(cond_type), cond_type)))
-                              for r in range(int(reps))]).flat)
-
[…]

### 2021-01-13 code/scripts/higher_order_sims.py
running new higher order sims

@@ -10,15 +10,15 @@ from matplotlib import pyplot as plt
 cond= sys.argv[1]
 r = sys.argv[2] #reps
 
-F = 4 #number of features
-T = 30 #number of timepoints
+F = sys.argv[3] #number of features
+T = sys.argv[4] #number of timepoints
 K = 2 #order
 
 fname = cond + '_' + str(F) + '_' + str(T) + '_' + str(K)
 
 width = 20
 
-results_dir = os.path.join(config['resultsdir'], 'higher_order_sims', cond + '_' + str(T))
+results_dir = os.path.join(config['resultsdir'], 'higher_order_sims_search', cond + '_' + str(T)+ '_' + str(K))
 
 try:
     if not os.path.exists(results_dir):

### 2021-01-15 paper/main.tex
added requested refs to intro and discussion, updated main and diffs

@@
 hypothesized) mental states or cognitive
-representations~\citep[e.g.,][]{HaxbEtal01, NormEtal06, TongPrat12,
+representations~\citep[e.g.,][]{HaxbEtal01, NormEtal06b, TongPrat12,
   MitcEtal08a, KamiTong05, NishEtal11, PereEtal18, HuthEtal12,
@@
   Turk13, DemeEtal19, SoloEtal19, LuriEtal18, PretEtal17, ZouEtal19,
-  MackEtal17}.
+  MackEtal17, BresKels01, McIn00}.
 
@@
 univariate or multivariate neural patterns~\citep[for review
-see][]{NormEtal06}, or (more recently) on patterns of dynamic
+see][]{NormEtal06b}, or (more recently) on patterns of dynamic
 first-order correlations~\citep[i.e., interactions between pairs of
@@
 code is carried by activity patterns that directly reflect ongoing
-cognition~\citep[e.g., following][]{HaxbEtal01, NormEtal06}, versus
+cognition~\citep[e.g., following][]{HaxbEtal01, NormEtal06b}, versus
 the dynamic properties of the network structure itself, independent of
@@
   ParkEtal18b, PretEtal17, MannEtal18, RoyEtal19, LiegEtal19, ZouEtal19,
-  ChanGlov10, GonzEtal19}.  Our study extends this line of work by
+  ChanGlov10, GonzEtal19, McIn00, BresKels01}.  Our study extends this line of work by
 finding cognitively relevant \textit{higher-order} network dynamics
@@
 a given brain structure may relate to how strongly connected that
-structure is with other brain areas~\citep{FallEtal19}.  Further study
+structure is with other brain areas~\citep{FallEtal20}.  Further study
 is needed to understand the role of temporal integration at different
@@
 Analysis~\citep[ICA;][]{JuttHera91, ComoEtal91}, $t$-Stochastic
-Neighbor Embedding~\citep[$t$-SNE;][]{MaatHint08}, Uniform Manifold
+Neighbor Embedding~\citep[$t$-SNE;][]{vandHint08}, Uniform Manifold
 Approximation and Projection~\citep[UMAP;][]{McInEtal18}, non-negative
@@
 matched across participants).  Code for carrying out HTFA on fMRI data
-may be found as part of the BrainIAK toolbox~\citep{brainiak}, which
+may be found as part of the BrainIAK toolbox~\citep{CapoEtal17}, which
 may be downloaded at \href{https://brainiak.org/}{brainiak.org}.
@@
 \bibliographystyle{apacite}
-\bibliography{CDL-bibliography/memlab}
+\bibliography{CDL-bibliography/cdl}
 

### 2021-05-31 paper/supplementary_materials.tex
WIP supplemental update

@@
 \centering
+\includegraphics[width=0.95\textwidth]{figs/sim_heatmaps_time}
+  \caption{\textbf{Recovery heatmap of simulated first-order and
+      second-order dynamic correlations across time and widths.}  Each panel displays a
+    heatmap of the average correlations
+    between the vectorized upper triangles of the recovered
+    first-order and second-order correlation matrices and the true
+    (simulated) first-order and second order correlation matrices
+    across varying times for each synthetic dataset and averaged
+    over all features amounts.  (The averages are taken
+    across 10 different recoveries from
+    randomly generated synthetic datasets of the given category).  For a complete description of each synthetic dataset,
+    see \textit{Synthetic data: simulating dynamic higher-order
+      correlations}.  Estimates were computed using a Laplace kernel with widths.  \textbf{ Constant correlations.}  These datasets
+    have stable (unchanging) underlying second-order correlation
+    matrices.  \textbf{Random correlations.} These datasets are
+    generated using a new independently drawn second-order correlation
+    matrix at each timepoint.  \textbf{Ramping correlations.}
+    These datasets are generated by smoothly varying the underlying
+    second-order correlations between the randomly drawn correlation
+    matrices at the first and last timepoints.  \textbf{Event-based
+      correlations.}  These datasets are each generated using five
+    randomly drawn second-order correlation matrices that each remain
+    stable for a fifth of the total timecourse. try it}
+\label{fig:supp_sim_heatmaps_time}
+\end{figure}
+
+\begin{figure}[p!]
+\centering
+\includegraphics[width=0.95\textwidth]{figs/sim_heatmaps_features}
+  \caption{\textbf{Recovery heatmap of simulated first-order and
+      second-order dynamic correlations across features and widths.}  Each panel displays a
+    heatmap of the average correlations
+    between the vectorized upper triangles of the recovered
+    first-order and second-order correlation matrices and the true
+    (simulated) first-order and second order correlation matrices
+    across varying number of features for each synthetic dataset and averaged
+    over all features amounts.  (The averages are taken
+    across 10 different recoveries from
+    randomly generated synthetic datasets of the given category).  For a complete description of each synthetic dataset,
+    see \textit{Synthetic data: simulating dynamic higher-order
+      correlations}.  Estimates were computed using a Laplace kernel with widths.  \textbf{ Constant correlations.}  These datasets
+    have stable (unchanging) underlying second-order correlation
+    matrices.  \textbf{Random correlations.} These datasets are
+    generated using a new independently drawn second-order correlation
+    matrix at each timepoint.  \textbf{Ramping correlations.}
+    These datasets are generated by smoothly varying the underlying
+    second-order correlations between the randomly drawn correlation
+    matrices at the first and last timepoints.  \textbf{Event-based
+      correlations.}  These datasets are each generated using five
+    randomly drawn second-order correlation matrices that each remain
+    stable for a fifth of the total timecourse. try it}
+\label{fig:supp_sim_heatmaps_features}
+\end{figure}
+
+\begin{figure}[p!]
+\centering
 \includegraphics[width=0.75\textwidth]{figs/supp_15_intact}

### 2021-05-31 code/scripts/higher_order_sims_refactor.py
cleanup higher order sims

@@ -70,38 +70,6 @@ def generate_templates(order=1, **kwargs):
   return templates
 
 
-def generate_templates_refactor(order=1, cov_list=None, **kwargs):
-  kwargs['return_corrs'] = True
-
-  T = kwargs['T']
-  templates = []
-  for n in range(order):
-      print(n)
-
-      if cov_list:
-          kwargs['datagen'] = cov_list[n]
-
-      _, next_template = tc.simulate_data(**kwargs)
-
-
-      if n >= 1:
-          expanded_corrmats_last = tc.vec2mat(templates[n-1])
-          expanded_corrmats_next = tc.vec2mat(next_template)
-
-          K2 = expanded_corrmats_last.shape[0] ** 2
-
-          next_template = np.zeros([K2, K2, T])
-
-          for t in range(T):
-              x_last = expanded_corrmats_last[:, :, t]
-              x_next = expanded_corrmats_next[:, :, t]
-              next_template[:, :, t] = np.kron(x_last, x_next)
-          next_template = tc.mat2vec(next_template)
-
-      templates.append(next_template)
-
-  return templates
-
 
 def generate_data(templates):
     order = len(templates) + 1
@@ -126,43 +94,6 @@ def generate_data(templates):
         next_corrmats = tc.mat2vec(draws)
         adjusted_templates.append(next_corrmats)
 
-        # try_it = np.random.multivariate_normal(np.zeros([sK * sK]), np.eye(sK * sK), size=T)
-        # for t in range(T):
-        #
-        #     #x_hat = np.random.multivariate_normal(means[:, :, t].ravel(), corrmats[:, :, t]).reshape(sK, sK, order='A')
-        #     #x_hat = np.random.multivariate_normal(np.zeros([sK * sK]), corrmats[:, :, t]).reshape(sK, sK, order='A')
-        #     #x_hat = np.random.multivariate_normal(np.zeros([sK * sK]), np.eye(sK * sK))
-        #
-        #     try_c = corrmats[:, :, t]
-        #     #try_c = nearPSD(try_c)
-        #     #sns.heatmap(try_c)
-        #     np.fill_diagonal(try_c, 10)
-        #     c = np.linalg.cholesky(try_c)
-        #
-        #     # #sns.heatmap(c)
-        #     # np.fill_diagonal(c, 0)
-        #     # c /= np.max(np.abs(c))
-        #     #
[…]

### 2021-05-31 paper/main.tex
updates to supp and main text

--- 2020-11-20 paper/main.tex
@@
 \newcommand{\kernelwidth}{S2}
-\newcommand{\intact}{S3}
-\newcommand{\para}{S4}
-\newcommand{\word}{S5}
-\newcommand{\rest}{S6}
-\newcommand{\pca}{S7}
+\newcommand{\time}{S3}
+\newcommand{\features}{S4}
+\newcommand{\intact}{S5}
+\newcommand{\para}{S6}
+\newcommand{\word}{S7}
+\newcommand{\rest}{S8}
+\newcommand{\pca}{S9}
 
@@
 (Fig.~\ref{fig:higher_order_sims}).  When the correlations were stable
-for longer intervals, or changed gradually (constant, ramping, and
+for longer intervals (Figs.~\time), or changed gradually (constant, ramping, and
 event datasets), recovery performance was relatively high, and we were

### 2021-05-31 paper/main.tex
updates to higher order sim text

@@
     computed using a Laplace kernel
-    (width~$=20$).  \textbf{a. Constant correlations.}  These datasets
+    (width~$=20$).  \textbf{Constant correlations.}  These datasets
     have stable (unchanging) underlying second-order correlation
-    matrices.  \textbf{b. Random correlations.} These datasets are
+    matrices.  \textbf{Random correlations.} These datasets are
     generated using a new independently drawn second-order correlation
-    matrix at each timepoint.  \textbf{c. Ramping correlations.}
+    matrix at each timepoint.  \textbf{Ramping correlations.}
     These datasets are generated by smoothly varying the underlying
     second-order correlations between the randomly drawn correlation
-    matrices at the first and last timepoints.  \textbf{d. Event-based
+    matrices at the first and last timepoints.  \textbf{Event-based
       correlations.}  These datasets are each generated using five
@@
 can then generate an order $n$ correlation matrix (for one timepoint, $t$) from an order
-$n - 1$ template (from the same timepoint) as follows:
+$n - 1$ template (from the same timepoint) using the Kronecker product as follows:
 \begin{align}
-  \mathbf{\Sigma_{n}}(t) &= \mathrm{mat}(\mathrm{vec}(\mathbf{\Sigma_{n-1}}(t)) \otimes \mathrm{vec}(\mathbf{\Sigma_{n-1}}(t))^\top).\label{eqn:veccorr}
+  \mathbf{\Sigma_{n}}(t) &= \mathrm{mat}(\mathrm{vec}(\mathbf{\Sigma_{n-1}}(t)) \otimes \mathrm{vec}(\mathbf{\Sigma_{n-1}}(t))).\label{eqn:veccorr}
 \end{align}

### 2021-05-31 paper/main.tex
JRM edits to main text and supplement, recompiled diffs

@@
 \newcommand{\kernelwidth}{S2}
-\newcommand{\time}{S3}
+\newcommand{\timeheatmap}{S3}
 \newcommand{\features}{S4}
@@
 (Fig.~\ref{fig:higher_order_sims}).  When the correlations were stable
-for longer intervals (Figs.~\time), or changed gradually (constant, ramping, and
+for longer intervals, or changed gradually (constant, ramping, and
 event datasets), recovery performance was relatively high, and we were
 better able to recover dynamic first-order correlations than
-second-order correlations.  We expected that this would happen, given
-that errors in our estimation procedure at lower orders necessarily
-propagate to higher orders (since lower-order correlations are used to
-estimate higher-order correlations).  Interestingly, we also found
-that when the correlations were particularly \textit{un}stable (random
-datasets), we better recovered second-order correlations.
+second-order correlations.  This is because errors in our \textit{estimation}
+procedure at lower orders necessarily propagate to higher orders
+(since lower-order correlations are used to estimate higher-order
+correlations).  Conversely, when the correlations were particularly
+\textit{un}stable (random datasets), we better recovered second-order
+correlations.  This is because noise in our \textit{data generation}
+procedure propagates from higher orders to lower orders (see
+\textit{Synthetic data: simulating dynamic high-order correlations}).
 
@@
     computed using a Laplace kernel
-    (width~$=20$).  \textbf{Constant correlations.}  These datasets
+    (width~$=20$).  \textbf{Constant.}  These datasets
     have stable (unchanging) underlying second-order correlation
-    matrices.  \textbf{Random correlations.} These datasets are
+    matrices.  \textbf{Random.} These datasets are
     generated using a new independently drawn second-order correlation
-    matrix at each timepoint.  \textbf{Ramping correlations.}
+    matrix at each timepoint.  \textbf{Ramping.}
     These datasets are generated by smoothly varying the underlying
     second-order correlations between the randomly drawn correlation
-    matrices at the first and last timepoints.  \textbf{Event-based
-      correlations.}  These datasets are each generated using five
+    matrices at the first and last timepoints.  \textbf{Event.}  These datasets are each generated using five
     randomly drawn second-order correlation matrices that each remain
@@
 \end{figure}
+
+We also examined the impact of the data duration (Fig.~\timeheatmap)
+and complexity (number of zero-order features; Fig.~\features) on our
+ability to accurately recover ground truth first-order and
+second-order dynamic correlations.  In general, we found that our approach
+better recovers ground truth dynamic correlations from longer duration
+timeseries data.
+
+We also found that our approach tends to best recover data generated
+using fewer zero-order features (i.e., lower complexity), although
+this tendency was not strictly monotonic.  Further, because our data
+generation procedure requires $\mathcal{O}(K^{4})$ memory to generate
+a second-order timeseries with $K$ zero-order features, we were not
+able to fully explore how the number of zero-order features affects
+recovery accuracy as the number of features gets larger (e.g., as it
+approaches the number of features present in the fMRI data we examine
+below).  Although we were not able to formally test this to our
+satisfaction, we expect that accurately estimating dynamic high-order
+correlations would require data with many more zero-order features
+than we were able to simulate.  Our reasoning is that
+high-order correlations necessarily involve larger numbers of
+lower-order features, so achieving adequate ``resolution'' high-order
+timeseries might require many low-order features.
 
@@
 order $n - 2$ order timeseries, and so on, until we obtain an order 0
-timeseries of simulated data that reflects the chosen high-order dynamics.
-
-The central mathematical operations in our procedure are two bookkeeping
-functions, $\mathrm{vec}(\cdot)$ and $\mathrm{mat}(\cdot)$.  The
-$\mathrm{vec}(\cdot)$ function takes as input a $K \times K$ symmetric
-matrix and returns as output a
-$\left(\frac{K^2 - K}{2} + K\right)$-dimensional column vector
-containing the entries in the upper triangle and diagonal.  The
-$\mathrm{mat}(\cdot)$ function inverts $\mathrm{vec}(\cdot)$ by taking
-as input a $\left(\frac{K^2 - K}{2} + K\right)$-dimensional column
-vector and returning a $K \times K$ symmetric matrix as output.  We
-can then generate an order $n$ correlation matrix (for one timepoint, $t$) from an order
-$n - 1$ template (from the same timepoint) using the Kronecker product as follows:
-\begin{align}
-  \mathbf{\Sigma_{n}}(t) &= \mathrm{mat}(\mathrm{vec}(\mathbf{\Sigma_{n-1}}(t)) \otimes \mathrm{vec}(\mathbf{\Sigma_{n-1}}(t))).\label{eqn:veccorr}
-\end{align}
-
-Given a timeseries of order $n$ correlation matrices, we can draw an
-order $n-1$ correlation matrix for each timepoint $t$ using
-\begin{align}
- \mathbf{\sigma_{n-1}}(t) &\sim \mathcal{N}\left(\mathbf{0}, \mathbf{\Sigma_n}(t)
-                   \right)\label{eqn:highorder-gen1}\\
-  \mathbf{\Sigma_{n-1}}(t) &= \mathrm{mat}(\mathbf{\sigma_{n-1}}(t)).\label{eqn:highorder-gen2}
-  \end{align}
-  We can then use repeated applications of
-  Equations~\ref{eqn:highorder-gen1} and~\ref{eqn:highorder-gen2} in
-  order to obtain a synthetic dataset.
-
- When the template first-order correlations are constructed to exhibit different
- temporal profiles (e.g., using the constant, random, ramping, and
- event procedures described above), the resulting high-order
- correlations and synthetic data will exhibit the same category of
- temporal profile. Following our approach to generating synthetic data exhibiting known
- first-order correlations, we constructed a total of 40 additional multivariate timeseries,
-collectively reflecting a total of 4 qualitatively different patterns
-of dynamic correlations (i.e., 10 datasets reflecting each type of
-dynamic pattern: constant, random, ramping, and event).
+timeseries of simulated data that reflects the chosen high-order
+dynamics.
+
+The central mathematical operation in our procedure is the Kronecker
+product ($\otimes$).  The Kronecker product of a $K \times K$ matrix,
+$m_1$, with itself (i.e., $m_1 \otimes m_1$) produces a new
+$K^2 \times K^2$ matrix, $m_2$ whose entries reflect a scaled tiling
+of the entries in $m_1$.  If these tilings (scaled copies of $m_1$) are
+indexed by row and column, then the tile in the
+$i$\textsuperscript{th} row and $j$\textsuperscript{th} column
+contains the entries of $m_1$, multiplied by $m_1(i, j)$.  Following
+this pattern, the Kronecker product $m_2 \otimes m_2$ yields the
+$K^4 \times K^4$ matrix $m_3$ whose tiles are scaled copies of $m_2$.
+In general, repeated applications of the Kronecker self-product may be
+used to generate $m_{n+1} = m_n \otimes m_n$ for $n > 1$, where
+$m_{n+1}$ is a $K^{2^n} \times K^{2^n}$ matrix.  After generating a
+first-order timeseries of dynamic correlations (see \textit{Synthetic
+  data: simulating dynamic first-order correlations}), we use this
+procedure (applied independently at each timepoint) to transform it
+into a timeseries of $n$\textsuperscript{th}-order correlations.  When
+$m_{n+1}$ is generated in this way, the temporal structure of the full
+timeseries (i.e., constant, random, ramping, event) is preserved,
+since changes in the original first-order timeseries are also
+reflected in the scaled tilings of itself that comprise the
+higher-order matrices.
+
+Given a timeseries of $n$\textsuperscript{th}-order correlations, we
+then need to work ``backwards'' in order to generate the order-zero
+timeseries.  If the $n$\textsuperscript{th}-order correlation matrix
+at a given timepoint is $m_n$, then we can generate an order $n-1$
+correlation matrix (for $n > 1$) by taking a draw from
+$\mathcal{N}\left(0, m_n\right)$ and reshaping the resulting vector to
+have square dimensions.  Intuitively, the re-shaped matrix will look
+like a noisy version of the template matrix, $m_{n-1}$.  (When
+$n = 1$, no re-shaping is needed; the resulting $K$-dimensional vector
+may be used as the observation at the given timepoint.)  After
+independently drawing each timepoint's order $n-1$ correlation matrix
+from that timepoint's order $n$ correlation matrix, this process can
+be applied repeatedly until $n = 0$.  This results in a
+$K$-dimensional timeseries of $T$ observations containing the
+specified high-order correlations at orders 1 through $n$.  Following
+our approach to generating synthetic data exhibiting known first-order
+correlations, we constructed a total of 40 additional multivariate
+timeseries, collectively reflecting a total of 4 qualitatively
+different patterns of dynamic correlations (i.e., 10 datasets
+reflecting each type of dynamic pattern: constant, random, ramping,
+and event).
 

### 2021-06-04 paper/main.tex
minor formatting edits

@@
 \textit{un}stable (random datasets), we better recovered second-order
-correlations.  This is because noise in our \textit{data generation}
+correlations.  This is because noises in our \textit{data generation}
 procedure propagates from higher orders to lower orders (see
@@
     stable for a fifth of the total timecourse.  The
-    vertical lines denote event boundaries.}
+    vertical lines denote event boundaries.  Note that the ``dips''
+    and ``ramps'' at the boundaries of sharp transitions (e.g., the
+    beginning and ends of the ``constant'' and ``ramping'' datasets,
+    and at the event boundaries of the ``event'' datasets) are
+    finite-sample effects that reflect the reduced numbers of samples
+    that may be used to accurately estimate correlations at sharp
+    boundaries.}
   \label{fig:higher_order_sims}
@@
 better recovers ground truth dynamic correlations from longer duration
-timeseries data.
-
-We also found that our approach tends to best recover data generated
+timeseries data.  We also found that our approach tends to best recover data generated
 using fewer zero-order features (i.e., lower complexity), although

### 2021-06-04 paper/supplementary_materials.tex
updates to supp and main text

--- 2020-11-20 paper/supplementary_materials.tex
@@
 \centering
+\includegraphics[width=0.95\textwidth]{figs/sim_heatmaps_time}
+  \caption{\textbf{Recovery heatmap of simulated first-order and
+      second-order dynamic correlations across time and widths.}  Each panel displays a
+    heatmap of the average correlations
+    between the vectorized upper triangles of the recovered
+    first-order and second-order correlation matrices and the true
+    (simulated) first-order and second order correlation matrices.
+    The averages are taken across several randomly generated
+    synthetic datasets for each timeseries pattern (constant, random,
+    ramping, and data; see \textit{Synthetic data: simulating dynamic higher-order
+      correlations}).  The $x$-axes of each heatmap denote varying
+    Laplace-shaped kernel widths (see Figs.~\ref{fig:supp_kernels}
+    and~\ref{fig:supp_widths}), and the $y$-axes of each heatmap
+    denote varying durations (in samples) of the synthetic datasets.
+    A total of 10 synthetic datasets were generated for each duration
+    (row) and timeseries pattern (panel).}
+\label{fig:time}
+\end{figure}
+
+\begin{figure}[p!]
+\centering
+\includegraphics[width=0.95\textwidth]{figs/sim_heatmaps_features}
+  \caption{\textbf{Recovery heatmap of simulated first-order and
+      second-order dynamic correlations across features and widths.}  Each panel displays a
+    heatmap of the average correlations
+    between the vectorized upper triangles of the recovered
+    first-order and second-order correlation matrices and the true
+    (simulated) first-order and second order correlation matrices.
+    The averages are taken across several randomly generated
+    synthetic datasets for each timeseries pattern (constant, random,
+    ramping, and data; see \textit{Synthetic data: simulating dynamic higher-order
+      correlations}).  The $x$-axes of each heatmap denote varying
+    Laplace-shaped kernel widths (see Figs.~\ref{fig:supp_kernels}
+    and~\ref{fig:supp_widths}), and the $y$-axes of each heatmap
+    denote varying numbers of features ($K$) used in each of the synthetic datasets.
+    A total of 10 synthetic datasets were generated for each number of features
+    (row) and timeseries pattern (panel).}
+\label{fig:features}
+\end{figure}
+
+\begin{figure}[p!]
+\centering
 \includegraphics[width=0.75\textwidth]{figs/supp_15_intact}
@@
 \renewcommand{\refname}{Supplementary references}
-\bibliography{CDL-bibliography/memlab}
+\bibliography{CDL-bibliography/cdl}
 

### 2021-06-09 paper/main.tex
updated main text, added cover letter and response to rev2 reviewer comments

@@
     underlying correlation at each timepoint or a reference
-    correlation matrix.  (The averages are taken across 10 different
-    randomly generated synthetic datasets of the given category.)
+    correlation matrix.  (The averages are taken across 100 different
+    randomly generated synthetic datasets of each given category, each
+    with $K = 50$ features and $T = 300$ timepoints.)
     Error ribbons denote 95\% confidence intervals (taken across
@@
 \textit{Synthetic data: simulating dynamic higher-order
-  correlations}).  We generated a total of 40 datasets that varied in
+  correlations}).  We generated a total of 400 datasets that varied in
 how the first-order and second-order correlations changed over time.
@@
     (simulated) first-order and second order correlation matrices at each
-    timepoint and for each synthetic dataset.  (The averages are taken across 10 different
-    randomly generated synthetic datasets of the given category.)
+    timepoint and for each synthetic dataset.  (The averages are taken across 100 different
+    randomly generated synthetic datasets of each given category, each
+    with $K = 10$ features and $T = 300$ timepoints.)
     Error ribbons denote 95\% confidence intervals (taken across
@@
 be similar across individuals.
+
+One limitation of our approach relates to how noise propagates in our
+estimation procedure.  Specifically, our procedure for estimating
+high-order dynamic correlations depends on estimates of lower-order
+dynamic correlations.  This means that our measures of which
+higher-order patterns are reliable and stable across experimental
+conditions are partially confounded with the stability of lower-order
+patterns.  Prior work suggests that the stability of what we refer to
+here as first-order dynamics likely varies across the experimental
+conditions we examined~\citep{SimoEtal16}.  Therefore a caveat to our
+claim that richer stimuli evoke more stable higher-order dynamics is
+that our approach assumes that those high-order dynamics reflect
+relations or interactions between lower-order features.
 
@@
 \subsubsection*{Synthetic data: simulating dynamic first-order correlations}
-We constructed a total of 40 different multivariate timeseries,
+We constructed a total of 400 different multivariate timeseries,
 collectively reflecting a total of 4 qualitatively different patterns
-of dynamic first-order correlations (i.e., 10 datasets reflecting each type of
+of dynamic first-order correlations (i.e., 100 datasets reflecting each type of
 dynamic pattern).  Each timeseries comprised 50 features (dimensions)
@@
 correlation ``dynamics'' when the ground truth correlations were
-static.  We constructed 10 multivariate timeseries whose observations
+static.  We constructed 100 multivariate timeseries whose observations
 were each drawn from a single (stable) Gaussian distribution.  For
@@
   were drawn from a multivariate Gaussian distribution with the same
-  covariance matrix, and the 10 datasets each used a different
+  covariance matrix, and the 100 datasets each used a different
   covariance matrix.
 
-  \paragraph*{Random.}  We generated a second set of 10 synthetic
+  \paragraph*{Random.}  We generated a second set of 100 synthetic
   datasets whose observations at each timepoint were drawn from a
@@
 
-  \paragraph*{Ramping.}  We generated a third set of 10 synthetic
+  \paragraph*{Ramping.}  We generated a third set of 100 synthetic
   datasets whose underlying correlations changed gradually over time.
@@
 
-\paragraph*{Event.} We generated a fourth set of 10 synthetic datasets
+\paragraph*{Event.} We generated a fourth set of 100 synthetic datasets
 whose underlying correlation matrices exhibited prolonged intervals of
@@
 our approach to generating synthetic data exhibiting known first-order
-correlations, we constructed a total of 40 additional multivariate
+correlations, we constructed a total of 400 additional multivariate
 timeseries, collectively reflecting a total of 4 qualitatively
-different patterns of dynamic correlations (i.e., 10 datasets
+different patterns of dynamic correlations (i.e., 100 datasets
 reflecting each type of dynamic pattern: constant, random, ramping,
-and event).
+and event).  Each timeseries comprised 10 zero-order features (dimensions)
+that varied over 300 timepoints.  After applying our dynamic
+correlation estimation procedure, this yielded a 100-dimensional
+timeseries of first-order
+features that could then be used to estimate dynamic second-order
+correlations.  (We chose to use $K=10$ zero-order features for our
+higher order simulations in order to put the accuracy computations
+displayed in Figs.~\ref{fig:synthetic} and~\ref{fig:higher_order_sims}
+on a roughly even footing.)
 

### 2021-06-10 paper/main.tex
minor typo corrections, recompiled diffs

@@
 narrow) performed best.  This is because, when every timepoint's
-correlations are independent of the correlations at every other
+correlations are independent from the correlations at every other
 timepoint, averaging data over time dilutes the available signal.
@@
 \textit{un}stable (random datasets), we better recovered second-order
-correlations.  This is because noises in our \textit{data generation}
+correlations.  This is because noise in our \textit{data generation}
 procedure propagates from higher orders to lower orders (see

### 2021-06-10 paper/main.tex
updated description of how we normalized the decoding accuracies in fig 4

@@
       PCA.}  This panel displays the same results as Panel a, but here
-    each curve has been normalized to have a maximum value of 1 and a
-    minimum value of 0 (including the upper and lower bounds of the
-    respective 95\% confidence intervals).  Panels a and b used PCA to
+    each curve has been normalized to be bounded between 0 and 1
+    (inclusive) by subtracting the minimum accuracy
+    (across all folds and orders) and then dividing by the maximum
+    accuracy (again, across all folds and orders).  Panels a and b used PCA to
     project each high-dimensional pattern of dynamic correlations onto

### 2021-06-10 paper/main.tex

--- 2021-06-09 paper/main.tex
@@
     correlation matrix.  (The averages are taken across 100 different
-    randomly generated synthetic datasets of each given category, each
-    with $K = 50$ features and $T = 300$ timepoints.)
+    randomly generated synthetic datasets of the given category.)
     Error ribbons denote 95\% confidence intervals (taken across
@@
 \textit{Synthetic data: simulating dynamic higher-order
-  correlations}).  We generated a total of 400 datasets that varied in
+  correlations}).  We generated a total of 400 datasets (100 datasets
+for each category) that varied in
 how the first-order and second-order correlations changed over time.
@@
     timepoint and for each synthetic dataset.  (The averages are taken across 100 different
-    randomly generated synthetic datasets of each given category, each
-    with $K = 10$ features and $T = 300$ timepoints.)
+    randomly generated synthetic datasets of the given category.)
     Error ribbons denote 95\% confidence intervals (taken across
@@
 be similar across individuals.
-
-One limitation of our approach relates to how noise propagates in our
-estimation procedure.  Specifically, our procedure for estimating
-high-order dynamic correlations depends on estimates of lower-order
-dynamic correlations.  This means that our measures of which
-higher-order patterns are reliable and stable across experimental
-conditions are partially confounded with the stability of lower-order
-patterns.  Prior work suggests that the stability of what we refer to
-here as first-order dynamics likely varies across the experimental
-conditions we examined~\citep{SimoEtal16}.  Therefore a caveat to our
-claim that richer stimuli evoke more stable higher-order dynamics is
-that our approach assumes that those high-order dynamics reflect
-relations or interactions between lower-order features.
 
@@
 reflecting each type of dynamic pattern: constant, random, ramping,
-and event).  Each timeseries comprised 10 zero-order features (dimensions)
-that varied over 300 timepoints.  After applying our dynamic
-correlation estimation procedure, this yielded a 100-dimensional
-timeseries of first-order
-features that could then be used to estimate dynamic second-order
-correlations.  (We chose to use $K=10$ zero-order features for our
-higher order simulations in order to put the accuracy computations
-displayed in Figs.~\ref{fig:synthetic} and~\ref{fig:higher_order_sims}
-on a roughly even footing.)
+and event).  Each timeseries comprised 10 features (dimensions)
+that varied over 300 timepoints for first-order correlations, and
+therefore 100 second-order features.
 

### 2021-06-10 paper/old.tex
rearranged order of sections in old.tex to improve accuracy of diff.tex

--- 2020-11-13 paper/main.tex
@@
     sets).  The colors denote the experimental condition.  Arrows
-    denote sets of features that yielded reliably higher (upwards
+    denote sets of features that yielded reliably higher (upward
     facing) or lower (downward facing) decoding accuracy than the mean
-    of all other features (via a two-tailed test, thresholded at
+    of all other features (via a two-tailed $t$-test, thresholded at
     $p < 0.05$).  Figure~\ref{fig:ttests} displays additional
@@
   ChieHone19}.  A similar hierarchy appears to play a role in
-predicting future events~\citep{LeeEtal20}.  Other
-related work in human and mouse brains indicates that the temporal
-response profile of a given brain structure may relate to how strongly
-connected that structure is with other brain
-areas~\citep{FallEtal19}.  Further study is needed to understand the
-role of temporal integration at different scales of network
-interaction, and across different anatomical structures. Importantly,
-our analyses do not speak to the physiological basis of higher-order
-dynamics, and could reflect nonlinearities, chaotic patterns,
-non-stationarities, or multistability, etc. However, our decoding analyses do indicate
-that higher-order dynamics are
-consistent across individuals, and therefore unlikely to be driven by
-non-stimulus-driven dynamics which are unlikely to be similar across
-individuals.
+predicting future events~\citep{LeeEtal20}.  Other related work in
+human and mouse brains indicates that the temporal response profile of
+a given brain structure may relate to how strongly connected that
+structure is with other brain areas~\citep{FallEtal20}.  Further study
+is needed to understand the role of temporal integration at different
+scales of network interaction, and across different anatomical
+structures. Importantly, our analyses do not speak to the
+physiological basis of higher-order dynamics, and could reflect
+nonlinearities, chaotic patterns, non-stationarities, and/or
+multistability, etc. However, our decoding analyses do indicate that
+higher-order dynamics are consistent across individuals, and therefore
+unlikely to reflect non-stimulus-driven dynamics that are unlikely to
+be similar across individuals.
 

### 2021-06-24 paper/main.tex

--- 2021-06-10 paper/main.tex
@@
 $\mathcal{N}\left(0, m_n\right)$ and reshaping the resulting vector to
-have square dimensions.  Intuitively, the re-shaped matrix will look
-like a noisy version of the template matrix, $m_{n-1}$.  (When
+have square dimensions.  To force the resulting matrix to be
+symmetric, we remove its lower triangle, and replace the lower
+triangle with (a reflected version
+of) its upper triangle.  Intuitively, the resulting re-shaped matrix will look
+like a noisy (but symmetric) version of the template matrix, $m_{n-1}$.  (When
 $n = 1$, no re-shaping is needed; the resulting $K$-dimensional vector

### 2021-07-02 paper/main.tex

--- 2021-06-10 paper/main.tex
@@
 \usepackage{setspace}
-\usepackage{apacite}
 \usepackage{hyperref}
-\usepackage[sort]{natbib}
+\usepackage[font=small,labelfont=bf]{caption}
+\usepackage[sort&compress, numbers, super]{natbib}
 \usepackage{pxfonts}
@@
 \usepackage{soul}
+\usepackage[nofiglist, fighead]{endfloat}
 \linenumbers
@@
   different subgraphs of the brain's functional connectome that display
-  homologous lower-level dynamic correlations.  We tested the
+  homologous lower-level dynamic correlations.  Here we test the
   hypothesis that high-level cognition is reflected in high-order
-  dynamic correlations in brain activity patterns.  We developed an
+  dynamic correlations in brain activity patterns.  We develop an
   approach to estimating high-order dynamic correlations in timeseries
-  data, and we applied the approach to neuroimaging data collected as
-  human participants either listened to a ten-minute story or listened
-  to a temporally scrambled version of the story.  We trained
+  data, and we apply the approach to neuroimaging data collected as
+  human participants either listen to a ten-minute story or listen
+  to a temporally scrambled version of the story.  We train
   across-participant pattern classifiers to decode (in held-out data)
   when in the session each neural activity snapshot was collected.  We
-  found that classifiers trained to decode from high-order dynamic
-  correlations yielded the best performance on data collected as
+  find that classifiers trained to decode from high-order dynamic
+  correlations yield the best performance on data collected as
   participants listened to the (unscrambled) story.  By contrast,
@@
 A central goal in cognitive neuroscience is to elucidate the
-\textit{neural code}: the mapping between (a) mental states or
+neural code: the mapping between (a) mental states or
 cognitive representations and (b) neural activity patterns. One means
@@
 see][]{ReimEtal17}?  Second-order correlations reflect
-\textit{homologous} patterns of correlation.  In other words, if the
+homologous patterns of correlation.  In other words, if the
 dynamic patterns of correlations between two regions, $A$ and $B$, are
@@
 latter approach characterizes correlations between each feature
-dimension's relative \textit{position} in the network (at each moment
+dimension's relative position in the network (at each moment
 in time) in favor of the specific activity histories of different
@@
 stimulus-driven high-order correlations in multivariate timeseries
-data (see \textit{Dynamic inter-subject functional connectivity
-  (DISFC)} and \textit{Dynamic higher-order correlations}).  We
+data (see Dynamic inter-subject functional connectivity
+  (DISFC) and Dynamic higher-order correlations).  We
 evaluated the efficacy of this framework at recovering known patterns
-in several synthetic datasets (see \textit{Synthetic data: simulating
-  dynamic first-order correlations} and \textit{Synthetic data:
-  simulating dynamic higher-order correlations}).  We then
+in several synthetic datasets (see Synthetic data: simulating
+  dynamic first-order correlations and Synthetic data:
+  simulating dynamic higher-order correlations).  We then
 applied the framework to a public fMRI dataset collected as
@@
 temporally scrambled version of the story, or underwent a resting
-state scan (see \textit{Functional neuroimaging data collected during
-  story listening}).  We used the relative decoding accuracies of
+state scan (see Functional neuroimaging data collected during
+  story listening).  We used the relative decoding accuracies of
 classifiers trained on different sets of neural features to estimate
@@
 
-\subsection*{Recovering known dynamic correlations from synthetic
-  data}
-\subsubsection*{Recovering dynamic first-order correlations}
+\subsection*{Recovering dynamic first-order correlations}
 We generated synthetic datasets that differed in how the underlying first-order
@@
     parameter.  For a complete description of each synthetic dataset,
-    see \textit{Synthetic data: simulating dynamic first-order
-      correlations}.  \textbf{a. Constant correlations.}  These
+    see Synthetic data: simulating dynamic first-order
+      correlations.  \textbf{a. Constant correlations.}  These
     datasets have a stable (unchanging) underlying correlation matrix.
@@
     correlations.  The middle panel compares the recovered
-    correlations with the \textit{first} timepoint's correlation
+    correlations with the first timepoint's correlation
     matrix.  The right panel compares the recovered correlations with
-    the \textit{last} timepoint's correlation matrix.
+    the last timepoint's correlation matrix.
     \textbf{d. Event-based correlations.}  These datasets are each
@@
 
-\subsubsection*{Recovering dynamic higher-order correlations}
+\subsection*{Recovering dynamic higher-order correlations}
 Following our approach to evaluating our ability to recover known
@@
 analogous second set of synthetic datasets that we designed to exhibit
-known dynamic first-order \textit{and} second-order correlations (see
-\textit{Synthetic data: simulating dynamic higher-order
-  correlations}).  We generated a total of 400 datasets (100 datasets
+known dynamic first-order and second-order correlations (see
+Synthetic data: simulating dynamic higher-order
+  correlations).  We generated a total of 400 datasets (100 datasets
 for each category) that varied in
@@
 better able to recover dynamic first-order correlations than
-second-order correlations.  This is because errors in our \textit{estimation}
+second-order correlations.  This is because errors in our estimation
 procedure at lower orders necessarily propagate to higher orders
@@
 correlations).  Conversely, when the correlations were particularly
-\textit{un}stable (random datasets), we better recovered second-order
-correlations.  This is because noises in our \textit{data generation}
+unstable (random datasets), we better recovered second-order
+correlations.  This is because noises in our data generation
 procedure propagates from higher orders to lower orders (see
-\textit{Synthetic data: simulating dynamic high-order correlations}).
+Synthetic data: simulating dynamic high-order correlations).
 
@@
     datasets).  For a complete description of each synthetic dataset,
-    see \textit{Synthetic data: simulating dynamic higher-order
-      correlations}.  All estimates represented in this figure were
+    see Synthetic data: simulating dynamic higher-order
+      correlations.  All estimates represented in this figure were
     computed using a Laplace kernel
@@
 We used across-participant temporal decoders to identify cognitively
-relevant neural patterns in fMRI data (see \textit{Forward inference
-  and decoding accuracy}).  The dataset we examined~\citep[collected
+relevant neural patterns in fMRI data (see Forward inference
+  and decoding accuracy).  The dataset we examined~\citep[collected
 by][]{SimoEtal16} comprised four experimental conditions that exposed
 participants to stimuli that varied systematically in how cognitively
-engaging they were.  The \textit{intact} experimental condition had
+engaging they were.  The intact experimental condition had
 participants listen to an audio recording of a 10-minute story.  The
-\textit{paragraph}-scrambled experimental condition had participants
+paragraph-scrambled experimental condition had participants
 listen to a temporally scrambled version of the story, where the
@@
 participants in this condition experienced the scrambled paragraphs in
-the same order.  The \textit{word}-scrambled experimental condition
+the same order.  The word-scrambled experimental condition
 had participants listen to a temporally scrambled version of the story
@@
 participants in the word condition experienced the scrambled words in
-the same order.  Finally, in a \textit{rest} experimental condition,
+the same order.  Finally, in a rest experimental condition,
 participants lay in the scanner with no overt stimulus, with their
@@
     \textbf{a.~Decoding accuracy as a function of order: PCA.}
-    \textit{Order} ($x$-axis) refers to the maximum order of dynamic
+    Order ($x$-axis) refers to the maximum order of dynamic
     correlations that were available to the classifiers (see
-    \textit{Feature weighting and testing}).  The reported
+    Feature weighting and testing).  The reported
     across-participant decoding accuracies are averaged over all
-    kernel shapes and widths (see \textit{Identifying robust decoding
-      results}).  The $y$-values are displayed relative to chance
+    kernel shapes and widths (see Identifying robust decoding
+      results).  The $y$-values are displayed relative to chance
     accuracy (intact: $\frac{1}{300}$; paragraph: $\frac{1}{272}$;
@@
 weighted blend of neural patterns that reflected up to
-$n^\mathrm{th}$-order dynamic correlations (see \textit{Feature
-  weighting and testing}, Fig.~\ref{fig:pipeline}).  We repeated this process for
+$n^\mathrm{th}$-order dynamic correlations (see Feature
+  weighting and testing, Fig.~\ref{fig:pipeline}).  We repeated this process for
 $n \in \left\{ 0, 1, 2, ..., 10 \right\}$.  Our examinations of
@@
 of kernel shapes and widths in order to identify results that were
-robust to specific kernel parameters (see \textit{Identifying robust
-  decoding results}).
+robust to specific kernel parameters (see Identifying robust
+  decoding results).
 
@@
   entries display the relative average optimized weight given to each type of feature in
-  a decoder that included all feature types (see \textit{Feature
-    weighting and testing}).}
+  a decoder that included all feature types (see Feature
+    weighting and testing).}
 \label{fig:ttests}
@@
     experimental condition.  Additional maps and their corresponding
-    Neurosynth terms may be found in the \textit{Supplementary
-      materials} (intact: Fig.~\intact; paragraph: Fig.~\para; word:
+    Neurosynth terms may be found in the Supplementary
+      materials (intact: Fig.~\intact; paragraph: Fig.~\para; word:
     Fig.~\word; rest: Fig.~\rest).}
@@
 correlated pairs of regions in each of these matrices
-(Fig.~\ref{fig:neurosynth}; see \textit{Reverse inference}).
+(Fig.~\ref{fig:neurosynth}; see Reverse inference).
 
@@
   ChanGlov10, GonzEtal19, McIn00, BresKels01}.  Our study extends this line of work by
-finding cognitively relevant \textit{higher-order} network dynamics
+finding cognitively relevant higher-order network dynamics
 that reflect ongoing cognition.  Our findings also complement other work
@@
 dynamic correlations between the columns of $\mathbf{X}_n$.  In this
-way, we refer to $n$ as the \textit{order} of the timeseries, where
+way, we refer to $n$ as the order of the timeseries, where
 $\mathbf{X}_0$ (order 0) denotes the original data and $\mathbf{X}_n$
@@
 We can generalize this formula to compute time-varying correlations by
-incorporating a \textit{kernel function} that takes a time $t$ as
+incorporating a kernel function that takes a time $t$ as
 input, and returns how much the observed data at each timepoint
@@
     Ricker wavelet centered on time $t$.  This function highlights the
-    \textit{contrasts} between local versus surrounding activity
+    contrasts between local versus surrounding activity
     patterns in estimating dynamic correlations. Weights derived using
@@
 can update the static correlation formula in Equation~\ref{eqn:corr}
-to estimate the \textit{instantaneous correlation} at timepoint $t$:
+to estimate the instantaneous correlation at timepoint $t$:
 \begin{align}
@@
 ($n > 0$) for each of $P$ participants in an experiment.  We can use
-\textit{inter-subject functional connectivity}~\citep[ISFC;
+inter-subject functional connectivity~\citep[ISFC;
 ][]{SimoEtal16, SimoChan20} to compute the stimulus-driven correlations reflected
@@
 (Eqn.~\ref{eqn:timecorr}) between each column of $\mathbf{X}_n^p$ and each
-column of the average $\mathbf{X}_n$ from all \textit{other}
+column of the average $\mathbf{X}_n$ from all other
 participants, $\bar{\mathbf{X}}_n^{ \backslash p}$:
@@
 data in $\mathbf{X}_0$.  We also explore graph measures that instead
-characterize each feature's relative \textit{position} in the broader
+characterize each feature's relative position in the broader
 network of interactions and connections.  To illustrate the
@@
 (correlation) between them will be close to 0.
-However, if $A$ and $B$ each interact with \textit{other} nodes in similar ways, we
+However, if $A$ and $B$ each interact with other nodes in similar ways, we
 might attempt to capture those similarities between $A$'s and $B$'s
@@
   datasets whose underlying correlations changed gradually over time.
-  For each dataset, we constructed two \textit{anchor} covariance
+  For each dataset, we constructed two anchor covariance
   matrices using Equation~\ref{eqn:randcorr},
@@
 $m_{n+1}$ is a $K^{2^n} \times K^{2^n}$ matrix.  After generating a
-first-order timeseries of dynamic correlations (see \textit{Synthetic
-  data: simulating dynamic first-order correlations}), we use this
+first-order timeseries of dynamic correlations (see Synthetic
+  data: simulating dynamic first-order correlations), we use this
 procedure (applied independently at each timepoint) to transform it
@@
 paper for which the data were collected~\citep{SimoEtal16}.
+Procedures were approved by the Princeton University Committee on Activities Involving Human Subjects, and by Western Institutional Review Board (Puyallup, WA).
+All subjects were native English speakers with normal hearing and provided written informed consent.
 
@@
 the true timepoint labels (for each group), we defined the
-\textit{decoding accuracy} as the average proportion of correctly
+decoding accuracy as the average proportion of correctly
 decoded timepoints, across both groups.  We defined the
-\textit{relative decoding accuracy} as the difference between the
+relative decoding accuracy as the difference between the
 decoding accuracy and chance accuracy (i.e., $\frac{1}{T}$).
@@
 might be reliably achieved by a different set of parameters, and the
-best decoding accuracy across \textit{all} timepoints might be
+best decoding accuracy across all timepoints might be
 reliably achieved by still another different set of parameters.
@@
 dynamic high-order correlations) measured at two RBF nodes (see
-\textit{Hierarchical Topographic Factor Analysis}).  Therefore, the 10
+Hierarchical Topographic Factor Analysis).  Therefore, the 10
 strongest correlations involved up to 20 RBF nodes.  Each RBF defines
@@
 order.
+
+\section*{Data Availability}
+
+The authors declare that the data supporting the findings of this
+study as well as the source data for this paper are available at \href{https://github.com/ContextLab/timecorr-paper/releases/tag/v0.3}{github.com/ContextLab/timecorr-paper/releases/tag/v0.3}.
+The fMRI dataset collected by \cite{SimoEtal16} has been made publicly available at
+\href{http://arks.princeton.edu/ark:/88435/dsp015d86p269k}{arks.princeton.edu/ark:/88435/dsp015d86p269k}
 
@@
 
-\bibliographystyle{apacite}
+\section*{Competing interests}
+The authors declare no competing financial interests.
+
+\bibliographystyle{naturemag}
 \bibliography{CDL-bibliography/cdl}

### 2021-07-02 paper/supplementary_materials.tex

@@
-\documentclass{article}
+\documentclass[english]{article}
+\usepackage{graphicx}
+\usepackage{amsmath}
+\usepackage{hyperref}
+\usepackage{setspace}
+\usepackage{hyperref}
+\usepackage[font=small,labelfont=bf]{caption}
+\usepackage[sort&compress, numbers, super]{natbib}
+\usepackage{pxfonts}
 \usepackage[utf8]{inputenc}
-\usepackage[english]{babel}
-\usepackage[font=small,labelfont=bf]{caption}
-\usepackage{geometry}
-\usepackage{natbib}
-\usepackage{pxfonts}
-\usepackage{graphicx}
-\usepackage{newfloat}
-\usepackage{setspace}
+\usepackage[left=1in,right=1in,top=1in,bottom=1in]{geometry}
+\usepackage[left]{lineno}
+\usepackage{soul}
+\linenumbers
 %\doublespacing
@@
   jeremy.r.manning@dartmouth.edu}
-
-\bibliographystyle{apa}
 
@@
       correlation order and cognitive engagement across kernels.}
-    \textbf{a.-c.~Timepoint decoding accuracy as a function of order: PCA.} \textit{Order} ($x$-axis) refers to the maximum order of dynamic
+    \textbf{a.-c.~Timepoint decoding accuracy as a function of order: PCA.} Order ($x$-axis) refers to the maximum order of dynamic
     correlations that were available to the classifiers (see
-    \textit{Feature weighting and testing}).  The reported
+    Feature weighting and testing).  The reported
     across-participant decoding accuracies for \textbf{a. Gaussian},
     \textbf{b. Laplace}, and \textbf{c. Mexican hat} kernel shapes are averaged over all
-   widths (see \textit{Identifying robust decoding
-      results}).  The $y$-values are displayed relative to chance
+   widths (see Identifying robust decoding
+      results).  The $y$-values are displayed relative to chance
     accuracy (intact: $\frac{1}{300}$; paragraph: $\frac{1}{272}$;
@@
       correlation order and cognitive engagement across widths.}
-    \textbf{a.-d.~Timepoint decoding accuracy as a function of order: PCA.} \textit{Order} ($x$-axis) refers to the maximum order of dynamic
+    \textbf{a.-d.~Timepoint decoding accuracy as a function of order: PCA.} Order ($x$-axis) refers to the maximum order of dynamic
     correlations that were available to the classifiers (see
-    \textit{Feature weighting and testing}).  The reported
+    Feature weighting and testing).  The reported
     across-participant decoding accuracies for kernel widths of \textbf{a. 5},
     \textbf{b. 10}, \textbf{c. 20}, and \textbf{d. 50} are averaged over all
-    kernel shapes (see \textit{Identifying robust decoding
-      results}).  The $y$-values are displayed relative to chance
+    kernel shapes (see Identifying robust decoding
+      results).  The $y$-values are displayed relative to chance
     accuracy (intact: $\frac{1}{300}$; paragraph: $\frac{1}{272}$;
@@
     synthetic datasets for each timeseries pattern (constant, random,
-    ramping, and data; see \textit{Synthetic data: simulating dynamic higher-order
-      correlations}).  The $x$-axes of each heatmap denote varying
+    ramping, and data; see Synthetic data: simulating dynamic higher-order
+      correlations).  The $x$-axes of each heatmap denote varying
     Laplace-shaped kernel widths (see Figs.~\ref{fig:supp_kernels}
@@
 \caption{\textbf{Top terms associated with the most strongly
-      correlated nodes at each order, for the \textit{intact} experimental
+      correlated nodes at each order, for the intact experimental
     condition.}  Each color corresponds to one order of inter-subject
@@
 \caption{\textbf{Top terms associated with the most strongly
-      correlated nodes at each order, for the \textit{paragraph} experimental
+      correlated nodes at each order, for the paragraph experimental
     condition.}  This figure is in the same format as
@@
 \caption{\textbf{Top terms associated with the most strongly
-      correlated nodes at each order, for the \textit{word} experimental
+      correlated nodes at each order, for the word experimental
     condition.}  This figure is in the same format as
@@
 \caption{\textbf{Top terms associated with the most strongly
-      correlated nodes at each order, for the \textit{rest} experimental
+      correlated nodes at each order, for the rest experimental
     condition.}  This figure is in the same format as
@@
 \caption{\textbf{Cumulative percent variance explained as a function
-    of the number of principle components.}  \textit{Order} refers to the order of the dynamic
+    of the number of principle components.}  Order refers to the order of the dynamic
     correlations calculated. Principle components analysis was
@@
 \renewcommand{\refname}{Supplementary references}
+\bibliographystyle{naturemag}
 \bibliography{CDL-bibliography/cdl}

### 2021-07-09 code/scripts/plot_15.py
code cleanup for replication with source data

@@ -1,13 +1,19 @@
 
 import supereeg as se
 import os
+import numpy as np
 from visbrain.objects import BrainObj, SceneObj, SourceObj, ColorbarObj
 
 cmap = 'autumn_r'
 
-neurosynth_dir ='../figs/neurosynth_data'
+replication_dir ='../figs/replication/'
+neurosynth_dir = os.path.join(replication_dir, 'neurosynth_data')
+fig_dir = replication_dir
 
-fig_dir = '../figs'
+#
+# neurosynth_dir ='../figs/neurosynth_data'
+#
+# fig_dir = '../figs'
 
 bo_dir = os.path.join(neurosynth_dir, 'bos')
 
@@ -19,68 +25,112 @@ conditions = ['intact', 'paragraph', 'rest', 'word']
 
 for c in conditions:
 
+    data1 = np.load(os.path.join(bo_dir,f'{c}_1_data_largest_abs.npy'))
+    xyz1 = np.load(os.path.join(bo_dir, f'{c}_1_locs_largest_abs.npy'))
 
-    b1 = se.load(os.path.join(bo_dir,f'{c}_1_largest_abs.bo'))
-    b2 = se.load(os.path.join(bo_dir,f'{c}_2_largest_abs.bo'))
-    b3 = se.load(os.path.join(bo_dir,f'{c}_3_largest_abs.bo'))
-    b4 = se.load(os.path.join(bo_dir,f'{c}_4_largest_abs.bo'))
-    b5 = se.load(os.path.join(bo_dir, f'{c}_5_largest_abs.bo'))
-    b6 = se.load(os.path.join(bo_dir, f'{c}_6_largest_abs.bo'))
-    b7 = se.load(os.path.join(bo_dir, f'{c}_7_largest_abs.bo'))
-    b8 = se.load(os.path.join(bo_dir, f'{c}_8_largest_abs.bo'))
-    b9 = se.load(os.path.join(bo_dir, f'{c}_9_largest_abs.bo'))
-    b10 = se.load(os.path.join(bo_dir, f'{c}_10_largest_abs.bo'))
-    b11 = se.load(os.path.join(bo_dir, f'{c}_11_largest_abs.bo'))
-    b12 = se.load(os.path.join(bo_dir, f'{c}_12_largest_abs.bo'))
-    b13 = se.load(os.path.join(bo_dir, f'{c}_13_largest_abs.bo'))
-    b14 = se.load(os.path.join(bo_dir, f'{c}_14_largest_abs.bo'))
[…]

### 2021-07-12 paper/main.tex
updates to figure legends

@@
   \includegraphics[width=\textwidth]{figs/patterns}
-  \caption{\textbf{Neural patterns.  a. A space of neural features.}
+  \caption{Neural patterns.  a. A space of neural features.
     Within-brain analyses are carried out within a single brain,
@@
     may be static (e.g., averaging over time) or dynamic.
-    \textbf{b. Summarizing neural patterns.}  To efficiently compute
+   b. Summarizing neural patterns.  To efficiently compute
     with complex neural patterns, it can be useful to characterize the
@@
   \includegraphics[width=\textwidth]{figs/synthetic_data}
-  \caption{\textbf{Recovering known dynamic first-order correlations
-      from synthetic data.}  Each panel displays the average
+  \caption{Recovering known dynamic first-order correlations
+      from synthetic data.  Each panel displays the average
     correlations between the vectorized upper triangles of the
@@
     see Synthetic data: simulating dynamic first-order
-      correlations.  \textbf{a. Constant correlations.}  These
+      correlations.  a. Constant correlations.  These
     datasets have a stable (unchanging) underlying correlation matrix.
-    \textbf{b. Random correlations.}  These datasets are generated
+    b. Random correlations.  These datasets are generated
     using a new independently drawn correlation matrix at each new
-    timepoint.  \textbf{c. Ramping correlations.}  These datasets are
+    timepoint. c. Ramping correlations.  These datasets are
     generated by smoothly varying the underlying correlations between
@@
     the last timepoint's correlation matrix.
-    \textbf{d. Event-based correlations.}  These datasets are each
+    d. Event-based correlations.  These datasets are each
     generated using five randomly drawn correlation matrices that each
@@
     correlation matrices unique to each event.  The vertical lines
-    denote event boundaries.}
+    denote event boundaries. Source data are provided as a Source Data file.}
   \label{fig:synthetic}
@@
   \includegraphics[width=\textwidth]{figs/higher_order_sims}
-  \caption{\textbf{Recovery of simulated first-order and second-order dynamic correlations.}  Each panel displays the average correlations
+  \caption{Recovery of simulated first-order and second-order dynamic correlations.  Each panel displays the average correlations
     between the vectorized upper triangles of the recovered
@@
     computed using a Laplace kernel
-    (width~$=20$).  \textbf{Constant.}  These datasets
+    (width~$=20$).  Constant.  These datasets
     have stable (unchanging) underlying second-order correlation
-    matrices.  \textbf{Random.} These datasets are
+    matrices.  Random. These datasets are
     generated using a new independently drawn second-order correlation
-    matrix at each timepoint.  \textbf{Ramping.}
+    matrix at each timepoint. Ramping.
     These datasets are generated by smoothly varying the underlying
     second-order correlations between the randomly drawn correlation
-    matrices at the first and last timepoints.  \textbf{Event.}  These datasets are each generated using five
+    matrices at the first and last timepoints. Event.  These datasets are each generated using five
     randomly drawn second-order correlation matrices that each remain
@@
   \includegraphics[width=\textwidth]{figs/decode_level}
-  \caption{\textbf{Across-participant timepoint decoding accuracy varies with
-      correlation order and cognitive engagement.}
-    \textbf{a.~Decoding accuracy as a function of order: PCA.}
+  \caption{Across-participant timepoint decoding accuracy varies with
+      correlation order and cognitive engagement.
+    a.~Decoding accuracy as a function of order: PCA.
     Order ($x$-axis) refers to the maximum order of dynamic
@@
     the maximum decoding accuracy within each experimental condition.
-    \textbf{b.~Normalized timepoint decoding accuracy as a function of order:
-      PCA.}  This panel displays the same results as Panel a, but here
+    b.~Normalized timepoint decoding accuracy as a function of order:
+      PCA.  This panel displays the same results as Panel a, but here
     each curve has been normalized to have a maximum value of 1 and a
@@
     project each high-dimensional pattern of dynamic correlations onto
-    a lower-dimensional space.  \textbf{c.~Timepoint decoding accuracy as a
-      function of order: eigenvector centrality.} This panel is in the
+    a lower-dimensional space. c.~Timepoint decoding accuracy as a
+      function of order: eigenvector centrality. This panel is in the
     same format as Panel a, but here eigenvector centrality has been
@@
     correlations onto a lower-dimensional space.
-    \textbf{d.~Normalized timepoint decoding accuracy as a function of order:
-      eigenvector centrality.} This panel is in the same format as
+   d.~Normalized timepoint decoding accuracy as a function of order:
+      eigenvector centrality. This panel is in the same format as
     Panel b, but here eigenvector centrality has been used to project
@@
 \includegraphics[width=1\textwidth]{figs/stats_heatmaps}
-\caption{\textbf{Statistical summary of decoding accuracies for
-    different neural features.}  Each column of matrices displays decoding
+\caption{Statistical summary of decoding accuracies for
+    different neural features.  Each column of matrices displays decoding
   results for one experimental condition (intact, paragraph, word, and
@@
   \includegraphics[width=\textwidth]{figs/most_abs}
-  \caption{\textbf{Top terms associated with the most strongly
-      correlated nodes at each order.}  Each color corresponds to one order of
+  \caption{Top terms associated with the most strongly
+      correlated nodes at each order.  Each color corresponds to one order of
     inter-subject functional correlations.  To calculate the dynamic
@@
   \includegraphics[width=0.6\textwidth]{figs/discussion}
-  \caption{\textbf{Proposed high-order network dynamics underlying
-      high-level cognition during story listening.}  Schematic depicts
+  \caption{Proposed high-order network dynamics underlying
+      high-level cognition during story listening.  Schematic depicts
     higher orders of
@@
   \includegraphics[width=0.5\textwidth]{figs/methods_fig}
-  \caption{\textbf{Estimating dynamic high-order correlations.}  Given
+  \caption{Estimating dynamic high-order correlations.  Given
     a $T$ by $K$ matrix of multivariate timeseries data,
@@
   \includegraphics[width=\textwidth]{figs/kernels}
-  \caption{\textbf{Examples of kernel functions.} Each panel displays
+  \caption{Examples of kernel functions. Each panel displays
     per-timepoint weights for a kernel centered at $t = 50$, evaluated
     at 100 timepoints ($\tau \in \left[1, ..., 100\right]$).
-    \textbf{a. Uniform kernel.} The weights are timepoint-invariant;
+    a. Uniform kernel. The weights are timepoint-invariant;
     observations at all timepoints are weighted equally, and do not
@@
     function that reduces dynamic correlations to static correlations.
-    \textbf{b. Dirac $\delta$ kernel.} Only the observation at
+   b. Dirac $\delta$ kernel. Only the observation at
     timepoint $t$ is given a non-zero weight (of 1).
-    \textbf{c. Gaussian kernels.} Each kernel's weights fall off in
+    c. Gaussian kernels. Each kernel's weights fall off in
     time according to a Gaussian probability density function centered
     on time $t$.  Weights derived using several different example
-    width parameters ($\sigma^2$) are displayed.  \textbf{d. Laplace
-      kernels.}  Each kernel's weights fall off in time according to a
+    width parameters ($\sigma^2$) are displayed.  d. Laplace
+      kernels.  Each kernel's weights fall off in time according to a
     Laplace probability density function centered on time $t$.
     Weights derived using several different example width parameters
-    ($b$) are displayed.  \textbf{e. Mexican hat (Ricker wavelet)
-      kernels.}  Each kernel's weights fall off in time according to a
+    ($b$) are displayed.  e. Mexican hat (Ricker wavelet)
+      kernels.  Each kernel's weights fall off in time according to a
     Ricker wavelet centered on time $t$.  This function highlights the
@@
   \includegraphics[width=0.85\textwidth]{figs/timecorr_pipeline}
-  \caption{\textbf{Decoding analysis pipeline.  a. Computing dynamic
-      correlations from timeseries data.}  Given a timeseries of
+  \caption{Decoding analysis pipeline.  a. Computing dynamic
+      correlations from timeseries data.  Given a timeseries of
     observations as a $T \times K$ matrix (or a set of $S$ such
@@
     Gaussian in the upper row of the panel), and once using a $\delta$
-    function kernel (lower row of the panel).    \textbf{b. Projecting
-      dynamic correlations into a lower-dimensional space.}  We
+    function kernel (lower row of the panel).   b. Projecting
+      dynamic correlations into a lower-dimensional space.  We
     project the training and test data into $K$-dimensional spaces to
@@
     given order (estimated using the analysis kernel).
-    \textbf{c. Kernel trick.} We project the dynamic correlations
+    c. Kernel trick. We project the dynamic correlations
     computed using a $\delta$ function kernel into a common
@@
     back through the analysis pipeline in order to compute features at
-    the next-highest order.  \textbf{d. Decoding analysis.} We split
+    the next-highest order.  d. Decoding analysis. We split
     the training data into two equal groups, and optimize the feature
@@
 
+\section*{Code Availability}
+
+All of our analysis code may be downloaded from\href{https://github.com/ContextLab/timecorr-paper/releases/tag/v0.3}{github.com/ContextLab/timecorr-paper/releases/tag/v0.3}.
+
 \section*{Acknowledgements}

### 2021-07-12 paper/supplementary_materials.tex
updates to figure legends

@@
     A total of 10 synthetic datasets were generated for each number of features
-    (row) and timeseries pattern (panel).}
+    (row) and timeseries pattern (panel). Source data are provided as a Source Data file.}
 \label{fig:features}
@@
 corresponding brain maps for each order.  (Also see Fig.~\neurosynth,
-top row, in the main text.)}
+top row, in the main text.) Source data are provided as a Source Data file.}
 \label{fig:intact}
@@
   paragraph-scrambled story listening condition.  (Also see Fig.~\neurosynth,
-second row, in the main text.)}
+second row, in the main text.) Source data are provided as a Source Data file.}
 \label{fig:paragraph}
@@
   word-scrambled story listening condition.  (Also see Fig.~\neurosynth,
-third row, in the main text.)}
+third row, in the main text.) Source data are provided as a Source Data file.}
 \label{fig:word}
@@
   resting state condition.  (Also see Fig.~\neurosynth,
-bottom row, in the main text.)}
+bottom row, in the main text.) Source data are provided as a Source Data file.}
 \label{fig:rest}
@@
     used to project the high-dimensional patterns of dynamic
-    correlations onto a lower-dimensional space. }
+    correlations onto a lower-dimensional space. Source data are provided as a Source Data file.}
 \label{fig:pca}

### 2021-07-12 paper/supplementary_materials.tex
updated text with reported pvalues

@@
     word: $\frac{1}{300}$; rest: $\frac{1}{400}$).  The error ribbons
-    denote 95\% confidence intervals across cross-validation folds
+    denote 95\% confidence intervals of the mean across cross-validation folds
     (i.e., random assignments of participants to the training and test
@@
     of all other features (via a two-tailed $t$-test, thresholded at
-    $p < 0.05$).  The circled values represent
+    $p < 0.05$, exact values are reported in the Source Data file).  The circled values represent
     the maximum decoding accuracy within each experimental
@@
     used to project the high-dimensional patterns of dynamic
-    correlations into lower-dimensional spaces.}
+    correlations into lower-dimensional spaces. Source data are provided as a Source Data file.}
 \label{fig:supp_kernels}
@@
     of all other features (via a two-tailed $t$-test, thresholded at
-    $p < 0.05$).  The circled values represent
+    $p < 0.05$, exact values are reported in the Source Data file).  The circled values represent
     the maximum decoding accuracy within each experimental condition.  Panels a.-d. used PCA to
@@
     used to project the high-dimensional patterns of dynamic
-    correlations into lower-dimensional spaces.}
+    correlations into lower-dimensional spaces.  Source data are provided as a Source Data file.}
 \label{fig:supp_widths}
@@
     A total of 10 synthetic datasets were generated for each duration
-    (row) and timeseries pattern (panel).}
+    (row) and timeseries pattern (panel).  Source data are provided as a Source Data file.}
 \label{fig:time}

### 2021-08-02 paper/main.tex
final edits for paper

@@
     randomly generated synthetic datasets of the given category.)
-    Error ribbons denote 95\% confidence intervals (taken across
+    Error ribbons denote 95\% confidence intervals of the mean (taken across
     datasets). Different colors denote different kernel shapes, and
@@
     randomly generated synthetic datasets of the given category.)
-    Error ribbons denote 95\% confidence intervals (taken across
+    Error ribbons denote 95\% confidence intervals of the mean (taken across
     datasets).  For a complete description of each synthetic dataset,
@@
     that may be used to accurately estimate correlations at sharp
-    boundaries.}
+    boundaries. Source data are provided as a Source Data file.}
   \label{fig:higher_order_sims}
@@
     relative accuracies reported on the $y$-axis).  The error ribbons
-    denote 95\% confidence intervals across cross-validation folds
+    denote 95\% confidence intervals of the means across cross-validation folds
     (i.e., random assignments of participants to the training and test
@@
     minimum value of 0 (including the upper and lower bounds of the
-    respective 95\% confidence intervals).  Panels a and b used PCA to
+    respective 95\% confidence intervals of the mean).  Panels a and b used PCA to
     project each high-dimensional pattern of dynamic correlations onto
@@
     the high-dimensional patterns of dynamic correlations onto a
-    lower-dimensional space. See Figures~\kernelshape~and~\kernelwidth~for decoding results broken down by kernel shape and width, respectively.}
+    lower-dimensional space. See
+    Figures~\kernelshape~and~\kernelwidth~for decoding results broken
+    down by kernel shape and width, respectively. Source data are provided as a Source Data file.}
   \label{fig:decoding}
@@
   a decoder that included all feature types (see Feature
-    weighting and testing).}
+    weighting and testing). Source data are provided as a Source Data file.}
 \label{fig:ttests}
@@
       materials (intact: Fig.~\intact; paragraph: Fig.~\para; word:
-    Fig.~\word; rest: Fig.~\rest).}
+    Fig.~\word; rest: Fig.~\rest). Source data are provided as a Source Data file.}
   \label{fig:neurosynth}

### 2021-08-02 paper/main.tex
Update main.tex

@@
 A central goal in cognitive neuroscience is to elucidate the
-neural code: the mapping between (a) mental states or
+neural code: i.e., the mapping between (a) mental states or
 cognitive representations and (b) neural activity patterns. One means

### 2021-08-02 paper/main.tex
added bold in figure formatting

--- 2021-08-02 paper/main.tex
@@
   \includegraphics[width=\textwidth]{figs/patterns}
-  \caption{Neural patterns.  a. A space of neural features.
+  \caption{\textbf{Neural patterns. a. A space of neural features.}
     Within-brain analyses are carried out within a single brain,
@@
     may be static (e.g., averaging over time) or dynamic.
-   b. Summarizing neural patterns.  To efficiently compute
+  \textbf{b. Summarizing neural patterns.} To efficiently compute
     with complex neural patterns, it can be useful to characterize the
@@
   \includegraphics[width=\textwidth]{figs/synthetic_data}
-  \caption{Recovering known dynamic first-order correlations
-      from synthetic data.  Each panel displays the average
+  \caption{\textbf{Recovering known dynamic first-order correlations
+       from synthetic data.} Each panel displays the average
     correlations between the vectorized upper triangles of the
@@
     see Synthetic data: simulating dynamic first-order
-      correlations.  a. Constant correlations.  These
+      correlations. \textbf{a. Constant correlations.}  These
     datasets have a stable (unchanging) underlying correlation matrix.
-    b. Random correlations.  These datasets are generated
+  \textbf{b. Random correlations.}  These datasets are generated
     using a new independently drawn correlation matrix at each new
-    timepoint. c. Ramping correlations.  These datasets are
+    timepoint. \textbf{c. Ramping correlations.} These datasets are
     generated by smoothly varying the underlying correlations between
@@
     the last timepoint's correlation matrix.
-    d. Event-based correlations.  These datasets are each
+  \textbf{d. Event-based correlations.} These datasets are each
     generated using five randomly drawn correlation matrices that each
@@
   \includegraphics[width=\textwidth]{figs/higher_order_sims}
-  \caption{Recovery of simulated first-order and second-order dynamic correlations.  Each panel displays the average correlations
+  \caption{\textbf{Recovery of simulated first-order and second-order dynamic correlations.} Each panel displays the average correlations
     between the vectorized upper triangles of the recovered
@@
     computed using a Laplace kernel
-    (width~$=20$).  Constant.  These datasets
+    (width~$=20$).  \textbf{Constant.} These datasets
     have stable (unchanging) underlying second-order correlation
-    matrices.  Random. These datasets are
+    matrices. \textbf{Random.} These datasets are
     generated using a new independently drawn second-order correlation
-    matrix at each timepoint. Ramping.
+    matrix at each timepoint. \textbf{Ramping.}
     These datasets are generated by smoothly varying the underlying
     second-order correlations between the randomly drawn correlation
-    matrices at the first and last timepoints. Event.  These datasets are each generated using five
+    matrices at the first and last timepoints. \textbf{Event.}  These datasets are each generated using five
     randomly drawn second-order correlation matrices that each remain
@@
   \includegraphics[width=\textwidth]{figs/decode_level}
-  \caption{Across-participant timepoint decoding accuracy varies with
-      correlation order and cognitive engagement.
-    a.~Decoding accuracy as a function of order: PCA.
+  \caption{\textbf{Across-participant timepoint decoding accuracy varies with
+       correlation order and cognitive engagement.}
+     \textbf{a.~Decoding accuracy as a function of order: PCA.}
     Order ($x$-axis) refers to the maximum order of dynamic
@@
     the maximum decoding accuracy within each experimental condition.
-    b.~Normalized timepoint decoding accuracy as a function of order:
-      PCA.  This panel displays the same results as Panel a, but here
+  \textbf{b.~Normalized timepoint decoding accuracy as a function of order:
+       PCA.}  This panel displays the same results as Panel a, but here
     each curve has been normalized to have a maximum value of 1 and a
@@
     project each high-dimensional pattern of dynamic correlations onto
-    a lower-dimensional space. c.~Timepoint decoding accuracy as a
-      function of order: eigenvector centrality. This panel is in the
+    a lower-dimensional space. \textbf{c.~Timepoint decoding accuracy as a
+       function of order: eigenvector centrality.} This panel is in the
     same format as Panel a, but here eigenvector centrality has been
@@
     correlations onto a lower-dimensional space.
-   d.~Normalized timepoint decoding accuracy as a function of order:
-      eigenvector centrality. This panel is in the same format as
+ \textbf{d.~Normalized timepoint decoding accuracy as a function of order:
+       eigenvector centrality.}  This panel is in the same format as
     Panel b, but here eigenvector centrality has been used to project
@@
 \includegraphics[width=1\textwidth]{figs/stats_heatmaps}
-\caption{Statistical summary of decoding accuracies for
-    different neural features.  Each column of matrices displays decoding
+\caption{\textbf{Statistical summary of decoding accuracies for
+     different neural features.}  Each column of matrices displays decoding
   results for one experimental condition (intact, paragraph, word, and
@@
   \includegraphics[width=\textwidth]{figs/most_abs}
-  \caption{Top terms associated with the most strongly
-      correlated nodes at each order.  Each color corresponds to one order of
+  \caption{\textbf{Top terms associated with the most strongly
+       correlated nodes at each order.}  Each color corresponds to one order of
     inter-subject functional correlations.  To calculate the dynamic
@@
   \includegraphics[width=0.6\textwidth]{figs/discussion}
-  \caption{Proposed high-order network dynamics underlying
-      high-level cognition during story listening.  Schematic depicts
+  \caption{\textbf{Proposed high-order network dynamics underlying
+       high-level cognition during story listening.}  Schematic depicts
     higher orders of
@@
   \includegraphics[width=0.5\textwidth]{figs/methods_fig}
-  \caption{Estimating dynamic high-order correlations.  Given
+  \caption{\textbf{Estimating dynamic high-order correlations.}  Given
     a $T$ by $K$ matrix of multivariate timeseries data,
@@
   \includegraphics[width=\textwidth]{figs/kernels}
-  \caption{Examples of kernel functions. Each panel displays
+  \caption{\textbf{Examples of kernel functions.} Each panel displays
     per-timepoint weights for a kernel centered at $t = 50$, evaluated
     at 100 timepoints ($\tau \in \left[1, ..., 100\right]$).
-    a. Uniform kernel. The weights are timepoint-invariant;
+   \textbf{a. Uniform kernel.} The weights are timepoint-invariant;
     observations at all timepoints are weighted equally, and do not
@@
     function that reduces dynamic correlations to static correlations.
-   b. Dirac $\delta$ kernel. Only the observation at
+   \textbf{b. Dirac $\delta$ kernel.} Only the observation at
     timepoint $t$ is given a non-zero weight (of 1).
-    c. Gaussian kernels. Each kernel's weights fall off in
+   \textbf{c. Gaussian kernels.} Each kernel's weights fall off in
     time according to a Gaussian probability density function centered
     on time $t$.  Weights derived using several different example
-    width parameters ($\sigma^2$) are displayed.  d. Laplace
-      kernels.  Each kernel's weights fall off in time according to a
+    width parameters ($\sigma^2$) are displayed.  \textbf{d. Laplace
+       kernels.}  Each kernel's weights fall off in time according to a
     Laplace probability density function centered on time $t$.
     Weights derived using several different example width parameters
-    ($b$) are displayed.  e. Mexican hat (Ricker wavelet)
-      kernels.  Each kernel's weights fall off in time according to a
+    ($b$) are displayed.  \textbf{e. Mexican hat (Ricker wavelet)
+       kernels.}  Each kernel's weights fall off in time according to a
     Ricker wavelet centered on time $t$.  This function highlights the
@@
   \includegraphics[width=0.85\textwidth]{figs/timecorr_pipeline}
-  \caption{Decoding analysis pipeline.  a. Computing dynamic
-      correlations from timeseries data.  Given a timeseries of
+  \caption{\textbf{Decoding analysis pipeline.  a. Computing dynamic
+       correlations from timeseries data.}  Given a timeseries of
     observations as a $T \times K$ matrix (or a set of $S$ such
@@
     Gaussian in the upper row of the panel), and once using a $\delta$
-    function kernel (lower row of the panel).   b. Projecting
-      dynamic correlations into a lower-dimensional space.  We
+    function kernel (lower row of the panel).    \textbf{b. Projecting
+       dynamic correlations into a lower-dimensional space.}  We
     project the training and test data into $K$-dimensional spaces to
@@
     given order (estimated using the analysis kernel).
-    c. Kernel trick. We project the dynamic correlations
+   \textbf{c. Kernel trick.}  We project the dynamic correlations
     computed using a $\delta$ function kernel into a common
@@
     back through the analysis pipeline in order to compute features at
-    the next-highest order.  d. Decoding analysis. We split
+    the next-highest order. \textbf{d. Decoding analysis.}  We split
     the training data into two equal groups, and optimize the feature

### 2021-08-02 paper/main.tex
WIP PR comments

@@
 
-\subsection*{Recovering dynamic first-order correlations}
+\subsection*{Recovering known dynamic first-order correlations}
 We generated synthetic datasets that differed in how the underlying first-order
@@
     correlation matrix.  (The averages are taken across 100 different
-    randomly generated synthetic datasets of the given category.)
+    randomly generated synthetic datasets of the given category, each
+    with $K = 50$ features and $T = 300$ timepoints.)
     Error ribbons denote 95\% confidence intervals of the mean (taken across
@@
 
-\subsection*{Recovering dynamic higher-order correlations}
+\subsection*{Recovering known dynamic higher-order correlations}
 Following our approach to evaluating our ability to recover known
@@
 unstable (random datasets), we better recovered second-order
-correlations.  This is because noises in our data generation
+correlations.  This is because noise in our data generation
 procedure propagates from higher orders to lower orders (see
@@
     timepoint and for each synthetic dataset.  (The averages are taken across 100 different
-    randomly generated synthetic datasets of the given category.)
+    randomly generated synthetic datasets of the given category, each
+    with $K = 10$ features and $T = 300$ timepoints.)
     Error ribbons denote 95\% confidence intervals of the mean (taken across
@@
 participants to stimuli that varied systematically in how cognitively
-engaging they were.  The intact experimental condition had
+engaging they were.  The intact experimental condition (intact) had
 participants listen to an audio recording of a 10-minute story.  The
-paragraph-scrambled experimental condition had participants
+paragraph-scrambled experimental condition (paragraph) had participants
 listen to a temporally scrambled version of the story, where the
@@
 participants in this condition experienced the scrambled paragraphs in
-the same order.  The word-scrambled experimental condition
+the same order.  The word-scrambled experimental condition (word)
 had participants listen to a temporally scrambled version of the story
@@
 participants in the word condition experienced the scrambled words in
-the same order.  Finally, in a rest experimental condition,
+the same order.  Finally, in a rest experimental condition (rest),
 participants lay in the scanner with no overt stimulus, with their
@@
      \textbf{a.~Decoding accuracy as a function of order: PCA.}
-    Order ($x$-axis) refers to the maximum order of dynamic
+   ``Order'' ($x$-axis) refers to the maximum order of dynamic
     correlations that were available to the classifiers (see
@@
     Gaussian in the upper row of the panel), and once using a $\delta$
-    function kernel (lower row of the panel).  \textbf{b. Projecting
+    function kernel (lower row of the panel).
+    \textbf{b. Projecting
        dynamic correlations into a lower-dimensional space.}  We

### 2021-08-02 paper/main.tex
PR updates

@@
   datasets whose underlying correlations changed gradually over time.
-  For each dataset, we constructed two anchor covariance
+  For each dataset, we constructed two``anchor'' covariance
   matrices using Equation~\ref{eqn:randcorr},
@@
 $\mathcal{N}\left(0, m_n\right)$ and reshaping the resulting vector to
-have square dimensions.  Intuitively, the re-shaped matrix will look
-like a noisy version of the template matrix, $m_{n-1}$.  (When
+have square dimensions.  To force the resulting matrix to be
+symmetric, we remove its lower triangle, and replace the lower
+triangle with (a reflected version
+of) its upper triangle. Intuitively, the re-shaped matrix will look
+like a noisy (but symmetric) version of the template matrix, $m_{n-1}$.  (When
 $n = 1$, no re-shaping is needed; the resulting $K$-dimensional vector
@@
 reflecting each type of dynamic pattern: constant, random, ramping,
-and event).  Each timeseries comprised 10 features (dimensions)
-that varied over 300 timepoints for first-order correlations, and
-therefore 100 second-order features.
+and event).   Each timeseries comprised 10 zero-order features (dimensions)
+that varied over 300 timepoints.  After applying our dynamic
+correlation estimation procedure, this yielded a 100-dimensional
+timeseries of first-order
+features that could then be used to estimate dynamic second-order
+correlations.  (We chose to use $K=10$ zero-order features for our
+higher order simulations in order to put the accuracy computations
+displayed in Figs.~\ref{fig:synthetic} and~\ref{fig:higher_order_sims}
+on a roughly even footing.)
 
@@
 participants).  Full neuroimaging details may be found in the original
-paper for which the data were collected~\citep{SimoEtal16}.
-Procedures were approved by the Princeton University Committee on Activities Involving Human Subjects, and by Western Institutional Review Board (Puyallup, WA).
-All subjects were native English speakers with normal hearing and provided written informed consent.
+paper for which the data were collected~\citep{SimoEtal16}. Procedures
+were approved by the Princeton University Committee on Activities
+Involving Human Subjects, and by the Western Institutional Review Board (Puyallup, WA). All subjects were native English speakers with normal hearing and provided written informed consent.
 
@@
 
-All of our analysis code may be downloaded from\href{https://github.com/ContextLab/timecorr-paper/releases/tag/v0.3}{github.com/ContextLab/timecorr-paper/releases/tag/v0.3}.
+All of our analysis code may be downloaded from \href{https://github.com/ContextLab/timecorr-paper/releases/tag/v0.3}{github.com/ContextLab/timecorr-paper/releases/tag/v0.3}.
 

### 2021-08-02 paper/supplementary_materials.tex
PR updates

@@
       correlation order and cognitive engagement across kernels.}
-    \textbf{a.-c.~Timepoint decoding accuracy as a function of order: PCA.} Order ($x$-axis) refers to the maximum order of dynamic
+    \textbf{a.-c.~Timepoint decoding accuracy as a function of order:
+      PCA.} \textit{Order} ($x$-axis) refers to the maximum order of dynamic
     correlations that were available to the classifiers (see
-    Feature weighting and testing).  The reported
+    \textit{Feature weighting and testing}).  The reported
     across-participant decoding accuracies for \textbf{a. Gaussian},
     \textbf{b. Laplace}, and \textbf{c. Mexican hat} kernel shapes are averaged over all
-   widths (see Identifying robust decoding
-      results).  The $y$-values are displayed relative to chance
+   widths (see \textit{Identifying robust decoding
+      results}).  The $y$-values are displayed relative to chance
     accuracy (intact: $\frac{1}{300}$; paragraph: $\frac{1}{272}$;
@@
     of all other features (via a two-tailed $t$-test, thresholded at
-    $p < 0.05$, exact values are reported in the Source Data file).  The circled values represent
+    $p < 0.05$; exact values are reported in the Source Data file).  The circled values represent
     the maximum decoding accuracy within each experimental
@@
       correlation order and cognitive engagement across widths.}
-    \textbf{a.-d.~Timepoint decoding accuracy as a function of order: PCA.} Order ($x$-axis) refers to the maximum order of dynamic
+    \textbf{a.-d.~Timepoint decoding accuracy as a function of order:
+      PCA.} \textit{Order} ($x$-axis) refers to the maximum order of dynamic
     correlations that were available to the classifiers (see
@@
     of all other features (via a two-tailed $t$-test, thresholded at
-    $p < 0.05$, exact values are reported in the Source Data file).  The circled values represent
+    $p < 0.05$; exact values are reported in the Source Data file).  The circled values represent
     the maximum decoding accuracy within each experimental condition.  Panels a.-d. used PCA to
@@
     synthetic datasets for each timeseries pattern (constant, random,
-    ramping, and data; see Synthetic data: simulating dynamic higher-order
-      correlations).  The $x$-axes of each heatmap denote varying
+    ramping, and data; see \textit{Synthetic data: simulating dynamic higher-order
+      correlations}).  The $x$-axes of each heatmap denote varying
     Laplace-shaped kernel widths (see Figs.~\ref{fig:supp_kernels}
@@
 \caption{\textbf{Top terms associated with the most strongly
-      correlated nodes at each order, for the intact experimental
+      correlated nodes at each order, for the \textit{intact} experimental
     condition.}  Each color corresponds to one order of inter-subject
@@
 \caption{\textbf{Top terms associated with the most strongly
-      correlated nodes at each order, for the paragraph experimental
+      correlated nodes at each order, for the \textit{paragraph} experimental
     condition.}  This figure is in the same format as
@@
 \caption{\textbf{Top terms associated with the most strongly
-      correlated nodes at each order, for the word experimental
+      correlated nodes at each order, for the \textit{word} experimental
     condition.}  This figure is in the same format as
@@
 \caption{\textbf{Top terms associated with the most strongly
-      correlated nodes at each order, for the rest experimental
+      correlated nodes at each order, for the \textit{rest} experimental
     condition.}  This figure is in the same format as
@@
 \caption{\textbf{Cumulative percent variance explained as a function
-    of the number of principle components.}  Order refers to the order of the dynamic
+    of the number of principle components.}  \textit{Order} refers to the order of the dynamic
     correlations calculated. Principle components analysis was

### 2021-08-02 paper/main.tex
updates from PR

@@
     correlation matrix.  (The averages are taken across 100 different
-    randomly generated synthetic datasets of the given category, each
+    randomly generated synthetic datasets of each given category, each
     with $K = 50$ features and $T = 300$ timepoints.)
@@
     timepoint and for each synthetic dataset.  (The averages are taken across 100 different
-    randomly generated synthetic datasets of the given category, each
+    randomly generated synthetic datasets of each given category, each
     with $K = 10$ features and $T = 300$ timepoints.)
@@
   datasets whose underlying correlations changed gradually over time.
-  For each dataset, we constructed two``anchor'' covariance
+  For each dataset, we constructed two ``anchor'' covariance
   matrices using Equation~\ref{eqn:randcorr},
@@
 
-All of our analysis code may be downloaded from \href{https://github.com/ContextLab/timecorr-paper/releases/tag/v0.3}{github.com/ContextLab/timecorr-paper/releases/tag/v0.3}.
+All of our analysis code may be downloaded from
+\href{https://github.com/ContextLab/timecorr-paper/releases/tag/v0.3}{github.com/ContextLab/timecorr-paper/releases/tag/v0.3}.
+We have also published a companion Python toolbox that may be downloaded from \href{https://timecorr.readthedocs.io}{timecorr.readthedocs.io}.
 

### 2021-08-02 paper/supplementary_materials.tex
updates from PR

@@
     correlations that were available to the classifiers (see
-    Feature weighting and testing).  The reported
+   \textit{Feature weighting and testing}).  The reported
     across-participant decoding accuracies for kernel widths of \textbf{a. 5},

### 2021-08-02 paper/main.tex
added bibliography to end of text

@@
 \bibliographystyle{naturemag}
-\bibliography{CDL-bibliography/cdl}
+%\bibliography{CDL-bibliography/cdl}
+
+\begin{thebibliography}{10}
+\expandafter\ifx\csname url\endcsname\relax
+  \def\url#1{\texttt{#1}}\fi
+\expandafter\ifx\csname urlprefix\endcsname\relax\def\urlprefix{URL }\fi
+\providecommand{\bibinfo}[2]{#2}
+\providecommand{\eprint}[2][]{\url{#2}}
+
+\bibitem{HaxbEtal01}
+\bibinfo{author}{Haxby, J.~V.} \emph{et~al.}
+\newblock \bibinfo{title}{Distributed and overlapping representations of faces
+  and objects in ventral temporal cortex}.
+\newblock \emph{\bibinfo{journal}{Science}} \textbf{\bibinfo{volume}{293}},
+  \bibinfo{pages}{2425--2430} (\bibinfo{year}{2001}).
+
+\bibitem{NormEtal06b}
+\bibinfo{author}{Norman, K.~A.}, \bibinfo{author}{Polyn, S.~M.},
+  \bibinfo{author}{Detre, G.~J.} \& \bibinfo{author}{Haxby, J.~V.}
+\newblock \bibinfo{title}{Beyond mind-reading: multi-voxel pattern analysis of
+  {fMRI} data}.
+\newblock \emph{\bibinfo{journal}{Trends in Cognitive Sciences}}
+  \textbf{\bibinfo{volume}{10}}, \bibinfo{pages}{424--430}
+  (\bibinfo{year}{2006}).
+
+\bibitem{TongPrat12}
+\bibinfo{author}{Tong, F.} \& \bibinfo{author}{Pratte, M.~S.}
+\newblock \bibinfo{title}{Decoding patterns of human brain activity}.
+\newblock \emph{\bibinfo{journal}{Annual Review of Psychology}}
+  \textbf{\bibinfo{volume}{63}}, \bibinfo{pages}{483--509}
+  (\bibinfo{year}{2012}).
+
+\bibitem{MitcEtal08a}
+\bibinfo{author}{Mitchell, T.~M.} \emph{et~al.}
+\newblock \bibinfo{title}{Predicting human brain activity associated with the
+  meanings of nouns}.
+\newblock \emph{\bibinfo{journal}{Science}} \textbf{\bibinfo{volume}{320}},
+  \bibinfo{pages}{1191} (\bibinfo{year}{2008}).
+
+\bibitem{KamiTong05}
+\bibinfo{author}{Kamitani, Y.} \& \bibinfo{author}{Tong, F.}
+\newblock \bibinfo{title}{Decoding the visual and subjective contents of the
+  human brain}.
+\newblock \emph{\bibinfo{journal}{Nature Neuroscience}}
+  \textbf{\bibinfo{volume}{8}}, \bibinfo{pages}{679--685}
+  (\bibinfo{year}{2005}).
+
+\bibitem{NishEtal11}
+\bibinfo{author}{Nishimoto, S.} \emph{et~al.}
+\newblock \bibinfo{title}{Reconstructing visual experience from brain activity
+  evoked by natural movies}.
+\newblock \emph{\bibinfo{journal}{Current Biology}}
+  \textbf{\bibinfo{volume}{21}}, \bibinfo{pages}{1--6} (\bibinfo{year}{2011}).
+
+\bibitem{PereEtal18}
+\bibinfo{author}{Pereira, F.} \emph{et~al.}
+\newblock \bibinfo{title}{Toward a universal decoder of linguistic meaning from
+  brain activation}.
+\newblock \emph{\bibinfo{journal}{Nature Communications}}
+  \textbf{\bibinfo{volume}{9}}, \bibinfo{pages}{1--13} (\bibinfo{year}{2018}).
+
+\bibitem{HuthEtal12}
+\bibinfo{author}{Huth, A.~G.}, \bibinfo{author}{Nisimoto, S.},
+  \bibinfo{author}{Vu, A.~T.} \& \bibinfo{author}{Gallant, J.~L.}
+\newblock \bibinfo{title}{A continuous semantic space describes the
+  representation of thousands of object and action categories across the human
+  brain}.
+\newblock \emph{\bibinfo{journal}{Neuron}} \textbf{\bibinfo{volume}{76}},
+  \bibinfo{pages}{1210--1224} (\bibinfo{year}{2012}).
+
+\bibitem{HuthEtal16}
+\bibinfo{author}{Huth, A.~G.}, \bibinfo{author}{de~Heer, W.~A.},
+  \bibinfo{author}{Griffiths, T.~L.}, \bibinfo{author}{Theunissen, F.~E.} \&
+  \bibinfo{author}{Gallant, J.~L.}
+\newblock \bibinfo{title}{Natural speech reveals the semantic maps that tile
+  human cerebral cortex}.
+\newblock \emph{\bibinfo{journal}{Nature}} \textbf{\bibinfo{volume}{532}},
+  \bibinfo{pages}{453--458} (\bibinfo{year}{2016}).
+
+\bibitem{EtzeEtal09}
+\bibinfo{author}{Etzel, J.~A.}, \bibinfo{author}{Gazzola, V.} \&
+  \bibinfo{author}{Keysers, C.}
+\newblock \bibinfo{title}{An introduction to anatomical {ROI}-based {fMRI}
+  classification}.
+\newblock \emph{\bibinfo{journal}{Brain Research}}
+  \textbf{\bibinfo{volume}{1281}}, \bibinfo{pages}{114--125}
+  (\bibinfo{year}{2009}).
+
+\bibitem{MannEtal18}
+\bibinfo{author}{Manning, J.~R.} \emph{et~al.}
+\newblock \bibinfo{title}{A probabilistic approach to discovering dynamic
+  full-brain functional connectivity patterns}.
+\newblock \emph{\bibinfo{journal}{{NeuroImage}}}
+  \textbf{\bibinfo{volume}{180}}, \bibinfo{pages}{243--252}
+  (\bibinfo{year}{2018}).
+
+\bibitem{FongEtal19}
+\bibinfo{author}{Fong, A. H.~C.} \emph{et~al.}
+\newblock \bibinfo{title}{Dynamic functional connectivity during task
+  performance and rest predicts individual differences in attention across
+  studies}.
+\newblock \emph{\bibinfo{journal}{{NeuroImage}}}
+  \textbf{\bibinfo{volume}{188}}, \bibinfo{pages}{14--25}
+  (\bibinfo{year}{2019}).
+
+\bibitem{Gros88}
+\bibinfo{author}{Grossberg, S.}
+\newblock \bibinfo{title}{Nonlinear neural networks: principles, mechanisms,
+  and architectures}.
+\newblock \emph{\bibinfo{journal}{Neural Networks}}
+  \textbf{\bibinfo{volume}{1}}, \bibinfo{pages}{17--61} (\bibinfo{year}{1988}).
+
+\bibitem{Fris00}
+\bibinfo{author}{Friston, K.~J.}
+\newblock \bibinfo{title}{The labile brain. {I}. neuronal transients and
+  nonlinear coupling}.
+\newblock \emph{\bibinfo{journal}{Philosophical Transactions of the Royal
+  Society of London}} \textbf{\bibinfo{volume}{355B}},
+  \bibinfo{pages}{215--236} (\bibinfo{year}{2000}).
+
+\bibitem{SporHone06}
+\bibinfo{author}{Sporns, O.} \& \bibinfo{author}{Honey, C.~J.}
+\newblock \bibinfo{title}{Small worlds inside big brains}.
+\newblock \emph{\bibinfo{journal}{Proceedings of the National Academy of
+  Sciences, {USA}}} \textbf{\bibinfo{volume}{103}},
+  \bibinfo{pages}{19219--19220} (\bibinfo{year}{2006}).
+
+\bibitem{BassEtal06}
+\bibinfo{author}{Bassett, D.}, \bibinfo{author}{Meyer-Lindenberg, A.},
+  \bibinfo{author}{Achard, S.}, \bibinfo{author}{Duke, T.} \&
+  \bibinfo{author}{Bullmore, E.}
+\newblock \bibinfo{title}{Adaptive reconfiguration of fractal small-world human
+  brain functional networks}.
+\newblock \emph{\bibinfo{journal}{Proceedings of the National Academy of
+  Sciences, {USA}}} \textbf{\bibinfo{volume}{103}},
+  \bibinfo{pages}{19518--19523} (\bibinfo{year}{2006}).
+
+\bibitem{Turk13}
+\bibinfo{author}{Turk-Browne, N.~B.}
+\newblock \bibinfo{title}{Functional interactions as big data in the human
+  brain}.
+\newblock \emph{\bibinfo{journal}{Science}} \textbf{\bibinfo{volume}{342}},
+  \bibinfo{pages}{580--584} (\bibinfo{year}{2013}).
+
+\bibitem{DemeEtal19}
+\bibinfo{author}{Demertzi, A.} \emph{et~al.}
+\newblock \bibinfo{title}{Human consciousness is supported by dynamic complex
+  patterns of brain signal coordination}.
+\newblock \emph{\bibinfo{journal}{Science Advances}}
+  \textbf{\bibinfo{volume}{5}}, \bibinfo{pages}{eaat7603}
+  (\bibinfo{year}{2019}).
+
+\bibitem{SoloEtal19}
+\bibinfo{author}{Solomon, S.~H.}, \bibinfo{author}{Medaglia, J.~D.} \&
+  \bibinfo{author}{Thompson-Schill, S.~L.}
+\newblock \bibinfo{title}{Implementing a concept network model}.
+\newblock \emph{\bibinfo{journal}{Behavior Research Methods}}
+  \textbf{\bibinfo{volume}{51}}, \bibinfo{pages}{1717--1736}
+  (\bibinfo{year}{2019}).
+
+\bibitem{LuriEtal18}
+\bibinfo{author}{Lurie, D.} \emph{et~al.}
+\newblock \bibinfo{title}{On the nature of time-varying functional connectivity
+  in resting f{MRI}}.
+\newblock \emph{\bibinfo{journal}{{PsyArXiv}}}
+  \textbf{\bibinfo{volume}{doi.org/10.31234/osf.io/xtzre}}
+  (\bibinfo{year}{2018}).
+
+\bibitem{PretEtal17}
+\bibinfo{author}{Preti, M.~G.}, \bibinfo{author}{Bolton, T. A.~W.} \&
+  \bibinfo{author}{{Van De Ville}, D.}
+\newblock \bibinfo{title}{The dynamic functional connectome: state-of-the-art
+  and perspectives}.
+\newblock \emph{\bibinfo{journal}{{NeuroImage}}}
+  \textbf{\bibinfo{volume}{160}}, \bibinfo{pages}{41--54}
+  (\bibinfo{year}{2017}).
+
+\bibitem{ZouEtal19}
+\bibinfo{author}{Zou, Y.}, \bibinfo{author}{Donner, R.~V.},
+  \bibinfo{author}{Marwan, N.}, \bibinfo{author}{Donges, J.~F.} \&
+  \bibinfo{author}{Kurths, J.}
+\newblock \bibinfo{title}{Complex network approaches to nonlinear time series
+  analysis}.
+\newblock \emph{\bibinfo{journal}{Physics Reports}}
+  \textbf{\bibinfo{volume}{787}}, \bibinfo{pages}{1--97}
+  (\bibinfo{year}{2019}).
+
+\bibitem{MackEtal17}
+\bibinfo{author}{Mack, M.~L.}, \bibinfo{author}{Preston, A.~R.} \&
+  \bibinfo{author}{Love, B.~C.}
+\newblock \bibinfo{title}{Medial prefrontal cortex compresses concept
+  representations through learning}.
+\newblock \emph{\bibinfo{journal}{{bioRxiv}}}
+  \textbf{\bibinfo{volume}{doi.org/10.1101/178145}} (\bibinfo{year}{2017}).
+
+\bibitem{BresKels01}
+\bibinfo{author}{Bressler, S.~L.} \& \bibinfo{author}{Kelso, J. A.~S.}
+\newblock \bibinfo{title}{Cortical coordination dynamics and cognition}.
+\newblock \emph{\bibinfo{journal}{Trends in Cognitive Sciences}}
+  \textbf{\bibinfo{volume}{5}}, \bibinfo{pages}{26--36} (\bibinfo{year}{2001}).
+
+\bibitem{McIn00}
+\bibinfo{author}{McIntosh, A.~R.}
+\newblock \bibinfo{title}{Towards a network theory of cognition}.
+\newblock \emph{\bibinfo{journal}{Neural Networks}}
+  \textbf{\bibinfo{volume}{13}}, \bibinfo{pages}{861--870}
+  (\bibinfo{year}{2000}).
+
+\bibitem{ReimEtal17}
+\bibinfo{author}{Reimann, M.~W.} \emph{et~al.}
+\newblock \bibinfo{title}{Cliques of neurons bound into cavities provide a
+  missing link between structure and function}.
+\newblock \emph{\bibinfo{journal}{Frontiers in Computational Neuroscience}}
+  \textbf{\bibinfo{volume}{11}}, \bibinfo{pages}{1--16} (\bibinfo{year}{2017}).
+
+\bibitem{BeatEtal16}
+\bibinfo{author}{Beaty, R.~E.}, \bibinfo{author}{Benedek, M.},
+  \bibinfo{author}{Silvia, P.~J.} \& \bibinfo{author}{Schacter, D.~L.}
+\newblock \bibinfo{title}{Creative cognition and brain network dynamics}.
+\newblock \emph{\bibinfo{journal}{Trends in Cognitive Sciences}}
+  \textbf{\bibinfo{volume}{20}}, \bibinfo{pages}{87--95}
+  (\bibinfo{year}{2016}).
+
+\bibitem{BullSpor09}
+\bibinfo{author}{Bullmore, E.} \& \bibinfo{author}{Sporns, O.}
+\newblock \bibinfo{title}{Complex brain networks: graph theoretical analysis of
+  structural and functional systems}.
+\newblock \emph{\bibinfo{journal}{Nature Reviews Neuroscience}}
+  \textbf{\bibinfo{volume}{10}}, \bibinfo{pages}{186--198}
+  (\bibinfo{year}{2009}).
+
+\bibitem{Pear01}
+\bibinfo{author}{Pearson, K.}
+\newblock \bibinfo{title}{On lines and planes of closest fit to systems of
+  points in space}.
+\newblock \emph{\bibinfo{journal}{The London, Edinburgh, and Dublin
+  Philosophical Magazine and Journal of Science}} \textbf{\bibinfo{volume}{2}},
+  \bibinfo{pages}{559--572} (\bibinfo{year}{1901}).
+
+\bibitem{McInJirs19}
+\bibinfo{author}{Mc{I}ntosh, A.~R.} \& \bibinfo{author}{Jirsa, V.~K.}
+\newblock \bibinfo{title}{The hidden repertoire of brain dynamics and
+  dysfunction}.
+\newblock \emph{\bibinfo{journal}{Network Neuroscience}}
+  \textbf{\bibinfo{volume}{doi.org/10.1162/netn\_a\_00107}}
+  (\bibinfo{year}{2019}).
+
+\bibitem{TokeSomm19}
+\bibinfo{author}{Toker, D.} \& \bibinfo{author}{Sommer, F.~T.}
+\newblock \bibinfo{title}{Information integration in large brain networks}.
+\newblock \emph{\bibinfo{journal}{{PLoS} Computational Biology}}
+  \textbf{\bibinfo{volume}{15}}, \bibinfo{pages}{e1006807}
+  (\bibinfo{year}{2019}).
+
+\bibitem{GonzEtal19}
+\bibinfo{author}{Gonzalez-Castillo, J.} \emph{et~al.}
+\newblock \bibinfo{title}{Imaging the spontaneous flow of thought: distinct
+  periods of cognition contribute to dynamic functional connectivity during
+  test}.
+\newblock \emph{\bibinfo{journal}{{NeuroImage}}} \textbf{\bibinfo{volume}{202}}
+  (\bibinfo{year}{2019}).
+
+\bibitem{Land95}
+\bibinfo{author}{Landau, E.}
+\newblock \bibinfo{title}{Zur relativen {Wertbemessung} der
+  {Turnierresultate}}.
+\newblock \emph{\bibinfo{journal}{Deutsches Wochenschach}}
+  \textbf{\bibinfo{volume}{11}}, \bibinfo{pages}{366--369}
+  (\bibinfo{year}{1895}).
+
+\bibitem{BetzEtal19}
+\bibinfo{author}{Betzel, R.~F.}, \bibinfo{author}{Byrge, L.},
+  \bibinfo{author}{Esfahlani, F.~Z.} \& \bibinfo{author}{Kennedy, D.~P.}
+\newblock \bibinfo{title}{Temporal fluctuations in the brain's modular
+  architecture during movie-watching}.
+\newblock \emph{\bibinfo{journal}{{bioRxiv}}}
+  \textbf{\bibinfo{volume}{doi.org/10.1101/750919}} (\bibinfo{year}{2019}).
+
+\bibitem{SizeEtal18}
+\bibinfo{author}{Sizemore, A.~E.} \emph{et~al.}
+\newblock \bibinfo{title}{Cliques and cavities in the human connectome}.
+\newblock \emph{\bibinfo{journal}{Journal of Computational Neuroscience}}
+  \textbf{\bibinfo{volume}{44}}, \bibinfo{pages}{115--145}
+  (\bibinfo{year}{2018}).
+
+\bibitem{SimoEtal16}
+\bibinfo{author}{Simony, E.}, \bibinfo{author}{Honey, C.~J.},
+  \bibinfo{author}{Chen, J.} \& \bibinfo{author}{Hasson, U.}
+\newblock \bibinfo{title}{Dynamic reconfiguration of the default mode network
+  during narrative comprehension}.
+\newblock \emph{\bibinfo{journal}{Nature Communications}}
+  \textbf{\bibinfo{volume}{7}}, \bibinfo{pages}{1--13} (\bibinfo{year}{2016}).
+
+\bibitem{HassEtal08}
+\bibinfo{author}{Hasson, U.}, \bibinfo{author}{Yang, E.},
+  \bibinfo{author}{Vallines, I.}, \bibinfo{author}{Heeger, D.~J.} \&
+  \bibinfo{author}{Rubin, N.}
+\newblock \bibinfo{title}{A hierarchy of temporal receptive windows in human
+  cortex}.
+\newblock \emph{\bibinfo{journal}{The Journal of Neuroscience}}
+  \textbf{\bibinfo{volume}{28}}, \bibinfo{pages}{2539--2550}
+  (\bibinfo{year}{2008}).
+
+\bibitem{RubiEtal17}
+\bibinfo{author}{Rubin, T.~N.} \emph{et~al.}
+\newblock \bibinfo{title}{Decoding brain activity using a large-scale
+  probabilistic functional-anatomical atlas of human cognition}.
+\newblock \emph{\bibinfo{journal}{{PLoS} Computational Biology}}
+  \textbf{\bibinfo{volume}{13}}, \bibinfo{pages}{e1005649}
+  (\bibinfo{year}{2017}).
+
+\bibitem{ParkEtal18b}
+\bibinfo{author}{Park, H.-J.}, \bibinfo{author}{Friston, K.~J.},
+  \bibinfo{author}{Pae, C.}, \bibinfo{author}{Park, B.} \&
+  \bibinfo{author}{Razi, A.}
+\newblock \bibinfo{title}{Dynamic effective connectivity in resting state
+  {fMRI}}.
+\newblock \emph{\bibinfo{journal}{{NeuroImage}}}
+  \textbf{\bibinfo{volume}{180}}, \bibinfo{pages}{594--608}
+  (\bibinfo{year}{2018}).
+
+\bibitem{RoyEtal19}
+\bibinfo{author}{Roy, D.~S.} \emph{et~al.}
+\newblock \bibinfo{title}{Brain-wide mapping of contextual fear memory engram
+  ensembles supports the dispersed engram complex hypothesis}.
+\newblock \emph{\bibinfo{journal}{{bioRxiv}}}
+  \textbf{\bibinfo{volume}{doi.org/10.1101/668483}} (\bibinfo{year}{2019}).
+
+\bibitem{LiegEtal19}
+\bibinfo{author}{Li\'{e}geois, R.} \emph{et~al.}
+\newblock \bibinfo{title}{Resting brain dynamics at different timescales
+  capture distinct aspects of human behavior}.
+\newblock \emph{\bibinfo{journal}{Nature Communications}}
+  \textbf{\bibinfo{volume}{10}}, \bibinfo{pages}{1--9} (\bibinfo{year}{2019}).
+
+\bibitem{ChanGlov10}
+\bibinfo{author}{Chang, C.} \& \bibinfo{author}{Glover, G.~H.}
+\newblock \bibinfo{title}{Time-frequency dynamics of resting-state brain
+  connectivity measured with f{MRI}}.
+\newblock \emph{\bibinfo{journal}{{NeuroImage}}} \textbf{\bibinfo{volume}{50}},
+  \bibinfo{pages}{81--98} (\bibinfo{year}{2010}).
+
+\bibitem{ZhenEtal19}
+\bibinfo{author}{Zheng, M.}, \bibinfo{author}{Allard, A.},
+  \bibinfo{author}{Hagmann, P.} \& \bibinfo{author}{Serrano, M. . .~A.}
+\newblock \bibinfo{title}{Geometric renormalization unravels self-similarity of
+  the multiscale human connectome}.
+\newblock \emph{\bibinfo{journal}{{arXiv}}}
+  \textbf{\bibinfo{volume}{1904.11793}} (\bibinfo{year}{2019}).
+
+\bibitem{BaldEtal17}
+\bibinfo{author}{Baldassano, C.} \emph{et~al.}
+\newblock \bibinfo{title}{Discovering event structure in continuous narrative
+  perception and memory}.
+\newblock \emph{\bibinfo{journal}{Neuron}} \textbf{\bibinfo{volume}{95}},
+  \bibinfo{pages}{709--721} (\bibinfo{year}{2017}).
+
+\bibitem{HassEtal15}
+\bibinfo{author}{Hasson, U.}, \bibinfo{author}{Chen, J.} \&
+  \bibinfo{author}{Honey, C.~J.}
+\newblock \bibinfo{title}{Hierarchical process memory: memory as an integral
+  component of information processing}.
+\newblock \emph{\bibinfo{journal}{Trends in Cognitive Sciences}}
+  \textbf{\bibinfo{volume}{19}}, \bibinfo{pages}{304--315}
+  (\bibinfo{year}{2015}).
+
+\bibitem{HoneEtal12a}
+\bibinfo{author}{Honey, C.~J.} \emph{et~al.}
+\newblock \bibinfo{title}{Slow cortical dynamics and the accumulation of
+  information over long timescales}.
+\newblock \emph{\bibinfo{journal}{Neuron}} \textbf{\bibinfo{volume}{76}},
+  \bibinfo{pages}{423--434} (\bibinfo{year}{2012}).
+
+\bibitem{LernEtal11}
+\bibinfo{author}{Lerner, Y.}, \bibinfo{author}{Honey, C.~J.},
+  \bibinfo{author}{Silbert, L.~J.} \& \bibinfo{author}{Hasson, U.}
+\newblock \bibinfo{title}{Topographic mapping of a hierarchy of temporal
+  receptive windows using a narrated story}.
+\newblock \emph{\bibinfo{journal}{The Journal of Neuroscience}}
+  \textbf{\bibinfo{volume}{31}}, \bibinfo{pages}{2906--2915}
+  (\bibinfo{year}{2011}).
+
+\bibitem{LernEtal14}
+\bibinfo{author}{Lerner, Y.}, \bibinfo{author}{Honey, C.~J.},
+  \bibinfo{author}{Katkov, M.} \& \bibinfo{author}{Hasson, U.}
+\newblock \bibinfo{title}{Temporal scaling of neural responses to compressed
+  and dilated natural speech}.
+\newblock \emph{\bibinfo{journal}{Journal of Neurophysiology}}
+  \textbf{\bibinfo{volume}{111}}, \bibinfo{pages}{2433--2444}
+  (\bibinfo{year}{2014}).
+
+\bibitem{ChieHone19}
+\bibinfo{author}{Chien, H.-Y.~S.} \& \bibinfo{author}{Honey, C.~J.}
+\newblock \bibinfo{title}{Constructing and forgetting temporal context in the
+  human cerebral cortex}.
+\newblock \emph{\bibinfo{journal}{{bioRxiv}}}
+  \textbf{\bibinfo{volume}{doi.org/10.1101/761593}} (\bibinfo{year}{2019}).
+
+\bibitem{LeeEtal20}
+\bibinfo{author}{Lee, C.~S.}, \bibinfo{author}{Aly, M.} \&
+  \bibinfo{author}{Baldassano, C.}
+\newblock \bibinfo{title}{Anticipation of temporally structured events in the
+  brain}.
+\newblock \emph{\bibinfo{journal}{{bioRxiv}}}
+  \textbf{\bibinfo{volume}{10.1101/2020.10.14.338145}} (\bibinfo{year}{2020}).
+
+\bibitem{FallEtal20}
+\bibinfo{author}{Fallon, J.}, \bibinfo{author}{Ward, P. G.~D.},
+  \bibinfo{author}{Parkes, L.} \& \bibinfo{author}{Oldham, S.}
+\newblock \bibinfo{title}{Timescales of spontaneous {fMRI} fluctuations relate
+  to structural connectivity in the brain}.
+\newblock \emph{\bibinfo{journal}{Network Neuroscience}}
+  \textbf{\bibinfo{volume}{4}}, \bibinfo{pages}{788--806}
+  (\bibinfo{year}{2020}).
+
+\bibitem{ShapEtal19}
+\bibinfo{author}{Shappell, H.}, \bibinfo{author}{Caffo, B.~S.},
+  \bibinfo{author}{Pekar, J.~J.} \& \bibinfo{author}{Lindquist, M.~A.}
+\newblock \bibinfo{title}{Improved state change estimation in dynamic
+  functional connectivity using hidden semi-{M}arkov models}.
+\newblock \emph{\bibinfo{journal}{{NeuroImage}}}
+  \textbf{\bibinfo{volume}{191}}, \bibinfo{pages}{243--257}
+  (\bibinfo{year}{2019}).
+
+\bibitem{VidaEtal18}
+\bibinfo{author}{Vidaurre, D.} \emph{et~al.}
+\newblock \bibinfo{title}{Discovering dynamic brain neworks from big data in
+  rest and task}.
+\newblock \emph{\bibinfo{journal}{{NeuroImage}}}
+  \textbf{\bibinfo{volume}{180}}, \bibinfo{pages}{646--656}
+  (\bibinfo{year}{2018}).
+
+\bibitem{AlleEtal12b}
+\bibinfo{author}{Allen, E.~A.} \emph{et~al.}
+\newblock \bibinfo{title}{Tracking whole-brain connectivity dynamics in the
+  resting state}.
+\newblock \emph{\bibinfo{journal}{Cerebral Cortex}}
+  \textbf{\bibinfo{volume}{24}}, \bibinfo{pages}{663--676}
+  (\bibinfo{year}{2012}).
+
+\bibitem{SimoChan20}
+\bibinfo{author}{Simony, E.} \& \bibinfo{author}{Chang, C.}
+\newblock \bibinfo{title}{Analysis of stimulus-induced brain dynamics during
+  naturalistic paradigms}.
+\newblock \emph{\bibinfo{journal}{{NeuroImage}}}
+  \textbf{\bibinfo{volume}{216}}, \bibinfo{pages}{116461}
+  (\bibinfo{year}{2020}).
+
+\bibitem{Zar10}
+\bibinfo{author}{Zar, J.~H.}
+\newblock \emph{\bibinfo{title}{Biostatistical analysis}}
+  (\bibinfo{publisher}{Prentice-Hall}, \bibinfo{year}{2010}).
+
+\bibitem{TippBish99}
+\bibinfo{author}{Tipping, M.~E.} \& \bibinfo{author}{Bishop, C.~M.}
+\newblock \bibinfo{title}{Probabilistic principal component analysis}.
+\newblock \emph{\bibinfo{journal}{Journal of Royal Statistical Society, Series
+  {B}}} \textbf{\bibinfo{volume}{61}}, \bibinfo{pages}{611--622}
+  (\bibinfo{year}{1999}).
+
+\bibitem{Spea04}
+\bibinfo{author}{Spearman, C.}
+\newblock \bibinfo{title}{General intelligence, objectively determined and
+  measured}.
+\newblock \emph{\bibinfo{journal}{Americal Journal of Psychology}}
+  \textbf{\bibinfo{volume}{15}}, \bibinfo{pages}{201--292}
+  (\bibinfo{year}{1904}).
+
+\bibitem{JuttHera91}
+\bibinfo{author}{Jutten, C.} \& \bibinfo{author}{Herault, J.}
+\newblock \bibinfo{title}{Blind separation of sources, part {I}: an adaptive
+  algorithm based on neuromimetic architecture}.
+\newblock \emph{\bibinfo{journal}{Signal Processing}}
+  \textbf{\bibinfo{volume}{24}}, \bibinfo{pages}{1--10} (\bibinfo{year}{1991}).
+
+\bibitem{ComoEtal91}
+\bibinfo{author}{Comon, P.}, \bibinfo{author}{Jutten, C.} \&
+  \bibinfo{author}{Herault, J.}
+\newblock \bibinfo{title}{Blind separation of sources, part {II}: problems
+  statement}.
+\newblock \emph{\bibinfo{journal}{Signal Processing}}
+  \textbf{\bibinfo{volume}{24}}, \bibinfo{pages}{11--20}
+  (\bibinfo{year}{1991}).
+
+\bibitem{vandHint08}
+\bibinfo{author}{van~der Maaten, L. J.~P.} \& \bibinfo{author}{Hinton, G.~E.}
+\newblock \bibinfo{title}{Visualizing high-dimensional data using {t-SNE}}.
+\newblock \emph{\bibinfo{journal}{Journal of Machine Learning Research}}
+  \textbf{\bibinfo{volume}{9}}, \bibinfo{pages}{2579--2605}
+  (\bibinfo{year}{2008}).
+
+\bibitem{McInEtal18}
+\bibinfo{author}{McInnes, L.}, \bibinfo{author}{Healy, J.} \&
+  \bibinfo{author}{Melville, J.}
+\newblock \bibinfo{title}{{UMAP}: uniform manifold approximation and projection
+  for dimension reduction}.
+\newblock \emph{\bibinfo{journal}{{arXiv}}} \textbf{\bibinfo{volume}{1802}}
+  (\bibinfo{year}{2018}).
+
+\bibitem{LeeSeun99}
+\bibinfo{author}{Lee, D.~D.} \& \bibinfo{author}{Seung, H.~S.}
+\newblock \bibinfo{title}{Learning the parts of objects by non-negative matrix
+  factorization}.
+\newblock \emph{\bibinfo{journal}{Nature}} \textbf{\bibinfo{volume}{401}},
+  \bibinfo{pages}{788--791} (\bibinfo{year}{1999}).
+
+\bibitem{MannEtal14b}
+\bibinfo{author}{Manning, J.~R.}, \bibinfo{author}{Ranganath, R.},
+  \bibinfo{author}{Norman, K.~A.} \& \bibinfo{author}{Blei, D.~M.}
+\newblock \bibinfo{title}{Topographic factor analysis: a {B}ayesian model for
+  inferring brain networks from neural data}.
+\newblock \emph{\bibinfo{journal}{{PLoS} One}} \textbf{\bibinfo{volume}{9}},
+  \bibinfo{pages}{e94914} (\bibinfo{year}{2014}).
+
+\bibitem{GersEtal11}
+\bibinfo{author}{Gershman, S.~J.}, \bibinfo{author}{Blei, D.~M.},
+  \bibinfo{author}{Pereira, F.} \& \bibinfo{author}{Norman, K.~A.}
+\newblock \bibinfo{title}{A topographic latent source model for {fMRI} data}.
+\newblock \emph{\bibinfo{journal}{{NeuroImage}}} \textbf{\bibinfo{volume}{57}},
+  \bibinfo{pages}{89--100} (\bibinfo{year}{2011}).
+
+\bibitem{MairEtal09a}
+\bibinfo{author}{Mairal, J.~B.}, \bibinfo{author}{Bach, F.},
+  \bibinfo{author}{Ponce, J.} \& \bibinfo{author}{Sapiro, G.}
+\newblock \bibinfo{title}{Online dictionary learning for sparse coding}.
+\newblock \emph{\bibinfo{journal}{Proceedings of the International Conference
+  on Machine Learning}} \bibinfo{pages}{689--696} (\bibinfo{year}{2009}).
+
+\bibitem{MairEtal09b}
+\bibinfo{author}{Mairal, J.}, \bibinfo{author}{Ponce, J.},
+  \bibinfo{author}{Sapiro, G.}, \bibinfo{author}{Zisserman, A.} \&
+  \bibinfo{author}{Bach, F.~R.}
+\newblock \bibinfo{title}{Supervised dictionary learning}.
+\newblock \emph{\bibinfo{journal}{Advances in Neural Information Processing
+  Systems}} \bibinfo{pages}{1033--1040} (\bibinfo{year}{2009}).
+
+\bibitem{HintSala06}
+\bibinfo{author}{Hinton, G.~E.} \& \bibinfo{author}{Salakhutdinov, R.~R.}
+\newblock \bibinfo{title}{Reducing the dimensionality of data with neural
+  networks}.
+\newblock \emph{\bibinfo{journal}{Science}} \textbf{\bibinfo{volume}{313}},
+  \bibinfo{pages}{504--507} (\bibinfo{year}{2006}).
+
+\bibitem{Newm05}
+\bibinfo{author}{Newman, M. E.~J.}
+\newblock \bibinfo{title}{A measure of betweenness centrality based on random
+  walks}.
+\newblock \emph{\bibinfo{journal}{Social Networks}}
+  \textbf{\bibinfo{volume}{27}}, \bibinfo{pages}{39--54}
+  (\bibinfo{year}{2005}).
+
+\bibitem{OpsaEtal10}
+\bibinfo{author}{Opsahl, T.}, \bibinfo{author}{Agneessens, F.} \&
+  \bibinfo{author}{Skvoretz, J.}
+\newblock \bibinfo{title}{Node centrality in weighted networks: generalizing
+  degree and shortest paths}.
+\newblock \emph{\bibinfo{journal}{Social Networks}}
+  \textbf{\bibinfo{volume}{32}}, \bibinfo{pages}{245--251}
+  (\bibinfo{year}{2010}).
+
+\bibitem{Bart04}
+\bibinfo{author}{Barth\'{e}lemy, M.}
+\newblock \bibinfo{title}{Betweenness centrality in large complex networks}.
+\newblock \emph{\bibinfo{journal}{{European} Physical Journal {B}}}
+  \textbf{\bibinfo{volume}{38}}, \bibinfo{pages}{163--168}
+  (\bibinfo{year}{2004}).
+
+\bibitem{GeisEtal08}
+\bibinfo{author}{Geisberger, R.}, \bibinfo{author}{Sanders, P.} \&
+  \bibinfo{author}{Schultes, D.}
+\newblock \bibinfo{title}{Better approximation of betweenness centrality}.
+\newblock \emph{\bibinfo{journal}{Proceedings of the Meeting on Algorithm
+  Engineering and Experiments}} \bibinfo{pages}{90--100}
+  (\bibinfo{year}{2008}).
+
+\bibitem{Free77}
+\bibinfo{author}{Freeman, L.~C.}
+\newblock \bibinfo{title}{A set of measures of centrality based on
+  betweenness}.
+\newblock \emph{\bibinfo{journal}{Sociometry}} \textbf{\bibinfo{volume}{40}},
+  \bibinfo{pages}{35--41} (\bibinfo{year}{1977}).
+
+\bibitem{Rao82}
+\bibinfo{author}{Rao, C.~R.}
+\newblock \bibinfo{title}{Diversity and dissimilarity coeficients: a unified
+  approach}.
+\newblock \emph{\bibinfo{journal}{Theoretical Population Biology}}
+  \textbf{\bibinfo{volume}{21}}, \bibinfo{pages}{24--43}
+  (\bibinfo{year}{1982}).
+
+\bibitem{Lin09}
+\bibinfo{author}{Lin, J.}
+\newblock \bibinfo{title}{Divergence measures based on the {Shannon} entropy}.
+\newblock \emph{\bibinfo{journal}{{IEEE} Transactions on Information Theory}}
+  \textbf{\bibinfo{volume}{37}}, \bibinfo{pages}{145--151}
+  (\bibinfo{year}{2009}).
+
+\bibitem{RicoSzei06}
+\bibinfo{author}{Ricotta, C.} \& \bibinfo{author}{Szeidl, L.}
+\newblock \bibinfo{title}{Towards a unifying approach to diversity measures:
+  bridging the gap between the {Shannon} entropy and {Rao's} quadratic index}.
+\newblock \emph{\bibinfo{journal}{Theoretical Population Biology}}
+  \textbf{\bibinfo{volume}{70}}, \bibinfo{pages}{237--243}
+  (\bibinfo{year}{2006}).
+
+\bibitem{Newm08}
+\bibinfo{author}{Newman, M. E.~J.}
+\newblock \bibinfo{title}{The mathematics of networks}.
+\newblock \emph{\bibinfo{journal}{The New Palgrave Encyclopedia of Economics}}
+  \textbf{\bibinfo{volume}{2}}, \bibinfo{pages}{1--12} (\bibinfo{year}{2008}).
+
+\bibitem{Bona07}
+\bibinfo{author}{Bonacich, P.}
+\newblock \bibinfo{title}{Some unique properties of eigenvector centrality}.
+\newblock \emph{\bibinfo{journal}{Social Networks}}
+  \textbf{\bibinfo{volume}{29}}, \bibinfo{pages}{555--564}
+  (\bibinfo{year}{2007}).
+
+\bibitem{LohmEtal10}
+\bibinfo{author}{Lohmann, G.} \emph{et~al.}
+\newblock \bibinfo{title}{Eigenvector centrality mapping for analyzing
+  connectivity patterns in {fMRI} data of the human brain}.
+\newblock \emph{\bibinfo{journal}{{PLoS} One}} \textbf{\bibinfo{volume}{5}},
+  \bibinfo{pages}{e10232} (\bibinfo{year}{2010}).
+
+\bibitem{HaluEtal13}
+\bibinfo{author}{Halu, A.}, \bibinfo{author}{Mondrag\'{o}n, R.~J.},
+  \bibinfo{author}{Panzarasa, P.} \& \bibinfo{author}{Bianconi, G.}
+\newblock \bibinfo{title}{Multiplex {PageRank}}.
+\newblock \emph{\bibinfo{journal}{{PLoS} One}} \textbf{\bibinfo{volume}{8}},
+  \bibinfo{pages}{e78293} (\bibinfo{year}{2013}).
+
+\bibitem{HoneEtal07}
+\bibinfo{author}{Honey, C.~J.}, \bibinfo{author}{K\"{o}tter, R.},
+  \bibinfo{author}{Breakspear, M.} \& \bibinfo{author}{Sporns, O.}
+\newblock \bibinfo{title}{Network structure of cerebral cortex shapes
+  functional connectivity on multiple time scales}.
+\newblock \emph{\bibinfo{journal}{Proceedings of the National Academy of
+  Sciences, {USA}}} \textbf{\bibinfo{volume}{104}},
+  \bibinfo{pages}{10240--10245} (\bibinfo{year}{2007}).
+
+\bibitem{Schr00}
+\bibinfo{author}{Schreiber, T.}
+\newblock \bibinfo{title}{Measuring information transfer}.
+\newblock \emph{\bibinfo{journal}{Physical Review Letters}}
+  \textbf{\bibinfo{volume}{85}}, \bibinfo{pages}{461--464}
+  (\bibinfo{year}{2000}).
+
+\bibitem{AlvaEtal05}
+\bibinfo{author}{Alvarez-Hamelin, I.}, \bibinfo{author}{Dall'Asta, L.},
+  \bibinfo{author}{Barrat, A.} \& \bibinfo{author}{Vespignani, A.}
+\newblock \bibinfo{title}{$k$-corr decomposition: a tool for the visualiztion
+  of large scale networks}.
+\newblock \emph{\bibinfo{journal}{{arXiv}}} \bibinfo{pages}{cs/0504107v2}
+  (\bibinfo{year}{2005}).
+
+\bibitem{ChriFowl10}
+\bibinfo{author}{Christakis, N.~A.} \& \bibinfo{author}{Fowler, J.~H.}
+\newblock \bibinfo{title}{Social network sensors for early detection of
+  contagious outbreaks}.
+\newblock \emph{\bibinfo{journal}{{PLoS} One}} \textbf{\bibinfo{volume}{5}},
+  \bibinfo{pages}{e12948} (\bibinfo{year}{2010}).
+
+\bibitem{RubiSpor10}
+\bibinfo{author}{Rubinov, M.} \& \bibinfo{author}{Sporns, O.}
+\newblock \bibinfo{title}{Complex network measures of brain connectivity: uses
+  and interpretations}.
+\newblock \emph{\bibinfo{journal}{{NeuroImage}}} \textbf{\bibinfo{volume}{52}},
+  \bibinfo{pages}{1059--1069} (\bibinfo{year}{2010}).
+
+\bibitem{EstrRodr05}
+\bibinfo{author}{Estrada, E.} \& \bibinfo{author}{Rodr\'{i}guez-Vel\'{a}zquez,
+  J.~A.}
+\newblock \bibinfo{title}{Subraph centrality in complex networks}.
+\newblock \emph{\bibinfo{journal}{Physical Review {E}}}
+  \textbf{\bibinfo{volume}{71}}, \bibinfo{pages}{056103}
+  (\bibinfo{year}{2005}).
+
+\bibitem{ThomEtal18}
+\bibinfo{author}{Thompson, W.~H.}, \bibinfo{author}{Richter, C.~G.},
+  \bibinfo{author}{Plav\'{e}n-Sigray, P.} \& \bibinfo{author}{Fransson, P.}
+\newblock \bibinfo{title}{Simulations to benchmark time-varying connectivity
+  methods for f{MRI}}.
+\newblock \emph{\bibinfo{journal}{{PLoS} Computational Biology}}
+  \textbf{\bibinfo{volume}{14}}, \bibinfo{pages}{e1006196}
+  (\bibinfo{year}{2018}).
+
+\bibitem{CapoEtal17}
+\bibinfo{author}{Capota, M.} \emph{et~al.}
+\newblock \bibinfo{title}{Brain imaging analysis kit} (\bibinfo{year}{2017}).
+
+\bibitem{NoceWrig06}
+\bibinfo{author}{Nocedal, J.} \& \bibinfo{author}{Wright, S.~J.}
+\newblock \emph{\bibinfo{title}{Numerical optimization}}
+  (\bibinfo{publisher}{Springer}, \bibinfo{address}{New York, {NY}},
+  \bibinfo{year}{2006}).
+
+\bibitem{CombEtal19}
+\bibinfo{author}{Combrisson, E.} \emph{et~al.}
+\newblock \bibinfo{title}{Visbrain: a multi-purpose {GPU}-accelerated
+  open-source suite for multimodal brain data visualization}.
+\newblock \emph{\bibinfo{journal}{Frontiers in Neuroinformatics}}
+  \textbf{\bibinfo{volume}{13}}, \bibinfo{pages}{1--14} (\bibinfo{year}{2019}).
+
+\end{thebibliography}
 

### 2021-08-05 paper/main.tex
text updates, but still need to update release version and zenodo link

@@
 The authors declare that the data supporting the findings of this
-study as well as the source data for this paper are available at \href{https://github.com/ContextLab/timecorr-paper/releases/tag/v0.3}{github.com/ContextLab/timecorr-paper/releases/tag/v0.3}.
-The fMRI dataset collected by \cite{SimoEtal16} has been made publicly available at
-\href{http://arks.princeton.edu/ark:/88435/dsp015d86p269k}{arks.princeton.edu/ark:/88435/dsp015d86p269k}
+study as well as the source data for this paper are available at
+\href{https://github.com/ContextLab/timecorr-paper/releases/tag/v0.3}{github.com/ContextLab/timecorr-paper/releases/tag/v0.3}
+and has been deposited in the Zenodo database under accession code
+(link here).
+The raw fMRI data are protected and are not available due to data
+privacy laws. The processed fMRI dataset collected by \cite{SimoEtal16} has been made publicly available at
+\href{http://arks.princeton.edu/ark:/88435/dsp015d86p269k}{arks.princeton.edu/ark:/88435/dsp015d86p269k}.
 

### 2021-08-05 paper/main.tex
final paper updates

@@
 The raw fMRI data are protected and are not available due to data
-privacy laws. The processed fMRI dataset collected by \cite{SimoEtal16} has been made publicly available at
+privacy laws. The processed fMRI dataset collected by
+\cite{SimoEtal16} has been made publicly available \cite{SimoEtal16b} at
 \href{http://arks.princeton.edu/ark:/88435/dsp015d86p269k}{arks.princeton.edu/ark:/88435/dsp015d86p269k}.
@@
 \newblock \emph{\bibinfo{journal}{Frontiers in Neuroinformatics}}
-  \textbf{\bibinfo{volume}{13}}, \bibinfo{pages}{1--14} (\bibinfo{year}{2019}).
+  \textbf{\bibinfo{volume}{13}}, \bibinfo{pages}{1--14}
+  (\bibinfo{year}{2019}).
+
+\bibitem{SimoEtal16b}
+\bibinfo{author}{Simony, E.}, \bibinfo{author}{Honey, C.~J.},
+  \bibinfo{author}{Chen, J.} \& \bibinfo{author}{Hasson, U.}
+\newblock \bibinfo{title}{Dynamic reconfiguration of the default mode network
+  during narrative comprehension}.
+\newblock \emph{\bibinfo{journal}{DataSpace}}
+  \textbf{\bibinfo{volume}{http://arks.princeton.edu/ark:/88435/dsp015d86p269k}} (\bibinfo{year}{2016}).
 

### 2021-08-05 paper/main.tex
updated with zenodo doi and update release number

@@
 study as well as the source data for this paper are available at
-\href{https://github.com/ContextLab/timecorr-paper/releases/tag/v0.3}{github.com/ContextLab/timecorr-paper/releases/tag/v0.3}
-and has been deposited in the Zenodo database under accession code
-(link here).
+\href{https://github.com/ContextLab/timecorr-paper/releases/tag/v0.4}{github.com/ContextLab/timecorr-paper/releases/tag/v0.4}
+and has been deposited in the Zenodo database under accession code \href{https://doi.org/10.5281/zenodo.5165253}{https://doi.org/10.5281/zenodo.5165253}.
 The raw fMRI data are protected and are not available due to data
@@
 All of our analysis code may be downloaded from
-\href{https://github.com/ContextLab/timecorr-paper/releases/tag/v0.3}{github.com/ContextLab/timecorr-paper/releases/tag/v0.3}.
+\href{https://github.com/ContextLab/timecorr-paper/releases/tag/v0.3}{github.com/ContextLab/timecorr-paper/releases/tag/v0.4}.
 We have also published a companion Python toolbox that may be downloaded from \href{https://timecorr.readthedocs.io}{timecorr.readthedocs.io}.

### 2021-08-06 paper/old.tex
updated old text file and diff file

@@
 \newcommand{\kernelwidth}{S2}
-\newcommand{\intact}{S3}
-\newcommand{\para}{S4}
-\newcommand{\word}{S5}
-\newcommand{\rest}{S6}
-\newcommand{\pca}{S7}
+\newcommand{\timeheatmap}{S3}
+\newcommand{\features}{S4}
+\newcommand{\intact}{S5}
+\newcommand{\para}{S6}
+\newcommand{\word}{S7}
+\newcommand{\rest}{S8}
+\newcommand{\pca}{S9}
 
@@
 better able to recover dynamic first-order correlations than
-second-order correlations.  We expected that this would happen, given
-that errors in our estimation procedure at lower orders necessarily
-propagate to higher orders (since lower-order correlations are used to
-estimate higher-order correlations).  Interestingly, we also found
-that when the correlations were particularly \textit{un}stable (random
-datasets), we better recovered second-order correlations.
+second-order correlations.  This is because errors in our \textit{estimation}
+procedure at lower orders necessarily propagate to higher orders
+(since lower-order correlations are used to estimate higher-order
+correlations).  Conversely, when the correlations were particularly
+\textit{un}stable (random datasets), we better recovered second-order
+correlations.  This is because noise in our \textit{data generation}
+procedure propagates from higher orders to lower orders (see
+\textit{Synthetic data: simulating dynamic high-order correlations}).
 
@@
     computed using a Laplace kernel
-    (width~$=20$).  \textbf{a. Constant correlations.}  These datasets
+    (width~$=20$).  \textbf{Constant.}  These datasets
     have stable (unchanging) underlying second-order correlation
-    matrices.  \textbf{b. Random correlations.} These datasets are
+    matrices.  \textbf{Random.} These datasets are
     generated using a new independently drawn second-order correlation
-    matrix at each timepoint.  \textbf{c. Ramping correlations.}
+    matrix at each timepoint.  \textbf{Ramping.}
     These datasets are generated by smoothly varying the underlying
     second-order correlations between the randomly drawn correlation
-    matrices at the first and last timepoints.  \textbf{d. Event-based
-      correlations.}  These datasets are each generated using five
+    matrices at the first and last timepoints.  \textbf{Event.}  These datasets are each generated using five
     randomly drawn second-order correlation matrices that each remain
     stable for a fifth of the total timecourse.  The
-    vertical lines denote event boundaries.}
+    vertical lines denote event boundaries.  Note that the ``dips''
+    and ``ramps'' at the boundaries of sharp transitions (e.g., the
+    beginning and ends of the ``constant'' and ``ramping'' datasets,
+    and at the event boundaries of the ``event'' datasets) are
+    finite-sample effects that reflect the reduced numbers of samples
+    that may be used to accurately estimate correlations at sharp
+    boundaries.}
   \label{fig:higher_order_sims}
 \end{figure}
+
+We also examined the impact of the data duration (Fig.~\timeheatmap)
+and complexity (number of zero-order features; Fig.~\features) on our
+ability to accurately recover ground truth first-order and
+second-order dynamic correlations.  In general, we found that our approach
+better recovers ground truth dynamic correlations from longer duration
+timeseries data.  We also found that our approach tends to best recover data generated
+using fewer zero-order features (i.e., lower complexity), although
+this tendency was not strictly monotonic.  Further, because our data
+generation procedure requires $\mathcal{O}(K^{4})$ memory to generate
+a second-order timeseries with $K$ zero-order features, we were not
+able to fully explore how the number of zero-order features affects
+recovery accuracy as the number of features gets larger (e.g., as it
+approaches the number of features present in the fMRI data we examine
+below).  Although we were not able to formally test this to our
+satisfaction, we expect that accurately estimating dynamic high-order
+correlations would require data with many more zero-order features
+than we were able to simulate.  Our reasoning is that
+high-order correlations necessarily involve larger numbers of
+lower-order features, so achieving adequate ``resolution'' high-order
+timeseries might require many low-order features.
 
@@
 order $n - 2$ order timeseries, and so on, until we obtain an order 0
-timeseries of simulated data that reflects the chosen high-order dynamics.
-
-The central mathematical operations in our procedure are two bookkeeping
-functions, $\mathrm{vec}(\cdot)$ and $\mathrm{mat}(\cdot)$.  The
-$\mathrm{vec}(\cdot)$ function takes as input a $K \times K$ symmetric
-matrix and returns as output a
-$\left(\frac{K^2 - K}{2} + K\right)$-dimensional column vector
-containing the entries in the upper triangle and diagonal.  The
-$\mathrm{mat}(\cdot)$ function inverts $\mathrm{vec}(\cdot)$ by taking
-as input a $\left(\frac{K^2 - K}{2} + K\right)$-dimensional column
-vector and returning a $K \times K$ symmetric matrix as output.  We
-can then generate an order $n$ correlation matrix (for one timepoint, $t$) from an order
-$n - 1$ template (from the same timepoint) as follows:
-\begin{align}
-  \mathbf{\Sigma_{n}}(t) &= \mathrm{mat}(\mathrm{vec}(\mathbf{\Sigma_{n-1}}(t)) \otimes \mathrm{vec}(\mathbf{\Sigma_{n-1}}(t))^\top).\label{eqn:veccorr}
-\end{align}
-
-Given a timeseries of order $n$ correlation matrices, we can draw an
-order $n-1$ correlation matrix for each timepoint $t$ using
-\begin{align}
- \mathbf{\sigma_{n-1}}(t) &\sim \mathcal{N}\left(\mathbf{0}, \mathbf{\Sigma_n}(t)
-                   \right)\label{eqn:highorder-gen1}\\
-  \mathbf{\Sigma_{n-1}}(t) &= \mathrm{mat}(\mathbf{\sigma_{n-1}}(t)).\label{eqn:highorder-gen2}
-  \end{align}
-  We can then use repeated applications of
-  Equations~\ref{eqn:highorder-gen1} and~\ref{eqn:highorder-gen2} in
-  order to obtain a synthetic dataset.
-
- When the template first-order correlations are constructed to exhibit different
- temporal profiles (e.g., using the constant, random, ramping, and
- event procedures described above), the resulting high-order
- correlations and synthetic data will exhibit the same category of
- temporal profile. Following our approach to generating synthetic data exhibiting known
- first-order correlations, we constructed a total of 40 additional multivariate timeseries,
-collectively reflecting a total of 4 qualitatively different patterns
-of dynamic correlations (i.e., 10 datasets reflecting each type of
-dynamic pattern: constant, random, ramping, and event).
+timeseries of simulated data that reflects the chosen high-order
+dynamics.
+
+The central mathematical operation in our procedure is the Kronecker
+product ($\otimes$).  The Kronecker product of a $K \times K$ matrix,
+$m_1$, with itself (i.e., $m_1 \otimes m_1$) produces a new
+$K^2 \times K^2$ matrix, $m_2$ whose entries reflect a scaled tiling
+of the entries in $m_1$.  If these tilings (scaled copies of $m_1$) are
+indexed by row and column, then the tile in the
+$i$\textsuperscript{th} row and $j$\textsuperscript{th} column
+contains the entries of $m_1$, multiplied by $m_1(i, j)$.  Following
+this pattern, the Kronecker product $m_2 \otimes m_2$ yields the
+$K^4 \times K^4$ matrix $m_3$ whose tiles are scaled copies of $m_2$.
+In general, repeated applications of the Kronecker self-product may be
+used to generate $m_{n+1} = m_n \otimes m_n$ for $n > 1$, where
+$m_{n+1}$ is a $K^{2^n} \times K^{2^n}$ matrix.  After generating a
+first-order timeseries of dynamic correlations (see \textit{Synthetic
+  data: simulating dynamic first-order correlations}), we use this
+procedure (applied independently at each timepoint) to transform it
+into a timeseries of $n$\textsuperscript{th}-order correlations.  When
+$m_{n+1}$ is generated in this way, the temporal structure of the full
+timeseries (i.e., constant, random, ramping, event) is preserved,
+since changes in the original first-order timeseries are also
+reflected in the scaled tilings of itself that comprise the
+higher-order matrices.
+
+Given a timeseries of $n$\textsuperscript{th}-order correlations, we
+then need to work ``backwards'' in order to generate the order-zero
+timeseries.  If the $n$\textsuperscript{th}-order correlation matrix
+at a given timepoint is $m_n$, then we can generate an order $n-1$
+correlation matrix (for $n > 1$) by taking a draw from
+$\mathcal{N}\left(0, m_n\right)$ and reshaping the resulting vector to
+have square dimensions.  To force the resulting matrix to be
+symmetric, we remove its lower triangle, and replace the lower
+triangle with (a reflected version
+of) its upper triangle.  Intuitively, the resulting re-shaped matrix will look
+like a noisy (but symmetric) version of the template matrix, $m_{n-1}$.  (When
+$n = 1$, no re-shaping is needed; the resulting $K$-dimensional vector
+may be used as the observation at the given timepoint.)  After
+independently drawing each timepoint's order $n-1$ correlation matrix
+from that timepoint's order $n$ correlation matrix, this process can
+be applied repeatedly until $n = 0$.  This results in a
+$K$-dimensional timeseries of $T$ observations containing the
+specified high-order correlations at orders 1 through $n$.  Following
+our approach to generating synthetic data exhibiting known first-order
+correlations, we constructed a total of 400 additional multivariate
+timeseries, collectively reflecting a total of 4 qualitatively
+different patterns of dynamic correlations (i.e., 100 datasets
+reflecting each type of dynamic pattern: constant, random, ramping,
+and event).  Each timeseries comprised 10 zero-order features (dimensions)
+that varied over 300 timepoints.  After applying our dynamic
+correlation estimation procedure, this yielded a 100-dimensional
+timeseries of first-order
+features that could then be used to estimate dynamic second-order
+correlations.  (We chose to use $K=10$ zero-order features for our
+higher order simulations in order to put the accuracy computations
+displayed in Figs.~\ref{fig:synthetic} and~\ref{fig:higher_order_sims}
+on a roughly even footing.)
 

### 2021-08-11 paper/main.tex
updates from editor

@@
 $n^\mathrm{th}$-order dynamic correlations (see Feature
-  weighting and testing, Fig.~\ref{fig:pipeline}).  We repeated this process for
+  weighting and testing).  We repeated this process for
 $n \in \left\{ 0, 1, 2, ..., 10 \right\}$.  Our examinations of
@@
 \href{https://github.com/ContextLab/timecorr-paper/releases/tag/v0.4}{github.com/ContextLab/timecorr-paper/releases/tag/v0.4}
-and has been deposited in the Zenodo database under accession code \href{https://doi.org/10.5281/zenodo.5165253}{https://doi.org/10.5281/zenodo.5165253}.
-The raw fMRI data are protected and are not available due to data
+and has been deposited in the Zenodo database under accession code
+\href{https://doi.org/10.5281/zenodo.5165253}{https://doi.org/10.5281/zenodo.5165253}.
+The source data underlying Figs. 2-6 and Supplementary Figs. S1-S9 are
+provided as a Source Data file. Source Data are provided with the
+manuscript. The raw fMRI data are protected and are not available due to data
 privacy laws. The processed fMRI dataset collected by
@@
 \section*{Competing interests}
-The authors declare no competing financial interests.
+The authors declare no competing interests.
 

### 2021-08-11 paper/main.tex
formatting edits

@@
 hypothesized) mental states or cognitive
-representations~\citep[e.g.,][]{HaxbEtal01, NormEtal06b, TongPrat12,
+representations~\cite{HaxbEtal01, NormEtal06b, TongPrat12,
   MitcEtal08a, KamiTong05, NishEtal11, PereEtal18, HuthEtal12,
@@
 region of interest analyses to estimate the anatomical locations of
-specific neural representations~\citep[e.g.,][]{EtzeEtal09}, or to
+specific neural representations~\cite{EtzeEtal09}, or to
 compare the relative contributions to the neural code of multivariate
 activity patterns versus dynamic correlations between neural activity
-patterns~\citep[e.g.,][]{MannEtal18, FongEtal19}.  An emerging theme
+patterns~\cite{MannEtal18, FongEtal19}.  An emerging theme
 in this literature is that cognition is mediated by dynamic
-interactions between brain structures~\citep{Gros88, Fris00, SporHone06, BassEtal06,
+interactions between brain structures~\cite{Gros88, Fris00, SporHone06, BassEtal06,
   Turk13, DemeEtal19, SoloEtal19, LuriEtal18, PretEtal17, ZouEtal19,
@@
 Studies of the neural code to date have primarily focused on
-univariate or multivariate neural patterns~\citep[for review
-see][]{NormEtal06b}, or (more recently) on patterns of dynamic
-first-order correlations~\citep[i.e., interactions between pairs of
-brain structures;][]{MannEtal18, FongEtal19, LuriEtal18, PretEtal17,
-  ZouEtal19, DemeEtal19}.  What might the future of this line of work
+univariate or multivariate neural patterns~\cite{NormEtal06b}, or (more recently) on patterns of dynamic
+first-order correlations (i.e., interactions between pairs of
+brain structures~\cite{MannEtal18, FongEtal19, LuriEtal18, PretEtal17,
+  ZouEtal19, DemeEtal19}).  What might the future of this line of work
 hold?  For example, is the neural code implemented through
-higher-order interactions between brain structures~\citep[e.g.,
-see][]{ReimEtal17}?  Second-order correlations reflect
+higher-order interactions between brain structures~\cite{ReimEtal17}?  Second-order correlations reflect
 homologous patterns of correlation.  In other words, if the
@@
 related to the notion that network dynamics reflect ongoing neural
-computations or cognitive processing~\citep[e.g.,][]{BeatEtal16}.  If
+computations or cognitive processing~\cite{BeatEtal16}.  If
 the nodes in two brain networks are interacting (within each network)
@@
 code is carried by activity patterns that directly reflect ongoing
-cognition~\citep[e.g., following][]{HaxbEtal01, NormEtal06b}, versus
+cognition~\cite{HaxbEtal01, NormEtal06b}, versus
 the dynamic properties of the network structure itself, independent of
-specific activity patterns in any given set of regions~\citep[e.g.,
-following][]{BassEtal06}.  For example, graph measures such as
-centrality and degree~\citep{BullSpor09} may be used to estimate how a
+specific activity patterns in any given set of regions~\cite{BassEtal06}.  For example, graph measures such as
+centrality and degree~\cite{BullSpor09} may be used to estimate how a
 given brain structure is ``communicating'' with other structures,
@@
 dimensionality reduction approaches: principle components
-analysis~\citep[PCA;][]{Pear01}, which preserves an approximately
-invertible transformation back to the original data~\citep[e.g., this
-follows related approaches taken by][]{McInJirs19, TokeSomm19,
-  GonzEtal19}; and a second non-invertible algorithm for computing
-dynamic patterns in eigenvector centrality~\citep{Land95}.  This
+analysis~\cite{Pear01} (PCA), which preserves an approximately
+invertible transformation back to the original data~\cite{McInJirs19, TokeSomm19,
+  GonzEtal19}, and a second non-invertible algorithm for computing
+dynamic patterns in eigenvector centrality~\cite{Land95}.  This
 latter approach characterizes correlations between each feature
@@
 in time) in favor of the specific activity histories of different
-features~\citep[also see][]{BetzEtal19, SizeEtal18, ReimEtal17}.
+features~\cite{BetzEtal19, SizeEtal18, ReimEtal17}.
 
@@
 scrambled version of the story, or underwent a resting state
-scan~\citep{SimoEtal16}.  Temporal scrambling has been used in a
+scan~\cite{SimoEtal16}.  Temporal scrambling has been used in a
 growing number of studies, largely by Uri Hasson's group, to identify
@@
 relevant neural patterns in fMRI data (see Forward inference
-  and decoding accuracy).  The dataset we examined~\citep[collected
-by][]{SimoEtal16} comprised four experimental conditions that exposed
+  and decoding accuracy).  The dataset we examined~\cite{SimoEtal16} comprised four experimental conditions that exposed
 participants to stimuli that varied systematically in how cognitively
@@
     (absolute value) correlations at each order, thresholded at 0.999,
-    and projected onto the cortical surface~\citep{CombEtal19}.  The
+    and projected onto the cortical surface~\cite{CombEtal19}.  The
     lists of terms on the right display the top five Neurosynth
-    terms~\citep{RubiEtal17} decoded from the corresponding brain maps
+    terms~\cite{RubiEtal17} decoded from the corresponding brain maps
     for each order.  Each row displays data from a different
@@
 single $K$ by $K$ $n^\mathrm{th}$-order DISFC matrix for each
-experimental condition.  We then used Neurosynth~\citep{RubiEtal17} to
+experimental condition.  We then used Neurosynth~\cite{RubiEtal17} to
 compute the terms most highly associated with the most strongly
@@
 We tested the hypothesis that high-level cognition is reflected in
-high-order brain network dynamics~\citep[e.g., see][]{SoloEtal19,
+high-order brain network dynamics~\cite{SoloEtal19,
   ReimEtal17}.  We examined high-order network dynamics in functional
@@
 proposed in myriad empirical studies and
-reviews~\citep[e.g.,][]{DemeEtal19, Turk13, LuriEtal18, FongEtal19,
+reviews~\cite{DemeEtal19, Turk13, LuriEtal18, FongEtal19,
   ParkEtal18b, PretEtal17, MannEtal18, RoyEtal19, LiegEtal19, ZouEtal19,
@@
 that uses graph theory and topology to characterize how brain networks
-reconfigure during cognition~\citep[e.g.,][]{BassEtal06, ZhenEtal19,
+reconfigure during cognition~\cite{BassEtal06, ZhenEtal19,
   McInJirs19, TokeSomm19, SizeEtal18, ReimEtal17, BetzEtal19}.
@@
 areas integrate information relatively quickly, whereas higher-level
-regions integrate information relatively slowly~\citep{BaldEtal17,
+regions integrate information relatively slowly~\cite{BaldEtal17,
   HassEtal08, HassEtal15, HoneEtal12a, LernEtal11, LernEtal14,
   ChieHone19}.  A similar hierarchy appears to play a role in
-predicting future events~\citep{LeeEtal20}.  Other related work in
+predicting future events~\cite{LeeEtal20}.  Other related work in
 human and mouse brains indicates that the temporal response profile of
 a given brain structure may relate to how strongly connected that
-structure is with other brain areas~\citep{FallEtal20}.  Further study
+structure is with other brain areas~\cite{FallEtal20}.  Further study
 is needed to understand the role of temporal integration at different
@@
 here as first-order dynamics likely varies across the experimental
-conditions we examined~\citep{SimoEtal16}.  Therefore a caveat to our
+conditions we examined~\cite{SimoEtal16}.  Therefore a caveat to our
 claim that richer stimuli evoke more stable higher-order dynamics is
@@
 suggesting that the brain undergoes rapid state changes, for example
-across event boundaries~\citep[e.g.,][]{BaldEtal17}.
+across event boundaries~\cite{BaldEtal17}.
 \cite{ShapEtal19} used hidden semi-Markov models to estimate
-state-specific network dynamics~\citep[also see][]{VidaEtal18}.  Our
+state-specific network dynamics~\cite{VidaEtal18}.  Our
 general approach might be extended by considering putative state
@@
 kernel-based dynamic correlations to extended the notion of (static)
-inter-subject functional connectivity~\citep{SimoEtal16} to a dynamic
+inter-subject functional connectivity~\cite{SimoEtal16} to a dynamic
 measure of inter-subject functional connectivity (DISFC) that does not
-rely on sliding windows~\citep[e.g., as in][]{MannEtal18}, and that
+rely on sliding windows~\cite{MannEtal18}, and that
 may be computed at individual timepoints.  This allowed us to
@@
 Pearson's correlation between any pair of columns, $\mathbf{X}(\cdot, i)$ and
-$\mathbf{X}(\cdot, j)$ using~\citep{Pear01}:
+$\mathbf{X}(\cdot, j)$ using~\cite{Pear01}:
 \begin{align}
@@
 $\tau \in \left[ -\infty, \infty \right]$ contributes to the estimated instantaneous
-correlation at time $t$~\citep[Fig.~\ref{fig:kernels}; also see][for a
-similar approach]{AlleEtal12b}.
+correlation~\cite{AlleEtal12b} at time $t$ (Fig.~\ref{fig:kernels}).
 \begin{figure}
@@
 ($n > 0$) for each of $P$ participants in an experiment.  We can use
-inter-subject functional connectivity~\citep[ISFC;
-][]{SimoEtal16, SimoChan20} to compute the stimulus-driven correlations reflected
+inter-subject functional connectivity~\cite{SimoEtal16, SimoChan20}
+(ISFC) to compute the stimulus-driven correlations reflected
 in the multi-participant dataset at a given timepoint $t$ using:
@@
 where $M$ extracts and vectorizes the upper triangle and diagonal of a symmetric
-matrix, $Z$ is the Fisher $z$-transformation~\citep{Zar10}:
+matrix, $Z$ is the Fisher $z$-transformation~\cite{Zar10}:
 \begin{align}
@@
 The modern toolkit of dimensionality reduction algorithms include
-Principal Components Analysis~\citep[PCA;][]{Pear01}, Probabilistic
-PCA~\citep[PPCA;][]{TippBish99}, Exploratory Factor
-Analysis~\citep[EFA;][]{Spea04}, Independent Components
-Analysis~\citep[ICA;][]{JuttHera91, ComoEtal91}, $t$-Stochastic
-Neighbor Embedding~\citep[$t$-SNE;][]{vandHint08}, Uniform Manifold
-Approximation and Projection~\citep[UMAP;][]{McInEtal18}, non-negative
-matrix factorization~\citep[NMF;][]{LeeSeun99}, Topographic Factor
-Analysis~\cite[TFA;][]{MannEtal14b}, Hierarchical Topographic Factor
-analysis~\cite[HTFA;][]{MannEtal18}, Topographic Latent Source
-Analysis~\cite[TLSA;][]{GersEtal11}, dictionary
-learning~\citep{MairEtal09a, MairEtal09b}, and deep
-auto-encoders~\citep{HintSala06}, among others.  While complete
+Principal Components Analysis~\cite{Pear01} (PCA), Probabilistic
+PCA~\cite{TippBish99} (PPCA), Exploratory Factor
+Analysis~\cite{Spea04} (EFA), Independent Components
+Analysis~\cite{JuttHera91, ComoEtal91} (ICA), $t$-Stochastic
+Neighbor Embedding~\cite{vandHint08} ($t$-SNE), Uniform Manifold
+Approximation and Projection~\cite{McInEtal18} (UMAP), non-negative
+matrix factorization~\cite{LeeSeun99} (NMF), Topographic Factor
+Analysis~\cite{MannEtal14b} (TFA), Hierarchical Topographic Factor
+analysis~\cite{MannEtal18} (HTFA), Topographic Latent Source
+Analysis~\cite{GersEtal11} (TLSA), dictionary
+learning~\cite{MairEtal09a, MairEtal09b}, and deep
+auto-encoders~\cite{HintSala06}, among others.  While complete
 characterizations of each of these algorithms is beyond the scope of
@@
 correlation matrix with respect to the rest of the population.  Widely
-used measures include betweenness centrality~\citep[the proportion of
+used measures include betweenness centrality (the proportion of
 shortest paths between each pair of nodes in the population that
-involves the given node in question; e.g.,][]{Newm05, OpsaEtal10,
-  Bart04, GeisEtal08, Free77}; diversity and
-dissimilarity~\citep[characterizations of how differently connected a
-given node is from others in the population; e.g.,][]{Rao82, Lin09,
-  RicoSzei06}; eigenvector centrality and pagerank
-centrality~\citep[measures of how influential a given node is within
-the broader network; e.g.,][]{Newm08, Bona07, LohmEtal10,
-  HaluEtal13}; transfer entropy and flow coefficients~\citep[a measure
+involves the given node in question~\cite{Newm05, OpsaEtal10,
+  Bart04, GeisEtal08, Free77}); diversity and
+dissimilarity (characterizations of how differently connected a
+given node is from others in the population~\cite{Rao82, Lin09,
+  RicoSzei06}); eigenvector centrality and pagerank
+centrality (measures of how influential a given node is within
+the broader network~\cite{Newm08, Bona07, LohmEtal10,
+  HaluEtal13}); transfer entropy and flow coefficients (a measure
 of how much information is flowing from a given node to other nodes in
-the network; e.g.,][]{HoneEtal07, Schr00}; $k$-coreness
-centrality~\citep[a measure of the connectivity of a node within its
-local subgraph; e.g.,][]{AlvaEtal05, ChriFowl10}; within-module
-degree~\citep[a measure of how many connections a node has to its
-close neighbors in the network; e.g.,][]{RubiSpor10}; participation
-coefficient~\citep[a measure of the diversity of a node's connections
-to different subgraphs in the network; e.g.,][]{RubiSpor10}; and
-subgraph centrality~\citep[a measure of a node's participation in all
-of the network's subgraphs; e.g.,][]{EstrRodr05}; among others.
+the network~\cite{HoneEtal07, Schr00}); $k$-coreness
+centrality (a measure of the connectivity of a node within its
+local subgraph~\cite{AlvaEtal05, ChriFowl10}); within-module
+degree (a measure of how many connections a node has to its
+close neighbors in the network~\cite{RubiSpor10}); participation
+coefficient (a measure of the diversity of a node's connections
+to different subgraphs in the network~\cite{RubiSpor10}); and
+subgraph centrality (a measure of a node's participation in all
+of the network's subgraphs~\cite{EstrRodr05}); among others.
 
@@
 neuroimaging data.  We constructed and leveraged the synthetic data to
-evaluate our general approach~\citep[for a related validation approach
-see][]{ThomEtal18}.  Specifically, we tested how well
+evaluate our general approach~\cite{ThomEtal18}.  Specifically, we tested how well
 Equation~\ref{eqn:timecorr} could be used to recover known dynamic
@@
 participants).  Full neuroimaging details may be found in the original
-paper for which the data were collected~\citep{SimoEtal16}. Procedures
+paper for which the data were collected~\cite{SimoEtal16}. Procedures
 were approved by the Princeton University Committee on Activities
@@
 \paragraph{Hierarchical topographic factor analysis (HTFA).}
-Following our prior related work, we used HTFA~\citep{MannEtal18} to
+Following our prior related work, we used HTFA~\cite{MannEtal18} to
 derive a compact representation of the neuroimaging data.  In brief,
@@
 voxels) using a much smaller number of radial basis function (RBF)
-nodes~\citep[in this case, 700 nodes, as determined by an optimization
-procedure described by][]{MannEtal18}.  This provides a convenient
+nodes (in this case, 700 nodes, as determined by an optimization
+procedure~\cite{MannEtal18}).  This provides a convenient
 representation for examining full-brain network dynamics.  All of the
@@
 matched across participants).  Code for carrying out HTFA on fMRI data
-may be found as part of the BrainIAK toolbox~\citep{CapoEtal17}, which
+may be found as part of the BrainIAK toolbox~\cite{CapoEtal17}, which
 may be downloaded at \href{https://brainiak.org/}{brainiak.org}.
@@
 extent that the corresponding cognitive representations are reflected
-in similar spatial patterns across people~\citep[also see][]{SimoChan20}.  Following this logic, we
+in similar spatial patterns across people~\cite{SimoChan20}.  Following this logic, we
 used an across-participant temporal decoding test developed by
@@
 weighted average of the $n+1$ matrices yielded the highest decoding
-accuracy.  We used quasi-Newton gradient ascent~\citep{NoceWrig06},
+accuracy.  We used quasi-Newton gradient ascent~\cite{NoceWrig06},
 using decoding accuracy (for $\mathcal{G}_{\mathrm{train}_1}$ and
@@
 1).  We then carried out a meta analysis using
-Neurosynth~\citep{RubiEtal17} to identify the 10 terms most commonly
+Neurosynth~\cite{RubiEtal17} to identify the 10 terms most commonly
 associated with the given map.  This resulted in a set of 10 terms

### 2021-08-12 paper/main.tex
made requested edits to fig 9 reference

@@
 template, the best-matching kernel was a Laplace kernel with a width
-of 50 (Fig.~\ref{fig:kernels}d; also see Fig.~\pca).  We used this kernel to compute a
+of 50 (see Kernel-based approach for computing dynamic correlations and Fig.~\pca).  We used this kernel to compute a
 single $K$ by $K$ $n^\mathrm{th}$-order DISFC matrix for each
@@
 \href{https://doi.org/10.5281/zenodo.5165253}{https://doi.org/10.5281/zenodo.5165253}.
-The source data underlying Figs. 2-6 and Supplementary Figs. S1-S9 are
-provided as a Source Data file. Source Data are provided with the
+The source data underlying Figures~2--6 and Supplementary Figures~S1--S9 are
+provided as Source Data files. Source Data are provided with the
 manuscript. The raw fMRI data are protected and are not available due to data
